### 2021-07-16 latex/main.tex
Create main.tex

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{letterpaper, margin=1.5in}
\usepackage{amsmath, amssymb, bm}
\usepackage{minted}

\newcommand{\SuperScreen}{\mintinline{python}{SuperScreen}\,}

\title{\texttt{SuperScreen}}
\author{Logan Bishop-Van Horn}
\date{\today}

\begin{document}

\maketitle

\section{Introduction}
\label{section:introduction}

\SuperScreen is an open-source Python package developed to simulate the magnetic response of structures composed of one or more layers containing superconducting thin films. \SuperScreen solves the coupled Maxwell's and London's equations in and around superconducting films with spatially-varying penetration depth in the presence of applied magnetic fields and trapped flux using a matrix inversion method introduced by Brandt [ref.] and initially implemented by Kirtley [ref, ref] to model the magnetic response of scanning superconducting quantum interference device (SQUID) sensors.

In Section~\ref{section:model} we outline Brandt's model, and in Section~\ref{section:implementation} we describe its numerical implementation. In Section~\ref{section:overview}, we provide an overview of the structure of the \SuperScreen package, highlighting important functions, classes, and features, and discuss some important development details. In Section~\ref{section:examples}, we demonstrate how to set up and solve several types of models using \SuperScreen. Finally, in Section~\ref{section:conlusion} we discuss potential applications, extensions, and improvements to the package.

\section{The Model}
\label{section:model}

The goal of \SuperScreen is to model the magnetic response of a thin superconducting film, or a structure composed of multiple superconducting films (which may or may not lie in the same plane), to an applied inhomogeneous out-of-plane magnetic field
$H_{z,\,\mathrm{applied}}(x, y, z)$.

Given $H_{z,\,\mathrm{applied}}(x, y, z)$ and information about the geometry and magnetic penetration depth of all films in a superconducting structure, we aim to calculate the thickness-integrated current density (or sheet current) $\vec{J}(x, y)$ at all points inside the films, from which one can calculate the vector magnetic field $\vec{H}(x, y, z)$ at all points both inside and outside the films.

A convenient method for solving this problem was introduced in [Brandt-PRB-2005], and used in [Kirtley-RSI-2016] and [Kirtley-SST-2016] to model the magnetic response of scanning Superconducting Quantum Interference Device (SQUID) susceptometers.

In the London model of superconductivity, the magnetic field $\vec{H}(\vec{r})$ and 3D current density $\vec{j}(\vec{r})$ in a superconductor with London penetration depth $\lambda(\vec{r})$ obey the second London equation:
$\nabla\times\vec{j}(\vec{r})=-\vec{H}(\vec{r})/\lambda^2(\vec{r})$, where
$\nabla=\left(\frac{\partial}{\partial x}, \frac{\partial}{\partial y}, \frac{\partial}{\partial z}\right)$.

Brandt's model assumes that the current density $\vec{j}$ is approximately independent of $z$, such $\vec{j}(\vec{r}) = \vec{j}(x, y, z)\approx\vec{j}_{z_0}(x, y)$ for a film lying parallel to the $x-y$ plane at vertical position $z_0$. Working now with the thickness-integrated current density (sheet current) $\vec{J}(x, y)=\vec{j}_{z_0}(x, y)\cdot d$, where $d$
is the thickness of the film, the second London equation reduces to

\begin{equation}
    \label{eq:london}
    \nabla\times\vec{J}(x, y)=-\vec{H}(x, y)/\Lambda(x, y),
\end{equation}

where $\Lambda(x, y)=\lambda^2(x, y)/d$ is the effective penetration depth
of the superconducting film (equal to half the Pearl length [Pearl-APL-1964]).

It is important to note that the assumption $\vec{j}(x, y, z)\approx\vec{j}_{z_0}(x, y)$ is valid for only films that are thinner than their London penetration depth ($d<\lambda$, such that $\Lambda=\lambda^2/d>\lambda$). However the model has been applied with some success in structures with $\lambda\lesssim d$ [Kirtley-RSI-2016] [Kirtley-SST-2016]. Aside from this limitation, the method described below can in principle to used to model films with any effective penetration depth $0\leq\Lambda<\infty$.

Because the sheet current has zero divergence in the superconducting film ($\nabla\cdot\vec{J}=0$)
except at small contacts where current can be injected, one can express the sheet current in terms
of a scalar potential $g(x, y)$, called the stream function:

\begin{equation}
    \label{eq:stream}
    \vec{J}(x, y) = -\hat{z}\times\nabla g
    = \nabla\times(g\hat{z})
    = \left(\frac{\partial g}{\partial y}, -\frac{\partial g}{\partial x}\right).
\end{equation}

The stream function $g$ can be thought of as the local magnetization of the film, or the area density of magnetic dipole sources (see [Brandt] for more interesting properties of the stream function). We can re-write Eq.~\ref{eq:london} for a 2D film in terms of $g$:

\begin{align}
    \label{eq:london_stream}
    \begin{split}
        \vec{H}(x, y) &= -\Lambda\left[\nabla\times\vec{J}(x, y)\right]\\
        &= -\Lambda\left[\nabla\times\left(\nabla\times(g\hat{z})\right)\right]\\
        &= -\Lambda\left[\nabla(\nabla\cdot(g\hat{z}))-\nabla^2(g\hat{z})\right]\\
        &=\Lambda\nabla^2g(x,y)\hat{z}\\
        &=H_z(x, y)\hat{z}
    \end{split}
\end{align}
where $\nabla^2=\nabla\cdot\nabla$ is the Laplace operator. (The fourth line follows from the fact that $\nabla\cdot\left(g(x,y)\hat{z}\right) = 0$). From Ampere's Law, the three components of the magnetic field at position $\vec{r}=(x, y, z)$ due to a sheet of current lying in the $x-y$ plane (at height $z'$) with stream function $g(x', y')$ are given by:

\begin{align}
    \label{eq:field_from_kernel}
    \begin{split}
        H_x(\vec{r}) &= \int_S Q_x(\vec{r},\vec{r}')g(x', y')\,\mathrm{d}^2r'\\
        H_y(\vec{r}) &= \int_S Q_y(\vec{r},\vec{r}')g(x', y')\,\mathrm{d}^2r'\\
        H_z(\vec{r}) &= H_{z,\,\mathrm{applied}}(\vec{r})
        + \int_S Q_z(\vec{r},\vec{r}')g(x', y')\,\mathrm{d}^2r'  
    \end{split}
\end{align}

Here we assume an applied magnetic field $\vec{H}_\mathrm{applied}(\vec{r}')=H_\mathrm{z,\,\mathrm{applied}}(\vec{r}')\hat{z}$. $S$ is the film area (with $g = 0$ outside of the film), and $Q_x(\vec{r},\vec{r}')$, $Q_y(\vec{r},\vec{r}')$, and $Q_z(\vec{r},\vec{r}')$ are dipole kernel functions which give the relevant component of the magnetic field at position $\vec{r}=(x, y, z)$ due to a dipole of unit strength at position $\vec{r}'=(x', y', z')$:

\begin{align}
    \label{eq:kernels}
    \begin{split}
        Q_x(\vec{r}, \vec{r}') &=  3\Delta z\frac{x-x'}
        {4\pi[(\Delta z)^2+\rho^2]^{5/2}}\\
        Q_y(\vec{r}, \vec{r}') &=  3\Delta z\frac{y-y'}
        {4\pi[(\Delta z)^2+\rho^2]^{5/2}}\\
        Q_z(\vec{r}, \vec{r}') &=  \frac{2(\Delta z)^2-\rho^2}
        {4\pi[(\Delta z)^2+\rho^2]^{5/2}},
    \end{split}
\end{align}
where $\Delta z = z - z'$ and $\rho=\sqrt{(x-x')^2 + (y-y')^2}$.

Comparing Eq.~\ref{eq:london_stream} and Eq.~\ref{eq:field_from_kernel}, we have in the plane of the film:

\begin{align}
    \label{eq:integral_equation}
    \begin{split}
        \underbrace{H_z(\vec{r}) = \vec{H}(\vec{r})\cdot\hat{z}
        = \Lambda\nabla^2g(x, y)}_{z-\text{component of the total field}}
        = \underbrace{H_{z,\,\mathrm{applied}}(\vec{r})}_{\text{applied field}}
        + \underbrace{\int_S Q_z(\vec{r},\vec{r}')g(\vec{r}')\,\mathrm{d}^2r'}_{\text{screening field}},
    \end{split}
\end{align}
(where now $\vec{r}$ and $\vec{r}'$ are 2D vectors, i.e. $\Delta z=0$, since the film is in the same plane as itself). From Eq.~\ref{eq:integral_equation}, we arrive at an integral equation relating the stream function $g$ for points inside the superconductor to the applied field $H_{z,\,\mathrm{applied}}$:

\begin{equation}
    \label{eq:applied_to_stream}
    H_{z,\,\mathrm{applied}}(\vec{r})
    = -\int_S\left[
        Q_z(\vec{r},\vec{r}')-\delta(\vec{r}-\vec{r}')\Lambda(\vec{r}')\nabla^2\right
    ]g(\vec{r}')\,\mathrm{d}^2r'
\end{equation}

The goal, then, is to solve (invert) Eq.~\ref{eq:applied_to_stream} for a given $H_{z,\,\mathrm{applied}}$ and film geometry $S$ to obtain $g$ for all points inside the film (with $g=0$ enforced outside the film). Once $g(\vec{r})$ is known, the full vector magnetic field $\vec{H}(\vec{r})$ can be calculated at any point $\vec{r}$
from Eqs.~\ref{eq:field_from_kernel} and \ref{eq:kernels}.

\subsection{Films with holes}
\label{section:model:holes}

In films that have holes (regions of vacuum completely surrounded by superconductor), each hole $k$ can contain a trapped flux $\Phi_k$, with an associated circulating current $I_{\mathrm{circ},\,k}$. The (hypothetical) applied field that would cause such a circulating current is given by Eq.~\ref{eq:applied_to_stream} if we set $g(\vec{r})=I_{\mathrm{circ},\,k}$ for all points $\vec{r}$ lying inside hole $k$:

\begin{equation}
    \label{eq:Heff}
    H_{z,\,\mathrm{eff},\,k}(\vec{r}) = -\int_{\mathrm{hole}\,k}[
        Q_z(\vec{r},\vec{r}')-\Lambda(\vec{r}')\nabla^2
    ] I_{\mathrm{circ},\,k} \,\mathrm{d}^2r'.   
\end{equation}

In this case, we modify the left-hand side of Eq.~\ref{eq:applied_to_stream} as follows:

\begin{equation}
    \label{eq:Heff_sub}
    H_{z,\,\mathrm{applied}}(\vec{r}) - \sum_k H_{z,\,\mathrm{eff},\,k}(\vec{r})
    = -\int_S\left[
        Q_z(\vec{r},\vec{r}')-\delta(\vec{r}-\vec{r}')\Lambda(\vec{r}')\nabla^2\right
    ]g(\vec{r}')\,\mathrm{d}^2r'.
\end{equation}

\subsection{Multi-layer structures}
\label{section:model:multilayer}

For structures with multiple films lying in different planes or layers, with layer $\ell$ lying in the plane $z=z_\ell$,
the stream functions and fields for all layers can be computed self-consistently using the following recipe:

\begin{enumerate}
    \item{
        Calculate the stream function $g_\ell(\vec{r})$ for each layer $\ell$ by solving Eq.~\ref{eq:Heff_sub} given an applied field $H_{z,\,\mathrm{applied}}(\vec{r}, z_\ell)$.
    }
    \item{
        For each layer $\ell$, calculate the $z$-component of the field due to the currents in all other layers $m\neq\ell$ (encoded in the stream function $g_m(\vec{r})$)
        using Eq.~\ref{eq:field_from_kernel}.
    }
    \item{
        Re-solve Eq.~\ref{eq:Heff_sub} taking the new applied field at each layer to be the original applied field plus the sum of screening fields from all other layers. This is accomplished via the substitution
        $$
            H_{z,\,\mathrm{applied}}(\vec{r}, z_\ell) \to
            H_{z,\,\mathrm{applied}}(\vec{r}, z_\ell)
            + \sum_{m\neq\ell}
            \int_S Q_z(\vec{r},\vec{r}')g_m(\vec{r}')\,\mathrm{d}^2r.
        $$
    }
    \item{
        Repeat steps 1-3 until the solution converges.
    }
\end{enumerate}

Convergence can be quantified by, for example, calculating the total magnetic flux though all films and holes in the model at the end of each iteration.

\section{Numerical Implementation}
\label{section:implementation}

In order to numerically solve Eq.~\ref{eq:field_from_kernel} and Eq.~\ref{eq:Heff_sub}, we have to discretize the films, holes, and the vacuum regions surrounding them. We use a triangular
(Delaunay) mesh, consisting of $n$ points (or vertices)
which together form $m$ triangles.

Below we denote column vectors and matrices using bold font. $\mathbf{A}\mathbf{B}$
denotes matrix multiplication, with $(\mathbf{A}\mathbf{B})_{ij}=\sum_{k=1}^\ell A_{ik}B_{kj}$
($\ell$ being the number of columns in $\mathbf{A}$ and the number of rows in $\mathbf{B}$). Column vectors are treated as matrices with $\ell$ rows and 1 column. On the other hand, we denote element-wise multiplication with a dot: $(\mathbf{A}\cdot\mathbf{B})_{ij}=A_{ij}B_{ij}$ for two matrices
and $(\mathbf{A}\cdot\mathbf{v})_{ij}=(\mathbf{v}\cdot\mathbf{A})_{ij}=A_{ij}v_{i}$ for a matrix $\mathbf{A}$ and a column vector $\mathbf{v}$.

The matrix version of Eq.~\ref{eq:field_from_kernel} is:

\begin{equation}
    \label{eq:field_from_kernel_num}
    \underbrace{\mathbf{h}_z}_\text{total field}
    = \underbrace{\mathbf{h}_{z,\,\mathrm{applied}}}_\text{applied field}
    + \underbrace{(\mathbf{Q}\cdot\mathbf{w})\mathbf{g}}_\text{screening field}.
\end{equation}

The kernel matrix $\mathbf{Q}$ and weight matrix $\mathbf{w}$ together play the role of the
kernel function $Q_z(\vec{r},\vec{r}')$ for all points lying in the plane of the film. They are both $n\times n$ matrices determined solely by the geometry of the mesh.
$\mathbf{h}_z$, $\mathbf{h}_{z,\,\mathrm{applied}}$, and $\mathbf{g}$ are all $n\times 1$ vectors, with each row representing the value of the quantity at the
corresponding vertex in the mesh. There are several different methods for constructing the weight matrix $\mathbf{w}$, which are discussed in Section[] below. The kernel
matrix $\mathbf{Q}$ is defined in terms of a matrix with
$(\mathbf{q})_{ij} = \left(4\pi|\vec{r}_i-\vec{r}_j|^3\right)^{-1}$
(which is $\lim_{\Delta z\to 0}Q_z(\vec{r},\vec{r}')$ cf. Eq.~\ref{eq:kernels}),
and a vector $\mathbf{C}$:

\begin{equation}
    \label{eq:kernel_matrix}
    Q_{ij} = (\delta_{ij}-1)q_{ij}
    + \delta_{ij}\frac{1}{w_{ij}}\left(C_i + \sum_{l\neq i}q_{il}w_{il}\right),
\end{equation}
where $\delta_{ij}$ is the Kronecker delta function. The diagonal terms involving $\mathbf{C}$ are meant to work around the fact that $q_{ii}$ diverge (see [Brandt-PRB-2005] for more details), and the vector is defined as

\begin{equation}
    \label{eq:C_vector}
    C_i = \frac{1}{4\pi}\sum_{p,q=\pm1}\sqrt{[\Delta x - p(x_i-\bar{x})]^{-2} + [\Delta y - q(y_i-\bar{y})]^{-2}},
\end{equation}
where $\Delta x=(x_\mathrm{max}-x_\mathrm{min})/2$ and $\Delta y=(y_\mathrm{max}-y_\mathrm{min})/2$ are half the side lengths of a rectangle bounding the modeled film and $(\bar{x}, \bar{y})$ are the coordinates of the center of the rectangle.

The matrix version of Eq.~\ref{eq:Heff_sub} is:

\begin{equation}
    \label{eq:Heff_sub_num}
     \mathbf{h}_{z,\,\mathrm{applied}} - \sum_{\mathrm{holes}\, k}\mathbf{h}_{z,\,\mathrm{eff},\,k} = -(\mathbf{Q}\cdot\mathbf{w}-\mathbf{\Lambda}\cdot\mathbf{\nabla}^2)\mathbf{g},
\end{equation}
where we exclude points in the mesh lying outside of the superconducting film, but keep points
inside holes in the film. $\mathbf{\Lambda}$ is either a scalar or a vector defining the effective penetration depth at every included vertex in the mesh, and $\mathbf{\nabla}^2$
is the Laplace operator (see Section[]), an $n\times n$ matrix defined such that $\mathbf{\nabla}^2\mathbf{f}$ computes the Laplacian $\nabla^2f(x,y)$ of a function $f(x,y)$ defined on the mesh.

Eq.~\ref{eq:Heff_sub_num} is a matrix equation relating the applied field to the stream function
inside a superconducting film, which can efficiently be solved (e.g. by matrix inversion or LU decomposition) for the unknown vector $\mathbf{g}$, the stream function inside the film. Since the stream function outside the film and inside holes in the film is already known, solving Eq.~\ref{eq:Heff_sub_num} gives us the stream function for the full mesh:

\begin{equation}
    \label{eq:full_stream}
    \mathbf{g} = \begin{cases}
        \left(-[\mathbf{Q}\cdot\mathbf{w}-\mathbf{\Lambda}\cdot\mathbf{\nabla}^2]\right)^{-1}
        \left(\mathbf{h}_{z,\,\mathrm{applied}} - \sum_{\mathrm{holes}\,k}\mathbf{h}_{z,\,\mathrm{eff},\,k}\right)
            & \text{inside the film}\\
        I_{\mathrm{circ},\,k}
            & \text{inside hole }k\\
        0
            & \text{elsewhere}
    \end{cases}
\end{equation}

Once the stream function $\mathbf{g}$ is known for the full mesh,
the sheet current flowing in the film can be computed from Eq.~\ref{eq:stream}, the $z$-component of the total field in the plane of the film can be computed
from Eq.~\ref{eq:field_from_kernel_num}, and the full vector magnetic field $\vec{H}(x, y, z)$
at any point in space can be computed from Eq.~\ref{eq:field_from_kernel}.

\subsection{Laplace operator}
\label{section:implementation:laplace}

The definition of the mesh Laplace operator $\mathbf{\nabla}^2$ (also called the Laplace-Beltrami operator [Laplacian-SGP-2014]) deserves special attention, as it reduces the problem of solving a partial differential equation $\nabla^2g(x,y)=f(x,y)$ to the problem of solving a matrix equation
$\mathbf{\nabla}^2\mathbf{g}=\mathbf{f}$. As described in [Vaillant-Laplacian-2013] and [Laplacian-SGP-2014] the Laplace operator $\mathbf{\nabla}^2$ for a mesh is defined in terms of two matrices, the mass matrix $\mathbf{M}$ and the
Laplacian matrix $\mathbf{L}$: $\mathbf{\nabla}^2 = \mathbf{M}^{-1}\mathbf{L}$.

In a 2D mesh, the mass matrix gives an effective area to each vertex in the mesh. There are multiple ways to construct the mass matrix, but here we use a ``lumped" mass matrix, which is diagonal with elements $(\mathbf{M})_{ii} = \frac{1}{3}\sum_{t\in\mathcal{N}(i)}\mathrm{area}(t)$,
where $\mathcal{N}(i)$ is the set of triangles $t$ adjacent to vertex $i$.

Each element $w_{ij}$ of the symmetric weight matrix $\mathbf{w}$ assigns a weight to the edge connecting vertex $i$ and vertex $j$ in the mesh. We use a normalized version of the weight matrix, where the sum of all off-diagonal elements in each row (or column) is 1, and each diagonal element is 1. Thus we can write $\mathbf{w}$ in terms of an un-normalized weight matrix $\mathbf{W}$:
$$
    w_{ij} = \begin{cases}
        1&\text{if }i = j\\
        W_{ij} / \sum_{i\neq j} W_{ij}&\text{otherwise}
    \end{cases}
$$

There are several different methods for constructing the un-normalized weight matrix $\mathbf{W}$:

\begin{enumerate}
    \item{
        Uniform weighting: In this case, $\mathbf{W}$ is simply the adjacency matrix for the mesh:
        $$
            W_{ij} =
            \begin{cases}
                0&\text{if }i=j\\
                1&\text{if }i\text{ is adjacent to }j\\
                0&\text{otherwise}
            \end{cases}
        $$
    }
    \item{
        Inverse-Euclidean weighting: Each edge is weighted by the inverse of its length: $|\vec{r}_i-\vec{r}_j|^{-1}$, where $\vec{r}_i$ is the position of vertex $i$.
        $$
            W_{ij} =
            \begin{cases}
                0&\text{if }i=j\\
                |\vec{r}_i-\vec{r}_j|^{-1}&\text{if }i\text{ is adjacent to }j\\
                0&\text{otherwise}
            \end{cases}
        $$
    }
    \item{
        Half-cotangent weighting: Each edge is weighted by the half the sum of the cotangents of the two angles opposite to it.
        $$
            W_{ij} =
            \begin{cases}
                0&\text{if }i=j\\
                \frac{1}{2}\left(\cot\alpha_{ij}+\cot\beta_{ij}\right)&\text{if }i\text{ is adjacent to }j\\
                0&\text{otherwise}
            \end{cases}
        $$
    }
\end{enumerate}

By default, \SuperScreen uses half-cotangent weighting. The Laplacian matrix $\mathbf{L}$ is defined in terms of the weight matrix $\mathbf{w}$: $(\mathbf{L})_{ij} = (\mathbf{w})_{ij} - \delta_{ij}\sum_{\ell}w_{i\ell}$. Finally, the Laplace operator is given by $\mathbf{\nabla}^2 = \mathbf{M}^{-1}\mathbf{L}$.

\section{Package Overview}
\label{section:overview}

In this section we give a high-level overview of the \SuperScreen package. More detailed documentation and tutorials can be found at superscreen.readthedocs.io.

\subsection{Parameters}
\label{section:overview:parameter}

A \mintinline{python}{superscreen.Parameter} is a wrapper around a Python function that computes a scalar value as a function of position coordinates ($x$, $y$, and optionally $z$) based on some keyword arguments. Addition, subtraction, multiplication, division, and exponentiation between \mintinline{python}{Parameters}, other \mintinline{python}{Parameters}, and Python scalars (\mintinline{python}{int} and \mintinline{python}{float}) are supported. For example:

\begin{minted}{python}
from superscreen import Parameter

def f(x, y, a=1, b=0):
    return a * x**2 + b * y

param = Parameter(f, a=0, b=1)
print(param)  # Parameter<f(a=0, b=1)>

other_param = Parameter(f, a=2, b=3)
print(other_param)  # Parameter<f(a=2, b=3)>

print(param(0, 0) == f(0, 0, a=0, b=1))  # True
print(other_param(1, 2) == f(1, 2, a=2, b=3))  # True

param_squared = param ** 2
print(param_squared)  # CompositeParameter<(f(a=0, b=1) ** 2)>

print(param_squared(3, 4) == f(3, 4, a=0, b=1) ** 2) # True
print(
    (5 * param_squared / other_param)(5, 6)
    == 5 * f(5, 6, a=0, b=1) ** 2 / f(5, 6, a=2, b=3)
)  # True
\end{minted}

\mintinline{python}{Parameters} can be used to define applied magnetic fields and penetration depths that depend on position.

\subsection{Devices}
\label{section:overview:device}

Information about the geometry and penetration depth of a superconducting structure is described by an instance of the \mintinline{python}{superscreen.Device} class. A \mintinline{python}{Device} is made up of one or more superconducting layers, each an instance of  \mintinline{python}{superscreen.Layer}. Each layer sits in a specified plane parallel to the $x-y$ plane and has its own effective penetration depth $\Lambda$, which can either be a constant or a \mintinline{python}{superscreen.Parameter} wrapping a function that computes $\Lambda(x, y)$, the penetration depth as a function of position. The effective penetration depth $\Lambda$ can instead be defined in terms of a layer's London penetration depth $\lambda$ and its thickness $d$: $\Lambda=\lambda^2/d$, in which case the London penetration depth can be either a constant or a \mintinline{python}{superscreen.Parameter}.

Each layer can contain one or more superconducting films which may have one or more holes in them. Films and holes are represented by instances of the \mintinline{python}{superscreen.Polygon} class. A \mintinline{python}{Polygon} contains the name of the layer to which is belongs, an array specifying the coordinates of its vertices, and a method, \mintinline{python}{Polygon.contains_points()}, which determines whether specified coordinates lie within the polygon or not. In addition to superconducting films and holes, one may define ``abstract regions,'' which are polygons that need not correspond to a physical feature in the structure, but will still be meshed. Abstract regions can be used to define a ``bounding box" around a structure.

Once the layers, films, holes, and abstract regions have been defined, one can generate the computational mesh by calling \mintinline{python}{Device.make_mesh()}. The region that is meshed is defined by the convex hull of the union of all polygons in the device. After the mesh is generated, the matrices and vectors described in Section~\ref{section:implementation} can be computed and one can begin solving models.

\subsection{Solvers}
\label{section:overview:solvers}

A \SuperScreen model consists of a \mintinline{python}{Device}, a function or \mintinline{python}{Parameter} that computes the applied magnetic field as a function of position $H_{z,\,\mathrm{applied}}(x, y, z)$, and (optionally) a value for the current circulating around each hole in the device due to trapped flux. These items serve as the inputs to \SuperScreen's main solver function, \mintinline{python}{superscreen.solve()}, which implements the calculation outlined in Section~\ref{section:implementation}. When simulating a device with more than one layer, one can specify the number of times to implement the iterative calculation described in Section~\ref{section:model:multilayer} in order to solve for the response of all layers self-consistently. One can also skip the iterative portion of the calculation entirely and only solve for the response of each layer to the applied field, assuming interaction between layers.

The output of \mintinline{python}{superscreen.solve()} is a \mintinline{python}{list} of \mintinline{python}{superscreen.Solution} objects, with a length of 1 plus the number of iterations used for the iterative portion of the calculation. A \mintinline{python}{Solution} encapsulates all of the information about a solved model: the \mintinline{python}{Device}, applied field, circulating currents, and calculated stream functions and screening fields for all layers in the device. A \mintinline{python}{Solution} also has methods for processing the simulation results, including:
\begin{itemize}
    \item{
    \mintinline{python}{Solution.grid_data()}: Interpolates the calculated stream functions and magnetic fields for each layer from the triangular mesh to a rectangular grid.
    }
    \item{
    \mintinline{python}{Solution.current_density()}: Interpolates the stream functions to a rectangular grid and calculates the current density (sheet current) $\vec{J}(x, y)$ in each layer using Eq.~\ref{eq:stream}.
    }
    \item{
    \mintinline{python}{Solution.polygon_flux()}: Calculates the total flux through each polygon in the device (films, holes, and abstract regions).
    }
    \item{
    \mintinline{python}{Solution.field_at_position()}: Calculates the vector magnetic field at any point(s) in space due the applied field and the currents flowing the in the device using Eqs.~\ref{eq:field_from_kernel} and \ref{eq:kernels}.
    }
\end{itemize}

One may wish to solve many models involving the same device while varying other aspects of the model, for example sweeping the applied field, circulating currents, or some parameter of one or more layers in the device. Fortunately, the mesh and large matrices described in Section~\ref{section:implementation} depend only on the geometry of the device parallel to the $x-y$ plane. This means that the same mesh and matrices can be re-used for models with different applied fields, circulating currents, layer heights, and layer penetration depths.

The \mintinline{python}{superscreen.solve_many()} function is designed to do just that. One can provide a sequence of \mintinline{python}{superscreen.Parameter} objects defining different applied fields and/or a sequence of circulating current values over which to sweep. One can also provide a ``layer updater" function that modifies each layer in the device according to some set of keyword arguments, which can also be swept. The latter option can be used to sweep layer heights or penetration depths. Given these inputs, \mintinline{python}{superscreen.solve_many()} will generate and solve all of the corresponding models. The models can either be solved in series in a single Python process (the default), or in parallel across multiple Python processes running on different CPUs. In either case, only a single copy of the device's mesh and large arrays is created, so the memory footprint is modest.

\subsection{Visualization}
\label{section:overview:visualization}

\SuperScreen offers several functions for visualizing the results of simulations (which are also aliased as method on \mintinline{python}{superscreen.Solution}):

\begin{itemize}
    \item{
    \mintinline{python}{superscreen.plot_streams()}: Given a \mintinline{python}{Solution}, plots the stream function $g(x, y)$ for one or more layers in the device. See also \mintinline{python}{Solution.plot_streams()}.
    }
    \item{
    \mintinline{python}{superscreen.plot_currents()}: Given a \mintinline{python}{Solution}, plots the sheet current $\vec{J}(x, y)$ for one or more layers in the device. See also \mintinline{python}{Solution.plot_currents()}.
    }
    \item{
    \mintinline{python}{superscreen.plot_fields()}: Given a \mintinline{python}{Solution}, plots the total field $H_z(x, y)$ or the screening field $H_z(x, y) - H_{z,\,\mathrm{applied}}(x, y)$ for one or more layers in the device. See also \mintinline{python}{Solution.plot_fields()}.
    }
    \item{
    \mintinline{python}{superscreen.plot_field_at_positions()}: Given a \mintinline{python}{Solution}, plots the total field $\vec{H}(x, y, z_0)$ or $H_z(x, y, z_0)$ at any points in space (where $z_0$ is not equal to the vertical position of any of the layers in the device). See also \mintinline{python}{Solution.plot_field_at_positions()}.
    }
\end{itemize}

See Section~\ref{section:examples} for examples of the figures generated by these functions.

\subsection{Comparison \& Persistence}
\label{section:overview:persistence}

\mintinline{python}{Parameters}, \mintinline{python}{Layers}, \mintinline{python}{Polygons}, \mintinline{python}{Devices}, and \mintinline{python}{Solutions} all implement the equality operator, \mintinline{python}{==}. Two \mintinline{python}{Parameters} are considered equal if the Python bytecode of their underlying functions is the same and their keyword arguments are the same. Two \mintinline{python}{Layers} are equal if their name, penetration depth, thickness, and vertical position are all equal. Two \mintinline{python}{Polygons} are equal if they are in the same layer and their name and polygon vertices are equal. Two \mintinline{python}{Devices} are equal if their name, layers, films, holes, and abstract regions are all equal. Two \mintinline{python}{Solutions} are equal if their device, applied field, circulating currents, timestamp (time at which the solution was created), and all stream function and magnetic field arrays are equal. Two solutions created at different times can also be compared by calling \mintinline{python}{solution.equal(other_solution, require_same_timestamp=False)}.

Instances of \mintinline{python}{superscreen.Device} and \mintinline{python}{superscreen.Solution} can be saved to and loaded from disk using their respective \mintinline{python}{to_file()} and \mintinline{python}{from_file()} methods, making it straightforward to share models and simulation results. \mintinline{python}{Layers}, \mintinline{python}{Polygons}, and all metadata are serialized to JSON, a widely-used, human-readable plain text format. Functions and \mintinline{python}{Parameters}, such as those that compute the applied field or penetration depth, are serialized in binary form using \mintinline{python}{dill}. \mintinline{python}{numpy} arrays, such as the mesh itself and the computed stream functions and fields, are saved in the well-established \mintinline{python}{numpy} \mintinline{python}{npz} file format. A \mintinline{python}{list} of \mintinline{python}{Solutions}, such as that returned by \mintinline{python}{superscreen.solve()} can be saved/loaded all at once using \mintinline{python}{superscreen.save_solutions()}/\mintinline{python}{superscreen.load_solutions()}.

\subsection{Development Details}
\label{section:overview:development}

\SuperScreen requires Python version 3.6 or later. The package is located in a public repository on GitHub, and a suite of unit tests is run automatically via GitHub Actions whenever a change or proposed change (Pull Request) is made to the \mintinline{python}{main} branch of the repository. At the time of writing, the test suite is executed using Python versions 3.6, 3.7, 3.8, and 3.9, and the test coverage is XX\%. Any changes to the \mintinline{python}{main} branch of the repository also trigger an automatic re-build of the online documentation, hosted by Read the Docs at superscreen.readthedocs.io. Stable versions of the package are tagged on GitHub and uploaded to PyPI, the Python Package Index. The source code and documentation are covered by the MIT License.

\SuperScreen has several important dependencies beyond the Python standard library: \mintinline{python}{numpy} and \mintinline{python}{scipy} for numerics, \mintinline{python}{pint} for handling physical units, \mintinline{python}{matplotlib} for visualization, \mintinline{python}{meshpy} and \mintinline{python}{optimesh} for mesh generation, \mintinline{python}{dill} for serializing objects to disk and between processes, and \mintinline{python}{ray} for parallel processing with shared memory.

\section{Examples}
\label{section:examples}

\subsection{Screening}
\label{section:example:screening}

\subsection{Inductance}
\label{section:examples:inductance}

\subsection{Mutual Inductance}
\label{section:examples:mutual-inductance}

\subsection{SQUID Susceptometry}
\label{section:examples:susceptometry}

\subsection{Parallel Processing}
\label{section:examples:parallel}

\section{Conclusion}
\label{section:conlusion}

\end{document}

### 2021-07-16 main.tex
Add citations

--- 2021-07-16 latex/main.tex
@@
 \SuperScreen is an open-source Python package developed to simulate the magnetic response of structures composed of one or more layers containing superconducting thin films.
-\SuperScreen solves the coupled Maxwell's and London's equations in and around superconducting films with spatially-varying penetration depth in the presence of applied magnetic fields and trapped flux using a matrix inversion method introduced by Brandt [ref.] and initially implemented by Kirtley [ref, ref] to model the magnetic response of scanning superconducting quantum interference device (SQUID) sensors.
+\SuperScreen solves the coupled Maxwell's and London's equations in and around superconducting films with spatially-varying penetration depth in the presence of applied magnetic fields and trapped flux using a matrix inversion method introduced by Brandt~\cite{brandt_thin_2005} and initially implemented by Kirtley, \emph{et al.}~\cite{kirtley_scanning_2016, kirtley_response_2016} to model the magnetic response of scanning superconducting quantum interference device (SQUID) sensors.
 
@@
 
-A convenient method for solving this problem was introduced in [Brandt-PRB-2005], and used in [Kirtley-RSI-2016] and [Kirtley-SST-2016] to model the magnetic response of scanning Superconducting Quantum Interference Device (SQUID) susceptometers.
+A convenient method for solving this problem was introduced in~\cite{brandt_thin_2005}, and used to model the magnetic response of scanning Superconducting Quantum Interference Device (SQUID) susceptometers~\cite{kirtley_scanning_2016, kirtley_response_2016}.
 
@@
 where $\Lambda(x, y)=\lambda^2(x, y)/d$ is the effective penetration depth
-of the superconducting film (equal to half the Pearl length [Pearl-APL-1964]).
+of the superconducting film (equal to half the Pearl length~\cite{pearl_current_1964}).
 
 It is important to note that the assumption $\vec{j}(x, y, z)\approx\vec{j}_{z_0}(x, y)$ is valid for only films that are thinner than their London penetration depth ($d<\lambda$, such that $\Lambda=\lambda^2/d>\lambda$).
-However the model has been applied with some success in structures with $\lambda\lesssim d$ [Kirtley-RSI-2016] [Kirtley-SST-2016].
+However the model has been applied with some success in structures with $\lambda\lesssim d$~\cite{kirtley_scanning_2016,kirtley_response_2016}.
 Aside from this limitation, the method described below can in principle to used to model films with any effective penetration depth $0\leq\Lambda<\infty$.
@@
 
-The stream function $g$ can be thought of as the local magnetization of the film, or the area density of magnetic dipole sources (see [Brandt] for more interesting properties of the stream function).
+The stream function $g$ can be thought of as the local magnetization of the film, or the area density of magnetic dipole sources (see \cite{brandt_thin_2005} for more interesting properties of the stream function).
 We can re-write Eq.~\ref{eq:london} for a 2D film in terms of $g$:
@@
 $\mathbf{h}_z$, $\mathbf{h}_{z,\,\mathrm{applied}}$, and $\mathbf{g}$ are all $n\times 1$ vectors, with each row representing the value of the quantity at the
-corresponding vertex in the mesh. There are several different methods for constructing the weight matrix $\mathbf{w}$, which are discussed in Section[] below. The kernel
+corresponding vertex in the mesh.
+There are several different methods for constructing the weight matrix $\mathbf{w}$, which are discussed in Section~\ref{section:implementation:laplace} below.
+The kernel
 matrix $\mathbf{Q}$ is defined in terms of a matrix with
@@
 where $\delta_{ij}$ is the Kronecker delta function.
-The diagonal terms involving $\mathbf{C}$ are meant to work around the fact that $q_{ii}$ diverge (see [Brandt-PRB-2005] for more details), and the vector is defined as
+The diagonal terms involving $\mathbf{C}$ are meant to work around the fact that $q_{ii}$ diverge (see \cite{brandt_thin_2005} for more details), and the vector is defined as
 
@@
 inside holes in the film. $\mathbf{\Lambda}$ is either a scalar or a vector defining the effective penetration depth at every included vertex in the mesh, and $\mathbf{\nabla}^2$
-is the Laplace operator (see Section[]), an $n\times n$ matrix defined such that $\mathbf{\nabla}^2\mathbf{f}$ computes the Laplacian $\nabla^2f(x,y)$ of a function $f(x,y)$ defined on the mesh.
+is the Laplace operator (see Section~\ref{section:implementation:laplace}), an $n\times n$ matrix defined such that $\mathbf{\nabla}^2\mathbf{f}$ computes the Laplacian $\nabla^2f(x,y)$ of a function $f(x,y)$ defined on the mesh.
 
@@
 
+\bibliographystyle{plain}
+\bibliography{references}
+
 \end{document}

### 2021-07-29 main_cpc.tex
Add CPC template

--- 2021-07-16 main.tex
@@
-\documentclass{article}
-\usepackage[utf8]{inputenc}
-\usepackage{geometry}
-\geometry{letterpaper, margin=1.5in}
+%% This template can be used to write a paper for
+%% Computer Physics Communications using LaTeX.
+%% For authors who want to write a computer program description,
+%% an example Program Summary is included that only has to be
+%% completed and which will give the correct layout in the
+%% preprint and the journal.
+%% The `elsarticle' style is used and more information on this style
+%% can be found at 
+%% http://www.elsevier.com/wps/find/authorsview.authors/elsarticle.
+%%
+%%
+\documentclass[preprint,12pt]{elsarticle}
+
+%% Use the option review to obtain double line spacing
+%% \documentclass[preprint,review,12pt]{elsarticle}
+
+%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
+%% for a journal layout:
+% \documentclass[final,1p,times]{elsarticle}
+% \documentclass[final,1p,times,twocolumn]{elsarticle}
+% \documentclass[final,3p,times]{elsarticle}
+% \documentclass[final,3p,times,twocolumn]{elsarticle}
+%% \documentclass[final,5p,times]{elsarticle}
+% \documentclass[final,5p,times,twocolumn]{elsarticle}
+
+%% if you use PostScript figures in your article
+%% use the graphics package for simple commands
+%% \usepackage{graphics}
+%% or use the graphicx package for more complicated commands
+%% \usepackage{graphicx}
+%% or use the epsfig package if you prefer to use the old commands
+%% \usepackage{epsfig}
+
+%% The amssymb package provides various useful mathematical symbols
 \usepackage{amsmath, amssymb, bm}
+%% The amsthm package provides extended theorem environments
+%% \usepackage{amsthm}
+
+%% The lineno packages adds line numbers. Start line numbering with
+%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
+%% for the whole article with \linenumbers after \end{frontmatter}.
+%% \usepackage{lineno}
+
+%% natbib.sty is loaded by default. However, natbib options can be
+%% provided with \biboptions{...} command. Following options are
+%% valid:
+
+%%   round  -  round parentheses are used (default)
+%%   square -  square brackets are used   [option]
+%%   curly  -  curly braces are used      {option}
+%%   angle  -  angle brackets are used    <option>
+%%   semicolon  -  multiple citations separated by semi-colon
+%%   colon  - same as semicolon, an earlier confusion
+%%   comma  -  separated by comma
+%%   numbers-  selects numerical citations
+%%   super  -  numerical citations as superscripts
+%%   sort   -  sorts multiple citations according to order in ref. list
+%%   sort&compress   -  like sort, but also compresses numerical citations
+%%   compress - compresses without sorting
+%%
+%% \biboptions{comma,round}
+
+% \biboptions{}
+
+%% This list environment is used for the references in the
+%% Program Summary
+%%
+\newcounter{bla}
+\newenvironment{refnummer}{%
+\list{[\arabic{bla}]}%
+{\usecounter{bla}%
+ \setlength{\itemindent}{0pt}%
+ \setlength{\topsep}{0pt}%
+ \setlength{\itemsep}{0pt}%
+ \setlength{\labelsep}{2pt}%
+ \setlength{\listparindent}{0pt}%
+ \settowidth{\labelwidth}{[9]}%
+ \setlength{\leftmargin}{\labelwidth}%
+ \addtolength{\leftmargin}{\labelsep}%
+ \setlength{\rightmargin}{0pt}}}
+ {\endlist}
+
 \usepackage{minted}
+\usepackage{hyperref}
 
@@
 
-\title{\texttt{SuperScreen}}
-\author{Logan Bishop-Van Horn}
-\date{\today}
+\journal{Computer Physics Communications}
 
@@
 
-\maketitle
+\begin{frontmatter}
 
+%% Title, authors and addresses
+
+%% use the tnoteref command within \title for footnotes;
+%% use the tnotetext command for the associated footnote;
+%% use the fnref command within \author or \address for footnotes;
+%% use the fntext command for the associated footnote;
+%% use the corref command within \author for corresponding author footnotes;
+%% use the cortext command for the associated footnote;
+%% use the ead command for the email address,
+%% and the form \ead[url] for the home page:
+%%
+%% \title{Title\tnoteref{label1}}
+%% \tnotetext[label1]{}
+%% \author{Name\corref{cor1}\fnref{label2}}
+%% \ead{email address}
+%% \ead[url]{home page}
+%% \fntext[label2]{}
+%% \cortext[cor1]{}
+%% \address{Address\fnref{label3}}
+%% \fntext[label3]{}
+
+\title{\texttt{SuperScreen}: An open-source package for simulating the magnetic response of 2D superconductors}
+
+%% use optional labels to link authors explicitly to addresses:
+%% \author[label1,label2]{<author name>}
+%% \address[label1]{<address>}
+%% \address[label2]{<address>}
+
+\author[a]{Logan Bishop-Van Horn}
+\author[a,b]{Kam Moler\corref{author}}
+
+\cortext[author]{Corresponding author.\\\textit{E-mail address:} kmoler@stanford.edu}
+\address[a]{First Address}
+\address[b]{Second Address}
+
+\begin{abstract}
+%% Text of abstract
+A submitted program is expected to satisfy the following criteria: it must be of benefit to other physicists, or be an exemplar of good programming practice, or illustrate new or novel programming techniques which are of importance to computational physics community; it should be implemented in a language and executable on hardware that is widely available and well documented; it should meet accepted standards for scientific programming; it should be adequately documented and, where appropriate, supplied with a separate User Manual, which together with the manuscript should make clear the structure, functionality, installation, and operation of the program.
+
+Your manuscript and figure sources should be submitted through Editorial Manager (EM) by using the online submission tool at \\
+https://www.editorialmanager.com/comphy/.
+
+In addition to the manuscript you must supply: the program source code; a README file giving the names and a brief description of the files/directory structure that make up the package and clear instructions on the installation and execution of the program; sample input and output data for at least one comprehensive test run; and, where appropriate, a user manual.
+
+A compressed archive program file or files, containing these items, should be uploaded at the "Attach Files" stage of the EM submission.
+
+For files larger than 1Gb, if difficulties are encountered during upload the author should contact the Technical Editor at cpc.mendeley@gmail.com.
+
+\end{abstract}
+
+\begin{keyword}
+%% keywords here, in the form: keyword \sep keyword
+keyword1; keyword2; keyword3; etc.
+
+\end{keyword}
+
+\end{frontmatter}
+
+%%
+%% Start line numbering here if you want
+%%
+% \linenumbers
+
+% All CPiP articles must contain the following
+% PROGRAM SUMMARY.
+\noindent
+{\bf PROGRAM SUMMARY}
+
+\begin{small}
+\noindent
+{\em SuperScreen:}\\
+{\em CPC Library link to program files:} (to be added by Technical Editor) \\
+{\em Developer's repository link:} \href{http://www.github.com/loganbvh/superscreen}{www.github.com/loganbvh/superscreen}\\
+{\em Code Ocean capsule:} (to be added by Technical Editor)\\
+{\em Licensing provisions:} MIT\\
+{\em Programming language: Python}\\
+{\em Supplementary material:}\\
+  % Fill in if necessary, otherwise leave out.
+% {\em Journal reference of previous version:}*\\
+  %Only required for a New Version summary, otherwise leave out.
+% {\em Does the new version supersede the previous version?:}*\\
+  %Only required for a New Version summary, otherwise leave out.
+% {\em Reasons for the new version:*}\\
+  %Only required for a New Version summary, otherwise leave out.
+% {\em Summary of revisions:}*\\
+  %Only required for a New Version summary, otherwise leave out.
+{\em Nature of problem(approx. 50-250 words):}\\
+  %Describe the nature of the problem here. \\
+{\em Solution method(approx. 50-250 words):}\\
+  %Describe the method solution here.
+{\em Additional comments including restrictions and unusual features (approx. 50-250 words):}\\
+  %Provide any additional comments here.
+   \\
+
+% \begin{thebibliography}{0}
+% \bibitem{1}Reference 1         % This list should only contain those items referenced in the                 
+% \bibitem{2}Reference 2         % Program Summary section.   
+% \bibitem{3}Reference 3         % Type references in text as [1], [2], etc.
+%                               % This list is different from the bibliography at the end of 
+%                               % the Long Write-Up.
+% \end{thebibliography}
+\end{small}
+
+%% main text
 \section{Introduction}
@@
 In Section~\ref{section:model} we outline Brandt's model, and in Section~\ref{section:implementation} we describe its numerical implementation.
-In Section~\ref{section:overview}, we provide an overview of the structure of the \SuperScreen package, highlighting important functions, classes, and features, and discuss some important development details.
+In Section~\ref{section:overview}, we provide an overview of the structure of the \SuperScreen package, highlighting notable functions, classes, and features, and discuss some important development details.
 In Section~\ref{section:examples}, we demonstrate how to set up and solve several types of models using \SuperScreen.
@@
 
-A convenient method for solving this problem was introduced in~\cite{brandt_thin_2005}, and used to model the magnetic response of scanning Superconducting Quantum Interference Device (SQUID) susceptometers~\cite{kirtley_scanning_2016, kirtley_response_2016}.
+A convenient method for solving this problem was introduced by Brandt in~\cite{brandt_thin_2005}, and subsequently used to model the magnetic response of scanning Superconducting Quantum Interference Device (SQUID) susceptometers~\cite{kirtley_scanning_2016, kirtley_response_2016}.
 
@@
 $\nabla=\left(\frac{\partial}{\partial x}, \frac{\partial}{\partial y}, \frac{\partial}{\partial z}\right)$.
-
 Brandt's model assumes that the current density $\vec{j}$ is approximately independent of $z$, such $\vec{j}(\vec{r}) = \vec{j}(x, y, z)\approx\vec{j}_{z_0}(x, y)$ for a film lying parallel to the $x-y$ plane at vertical position $z_0$.
-Working now with the thickness-integrated current density (sheet current) $\vec{J}(x, y)=\vec{j}_{z_0}(x, y)\cdot d$, where $d$
+Working now with the thickness-integrated current density (sheet current) $\vec{J}(x, y)\approx\vec{j}_{z_0}(x, y)\cdot d$, where $d$
 is the thickness of the film, the second London equation reduces to
@@
 \end{equation}
-
 where $\Lambda(x, y)=\lambda^2(x, y)/d$ is the effective penetration depth
@@
 where $\nabla^2=\nabla\cdot\nabla$ is the Laplace operator.
-(The fourth line follows from the fact that $\nabla\cdot\left(g(x,y)\hat{z}\right) = 0$).
-From Ampere's Law, the three components of the magnetic field at position $\vec{r}=(x, y, z)$ due to a sheet of current lying in the $x-y$ plane (at height $z'$) with stream function $g(x', y')$ are given by:
+(The fourth line follows from the fact that $\nabla\cdot\left[g(x,y)\hat{z}\right] = 0$).
+From Ampere's Law, the three components of the magnetic field at position $\vec{r}=(x, y, z)$ due to a sheet of current lying in the $x-y$ plane (at vertical position $z'$) with stream function $g(x', y')$ are given by:
 
@@
 
-Here we assume an applied magnetic field $\vec{H}_\mathrm{applied}(\vec{r}')=H_\mathrm{z,\,\mathrm{applied}}(\vec{r}')\hat{z}$.
+Here we assume an out-of-plane applied magnetic field $\vec{H}_\mathrm{applied}(\vec{r}')=H_\mathrm{z,\,\mathrm{applied}}(\vec{r}')\hat{z}$.
 $S$ is the film area (with $g = 0$ outside of the film), and $Q_x(\vec{r},\vec{r}')$, $Q_y(\vec{r},\vec{r}')$, and $Q_z(\vec{r},\vec{r}')$ are dipole kernel functions which give the relevant component of the magnetic field at position $\vec{r}=(x, y, z)$ due to a dipole of unit strength at position $\vec{r}'=(x', y', z')$:
@@
     \begin{split}
-        Q_x(\vec{r}, \vec{r}') &=  3\Delta z\frac{x-x'}
-        {4\pi[(\Delta z)^2+\rho^2]^{5/2}}\\
-        Q_y(\vec{r}, \vec{r}') &=  3\Delta z\frac{y-y'}
-        {4\pi[(\Delta z)^2+\rho^2]^{5/2}}\\
-        Q_z(\vec{r}, \vec{r}') &=  \frac{2(\Delta z)^2-\rho^2}
-        {4\pi[(\Delta z)^2+\rho^2]^{5/2}},
+        Q_x(\vec{r}, \vec{r}') &=  3\frac{(x-x')(z-z')}
+        {4\pi[(z-z')^2+\rho^2]^{5/2}}\\
+        Q_y(\vec{r}, \vec{r}') &=  3\frac{(y-y')(z-z')}
+        {4\pi[(z-z')^2+\rho^2]^{5/2}}\\
+        Q_z(\vec{r}, \vec{r}') &=  \frac{2(z-z')^2-\rho^2}
+        {4\pi[(z-z')^2+\rho^2]^{5/2}},
     \end{split}
 \end{align}
-where $\Delta z = z - z'$ and $\rho=\sqrt{(x-x')^2 + (y-y')^2}$.
+where $\rho=\sqrt{(x-x')^2 + (y-y')^2}$.
 
@@
     \label{eq:Heff_sub}
-    H_{z,\,\mathrm{applied}}(\vec{r}) - \sum_k H_{z,\,\mathrm{eff},\,k}(\vec{r})
+    H_{z,\,\mathrm{applied}}(\vec{r}) - \sum_{\mathrm{holes}\,k} H_{z,\,\mathrm{eff},\,k}(\vec{r})
     = -\int_S\left[
@@
 (Delaunay) mesh, consisting of $n$ points (or vertices)
-which together form $m$ triangles.
-
-Below we denote column vectors and matrices using bold font. $\mathbf{A}\mathbf{B}$
+which together form $m$ triangles. Below we denote column vectors and matrices using bold font. $\mathbf{A}\mathbf{B}$
 denotes matrix multiplication, with $(\mathbf{A}\mathbf{B})_{ij}=\sum_{k=1}^\ell A_{ik}B_{kj}$
@@
 The kernel
-matrix $\mathbf{Q}$ is defined in terms of a matrix with
-$(\mathbf{q})_{ij} = \left(4\pi|\vec{r}_i-\vec{r}_j|^3\right)^{-1}$
+matrix $\mathbf{Q}$ is defined in terms of a matrix $\mathbf{q}$ with
+$q_{ij} = \left(4\pi|\vec{r}_i-\vec{r}_j|^3\right)^{-1}$
 (which is $\lim_{\Delta z\to 0}Q_z(\vec{r},\vec{r}')$ cf. Eq.~\ref{eq:kernels}),
@@
 \end{equation}
-where we exclude points in the mesh lying outside of the superconducting film, but keep points
+where we exclude points in the mesh lying outside of the superconducting film but keep points
 inside holes in the film. $\mathbf{\Lambda}$ is either a scalar or a vector defining the effective penetration depth at every included vertex in the mesh, and $\mathbf{\nabla}^2$
-is the Laplace operator (see Section~\ref{section:implementation:laplace}), an $n\times n$ matrix defined such that $\mathbf{\nabla}^2\mathbf{f}$ computes the Laplacian $\nabla^2f(x,y)$ of a function $f(x,y)$ defined on the mesh.
+is the Laplace operator, an $n\times n$ matrix defined such that $\mathbf{\nabla}^2\mathbf{f}$ computes the Laplacian $\nabla^2f(x,y)$ of a function $f(x,y)$ defined on the mesh  (see Section~\ref{section:implementation:laplace}).
 
@@
 
-The definition of the mesh Laplace operator $\mathbf{\nabla}^2$ (also called the Laplace-Beltrami operator [Laplacian-SGP-2014]) deserves special attention, as it reduces the problem of solving a partial differential equation $\nabla^2g(x,y)=f(x,y)$ to the problem of solving a matrix equation
-$\mathbf{\nabla}^2\mathbf{g}=\mathbf{f}$.
+The definition of the discrete Laplace operator $\mathbf{\nabla}^2$ (also called the Laplace-Beltrami operator) deserves special attention, as it reduces the problem of solving a partial differential equation $\nabla^2g(x,y)=f(x,y)$ to the problem of solving a matrix equation
+$\mathbf{\nabla}^2\mathbf{g}=\mathbf{f}$~\cite{Reuter_Biasotti_Giorgi_Patane_Spagnuolo_2009}.
 As described in [Vaillant-Laplacian-2013] and [Laplacian-SGP-2014] the Laplace operator $\mathbf{\nabla}^2$ for a mesh is defined in terms of two matrices, the mass matrix $\mathbf{M}$ and the
-Laplacian matrix $\mathbf{L}$: $\mathbf{\nabla}^2 = \mathbf{M}^{-1}\mathbf{L}$.
+weak Laplacian matrix $\mathbf{L}$: $\mathbf{\nabla}^2 = \mathbf{M}^{-1}\mathbf{L}$.
 
-In a 2D mesh, the mass matrix gives an effective area to each vertex in the mesh.
-There are multiple ways to construct the mass matrix, but here we use a ``lumped" mass matrix, which is diagonal with elements $(\mathbf{M})_{ii} = \frac{1}{3}\sum_{t\in\mathcal{N}(i)}\mathrm{area}(t)$,
+In a 2D mesh, the mass matrix $\mathbf{M}$ gives an effective area to each vertex in the mesh.
+Here we use a ``lumped" mass matrix, which is diagonal with elements $M_{ii} = \frac{1}{3}\sum_{t\in\mathcal{N}(i)}\mathrm{area}(t)$,
 where $\mathcal{N}(i)$ is the set of triangles $t$ adjacent to vertex $i$.
-
-Each element $w_{ij}$ of the symmetric weight matrix $\mathbf{w}$ assigns a weight to the edge connecting vertex $i$ and vertex $j$ in the mesh.
-We use a normalized version of the weight matrix, where the sum of all off-diagonal elements in each row (or column) is 1, and each diagonal element is 1.
-Thus we can write $\mathbf{w}$ in terms of an un-normalized weight matrix $\mathbf{W}$:
-$$
-    w_{ij} = \begin{cases}
-        1&\text{if }i = j\\
-        W_{ij} / \sum_{i\neq j} W_{ij}&\text{otherwise}
-    \end{cases}
-$$
-
-There are several different methods for constructing the un-normalized weight matrix $\mathbf{W}$:
+The weak Laplacian matrix $\mathbf{L}$ is defined in terms of a symmetric weight matrix $\mathbf{W}$, which assigns a weight to every edge in the mesh.
+$\mathbf{W}$ may be defined in a number of ways:
 
@@
     \item{
-        Uniform weighting: In this case, $\mathbf{W}$ is simply the adjacency matrix for the mesh:
+        Uniform weighting: In this case, $\mathbf{W}$ is simply the adjacency matrix for the mesh vertices:
         $$
@@
 By default, \SuperScreen uses half-cotangent weighting.
-The Laplacian matrix $\mathbf{L}$ is defined in terms of the weight matrix $\mathbf{w}$: $(\mathbf{L})_{ij} = (\mathbf{w})_{ij} - \delta_{ij}\sum_{\ell}w_{i\ell}$.
+The Laplacian matrix $\mathbf{C}$ is defined in terms of the weight matrix $\mathbf{W}$: $(\mathbf{L})_{ij} = (\mathbf{W})_{ij} - \delta_{ij}\sum_{\ell}W_{i\ell}$.
 Finally, the Laplace operator is given by $\mathbf{\nabla}^2 = \mathbf{M}^{-1}\mathbf{L}$.
+
+The matrix $\mathbf{w}$ in Eqs.~\ref{eq:field_from_kernel_num} and \ref{eq:Heff_sub_num} that is used, together with the kernel matrix $\mathbf{Q}$, to approximate the dipole kernel $Q_z(\vec{r},\vec{r}')$ (Eq.~\ref{eq:kernels}) is simply a normalized version of the weight matrix $\mathbf{W}$ used in defining the Laplace operator.
+The relationship between $\mathbf{w}$ and $\mathbf{W}$ is given by:
+$$
+    w_{ij} = \begin{cases}
+        1&\text{if }i = j\\
+        W_{ij} / \sum_{i\neq j} W_{ij}&\text{otherwise}
+    \end{cases}
+$$
 
@@
 
-In this section we give a high-level overview of the \SuperScreen package. More detailed documentation and tutorials can be found at superscreen.readthedocs.io.
+In this section we give a high-level overview of the \SuperScreen package.
+More detailed documentation and tutorials can be found at \href{http://www.superscreen.readthedocs.io}{www.superscreen.readthedocs.io}.
 
@@
 
-A \mintinline{python}{superscreen.Parameter} is a wrapper around a Python function that computes a scalar value as a function of position coordinates ($x$, $y$, and optionally $z$) based on some keyword arguments.
+A \mintinline{python}{superscreen.Parameter} is a wrapper around a Python function that computes a scalar value as a function of position coordinates ($x$, $y$, and optionally $z$) based on some set of keyword arguments.
 Addition, subtraction, multiplication, division, and exponentiation between \mintinline{python}{Parameters}, other \mintinline{python}{Parameters}, and Python scalars (\mintinline{python}{int} and \mintinline{python}{float}) are supported.
@@
 A \mintinline{python}{Device} is made up of one or more superconducting layers, each an instance of  \mintinline{python}{superscreen.Layer}.
-Each layer sits in a specified plane parallel to the $x-y$ plane and has its own effective penetration depth $\Lambda$, which can either be a constant or a \mintinline{python}{superscreen.Parameter} wrapping a function that computes $\Lambda(x, y)$, the penetration depth as a function of position.
+Each layer sits in a specified plane parallel to the $x-y$ plane and has its own effective penetration depth $\Lambda$, which can either be a constant or a \mintinline{python}{superscreen.Parameter} that defines $\Lambda(x, y)$, the effective penetration depth as a function of position.
 The effective penetration depth $\Lambda$ can instead be defined in terms of a layer's London penetration depth $\lambda$ and its thickness $d$: $\Lambda=\lambda^2/d$, in which case the London penetration depth can be either a constant or a \mintinline{python}{superscreen.Parameter}.
@@
 
-A \SuperScreen model consists of a \mintinline{python}{Device}, a function or \mintinline{python}{Parameter} that computes the applied magnetic field as a function of position $H_{z,\,\mathrm{applied}}(x, y, z)$, and (optionally) a value for the current circulating around each hole in the device due to trapped flux.
+A \SuperScreen model consists of a \mintinline{python}{Device}, a function or \mintinline{python}{Parameter} that defines the applied magnetic field as a function of position $H_{z,\,\mathrm{applied}}(x, y, z)$, and (optionally) a value for the current circulating around each hole in the device due to trapped flux.
 These items serve as the inputs to \SuperScreen's main solver function, \mintinline{python}{superscreen.solve()}, which implements the calculation outlined in Section~\ref{section:implementation}.
 When simulating a device with more than one layer, one can specify the number of times to implement the iterative calculation described in Section~\ref{section:model:multilayer} in order to solve for the response of all layers self-consistently.
-One can also skip the iterative portion of the calculation entirely and only solve for the response of each layer to the applied field, assuming interaction between layers.
+One can also skip the iterative portion of the calculation entirely and only solve for the response of each layer to the applied field, assuming no interaction between layers.
 
 The output of \mintinline{python}{superscreen.solve()} is a \mintinline{python}{list} of \mintinline{python}{superscreen.Solution} objects, with a length of 1 plus the number of iterations used for the iterative portion of the calculation.
-A \mintinline{python}{Solution} encapsulates all of the information about a solved model: the \mintinline{python}{Device}, applied field, circulating currents, and calculated stream functions and screening fields for all layers in the device.
+A \mintinline{python}{Solution} encapsulates all of the information about a solved model: the \mintinline{python}{Device}, applied field, circulating currents, and calculated stream functions and magnetic fields for all layers in the device.
 A \mintinline{python}{Solution} also has methods for processing the simulation results, including:
@@
 Fortunately, the mesh and large matrices described in Section~\ref{section:implementation} depend only on the geometry of the device parallel to the $x-y$ plane.
-This means that the same mesh and matrices can be re-used for models with different applied fields, circulating currents, layer heights, and layer penetration depths.
+This means that the same mesh and matrices can be re-used for models with different applied fields, circulating currents, layer heights (vertical positions), and penetration depths.
 
-The \mintinline{python}{superscreen.solve_many()} function is designed to do just that.
-One can provide a sequence of \mintinline{python}{superscreen.Parameter} objects defining different applied fields and/or a sequence of circulating current values over which to sweep.
-One can also provide a ``layer updater" function that modifies each layer in the device according to some set of keyword arguments, which can also be swept.
+The \mintinline{python}{superscreen.solve_many()} function manages the setup and execution of such a sweep.
+One can provide a sequence of \mintinline{python}{superscreen.Parameter} objects defining different applied fields and/or a sequence of circulating current values over which to sweep and/or a ``layer updater" function that modifies each layer in the device according to some set of keyword arguments, which can also be swept.
 The latter option can be used to sweep layer heights or penetration depths.
 Given these inputs, \mintinline{python}{superscreen.solve_many()} will generate and solve all of the corresponding models.
-The models can either be solved in series in a single Python process (the default), or in parallel across multiple Python processes running on different CPUs.
-In either case, only a single copy of the device's mesh and large arrays is created, so the memory footprint is modest.
+The models can either be solved in series in a single Python process (the default), or in parallel across multiple Python processes running across multiple CPUs, or even across multiple nodes in a cluster.
+In any case, only a single copy of the device's mesh and large arrays is created, so the memory overhead is modest.
 
@@
 
-\SuperScreen offers several functions for visualizing the results of simulations (which are also aliased as method on \mintinline{python}{superscreen.Solution}):
+\SuperScreen offers several functions for visualizing the results of simulations (which are also aliased as methods on \mintinline{python}{superscreen.Solution}):
 
@@
     \mintinline{python}{superscreen.plot_streams()}: Given a \mintinline{python}{Solution}, plots the stream function $g(x, y)$ for one or more layers in the device.
-See also \mintinline{python}{Solution.plot_streams()}.
+
+    See also: \mintinline{python}{Solution.plot_streams()}.
     }
@@
     \mintinline{python}{superscreen.plot_currents()}: Given a \mintinline{python}{Solution}, plots the sheet current $\vec{J}(x, y)$ for one or more layers in the device.
-See also \mintinline{python}{Solution.plot_currents()}.
+
+    See also: \mintinline{python}{Solution.plot_currents()}.
     }
@@
     \mintinline{python}{superscreen.plot_fields()}: Given a \mintinline{python}{Solution}, plots the total field $H_z(x, y)$ or the screening field $H_z(x, y) - H_{z,\,\mathrm{applied}}(x, y)$ for one or more layers in the device.
-See also \mintinline{python}{Solution.plot_fields()}.
+
+    See also: \mintinline{python}{Solution.plot_fields()}.
     }
@@
     \mintinline{python}{superscreen.plot_field_at_positions()}: Given a \mintinline{python}{Solution}, plots the total field $\vec{H}(x, y, z_0)$ or $H_z(x, y, z_0)$ at any points in space (where $z_0$ is not equal to the vertical position of any of the layers in the device).
-See also \mintinline{python}{Solution.plot_field_at_positions()}.
+
+    See also: \mintinline{python}{Solution.plot_field_at_positions()}.
     }
@@
 Two \mintinline{python}{Solutions} are equal if their device, applied field, circulating currents, timestamp (time at which the solution was created), and all stream function and magnetic field arrays are equal.
-Two solutions created at different times can also be compared by calling \mintinline{python}{solution.equal(other_solution, require_same_timestamp=False)}.
+Two \mintinline{python}{Solutions} created at different times can also be compared by calling \mintinline{python}{solution.equals(other_solution, require_same_timestamp=False)}.
 
 Instances of \mintinline{python}{superscreen.Device} and \mintinline{python}{superscreen.Solution} can be saved to and loaded from disk using their respective \mintinline{python}{to_file()} and \mintinline{python}{from_file()} methods, making it straightforward to share models and simulation results.
-\mintinline{python}{Layers}, \mintinline{python}{Polygons}, and all metadata are serialized to JSON, a widely-used, human-readable plain text format.
-Functions and \mintinline{python}{Parameters}, such as those that compute the applied field or penetration depth, are serialized in binary form using \mintinline{python}{dill}.
+\mintinline{python}{Layers}, \mintinline{python}{Polygons}, and all metadata are serialized to JSON, a widely-used, human-readable plain text format~\cite{JSON}.
+Functions and \mintinline{python}{Parameters}, such as those that compute the applied field or penetration depth, are serialized in binary form using \mintinline{python}{dill}~\cite{McKerns}.
 \mintinline{python}{numpy} arrays, such as the mesh itself and the computed stream functions and fields, are saved in the well-established \mintinline{python}{numpy} \mintinline{python}{npz} file format.
-A \mintinline{python}{list} of \mintinline{python}{Solutions}, such as that returned by \mintinline{python}{superscreen.solve()} can be saved/loaded all at once using \mintinline{python}{superscreen.save_solutions()}/\mintinline{python}{superscreen.load_solutions()}.
+A \mintinline{python}{list} of \mintinline{python}{Solutions}, such as that returned by \mintinline{python}{superscreen.solve()} can be saved/loaded all at once using \mintinline{python}{save_solutions()} and \mintinline{python}{load_solutions()}.
 
@@
 \SuperScreen requires Python version 3.6 or later.
-The package is located in a public repository on GitHub, and a suite of unit tests is run automatically via GitHub Actions whenever a change or proposed change (Pull Request) is made to the \mintinline{python}{main} branch of the repository.
+The package is located in a public repository on GitHub~\cite{superscreen}, and a suite of unit tests is run automatically via GitHub Actions whenever a change or proposed change (Pull Request) is made to the \mintinline{python}{main} branch of the repository.
 At the time of writing, the test suite is executed using Python versions 3.6, 3.7, 3.8, and 3.9, and the test coverage is XX\%.
@@
 
-\SuperScreen has several important dependencies beyond the Python standard library: \mintinline{python}{numpy} and \mintinline{python}{scipy} for numerics, \mintinline{python}{pint} for handling physical units, \mintinline{python}{matplotlib} for visualization, \mintinline{python}{meshpy} and \mintinline{python}{optimesh} for mesh generation, \mintinline{python}{dill} for serializing objects to disk and between processes, and \mintinline{python}{ray} for parallel processing with shared memory.
+\SuperScreen has several important dependencies beyond the Python standard library: \mintinline{python}{numpy}~\cite{2020NumPy-Array} and \mintinline{python}{scipy}~\cite{2020SciPy-NMeth} for numerics, \mintinline{python}{pint}~\cite{Grecco} for handling physical units, \mintinline{python}{matplotlib}~\cite{Hunter_2007} for visualization, \mintinline{python}{meshpy}~\cite{Klockner,Shewchuk} and \mintinline{python}{optimesh}~\cite{Schlomer} for mesh generation, \mintinline{python}{dill}~\cite{McKerns} for serializing objects to disk and between processes, and \mintinline{python}{ray}~\cite{ray_2018} for parallel processing with shared memory.
 
@@
 
-\bibliographystyle{plain}
+%% The Appendices part is started with the command \appendix;
+%% appendix sections are then done as normal sections
+%% \appendix
+
+%% \section{}
+%% \label{}
+
+%% References
+%%
+%% Following citation commands can be used in the body text:
+%% Usage of \cite is as follows:
+%%   \cite{key}         ==>>  [#]
+%%   \cite[chap. 2]{key} ==>> [#, chap. 2]
+%%
+
+%% References with bibTeX database:
+
+\bibliographystyle{elsarticle-num}
 \bibliography{references}
 
+%% Authors are advised to submit their bibtex database files. They are
+%% requested to list a bibtex style file in the manuscript if they do
+%% not want to use elsarticle-num.bst.
+
+%% References without bibTeX database:
+
+% \begin{thebibliography}{00}
+
+%% \bibitem must have the following form:
+%%   \bibitem{key}...
+%%
+
+% \bibitem{}
+
+% \end{thebibliography}
+
 \end{document}
+
+%%
+%% End of file

### 2021-07-30 examples/scripts/disk.py
add examples/scripts

@@ -1,0 +1,117 @@
+import os
+import logging
+
+import numpy as np
+
+import superscreen as sc
+
+from plot_solutions import plot_solutions
+
+
+def make_disk(Lambda=1, radius=5, length_units="um"):
+    layers = [
+        sc.Layer("base", Lambda=Lambda, z0=0),
+    ]
+    films = [
+        sc.Polygon(
+            "disk",
+            layer="base",
+            points=sc.geometry.circle(radius, points=401),
+        ),
+    ]
+    abstract_regions = [
+        sc.Polygon(
+            "bounding_box",
+            layer="base",
+            points=sc.geometry.square(2 * (radius + 1), points_per_side=11),
+        ),
+    ]
+    disk = sc.Device(
+        "disk",
+        layers=layers,
+        films=films,
+        abstract_regions=abstract_regions,
+        length_units=length_units,
+    )
+    return disk
+
+
+def Lambda_linear_ramp(x, y, xmin=0, xmax=1, Lambda0=0, Lambda1=0):
+    Lambda = Lambda0 + (Lambda1 - Lambda0) * ((x - xmin) / (xmax - xmin))
+    return Lambda
+
+
+if __name__ == "__main__":
+
+    logging.basicConfig(level=logging.INFO)
+
+    imagedir = os.path.join(os.pardir, "images", "disk")
+    os.makedirs(imagedir, exist_ok=True)
+
+    disk_radius = 5
+    length_units = "um"
+
+    # Make the disk Device
+    disk = make_disk(radius=disk_radius, length_units=length_units)
+    disk.make_mesh(min_triangles=8000, optimesh_steps=100)
+
+    # Plot the disk's mesh and polygons
+    ax = disk.plot_mesh(figsize=(6, 6))
+    ax = disk.plot_polygons(ax=ax, color="k")
+    npoints = disk.points.shape[0]
+    ntriangles = disk.triangles.shape[0]
+    ax.set_title(f"Mesh: {npoints} points, {ntriangles}")
+    ax.figure.savefig(os.path.join(imagedir, f"{disk.name}_mesh.png"))
+
+    # Define a uniform applied field.
+    applied_field = sc.sources.ConstantField(1)
+    field_units = "mT"
+
+    # Simulate screening of a uniform applied magnetic field
+    # over a wide range of spatially-uniform effective
+    # penetration depths (Lambdas).
+    Lambdas = np.logspace(-1, 1, 5)
+    solutions = []
+    for Lambda in Lambdas:
[…]

### 2021-07-30 examples/scripts/plot_solutions.py

@@ -1,0 +1,108 @@
+import numpy as np
+import matplotlib.colors as cm
+import matplotlib.pyplot as plt
+from mpl_toolkits.axes_grid1.axes_divider import make_axes_locatable
+
+import superscreen as sc
+
+plt.rcParams["font.size"] = 14
+plt.rcParams["savefig.dpi"] = 150
+
+
+def plot_solutions(
+    solutions,
+    Lambdas,
+    figsize=(14, 10),
+    grid_shape=200,
+    line_cmap="viridis",
+    lw=2.5,
+    show_Lambda=1,
+    plot_polygons=True,
+):
+    N = grid_shape // 2
+
+    fig, axes = plt.subplots(2, 2, figsize=figsize)
+    (ax, bx), (cx, dx) = axes
+    ax.set_aspect("equal")
+    bx.set_aspect("equal")
+    cx.grid(True)
+    dx.grid(True)
+
+    colors = plt.get_cmap(line_cmap)(np.linspace(0, 1, len(Lambdas)))
+
+    for i, (solution, Lambda, color) in enumerate(zip(solutions, Lambdas, colors)):
+
+        xgrid, ygrid, fields = solution.grid_data("fields", grid_shape=grid_shape)
+        field = fields["base"]
+
+        if Lambda == show_Lambda:
+            im = ax.pcolormesh(xgrid, ygrid, field, shading="auto", cmap="cividis")
+            ax.set_xlabel("$x$ [$\\mu$m]")
+            ax.set_ylabel("$y$ [$\\mu$m]")
+            ax.set_title("Magnetic field, $\\mu_0H_z$\n$\\Lambda$ = 1 $\\mu$m")
+            ax_divider = make_axes_locatable(ax)
+            cax = ax_divider.append_axes("right", size="8%", pad="4%")
+            cbar = fig.colorbar(im, cax=cax)
+            cbar.set_label(f"$\\mu_0H_z$ [{solution.field_units}]")
+            ax.axhline(xvec[N], ls="--", color="w", lw=lw)
+            if plot_polygons:
+                solution.device.plot_polygons(ax=ax, color="w", lw=1, legend=False)
+
+        xvec, yvec = sc.grids_to_vecs(xgrid, ygrid)
+        cx.plot(xvec, field[N, :], color=color, lw=lw)
+
+        xgrid, ygrid, jcs = solution.current_density(
[…]

### 2021-07-30 examples/scripts/ring.py

@@ -1,0 +1,243 @@
+import os
+import logging
+import tempfile
+
+import numpy as np
+
+import superscreen as sc
+
+from plot_solutions import plot_solutions
+
+
+def make_ring(
+    inner_radius=2.5, outer_radius=5, Lambda=1, length_units="um", square=False,
+):
+    if square:
+        outer_points = sc.geometry.square(outer_radius * 2, points_per_side=60)
+        inner_points = sc.geometry.square(inner_radius * 2, points_per_side=20)
+        bbox_points = sc.geometry.square(outer_radius * 2 * 1.4, points_per_side=5)
+    else:
+        outer_points = sc.geometry.circle(outer_radius)
+        inner_points = sc.geometry.circle(inner_radius)
+        bbox_points = sc.geometry.circle(outer_radius * 1.4, points=21)
+
+    layers = [
+        sc.Layer("base", Lambda=Lambda, z0=0),
+    ]
+    films = [
+        sc.Polygon(
+            "ring",
+            layer="base",
+            points=outer_points,
+        ),
+    ]
+    holes = [
+        sc.Polygon(
+            "hole",
+            layer="base",
+            points=inner_points,
+        ),
+    ]
+    abstract_regions = [
+        sc.Polygon(
+            "bounding_box",
+            layer="base",
+            points=bbox_points,
+        )
+    ]
+    name = "square_ring" if square else "ring"
+    ring = sc.Device(
+        name,
+        layers=layers,
+        films=films,
+        holes=holes,
+        abstract_regions=abstract_regions,
+        length_units=length_units,
+    )
+    return ring
+
+
+def layer_updater(layer, Lambda=None):
+    if layer.name == "base":
+        layer.Lambda = Lambda
+    return layer
+
+
+def vortex_field(x, y, z, vortex_position=(0, 0, 0), nPhi0=1):
+    """The field from an isolated vortex.
+
+    Args:
+        x, y, z: Position coordinates.
+        vortex_position: (x, y, z) position of the vortex.
+        nPhi0: Number of flux quanta contained in the vortex.
+
+    Returns:
+        Magnetic field in units of Phi_0 / (length_units)^2,
+        where length_units are the units of x, y, z, etc.
+    """
+    xv, yv, zv = vortex_position
+    xp = x - xv
+    yp = y - yv
+    zp = z - zv
[…]

### 2021-07-30 examples/scripts/square_washer.py

@@ -1,0 +1,127 @@
+import os
+import logging
+
+import numpy as np
+
+import superscreen as sc
+
+from plot_solutions import plot_solutions
+
+
+def make_washer(inner_radius=2.5, outer_radius=5, Lambda=1, length_units="um"):
+    layers = [
+        sc.Layer("base", Lambda=Lambda, z0=0),
+    ]
+    films = [
+        sc.Polygon(
+            "washer",
+            layer="base",
+            points=sc.geometry.circle(outer_radius),
+        ),
+    ]
+    holes = [
+        sc.Polygon(
+            "hole",
+            layer="base",
+            points=sc.geometry.circle(inner_radius),
+        ),
+    ]
+    abstract_regions = [
+        sc.Polygon(
+            "bounding_box",
+            layer="base",
+            points=sc.geometry.circle(outer_radius * 1.4, points=21),
+        )
+    ]
+    washer = sc.Device(
+        "washer",
+        layers=layers,
+        films=films,
+        holes=holes,
+        abstract_regions=abstract_regions,
+        length_units=length_units,
+    )
+    return washer
+
+
+if __name__ == "__main__":
+
+    logging.basicConfig(level=logging.INFO)
+
+    imagedir = os.path.join(os.pardir, "images")
+
+    inner_radius = 2.5
+    outer_radius = 5.0
+    Lambda = 1
+    length_units = "um"
+    field_units = "mT"
+
+    # Make the disk Device
+    washer = make_washer(
+        inner_radius=inner_radius,
+        outer_radius=outer_radius,
+        Lambda=Lambda,
+        length_units=length_units,
+    )
+    washer.make_mesh(min_triangles=8000, optimesh_steps=400)
+
+    # Simulate a current circulating around the hole in the washer.
+    circulating_currents = {"hole": "1 mA"}
+
+    solution = sc.solve(device=washer, circulating_currents=circulating_currents)[-1]
+    fig, axes = solution.plot_fields(figsize=(6, 7), cross_section_ys=[0])
+    fig.savefig(os.path.join(imagedir, f"{washer.name}_plot_fields.png"))
+
+    fig, axes = solution.plot_currents(
+        figsize=(6, 7), cross_section_ys=[0], units="mA/um"
+    )
+    fig.savefig(os.path.join(imagedir, f"{washer.name}_plot_currents.png"))
+
+    # Perform a surface integral of the resulting fields to calculcate the
+    # flux through the washer and the washer's self-inductance.
+    flux_dict = solution.polygon_flux()
[…]

### 2021-07-30 main_cpc.tex
Add iamges

@@
 
-\subsection{Screening}
+\subsection{Screening: superconducting disk}
 \label{section:example:screening}
 
-\subsection{Inductance}
+\begin{figure}
+    \centering
+    \includegraphics[scale=.40]{examples/images/disk/disk_uniform_field.png}
+    \caption{Caption}
+    \label{fig:disk_uniform_field}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[scale=.40]{examples/images/ring/ring_uniform_field.png}
+    \caption{Caption}
+    \label{fig:ring_uniform_field}
+\end{figure}
+
+\subsection{Inductance: superconducting ring}
 \label{section:examples:inductance}
+
+\begin{figure}
+    \centering
+    \includegraphics[scale=.40]{examples/images/ring/ring_circulating_current.png}
+    \caption{Caption}
+    \label{fig:ring_circ_current}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[scale=.40]{examples/images/ring/square_ring_circulating_current.png}
+    \caption{Caption}
+    \label{fig:square_ring_circ_current}
+\end{figure}
 

### 2021-07-30 examples/scripts/plot_solutions.py
update images

@@ -5,7 +5,7 @@ from mpl_toolkits.axes_grid1.axes_divider import make_axes_locatable
 
 import superscreen as sc
 
-plt.rcParams["font.size"] = 14
+plt.rcParams["font.size"] = 18
 plt.rcParams["savefig.dpi"] = 150
 
 

### 2021-07-30 examples/scripts/ring.py

@@ -100,7 +100,7 @@ if __name__ == "__main__":
     # Valid options are None (i.e. serial execution), "ray", and "multiprocessing".
     # Note that for models this quick to solve, you should not expect any significatnt
     # speedup from parallel processing (especially using "multiprocessing").
-    parallel_method = "ray"
+    parallel_method = None
 
     for square in (False, True):
 

### 2021-07-30 examples/scripts/disk.py
update plots

@@ -61,7 +61,10 @@ if __name__ == "__main__":
     npoints = disk.points.shape[0]
     ntriangles = disk.triangles.shape[0]
     ax.set_title(f"Mesh: {npoints} points, {ntriangles}")
-    ax.figure.savefig(os.path.join(imagedir, f"{disk.name}_mesh.png"))
+    ax.figure.savefig(
+        os.path.join(imagedir, f"{disk.name}_mesh.png"),
+        bbox_inches="tight",
+    )
 
     # Define a uniform applied field.
     applied_field = sc.sources.ConstantField(1)
@@ -85,7 +88,10 @@ if __name__ == "__main__":
         )
 
     fig, axes = plot_solutions(solutions, Lambdas)
-    fig.savefig(os.path.join(imagedir, f"{disk.name}_uniform_field.png"))
+    fig.savefig(
+        os.path.join(imagedir, f"{disk.name}_uniform_field.png"),
+        bbox_inches="tight",
+    )
 
     # Simulate screening of a uniform applied magnetic field
     # by a disk with a spatially-nonuniform Lambda.
@@ -107,11 +113,24 @@ if __name__ == "__main__":
     )[-1]
 
     # Plot the fields.
-    fig, axes = solution.plot_fields(figsize=(5, 6), cross_section_ys=[-2, 0, 2])
-    fig.savefig(os.path.join(imagedir, f"{disk.name}_fields_nonuniform_lambda.png"))
+    fig, axes = solution.plot_fields(
+        figsize=(5, 6),
+        cross_section_ys=[-2, 0, 2],
+        auto_range_cutoff=0.1,
+    )
+    fig.savefig(
+        os.path.join(imagedir, f"{disk.name}_fields_nonuniform_lambda.png"),
+        bbox_inches="tight",
+    )
 
     # Plot the currents.
     fig, axes = solution.plot_currents(
-        figsize=(5, 6), cross_section_ys=[-2, 0, 2], units="mA/um"
+        figsize=(5, 6),
+        cross_section_ys=[-2, 0, 2],
+        units="mA/um",
+        auto_range_cutoff=0.1,
     )
-    fig.savefig(os.path.join(imagedir, f"{disk.name}_currents_nonuniform_lambda.png"))
+    fig.savefig(
+        os.path.join(imagedir, f"{disk.name}_currents_nonuniform_lambda.png"),
+        bbox_inches="tight",
+    )

### 2021-07-30 examples/scripts/plot_solutions.py

@@ -18,6 +18,7 @@ def plot_solutions(
     lw=2.5,
     show_Lambda=1,
     plot_polygons=True,
+    auto_range_cutoff=0.1,
 ):
     N = grid_shape // 2
 
@@ -36,7 +37,10 @@ def plot_solutions(
         field = fields["base"]
 
         if Lambda == show_Lambda:
-            im = ax.pcolormesh(xgrid, ygrid, field, shading="auto", cmap="cividis")
+            vmin, vmax = sc.visualization.auto_range_iqr(field, auto_range_cutoff)
+            im = ax.pcolormesh(
+                xgrid, ygrid, field, shading="auto", cmap="cividis", vmin=vmin, vmax=vmax,
+            )
             ax.set_xlabel("$x$ [$\\mu$m]")
             ax.set_ylabel("$y$ [$\\mu$m]")
             ax.set_title("Magnetic field, $\\mu_0H_z$\n$\\Lambda$ = 1 $\\mu$m")

### 2021-07-30 examples/scripts/ring.py

@@ -119,19 +119,35 @@ if __name__ == "__main__":
         npoints = ring.points.shape[0]
         ntriangles = ring.triangles.shape[0]
         ax.set_title(f"Mesh: {npoints} points, {ntriangles}")
-        ax.figure.savefig(os.path.join(imagedir, f"{ring.name}_mesh.png"))
+        ax.figure.savefig(
+            os.path.join(imagedir, f"{ring.name}_mesh.png"),
+            bbox_inches="tight",
+        )
 
         # Simulate a current circulating around the hole in the ring.
         circulating_currents = {"hole": "1 mA"}
 
         solution = sc.solve(device=ring, circulating_currents=circulating_currents)[-1]
-        fig, axes = solution.plot_fields(figsize=(6, 7), cross_section_ys=[0])
-        fig.savefig(os.path.join(imagedir, f"{ring.name}_plot_fields.png"))
+        fig, axes = solution.plot_fields(
+            figsize=(6, 7),
+            cross_section_ys=[0],
+            auto_range_cutoff=0.1,
+        )
+        fig.savefig(
+            os.path.join(imagedir, f"{ring.name}_plot_fields.png"),
+            bbox_inches="tight",
+        )
 
         fig, axes = solution.plot_currents(
-            figsize=(6, 7), cross_section_ys=[0], units="mA/um"
+            figsize=(6, 7),
+            cross_section_ys=[0],
+            units="mA/um",
+            auto_range_cutoff=0.1,
         )
-        fig.savefig(os.path.join(imagedir, f"{ring.name}_plot_currents.png"))
+        fig.savefig(
+            os.path.join(imagedir, f"{ring.name}_plot_currents.png"),
+            bbox_inches="tight",
+        )
 
         # Perform a surface integral of the resulting fields to calculcate the
         # flux through the ring and the ring's self-inductance.
@@ -175,7 +191,10 @@ if __name__ == "__main__":
         #     )
 
         fig, axes = plot_solutions(solutions, Lambdas)
-        fig.savefig(os.path.join(imagedir, f"{ring.name}_circulating_current.png"))
+        fig.savefig(
+            os.path.join(imagedir, f"{ring.name}_circulating_current.png"),
+            bbox_inches="tight",
+        )
 
         # Simulate the field and current distributions for a given
         # uniform applied field across a wide range of Lambdas,
@@ -208,7 +227,10 @@ if __name__ == "__main__":
         #     )
 
[…]

### 2021-07-30 examples/scripts/plot_solutions.py
formatting

@@ -39,7 +39,13 @@ def plot_solutions(
         if Lambda == show_Lambda:
             vmin, vmax = sc.visualization.auto_range_iqr(field, auto_range_cutoff)
             im = ax.pcolormesh(
-                xgrid, ygrid, field, shading="auto", cmap="cividis", vmin=vmin, vmax=vmax,
+                xgrid,
+                ygrid,
+                field,
+                shading="auto",
+                cmap="cividis",
+                vmin=vmin,
+                vmax=vmax,
             )
             ax.set_xlabel("$x$ [$\\mu$m]")
             ax.set_ylabel("$y$ [$\\mu$m]")

### 2021-07-30 examples/scripts/ring.py

@@ -10,7 +10,11 @@ from plot_solutions import plot_solutions
 
 
 def make_ring(
-    inner_radius=2.5, outer_radius=5, Lambda=1, length_units="um", square=False,
+    inner_radius=2.5,
+    outer_radius=5,
+    Lambda=1,
+    length_units="um",
+    square=False,
 ):
     if square:
         outer_points = sc.geometry.square(outer_radius * 2, points_per_side=60)
@@ -95,7 +99,7 @@ if __name__ == "__main__":
     Lambda = 1
     length_units = "um"
     field_units = "mT"
-    
+
     # The method used for parallel execution.
     # Valid options are None (i.e. serial execution), "ray", and "multiprocessing".
     # Note that for models this quick to solve, you should not expect any significatnt

### 2021-08-02 examples/scripts/disk.py
update examples

@@ -1,5 +1,6 @@
 import os
 import logging
+from matplotlib.pyplot import show
 
 import numpy as np
 
@@ -50,6 +51,8 @@ if __name__ == "__main__":
 
     disk_radius = 5
     length_units = "um"
+    # Plot the fields and currents for this value of Lambda
+    show_Lambda = 1.0
 
     # Make the disk Device
     disk = make_disk(radius=disk_radius, length_units=length_units)
@@ -87,7 +90,7 @@ if __name__ == "__main__":
             )[-1]
         )
 
-    fig, axes = plot_solutions(solutions, Lambdas)
+    fig, axes = plot_solutions(solutions, Lambdas, show_Lambda=show_Lambda)
     fig.savefig(
         os.path.join(imagedir, f"{disk.name}_uniform_field.png"),
         bbox_inches="tight",

### 2021-08-02 examples/scripts/plot_solutions.py

@@ -49,7 +49,9 @@ def plot_solutions(
             )
             ax.set_xlabel("$x$ [$\\mu$m]")
             ax.set_ylabel("$y$ [$\\mu$m]")
-            ax.set_title("Magnetic field, $\\mu_0H_z$\n$\\Lambda$ = 1 $\\mu$m")
+            ax.set_title(
+                f"Magnetic field, $\\mu_0H_z$\n$\\Lambda$ = {show_Lambda:.2f} $\\mu$m"
+            )
             ax_divider = make_axes_locatable(ax)
             cax = ax_divider.append_axes("right", size="8%", pad="4%")
             cbar = fig.colorbar(im, cax=cax)
@@ -82,7 +84,10 @@ def plot_solutions(
             im = bx.pcolormesh(xvec, yvec, J, shading="auto", cmap="inferno")
             bx.set_xlabel("$x$ [$\\mu$m]")
             bx.set_ylabel("$y$ [$\\mu$m]")
-            bx.set_title("Sheet current, $|\\vec{J}|$\n$\\Lambda$ = 1 $\\mu$m")
+            bx.set_title(
+                "Sheet current, $|\\vec{J}|$"
+                + f"\n$\\Lambda$ = {show_Lambda:.2f} $\\mu$m"
+            )
             ax_divider = make_axes_locatable(bx)
             cax = ax_divider.append_axes("right", size="6%", pad="4%")
             cbar = fig.colorbar(im, cax=cax)

### 2021-08-02 examples/scripts/ring.py

@@ -99,6 +99,8 @@ if __name__ == "__main__":
     Lambda = 1
     length_units = "um"
     field_units = "mT"
+    # Plot the fields and currents for this value of Lambda
+    show_Lambda = 0.1
 
     # The method used for parallel execution.
     # Valid options are None (i.e. serial execution), "ray", and "multiprocessing".
@@ -167,7 +169,8 @@ if __name__ == "__main__":
 
         # Simulate the field and current distributions for a given total
         # circulating current across a wide range of Lambdas.
-        Lambdas = np.logspace(-2, 2, 11)
+        Lambdas = np.logspace(-2, 2, 13)
+        assert np.any(Lambdas == show_Lambda), "show_Lambda not in Lambdas"
 
         layer_update_kwargs = [dict(Lambda=Lambda) for Lambda in Lambdas]
 
@@ -194,7 +197,7 @@ if __name__ == "__main__":
         #         )[-1]
         #     )
 
-        fig, axes = plot_solutions(solutions, Lambdas)
+        fig, axes = plot_solutions(solutions, Lambdas, show_Lambda=show_Lambda)
         fig.savefig(
             os.path.join(imagedir, f"{ring.name}_circulating_current.png"),
             bbox_inches="tight",
@@ -230,16 +233,26 @@ if __name__ == "__main__":
         #         )[-1]
         #     )
 
-        fig, axes = plot_solutions(solutions, Lambdas)
+        fig, axes = plot_solutions(solutions, Lambdas, show_Lambda=show_Lambda)
         fig.savefig(
             os.path.join(imagedir, f"{ring.name}_uniform_field.png"),
             bbox_inches="tight",
         )
 
         # Simulate the field and current distribution for a nonuniform applied field,
-        # namely the field from an isolated vortex pinned below the plane of the ring.
-        vortex_position = (-3.75, 0, -0.5)  # x, y, z
-        applied_field = sc.Parameter(vortex_field, vortex_position=(-3.75, 0, -0.5))
+        # namely the field from several isolated vortcies pinned below
+        # the plane of the ring.
+        vortex_positions = [
+            # (x, y, z),
+            (-3.75, 0, -0.5),
+            (2.5, -2.5, -0.5),
+            (0, 5, -0.5),
+        ]
+        # Define the applied field as a sum of Parameters
+        applied_field = sum(
+            sc.Parameter(vortex_field, vortex_position=position)
+            for position in vortex_positions
[…]

### 2021-08-02 examples/scripts/disk.py
cleanup

@@ -1,6 +1,5 @@
 import os
 import logging
-from matplotlib.pyplot import show
 
 import numpy as np
 

### 2021-08-02 examples/scripts/plot_solutions.py

@@ -36,6 +36,8 @@ def plot_solutions(
         xgrid, ygrid, fields = solution.grid_data("fields", grid_shape=grid_shape)
         field = fields["base"]
 
+        xvec, yvec = sc.grids_to_vecs(xgrid, ygrid)
+
         if Lambda == show_Lambda:
             vmin, vmax = sc.visualization.auto_range_iqr(field, auto_range_cutoff)
             im = ax.pcolormesh(
@@ -60,7 +62,6 @@ def plot_solutions(
             if plot_polygons:
                 solution.device.plot_polygons(ax=ax, color="w", lw=1, legend=False)
 
-        xvec, yvec = sc.grids_to_vecs(xgrid, ygrid)
         cx.plot(xvec, field[N, :], color=color, lw=lw)
 
         xgrid, ygrid, jcs = solution.current_density(

### 2021-08-02 examples/scripts/ring.py

@@ -1,6 +1,5 @@
 import os
 import logging
-import tempfile
 
 import numpy as np
 

### 2021-08-02 examples/scripts/disk.py
figures

@@ -62,7 +62,7 @@ if __name__ == "__main__":
     ax = disk.plot_polygons(ax=ax, color="k")
     npoints = disk.points.shape[0]
     ntriangles = disk.triangles.shape[0]
-    ax.set_title(f"Mesh: {npoints} points, {ntriangles}")
+    ax.set_title(f"{disk.name} mesh:\n{npoints} points, {ntriangles}")
     ax.figure.savefig(
         os.path.join(imagedir, f"{disk.name}_mesh.png"),
         bbox_inches="tight",

### 2021-08-02 examples/scripts/ring.py

@@ -16,40 +16,29 @@ def make_ring(
     square=False,
 ):
     if square:
-        outer_points = sc.geometry.square(outer_radius * 2, points_per_side=60)
-        inner_points = sc.geometry.square(inner_radius * 2, points_per_side=20)
-        bbox_points = sc.geometry.square(outer_radius * 2 * 1.4, points_per_side=5)
+        name = "square_ring"
+        outer_points = sc.geometry.square(
+            outer_radius * 2, points_per_side=60
+        )
+        inner_points = sc.geometry.square(
+            inner_radius * 2, points_per_side=20
+        )
+        bbox_points = sc.geometry.square(
+            outer_radius * 2 * 1.4, points_per_side=5
+        )
     else:
+        name = "circular_ring"
         outer_points = sc.geometry.circle(outer_radius)
         inner_points = sc.geometry.circle(inner_radius)
-        bbox_points = sc.geometry.circle(outer_radius * 1.4, points=21)
+        bbox_points = sc.geometry.circle(outer_radius * 1.4, points=2)
 
-    layers = [
-        sc.Layer("base", Lambda=Lambda, z0=0),
-    ]
-    films = [
-        sc.Polygon(
-            "ring",
-            layer="base",
-            points=outer_points,
-        ),
-    ]
-    holes = [
-        sc.Polygon(
-            "hole",
-            layer="base",
-            points=inner_points,
-        ),
-    ]
+    layers = [sc.Layer("base", Lambda=Lambda, z0=0)]
+    films = [sc.Polygon("ring", layer="base", points=outer_points)]
+    holes = [sc.Polygon("hole", layer="base", points=inner_points)]
     abstract_regions = [
-        sc.Polygon(
-            "bounding_box",
-            layer="base",
-            points=bbox_points,
-        )
+        sc.Polygon("bounding_box", layer="base", points=bbox_points),
     ]
-    name = "square_ring" if square else "ring"
-    ring = sc.Device(
+    return sc.Device(
         name,
         layers=layers,
         films=films,
@@ -57,7 +46,6 @@ def make_ring(
         abstract_regions=abstract_regions,
         length_units=length_units,
     )
-    return ring
 
 
 def layer_updater(layer, Lambda=None):
@@ -123,7 +111,7 @@ if __name__ == "__main__":
         ax = ring.plot_polygons(ax=ax, color="k")
         npoints = ring.points.shape[0]
[…]

### 2021-08-02 main_cpc.tex

@@
  {\endlist}
+\usepackage{subcaption}
+\usepackage[newfloat]{minted}
+\usepackage{hyperref}
+\usepackage{tcolorbox}
+\usepackage{etoolbox}
+\BeforeBeginEnvironment{minted}{\begin{tcolorbox}}
+\AfterEndEnvironment{minted}{\end{tcolorbox}}
+\usepackage{caption}
 
-\usepackage{minted}
-\usepackage{hyperref}
+\newenvironment{code}{\captionsetup{type=listing}}{}
+\SetupFloatingEnvironment{listing}{name=Code Block}
 
@@
 By default, \SuperScreen uses half-cotangent weighting.
-The Laplacian matrix $\mathbf{C}$ is defined in terms of the weight matrix $\mathbf{W}$: $(\mathbf{L})_{ij} = (\mathbf{W})_{ij} - \delta_{ij}\sum_{\ell}W_{i\ell}$.
+The Laplacian matrix $\mathbf{C}$ is defined in terms of the weight matrix $\mathbf{W}$: $L_{ij} = W_{ij} - \delta_{ij}\sum_{\ell}W_{i\ell}$.
 Finally, the Laplace operator is given by $\mathbf{\nabla}^2 = \mathbf{M}^{-1}\mathbf{L}$.
@@
 Addition, subtraction, multiplication, division, and exponentiation between \mintinline{python}{Parameters}, other \mintinline{python}{Parameters}, and Python scalars (\mintinline{python}{int} and \mintinline{python}{float}) are supported.
-For example:
+For example, see Code Block~\ref{code:parameters}.
 
-\begin{minted}{python}
+\begin{code}
+\begin{minted}[fontsize=\footnotesize]{python}
 from superscreen import Parameter
@@
 param = Parameter(f, a=0, b=1)
-print(param)  # Parameter<f(a=0, b=1)>
+print(param)
+# Parameter<f(a=0, b=1)>
 
 other_param = Parameter(f, a=2, b=3)
-print(other_param)  # Parameter<f(a=2, b=3)>
+print(other_param)
+# Parameter<f(a=2, b=3)>
 
-print(param(0, 0) == f(0, 0, a=0, b=1))  # True
-print(other_param(1, 2) == f(1, 2, a=2, b=3))  # True
+print(param(0, 0) == f(0, 0, a=0, b=1))
+# True
+print(other_param(1, 2) == f(1, 2, a=2, b=3))
+# True
 
 param_squared = param ** 2
-print(param_squared)  # CompositeParameter<(f(a=0, b=1) ** 2)>
+print(param_squared)
+# CompositeParameter<(f(a=0, b=1) ** 2)>
 
-print(param_squared(3, 4) == f(3, 4, a=0, b=1) ** 2) # True
+print(param_squared(3, 4) == f(3, 4, a=0, b=1) ** 2)
+# True
 print(
@@
     == 5 * f(5, 6, a=0, b=1) ** 2 / f(5, 6, a=2, b=3)
-)  # True
+)
+# True
 \end{minted}
-
-\mintinline{python}{Parameters} can be used to define applied magnetic fields and penetration depths that depend on position.
+\captionof{listing}{The basic usage of \mintinline{python}{Parameters}.
+\mintinline{python}{Parameters} can be used to conveniently define applied magnetic fields and penetration depths that depend on position.}
+\label{code:parameters}
+\end{code}
 
@@
 Abstract regions can be used to define a ``bounding box" around a structure.
+The \mintinline{python}{superscreen.geometry} module provides functions for generating the underlying polygon vertices for simple geometries (circles and rectangles).
+See Code Block~\ref{code:device} for an example of a function that creates a square or circular superconducting ring centered at the origin.
+
+\begin{code}
+\begin{minted}[fontsize=\footnotesize]{python}
+import superscreen as sc
+
+def make_ring(
+    inner_radius=2.5,
+    outer_radius=5,
+    Lambda=1,
+    length_units="um",
+    square=False,
+):
+    if square:
+        name = "square_ring"
+        outer_points = sc.geometry.square(
+            outer_radius * 2, points_per_side=60
+        )
+        inner_points = sc.geometry.square(
+            inner_radius * 2, points_per_side=20
+        )
+        bbox_points = sc.geometry.square(
+            outer_radius * 2 * 1.4, points_per_side=5
+        )
+    else:
+        name = "circular_ring"
+        outer_points = sc.geometry.circle(outer_radius)
+        inner_points = sc.geometry.circle(inner_radius)
+        bbox_points = sc.geometry.circle(outer_radius * 1.4, points=2)
+
+    layers = [sc.Layer("base", Lambda=Lambda, z0=0)]
+    films = [sc.Polygon("ring", layer="base", points=outer_points)]
+    holes = [sc.Polygon("hole", layer="base", points=inner_points)]
+    abstract_regions = [
+        sc.Polygon("bounding_box", layer="base", points=bbox_points),
+    ]
+    return sc.Device(
+        name,
+        layers=layers,
+        films=films,
+        holes=holes,
+        abstract_regions=abstract_regions,
+        length_units=length_units,
+    )
+\end{minted}
+\captionof{listing}{A function that creates a \mintinline{python}{Device} representing a circular or square ring centered at the origin.}
+\label{code:device}
+\end{code}
 
@@
 The region that is meshed is defined by the convex hull of the union of all polygons in the device.
+Mesh generation is a two step process.
+First, an initial Delaunay mesh is created using \mintinline{python}{MeshPy}~\cite{Klockner}, a Python interface to Triangle~\cite{shewchuk96b, Shewchuk}, a fast compiled 2D mesh generation tool.
+Second (and optionally), the mesh can be further optimized using \mintinline{python}{optimesh}~\cite{nico_schlomer_adam_dobrawy_2021}.
+The goal of the mesh optimization step is to improve the quality of each triangular element in the mesh, where quality is defined as twice the ratio of the incircle radius to the circumcircle radius (quality $\leq1$, with equality for equilateral triangles).
+The local density of triangles in the mesh is determined by the density of vertices in the device's polygons, i.e.
+regions where there are many polygon vertices will be meshed densely.
+If no \mintinline{python}{optimesh} optimization is done, then every polygon vertex is guaranteed to be a mesh vertex.
+
+\begin{code}
+\begin{minted}[fontsize=\footnotesize]{python}
+# min_triangles specifies the minimum number of mesh elements.
+min_triangles = 8000
+# optimesh_steps specifies the the number of iterations of
+# optimesh optimization to perform.
+# Set optimesh_steps=None to disable optimesh optimization.
+optimesh_steps = 400
+# For more meshing options, see the docstring for Device.make_mesh().
+
+for square in (False, True):
+    ring = make_ring(square=square)
+    ring.make_mesh(
+        min_triangles=min_triangles,
+        optimesh_steps=optimesh_steps,
+    )
+
+    ax = ring.plot_mesh(figsize=(6, 6))
+    ax = ring.plot_polygons(ax=ax, color="k")
+\end{minted}
+\captionof{listing}{Generating and visualizing the computational mesh.}
+\label{code:mesh_generation}
+\end{code}
+
+\begin{figure}
+\centering
+\begin{subfigure}{.45\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{examples/images/ring/ring_mesh.png}
+  \caption{A subfigure}
+  \label{fig:circular_ring_mesh}
+\end{subfigure}%
+\begin{subfigure}{.45\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{examples/images/ring/ring_mesh.png}
+  \caption{A subfigure}
+  \label{fig:square_ring_mesh}
+\end{subfigure}
+\caption{A figure with two subfigures}
+\label{fig:ring_mesh}
+\end{figure}
+
 After the mesh is generated, the matrices and vectors described in Section~\ref{section:implementation} can be computed and one can begin solving models.
@@
 
-A \SuperScreen model consists of a \mintinline{python}{Device}, a function or \mintinline{python}{Parameter} that defines the applied magnetic field as a function of position $H_{z,\,\mathrm{applied}}(x, y, z)$, and (optionally) a value for the current circulating around each hole in the device due to trapped flux.
+A \SuperScreen model consists of a \mintinline{python}{Device}, a function or \mintinline{python}{Parameter} that defines the applied magnetic field as a function of position $H_{z,\,\mathrm{applied}}(x, y, z)$, and a value for the current circulating around each hole in the device due to trapped flux (if any).
 These items serve as the inputs to \SuperScreen's main solver function, \mintinline{python}{superscreen.solve()}, which implements the calculation outlined in Section~\ref{section:implementation}.
@@
 The \mintinline{python}{superscreen.solve_many()} function manages the setup and execution of such a sweep.
-One can provide a sequence of \mintinline{python}{superscreen.Parameter} objects defining different applied fields and/or a sequence of circulating current values over which to sweep and/or a ``layer updater" function that modifies each layer in the device according to some set of keyword arguments, which can also be swept.
+One can provide a sequence of \mintinline{python}{Parameter} objects defining different applied fields and/or a sequence of circulating current values over which to sweep and/or a ``layer updater" function that modifies each layer in the device according to some set of keyword arguments, which can also be swept.
 The latter option can be used to sweep layer heights or penetration depths.
@@
 
-\SuperScreen has several important dependencies beyond the Python standard library: \mintinline{python}{numpy}~\cite{2020NumPy-Array} and \mintinline{python}{scipy}~\cite{2020SciPy-NMeth} for numerics, \mintinline{python}{pint}~\cite{Grecco} for handling physical units, \mintinline{python}{matplotlib}~\cite{Hunter_2007} for visualization, \mintinline{python}{meshpy}~\cite{Klockner,Shewchuk} and \mintinline{python}{optimesh}~\cite{Schlomer} for mesh generation, \mintinline{python}{dill}~\cite{McKerns} for serializing objects to disk and between processes, and \mintinline{python}{ray}~\cite{ray_2018} for parallel processing with shared memory.
+\SuperScreen has several important dependencies beyond the Python standard library: \mintinline{python}{numpy}~\cite{2020NumPy-Array} and \mintinline{python}{scipy}~\cite{2020SciPy-NMeth} for numerics, \mintinline{python}{pint}~\cite{Grecco} for handling physical units, \mintinline{python}{matplotlib}~\cite{Hunter_2007} for visualization, \mintinline{python}{meshpy}~\cite{Klockner,Shewchuk} and \mintinline{python}{optimesh}~\cite{nico_schlomer_adam_dobrawy_2021} for mesh generation, \mintinline{python}{dill}~\cite{McKerns} for serializing objects to disk and between processes, and \mintinline{python}{ray}~\cite{ray_2018} for parallel processing with shared memory.
 
@@
 
-\subsection{Screening: superconducting disk}
+Below we demonstrate how to solve several different classes of problems using \mintinline{python}{SuperScreen}: screening of and applied magnetic field by a single superconducting film, current distribution and self-inductance of superconducting rings, and mutual inductance of two superconducting rings.
+The full source code and interactive Jupyter notebooks for each of the examples can be found in the "examples" directory of the GitHub repository accompanying this paper.
+
+\subsection{Device setup}
+\label{section:example:setup}
+
+The model geometry is defined by creating an instance of \mintinline{python}{superscreen.Device}.
+Here we define a disk, a circular ring, and a square ring, and generate the computational mesh for each of them.
+
+\begin{minted}[fontsize=\footnotesize]{python}
+import superscreen as sc
+
+def make_disk(Lambda=1, radius=5, length_units="um"):
+    layers = [sc.Layer("base", Lambda=Lambda, z0=0)]
+    films = [
+        sc.Polygon(
+            "disk",
+            layer="base",
+            points=sc.geometry.circle(radius, points=401),
+        ),
+    ]
+    abstract_regions = [
+        sc.Polygon(
+            "bounding_box",
+            layer="base",
+            points=sc.geometry.square(
+                2 * (radius + 1), points_per_side=11
+            ),
+        ),
+    ]
+    disk = sc.Device(
+        "disk",
+        layers=layers,
+        films=films,
+        abstract_regions=abstract_regions,
+        length_units=length_units,
+    )
+    return disk
+\end{minted}
+
+\subsection{Screening}
 \label{section:example:screening}
+
+Here we simulate Meissner screening of both uniform and non-uniform applied magnetic fields by superconducting films with different geometries and penetration depths.
 
@@
 
-\subsection{Inductance: superconducting ring}
+\subsection{Self-inductance}
 \label{section:examples:inductance}

### 2021-08-02 examples/scripts/ring.py
typo

@@ -30,7 +30,7 @@ def make_ring(
         name = "circular_ring"
         outer_points = sc.geometry.circle(outer_radius)
         inner_points = sc.geometry.circle(inner_radius)
-        bbox_points = sc.geometry.circle(outer_radius * 1.4, points=2)
+        bbox_points = sc.geometry.circle(outer_radius * 1.4, points=21)
 
     layers = [sc.Layer("base", Lambda=Lambda, z0=0)]
     films = [sc.Polygon("ring", layer="base", points=outer_points)]

### 2021-08-02 main_cpc.tex
Updates from Overleaf

@@
         inner_points = sc.geometry.circle(inner_radius)
-        bbox_points = sc.geometry.circle(outer_radius * 1.4, points=2)
+        bbox_points = sc.geometry.circle(outer_radius * 1.4, points=21)
 
@@
   \centering
-  \includegraphics[width=\linewidth]{examples/images/ring/ring_mesh.png}
+  \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_mesh.png}
   \caption{A subfigure}
@@
   \centering
-  \includegraphics[width=\linewidth]{examples/images/ring/ring_mesh.png}
+  \includegraphics[width=\linewidth]{examples/images/ring/square_ring_mesh.png}
   \caption{A subfigure}
@@
     \centering
-    \includegraphics[scale=.40]{examples/images/ring/ring_uniform_field.png}
+    \includegraphics[scale=.40]{examples/images/ring/circular_ring_uniform_field.png}
     \caption{Caption}
@@
     \centering
-    \includegraphics[scale=.40]{examples/images/ring/ring_circulating_current.png}
+    \includegraphics[scale=.40]{examples/images/ring/circular_ring_circulating_current.png}
     \caption{Caption}

### 2021-08-02 examples/scripts/disk.py
typo

@@ -62,7 +62,7 @@ if __name__ == "__main__":
     ax = disk.plot_polygons(ax=ax, color="k")
     npoints = disk.points.shape[0]
     ntriangles = disk.triangles.shape[0]
-    ax.set_title(f"{disk.name} mesh:\n{npoints} points, {ntriangles}")
+    ax.set_title(f"{disk.name} mesh:\n{npoints} points, {ntriangles} triangles")
     ax.figure.savefig(
         os.path.join(imagedir, f"{disk.name}_mesh.png"),
         bbox_inches="tight",

### 2021-08-02 examples/scripts/ring.py

@@ -111,7 +111,7 @@ if __name__ == "__main__":
         ax = ring.plot_polygons(ax=ax, color="k")
         npoints = ring.points.shape[0]
         ntriangles = ring.triangles.shape[0]
-        ax.set_title(f"{ring.name} mesh:\n{npoints} points, {ntriangles}")
+        ax.set_title(f"{ring.name} mesh:\n{npoints} points, {ntriangles} triangles")
         ax.figure.savefig(
             os.path.join(imagedir, f"{ring.name}_mesh.png"),
             bbox_inches="tight",

### 2021-08-02 main_cpc.tex

@@
 
-\subsection{Device setup}
-\label{section:example:setup}
-
-The model geometry is defined by creating an instance of \mintinline{python}{superscreen.Device}.
-Here we define a disk, a circular ring, and a square ring, and generate the computational mesh for each of them.
-
-\begin{minted}[fontsize=\footnotesize]{python}
-import superscreen as sc
-
-def make_disk(Lambda=1, radius=5, length_units="um"):
-    layers = [sc.Layer("base", Lambda=Lambda, z0=0)]
-    films = [
-        sc.Polygon(
-            "disk",
-            layer="base",
-            points=sc.geometry.circle(radius, points=401),
-        ),
-    ]
-    abstract_regions = [
-        sc.Polygon(
-            "bounding_box",
-            layer="base",
-            points=sc.geometry.square(
-                2 * (radius + 1), points_per_side=11
-            ),
-        ),
-    ]
-    disk = sc.Device(
-        "disk",
-        layers=layers,
-        films=films,
-        abstract_regions=abstract_regions,
-        length_units=length_units,
-    )
-    return disk
-\end{minted}
-
 \subsection{Screening}

### 2021-08-02 main_cpc.tex
Updates from Overleaf

@@
   \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_mesh.png}
-  \caption{A subfigure}
+%   \caption{A subfigure}
   \label{fig:circular_ring_mesh}
@@
   \includegraphics[width=\linewidth]{examples/images/ring/square_ring_mesh.png}
-  \caption{A subfigure}
+%   \caption{A subfigure}
   \label{fig:square_ring_mesh}
 \end{subfigure}
-\caption{A figure with two subfigures}
+\caption{Device geometry and mesh for a circular and square ring generated using Code Blocks~\ref{code:device} and \ref{code:mesh_generation}.}
 \label{fig:ring_mesh}
@@
 
+\begin{figure}
+\centering
+\begin{subfigure}{.45\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_mesh.png}
+%   \caption{A subfigure}
+  \label{fig:circular_ring_mesh}
+\end{subfigure}%
+\begin{subfigure}{.45\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{examples/images/ring/square_ring_mesh.png}
+%   \caption{A subfigure}
+  \label{fig:square_ring_mesh}
+\end{subfigure}
+\caption{Device geometry and mesh for a circular and square ring generated using Code Blocks~\ref{code:device} and \ref{code:mesh_generation}.}
+\label{fig:ring_mesh}
+\end{figure}
 After the mesh is generated, the matrices and vectors described in Section~\ref{section:implementation} can be computed and one can begin solving models.

### 2021-08-02 examples/scripts/ring.py
plots

@@ -117,30 +117,42 @@ if __name__ == "__main__":
             bbox_inches="tight",
         )
 
-        # Simulate a current circulating around the hole in the ring.
+        # Uniform applied field
+        applied_field = sc.sources.ConstantField(0.2)  # mT
+
+        # Current circulating around the hole in the ring.
         circulating_currents = {"hole": "1 mA"}
 
-        solution = sc.solve(device=ring, circulating_currents=circulating_currents)[-1]
-        fig, axes = solution.plot_fields(
-            figsize=(6, 7),
-            cross_section_ys=[0],
-            auto_range_cutoff=0.1,
-        )
-        fig.savefig(
-            os.path.join(imagedir, f"{ring.name}_plot_fields.png"),
-            bbox_inches="tight",
-        )
+        for field, current, label in [
+            (applied_field, None, "uniform"), (None, circulating_currents, "circ")
+        ]:
+            solution = sc.solve(
+                device=ring,
+                applied_field=field,
+                circulating_currents=current,
+                field_units=field_units,
+            )[-1]
 
-        fig, axes = solution.plot_currents(
-            figsize=(6, 7),
-            cross_section_ys=[0],
-            units="mA/um",
-            auto_range_cutoff=0.1,
-        )
-        fig.savefig(
-            os.path.join(imagedir, f"{ring.name}_plot_currents.png"),
-            bbox_inches="tight",
-        )
+            fig, axes = solution.plot_fields(
+                figsize=(6, 7),
+                cross_section_ys=[0],
+                auto_range_cutoff=0.1,
+            )
+            fig.savefig(
+                os.path.join(imagedir, f"{ring.name}_{label}_plot_fields.png"),
+                bbox_inches="tight",
+            )
+
+            fig, axes = solution.plot_currents(
+                figsize=(6, 7),
+                cross_section_ys=[0],
+                units="mA/um",
+                auto_range_cutoff=0.1,
+            )
+            fig.savefig(
+                os.path.join(imagedir, f"{ring.name}_{label}_plot_currents.png"),
+                bbox_inches="tight",
+            )
 
         # Perform a surface integral of the resulting fields to calculcate the
         # flux through the ring and the ring's self-inductance.

### 2021-08-02 main_cpc.tex
Updates from Overleaf

--- 2021-08-02 main_cpc.tex
@@
 \centering
-\begin{subfigure}{.45\textwidth}
+\begin{subfigure}{.4\textwidth}
   \centering
   \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_mesh.png}
-  \caption{A subfigure}
+  \caption{Circular ring, \mintinline{python}{optimesh_steps=400}.}
   \label{fig:circular_ring_mesh}
 \end{subfigure}%
-\begin{subfigure}{.45\textwidth}
+\begin{subfigure}{.4\textwidth}
   \centering
   \includegraphics[width=\linewidth]{examples/images/ring/square_ring_mesh.png}
-  \caption{A subfigure}
+  \caption{Square ring, \mintinline{python}{optimesh_steps=400}.}
   \label{fig:square_ring_mesh}
 \end{subfigure}
-\caption{A figure with two subfigures}
+\begin{subfigure}{.4\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_mesh_no_optimesh.png}
+  \caption{Circular ring, \mintinline{python}{optimesh_steps=None}.}
+  \label{fig:circular_ring_mesh_no_opt}
+\end{subfigure}%
+\begin{subfigure}{.4\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{examples/images/ring/square_ring_mesh_no_optimesh.png}
+  \caption{Square ring, \mintinline{python}{optimesh_steps=None}.}
+  \label{fig:square_ring_mesh_no_opt}
+\end{subfigure}
+\caption{Device geometry and mesh for a circular and square ring generated using Code Blocks~\ref{code:device} and \ref{code:mesh_generation}, with (top row) and without (bottom row) \mintinline{python}{optimesh} optimization.}
 \label{fig:ring_mesh}
@@
 One can also skip the iterative portion of the calculation entirely and only solve for the response of each layer to the applied field, assuming no interaction between layers.
+
+For example, Code Block~\ref{code:ring_circulating_current} solves two models involving the \mintinline{python}{ring} device.
+First, Meissner screening of a spatially uniform applied magnetic field, and second, the response of the ring to trapped flux with an associated circulating current of 1 mA with no applied magnetic field.
+The resulting sheet current and magnetic field distributions can be visualized using the \mintinline{python}{plot_current()} and \mintinline{python}{plot_fields()} methods, which produce the images shown in Figure~\ref{fig:ring_plot_fields_currents}.
+
+\begin{code}
+\begin{minted}[fontsize=\footnotesize]{python}
+# Simulate the response to a uniform applied field of 0.2 mT
+applied_field = sc.sources.ConstantField(0.2)
+field_units = "mT"
+
+solutions = sc.solve(
+    device=ring,
+    applied_field=applied_field,
+    field_units=field_units,
+)
+assert len(solutions) == 1 # Since there is only one layer
+uniform_field = solutions[-1]
+
+# Simulate a current circulating around the hole in the ring.
+circulating_currents = {"hole": "1 mA"}
+
+solutions = sc.solve(
+    device=ring,
+    applied_field=None,
+    circulating_currents=circulating_currents
+)
+assert len(solutions) == 1 # Since there is only one layer
+trapped_flux = solutions[-1]
+
+for solution in (uniform_field, trapped_flux):
+    solution.plot_currents(
+        figsize=(6, 7), cross_section_ys=[0], units="mA/um",
+    )
+    solution.plot_fields(figsize=(6, 7), cross_section_ys=[0])
+\end{minted}
+\captionof{listing}{Solve for the current and magnetic field distributions resulting from a total current of 1 mA flowing in our \mintinline{python}{ring} device.}
+\label{code:ring_circulating_current}
+\end{code}
+
+% \begin{code}
+% \begin{minted}[fontsize=\footnotesize]{python}
+% # Simulate a current circulating around the hole in the ring.
+% circulating_currents = {"hole": "1 mA"}
+
+% solutions = sc.solve(
+%     device=ring,
+%     applied_field=None,
+%     circulating_currents=circulating_currents
+% )
+% assert len(solutions) == 1 # Since there is only one layer
+% solution = solutions[-1]
+
+% solution.plot_currents(
+%     figsize=(6, 7), cross_section_ys=[0], units="mA/um",
+% )
+
+% solution.plot_fields(
+%     figsize=(6, 7), cross_section_ys=[0],
+% )
+% \end{minted}
+% \captionof{listing}{Solve for the current and magnetic field distributions resulting from a total current of 1 mA flowing in our \mintinline{python}{ring} device.}
+% \label{code:ring_circulating_current}
+% \end{code}
+
+\begin{figure}
+\centering
+\begin{subfigure}{.4\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_plot_currents.png}
+  \caption{Circular ring sheet current.}
+  \label{fig:circular_ring_plot_currents}
+\end{subfigure}
+\begin{subfigure}{.4\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_plot_fields.png}
+  \caption{Circular ring magnetic field.}
+  \label{fig:circular_ring_plot_fields}
+\end{subfigure}
+
+\begin{subfigure}{.4\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{examples/images/ring/square_ring_plot_currents.png}
+  \caption{Square ring sheet current.}
+  \label{fig:square_ring_plot_currents}
+\end{subfigure}
+\begin{subfigure}{.4\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{examples/images/ring/square_ring_plot_fields.png}
+  \caption{Square ring magnetic field.}
+  \label{fig:square_ring_plot_fields}
+\end{subfigure}
+
+\caption{Sheet current $\vec{J}$ and magnetic field $\mu_0H_z$ distributions for the circular (top) and square (bottom) ring calculated using Code Block~\ref{code:ring_circulating_current}.}
+\label{fig:ring_circulating_current}
+\end{figure}
 

### 2021-08-02 main_cpc.tex

@@
   \centering
-  \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_plot_currents.png}
+  \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_uniform_plot_currents.png}
   \caption{Circular ring sheet current.}
@@
   \centering
-  \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_plot_fields.png}
+  \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_uniform_plot_fields.png}
   \caption{Circular ring magnetic field.}
@@
   \centering
-  \includegraphics[width=\linewidth]{examples/images/ring/square_ring_plot_currents.png}
+  \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_circ_plot_currents.png}
   \caption{Square ring sheet current.}
@@
   \centering
-  \includegraphics[width=\linewidth]{examples/images/ring/square_ring_plot_fields.png}
+  \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_circ_plot_fields.png}
   \caption{Square ring magnetic field.}

### 2021-08-02 examples/scripts/ring.py
use 0.25 mT

@@ -118,7 +118,7 @@ if __name__ == "__main__":
         )
 
         # Uniform applied field
-        applied_field = sc.sources.ConstantField(0.2)  # mT
+        applied_field = sc.sources.ConstantField(0.25)  # mT
 
         # Current circulating around the hole in the ring.
         circulating_currents = {"hole": "1 mA"}
@@ -205,7 +205,7 @@ if __name__ == "__main__":
         # Simulate the field and current distributions for a given
         # uniform applied field across a wide range of Lambdas,
         # assuming no trapped flux.
-        applied_field = sc.sources.ConstantField(0.2)
+        applied_field = sc.sources.ConstantField(0.25)
 
         solutions, _ = sc.solve_many(
             device=ring,

### 2021-08-02 main_cpc.tex
Updates from Overleaf

@@
 \begin{minted}[fontsize=\footnotesize]{python}
-# Simulate the response to a uniform applied field of 0.2 mT
-applied_field = sc.sources.ConstantField(0.2)
+# Simulate the response to a uniform applied field of 0.25 mT
+applied_field = sc.sources.ConstantField(0.25)
 field_units = "mT"
@@
 \caption{Sheet current $\vec{J}$ and magnetic field $\mu_0H_z$ distributions for the circular (top) and square (bottom) ring calculated using Code Block~\ref{code:ring_circulating_current}.}
-\label{fig:ring_circulating_current}
+\label{fig:ring_plot_fields_currents}
 \end{figure}

### 2021-08-02 examples/scripts/disk.py
alias supercreen.geometry

@@ -4,6 +4,7 @@ import logging
 import numpy as np
 
 import superscreen as sc
+import superscreen.geometry as geo
 
 from plot_solutions import plot_solutions
 
@@ -16,14 +17,14 @@ def make_disk(Lambda=1, radius=5, length_units="um"):
         sc.Polygon(
             "disk",
             layer="base",
-            points=sc.geometry.circle(radius, points=401),
+            points=geo.circle(radius, points=401),
         ),
     ]
     abstract_regions = [
         sc.Polygon(
             "bounding_box",
             layer="base",
-            points=sc.geometry.square(2 * (radius + 1), points_per_side=11),
+            points=geo.square(2 * (radius + 1), points_per_side=11),
         ),
     ]
     disk = sc.Device(

### 2021-08-02 examples/scripts/ring.py

@@ -4,6 +4,7 @@ import logging
 import numpy as np
 
 import superscreen as sc
+import superscreen.geometry as geo
 
 from plot_solutions import plot_solutions
 
@@ -17,20 +18,20 @@ def make_ring(
 ):
     if square:
         name = "square_ring"
-        outer_points = sc.geometry.square(
+        outer_points = geo.square(
             outer_radius * 2, points_per_side=60
         )
-        inner_points = sc.geometry.square(
+        inner_points = geo.square(
             inner_radius * 2, points_per_side=20
         )
-        bbox_points = sc.geometry.square(
+        bbox_points = geo.square(
             outer_radius * 2 * 1.4, points_per_side=5
         )
     else:
         name = "circular_ring"
-        outer_points = sc.geometry.circle(outer_radius)
-        inner_points = sc.geometry.circle(inner_radius)
-        bbox_points = sc.geometry.circle(outer_radius * 1.4, points=21)
+        outer_points = geo.circle(outer_radius)
+        inner_points = geo.circle(inner_radius)
+        bbox_points = geo.circle(outer_radius * 1.4, points=21)
 
     layers = [sc.Layer("base", Lambda=Lambda, z0=0)]
     films = [sc.Polygon("ring", layer="base", points=outer_points)]

### 2021-08-02 main_cpc.tex
Updates from Overleaf

@@
 The \mintinline{python}{superscreen.geometry} module provides functions for generating the underlying polygon vertices for simple geometries (circles and rectangles).
-See Code Block~\ref{code:device} for an example of a function that creates a square or circular superconducting ring centered at the origin.
+See Code Block~\ref{code:device} for an example of a function that creates a square or circular superconducting ring centered at the origin, with an effective penetration depth $\Lambda = 1\,\mu\mathrm{m}$.
 
@@
 import superscreen as sc
+import superscreen.geometry as geo
 
@@
         name = "square_ring"
-        outer_points = sc.geometry.square(
-            outer_radius * 2, points_per_side=60
-        )
-        inner_points = sc.geometry.square(
-            inner_radius * 2, points_per_side=20
-        )
-        bbox_points = sc.geometry.square(
-            outer_radius * 2 * 1.4, points_per_side=5
-        )
+        outer = geo.square(outer_radius * 2, points_per_side=60)
+        inner = geo.square(inner_radius * 2, points_per_side=20)
+        bbox = geo.square(outer_radius * 2 * 1.4, points_per_side=5)
     else:
         name = "circular_ring"
-        outer_points = sc.geometry.circle(outer_radius)
-        inner_points = sc.geometry.circle(inner_radius)
-        bbox_points = sc.geometry.circle(outer_radius * 1.4, points=21)
+        outer_points = geo.circle(outer_radius)
+        inner_points = geo.circle(inner_radius)
+        bbox = geo.circle(outer_radius * 1.4, points=21)
 
@@
     abstract_regions = [
-        sc.Polygon("bounding_box", layer="base", points=bbox_points),
+        sc.Polygon("bounding_box", layer="base", points=bbox),
     ]
@@
   \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_uniform_plot_currents.png}
-  \caption{Circular ring sheet current.}
+  \caption{Screening current, uniform applied field model.}
   \label{fig:circular_ring_plot_currents}
@@
   \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_uniform_plot_fields.png}
-  \caption{Circular ring magnetic field.}
+  \caption{Total magnetic field, uniform applied field model.}
   \label{fig:circular_ring_plot_fields}
@@
   \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_circ_plot_currents.png}
-  \caption{Square ring sheet current.}
+  \caption{Screening current, trapped flux model.}
   \label{fig:square_ring_plot_currents}
@@
   \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_circ_plot_fields.png}
-  \caption{Square ring magnetic field.}
+  \caption{Total magnetic field, trapped flux model.}
   \label{fig:square_ring_plot_fields}
@@
 
-\caption{Sheet current $\vec{J}$ and magnetic field $\mu_0H_z$ distributions for the circular (top) and square (bottom) ring calculated using Code Block~\ref{code:ring_circulating_current}.}
+\caption{Sheet current $\vec{J}$ and magnetic field $\mu_0H_z$ distributions for the circular ring with a uniform applied field of 0.25 mT (top) and a circulating current of 1 mA (bottom) calculated using Code Block~\ref{code:ring_circulating_current}.}
 \label{fig:ring_plot_fields_currents}
@@
 \end{itemize}
+\mintinline{python}{Solutions} also have several visualization methods built in (see Section~\ref{section:overview:visualization}).
 

### 2021-08-03 examples/scripts/square_washer.py
Add susceptometry example

@@ -1,127 +1,0 @@
-import os
-import logging
-
-import numpy as np
-
-import superscreen as sc
-
-from plot_solutions import plot_solutions
-
-
-def make_washer(inner_radius=2.5, outer_radius=5, Lambda=1, length_units="um"):
-    layers = [
-        sc.Layer("base", Lambda=Lambda, z0=0),
-    ]
-    films = [
-        sc.Polygon(
-            "washer",
-            layer="base",
-            points=sc.geometry.circle(outer_radius),
-        ),
-    ]
-    holes = [
-        sc.Polygon(
-            "hole",
-            layer="base",
-            points=sc.geometry.circle(inner_radius),
-        ),
-    ]
-    abstract_regions = [
-        sc.Polygon(
-            "bounding_box",
-            layer="base",
-            points=sc.geometry.circle(outer_radius * 1.4, points=21),
-        )
-    ]
-    washer = sc.Device(
-        "washer",
-        layers=layers,
-        films=films,
-        holes=holes,
-        abstract_regions=abstract_regions,
-        length_units=length_units,
-    )
-    return washer
-
-
-if __name__ == "__main__":
-
-    logging.basicConfig(level=logging.INFO)
-
-    imagedir = os.path.join(os.pardir, "images")
-
-    inner_radius = 2.5
-    outer_radius = 5.0
-    Lambda = 1
-    length_units = "um"
-    field_units = "mT"
-
-    # Make the disk Device
-    washer = make_washer(
-        inner_radius=inner_radius,
-        outer_radius=outer_radius,
-        Lambda=Lambda,
-        length_units=length_units,
-    )
-    washer.make_mesh(min_triangles=8000, optimesh_steps=400)
-
-    # Simulate a current circulating around the hole in the washer.
-    circulating_currents = {"hole": "1 mA"}
-
-    solution = sc.solve(device=washer, circulating_currents=circulating_currents)[-1]
-    fig, axes = solution.plot_fields(figsize=(6, 7), cross_section_ys=[0])
-    fig.savefig(os.path.join(imagedir, f"{washer.name}_plot_fields.png"))
-
-    fig, axes = solution.plot_currents(
-        figsize=(6, 7), cross_section_ys=[0], units="mA/um"
-    )
-    fig.savefig(os.path.join(imagedir, f"{washer.name}_plot_currents.png"))
-
-    # Perform a surface integral of the resulting fields to calculcate the
-    # flux through the washer and the washer's self-inductance.
-    flux_dict = solution.polygon_flux()
[…]

### 2021-08-03 examples/scripts/susceptometry.py

@@ -1,0 +1,243 @@
+import os
+import time
+import logging
+
+import ray
+import numpy as np
+import matplotlib.pyplot as plt
+
+import superscreen as sc
+import superscreen.geometry as geo
+
+
+def susceptibility_analytical(z, Lambda, a=8.4):
+    """See Table 1 of 10.1103/PhysRevB.85.224518 (arXiv:1204.3355).
+    
+    Args:
+        z: Vertical distance between the sample and sensor.
+        Lambda: Effective penetration depth of the sample,
+            Lambda = london_lambda**2/thickness.
+        a: Effective field coil radius = 8.4 microns from the paper.
+    
+    Returns:
+        Normalized susceptibility signal (M - M_no_sample) / M_no_sample,
+        where M is the field coil - pickup loop mutual inductance.
+    """
+    # In the above paper, Lambda = 2 * lambda_london**2 / thickness, i.e. Pearl length.
+    Lambda_Pearl = 2 * Lambda
+    zbar = z / a
+    return -a / Lambda_Pearl * (1 - 2 * zbar / np.sqrt(1 + 4 * zbar ** 2))
+
+
+def sensor_and_sample(
+    *,
+    field_coil_inner_radius,
+    field_coil_outer_radius,
+    field_coil_Lambda,
+    pickup_loop_inner_radius,
+    pickup_loop_outer_radius,
+    pickup_loop_Lambda,
+    sample_size,
+    sample_Lambda,
+    sample_z0=-1,
+    length_units="um",
+):
+    layers = [
+        sc.Layer("fc_layer", Lambda=field_coil_Lambda, z0=0.57),
+        sc.Layer("pl_layer", Lambda=pickup_loop_Lambda, z0=0),
+        sc.Layer("sample_layer", Lambda=sample_Lambda, z0=sample_z0)
+    ]
+    films = [
+        sc.Polygon(
+            "field_coil", layer="fc_layer", points=geo.circle(field_coil_outer_radius)
+        ),
+        sc.Polygon(
+            "pickup_loop", layer="pl_layer", points=geo.circle(pickup_loop_outer_radius)
+        ),
+        sc.Polygon(
+            "sample", layer="sample_layer", points=geo.square(sample_size)
+        ),
+    ]
+    holes = [
+        sc.Polygon(
+            "fc_hole", layer="fc_layer", points=geo.circle(field_coil_inner_radius)
+        ),
+        sc.Polygon(
[…]

### 2021-08-10 examples/scripts/disk.py
updates

@@ -59,8 +59,8 @@ if __name__ == "__main__":
     disk.make_mesh(min_triangles=8000, optimesh_steps=100)
 
     # Plot the disk's mesh and polygons
-    ax = disk.plot_mesh(figsize=(6, 6))
-    ax = disk.plot_polygons(ax=ax, color="k")
+    ax = disk.plot_mesh(figsize=(6, 6), color="k", alpha=0.5)
+    ax = disk.plot_polygons(ax=ax, linewidth=4)
     npoints = disk.points.shape[0]
     ntriangles = disk.triangles.shape[0]
     ax.set_title(f"{disk.name} mesh:\n{npoints} points, {ntriangles} triangles")

### 2021-08-10 examples/scripts/ring.py

@@ -106,17 +106,22 @@ if __name__ == "__main__":
             length_units=length_units,
             square=square,
         )
-        ring.make_mesh(min_triangles=8000, optimesh_steps=400)
+        for optimesh_steps in [None, 400]:
+            if optimesh_steps is None:
+                save_path = os.path.join(
+                    imagedir, f"{ring.name}_mesh_no_optimesh.png"
+                )
+            else:
+                save_path = os.path.join(imagedir, f"{ring.name}_mesh.png")
 
-        ax = ring.plot_mesh(figsize=(6, 6))
-        ax = ring.plot_polygons(ax=ax, color="k")
-        npoints = ring.points.shape[0]
-        ntriangles = ring.triangles.shape[0]
-        ax.set_title(f"{ring.name} mesh:\n{npoints} points, {ntriangles} triangles")
-        ax.figure.savefig(
-            os.path.join(imagedir, f"{ring.name}_mesh.png"),
-            bbox_inches="tight",
-        )
+            ring.make_mesh(min_triangles=8000, optimesh_steps=optimesh_steps)
+
+            ax = ring.plot_mesh(figsize=(6, 6), color="k", alpha=0.5)
+            ax = ring.plot_polygons(ax=ax, linewidth=4)
+            npoints = ring.points.shape[0]
+            ntriangles = ring.triangles.shape[0]
+            ax.set_title(f"{ring.name} mesh:\n{npoints} points, {ntriangles} triangles")
+            ax.figure.savefig(save_path, bbox_inches="tight", dpi=150)
 
         # Uniform applied field
         applied_field = sc.sources.ConstantField(0.25)  # mT

### 2021-08-10 examples/scripts/squid_susceptometry/huber_squid.py

@@ -1,0 +1,245 @@
+import numpy as np
+
+import superscreen as sc
+
+
+def huber_geometry(interp_points=101):
+
+    ri_pl = 1.7
+    ro_pl = 2.7
+    w_pl_center = 1.18
+    w_pl_outer = 3.10
+    pl_angle = 0
+    pl_total_length = 15
+    y0_pl_leads = -(pl_total_length - ro_pl)
+
+    x0_pl_center = w_pl_center / 2
+    theta0_pl_center = np.arcsin(x0_pl_center / ri_pl)
+    thetas_pl_center = (
+        np.linspace(theta0_pl_center, 2 * np.pi - theta0_pl_center, 101) - np.pi / 2
+    )
+
+    x0_pl_outer = w_pl_outer / 2
+    theta0_pl_outer = np.arcsin(x0_pl_outer / ro_pl)
+    thetas_pl_outer = (
+        np.linspace(theta0_pl_outer, 2 * np.pi - theta0_pl_outer, 101) - np.pi / 2
+    )
+
+    pl_points = np.concatenate(
+        [
+            [[-w_pl_outer / 2, y0_pl_leads]],
+            ro_pl
+            * np.stack([np.cos(thetas_pl_outer), np.sin(thetas_pl_outer)], axis=1)[
+                ::-1
+            ],
+            [[w_pl_outer / 2, y0_pl_leads]],
+            [[w_pl_center / 2, y0_pl_leads]],
+            ri_pl
+            * np.stack([np.cos(thetas_pl_center), np.sin(thetas_pl_center)], axis=1),
+            [[-w_pl_center / 2, y0_pl_leads]],
+            [[-w_pl_outer / 2, y0_pl_leads]],
+        ]
+    )
+    pl_points = sc.geometry.rotate(pl_points, pl_angle)
+
+    pl_shield = np.concatenate(
+        [
+            [[-(w_pl_outer / 2 + 0.25), -(ri_pl + 0.5)]],
+            [[-w_pl_outer / 2, -(ri_pl + 0.25)]],
+            [[+w_pl_outer / 2, -(ri_pl + 0.25)]],
+            [[+(w_pl_outer / 2 + 0.25), -(ri_pl + 0.5)]],
+            [[+(w_pl_outer / 2 + 0.25), y0_pl_leads - 0.5]],
+            [[-(w_pl_outer / 2 + 0.25), y0_pl_leads - 0.5]],
[…]

### 2021-08-10 examples/scripts/squid_susceptometry/sweep_lambda_z0.py

@@ -1,0 +1,249 @@
+import os
+import time
+import logging
+import tempfile
+
+import ray
+import numpy as np
+import pandas as pd
+import matplotlib.pyplot as plt
+
+import superscreen as sc
+
+from .huber_squid import squid_with_sample
+
+plt.rcParams["font.size"] = 14
+plt.rcParams["savefig.dpi"] = 150
+
+
+def layer_updater(layer, Lambda=None, z0=None):
+    if layer.name == "sample_layer":
+        if Lambda is not None:
+            layer.Lambda = Lambda
+        if z0 is not None:
+            layer.z0 = z0
+    return layer
+
+
+if __name__ == "__main__":
+    import argparse
+
+    parser = argparse.ArgumentParser()
+    parser.add_argument(
+        "--sweep_type",
+        choices=["Lambda", "z0"],
+        help="Parameter to sweep, either Lambda or z0."
+    )
+    parser.add_argument(
+        "-n",
+        "--num_points",
+        type=int,
+        default=10,
+        help="Number of points in the sweep."
+    )
+    parser.add_argument(
+        "-c",
+        "--num_cpus",
+        type=int,
+        default=0,
+        help="Number of CPUs to use. Set to 0 for serial execution."
+    )
+    parser.add_argument(
+        "-f",
+        "--figures",
+        type=bool,
+        default=True,
+        help="Whether to save all figures."
+    )
+    args = parser.parse_args()
+
+    parallel_method = "ray" if (args.num_cpus > 0) else None
+
+    logging.basicConfig(level=logging.INFO)
+
+    imagedir = os.path.join(os.pardir, "images", "squid_susceptometry")
+    os.makedirs(imagedir, exist_ok=True)
+    
+    squid = squid_with_sample()
+    print(squid)
+    squid.make_mesh(min_triangles=8500, optimesh_steps=400)
+
+    if args.figures:
+        ax = squid.plot_mesh(figsize=(8, 6), color="k", alpha=0.5)
+        ax = squid.plot_polygons(ax=ax, linewidth=4)
+        npoints = squid.points.shape[0]
+        ntriangles = squid.triangles.shape[0]
+        ax.set_title(f"{squid.name} mesh:\n{npoints} points, {ntriangles} triangles")
+        ax.figure.savefig(
+            os.path.join(imagedir, f"{squid.name}_mesh.png"),
+            bbox_inches="tight",
+            dpi=150,
+        )
+
+    # Current flowing in the field coil
[…]

### 2021-08-10 examples/scripts/susceptometry.py

@@ -31,36 +31,46 @@ def susceptibility_analytical(z, Lambda, a=8.4):
 
 def sensor_and_sample(
     *,
-    field_coil_inner_radius,
-    field_coil_outer_radius,
+    field_coil_mean_radius,
     field_coil_Lambda,
-    pickup_loop_inner_radius,
-    pickup_loop_outer_radius,
+    pickup_loop_mean_radius,
     pickup_loop_Lambda,
-    sample_size,
+    line_width,
     sample_Lambda,
     sample_z0=-1,
     length_units="um",
 ):
     layers = [
-        sc.Layer("fc_layer", Lambda=field_coil_Lambda, z0=0.57),
-        sc.Layer("pl_layer", Lambda=pickup_loop_Lambda, z0=0),
+        sc.Layer("fc_layer", Lambda=field_coil_Lambda, z0=0),
+        sc.Layer("pl_layer", Lambda=pickup_loop_Lambda, z0=-0.4),
         sc.Layer("sample_layer", Lambda=sample_Lambda, z0=sample_z0)
     ]
+    field_coil_outer_radius = field_coil_mean_radius + line_width / 2
+    field_coil_inner_radius = field_coil_mean_radius - line_width / 2
+    pickup_loop_outer_radius = pickup_loop_mean_radius + line_width / 2
+    pickup_loop_inner_radius = pickup_loop_mean_radius - line_width / 2
     films = [
         sc.Polygon(
-            "field_coil", layer="fc_layer", points=geo.circle(field_coil_outer_radius)
+            "field_coil",
+            layer="fc_layer",
+            points=geo.circle(field_coil_outer_radius, points=301),
         ),
         sc.Polygon(
-            "pickup_loop", layer="pl_layer", points=geo.circle(pickup_loop_outer_radius)
+            "pickup_loop",
+            layer="pl_layer",
+            points=geo.circle(pickup_loop_outer_radius),
         ),
         sc.Polygon(
-            "sample", layer="sample_layer", points=geo.square(sample_size)
+            "sample",
+            layer="sample_layer",
+            points=geo.circle(field_coil_mean_radius * 1.5, points=21),
         ),
     ]
     holes = [
         sc.Polygon(
-            "fc_hole", layer="fc_layer", points=geo.circle(field_coil_inner_radius)
+            "fc_hole",
+            layer="fc_layer",
+            points=geo.circle(field_coil_inner_radius, points=201),
         ),
[…]

### 2021-08-10 examples/scripts/squid_susceptometry/sweep_lambda_z0.py
Update sweep_lambda_z0.py

@@ -1,4 +1,7 @@
 import os
+
+os.environ["OPENBLAS_NUM_THREADS"] = "1"
+
 import time
 import logging
 import tempfile

### 2021-08-10 main.tex
Updates from Overleaf

@@
-\documentclass{article}
-\usepackage[utf8]{inputenc}
-\usepackage{geometry}
-\geometry{letterpaper, margin=1.5in}
+%% This template can be used to write a paper for
+%% Computer Physics Communications using LaTeX.
+%% For authors who want to write a computer program description,
+%% an example Program Summary is included that only has to be
+%% completed and which will give the correct layout in the
+%% preprint and the journal.
+%% The `elsarticle' style is used and more information on this style
+%% can be found at 
+%% http://www.elsevier.com/wps/find/authorsview.authors/elsarticle.
+%%
+
+%% Use the option review to obtain double line spacing
+% \documentclass[preprint,12pt]{elsarticle}
+
+%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
+%% for a journal layout:
+% \documentclass[final,1p,times]{elsarticle}
+% \documentclass[final,1p,times,twocolumn]{elsarticle}
+\documentclass[final,3p,times]{elsarticle}
+% \documentclass[final,3p,times,twocolumn]{elsarticle}
+%% \documentclass[final,5p,times]{elsarticle}
+% \documentclass[final,5p,times,twocolumn]{elsarticle}
+
+\usepackage{subcaption}
+\usepackage[newfloat]{minted}
+\usepackage{hyperref}
+\usepackage{tcolorbox}
+\usepackage{etoolbox}
+\BeforeBeginEnvironment{minted}{\begin{center}\begin{tcolorbox}[width=0.9\textwidth]}
+\AfterEndEnvironment{minted}{\end{tcolorbox}\end{center}}
+\usepackage{caption}
+\usepackage{xspace}
+\usepackage[toc,page]{appendix}
+
+\newcommand{\inline}[1]{\mintinline{python}{#1}\xspace}
+\newcommand{\SuperScreen}{\inline{SuperScreen}}
+
+\newenvironment{code}{\captionsetup{type=listing}}{\hfill}
+\SetupFloatingEnvironment{listing}{name=Code Block}
+
+%% if you use PostScript figures in your article
+%% use the graphics package for simple commands
+%% \usepackage{graphics}
+%% or use the graphicx package for more complicated commands
+%% \usepackage{graphicx}
+%% or use the epsfig package if you prefer to use the old commands
+%% \usepackage{epsfig}
+
+%% The amssymb package provides various useful mathematical symbols
 \usepackage{amsmath, amssymb, bm}
-\usepackage{minted}
+%% The amsthm package provides extended theorem environments
+%% \usepackage{amsthm}
 
-\newcommand{\SuperScreen}{\mintinline{python}{SuperScreen}\,}
+%% The lineno packages adds line numbers. Start line numbering with
+%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
+%% for the whole article with \linenumbers after \end{frontmatter}.
+%% \usepackage{lineno}
 
-\title{\texttt{SuperScreen}}
-\author{Logan Bishop-Van Horn}
-\date{\today}
+%% natbib.sty is loaded by default. However, natbib options can be
+%% provided with \biboptions{...} command. Following options are
+%% valid:
+
+%%   round  -  round parentheses are used (default)
+%%   square -  square brackets are used   [option]
+%%   curly  -  curly braces are used      {option}
+%%   angle  -  angle brackets are used    <option>
+%%   semicolon  -  multiple citations separated by semi-colon
+%%   colon  - same as semicolon, an earlier confusion
+%%   comma  -  separated by comma
+%%   numbers-  selects numerical citations
+%%   super  -  numerical citations as superscripts
+%%   sort   -  sorts multiple citations according to order in ref. list
+%%   sort&compress   -  like sort, but also compresses numerical citations
+%%   compress - compresses without sorting
+%%
+%% \biboptions{comma,round}
+
+% \biboptions{}
+
+%% This list environment is used for the references in the
+%% Program Summary
+%%
+\newcounter{bla}
+\newenvironment{refnummer}{%
+\list{[\arabic{bla}]}%
+{\usecounter{bla}%
+ \setlength{\itemindent}{0pt}%
+ \setlength{\topsep}{0pt}%
+ \setlength{\itemsep}{0pt}%
+ \setlength{\labelsep}{2pt}%
+ \setlength{\listparindent}{0pt}%
+ \settowidth{\labelwidth}{[9]}%
+ \setlength{\leftmargin}{\labelwidth}%
+ \addtolength{\leftmargin}{\labelsep}%
+ \setlength{\rightmargin}{0pt}}}
+ {\endlist}
+
+\journal{Computer Physics Communications}
 
@@
 
-\maketitle
+\begin{frontmatter}
 
+%% Title, authors and addresses
+
+%% use the tnoteref command within \title for footnotes;
+%% use the tnotetext command for the associated footnote;
+%% use the fnref command within \author or \address for footnotes;
+%% use the fntext command for the associated footnote;
+%% use the corref command within \author for corresponding author footnotes;
+%% use the cortext command for the associated footnote;
+%% use the ead command for the email address,
+%% and the form \ead[url] for the home page:
+%%
+%% \title{Title\tnoteref{label1}}
+%% \tnotetext[label1]{}
+%% \author{Name\corref{cor1}\fnref{label2}}
+%% \ead{email address}
+%% \ead[url]{home page}
+%% \fntext[label2]{}
+%% \cortext[cor1]{}
+%% \address{Address\fnref{label3}}
+%% \fntext[label3]{}
+
+\title{\texttt{SuperScreen}: An open-source package for simulating the magnetic response of two-dimensional superconductors}
+
+%% use optional labels to link authors explicitly to addresses:
+%% \author[label1,label2]{<author name>}
+%% \address[label1]{<address>}
+%% \address[label2]{<address>}
+
+\author[a]{Logan Bishop-Van Horn}
+\author[a,b]{Kam Moler\corref{author}}
+
+\cortext[author]{Corresponding author.\\\textit{E-mail address:} kmoler@stanford.edu}
+\address[a]{First Address}
+\address[b]{Second Address}
+
+\begin{abstract}
+Quantitative understanding of the spatial distribution of magnetic fields and screening currents in two-dimensional (2D) superconductors and mesoscopic superconducting devices is critical to interpreting the results of magnetic measurements of such systems.
+Here we introduce \SuperScreen, an open-source Python package for simulating the magnetic response of two-dimensional superconductors to applied time-independent magnetic fields.
+Given an applied magnetic field, \SuperScreen solves for Meissner screening currents and the resulting magnetic fields in structures composed of one or more superconducting thin films of arbitrary geometry with spatially inhomogeneous magnetic penetration depth using a matrix inversion method introduced by Brandt~\cite{brandt_thin_2005}.
+\SuperScreen can be used to model screening effects and calculate self- and mutual-inductance in superconducting circuits, and simulate the magnetic response of inhomogeneous 2D superconductors.
+
+\end{abstract}
+
+\begin{keyword}
+%% keywords here, in the form: keyword \sep keyword
+superconductivity\sep Meissner screening\sep thin film
+
+\end{keyword}
+
+\end{frontmatter}
+
+%%
+%% Start line numbering here if you want
+%%
+% \linenumbers
+
+% All CPiP articles must contain the following
+% PROGRAM SUMMARY.
+\noindent
+{\bf PROGRAM SUMMARY}
+
+\begin{small}
+\noindent
+{\em SuperScreen}\\
+{\em CPC Library link to program files:} (to be added by Technical Editor) \\
+{\em Developer's repository link:} \href{http://www.github.com/loganbvh/superscreen}{www.github.com/loganbvh/superscreen}\\
+{\em Code Ocean capsule:} (to be added by Technical Editor)\\
+{\em Licensing provisions:} MIT\\
+{\em Programming language: Python}\\
+% {\em Supplementary material:}\\
+  % Fill in if necessary, otherwise leave out.
+% {\em Journal reference of previous version:}*\\
+  %Only required for a New Version summary, otherwise leave out.
+% {\em Does the new version supersede the previous version?:}*\\
+  %Only required for a New Version summary, otherwise leave out.
+% {\em Reasons for the new version:*}\\
+  %Only required for a New Version summary, otherwise leave out.
+% {\em Summary of revisions:}*\\
+  %Only required for a New Version summary, otherwise leave out.
+{\em Nature of problem:} \SuperScreen solves for Meissner screening currents in structures composed of 2D or thin film superconductors in the presence of an applied magnetic field.\\
+  %Describe the nature of the problem here. \\
+{\em Solution method:} The package solves the 2D London equations inside superconducting regions and Maxwell's equations outside the superconductor using a matrix inversion method introduced by Brandt~\cite{brandt_thin_2005}.\\
+  %Describe the method solution here.
+% {\em Additional comments including restrictions and unusual features (approx. 50-250 words):}\\
+  %Provide any additional comments here.
+   \\
+
+% \begin{thebibliography}{0}
+% \bibitem{1}Reference 1         % This list should only contain those items referenced in the                 
+% \bibitem{2}Reference 2         % Program Summary section.   
+% \bibitem{3}Reference 3         % Type references in text as [1], [2], etc.
+%                               % This list is different from the bibliography at the end of 
+%                               % the Long Write-Up.
+% \end{thebibliography}
+\end{small}
+
+%% main text
 \section{Introduction}
@@
 In Section~\ref{section:model} we outline Brandt's model, and in Section~\ref{section:implementation} we describe its numerical implementation.
-In Section~\ref{section:overview}, we provide an overview of the structure of the \SuperScreen package, highlighting important functions, classes, and features, and discuss some important development details.
-In Section~\ref{section:examples}, we demonstrate how to set up and solve several types of models using \SuperScreen.
-Finally, in Section~\ref{section:conlusion} we discuss potential applications, extensions, and improvements to the package.
+In Section~\ref{section:overview}, we provide an overview of the structure of the \SuperScreen package, highlighting notable functions, classes, and features, and discuss some important development details.
+Finally, in Section~\ref{section:conlusion} we conclude with potential applications, extensions, and improvements to the package.
 
@@
 
-The matrix version of Eq.~\ref{eq:field_from_kernel} is:
+The matrix version of Eq.~\ref{eq:field_from_kernel} is
 
@@
 corresponding vertex in the mesh.
-There are several different methods for constructing the weight matrix $\mathbf{w}$, which are discussed in Section~\ref{section:implementation:laplace} below.
-The kernel
-matrix $\mathbf{Q}$ is defined in terms of a matrix with
-$(\mathbf{q})_{ij} = \left(4\pi|\vec{r}_i-\vec{r}_j|^3\right)^{-1}$
-(which is $\lim_{\Delta z\to 0}Q_z(\vec{r},\vec{r}')$ cf. Eq.~\ref{eq:kernels}),
-and a vector $\mathbf{C}$:
+There are several different methods for constructing the weight matrix $\mathbf{w}$, which are discussed in~\ref{section:implementation:laplace}.
+The kernel matrix $\mathbf{Q}$ is given by
 
@@
 \end{equation}
-where $\delta_{ij}$ is the Kronecker delta function.
-The diagonal terms involving $\mathbf{C}$ are meant to work around the fact that $q_{ii}$ diverge (see \cite{brandt_thin_2005} for more details), and the vector is defined as
+where $q_{ij} = \left(4\pi|\vec{r}_i-\vec{r}_j|^3\right)^{-1}$
+(which is $\lim_{\Delta z\to 0}Q_z(\vec{r},\vec{r}')$ cf. Eq.~\ref{eq:kernels}),
+and $\delta_{ij}$ is the Kronecker delta function.
+The diagonal terms involving the vector $\mathbf{C}$ are meant to work around the fact that $q_{ii}$ diverge (see \cite{brandt_thin_2005} for more details), and $\mathbf{C}$ is given by
 
@@
 
-The matrix version of Eq.~\ref{eq:Heff_sub} is:
+The matrix version of Eq.~\ref{eq:Heff_sub} is
 
@@
 \end{equation}
-where we exclude points in the mesh lying outside of the superconducting film, but keep points
+where we exclude points in the mesh lying outside of the superconducting film but keep points
 inside holes in the film. $\mathbf{\Lambda}$ is either a scalar or a vector defining the effective penetration depth at every included vertex in the mesh, and $\mathbf{\nabla}^2$
-is the Laplace operator (see Section~\ref{section:implementation:laplace}), an $n\times n$ matrix defined such that $\mathbf{\nabla}^2\mathbf{f}$ computes the Laplacian $\nabla^2f(x,y)$ of a function $f(x,y)$ defined on the mesh.
+is the Laplace operator, an $n\times n$ matrix defined such that $\mathbf{\nabla}^2\mathbf{f}$ computes the Laplacian $\nabla^2f(x,y)$ of a function $f(x,y)$ defined on the mesh  (see~\ref{section:implementation:laplace}).
 
@@
 
-\subsection{Laplace operator}
+\section{Package Overview}
+\label{section:overview}
+
+In this section we give a high-level overview of the \SuperScreen package. More detailed documentation and tutorials can be found online in [ref. for online documentation].
+
+\subsection{Development Details}
+\label{section:overview:development}
+
+\SuperScreen requires Python version 3.6 or later.
+The package is located in a public repository on GitHub~\cite{superscreen}, and a suite of unit tests is run automatically via GitHub Actions whenever a change or proposed change (Pull Request) is made to the \inline{main} branch of the repository.
+At the time of writing, the test suite is executed using Python versions 3.6, 3.7, 3.8, and 3.9, and the test coverage is XX\%.
+Any changes to the \inline{main} branch of the repository also trigger an automatic re-build of the online documentation, which is hosted by Read the Docs at superscreen.readthedocs.io [ref.
+for online documentation].
+Stable versions of the package are tagged on GitHub and uploaded to PyPI, the Python Package Index [ref for pypi].
+The source code and documentation are covered by the MIT License.
+
+\SuperScreen has several important dependencies beyond the Python standard library: \inline{numpy}~\cite{2020NumPy-Array} and \inline{scipy}~\cite{2020SciPy-NMeth} for numerics, \inline{pint}~\cite{Grecco} for handling physical units, \inline{matplotlib}~\cite{Hunter_2007} for visualization, \inline{meshpy}~\cite{Klockner,Shewchuk,shewchuk96b} and \inline{optimesh}~\cite{nico_schlomer_adam_dobrawy_2021} for mesh generation, \inline{dill}~\cite{McKerns} for serializing objects to disk and between processes, and \inline{ray}~\cite{ray_2018,ray-docs} for parallel processing with shared memory (see~\ref{section:parallel}).
+
+\subsection{Parameters}
+\label{section:overview:parameter}
+
+A \inline{superscreen.Parameter} is a wrapper around a Python function that computes a scalar value as a function of position coordinates ($x$, $y$, and optionally $z$) based on some set of keyword arguments.
+Addition, subtraction, multiplication, division, and exponentiation between \inline{Parameters}, other \inline{Parameters}, and Python scalars (\inline{int} and \inline{float}) are supported.
+For example, see Code Block~\ref{code:parameters}.
+\inline{Parameters} can be used to conveniently define applied magnetic fields and penetration depths that depend on position, and make it possible to serialize wrapped Python functions for storage or inter-process communication.
+
+\begin{code}
+\begin{minted}[fontsize=\small]{python}
+from superscreen import Parameter
+
+def f(x, y, a=1, b=0):
+    return a * x**2 + b * y
+
+param = Parameter(f, a=0, b=1)
+print(param)
+# Parameter<f(a=0, b=1)>
+
+other_param = Parameter(f, a=2, b=3)
+print(other_param)
+# Parameter<f(a=2, b=3)>
+
+print(param(0, 0) == f(0, 0, a=0, b=1))
+# True
+print(other_param(1, 2) == f(1, 2, a=2, b=3))
+# True
+
+param_squared = param ** 2
+print(param_squared)
+# CompositeParameter<(f(a=0, b=1) ** 2)>
+
+print(param_squared(3, 4) == f(3, 4, a=0, b=1) ** 2)
+# True
+print(
+    (5 * param_squared / other_param)(5, 6)
+    == 5 * f(5, 6, a=0, b=1) ** 2 / f(5, 6, a=2, b=3)
+)
+# True
+\end{minted}
+\captionof{listing}{The basic usage of \inline{superscreen.Parameters}.}
+\label{code:parameters}
+\end{code}
+
+\subsection{Devices}
+\label{section:overview:device}
+
+Information about the geometry and penetration depth of a superconducting structure is described by an instance of the \inline{superscreen.Device} class.
+A \inline{Device} is made up of one or more superconducting layers, each represented by an instance of  \inline{superscreen.Layer}.
+Each layer sits in a specified plane parallel to the $x-y$ plane and has its own effective penetration depth $\Lambda$, which can either be a constant or a \inline{superscreen.Parameter} that defines $\Lambda(x, y)$, the effective penetration depth as a function of position.
+The effective penetration depth $\Lambda$ can instead be defined in terms of a layer's London penetration depth $\lambda$ and its thickness $d$: $\Lambda=\lambda^2/d$, in which case the London penetration depth can be either a constant or a \inline{superscreen.Parameter}.
+
+Each layer can contain one or more superconducting films which may have one or more holes in them.
+Films and holes are represented by instances of the \inline{superscreen.Polygon} class.
+A \inline{Polygon} contains the name of the layer to which is belongs, an array specifying the coordinates of its vertices, and a method, \inline{Polygon.contains_points()}, which determines whether specified coordinates lie within the polygon or not.
+In addition to superconducting films and holes, one may define ``abstract regions,'' which are polygons that need not correspond to a physical feature in the structure, but will still be meshed.
+Abstract regions can be used to define a ``bounding box" around a structure.
+The \inline{superscreen.geometry} module provides functions for generating the underlying polygon vertices for simple geometries (circles and rectangles).
+See Code Block~\ref{code:device} for an example of a function that creates a square or circular superconducting ring centered at the origin, with an effective penetration depth $\Lambda = 1\,\mu\mathrm{m}$.
+
+\begin{code}
+\begin{minted}[fontsize=\small]{python}
+import superscreen as sc
+import superscreen.geometry as geo
+
+def make_ring(
+    inner_radius=2.5,
+    outer_radius=5,
+    Lambda=1,
+    length_units="um",
+    square=False,
+):
+    if square:
+        name = "square_ring"
+        outer = geo.square(outer_radius * 2, points_per_side=60)
+        inner = geo.square(inner_radius * 2, points_per_side=20)
+        bbox = geo.square(outer_radius * 2 * 1.4, points_per_side=5)
+    else:
+        name = "circular_ring"
+        outer_points = geo.circle(outer_radius)
+        inner_points = geo.circle(inner_radius)
+        bbox = geo.circle(outer_radius * 1.4, points=21)
+
+    layers = [sc.Layer("base", Lambda=Lambda, z0=0)]
+    films = [sc.Polygon("ring", layer="base", points=outer_points)]
+    holes = [sc.Polygon("hole", layer="base", points=inner_points)]
+    abstract_regions = [
+        sc.Polygon("bounding_box", layer="base", points=bbox),
+    ]
+    return sc.Device(
+        name,
+        layers=layers,
+        films=films,
+        holes=holes,
+        abstract_regions=abstract_regions,
+        length_units=length_units,
+    )
+\end{minted}
+\captionof{listing}{A function that creates a \inline{Device} representing a circular or square ring centered at the origin.}
+\label{code:device}
+\end{code}
+
+Once the layers, films, holes, and abstract regions have been defined, one can generate the computational mesh by calling \inline{Device.make_mesh()}.
+The region that is meshed is defined by the convex hull of the union of all polygons in the device.
+Mesh generation is a two step process.
+First, an initial Delaunay mesh is created using \inline{meshpy}~\cite{Klockner}, a Python interface to Triangle~\cite{shewchuk96b, Shewchuk}, a fast compiled 2D mesh generation tool.
+Second (and optionally), the mesh can be further optimized using \inline{optimesh}~\cite{nico_schlomer_adam_dobrawy_2021}.
+The goal of the mesh optimization step is to improve the quality of each triangular element in the mesh, where quality is defined as twice the ratio of the incircle radius to the circumcircle radius (quality $\leq1$, with equality for equilateral triangles).
+The local density of triangles in the mesh is determined by the density of vertices in the device's polygons and the total number of triangles.
+Regions where there are many polygon vertices will be meshed more densely than regions with few polygon vertices.
+If no \inline{optimesh} optimization is done, then every polygon vertex is guaranteed to be a mesh vertex.
+
+See Code Block~\ref{code:mesh_generation} for a demonstration of \inline{Device.make_mesh()} and Figure~\ref{fig:ring_mesh} to view the resulting meshes both with and without \inline{optimesh} optimization.
+After the mesh has been generated, the matrices and vectors described in Section~\ref{section:implementation} can be computed and one can begin solving models.
+
+\begin{code}
+\begin{minted}[fontsize=\small]{python}
+# min_triangles specifies the minimum number of mesh elements.
+min_triangles = 8000
+# optimesh_steps specifies the the number of iterations of
+# optimesh optimization to perform.
+# Set optimesh_steps=None to disable optimesh optimization.
+optimesh_steps = 400
+# For more meshing options, see the docstring for Device.make_mesh().
+
+for square in (False, True):
+    ring = make_ring(square=square)
+    ring.make_mesh(
+        min_triangles=min_triangles,
+        optimesh_steps=optimesh_steps,
+    )
+    ax = ring.plot_mesh(figsize=(6, 6), color="k", alpha=0.5)
+    ax = ring.plot_polygons(ax=ax)
+\end{minted}
+\captionof{listing}{Generating and visualizing the computational mesh.}
+\label{code:mesh_generation}
+\end{code}
+
+\begin{figure}[!h]
+\centering
+\begin{subfigure}{.235\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_mesh.png}
+  \caption{\inline{optimesh_steps=400}.}
+  \label{fig:circular_ring_mesh}
+\end{subfigure}%
+\begin{subfigure}{.235\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_mesh_no_optimesh.png}
+  \caption{\inline{optimesh_steps=None}.}
+  \label{fig:circular_ring_mesh_no_opt}
+\end{subfigure}%
+\begin{subfigure}{.235\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{examples/images/ring/square_ring_mesh.png}
+  \caption{\inline{optimesh_steps=400}.}
+  \label{fig:square_ring_mesh}
+\end{subfigure}
+\begin{subfigure}{.235\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{examples/images/ring/square_ring_mesh_no_optimesh.png}
+  \caption{\inline{optimesh_steps=None}.}
+  \label{fig:square_ring_mesh_no_opt}
+\end{subfigure}
+\caption{Device geometry and mesh for a circular (a, b) and square ring (c, d) generated using Code Blocks~\ref{code:device} and \ref{code:mesh_generation}, with (a, c) and without (b, d) \inline{optimesh} optimization.}
+\label{fig:ring_mesh}
+\end{figure}
+
+\subsection{Solvers}
+\label{section:overview:solvers}
+
+A \SuperScreen model consists of a \inline{Device}, a function or \inline{Parameter} that defines the applied magnetic field as a function of position $H_{z,\,\mathrm{applied}}(x, y, z)$, and a value for the current circulating around each hole in the device due to trapped flux (if any).
+These items serve as the inputs to \SuperScreen's main solver function, \inline{superscreen.solve()}, which implements the calculation outlined in Section~\ref{section:implementation}.
+When simulating a device with more than one layer, one can specify the number of times to implement the iterative calculation described in Section~\ref{section:model:multilayer} in order to solve for the response of all layers self-consistently.
+One can also skip the iterative portion of the calculation entirely and only solve for the response of each layer to the applied field, assuming no interaction between layers.
+
+\begin{code}
+\begin{minted}[fontsize=\small]{python}
+# Simulate the response to a uniform applied field of 0.25 mT
+applied_field = sc.sources.ConstantField(0.25)
+field_units = "mT"
+
+solutions = sc.solve(
+    device=ring,
+    applied_field=applied_field,
+    field_units=field_units,
+)
+assert len(solutions) == 1 # Since there is only one layer
+uniform_field = solutions[-1]
+
+# Simulate a current circulating around the hole in the ring.
+circulating_currents = {"hole": "1 mA"}
+
+solutions = sc.solve(
+    device=ring,
+    applied_field=None,
+    circulating_currents=circulating_currents
+)
+assert len(solutions) == 1 # Since there is only one layer
+trapped_flux = solutions[-1]
+
+for solution in (uniform_field, trapped_flux):
+    solution.plot_currents(
+        figsize=(6, 7), cross_section_ys=[0], units="mA/um",
+    )
+    solution.plot_fields(figsize=(6, 7), cross_section_ys=[0])
+\end{minted}
+\captionof{listing}{Solves for the current and magnetic field distributions for the \inline{ring} device given a uniform applied field, and circulating current with no applied field.}
+\label{code:ring_circulating_current}
+\end{code}
+
+Code Block~\ref{code:ring_circulating_current} solves two models involving the \inline{ring} device.
+First, Meissner screening of a spatially uniform applied out-of-plane magnetic field and second, the response of the ring to trapped flux with an associated circulating current of 1 mA (with no applied magnetic field).
+The resulting sheet current and magnetic field distributions can be visualized using the \inline{plot_current()} and \inline{plot_fields()} methods, which produce the images shown in Figure~\ref{fig:ring_plot_fields_currents}.
+
+\begin{figure}[!h]
+\centering
+\begin{subfigure}{.235\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_uniform_plot_currents.png}
+  \caption{Uniform applied field.}
+  \label{fig:circular_ring_plot_currents}
+\end{subfigure}
+\begin{subfigure}{.235\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_uniform_plot_fields.png}
+  \caption{Uniform applied field.}
+  \label{fig:circular_ring_plot_fields}
+\end{subfigure}
+\begin{subfigure}{.235\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_circ_plot_currents.png}
+  \caption{Trapped flux.}
+  \label{fig:square_ring_plot_currents}
+\end{subfigure}
+\begin{subfigure}{.235\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_circ_plot_fields.png}
+  \caption{Trapped flux.}
+  \label{fig:square_ring_plot_fields}
+\end{subfigure}
+
+\caption{Sheet current $\vec{J}$ (a, c) and magnetic field $\mu_0H_z$ (b, d) distributions for the circular ring with a uniform field of 0.25 mT applied out-of-plane (a, b) and a circulating current of 1 mA (c, d) calculated using Code Block~\ref{code:ring_circulating_current}.}
+\label{fig:ring_plot_fields_currents}
+\end{figure}
+
+The output of \inline{superscreen.solve()} is a \inline{list} of \inline{superscreen.Solution} objects, with a length of 1 plus the number of iterations used for the iterative portion of the calculation.
+A \inline{Solution} encapsulates all of the information about a solved model: the \inline{Device}, applied field, circulating currents, and calculated stream functions and magnetic fields for all layers in the device.
+A \inline{Solution} also has methods for processing the simulation results, including:
+\begin{itemize}
+    \item{
+    \inline{Solution.grid_data()}: Interpolates the calculated stream functions and magnetic fields for each layer from the triangular mesh to a rectangular grid.
+    }
+    \item{
+    \inline{Solution.current_density()}: Interpolates the stream functions to a rectangular grid and calculates the current density (sheet current) $\vec{J}(x, y)$ in each layer using Eq.~\ref{eq:stream}.
+    }
+    \item{
+    \inline{Solution.polygon_flux()}: Calculates the total flux through each polygon in the device (films, holes, and abstract regions).
+    }
+    \item{
+    \inline{Solution.field_at_position()}: Calculates the vector magnetic field at any point(s) in space due the applied field and the currents flowing the in the device using Eqs.~\ref{eq:field_from_kernel} and \ref{eq:kernels}.
+    }
+\end{itemize}
+\inline{Solutions} also have several visualization methods built in (see Section~\ref{section:overview:visualization}).
+
+One may wish to solve many models involving the same device while varying other aspects of the model, for example sweeping the applied field, circulating currents, or some parameter of one or more layers in the device.
+Fortunately, the mesh and large matrices described in Section~\ref{section:implementation} depend only on the geometry of the device parallel to the $x-y$ plane.
+This means that the same mesh and matrices can be re-used for models with different applied fields, circulating currents, layer heights (vertical positions), and penetration depths.
+
+The \inline{superscreen.solve_many()} function manages the setup and execution of such a sweep.
+One can provide a sequence of \inline{Parameter} objects defining different applied fields and/or a sequence of circulating current values over which to sweep and/or a ``layer updater" function that modifies each layer in the device according to some set of keyword arguments, which can also be swept.
+The latter option can be used to sweep layer heights or penetration depths.
+Given these inputs, \inline{superscreen.solve_many()} will generate and solve all of the corresponding models.
+The models can either be solved in series in a single Python process (the default), or in parallel in multiple Python processes running across multiple CPUs, or even across multiple nodes in a cluster (see~\ref{section:parallel}).
+
+\subsection{Visualization}
+\label{section:overview:visualization}
+
+\SuperScreen offers several functions for visualizing the results of simulations (which are also aliased as methods on \inline{superscreen.Solution}):
+
+\begin{itemize}
+    \item{
+    \inline{superscreen.plot_streams()}: Given a \inline{Solution}, plots the stream function $g(x, y)$ for one or more layers in the device.
+
+    See also: \inline{Solution.plot_streams()}.
+    }
+    \item{
+    \inline{superscreen.plot_currents()}: Given a \inline{Solution}, plots the sheet current $\vec{J}(x, y)$ for one or more layers in the device.
+
+    See also: \inline{Solution.plot_currents()}.
+    }
+    \item{
+    \inline{superscreen.plot_fields()}: Given a \inline{Solution}, plots the total field $H_z(x, y)$ or the screening field $H_z(x, y) - H_{z,\,\mathrm{applied}}(x, y)$ for one or more layers in the device.
+
+    See also: \inline{Solution.plot_fields()}.
+    }
+    \item{
+    \inline{superscreen.plot_field_at_positions()}: Given a \inline{Solution}, plots the total field $\vec{H}(x, y, z_0)$ or $H_z(x, y, z_0)$ at any points in space (where $z_0$ is not equal to the vertical position of any of the layers in the device).
+
+    See also: \inline{Solution.plot_field_at_positions()}.
+    }
+\end{itemize}
+
+See Code Block~\ref{code:ring_circulating_current} and  Figure~\ref{fig:ring_plot_fields_currents} for an example of the usage and output of \inline{plot_fields()} and \inline{plot_currents()}.
+
+\subsection{Comparison \& Persistence}
+\label{section:overview:persistence}
+
+\inline{Parameters}, \inline{Layers}, \inline{Polygons}, \inline{Devices}, and \inline{Solutions} all implement the equality operator, \inline{==}.
+Two \inline{Parameters} are considered equal if the Python bytecode of their underlying functions is the same and their keyword arguments are the same.
+Two \inline{Layers} are equal if their name, penetration depth, thickness, and vertical position are all equal.
+Two \inline{Polygons} are equal if they are in the same layer and their name and polygon vertices are equal.
+Two \inline{Devices} are equal if their name, layers, films, holes, and abstract regions are all equal.
+Two \inline{Solutions} are equal if their device, applied field, circulating currents, timestamp (time at which the solution was created), and all stream function and magnetic field arrays are equal.
+Two \inline{Solutions} created at different times can also be compared using the  \inline{solution.equals()} method.
+
+Instances of \inline{superscreen.Device} and \inline{superscreen.Solution} can be saved to and loaded from disk using their respective \inline{to_file()} and \inline{from_file()} methods, making it straightforward to share models and simulation results.
+\inline{Layers}, \inline{Polygons}, and all metadata are serialized to JSON, a widely-used, human-readable plain text format~\cite{JSON}.
+Functions and \inline{Parameters}, such as those that compute the applied field or penetration depth, are serialized in binary form using \inline{dill}~\cite{McKerns}.
+\inline{Numpy} arrays, such as the mesh itself and the computed stream functions and fields, are saved in the well-established \inline{numpy} \inline{npz} file format.
+A \inline{list} of \inline{Solutions}, such as that returned by \inline{superscreen.solve()} can be saved/loaded all at once using \inline{save_solutions()} and \inline{load_solutions()}.
+
+\section{Example application: Scanning SQUID susceptometry}
+\label{section:application}
+In scanning superconducting quantum interference device (SQUID) susceptometry, the diamagnetic susceptibility of a superconducting sample is measured by bringing the sample close to a pair of superconducting loops.
+The first loop, called the ``pickup loop" is attached to a SQUID circuit that sensitively measures the magnetic flux threading the loop.
+The second loop, called the ``field coil," carries a known current and applies a known magnetic field to both the pickup loop and the sample.
+The superconducting sample screens the magnetic field from the field coil, modifying the amount of flux threading the pickup loop.
+Thus the mutual inductance between the field coil and pickup loop provides a measure of the sample's diamagnetic susceptibility, which is in turn a measure of the sample's penetration depth.
+
+Analysis developed to interpret the results of scanning SQUID susceptometry measurements makes several simplifying assumptions that are not always satisfied: 1) the sample's effective penetration depth $\Lambda$ (or Pearl length $2\Lambda$) is spatially homogeneous, 2) the sample is much larger than the field coil, and 3) the field coil and pickup loop can be approximated as one-dimensional coaxial, coplanar circular loops~\cite{Kirtley_Kalisky_2012}.
+
+Figure X shows a \inline{Device} representing field coil and pickup loop of an actual scanning SQUID sensor.
+In addition to the field coil and pickup loop, there are superconducting shields that limit the amount of magnetic flux that can penetrate the leads connecting the loops to the rest of the circuit.
+There are three relevant layers of superconducting films: the base electrode (``BE"), which is furthest from the sample contains the field coil; the first wiring layer (``W1"), which contains the pickup loop and a shield covering the field coil leads; and the second wiring layer (``W2"), which is closest to the sample and contains a shield covering the pickup loop leads.
+The device also contains a layer and film representing the superconducting sample.
+
+To model a SQUID susceptometry measurement, we first calculate $M_0$, the mutual inductance between the field coil and pickup loop in the absence of the sample.
+This can be done by temporarily setting the sample layer effective penetration depth to a very large value such that it essentially does not screen the field from the field coil.
+We then model the field from a known current flowing in the field coil following Section~\ref{section:model:holes} and self-consistently calculate the response of both the sample and the other superconducting layers of the SQUID sensor following Section~\ref{section:model:multilayer}.
+To ensure that the 2D current distribution in the field coil is approximately uniform (as we would expect for a real applied current), we set the field coil layer effective penetration depth to be greater than the width of the field coil conductor.
+
+Once $M_0$ is known, we can ``turn on" the sample's diamagnetic response by setting its effective penetration depth $\Lambda$ to the desired value and compute $M(z, \Lambda)$ for a given vertical distance $z$ between the sample and the SQUID as described in the previous paragraph.
+The SQUID susceptibility signal is then $M(z, \Lambda) - M_0$, the change in mutual inductance between the field coil and pickup loop due to the presence of the sample (usually given in units of $\Phi_0/\mathrm{A}$, where $\Phi_0$ is the superconducting flux quantum).
+The susceptibility can also be normalized to the bare mutual inductance $M_0$, giving a dimensionless susceptibility $\chi(z, \Lambda)=[M(z, \Lambda) - M_0] / M_0$.
+
+\section{Conclusion}
+\label{section:conlusion}
+
+The ability to model and visualize screening effects in inhomogeneous 2D superconductors and devices constructed from superconducting thin films can help to build intuition about these systems, aid in interpretation of measurement results, and enable optimization of measurement and device design.
+\SuperScreen is an open-source, user-friendly, portable, and efficient tool that solves this problem.
+Applications of the package include calculating self- and mutual-inductance in mesoscopic superconducting circuits, and modeling the magnetic interaction between inhomogeneous superconducting samples and superconducting sensors such as scanning SQUID susceptometers~\cite{kirtley_scanning_2016}.
+
+There are two important limitations to the applicability of \SuperScreen and the matrix inversion method on which it is based~\cite{brandt_thin_2005}.
+First, strictly speaking all superconducting films should be in the 2D limit, with London penetration depth $\lambda$ less than film thickness $d$, such that the out-of-plane current density is approximately constant.
+There are cases where the model reproduces experimental results despite violation of this condition (e.g.
+the calculations in Section~\ref{section:application} and in~\cite{kirtley_scanning_2016,kirtley_response_2016}), but great care must be taking in interpreting results in these cases.
+Second, as a London model, Brandt's method assumes that all superconducting films behave linearly and without dissipation.
+Care should also be taken to ensure that for a given model the mesh is of sufficient density and quality that, to within the desired precision, the results of simulations do not depend on mesh size.
+
+Potential improvements to \SuperScreen include: more sophisticated mesh generation (e.g.
+automated local mesh refinement based on device geometry), automated determination of solution convergence for models with multiple layers, an improved interface for generating complex device geometries, and further optimization for memory and CPU efficiency (especially in the context of parallel processing).
+
+%% The Appendices part is started with the command \appendix;
+%% appendix sections are then done as normal sections
+%% \appendix
+
+%% \section{}
+%% \label{}
+
+\appendix
+
+\section{Laplace operator}
 \label{section:implementation:laplace}
 
-The definition of the mesh Laplace operator $\mathbf{\nabla}^2$ (also called the Laplace-Beltrami operator [Laplacian-SGP-2014]) deserves special attention, as it reduces the problem of solving a partial differential equation $\nabla^2g(x,y)=f(x,y)$ to the problem of solving a matrix equation
-$\mathbf{\nabla}^2\mathbf{g}=\mathbf{f}$.
+The definition of the discrete Laplace operator $\mathbf{\nabla}^2$ (also called the Laplace-Beltrami operator) deserves special attention, as it reduces the problem of solving a partial differential equation $\nabla^2g(x,y)=f(x,y)$ to the problem of solving a matrix equation
+$\mathbf{\nabla}^2\mathbf{g}=\mathbf{f}$~\cite{Reuter_Biasotti_Giorgi_Patane_Spagnuolo_2009}.
 As described in [Vaillant-Laplacian-2013] and [Laplacian-SGP-2014] the Laplace operator $\mathbf{\nabla}^2$ for a mesh is defined in terms of two matrices, the mass matrix $\mathbf{M}$ and the
-Laplacian matrix $\mathbf{L}$: $\mathbf{\nabla}^2 = \mathbf{M}^{-1}\mathbf{L}$.
+weak Laplacian matrix $\mathbf{L}$: $\mathbf{\nabla}^2 = \mathbf{M}^{-1}\mathbf{L}$.
 
-In a 2D mesh, the mass matrix gives an effective area to each vertex in the mesh.
-There are multiple ways to construct the mass matrix, but here we use a ``lumped" mass matrix, which is diagonal with elements $(\mathbf{M})_{ii} = \frac{1}{3}\sum_{t\in\mathcal{N}(i)}\mathrm{area}(t)$,
+In a 2D mesh, the mass matrix $\mathbf{M}$ gives an effective area to each vertex in the mesh.
+Here we use a ``lumped" mass matrix, which is diagonal with elements $M_{ii} = \frac{1}{3}\sum_{t\in\mathcal{N}(i)}\mathrm{area}(t)$,
 where $\mathcal{N}(i)$ is the set of triangles $t$ adjacent to vertex $i$.
-
-Each element $w_{ij}$ of the symmetric weight matrix $\mathbf{w}$ assigns a weight to the edge connecting vertex $i$ and vertex $j$ in the mesh.
-We use a normalized version of the weight matrix, where the sum of all off-diagonal elements in each row (or column) is 1, and each diagonal element is 1.
-Thus we can write $\mathbf{w}$ in terms of an un-normalized weight matrix $\mathbf{W}$:
-$$
-    w_{ij} = \begin{cases}
-        1&\text{if }i = j\\
-        W_{ij} / \sum_{i\neq j} W_{ij}&\text{otherwise}
-    \end{cases}
-$$
-
-There are several different methods for constructing the un-normalized weight matrix $\mathbf{W}$:
+The weak Laplacian matrix $\mathbf{L}$ is defined in terms of a symmetric weight matrix $\mathbf{W}$, which assigns a weight to every edge in the mesh.
+$\mathbf{W}$ may be defined in a number of ways:
 
@@
 By default, \SuperScreen uses half-cotangent weighting.
-The Laplacian matrix $\mathbf{L}$ is defined in terms of the weight matrix $\mathbf{w}$: $(\mathbf{L})_{ij} = (\mathbf{w})_{ij} - \delta_{ij}\sum_{\ell}w_{i\ell}$.
+The Laplacian matrix $\mathbf{L}$ is defined in terms of the weight matrix $\mathbf{W}$: $L_{ij} = W_{ij} - \delta_{ij}\sum_{\ell}W_{i\ell}$.
 Finally, the Laplace operator is given by $\mathbf{\nabla}^2 = \mathbf{M}^{-1}\mathbf{L}$.
 
-\section{Package Overview}
-\label{section:overview}
+The matrix $\mathbf{w}$ in Eqs.~\ref{eq:field_from_kernel_num} and \ref{eq:Heff_sub_num} that is used, together with the kernel matrix $\mathbf{Q}$, to approximate the dipole kernel $Q_z(\vec{r},\vec{r}')$ (Eq.~\ref{eq:kernels}) is simply a normalized version of the weight matrix $\mathbf{W}$ used in defining the Laplace operator.
+The relationship between $\mathbf{w}$ and $\mathbf{W}$ is given by:
+$$
+    w_{ij} = \begin{cases}
+        1&\text{if }i = j\\
+        W_{ij} / \sum_{i\neq j} W_{ij}&\text{otherwise.}
+    \end{cases}
+$$
 
-In this section we give a high-level overview of the \SuperScreen package. More detailed documentation and tutorials can be found at superscreen.readthedocs.io.
+\section{Parallel processing}
+\label{section:parallel}
+As discussed above, one can solve many models involving the same \inline{Device} in parallel across multiple CPUs using the \inline{superscreen.solve_many()} function.
+The recommended method for parallel processing is using \inline{ray}, a library for distributed computing using shared memory~\cite{ray_2018}.
+Note that at the time of writing, \inline{ray} support for Windows is experimental and under active development.
+\SuperScreen also supports parallel processing using the \inline{multiprocessing} module from the Python standard library, however this is generally less efficient than \inline{ray} in this application.
 
-\subsection{Parameters}
-\label{section:overview:parameter}
+There are three ways to invoke \inline{ray} from \SuperScreen when running on a single machine, e.g.
+a multi-core CPU.
+The first is to simply pass the keyword argument \inline{parallel_method="ray"} when calling \inline{solve_many()}.
+This will automatically create a \inline{ray} cluster using all available physical CPU cores, solve the models in parallel, and then shut down the cluster before returning.
+The second method is to manually create a \inline{ray} cluster using the \inline{ray} Python application programming interface (API) prior to calling \inline{solve_many(..., parallel_method="ray")}, as demonstrated in Code Block~\ref{code:ray-python}.
+The third method is to start a \inline{ray} cluster using the command line interface (CLI), then connect to the existing cluster using the Python API prior to calling \inline{solve_many(..., parallel_method="ray")}, as demonstrated in Code Block~\ref{code:ray-cli}.
+One of the latter two methods should be used for finer control over the \inline{ray} cluster (number of CPUs to utilize, etc.).
 
-A \mintinline{python}{superscreen.Parameter} is a wrapper around a Python function that computes a scalar value as a function of position coordinates ($x$, $y$, and optionally $z$) based on some keyword arguments.
-Addition, subtraction, multiplication, division, and exponentiation between \mintinline{python}{Parameters}, other \mintinline{python}{Parameters}, and Python scalars (\mintinline{python}{int} and \mintinline{python}{float}) are supported.
-For example:
+\begin{code}
+\begin{minted}[fontsize=\small]{python}
+# Assume that we have already created a Device and put all
+# other inputs to superscreen.solve_many() into a dictionary
+# called other_kwargs.
 
-\begin{minted}{python}
-from superscreen import Parameter
+import psutil
+import ray
 
-def f(x, y, a=1, b=0):
-    return a * x**2 + b * y
+# Specify the number of CPUs/cores to allocate.
+num_cpus = 3
+# Use at most N processes for a machine with N physical CPUs.
+num_cpus = min(num_cpus, psutil.cpu_count(logical=False))
 
-param = Parameter(f, a=0, b=1)
-print(param)  # Parameter<f(a=0, b=1)>
+# Start a ray cluster
+ray.init(num_cpus=num_cpus)
+# Solve the models
+solutions, paths = superscreen.solve_many(
+    parallel_method="ray",
+    **other_kwargs,
+)
+# Shutdown the ray cluster
+ray.shutdown()
+\end{minted}
+\captionof{listing}{Starting and stopping \inline{ray} outside of \inline{superscreen.solve_many()} using the Python API.
+See the ``API and Package Reference" section of the \inline{ray} documentation for additional options in \inline{ray.init()}~\cite{ray-docs}.}
+\label{code:ray-python}
+\end{code}
 
-other_param = Parameter(f, a=2, b=3)
-print(other_param)  # Parameter<f(a=2, b=3)>
-
-print(param(0, 0) == f(0, 0, a=0, b=1))  # True
-print(other_param(1, 2) == f(1, 2, a=2, b=3))  # True
-
-param_squared = param ** 2
-print(param_squared)  # CompositeParameter<(f(a=0, b=1) ** 2)>
-
-print(param_squared(3, 4) == f(3, 4, a=0, b=1) ** 2) # True
-print(
-    (5 * param_squared / other_param)(5, 6)
-    == 5 * f(5, 6, a=0, b=1) ** 2 / f(5, 6, a=2, b=3)
-)  # True
+\begin{minipage}{\textwidth}
+\begin{code}
+\begin{minted}[fontsize=\small]{bash}
+# Start a ray cluster from the command line, e.g. bash
+ray start --head --num=cpus=3
 \end{minted}
 
-\mintinline{python}{Parameters} can be used to define applied magnetic fields and penetration depths that depend on position.
+\begin{minted}[fontsize=\small]{python}
+# Assume that we have already created a Device and put all
+# other inputs to superscreen.solve_many() into a dictionary
+# called other_kwargs.
+import ray
+# Connect to the existing ray cluster.
+# If more than one ray cluster is running, specify
+# which to connect to using address="{ip}:{port}".
+ray.init(address="auto")
+# Solve the models.
+solutions, paths = superscreen.solve_many(
+    parallel_method="ray",
+    **other_kwargs,
+)
+\end{minted}
 
-\subsection{Devices}
-\label{section:overview:device}
+\begin{minted}[fontsize=\small]{bash}
+# Shut down the ray cluster from the command line
+ray stop
+\end{minted}
+\captionof{listing}{Starting and stopping \inline{ray} outside of \inline{superscreen.solve_many()} using the command line interface.
+See the \inline{ray} documentation for additional options in \inline{ray start}~\cite{ray-docs}.}
+\label{code:ray-cli}
+\end{code}
+\end{minipage}
 
-Information about the geometry and penetration depth of a superconducting structure is described by an instance of the \mintinline{python}{superscreen.Device} class.
-A \mintinline{python}{Device} is made up of one or more superconducting layers, each an instance of  \mintinline{python}{superscreen.Layer}.
-Each layer sits in a specified plane parallel to the $x-y$ plane and has its own effective penetration depth $\Lambda$, which can either be a constant or a \mintinline{python}{superscreen.Parameter} wrapping a function that computes $\Lambda(x, y)$, the penetration depth as a function of position.
-The effective penetration depth $\Lambda$ can instead be defined in terms of a layer's London penetration depth $\lambda$ and its thickness $d$: $\Lambda=\lambda^2/d$, in which case the London penetration depth can be either a constant or a \mintinline{python}{superscreen.Parameter}.
+Running \inline{superscreen.solve_many()} in parallel across multiple nodes in a computing cluster is a simple extension to the method outlined in Code Block~\ref{code:ray-cli}, although the specifics depend upon the infrastructure of the cluster, e.g.
+job management software.
+See the ``Multi-Node Ray" section of the \inline{ray} documentation for more details~\cite{ray-docs}.
 
-Each layer can contain one or more superconducting films which may have one or more holes in them.
-Films and holes are represented by instances of the \mintinline{python}{superscreen.Polygon} class.
-A \mintinline{python}{Polygon} contains the name of the layer to which is belongs, an array specifying the coordinates of its vertices, and a method, \mintinline{python}{Polygon.contains_points()}, which determines whether specified coordinates lie within the polygon or not.
-In addition to superconducting films and holes, one may define ``abstract regions,'' which are polygons that need not correspond to a physical feature in the structure, but will still be meshed.
-Abstract regions can be used to define a ``bounding box" around a structure.
+Maybe demonstrate scaling on Sherlock here.
 
-Once the layers, films, holes, and abstract regions have been defined, one can generate the computational mesh by calling \mintinline{python}{Device.make_mesh()}.
-The region that is meshed is defined by the convex hull of the union of all polygons in the device.
-After the mesh is generated, the matrices and vectors described in Section~\ref{section:implementation} can be computed and one can begin solving models.
+%% References
+%%
+%% Following citation commands can be used in the body text:
+%% Usage of \cite is as follows:
+%%   \cite{key}         ==>>  [#]
+%%   \cite[chap. 2]{key} ==>> [#, chap. 2]
+%%
 
-\subsection{Solvers}
-\label{section:overview:solvers}
+%% References with bibTeX database:
 
-A \SuperScreen model consists of a \mintinline{python}{Device}, a function or \mintinline{python}{Parameter} that computes the applied magnetic field as a function of position $H_{z,\,\mathrm{applied}}(x, y, z)$, and (optionally) a value for the current circulating around each hole in the device due to trapped flux.
-These items serve as the inputs to \SuperScreen's main solver function, \mintinline{python}{superscreen.solve()}, which implements the calculation outlined in Section~\ref{section:implementation}.
-When simulating a device with more than one layer, one can specify the number of times to implement the iterative calculation described in Section~\ref{section:model:multilayer} in order to solve for the response of all layers self-consistently.
-One can also skip the iterative portion of the calculation entirely and only solve for the response of each layer to the applied field, assuming interaction between layers.
-
-The output of \mintinline{python}{superscreen.solve()} is a \mintinline{python}{list} of \mintinline{python}{superscreen.Solution} objects, with a length of 1 plus the number of iterations used for the iterative portion of the calculation.
-A \mintinline{python}{Solution} encapsulates all of the information about a solved model: the \mintinline{python}{Device}, applied field, circulating currents, and calculated stream functions and screening fields for all layers in the device.
-A \mintinline{python}{Solution} also has methods for processing the simulation results, including:
-\begin{itemize}
-    \item{
-    \mintinline{python}{Solution.grid_data()}: Interpolates the calculated stream functions and magnetic fields for each layer from the triangular mesh to a rectangular grid.
-    }
-    \item{
-    \mintinline{python}{Solution.current_density()}: Interpolates the stream functions to a rectangular grid and calculates the current density (sheet current) $\vec{J}(x, y)$ in each layer using Eq.~\ref{eq:stream}.
-    }
-    \item{
-    \mintinline{python}{Solution.polygon_flux()}: Calculates the total flux through each polygon in the device (films, holes, and abstract regions).
-    }
-    \item{
-    \mintinline{python}{Solution.field_at_position()}: Calculates the vector magnetic field at any point(s) in space due the applied field and the currents flowing the in the device using Eqs.~\ref{eq:field_from_kernel} and \ref{eq:kernels}.
-    }
-\end{itemize}
-
-One may wish to solve many models involving the same device while varying other aspects of the model, for example sweeping the applied field, circulating currents, or some parameter of one or more layers in the device.
-Fortunately, the mesh and large matrices described in Section~\ref{section:implementation} depend only on the geometry of the device parallel to the $x-y$ plane.
-This means that the same mesh and matrices can be re-used for models with different applied fields, circulating currents, layer heights, and layer penetration depths.
-
-The \mintinline{python}{superscreen.solve_many()} function is designed to do just that.
-One can provide a sequence of \mintinline{python}{superscreen.Parameter} objects defining different applied fields and/or a sequence of circulating current values over which to sweep.
-One can also provide a ``layer updater" function that modifies each layer in the device according to some set of keyword arguments, which can also be swept.
-The latter option can be used to sweep layer heights or penetration depths.
-Given these inputs, \mintinline{python}{superscreen.solve_many()} will generate and solve all of the corresponding models.
-The models can either be solved in series in a single Python process (the default), or in parallel across multiple Python processes running on different CPUs.
-In either case, only a single copy of the device's mesh and large arrays is created, so the memory footprint is modest.
-
-\subsection{Visualization}
-\label{section:overview:visualization}
-
-\SuperScreen offers several functions for visualizing the results of simulations (which are also aliased as method on \mintinline{python}{superscreen.Solution}):
-
-\begin{itemize}
-    \item{
-    \mintinline{python}{superscreen.plot_streams()}: Given a \mintinline{python}{Solution}, plots the stream function $g(x, y)$ for one or more layers in the device.
-See also \mintinline{python}{Solution.plot_streams()}.
-    }
-    \item{
-    \mintinline{python}{superscreen.plot_currents()}: Given a \mintinline{python}{Solution}, plots the sheet current $\vec{J}(x, y)$ for one or more layers in the device.
-See also \mintinline{python}{Solution.plot_currents()}.
-    }
-    \item{
-    \mintinline{python}{superscreen.plot_fields()}: Given a \mintinline{python}{Solution}, plots the total field $H_z(x, y)$ or the screening field $H_z(x, y) - H_{z,\,\mathrm{applied}}(x, y)$ for one or more layers in the device.
-See also \mintinline{python}{Solution.plot_fields()}.
-    }
-    \item{
-    \mintinline{python}{superscreen.plot_field_at_positions()}: Given a \mintinline{python}{Solution}, plots the total field $\vec{H}(x, y, z_0)$ or $H_z(x, y, z_0)$ at any points in space (where $z_0$ is not equal to the vertical position of any of the layers in the device).
-See also \mintinline{python}{Solution.plot_field_at_positions()}.
-    }
-\end{itemize}
-
-See Section~\ref{section:examples} for examples of the figures generated by these functions.
-
-\subsection{Comparison \& Persistence}
-\label{section:overview:persistence}
-
-\mintinline{python}{Parameters}, \mintinline{python}{Layers}, \mintinline{python}{Polygons}, \mintinline{python}{Devices}, and \mintinline{python}{Solutions} all implement the equality operator, \mintinline{python}{==}.
-Two \mintinline{python}{Parameters} are considered equal if the Python bytecode of their underlying functions is the same and their keyword arguments are the same.
-Two \mintinline{python}{Layers} are equal if their name, penetration depth, thickness, and vertical position are all equal.
-Two \mintinline{python}{Polygons} are equal if they are in the same layer and their name and polygon vertices are equal.
-Two \mintinline{python}{Devices} are equal if their name, layers, films, holes, and abstract regions are all equal.
-Two \mintinline{python}{Solutions} are equal if their device, applied field, circulating currents, timestamp (time at which the solution was created), and all stream function and magnetic field arrays are equal.
-Two solutions created at different times can also be compared by calling \mintinline{python}{solution.equal(other_solution, require_same_timestamp=False)}.
-
-Instances of \mintinline{python}{superscreen.Device} and \mintinline{python}{superscreen.Solution} can be saved to and loaded from disk using their respective \mintinline{python}{to_file()} and \mintinline{python}{from_file()} methods, making it straightforward to share models and simulation results.
-\mintinline{python}{Layers}, \mintinline{python}{Polygons}, and all metadata are serialized to JSON, a widely-used, human-readable plain text format.
-Functions and \mintinline{python}{Parameters}, such as those that compute the applied field or penetration depth, are serialized in binary form using \mintinline{python}{dill}.
-\mintinline{python}{numpy} arrays, such as the mesh itself and the computed stream functions and fields, are saved in the well-established \mintinline{python}{numpy} \mintinline{python}{npz} file format.
-A \mintinline{python}{list} of \mintinline{python}{Solutions}, such as that returned by \mintinline{python}{superscreen.solve()} can be saved/loaded all at once using \mintinline{python}{superscreen.save_solutions()}/\mintinline{python}{superscreen.load_solutions()}.
-
-\subsection{Development Details}
-\label{section:overview:development}
-
-\SuperScreen requires Python version 3.6 or later.
-The package is located in a public repository on GitHub, and a suite of unit tests is run automatically via GitHub Actions whenever a change or proposed change (Pull Request) is made to the \mintinline{python}{main} branch of the repository.
-At the time of writing, the test suite is executed using Python versions 3.6, 3.7, 3.8, and 3.9, and the test coverage is XX\%.
-Any changes to the \mintinline{python}{main} branch of the repository also trigger an automatic re-build of the online documentation, hosted by Read the Docs at superscreen.readthedocs.io.
-Stable versions of the package are tagged on GitHub and uploaded to PyPI, the Python Package Index.
-The source code and documentation are covered by the MIT License.
-
-\SuperScreen has several important dependencies beyond the Python standard library: \mintinline{python}{numpy} and \mintinline{python}{scipy} for numerics, \mintinline{python}{pint} for handling physical units, \mintinline{python}{matplotlib} for visualization, \mintinline{python}{meshpy} and \mintinline{python}{optimesh} for mesh generation, \mintinline{python}{dill} for serializing objects to disk and between processes, and \mintinline{python}{ray} for parallel processing with shared memory.
-
-\section{Examples}
-\label{section:examples}
-
-\subsection{Screening}
-\label{section:example:screening}
-
-\subsection{Inductance}
-\label{section:examples:inductance}
-
-\subsection{Mutual Inductance}
-\label{section:examples:mutual-inductance}
-
-\subsection{SQUID Susceptometry}
-\label{section:examples:susceptometry}
-
-\subsection{Parallel Processing}
-\label{section:examples:parallel}
-
-\section{Conclusion}
-\label{section:conlusion}
-
-\bibliographystyle{plain}
+\bibliographystyle{elsarticle-num}
 \bibliography{references}
 
+%% Authors are advised to submit their bibtex database files. They are
+%% requested to list a bibtex style file in the manuscript if they do
+%% not want to use elsarticle-num.bst.
+
+%% References without bibTeX database:
+
+% \begin{thebibliography}{00}
+
+%% \bibitem must have the following form:
+%%   \bibitem{key}...
+%%
+
+% \bibitem{}
+
+% \end{thebibliography}
+
 \end{document}
+
+%%
+%% End of file

### 2021-08-12 main.tex

@@
 
+\begin{figure}[!h]
+\centering
+\begin{subfigure}{.35\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{examples/images/squid_susceptometry/squid_with_sample_mesh.png}
+%   \caption{Device polygons and mesh for the SQUID susceptometer model.}
+  \label{fig:squid_mesh}
+\end{subfigure}%
+\hspace{10pt}
+\begin{subfigure}{.5\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{examples/images/squid_susceptometry/squid_with_sample_M0_convergence.png}
+%   \caption{Fractional change in flux though all polygons vs.
+solver iteration with a current of $1\,\mathrm{mA}$ flowing in the field coil (\inline{fc}).
+The mutual inductance $M_0$ is given by the flux through the pickup loop (\inline{pl_hull}) divided by the field coil current.}
+  \label{fig:squid_convergence}
+\end{subfigure}%
+\caption{Left: Device polygons and mesh for the SQUID susceptometer model.
+Right: Fractional change in flux though all polygons vs.
+solver iteration with a current of $1\,\mathrm{mA}$ flowing in the field coil (\inline{fc}).
+The mutual inductance $M_0$ is given by the flux through the pickup loop (\inline{pl_hull}) divided by the field coil current.}
+\label{fig:susceptometry}
+\end{figure}
+
 Figure X shows a \inline{Device} representing field coil and pickup loop of an actual scanning SQUID sensor.
-In addition to the field coil and pickup loop, there are superconducting shields that limit the amount of magnetic flux that can penetrate the leads connecting the loops to the rest of the circuit.
+In addition to the field coil and pickup loop, there are superconducting shields that limit the amount of magnetic flux that can penetrate the leads connecting the loops to the rest of the circuit (the rest of the circuit is not modeled).
 There are three relevant layers of superconducting films: the base electrode (``BE"), which is furthest from the sample contains the field coil; the first wiring layer (``W1"), which contains the pickup loop and a shield covering the field coil leads; and the second wiring layer (``W2"), which is closest to the sample and contains a shield covering the pickup loop leads.
@@
 To model a SQUID susceptometry measurement, we first calculate $M_0$, the mutual inductance between the field coil and pickup loop in the absence of the sample.
-This can be done by temporarily setting the sample layer effective penetration depth to a very large value such that it essentially does not screen the field from the field coil.
+This can be done by temporarily setting the sample layer effective penetration depth to a very large value such that it essentially does not screen the field from the field coil (in this case, we set $\Lambda = 10^5\,\mu\mathrm{m}$).
 We then model the field from a known current flowing in the field coil following Section~\ref{section:model:holes} and self-consistently calculate the response of both the sample and the other superconducting layers of the SQUID sensor following Section~\ref{section:model:multilayer}.
@@
 The susceptibility can also be normalized to the bare mutual inductance $M_0$, giving a dimensionless susceptibility $\chi(z, \Lambda)=[M(z, \Lambda) - M_0] / M_0$.
+
+\begin{figure}[!h]
+\centering
+\begin{subfigure}{\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{examples/images/squid_susceptometry/squid_with_sample_currents_Lambda=1_00__um__z_0=-1_00__um.png}
+%   \caption{Device polygons and mesh for the SQUID susceptometer model.}
+  \label{fig:squid_mesh}
+\end{subfigure}%
+
+\begin{subfigure}{\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{examples/images/squid_susceptometry/squid_with_sample_currents_Lambda=1_00__um__z_0=-10_00__um.png}
+%   \caption{Fractional change in flux though all polygons vs.
+solver iteration with a current of $1\,\mathrm{mA}$ flowing in the field coil (\inline{fc}).
+The mutual inductance $M_0$ is given by the flux through the pickup loop (\inline{pl_hull}) divided by the field coil current.}
+  \label{fig:squid_convergence}
+\end{subfigure}%
+
+\begin{subfigure}{\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{examples/images/squid_susceptometry/squid_with_sample_currents_Lambda=10_00__um__z_0=-1_00__um.png}
+%   \caption{Fractional change in flux though all polygons vs.
+solver iteration with a current of $1\,\mathrm{mA}$ flowing in the field coil (\inline{fc}).
+The mutual inductance $M_0$ is given by the flux through the pickup loop (\inline{pl_hull}) divided by the field coil current.}
+  \label{fig:squid_convergence}
+\end{subfigure}%
+\caption{Left: Device polygons and mesh for the SQUID susceptometer model.
+Right: Fractional change in flux though all polygons vs.
+solver iteration with a current of $1\,\mathrm{mA}$ flowing in the field coil (\inline{fc}).
+The mutual inductance $M_0$ is given by the flux through the pickup loop (\inline{pl_hull}) divided by the field coil current.}
+\label{fig:susceptometry}
+\end{figure}
 

### 2021-08-13 examples/scripts/small_squid/mutual_inductance.py
add small squid scripts

@@ -1,0 +1,139 @@
+import os
+
+import numpy as np
+import pandas as pd
+import matplotlib.pyplot as plt
+
+import superscreen as sc
+
+from squid import make_squid
+
+plt.rcParams["font.size"] = 14
+plt.rcParams["savefig.dpi"] = 150
+
+
+if __name__ == "__main__":
+
+    import argparse
+    import logging
+
+    parser = argparse.ArgumentParser()
+    parser.add_argument(
+        "--min_triangles",
+        type=int,
+        default=8000,
+        help="Minimum number of trianges in the mesh.",
+    )
+    parser.add_argument(
+        "--optimesh_steps",
+        type=int,
+        default=400,
+        help="Number of optimesh steps to perform when making the mesh."
+    )
+    parser.add_argument(
+        "--iterations",
+        type=int,
+        default=9,
+        help="Number of solver iterations to perform."
+    )
+    args = parser.parse_args()
+
+    logging.basicConfig(level=logging.INFO)
+
+    imagedir = os.path.join(os.pardir, "images", "small_squid")
+    os.makedirs(imagedir, exist_ok=True)
+
+    device = make_squid()
+    device.layers["BE"].london_lambda = 1
+    device.make_mesh(min_triangles=args.min_triangles, optimesh_steps=args.optimesh_steps)
+    print(device)
+
+    # Plot the device's mesh and polygons
+    ax = device.plot_mesh(figsize=(6, 6), color="k", alpha=0.4)
+    ax = device.plot_polygons(ax=ax, linewidth=4)
+    npoints = device.points.shape[0]
+    ntriangles = device.triangles.shape[0]
+    ax.set_title(f"{device.name} mesh:\n{npoints} points, {ntriangles} triangles")
+    ax.figure.savefig(
+        os.path.join(imagedir, f"{device.name}_mutual_mesh.png"),
+        bbox_inches="tight",
+    )
+
+    applied_field = sc.sources.ConstantField(0)
+    circulating_currents = {"fc_center": "1 mA"}
+    I_fc = device.ureg(circulating_currents["fc_center"]).to("A")
+
+    solutions = sc.solve(
+        device=device,
+        applied_field=applied_field,
+        circulating_currents=circulating_currents,
[…]

### 2021-08-13 examples/scripts/small_squid/point_spread_function.py

@@ -1,0 +1,156 @@
+import os
+import itertools
+import tempfile
+
+import numpy as np
+import pandas as pd
+import matplotlib.pyplot as plt
+
+import superscreen as sc
+
+from squid import make_squid, split_layer
+
+plt.rcParams["font.size"] = 14
+plt.rcParams["savefig.dpi"] = 150
+
+
+def vortex_field(x, y, z, x0=0, y0=0, z0=0, nPhi0=1):
+    """Field from an isolated vortex.
+
+    Args:
+        x, y, z: Position coordinates.
+        x0, y0, z0: Vortex position
+        nPhi0: Number of flux quanta contained in the vortex.
+    """
+    xp = x - x0
+    yp = y - y0
+    zp = z - z0
+    Hz0 = zp / (xp ** 2 + yp ** 2 + zp ** 2) ** (3 / 2) / (2 * np.pi)
+    return nPhi0 * Hz0
+
+
+def VortexField(x0=0, y0=0, z0=0, nPhi0=1):
+    return sc.Parameter(vortex_field, x0=x0, y0=y0, z0=z0, nPhi0=nPhi0)
+
+
+if __name__ == "__main__":
+
+    import argparse
+    import logging
+
+    parser = argparse.ArgumentParser()
+    parser.add_argument(
+        "--vortex_height",
+        type=float,
+        default=-2.0,
+        help="Height of the vortex relative to the SQUID."
+    )
+    parser.add_argument(
+        "--min_triangles",
+        type=int,
+        default=8000,
+        help="Minimum number of trianges in the mesh.",
+    )
+    parser.add_argument(
+        "--optimesh_steps",
+        type=int,
+        default=400,
+        help="Number of optimesh steps to perform when making the mesh."
+    )
+    parser.add_argument(
+        "--iterations",
+        type=int,
+        default=5,
+        help="Number of solver iterations to perform."
+    )
+    parser.add_argument(
+        "--max_thickness",
+        type=float,
+        default=None,
+        help="Maximum thickness of Layers making up the pickup loop shield."
+    )
+    parser.add_argument(
+        "--pixel_size",
+        type=float,
+        default=0.25,
+        help="Linear pixel size in microns."
+    )
+    parser.add_argument(
+        "--use_ray",
+        type=bool,
+        default=True,
+    )
+    args = parser.parse_args()
+
+    logging.basicConfig(level=logging.INFO)
+
+    imagedir = os.path.join(os.pardir, "images", "small_squid")
[…]

### 2021-08-13 examples/scripts/small_squid/squid.py

@@ -1,0 +1,366 @@
+import os
+
+import numpy as np
+from scipy.io import loadmat
+
+from superscreen import Device, Layer, Polygon
+from superscreen.geometry import rotate
+
+
+def split_layer(device, layer_name, max_thickness=0.05):
+    """Splits a given layer into multiple thinner layers."""
+    layers = device.layers
+    films = device.films
+    holes = device.holes
+    abstract_regions = device.abstract_regions
+    
+    layer_to_split = layers.pop(layer_name)
+    london_lambda = layer_to_split.london_lambda
+    z0 = layer_to_split.z0
+    d = layer_to_split.thickness
+    
+    num_layers, mod = divmod(d, max_thickness)
+    num_layers = int(num_layers)
+    new_ds = [max_thickness for _ in range(num_layers)]
+    if mod:
+        num_layers += 1
+        new_ds.append(mod)
+    new_layers = {}
+    for i, new_d in enumerate(new_ds):
+        name = f"{layer_name}_{i}"
+        z = i * max_thickness + new_d / 2
+        new_layers[name] = Layer(
+            name, london_lambda=london_lambda, thickness=new_d, z0=z
+        )
+
+    new_films = {}
+    for name, film in films.items():
+        if film.layer == layer_name:
+            for i, new_layer_name in enumerate(new_layers):
+                film_name = f"{name}_{i}"
+                new_film = film.copy()
+                new_film.name = film_name
+                new_film.layer = new_layer_name
+                new_films[film_name] = new_film
+        else:
+            new_films[name] = film
+            
+    new_holes = {}
+    for name, hole in holes.items():
+        if hole.layer == layer_name:
+            for i, new_layer_name in enumerate(new_layers):
+                hole_name = f"{name}_{i}"
+                new_hole = hole.copy()
+                new_hole.name = hole_name
+                new_hole.layer = new_layer_name
+                new_holes[film_name] = new_hole
+        else:
+            new_holes[name] = hole
+            
+    new_abstract_regions = {}
+    for name, region in abstract_regions.items():
[…]

### 2021-08-13 examples/scripts/squid_susceptometry/huber_squid.py

@@ -165,7 +165,7 @@ def huber_geometry(interp_points=101):
 
 def huber_squid():
 
-    interp_points = 151
+    interp_points = 101
 
     # See Nick Koshnick thesis
     # bottom of page 29 and table 3.2 on page 32).
@@ -200,8 +200,8 @@ def huber_squid():
         sc.Polygon(
             "bounding_box",
             layer="W1",
-            # points=sc.geometry.circle(18, center=(2, -2)),
-            points=sc.geometry.square(30, center=(2, -2), points_per_side=100),
+            points=sc.geometry.circle(20),
+            # points=sc.geometry.square(30, center=(2, -2)),
         ),
         sc.Polygon("pl_hull", layer="W1", points=polygons["pl_hull"]),
     ]
@@ -220,24 +220,27 @@ def huber_squid():
 def squid_with_sample(sample_Lambda=10, sample_height=-1):
 
     squid = huber_squid()
-    layers = squid.layers
+    layers = squid.layers_list
     films = squid.films
     abstract_regions = squid.abstract_regions
 
     # Add the sample layer and film
-    layers["sample_layer"] = sc.Layer(
-        "sample_layer", Lambda=sample_Lambda, z0=sample_height,
+    layers.insert(
+        0,
+        sc.Layer(
+            "sample_layer", Lambda=sample_Lambda, z0=sample_height,
+        )
     )
     films["sample"] = sc.Polygon(
         "sample",
         layer="sample_layer",
-        # points=sc.geometry.circle(18, center=(2, -2)),
-        points=sc.geometry.square(30, center=(2, -2), points_per_side=100),
+        points=sc.geometry.circle(20),
+        # points=sc.geometry.square(30, center=(2, -2)),
     )
     # Remove the old bounding box
     del abstract_regions["bounding_box"]
 
-    squid.layers = layers
+    squid.layers_list = layers
     squid.films = films
     squid.abstract_regions = abstract_regions
     squid.name = "squid_with_sample"

### 2021-08-13 examples/scripts/squid_susceptometry/sweep_lambda_z0.py

@@ -41,7 +41,7 @@ if __name__ == "__main__":
         "-n",
         "--num_points",
         type=int,
-        default=10,
+        default=5,
         help="Number of points in the sweep."
     )
     parser.add_argument(
@@ -58,9 +58,19 @@ if __name__ == "__main__":
         default=True,
         help="Whether to save all figures."
     )
+    parser.add_argument(
+        "-s",
+        "--sweep_num_cpus",
+        type=bool,
+        default=False,
+        help="If True, then sweep the number of cpus from 0 to num_cpus.",
+    )
     args = parser.parse_args()
 
-    parallel_method = "ray" if (args.num_cpus > 0) else None
+    if args.sweep_num_cpus:
+        num_cpus_list = list(range(args.num_cpus))
+    else:
+        num_cpus_list = [args.num_cpus]
 
     logging.basicConfig(level=logging.INFO)
 
@@ -108,14 +118,27 @@ if __name__ == "__main__":
     print("Polygon flux (Phi_0):")
     print(df)
 
+    pl_flux = df["pl_hull"].values[4] * squid.ureg("Phi_0")
+    mutual0 = (pl_flux / I_fc).to("Phi_0 / A")
+    print("Without sample:")
+    print(f"\tPickup loop flux = {pl_flux:.3e~P}")
+    print(
+        f"\tMutual inductance = {mutual0:.3f~P} = "
+        f"{mutual0.to('pH'):.3f~P}"
+    )
+
     if args.figures:
         fig, ax = plt.subplots(figsize=(8, 6))
         ax.grid(True)
         for col in df.columns:
             ys = df[col].values
-            ys = np.abs(np.diff(ys))[1:] / np.abs(ys)[1:-1]
+            ys = np.abs(np.diff(ys)[1:] / ys[1:-1])
             ax.plot(np.arange(len(ys)) + 1, ys, 'o--', lw=3, label=col)
-        ax.set_title("Fractional change in polygon flux vs. iteration")
+        title = (
+            "Fractional change in polygon flux vs. iteration"
+            + f"\n$\\Phi =$ {pl_flux.m:.3f} $\\Phi_0$, $M_0$ = {mutual0.m:.0f} $\\Phi_0$ / A"
+        )
+        ax.set_title(title)
         ax.set_ylabel("$\\left|(\\Phi_{(i+1)} -\\Phi_{(i)}) / \\Phi_{(i)}\\right|$")
[…]

### 2021-08-13 examples/scripts/small_squid/point_spread_function.py
add sbatch script

@@ -1,7 +1,9 @@
 import os
+import time
 import itertools
 import tempfile
 
+import ray
 import numpy as np
 import pandas as pd
 import matplotlib.pyplot as plt
@@ -40,9 +42,19 @@ if __name__ == "__main__":
 
     parser = argparse.ArgumentParser()
     parser.add_argument(
+        "--num_cpus",
+        type=int,
+        default=0,
+    )
+    parser.add_argument(
+        "--outdir",
+        type=str,
+        default=None,
+    )
+    parser.add_argument(
         "--vortex_height",
         type=float,
-        default=-2.0,
+        default=-0.2,
         help="Height of the vortex relative to the SQUID."
     )
     parser.add_argument(
@@ -76,9 +88,9 @@ if __name__ == "__main__":
         help="Linear pixel size in microns."
     )
     parser.add_argument(
-        "--use_ray",
-        type=bool,
-        default=True,
+        "--job_id",
+        type=str,
+        default=None,
     )
     args = parser.parse_args()
 
@@ -116,11 +128,19 @@ if __name__ == "__main__":
         VortexField(x0=x0, y0=y0, z0=z0) for x0, y0 in itertools.product(xs, ys)
     ]
 
-    parallel_method = "ray" if args.use_ray else None
+    if args.num_cpus == 0:
+        parallel_method = None
+    else:
+        parallel_method = "ray"
+        ray.init(num_cpus=args.num_cpus)
 
-    arrays = device.get_arrays(dense=False)
+    if args.outdir is None:
+        save_context = tempfile.TemporaryDirectory()
+    else:
+        outdir = os.path.join(args.outdir, time.strftime("%y%m%d_%H%M%S_small_squid_psf"))
+        save_context = sc.io.NullContextManager(outdir)
 
-    with tempfile.TemporaryDirectory() as directory:
+    with save_context as directory:
         _, paths = sc.solve_many(
             device=device,
             applied_fields=applied_fields,
@@ -136,12 +156,14 @@ if __name__ == "__main__":
         records = []
         for path, vortex in zip(paths, applied_fields):
             solution = sc.Solution.from_file(os.path.join(directory, path))
-            solution.device.set_arrays(arrays)
             flux_dict = solution.polygon_flux(units="Phi_0", with_units=False)
             flux_dict["x0"] = vortex.kwargs["x0"]
             flux_dict["y0"] = vortex.kwargs["y0"]
[…]

### 2021-09-17 examples/scripts/plot_solutions.py
remove unused examples

@@ -1,124 +1,0 @@
-import numpy as np
-import matplotlib.colors as cm
-import matplotlib.pyplot as plt
-from mpl_toolkits.axes_grid1.axes_divider import make_axes_locatable
-
-import superscreen as sc
-
-plt.rcParams["font.size"] = 18
-plt.rcParams["savefig.dpi"] = 150
-
-
-def plot_solutions(
-    solutions,
-    Lambdas,
-    figsize=(14, 10),
-    grid_shape=200,
-    line_cmap="viridis",
-    lw=2.5,
-    show_Lambda=1,
-    plot_polygons=True,
-    auto_range_cutoff=0.1,
-):
-    N = grid_shape // 2
-
-    fig, axes = plt.subplots(2, 2, figsize=figsize)
-    (ax, bx), (cx, dx) = axes
-    ax.set_aspect("equal")
-    bx.set_aspect("equal")
-    cx.grid(True)
-    dx.grid(True)
-
-    colors = plt.get_cmap(line_cmap)(np.linspace(0, 1, len(Lambdas)))
-
-    for i, (solution, Lambda, color) in enumerate(zip(solutions, Lambdas, colors)):
-
-        xgrid, ygrid, fields = solution.grid_data("fields", grid_shape=grid_shape)
-        field = fields["base"]
-
-        xvec, yvec = sc.grids_to_vecs(xgrid, ygrid)
-
-        if Lambda == show_Lambda:
-            vmin, vmax = sc.visualization.auto_range_iqr(field, auto_range_cutoff)
-            im = ax.pcolormesh(
-                xgrid,
-                ygrid,
-                field,
-                shading="auto",
-                cmap="cividis",
-                vmin=vmin,
-                vmax=vmax,
-            )
-            ax.set_xlabel("$x$ [$\\mu$m]")
-            ax.set_ylabel("$y$ [$\\mu$m]")
-            ax.set_title(
-                f"Magnetic field, $\\mu_0H_z$\n$\\Lambda$ = {show_Lambda:.2f} $\\mu$m"
-            )
-            ax_divider = make_axes_locatable(ax)
-            cax = ax_divider.append_axes("right", size="8%", pad="4%")
-            cbar = fig.colorbar(im, cax=cax)
-            cbar.set_label(f"$\\mu_0H_z$ [{solution.field_units}]")
-            ax.axhline(xvec[N], ls="--", color="w", lw=lw)
[…]

### 2021-09-17 examples/scripts/small_squid/mutual_inductance.py

@@ -1,139 +1,0 @@
-import os
-
-import numpy as np
-import pandas as pd
-import matplotlib.pyplot as plt
-
-import superscreen as sc
-
-from squid import make_squid
-
-plt.rcParams["font.size"] = 14
-plt.rcParams["savefig.dpi"] = 150
-
-
-if __name__ == "__main__":
-
-    import argparse
-    import logging
-
-    parser = argparse.ArgumentParser()
-    parser.add_argument(
-        "--min_triangles",
-        type=int,
-        default=8000,
-        help="Minimum number of trianges in the mesh.",
-    )
-    parser.add_argument(
-        "--optimesh_steps",
-        type=int,
-        default=400,
-        help="Number of optimesh steps to perform when making the mesh."
-    )
-    parser.add_argument(
-        "--iterations",
-        type=int,
-        default=9,
-        help="Number of solver iterations to perform."
-    )
-    args = parser.parse_args()
-
-    logging.basicConfig(level=logging.INFO)
-
-    imagedir = os.path.join(os.pardir, "images", "small_squid")
-    os.makedirs(imagedir, exist_ok=True)
-
-    device = make_squid()
-    device.layers["BE"].london_lambda = 1
-    device.make_mesh(min_triangles=args.min_triangles, optimesh_steps=args.optimesh_steps)
-    print(device)
-
-    # Plot the device's mesh and polygons
-    ax = device.plot_mesh(figsize=(6, 6), color="k", alpha=0.4)
-    ax = device.plot_polygons(ax=ax, linewidth=4)
-    npoints = device.points.shape[0]
-    ntriangles = device.triangles.shape[0]
-    ax.set_title(f"{device.name} mesh:\n{npoints} points, {ntriangles} triangles")
-    ax.figure.savefig(
-        os.path.join(imagedir, f"{device.name}_mutual_mesh.png"),
-        bbox_inches="tight",
-    )
-
-    applied_field = sc.sources.ConstantField(0)
-    circulating_currents = {"fc_center": "1 mA"}
-    I_fc = device.ureg(circulating_currents["fc_center"]).to("A")
-
-    solutions = sc.solve(
-        device=device,
-        applied_field=applied_field,
-        circulating_currents=circulating_currents,
[…]

### 2021-09-17 examples/scripts/small_squid/point_spread_function.py

@@ -1,180 +1,0 @@
-import os
-import time
-import itertools
-import tempfile
-
-import ray
-import numpy as np
-import pandas as pd
-import matplotlib.pyplot as plt
-
-import superscreen as sc
-
-from squid import make_squid, split_layer
-
-plt.rcParams["font.size"] = 14
-plt.rcParams["savefig.dpi"] = 150
-
-
-def vortex_field(x, y, z, x0=0, y0=0, z0=0, nPhi0=1):
-    """Field from an isolated vortex.
-
-    Args:
-        x, y, z: Position coordinates.
-        x0, y0, z0: Vortex position
-        nPhi0: Number of flux quanta contained in the vortex.
-    """
-    xp = x - x0
-    yp = y - y0
-    zp = z - z0
-    Hz0 = zp / (xp ** 2 + yp ** 2 + zp ** 2) ** (3 / 2) / (2 * np.pi)
-    return nPhi0 * Hz0
-
-
-def VortexField(x0=0, y0=0, z0=0, nPhi0=1):
-    return sc.Parameter(vortex_field, x0=x0, y0=y0, z0=z0, nPhi0=nPhi0)
-
-
-if __name__ == "__main__":
-
-    import argparse
-    import logging
-
-    parser = argparse.ArgumentParser()
-    parser.add_argument(
-        "--num_cpus",
-        type=int,
-        default=0,
-    )
-    parser.add_argument(
-        "--outdir",
-        type=str,
-        default=None,
-    )
-    parser.add_argument(
-        "--vortex_height",
-        type=float,
-        default=-0.2,
-        help="Height of the vortex relative to the SQUID."
-    )
-    parser.add_argument(
-        "--min_triangles",
-        type=int,
-        default=8000,
-        help="Minimum number of trianges in the mesh.",
-    )
-    parser.add_argument(
-        "--optimesh_steps",
-        type=int,
-        default=400,
-        help="Number of optimesh steps to perform when making the mesh."
-    )
-    parser.add_argument(
-        "--iterations",
-        type=int,
-        default=5,
-        help="Number of solver iterations to perform."
-    )
-    parser.add_argument(
-        "--max_thickness",
-        type=float,
-        default=None,
-        help="Maximum thickness of Layers making up the pickup loop shield."
-    )
-    parser.add_argument(
-        "--pixel_size",
-        type=float,
-        default=0.25,
-        help="Linear pixel size in microns."
-    )
-    parser.add_argument(
[…]

### 2021-09-17 examples/scripts/small_squid/squid.py

@@ -1,366 +1,0 @@
-import os
-
-import numpy as np
-from scipy.io import loadmat
-
-from superscreen import Device, Layer, Polygon
-from superscreen.geometry import rotate
-
-
-def split_layer(device, layer_name, max_thickness=0.05):
-    """Splits a given layer into multiple thinner layers."""
-    layers = device.layers
-    films = device.films
-    holes = device.holes
-    abstract_regions = device.abstract_regions
-    
-    layer_to_split = layers.pop(layer_name)
-    london_lambda = layer_to_split.london_lambda
-    z0 = layer_to_split.z0
-    d = layer_to_split.thickness
-    
-    num_layers, mod = divmod(d, max_thickness)
-    num_layers = int(num_layers)
-    new_ds = [max_thickness for _ in range(num_layers)]
-    if mod:
-        num_layers += 1
-        new_ds.append(mod)
-    new_layers = {}
-    for i, new_d in enumerate(new_ds):
-        name = f"{layer_name}_{i}"
-        z = i * max_thickness + new_d / 2
-        new_layers[name] = Layer(
-            name, london_lambda=london_lambda, thickness=new_d, z0=z
-        )
-
-    new_films = {}
-    for name, film in films.items():
-        if film.layer == layer_name:
-            for i, new_layer_name in enumerate(new_layers):
-                film_name = f"{name}_{i}"
-                new_film = film.copy()
-                new_film.name = film_name
-                new_film.layer = new_layer_name
-                new_films[film_name] = new_film
-        else:
-            new_films[name] = film
-            
-    new_holes = {}
-    for name, hole in holes.items():
-        if hole.layer == layer_name:
-            for i, new_layer_name in enumerate(new_layers):
-                hole_name = f"{name}_{i}"
-                new_hole = hole.copy()
-                new_hole.name = hole_name
-                new_hole.layer = new_layer_name
-                new_holes[film_name] = new_hole
-        else:
-            new_holes[name] = hole
-            
-    new_abstract_regions = {}
-    for name, region in abstract_regions.items():
[…]

### 2021-09-17 examples/scripts/squid_susceptometry/huber_squid.py

@@ -1,248 +1,0 @@
-import numpy as np
-
-import superscreen as sc
-
-
-def huber_geometry(interp_points=101):
-
-    ri_pl = 1.7
-    ro_pl = 2.7
-    w_pl_center = 1.18
-    w_pl_outer = 3.10
-    pl_angle = 0
-    pl_total_length = 15
-    y0_pl_leads = -(pl_total_length - ro_pl)
-
-    x0_pl_center = w_pl_center / 2
-    theta0_pl_center = np.arcsin(x0_pl_center / ri_pl)
-    thetas_pl_center = (
-        np.linspace(theta0_pl_center, 2 * np.pi - theta0_pl_center, 101) - np.pi / 2
-    )
-
-    x0_pl_outer = w_pl_outer / 2
-    theta0_pl_outer = np.arcsin(x0_pl_outer / ro_pl)
-    thetas_pl_outer = (
-        np.linspace(theta0_pl_outer, 2 * np.pi - theta0_pl_outer, 101) - np.pi / 2
-    )
-
-    pl_points = np.concatenate(
-        [
-            [[-w_pl_outer / 2, y0_pl_leads]],
-            ro_pl
-            * np.stack([np.cos(thetas_pl_outer), np.sin(thetas_pl_outer)], axis=1)[
-                ::-1
-            ],
-            [[w_pl_outer / 2, y0_pl_leads]],
-            [[w_pl_center / 2, y0_pl_leads]],
-            ri_pl
-            * np.stack([np.cos(thetas_pl_center), np.sin(thetas_pl_center)], axis=1),
-            [[-w_pl_center / 2, y0_pl_leads]],
-            [[-w_pl_outer / 2, y0_pl_leads]],
-        ]
-    )
-    pl_points = sc.geometry.rotate(pl_points, pl_angle)
-
-    pl_shield = np.concatenate(
-        [
-            [[-(w_pl_outer / 2 + 0.25), -(ri_pl + 0.5)]],
-            [[-w_pl_outer / 2, -(ri_pl + 0.25)]],
-            [[+w_pl_outer / 2, -(ri_pl + 0.25)]],
-            [[+(w_pl_outer / 2 + 0.25), -(ri_pl + 0.5)]],
-            [[+(w_pl_outer / 2 + 0.25), y0_pl_leads - 0.5]],
-            [[-(w_pl_outer / 2 + 0.25), y0_pl_leads - 0.5]],
[…]

### 2021-09-17 examples/scripts/squid_susceptometry/sweep_lambda_z0.py

@@ -1,306 +1,0 @@
-import os
-
-os.environ["OPENBLAS_NUM_THREADS"] = "1"
-
-import time
-import logging
-import tempfile
-
-import ray
-import numpy as np
-import pandas as pd
-import matplotlib.pyplot as plt
-
-import superscreen as sc
-
-from .huber_squid import squid_with_sample
-
-plt.rcParams["font.size"] = 14
-plt.rcParams["savefig.dpi"] = 150
-
-
-def layer_updater(layer, Lambda=None, z0=None):
-    if layer.name == "sample_layer":
-        if Lambda is not None:
-            layer.Lambda = Lambda
-        if z0 is not None:
-            layer.z0 = z0
-    return layer
-
-
-if __name__ == "__main__":
-    import argparse
-
-    parser = argparse.ArgumentParser()
-    parser.add_argument(
-        "--sweep_type",
-        choices=["Lambda", "z0"],
-        help="Parameter to sweep, either Lambda or z0."
-    )
-    parser.add_argument(
-        "-n",
-        "--num_points",
-        type=int,
-        default=5,
-        help="Number of points in the sweep."
-    )
-    parser.add_argument(
-        "-c",
-        "--num_cpus",
-        type=int,
-        default=0,
-        help="Number of CPUs to use. Set to 0 for serial execution."
-    )
-    parser.add_argument(
-        "-f",
-        "--figures",
-        type=bool,
-        default=True,
-        help="Whether to save all figures."
-    )
-    parser.add_argument(
-        "-s",
-        "--sweep_num_cpus",
-        type=bool,
-        default=False,
-        help="If True, then sweep the number of cpus from 0 to num_cpus.",
-    )
-    args = parser.parse_args()
-
-    if args.sweep_num_cpus:
-        num_cpus_list = list(range(args.num_cpus))
-    else:
-        num_cpus_list = [args.num_cpus]
-
-    logging.basicConfig(level=logging.INFO)
-
-    imagedir = os.path.join(os.pardir, "images", "squid_susceptometry")
-    os.makedirs(imagedir, exist_ok=True)
-    
-    squid = squid_with_sample()
-    print(squid)
-    squid.make_mesh(min_triangles=8500, optimesh_steps=400)
-
-    if args.figures:
-        ax = squid.plot_mesh(figsize=(8, 6), color="k", alpha=0.5)
-        ax = squid.plot_polygons(ax=ax, linewidth=4)
-        npoints = squid.points.shape[0]
-        ntriangles = squid.triangles.shape[0]
[…]

### 2021-09-17 examples/scripts/susceptometry.py

@@ -1,277 +1,0 @@
-import os
-import time
-import logging
-
-import ray
-import numpy as np
-import matplotlib.pyplot as plt
-
-import superscreen as sc
-import superscreen.geometry as geo
-
-
-def susceptibility_analytical(z, Lambda, a=8.4):
-    """See Table 1 of 10.1103/PhysRevB.85.224518 (arXiv:1204.3355).
-    
-    Args:
-        z: Vertical distance between the sample and sensor.
-        Lambda: Effective penetration depth of the sample,
-            Lambda = london_lambda**2/thickness.
-        a: Effective field coil radius = 8.4 microns from the paper.
-    
-    Returns:
-        Normalized susceptibility signal (M - M_no_sample) / M_no_sample,
-        where M is the field coil - pickup loop mutual inductance.
-    """
-    # In the above paper, Lambda = 2 * lambda_london**2 / thickness, i.e. Pearl length.
-    Lambda_Pearl = 2 * Lambda
-    zbar = z / a
-    return -a / Lambda_Pearl * (1 - 2 * zbar / np.sqrt(1 + 4 * zbar ** 2))
-
-
-def sensor_and_sample(
-    *,
-    field_coil_mean_radius,
-    field_coil_Lambda,
-    pickup_loop_mean_radius,
-    pickup_loop_Lambda,
-    line_width,
-    sample_Lambda,
-    sample_z0=-1,
-    length_units="um",
-):
-    layers = [
-        sc.Layer("fc_layer", Lambda=field_coil_Lambda, z0=0),
-        sc.Layer("pl_layer", Lambda=pickup_loop_Lambda, z0=-0.4),
-        sc.Layer("sample_layer", Lambda=sample_Lambda, z0=sample_z0)
-    ]
-    field_coil_outer_radius = field_coil_mean_radius + line_width / 2
-    field_coil_inner_radius = field_coil_mean_radius - line_width / 2
-    pickup_loop_outer_radius = pickup_loop_mean_radius + line_width / 2
-    pickup_loop_inner_radius = pickup_loop_mean_radius - line_width / 2
-    films = [
-        sc.Polygon(
-            "field_coil",
-            layer="fc_layer",
-            points=geo.circle(field_coil_outer_radius, points=301),
-        ),
-        sc.Polygon(
-            "pickup_loop",
-            layer="pl_layer",
-            points=geo.circle(pickup_loop_outer_radius),
-        ),
-        sc.Polygon(
-            "sample",
-            layer="sample_layer",
[…]

### 2021-09-17 main.tex

--- 2021-08-10 main.tex
@@
 from Eq.~\ref{eq:field_from_kernel_num}, and the full vector magnetic field $\vec{H}(x, y, z)$
-at any point in space can be computed from Eq.~\ref{eq:field_from_kernel}.
+at any point in space can be computed from Eqs.~\ref{eq:field_from_kernel} and ~\ref{eq:kernels}.
 
@@
 A \inline{superscreen.Parameter} is a wrapper around a Python function that computes a scalar value as a function of position coordinates ($x$, $y$, and optionally $z$) based on some set of keyword arguments.
-Addition, subtraction, multiplication, division, and exponentiation between \inline{Parameters}, other \inline{Parameters}, and Python scalars (\inline{int} and \inline{float}) are supported.
-For example, see Code Block~\ref{code:parameters}.
-\inline{Parameters} can be used to conveniently define applied magnetic fields and penetration depths that depend on position, and make it possible to serialize wrapped Python functions for storage or inter-process communication.
+Addition, subtraction, multiplication, division, and exponentiation between \inline{Parameters}, other \inline{Parameters}, and Python scalars (\inline{int} and \inline{float}) are supported (see Code Block~\ref{code:parameters}).
+\inline{Parameters} can be used to conveniently define applied magnetic fields and penetration depths that depend on position, and make it possible to serialize wrapped Python functions for storage to disk or inter-process communication.
 
@@
 Mesh generation is a two step process.
-First, an initial Delaunay mesh is created using \inline{meshpy}~\cite{Klockner}, a Python interface to Triangle~\cite{shewchuk96b, Shewchuk}, a fast compiled 2D mesh generation tool.
+First, an initial Delaunay mesh is created using \inline{meshpy}~\cite{Klockner}, which is a Python interface to Triangle~\cite{shewchuk96b, Shewchuk}, a fast compiled 2D mesh generation tool.
 Second (and optionally), the mesh can be further optimized using \inline{optimesh}~\cite{nico_schlomer_adam_dobrawy_2021}.
@@
 
-Figure X shows a \inline{Device} representing field coil and pickup loop of an actual scanning SQUID sensor.
-In addition to the field coil and pickup loop, there are superconducting shields that limit the amount of magnetic flux that can penetrate the leads connecting the loops to the rest of the circuit.
+% \begin{figure}[!h]
+% \centering
+% \begin{subfigure}{.35\textwidth}
+%   \centering
+%   \includegraphics[width=\linewidth]{examples/images/squid_susceptometry/squid_with_sample_mesh.png}
+%   \label{fig:squid_mesh}
+%   \caption{}
+% \end{subfigure}%
+% \hspace{10pt}
+% \begin{subfigure}{.5\textwidth}
+%   \centering
+%   \includegraphics[width=\linewidth]{examples/images/squid_susceptometry/squid_with_sample_M0_convergence.png}
+%   \label{fig:squid_convergence}
+%   \caption{}
+% %   \caption{Fractional change in flux though all polygons vs.
+solver iteration with a current of $1\,\mathrm{mA}$ flowing in the field coil (\inline{fc}).
+The mutual inductance $M_0$ is given by the flux through the pickup loop (\inline{pl_hull}) divided by the field coil current.}
+% \end{subfigure}%
+% \caption{(a): Device polygons and mesh for the SQUID susceptometer model.
+(b) Fractional change in flux though all polygons vs.
+solver iteration with a current of $1\,\mathrm{mA}$ flowing in the field coil (\inline{fc}).
+The mutual inductance $M_0$ is given by the flux through the pickup loop (\inline{pl_hull}) divided by the field coil current.}
+% \label{fig:susceptometry}
+% \end{figure}
+
+Figure~\ref{fig:susceptometry}(a) shows a \inline{Device} representing field coil and pickup loop of an actual scanning SQUID sensor.
+In addition to the field coil and pickup loop, there are superconducting shields that limit the amount of magnetic flux that can penetrate the leads connecting the loops to the rest of the circuit (the rest of the circuit is not modeled).
 There are three relevant layers of superconducting films: the base electrode (``BE"), which is furthest from the sample contains the field coil; the first wiring layer (``W1"), which contains the pickup loop and a shield covering the field coil leads; and the second wiring layer (``W2"), which is closest to the sample and contains a shield covering the pickup loop leads.
@@
 The susceptibility can also be normalized to the bare mutual inductance $M_0$, giving a dimensionless susceptibility $\chi(z, \Lambda)=[M(z, \Lambda) - M_0] / M_0$.
+
+% \begin{figure}[!h]
+% \centering
+% \begin{subfigure}{\textwidth}
+%   \centering
+%   \includegraphics[width=\linewidth]{examples/images/squid_susceptometry/squid_with_sample_currents_Lambda=1_00__um__z=-1_00__um.png}
+% %   \caption{Device polygons and mesh for the SQUID susceptometer model.}
+% %   \label{fig:squid_mesh}
+% \end{subfigure}%
+% \vspace{-15pt}
+% \begin{subfigure}{\textwidth}
+%   \centering
+%   \includegraphics[width=\linewidth]{examples/images/squid_susceptometry/squid_with_sample_currents_Lambda=10_00__um__z=-1_00__um.png}
+% %   \caption{Fractional change in flux though all polygons vs.
+solver iteration with a current of $1\,\mathrm{mA}$ flowing in the field coil (\inline{fc}).
+The mutual inductance $M_0$ is given by the flux through the pickup loop (\inline{pl_hull}) divided by the field coil current.}
+% %   \label{fig:squid_convergence}
+% \end{subfigure}%
+% \vspace{-15pt}
+% \begin{subfigure}{\textwidth}
+%   \centering
+%   \includegraphics[width=\linewidth]{examples/images/squid_susceptometry/squid_with_sample_currents_Lambda=1_00__um__z=-10_00__um.png}
+% %   \caption{Fractional change in flux though all polygons vs.
+solver iteration with a current of $1\,\mathrm{mA}$ flowing in the field coil (\inline{fc}).
+The mutual inductance $M_0$ is given by the flux through the pickup loop (\inline{pl_hull}) divided by the field coil current.}
+% %   \label{fig:squid_convergence}
+% \end{subfigure}%
+% \caption{Left: Device polygons and mesh for the SQUID susceptometer model.
+Right: Fractional change in flux though all polygons vs.
+solver iteration with a current of $1\,\mathrm{mA}$ flowing in the field coil (\inline{fc}).
+The mutual inductance $M_0$ is given by the flux through the pickup loop (\inline{pl_hull}) divided by the field coil current.}
+% % \label{fig:susceptometry}
+% \end{figure}
 
@@
 # Start a ray cluster from the command line, e.g. bash
-ray start --head --num=cpus=3
+ray start --head --num-cpus=3
 \end{minted}
@@
 
-Maybe demonstrate scaling on Sherlock here.
-
 %% References

### 2021-10-20 main.tex
pushing overleaf changes

@@
 
-\title{\texttt{SuperScreen}: An open-source package for simulating the magnetic response of two-dimensional superconductors}
+\title{\texttt{SuperScreen}: An open-source package for simulating the magnetic response of two-dimensional superconducting devices}
 
@@
 
-\author[a]{Logan Bishop-Van Horn}
-\author[a,b]{Kam Moler\corref{author}}
+\author[PHYS,SIMES]{Logan Bishop-Van Horn}
+\author[AP,SIMES,GLAM]{Kathryn A. Moler\corref{author}}
 
 \cortext[author]{Corresponding author.\\\textit{E-mail address:} kmoler@stanford.edu}
-\address[a]{First Address}
-\address[b]{Second Address}
+
+\address[PHYS]{Department of Physics, Stanford University, Stanford, California 94305, USA}
+\address[AP]{Department of Applied Physics, Stanford University, Stanford, California 94305, USA}
+\address[SIMES]{Stanford Institute for Materials and Energy Sciences, SLAC National Accelerator Laboratory, 2575 Sand Hill Road, Menlo Park, California 94025, USA}
+\address[GLAM]{Geballe Laboratory for Advanced Materials, Stanford University, Stanford, California 94305, USA}
 
 \begin{abstract}
-Quantitative understanding of the spatial distribution of magnetic fields and screening currents in two-dimensional (2D) superconductors and mesoscopic superconducting devices is critical to interpreting the results of magnetic measurements of such systems.
+Quantitative understanding of the spatial distribution of magnetic fields and screening currents in two-dimensional (2D) superconductors and mesoscopic thin film superconducting devices is critical to interpreting the results of magnetic measurements of such systems.
 Here we introduce \SuperScreen, an open-source Python package for simulating the magnetic response of two-dimensional superconductors to applied time-independent magnetic fields.
-Given an applied magnetic field, \SuperScreen solves for Meissner screening currents and the resulting magnetic fields in structures composed of one or more superconducting thin films of arbitrary geometry with spatially inhomogeneous magnetic penetration depth using a matrix inversion method introduced by Brandt~\cite{brandt_thin_2005}.
+Given an applied magnetic field, \SuperScreen solves for Meissner screening currents and the resulting magnetic fields in structures composed of one or more superconducting thin films of arbitrary geometry with spatially inhomogeneous magnetic penetration depth using a matrix inversion method introduced by Brandt and Clem~\cite{Brandt_Clem_2004, brandt_thin_2005}.
 \SuperScreen can be used to model screening effects and calculate self- and mutual-inductance in superconducting circuits, and simulate the magnetic response of inhomogeneous 2D superconductors.
@@
 %% keywords here, in the form: keyword \sep keyword
-superconductivity\sep Meissner screening\sep thin film
+superconductivity\sep Meissner screening\sep thin film\sep London equations
 
@@
   %Describe the nature of the problem here. \\
-{\em Solution method:} The package solves the 2D London equations inside superconducting regions and Maxwell's equations outside the superconductor using a matrix inversion method introduced by Brandt~\cite{brandt_thin_2005}.\\
+{\em Solution method:} The package solves the 2D London equations inside superconducting regions and Maxwell's equations outside the superconductor using a matrix inversion method introduced by Brandt and Clem~\cite{Brandt_Clem_2004,brandt_thin_2005}.\\
   %Describe the method solution here.
@@
 
-\SuperScreen is an open-source Python package developed to simulate the magnetic response of structures composed of one or more layers containing superconducting thin films.
-\SuperScreen solves the coupled Maxwell's and London's equations in and around superconducting films with spatially-varying penetration depth in the presence of applied magnetic fields and trapped flux using a matrix inversion method introduced by Brandt~\cite{brandt_thin_2005} and initially implemented by Kirtley, \emph{et al.}~\cite{kirtley_scanning_2016, kirtley_response_2016} to model the magnetic response of scanning superconducting quantum interference device (SQUID) sensors.
+\SuperScreen is an open-source Python package developed to simulate the static magnetic response of structures composed of one or more layers containing superconducting thin films.
+\SuperScreen solves the coupled Maxwell's and London's equations in and around superconducting films with spatially-varying penetration depth in the presence of applied magnetic fields, pinned vortices, and trapped flux using a matrix inversion method introduced by Brandt and Clem~\cite{Brandt_Clem_2004,brandt_thin_2005} and initially implemented by Kirtley, \emph{et al.} to model the magnetic response of scanning superconducting quantum interference device (SQUID) sensors.~\cite{kirtley_scanning_2016, kirtley_response_2016}
 
@@
 $H_{z,\,\mathrm{applied}}(x, y, z)$.
-
 Given $H_{z,\,\mathrm{applied}}(x, y, z)$ and information about the geometry and magnetic penetration depth of all films in a superconducting structure, we aim to calculate the thickness-integrated current density (or sheet current) $\vec{J}(x, y)$ at all points inside the films, from which one can calculate the vector magnetic field $\vec{H}(x, y, z)$ at all points both inside and outside the films.
 
-A convenient method for solving this problem was introduced by Brandt in~\cite{brandt_thin_2005}, and subsequently used to model the magnetic response of scanning Superconducting Quantum Interference Device (SQUID) susceptometers~\cite{kirtley_scanning_2016, kirtley_response_2016}.
-
+A convenient method for solving this problem was introduced by Brandt and Clem in Ref.~\cite{Brandt_Clem_2004}, expanded by Brandt in Ref.~\cite{brandt_thin_2005}, and subsequently used to model the magnetic response of scanning Superconducting Quantum Interference Device (SQUID) susceptometers~\cite{kirtley_scanning_2016, kirtley_response_2016}.
 In the London model of superconductivity, the magnetic field $\vec{H}(\vec{r})$ and 3D current density $\vec{j}(\vec{r})$ in a superconductor with London penetration depth $\lambda(\vec{r})$ obey the second London equation:
@@
 $\nabla=\left(\frac{\partial}{\partial x}, \frac{\partial}{\partial y}, \frac{\partial}{\partial z}\right)$.
-Brandt's model assumes that the current density $\vec{j}$ is approximately independent of $z$, such $\vec{j}(\vec{r}) = \vec{j}(x, y, z)\approx\vec{j}_{z_0}(x, y)$ for a film lying parallel to the $x-y$ plane at vertical position $z_0$.
-Working now with the thickness-integrated current density (sheet current) $\vec{J}(x, y)\approx\vec{j}_{z_0}(x, y)\cdot d$, where $d$
+Brandt's model assumes that the current density $\vec{j}$ is approximately independent of $z$, such that  $\vec{j}(\vec{r}) = \vec{j}(x, y, z)\approx\vec{j}_{z_0}(x, y)$ for a film lying parallel to the $x-y$ plane at vertical position $z_0$.
+Working now with the thickness-integrated current density (sheet current) $\vec{J}(x, y)=\vec{j}_{z_0}(x, y)\cdot d$, where $d$
 is the thickness of the film, the second London equation reduces to
@@
 
-Because the sheet current has zero divergence in the superconducting film ($\nabla\cdot\vec{J}=0$)
+Because the sheet current has zero divergence inside the superconducting film ($\nabla\cdot\vec{J}=0$)
 except at small contacts where current can be injected, one can express the sheet current in terms
@@
 
-The stream function $g$ can be thought of as the local magnetization of the film, or the area density of magnetic dipole sources (see \cite{brandt_thin_2005} for more interesting properties of the stream function).
-We can re-write Eq.~\ref{eq:london} for a 2D film in terms of $g$:
+The stream function $g$ can be thought of as the local magnetization of the film, or the area density of magnetic dipole sources (see Ref.~\cite{brandt_thin_2005} for more interesting properties of the stream function).
+We can rewrite Eq.~\ref{eq:london}, which gives the magnetic field inside of a 2D film, in terms of $g$:
 
@@
         &= -\Lambda\left[\nabla(\nabla\cdot(g\hat{z}))-\nabla^2(g\hat{z})\right]\\
-        &=\Lambda\nabla^2g(x,y)\hat{z}\\
-        &=H_z(x, y)\hat{z}
+        &=\Lambda\nabla^2g(x,y)\hat{z}
     \end{split}
@@
 where $\nabla^2=\nabla\cdot\nabla$ is the Laplace operator.
-(The fourth line follows from the fact that $\nabla\cdot\left[g(x,y)\hat{z}\right] = 0$).
-From Ampere's Law, the three components of the magnetic field at position $\vec{r}=(x, y, z)$ due to a sheet of current lying in the $x-y$ plane (at vertical position $z'$) with stream function $g(x', y')$ are given by:
+(The last line follows from the fact that $\nabla\cdot\left[g(x,y)\hat{z}\right] = 0$).
+From Ampere's Law, the three components of the magnetic field $\vec{H}(\vec{r})$ at position $\vec{r}=(x, y, z)$ due to a sheet of current lying in the $x-y$ plane (at vertical position $z'$) with stream function $g(x', y')$ are given by:
 
@@
     \begin{split}
-        H_x(\vec{r}) &= \int_S Q_x(\vec{r},\vec{r}')g(x', y')\,\mathrm{d}^2r'\\
-        H_y(\vec{r}) &= \int_S Q_y(\vec{r},\vec{r}')g(x', y')\,\mathrm{d}^2r'\\
+        H_x(\vec{r}) &= \int_F Q_x(\vec{r},\vec{r}')g(x', y')\,\mathrm{d}^2r'\\
+        H_y(\vec{r}) &= \int_F Q_y(\vec{r},\vec{r}')g(x', y')\,\mathrm{d}^2r'\\
         H_z(\vec{r}) &= H_{z,\,\mathrm{applied}}(\vec{r})
-        + \int_S Q_z(\vec{r},\vec{r}')g(x', y')\,\mathrm{d}^2r'  
+        + \int_F Q_z(\vec{r},\vec{r}')g(x', y')\,\mathrm{d}^2r'  
     \end{split}
@@
 Here we assume an out-of-plane applied magnetic field $\vec{H}_\mathrm{applied}(\vec{r}')=H_\mathrm{z,\,\mathrm{applied}}(\vec{r}')\hat{z}$.
-$S$ is the film area (with $g = 0$ outside of the film), and $Q_x(\vec{r},\vec{r}')$, $Q_y(\vec{r},\vec{r}')$, and $Q_z(\vec{r},\vec{r}')$ are dipole kernel functions which give the relevant component of the magnetic field at position $\vec{r}=(x, y, z)$ due to a dipole of unit strength at position $\vec{r}'=(x', y', z')$:
+$F$ is the film area (with $g = 0$ outside of the film), and $Q_x(\vec{r},\vec{r}')$, $Q_y(\vec{r},\vec{r}')$, and $Q_z(\vec{r},\vec{r}')$ are dipole kernel functions which give the respective component of the magnetic field at position $\vec{r}=(x, y, z)$ due to a dipole of unit strength at position $\vec{r}'=(x', y', z')$:
 
@@
     \begin{split}
-        \underbrace{H_z(\vec{r}) = \vec{H}(\vec{r})\cdot\hat{z}
+        \underbrace{\vec{H}(\vec{r})\cdot\hat{z} = H_z(\vec{r})
         = \Lambda\nabla^2g(x, y)}_{z-\text{component of the total field}}
         = \underbrace{H_{z,\,\mathrm{applied}}(\vec{r})}_{\text{applied field}}
-        + \underbrace{\int_S Q_z(\vec{r},\vec{r}')g(\vec{r}')\,\mathrm{d}^2r'}_{\text{screening field}},
+        + \underbrace{\int_F Q_z(\vec{r},\vec{r}')g(\vec{r}')\,\mathrm{d}^2r'}_{\text{screening field}},
     \end{split}
 \end{align}
-(where now $\vec{r}$ and $\vec{r}'$ are 2D vectors, i.e.
-$\Delta z=0$, since the film is in the same plane as itself).
+where now $\vec{r}$ and $\vec{r}'$ are 2D vectors, i.e.
+$z-z'=0$ since the film is in the same plane as itself.
 From Eq.~\ref{eq:integral_equation}, we arrive at an integral equation relating the stream function $g$ for points inside the superconductor to the applied field $H_{z,\,\mathrm{applied}}$:
@@
     H_{z,\,\mathrm{applied}}(\vec{r})
-    = -\int_S\left[
+    = -\int_F\left[
         Q_z(\vec{r},\vec{r}')-\delta(\vec{r}-\vec{r}')\Lambda(\vec{r}')\nabla^2\right
-    ]g(\vec{r}')\,\mathrm{d}^2r'
+    ]g(\vec{r}')\,\mathrm{d}^2r',
 \end{equation}
-
-The goal, then, is to solve (invert) Eq.~\ref{eq:applied_to_stream} for a given $H_{z,\,\mathrm{applied}}$ and film geometry $S$ to obtain $g$ for all points inside the film (with $g=0$ enforced outside the film).
+where $\delta$ is the 2D Dirac delta function.
+
+The goal, then, is to solve (invert) Eq.~\ref{eq:applied_to_stream} for a given $H_{z,\,\mathrm{applied}}$ and film geometry $F$ to obtain $g$ for all points inside the film (with the boundary condition $g=0$ enforced outside the film).
 Once $g(\vec{r})$ is known, the full vector magnetic field $\vec{H}(\vec{r})$ can be calculated at any point $\vec{r}$
@@
 In films that have holes (regions of vacuum completely surrounded by superconductor), each hole $k$ can contain a trapped flux $\Phi_k$, with an associated circulating current $I_{\mathrm{circ},\,k}$.
-The (hypothetical) applied field that would cause such a circulating current is given by Eq.~\ref{eq:applied_to_stream} if we set $g(\vec{r})=I_{\mathrm{circ},\,k}$ for all points $\vec{r}$ lying inside hole $k$:
+The (hypothetical) applied field that would cause such a circulating current is given by Eq.~\ref{eq:applied_to_stream} if we set $g=I_{\mathrm{circ},\,k}$ for all points lying inside hole $k$:
 
@@
     H_{z,\,\mathrm{applied}}(\vec{r}) - \sum_{\mathrm{holes}\,k} H_{z,\,\mathrm{eff},\,k}(\vec{r})
-    = -\int_S\left[
+    = -\int_F\left[
         Q_z(\vec{r},\vec{r}')-\delta(\vec{r}-\vec{r}')\Lambda(\vec{r}')\nabla^2\right
@@
 \end{equation}
+
+\subsection{The fluxoid}
+\label{section:model:fluxoid}
+
+The fluxoid $\Phi^f_S$ for a 2D region $S$ with 1D boundary $\partial S$ is given by the sum of flux through $S$ and the line integral of sheet current around $\partial S$~\cite{brandt_thin_2005,Clem_Brandt_2005,tinkham2004introduction}:
+
+\begin{equation}
+    \Phi^f_S = \underbrace{\int_S\mu_0H_z(\vec{r})\,\mathrm{d}^2r}_\text{``flux part''} + \underbrace{\oint_{\partial S}\mu_0\Lambda(\vec{r})\vec{J}(\vec{r})\cdot\mathrm{d}\vec{r}}_\text{``supercurrent part''}.
+    \label{eq:fluxoid}
+\end{equation}
+
+The fluxoid should vanish for a region $S$ completely contained within a superconducting film that contains no holes or vortices.
+Similarly, the fluxoid $\Phi^f_S$ should have the same value for any region containing a given hole or collection of vortices in a superconducting film.
+This path-independence of the fluxoid follows from the static London equation (Eq.~\ref{eq:london}) on which the present model is based.
+However, because Eq.~\ref{eq:london} does not relate the supercurrent density $\vec{J}$ to the phase of a complex order parameter as in Ginzburg-Landau (GL) theory, or invoke the semi-classical Bohr-Sommerfeld quantization rule as London did~\cite{tinkham2004introduction}, within this model the fluxoid is in no way constrained to be an integer multiple of the flux quantum $\Phi_0=h/2e$.
+
+\subsection{Vortices}
+\label{section:model:vortices}
+In addition to being trapped in holes (see Section~\ref{section:model:holes}), flux may be trapped in a superconducting film in the form of vortices.
+The presence of vortices trapped in a film at positions $\vec{r}_v$ modifies Eq.~\ref{eq:applied_to_stream} as follows:
+
+\begin{equation}
+    \label{eq:applied_to_stream_vortices}
+    H_{z,\,\mathrm{applied}}(\vec{r}) - \sum_{\mathrm{vortices}\,v}\frac{\Phi_v}{\mu_0}\delta(\vec{r}-\vec{r}_v)
+    = -\int_F\left[
+        Q_z(\vec{r},\vec{r}')-\delta(\vec{r}-\vec{r}')\Lambda(\vec{r}')\nabla^2\right
+    ]g(\vec{r}')\,\mathrm{d}^2r',
+\end{equation}
+where $\delta$ is the 2D Dirac delta function and each vortex $v$ is associated with a flux $\Phi_v$ (typically $\Phi_v=n\Phi_0=nh/2e$, where $n$ is an integer, $\Phi_0$ is the magnetic flux quantum, $h$ is the Planck constant, and $e$ is the elementary charge).
+By solving Eq.~\ref{eq:applied_to_stream_vortices} to obtain $g(\vec{r})$, one can compute the supercurrent density in the film due to both an applied field and trapped vortices.
+For a simply-connected region $S$ containing a set of vortices $v$ each associated with a flux $\Phi_v$, the fluxoid should be equal to $\Phi^f_S=\sum_{\mathrm{vortices}\,v}\Phi_v$.
+It is important to note that this 2D London model does not contain the physics associated with how and where vortices nucleate in superconductors, nor is it included in the model that the flux carried by vortices must be quantized in units of $\Phi_0$, both which are captured phenomenologically by GL theory.
+The numerical solution to Eq.~\ref{eq:applied_to_stream_vortices} is described at the end of Section~\ref{section:implementation}.
 
@@
             + \sum_{m\neq\ell}
-            \int_S Q_z(\vec{r},\vec{r}')g_m(\vec{r}')\,\mathrm{d}^2r.
+            \int_{F_m} Q_z(\vec{r},\vec{r}')g_m(\vec{r}')\,\mathrm{d}^2r',
         $$
+        where $F_m$ is surface of all films in layer $m$ and $g_m$ is the stream function for layer $m$.
     }
@@
 
-In order to numerically solve Eq.~\ref{eq:field_from_kernel} and Eq.~\ref{eq:Heff_sub}, we have to discretize the films, holes, and the vacuum regions surrounding them. We use a triangular
+In order to numerically solve Eq.~\ref{eq:field_from_kernel} and Eq.~\ref{eq:applied_to_stream}, we have to discretize the films, holes, and the vacuum regions surrounding them. We use a triangular
 (Delaunay) mesh, consisting of $n$ points (or vertices)
-which together form $m$ triangles. Below we denote column vectors and matrices using bold font. $\mathbf{A}\mathbf{B}$
+which together form $t$ triangles. Below we denote column vectors and matrices using bold font. $\mathbf{A}\mathbf{B}$
 denotes matrix multiplication, with $(\mathbf{A}\mathbf{B})_{ij}=\sum_{k=1}^\ell A_{ik}B_{kj}$
@@
 corresponding vertex in the mesh.
-There are several different methods for constructing the weight matrix $\mathbf{w}$, which are discussed in~\ref{section:implementation:laplace}.
+There are several different methods for constructing the weight matrix $\mathbf{w}$, which are discussed in~\ref{appendix:laplace}.
 The kernel matrix $\mathbf{Q}$ is given by
@@
 inside holes in the film. $\mathbf{\Lambda}$ is either a scalar or a vector defining the effective penetration depth at every included vertex in the mesh, and $\mathbf{\nabla}^2$
-is the Laplace operator, an $n\times n$ matrix defined such that $\mathbf{\nabla}^2\mathbf{f}$ computes the Laplacian $\nabla^2f(x,y)$ of a function $f(x,y)$ defined on the mesh  (see~\ref{section:implementation:laplace}).
+is the Laplace operator, an $n\times n$ matrix defined such that $\mathbf{\nabla}^2\mathbf{f}$ computes the Laplacian $\nabla^2f(x,y)$ of a function $f(x,y)$ defined on the mesh  (see~\ref{appendix:laplace}).
 
@@
 by matrix inversion or LU decomposition) for the unknown vector $\mathbf{g}$, the stream function inside the film.
-Since the stream function outside the film and inside holes in the film is already known, solving Eq.~\ref{eq:Heff_sub_num} gives us the stream function for the full mesh:
+Since the stream function outside the film and inside holes in the film is already known, solving Eq.~\ref{eq:Heff_sub_num} gives us the stream function for the full mesh.
+Defining $\mathbf{K} = \left(\mathbf{Q}\cdot\mathbf{w}-\mathbf{\Lambda}\cdot\mathbf{\nabla}^2\right)^{-1}$, we have
 
@@
     \mathbf{g} = \begin{cases}
-        \left(-[\mathbf{Q}\cdot\mathbf{w}-\mathbf{\Lambda}\cdot\mathbf{\nabla}^2]\right)^{-1}
+        -\mathbf{K}
         \left(\mathbf{h}_{z,\,\mathrm{applied}} - \sum_{\mathrm{holes}\,k}\mathbf{h}_{z,\,\mathrm{eff},\,k}\right)
@@
 
+If there is a vortex with flux $\Phi_j$ located in a film at position $\vec{r}_j$ indexed as mesh vertex $j$, then for each position $\vec{r}_i$ within that film, we add to the stream function $g_i$ the quantity $\mu_0^{-1}\Phi_jK_{ij} / M_{jj}$, where $K_{ij}$ is an element of the inverse matrix defined above, and $M_{jj}$ is an element of the ``mass matrix'' which assigns an effective area to the mesh vertex at which the vortex is located (see \ref{appendix:laplace} for the definition of the mass matrix).
+This process amounts to numerically inverting Eq.~\ref{eq:applied_to_stream_vortices}.
+
 Once the stream function $\mathbf{g}$ is known for the full mesh,
@@
 at any point in space can be computed from Eqs.~\ref{eq:field_from_kernel} and ~\ref{eq:kernels}.
+Multiply-connected films and multi-layer structures are solved as described in Sections~\ref{section:model:holes} and \ref{section:model:multilayer} respectively.
 
@@
 
-In this section we give a high-level overview of the \SuperScreen package. More detailed documentation and tutorials can be found online in [ref. for online documentation].
+In this section we give a high-level overview of the \SuperScreen package. Further details can be found in the online documentation~\cite{superscreen-rtd}.
 
@@
 
-\SuperScreen requires Python version 3.6 or later.
-The package is located in a public repository on GitHub~\cite{superscreen}, and a suite of unit tests is run automatically via GitHub Actions whenever a change or proposed change (Pull Request) is made to the \inline{main} branch of the repository.
-At the time of writing, the test suite is executed using Python versions 3.6, 3.7, 3.8, and 3.9, and the test coverage is XX\%.
-Any changes to the \inline{main} branch of the repository also trigger an automatic re-build of the online documentation, which is hosted by Read the Docs at superscreen.readthedocs.io [ref.
-for online documentation].
-Stable versions of the package are tagged on GitHub and uploaded to PyPI, the Python Package Index [ref for pypi].
+\SuperScreen requires Python version 3.6 - 3.9.
+The package is located in a public repository on GitHub~\cite{superscreen}, and a suite of unit tests is run automatically via the GitHub Actions continuous integration (CI) tool whenever a change or proposed change (Pull Request) is made to the \inline{main} branch of the repository.
+At the time of writing, the test suite is executed using Python versions 3.6 through 3.9, and the test coverage is $>95\%$.
+Any changes to the \inline{main} branch of the repository also trigger an automatic re-build of the online documentation, which is hosted by Read the Docs at \inline{superscreen.readthedocs.io}~\cite{superscreen-rtd}.
+Stable versions of the package are tagged on GitHub and uploaded to PyPI, the Python Package Index.
 The source code and documentation are covered by the MIT License.
@@
 param = Parameter(f, a=0, b=1)
-print(param)
-# Parameter<f(a=0, b=1)>
+print(param) # Parameter<f(a=0, b=1)>
 
 other_param = Parameter(f, a=2, b=3)
-print(other_param)
-# Parameter<f(a=2, b=3)>
-
-print(param(0, 0) == f(0, 0, a=0, b=1))
-# True
-print(other_param(1, 2) == f(1, 2, a=2, b=3))
-# True
+print(other_param) # Parameter<f(a=2, b=3)>
+
+print(param(0, 0) == f(0, 0, a=0, b=1)) # True
+print(other_param(1, 2) == f(1, 2, a=2, b=3)) # True
 
 param_squared = param ** 2
-print(param_squared)
-# CompositeParameter<(f(a=0, b=1) ** 2)>
-
-print(param_squared(3, 4) == f(3, 4, a=0, b=1) ** 2)
-# True
+print(param_squared) # CompositeParameter<(f(a=0, b=1) ** 2)>
+
+print(param_squared(3, 4) == f(3, 4, a=0, b=1) ** 2) # True
 print(
@@
     == 5 * f(5, 6, a=0, b=1) ** 2 / f(5, 6, a=2, b=3)
-)
-# True
+) # True
 \end{minted}
@@
 Each layer sits in a specified plane parallel to the $x-y$ plane and has its own effective penetration depth $\Lambda$, which can either be a constant or a \inline{superscreen.Parameter} that defines $\Lambda(x, y)$, the effective penetration depth as a function of position.
-The effective penetration depth $\Lambda$ can instead be defined in terms of a layer's London penetration depth $\lambda$ and its thickness $d$: $\Lambda=\lambda^2/d$, in which case the London penetration depth can be either a constant or a \inline{superscreen.Parameter}.
+Alternatively, the effective penetration depth $\Lambda$ can be defined in terms of a layer's London penetration depth $\lambda$ and its thickness $d$: $\Lambda=\lambda^2/d$, in which case the London penetration depth can be either a constant or a \inline{superscreen.Parameter}.
 
@@
 Abstract regions can be used to define a ``bounding box" around a structure.
-The \inline{superscreen.geometry} module provides functions for generating the underlying polygon vertices for simple geometries (circles and rectangles).
+The \inline{superscreen.geometry} module provides functions for generating the underlying polygon vertices for simple geometries (ellipses and rectangles).
 See Code Block~\ref{code:device} for an example of a function that creates a square or circular superconducting ring centered at the origin, with an effective penetration depth $\Lambda = 1\,\mu\mathrm{m}$.
@@
 First, an initial Delaunay mesh is created using \inline{meshpy}~\cite{Klockner}, which is a Python interface to Triangle~\cite{shewchuk96b, Shewchuk}, a fast compiled 2D mesh generation tool.
-Second (and optionally), the mesh can be further optimized using \inline{optimesh}~\cite{nico_schlomer_adam_dobrawy_2021}.
+Second (and optionally), the mesh is further optimized using \inline{optimesh}~\cite{nico_schlomer_adam_dobrawy_2021}.
 The goal of the mesh optimization step is to improve the quality of each triangular element in the mesh, where quality is defined as twice the ratio of the incircle radius to the circumcircle radius (quality $\leq1$, with equality for equilateral triangles).
@@
 See Code Block~\ref{code:mesh_generation} for a demonstration of \inline{Device.make_mesh()} and Figure~\ref{fig:ring_mesh} to view the resulting meshes both with and without \inline{optimesh} optimization.
-After the mesh has been generated, the matrices and vectors described in Section~\ref{section:implementation} can be computed and one can begin solving models.
+After the mesh has been generated, the matrices and vectors described in Section~\ref{section:implementation} are computed and one can begin solving models.
 
@@
 # min_triangles specifies the minimum number of mesh elements.
-min_triangles = 8000
+min_triangles = 8_000
 # optimesh_steps specifies the the number of iterations of
@@
 
-A \SuperScreen model consists of a \inline{Device}, a function or \inline{Parameter} that defines the applied magnetic field as a function of position $H_{z,\,\mathrm{applied}}(x, y, z)$, and a value for the current circulating around each hole in the device due to trapped flux (if any).
+A \SuperScreen model consists of 1) a \inline{Device} with a mesh, 2) a function or \inline{Parameter} that defines the applied magnetic field as a function of position $H_{z,\,\mathrm{applied}}(x, y, z)$, 3) a value for the current circulating around each hole in the device due to trapped flux, and 4) a collection of vortices $v$ located at positions $\vec{r}_v$ and carrying flux $\Phi_v$.
 These items serve as the inputs to \SuperScreen's main solver function, \inline{superscreen.solve()}, which implements the calculation outlined in Section~\ref{section:implementation}.
@@
 The output of \inline{superscreen.solve()} is a \inline{list} of \inline{superscreen.Solution} objects, with a length of 1 plus the number of iterations used for the iterative portion of the calculation.
-A \inline{Solution} encapsulates all of the information about a solved model: the \inline{Device}, applied field, circulating currents, and calculated stream functions and magnetic fields for all layers in the device.
+A \inline{Solution} encapsulates all of the information about a solved model: the \inline{Device}, applied field, circulating currents, vortices, and calculated stream functions and magnetic fields for all layers in the device.
 A \inline{Solution} also has methods for processing the simulation results, including:
@@
     \item{
+    \inline{Solution.interp_current_density()}: Evaluates the current density (sheet current) $\vec{J}(x, y)$ in each layer at arbitrary $(x, y)$ coordinates via interpolation.
+    }
+    \item{
     \inline{Solution.polygon_flux()}: Calculates the total flux through each polygon in the device (films, holes, and abstract regions).
+    }
+    \item{
+    \inline{Solution.polygon_fluxoid()}: Calculates the fluxoid for a specified polygonal region in the device. See \ref{secction:fluxoid} for more details.
     }
@@
 
-One may wish to solve many models involving the same device while varying other aspects of the model, for example sweeping the applied field, circulating currents, or some parameter of one or more layers in the device.
+One may wish to solve many models involving the same device while varying other aspects of the model, for example sweeping the applied field, circulating currents, vortex properties, or some parameter of one or more layers in the device.
 Fortunately, the mesh and large matrices described in Section~\ref{section:implementation} depend only on the geometry of the device parallel to the $x-y$ plane.
-This means that the same mesh and matrices can be re-used for models with different applied fields, circulating currents, layer heights (vertical positions), and penetration depths.
+This means that the same mesh and matrices can be re-used for models with different applied fields, circulating currents, vortex properties, layer heights (vertical positions), and penetration depths.
 
@@
     \item{
-    \inline{superscreen.plot_field_at_positions()}: Given a \inline{Solution}, plots the total field $\vec{H}(x, y, z_0)$ or $H_z(x, y, z_0)$ at any points in space (where $z_0$ is not equal to the vertical position of any of the layers in the device).
+    \inline{superscreen.plot_field_at_positions()}: Given a \inline{Solution}, plots the total field $\vec{H}(x, y, z)$ or $H_z(x, y, z)$ at an arbitrary set of positions $(x, y, z)$.
 
@@
 Two \inline{Devices} are equal if their name, layers, films, holes, and abstract regions are all equal.
-Two \inline{Solutions} are equal if their device, applied field, circulating currents, timestamp (time at which the solution was created), and all stream function and magnetic field arrays are equal.
+Two \inline{Solutions} are equal if their device, applied field, circulating currents, list of trapped vortices, timestamp (time at which the solution was created), and all stream function and magnetic field arrays are equal.
 Two \inline{Solutions} created at different times can also be compared using the  \inline{solution.equals()} method.
@@
 
-\section{Example application: Scanning SQUID susceptometry}
+\section{Example application: Scanning SQUID magnetometry}
 \label{section:application}
@@
 
-To model a SQUID susceptometry measurement, we first calculate $M_0$, the mutual inductance between the field coil and pickup loop in the absence of the sample.
+% To model a SQUID susceptometry measurement, we first calculate $M_0$, the mutual inductance between the field coil and pickup loop in the absence of the sample.
 This can be done by temporarily setting the sample layer effective penetration depth to a very large value such that it essentially does not screen the field from the field coil (in this case, we set $\Lambda = 10^5\,\mu\mathrm{m}$).
@@
 
-Once $M_0$ is known, we can ``turn on" the sample's diamagnetic response by setting its effective penetration depth $\Lambda$ to the desired value and compute $M(z, \Lambda)$ for a given vertical distance $z$ between the sample and the SQUID as described in the previous paragraph.
+% Once $M_0$ is known, we can ``turn on" the sample's diamagnetic response by setting its effective penetration depth $\Lambda$ to the desired value and compute $M(z, \Lambda)$ for a given vertical distance $z$ between the sample and the SQUID as described in the previous paragraph.
 The SQUID susceptibility signal is then $M(z, \Lambda) - M_0$, the change in mutual inductance between the field coil and pickup loop due to the presence of the sample (usually given in units of $\Phi_0/\mathrm{A}$, where $\Phi_0$ is the superconducting flux quantum).
@@
 
-% \begin{figure}[!h]
-% \centering
-% \begin{subfigure}{\textwidth}
-%   \centering
-%   \includegraphics[width=\linewidth]{examples/images/squid_susceptometry/squid_with_sample_currents_Lambda=1_00__um__z=-1_00__um.png}
-% %   \caption{Device polygons and mesh for the SQUID susceptometer model.}
-% %   \label{fig:squid_mesh}
-% \end{subfigure}%
-% \vspace{-15pt}
-% \begin{subfigure}{\textwidth}
-%   \centering
-%   \includegraphics[width=\linewidth]{examples/images/squid_susceptometry/squid_with_sample_currents_Lambda=10_00__um__z=-1_00__um.png}
-% %   \caption{Fractional change in flux though all polygons vs.
+% % \begin{figure}[!h]
+% % \centering
+% % \begin{subfigure}{\textwidth}
+% %   \centering
+% %   \includegraphics[width=\linewidth]{examples/images/squid_susceptometry/squid_with_sample_currents_Lambda=1_00__um__z=-1_00__um.png}
+% % %   \caption{Device polygons and mesh for the SQUID susceptometer model.}
+% % %   \label{fig:squid_mesh}
+% % \end{subfigure}%
+% % \vspace{-15pt}
+% % \begin{subfigure}{\textwidth}
+% %   \centering
+% %   \includegraphics[width=\linewidth]{examples/images/squid_susceptometry/squid_with_sample_currents_Lambda=10_00__um__z=-1_00__um.png}
+% % %   \caption{Fractional change in flux though all polygons vs.
 solver iteration with a current of $1\,\mathrm{mA}$ flowing in the field coil (\inline{fc}).
 The mutual inductance $M_0$ is given by the flux through the pickup loop (\inline{pl_hull}) divided by the field coil current.}
-% %   \label{fig:squid_convergence}
-% \end{subfigure}%
-% \vspace{-15pt}
-% \begin{subfigure}{\textwidth}
-%   \centering
-%   \includegraphics[width=\linewidth]{examples/images/squid_susceptometry/squid_with_sample_currents_Lambda=1_00__um__z=-10_00__um.png}
-% %   \caption{Fractional change in flux though all polygons vs.
+% % %   \label{fig:squid_convergence}
+% % \end{subfigure}%
+% % \vspace{-15pt}
+% % \begin{subfigure}{\textwidth}
+% %   \centering
+% %   \includegraphics[width=\linewidth]{examples/images/squid_susceptometry/squid_with_sample_currents_Lambda=1_00__um__z=-10_00__um.png}
+% % %   \caption{Fractional change in flux though all polygons vs.
 solver iteration with a current of $1\,\mathrm{mA}$ flowing in the field coil (\inline{fc}).
 The mutual inductance $M_0$ is given by the flux through the pickup loop (\inline{pl_hull}) divided by the field coil current.}
-% %   \label{fig:squid_convergence}
-% \end{subfigure}%
-% \caption{Left: Device polygons and mesh for the SQUID susceptometer model.
+% % %   \label{fig:squid_convergence}
+% % \end{subfigure}%
+% % \caption{Left: Device polygons and mesh for the SQUID susceptometer model.
 Right: Fractional change in flux though all polygons vs.
@@
 The mutual inductance $M_0$ is given by the flux through the pickup loop (\inline{pl_hull}) divided by the field coil current.}
-% % \label{fig:susceptometry}
-% \end{figure}
+% % % \label{fig:susceptometry}
+% % \end{figure}
 
@@
 
-There are two important limitations to the applicability of \SuperScreen and the matrix inversion method on which it is based~\cite{brandt_thin_2005}.
+There are three important limitations to the applicability of \SuperScreen and the matrix inversion method on which it is based~\cite{Brandt_Clem_2004,brandt_thin_2005}.
 First, strictly speaking all superconducting films should be in the 2D limit, with London penetration depth $\lambda$ less than film thickness $d$, such that the out-of-plane current density is approximately constant.
 There are cases where the model reproduces experimental results despite violation of this condition (e.g.
-the calculations in Section~\ref{section:application} and in~\cite{kirtley_scanning_2016,kirtley_response_2016}), but great care must be taking in interpreting results in these cases.
-Second, as a London model, Brandt's method assumes that all superconducting films behave linearly and without dissipation.
-Care should also be taken to ensure that for a given model the mesh is of sufficient density and quality that, to within the desired precision, the results of simulations do not depend on mesh size.
-
-Potential improvements to \SuperScreen include: more sophisticated mesh generation (e.g.
-automated local mesh refinement based on device geometry), automated determination of solution convergence for models with multiple layers, an improved interface for generating complex device geometries, and further optimization for memory and CPU efficiency (especially in the context of parallel processing).
+the calculations in Section~\ref{section:application} and in~\cite{kirtley_scanning_2016,kirtley_response_2016}), but care must be taking in interpreting results in these cases.
+Second, as a London model, Brandt and Clem's method assumes that all superconducting films behave linearly and without dissipation, and that the applied magnetic field and current density are below the film's critical field and critical current density.
+Third, while currents associated with vortices and flux trapped in holes can be modeled, \SuperScreen does not enforce fluxoid quantization or treat the energetics of vortex nucleation in films or fluxoid transitions in multiply-connected films.
+For further discussion of these topics in the context of the present model, see Refs.~\cite{Brandt_Clem_2004, Clem_Brandt_2005}.
+Finally, care should be taken to ensure that for a given model the mesh is of sufficient density and quality that, to within the desired precision, the results of simulations do not depend on mesh size.
+
+Potential improvements to \SuperScreen include: more complete treatment of multiply-connected superconductors~\cite{Clem_Brandt_2005}, more sophisticated mesh generation (e.g.
+automated local mesh refinement based on device geometry), automated determination of solution convergence for models with multiple layers, an improved interface for generating complex device geometries (for example using 2D constructive solid geometry, CSG), and further optimization for memory and CPU efficiency (especially in the context of parallel processing).
 
@@
 \section{Laplace operator}
-\label{section:implementation:laplace}
+\label{appendix:laplace}
 
@@
 $\mathbf{\nabla}^2\mathbf{g}=\mathbf{f}$~\cite{Reuter_Biasotti_Giorgi_Patane_Spagnuolo_2009}.
-As described in [Vaillant-Laplacian-2013] and [Laplacian-SGP-2014] the Laplace operator $\mathbf{\nabla}^2$ for a mesh is defined in terms of two matrices, the mass matrix $\mathbf{M}$ and the
+As described in Ref.~\cite{Crane_Vouga_2014}, the Laplace operator $\mathbf{\nabla}^2$ for a mesh is defined in terms of two matrices, the mass matrix $\mathbf{M}$ and the
 weak Laplacian matrix $\mathbf{L}$: $\mathbf{\nabla}^2 = \mathbf{M}^{-1}\mathbf{L}$.
@@
 $$
+
+% \section{Scaling with number of layers}
+% \label{section:scaling-layers}
+% The iterative method used to solve multi-layer structures (Section~\ref{section:model:multilayer}) is time-consuming and memory-intensive for models with a large mesh (many vertices $v$ and triangles $t$) and/or many layers $L$.
+As mentioned in Section~\ref{section:model:multilayer}, at each iteration of this process, we update the applied field $H_{z,\,\mathrm{applied}}(\vec{r}, z_\ell)$ at each layer $\ell$ based on the currents flowing in all other layers $m\neq\ell$, according to
+
+% \begin{equation}
+%     H_{z,\,\mathrm{applied}}(\vec{r}, z_\ell) \to
+%     H_{z,\,\mathrm{applied}}(\vec{r}, z_\ell)
+%     + \sum_{m\neq\ell}
+%     \int_{S_m} Q_z(\vec{r},\vec{r}')g_m(\vec{r}')\,\mathrm{d}^2r',
+%     \label{eq:iterative}
+% \end{equation}
+% where $S_m$ is surface of all films in layer $m$ and $g_m$ is the stream function for layer $m$.
+For a model with $L$ layers, at each iteration Eq.~\ref{eq:iterative} requires the calculation of $\binom{L}{2} = L(L-1)/2$ kernel matrices $\mathbf{Q_z}$, each of which is a dense $v\times t$ floating point matrix.
+For a mesh with $t=10,000$ triangles, each of these $\mathbf{Q_z}$ matrices is 800 MB.
+Furthermore, each iteration requires performing $2\binom{L}{2} = L(L-1)$ sums involving $\mathbf{Q_z}\cdot\mathbf{g}_m$, where $\mathbf{g}_m$ is the $n\times1$ vector defining the stream function in layer $m$ evaluated at the center of each triangle in the mesh.
+
+% To avoid redundant computation at each iteration and running out of memory during the iterative process, the $\mathbf{Q_z}$ matrices are computed once during the first iteration, cached to a temporary directory on disk, and loaded from disk during subsequent iterations, such that only a single $\mathbf{Q_z}$ is in memory at any given time.
+If running \SuperScreen on a machine with both hard disk (HDD) and solid state disk (SSD) storage, one should ensure that Python uses a temporary directory located on a solid state disk to avoid a significant performance penalty due to hard disk read/write speeds.
+See the documentation for the \inline{tempfile} module of the Python standard library for more details.
+Both the amount of computation needed per iteration and the number of iterations required to reach a certain level of convergence (quantified, for example, by the fractional change in flux through each polygon in the model from one iteration to the next)
 
@@
 See the ``Multi-Node Ray" section of the \inline{ray} documentation for more details~\cite{ray-docs}.
+% Some applications of \SuperScreen may be ``embarrassingly parallel'' in the sense that all calls to \inline{superscreen.solve()} are completely independent.
+One such application is the scanning SQUID susceptometry simulation shown in Section~\ref{section:application}.
+In such cases, it may be simpler to avoid using \inline{ray} for shared memory and run many
 

### 2021-10-21 examples/scripts/disk.py
local updates

@@ -1,139 +1,0 @@
-import os
-import logging
-
-import numpy as np
-
-import superscreen as sc
-import superscreen.geometry as geo
-
-from plot_solutions import plot_solutions
-
-
-def make_disk(Lambda=1, radius=5, length_units="um"):
-    layers = [
-        sc.Layer("base", Lambda=Lambda, z0=0),
-    ]
-    films = [
-        sc.Polygon(
-            "disk",
-            layer="base",
-            points=geo.circle(radius, points=401),
-        ),
-    ]
-    abstract_regions = [
-        sc.Polygon(
-            "bounding_box",
-            layer="base",
-            points=geo.square(2 * (radius + 1), points_per_side=11),
-        ),
-    ]
-    disk = sc.Device(
-        "disk",
-        layers=layers,
-        films=films,
-        abstract_regions=abstract_regions,
-        length_units=length_units,
-    )
-    return disk
-
-
-def Lambda_linear_ramp(x, y, xmin=0, xmax=1, Lambda0=0, Lambda1=0):
-    Lambda = Lambda0 + (Lambda1 - Lambda0) * ((x - xmin) / (xmax - xmin))
-    return Lambda
-
-
-if __name__ == "__main__":
-
-    logging.basicConfig(level=logging.INFO)
-
-    imagedir = os.path.join(os.pardir, "images", "disk")
-    os.makedirs(imagedir, exist_ok=True)
-
-    disk_radius = 5
-    length_units = "um"
-    # Plot the fields and currents for this value of Lambda
-    show_Lambda = 1.0
-
-    # Make the disk Device
-    disk = make_disk(radius=disk_radius, length_units=length_units)
-    disk.make_mesh(min_triangles=8000, optimesh_steps=100)
-
-    # Plot the disk's mesh and polygons
-    ax = disk.plot_mesh(figsize=(6, 6), color="k", alpha=0.5)
-    ax = disk.plot_polygons(ax=ax, linewidth=4)
-    npoints = disk.points.shape[0]
-    ntriangles = disk.triangles.shape[0]
-    ax.set_title(f"{disk.name} mesh:\n{npoints} points, {ntriangles} triangles")
-    ax.figure.savefig(
-        os.path.join(imagedir, f"{disk.name}_mesh.png"),
-        bbox_inches="tight",
-    )
-
-    # Define a uniform applied field.
-    applied_field = sc.sources.ConstantField(1)
-    field_units = "mT"
-
[…]

### 2021-10-21 examples/scripts/ring.py

@@ -1,290 +1,0 @@
-import os
-import logging
-
-import numpy as np
-
-import superscreen as sc
-import superscreen.geometry as geo
-
-from plot_solutions import plot_solutions
-
-
-def make_ring(
-    inner_radius=2.5,
-    outer_radius=5,
-    Lambda=1,
-    length_units="um",
-    square=False,
-):
-    if square:
-        name = "square_ring"
-        outer_points = geo.square(
-            outer_radius * 2, points_per_side=60
-        )
-        inner_points = geo.square(
-            inner_radius * 2, points_per_side=20
-        )
-        bbox_points = geo.square(
-            outer_radius * 2 * 1.4, points_per_side=5
-        )
-    else:
-        name = "circular_ring"
-        outer_points = geo.circle(outer_radius)
-        inner_points = geo.circle(inner_radius)
-        bbox_points = geo.circle(outer_radius * 1.4, points=21)
-
-    layers = [sc.Layer("base", Lambda=Lambda, z0=0)]
-    films = [sc.Polygon("ring", layer="base", points=outer_points)]
-    holes = [sc.Polygon("hole", layer="base", points=inner_points)]
-    abstract_regions = [
-        sc.Polygon("bounding_box", layer="base", points=bbox_points),
-    ]
-    return sc.Device(
-        name,
-        layers=layers,
-        films=films,
-        holes=holes,
-        abstract_regions=abstract_regions,
-        length_units=length_units,
-    )
-
-
-def layer_updater(layer, Lambda=None):
-    if layer.name == "base":
-        layer.Lambda = Lambda
-    return layer
-
-
-def vortex_field(x, y, z, vortex_position=(0, 0, 0), nPhi0=1):
-    """The field from an isolated vortex.
-
-    Args:
-        x, y, z: Position coordinates.
-        vortex_position: (x, y, z) position of the vortex.
-        nPhi0: Number of flux quanta contained in the vortex.
-
-    Returns:
-        Magnetic field in units of Phi_0 / (length_units)^2,
-        where length_units are the units of x, y, z, etc.
-    """
-    xv, yv, zv = vortex_position
-    xp = x - xv
-    yp = y - yv
-    zp = z - zv
-    Hz0 = zp / (xp ** 2 + yp ** 2 + zp ** 2) ** (3 / 2) / (2 * np.pi)
-    return nPhi0 * Hz0
-
-
-if __name__ == "__main__":
-
[…]

### 2021-10-21 main.tex
Updates from Overleaf

@@
 
-def make_ring(
-    inner_radius=2.5,
-    outer_radius=5,
-    Lambda=1,
-    length_units="um",
-    square=False,
-):
+def make_ring(inner_radius=2.5, outer_radius=5, Lambda=1, square=False):
     if square:
-        name = "square_ring"
-        outer = geo.square(outer_radius * 2, points_per_side=60)
-        inner = geo.square(inner_radius * 2, points_per_side=20)
-        bbox = geo.square(outer_radius * 2 * 1.4, points_per_side=5)
+        outer_points = geo.square(2 * outer_radius, points_per_side=150)
+        inner_points = geo.square(2 * inner_radius, points_per_side=75)
+        bbox = geo.square(1.25 * 2 * outer_radius, points_per_side=10)
     else:
-        name = "circular_ring"
-        outer_points = geo.circle(outer_radius)
-        inner_points = geo.circle(inner_radius)
-        bbox = geo.circle(outer_radius * 1.4, points=21)
-
+        outer_points = geo.circle(outer_radius, points=500)
+        inner_points = geo.circle(inner_radius, points=300)
+        bbox = geo.circle(1.4 * outer_radius, points=50)
     layers = [sc.Layer("base", Lambda=Lambda, z0=0)]
@@
     holes = [sc.Polygon("hole", layer="base", points=inner_points)]
-    abstract_regions = [
-        sc.Polygon("bounding_box", layer="base", points=bbox),
-    ]
+    abstract_regions = [sc.Polygon("bbox", layer="base", points=bbox)]
     return sc.Device(
-        name,
+        "ring",
         layers=layers,
@@
         abstract_regions=abstract_regions,
-        length_units=length_units,
+        length_units="um",
     )
@@
 \begin{minted}[fontsize=\small]{python}
+import matplotlib.pyplot as plt
+
+fig, axes = plt.subplots(2, 2, figsize=(8, 8), constrained_layout=True)
+# Create the Devices
+ring = make_ring(square=False)
+square_ring = make_ring(square=True)
 # min_triangles specifies the minimum number of mesh elements.
-min_triangles = 8_000
+min_triangles = 12000
 # optimesh_steps specifies the the number of iterations of
@@
 # Set optimesh_steps=None to disable optimesh optimization.
-optimesh_steps = 400
+optimesh_steps = (None, 40)
 # For more meshing options, see the docstring for Device.make_mesh().
-
-for square in (False, True):
-    ring = make_ring(square=square)
-    ring.make_mesh(
-        min_triangles=min_triangles,
-        optimesh_steps=optimesh_steps,
-    )
-    ax = ring.plot_mesh(figsize=(6, 6), color="k", alpha=0.5)
-    ax = ring.plot_polygons(ax=ax)
+for opt_steps, row in zip(optimesh_steps, axes):
+    title = f"optimesh_steps = {opt_steps}"
+    for device, ax in zip((ring, square_ring), row):
+        # Generate the mesh
+        device.make_mesh(min_triangles=min_triangles, optimesh_steps=opt_steps)
+        # Visualize the mesh
+        device.plot_mesh(ax=ax, color="gray", linewidth=0.75)
+        device.plot_polygons(ax=ax, linewidth=3, legend=False)
+        ax.axis("off")
+        ax.set_title(title, fontfamily="monospace")
+axes[0, 0].legend(loc="best")
 \end{minted}
@@
     \item{
-    \inline{Solution.current_density()}: Interpolates the stream functions to a rectangular grid and calculates the current density (sheet current) $\vec{J}(x, y)$ in each layer using Eq.~\ref{eq:stream}.
+    \inline{Solution.grid_current_density()}: Interpolates the stream functions to a rectangular grid and calculates the current density (sheet current) $\vec{J}(x, y)$ in each layer using Eq.~\ref{eq:stream}.
     }

### 2021-10-21 main.tex
Updates from Overleaf

@@
 # For more meshing options, see the docstring for Device.make_mesh().
-for opt_steps, row in zip(optimesh_steps, axes):
+for row, opt_steps in zip(axes, optimesh_steps):
     title = f"optimesh_steps = {opt_steps}"
-    for device, ax in zip((ring, square_ring), row):
+    for ax, device in zip(row, (ring, square_ring)):
         # Generate the mesh

### 2021-10-21 main.tex
Updates from Overleaf

@@
 
-fig, axes = plt.subplots(2, 2, figsize=(8, 8), constrained_layout=True)
+fig, axes = plt.subplots(2, 2, figsize=(8, 8), facecolor="w", constrained_layout=True)
+axlist = list(axes.flat)
 # Create the Devices
@@
 # For more meshing options, see the docstring for Device.make_mesh().
-for row, opt_steps in zip(axes, optimesh_steps):
-    title = f"optimesh_steps = {opt_steps}"
-    for ax, device in zip(row, (ring, square_ring)):
+for row, device in zip(axes, (ring, square_ring)):
+    for ax, opt_steps in zip(row, optimesh_steps):
         # Generate the mesh
@@
         device.plot_polygons(ax=ax, linewidth=3, legend=False)
+        label = "abcd"[axlist.index(ax)]
+        title = f"{label}) optimesh_steps = {opt_steps}"
+        ax.set_title(title, fontsize=16, fontfamily="monospace")
         ax.axis("off")
-        ax.set_title(title, fontfamily="monospace")
-axes[0, 0].legend(loc="best")
+axlist[0].legend(loc="best")
 \end{minted}
@@
 
-\begin{figure}[!h]
+\begin{figure}[h]
     \centering
-\begin{subfigure}{.235\textwidth}
-  \centering
-  \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_mesh.png}
-  \caption{\inline{optimesh_steps=400}.}
-  \label{fig:circular_ring_mesh}
-\end{subfigure}%
-\begin{subfigure}{.235\textwidth}
-  \centering
-  \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_mesh_no_optimesh.png}
-  \caption{\inline{optimesh_steps=None}.}
-  \label{fig:circular_ring_mesh_no_opt}
-\end{subfigure}%
-\begin{subfigure}{.235\textwidth}
-  \centering
-  \includegraphics[width=\linewidth]{examples/images/ring/square_ring_mesh.png}
-  \caption{\inline{optimesh_steps=400}.}
-  \label{fig:square_ring_mesh}
-\end{subfigure}
-\begin{subfigure}{.235\textwidth}
-  \centering
-  \includegraphics[width=\linewidth]{examples/images/ring/square_ring_mesh_no_optimesh.png}
-  \caption{\inline{optimesh_steps=None}.}
-  \label{fig:square_ring_mesh_no_opt}
-\end{subfigure}
-\caption{Device geometry and mesh for a circular (a, b) and square ring (c, d) generated using Code Blocks~\ref{code:device} and \ref{code:mesh_generation}, with (a, c) and without (b, d) \inline{optimesh} optimization.}
-\label{fig:ring_mesh}
+    \includegraphics[width=0.55\textwidth]{examples/images/mesh.pdf}
+    \caption{Computational meshes for }
+    \label{fig:mesh}
 \end{figure}
+
+% \begin{figure}[!h]
+% \centering
+% \begin{subfigure}{.235\textwidth}
+%   \centering
+%   \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_mesh.png}
+%   \caption{\inline{optimesh_steps=400}.}
+%   \label{fig:circular_ring_mesh}
+% \end{subfigure}%
+% \begin{subfigure}{.235\textwidth}
+%   \centering
+%   \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_mesh_no_optimesh.png}
+%   \caption{\inline{optimesh_steps=None}.}
+%   \label{fig:circular_ring_mesh_no_opt}
+% \end{subfigure}%
+% \begin{subfigure}{.235\textwidth}
+%   \centering
+%   \includegraphics[width=\linewidth]{examples/images/ring/square_ring_mesh.png}
+%   \caption{\inline{optimesh_steps=400}.}
+%   \label{fig:square_ring_mesh}
+% \end{subfigure}
+% \begin{subfigure}{.235\textwidth}
+%   \centering
+%   \includegraphics[width=\linewidth]{examples/images/ring/square_ring_mesh_no_optimesh.png}
+%   \caption{\inline{optimesh_steps=None}.}
+%   \label{fig:square_ring_mesh_no_opt}
+% \end{subfigure}
+% \caption{Device geometry and mesh for a circular (a, b) and square ring (c, d) generated using Code Blocks~\ref{code:device} and \ref{code:mesh_generation}, with (a, c) and without (b, d) \inline{optimesh} optimization.}
+% \label{fig:ring_mesh}
+% \end{figure}
 

### 2021-10-21 main.tex
Updates from Overleaf

@@
 If no \inline{optimesh} optimization is done, then every polygon vertex is guaranteed to be a mesh vertex.
-
-See Code Block~\ref{code:mesh_generation} for a demonstration of \inline{Device.make_mesh()} and Figure~\ref{fig:ring_mesh} to view the resulting meshes both with and without \inline{optimesh} optimization.
+See Code Block~\ref{code:mesh_generation} for a demonstration of \inline{Device.make_mesh()} and Figure~\ref{fig:mesh} to view the resulting meshes both with and without \inline{optimesh} optimization.
 After the mesh has been generated, the matrices and vectors described in Section~\ref{section:implementation} are computed and one can begin solving models.
@@
 
-fig, axes = plt.subplots(2, 2, figsize=(8, 8), facecolor="w", constrained_layout=True)
-axlist = list(axes.flat)
+fig, axes = plt.subplots(2, 2, figsize=(8, 8), constrained_layout=True)
 # Create the Devices
@@
     for ax, opt_steps in zip(row, optimesh_steps):
-        # Generate the mesh
+        # Generate and visualize the mesh
         device.make_mesh(min_triangles=min_triangles, optimesh_steps=opt_steps)
-        # Visualize the mesh
         device.plot_mesh(ax=ax, color="gray", linewidth=0.75)
         device.plot_polygons(ax=ax, linewidth=3, legend=False)
-        label = "abcd"[axlist.index(ax)]
-        title = f"{label}) optimesh_steps = {opt_steps}"
-        ax.set_title(title, fontsize=16, fontfamily="monospace")
-        ax.axis("off")
-axlist[0].legend(loc="best")
 \end{minted}
@@
     \centering
-    \includegraphics[width=0.55\textwidth]{examples/images/mesh.pdf}
-    \caption{Computational meshes for }
+    \includegraphics[width=0.6\textwidth]{examples/images/mesh.pdf}
+    \caption{Computational meshes for circular (a, b) and square (c, d) rings, without (a, c) and with (b, d) \inline{optimesh} optimization, generated using Code Block~\ref{code:mesh_generation}.
+The bounding box (\inline{bbox}) is shown in purple, the ring's outer edge (\inline{ring}) is shown in red, and the ring's inner edge (\inline{hole}) is shown in blue.
+Note that optimizing the mesh does not change the total number of vertices or triangles, but tends to make the triangle density more uniform across the mesh.
+In this case, all four meshes (a-d) contain around 6,000 points and 12,000 triangles.}
     \label{fig:mesh}

### 2021-10-21 main.tex
Updates from Overleaf

@@
 
-fig, axes = plt.subplots(2, 2, figsize=(8, 8), constrained_layout=True)
+fig, axes = plt.subplots(2, 2, figsize=(6, 6), constrained_layout=True)
 # Create the Devices

### 2021-10-21 main.tex
Updates from Overleaf

@@
 The bounding box (\inline{bbox}) is shown in purple, the ring's outer edge (\inline{ring}) is shown in red, and the ring's inner edge (\inline{hole}) is shown in blue.
-Note that optimizing the mesh does not change the total number of vertices or triangles, but tends to make the triangle density more uniform across the mesh.
+Note that optimizing the mesh does not change the total number of vertices or triangles, but tends to make the triangle size and density more uniform across the mesh.
 In this case, all four meshes (a-d) contain around 6,000 points and 12,000 triangles.}

### 2021-10-21 main.tex

@@
 
-\begin{figure}[!h]
+\begin{figure}
     \centering
-\begin{subfigure}{.235\textwidth}
-  \centering
-  \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_uniform_plot_currents.png}
-  \caption{Uniform applied field.}
-  \label{fig:circular_ring_plot_currents}
-\end{subfigure}
-\begin{subfigure}{.235\textwidth}
-  \centering
-  \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_uniform_plot_fields.png}
-  \caption{Uniform applied field.}
-  \label{fig:circular_ring_plot_fields}
-\end{subfigure}
-\begin{subfigure}{.235\textwidth}
-  \centering
-  \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_circ_plot_currents.png}
-  \caption{Trapped flux.}
-  \label{fig:square_ring_plot_currents}
-\end{subfigure}
-\begin{subfigure}{.235\textwidth}
-  \centering
-  \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_circ_plot_fields.png}
-  \caption{Trapped flux.}
-  \label{fig:square_ring_plot_fields}
-\end{subfigure}
-
-\caption{Sheet current $\vec{J}$ (a, c) and magnetic field $\mu_0H_z$ (b, d) distributions for the circular ring with a uniform field of 0.25 mT applied out-of-plane (a, b) and a circulating current of 1 mA (c, d) calculated using Code Block~\ref{code:ring_circulating_current}.}
-\label{fig:ring_plot_fields_currents}
+    \includegraphics[width=\textwidth]{examples/images/square_ring_results.png}
+    \caption{Caption}
+    \label{fig:square-ring-results}
 \end{figure}
+
+% \begin{figure}[!h]
+% \centering
+% \begin{subfigure}{.235\textwidth}
+%   \centering
+%   \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_uniform_plot_currents.png}
+%   \caption{Uniform applied field.}
+%   \label{fig:circular_ring_plot_currents}
+% \end{subfigure}
+% \begin{subfigure}{.235\textwidth}
+%   \centering
+%   \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_uniform_plot_fields.png}
+%   \caption{Uniform applied field.}
+%   \label{fig:circular_ring_plot_fields}
+% \end{subfigure}
+% \begin{subfigure}{.235\textwidth}
+%   \centering
+%   \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_circ_plot_currents.png}
+%   \caption{Trapped flux.}
+%   \label{fig:square_ring_plot_currents}
+% \end{subfigure}
+% \begin{subfigure}{.235\textwidth}
+%   \centering
+%   \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_circ_plot_fields.png}
+%   \caption{Trapped flux.}
+%   \label{fig:square_ring_plot_fields}
+% \end{subfigure}
+
+% \caption{Sheet current $\vec{J}$ (a, c) and magnetic field $\mu_0H_z$ (b, d) distributions for the circular ring with a uniform field of 0.25 mT applied out-of-plane (a, b) and a circulating current of 1 mA (c, d) calculated using Code Block~\ref{code:ring_circulating_current}.}
+% \label{fig:ring_plot_fields_currents}
+% \end{figure}
 

### 2021-10-21 main.tex
Updates from Overleaf

@@
     \centering
-    \includegraphics[width=\textwidth]{examples/images/square_ring_results.png}
-    \caption{Caption}
+    \includegraphics[width=0.6\textwidth]{examples/images/square_ring_results.png}
+    \caption{Sheet current $\vec{J}(x, y)$ and out-of-plane magnetic field $\mu_0H_z(x, y)$ evaluated in the plane of a square ring with effective penetration depth $\Lambda=1\,\mu\mathrm{m}$ subject to a uniform applied field of 0.5 mT (a, b) and trapped flux inducing a circulating current of 1 mA (c, d).
+The sub-figures show the output of \inline{Solution.plot_currents()} (a, c) and \inline{Solution.plot_fields()} (b, d).
+For the current plots (a, c), the colorscale indicates the magnitude of the sheet current (or current density), $|\vec{J}|$, and the direction is indicated by the white streamlines.}
     \label{fig:square-ring-results}

### 2021-10-21 main.tex

@@
 The sub-figures show the output of \inline{Solution.plot_currents()} (a, c) and \inline{Solution.plot_fields()} (b, d).
-For the current plots (a, c), the colorscale indicates the magnitude of the sheet current (or current density), $|\vec{J}|$, and the direction is indicated by the white streamlines.}
+For the current plots (a, c), the color-scale indicates the magnitude of the sheet current (or current density), $|\vec{J}|$, and the direction is indicated by the white streamlines.}
     \label{fig:square-ring-results}

### 2021-10-21 main.tex
Updates from Overleaf

--- 2021-10-21 main.tex
@@
 
-If there is a vortex with flux $\Phi_j$ located in a film at position $\vec{r}_j$ indexed as mesh vertex $j$, then for each position $\vec{r}_i$ within that film, we add to the stream function $g_i$ the quantity $\mu_0^{-1}\Phi_jK_{ij} / M_{jj}$, where $K_{ij}$ is an element of the inverse matrix defined above, and $M_{jj}$ is an element of the ``mass matrix'' which assigns an effective area to the mesh vertex at which the vortex is located (see \ref{appendix:laplace} for the definition of the mass matrix).
-This process amounts to numerically inverting Eq.~\ref{eq:applied_to_stream_vortices}.
+If there is a vortex containing flux $\Phi_j$ located in a film at position $\vec{r}_j$ indexed as mesh vertex $j$, then for each position $\vec{r}_i$ within that film, we add to the stream function $g_i$ the quantity $\mu_0^{-1}\Phi_jK_{ij} / M_{jj}$, where $K_{ij}$ is an element of the inverse matrix defined above, and $M_{jj}$ is an element of the ``mass matrix'' which assigns an effective area to the mesh vertex at which the vortex is located (see \ref{appendix:laplace} for the definition of the mass matrix).
+This process amounts to numerically inverting Eq.~\ref{eq:applied_to_stream_vortices} as described in Ref.~\cite{brandt_thin_2005}.
 
@@
 
-\SuperScreen requires Python version 3.6 - 3.9.
+\SuperScreen requires Python version 3.6--3.9.
 The package is located in a public repository on GitHub~\cite{superscreen}, and a suite of unit tests is run automatically via the GitHub Actions continuous integration (CI) tool whenever a change or proposed change (Pull Request) is made to the \inline{main} branch of the repository.
 At the time of writing, the test suite is executed using Python versions 3.6 through 3.9, and the test coverage is $>95\%$.
-Any changes to the \inline{main} branch of the repository also trigger an automatic re-build of the online documentation, which is hosted by Read the Docs at \inline{superscreen.readthedocs.io}~\cite{superscreen-rtd}.
+Any changes to the \inline{main} branch of the repository also trigger an automatic re-build of the online documentation, which is located at \inline{superscreen.readthedocs.io}~\cite{superscreen-rtd}.
 Stable versions of the package are tagged on GitHub and uploaded to PyPI, the Python Package Index.
@@
 print(param) # Parameter<f(a=0, b=1)>
-
 other_param = Parameter(f, a=2, b=3)
 print(other_param) # Parameter<f(a=2, b=3)>
-
 print(param(0, 0) == f(0, 0, a=0, b=1)) # True
 print(other_param(1, 2) == f(1, 2, a=2, b=3)) # True
-
 param_squared = param ** 2
 print(param_squared) # CompositeParameter<(f(a=0, b=1) ** 2)>
-
-print(param_squared(3, 4) == f(3, 4, a=0, b=1) ** 2) # True
 print(
@@
 See Code Block~\ref{code:mesh_generation} for a demonstration of \inline{Device.make_mesh()} and Figure~\ref{fig:mesh} to view the resulting meshes both with and without \inline{optimesh} optimization.
-After the mesh has been generated, the matrices and vectors described in Section~\ref{section:implementation} are computed and one can begin solving models.
+After the mesh has been generated, the geometry-dependent matrices and vectors described in Section~\ref{section:implementation} are computed and one can begin solving models.
 
@@
 
-fig, axes = plt.subplots(2, 2, figsize=(6, 6), constrained_layout=True)
+fig, axes = plt.subplots(1, 4, figsize=(14, 5), constrained_layout=True)
 # Create the Devices
@@
 # For more meshing options, see the docstring for Device.make_mesh().
-for row, device in zip(axes, (ring, square_ring)):
+for row, device in zip(axes.reshape(2, 2), (ring, square_ring)):
     for ax, opt_steps in zip(row, optimesh_steps):
@@
 \end{minted}
-\captionof{listing}{Generating and visualizing the computational mesh.}
+\captionof{listing}{Generating and visualizing the computational mesh. See Figure~\ref{fig:mesh} to view the resulting meshes.}
 \label{code:mesh_generation}
@@
 
-\begin{figure}[h]
+\begin{figure}
     \centering
-    \includegraphics[width=0.6\textwidth]{examples/images/mesh.pdf}
+    \includegraphics[width=\textwidth]{examples/images/mesh.pdf}
     \caption{Computational meshes for circular (a, b) and square (c, d) rings, without (a, c) and with (b, d) \inline{optimesh} optimization, generated using Code Block~\ref{code:mesh_generation}.
 The bounding box (\inline{bbox}) is shown in purple, the ring's outer edge (\inline{ring}) is shown in red, and the ring's inner edge (\inline{hole}) is shown in blue.
-Note that optimizing the mesh does not change the total number of vertices or triangles, but tends to make the triangle size and density more uniform across the mesh.
+Note that optimizing the mesh does not change the total number of vertices or triangles, but does tend to make the triangle size and density more uniform across the mesh.
 In this case, all four meshes (a-d) contain around 6,000 points and 12,000 triangles.}
@@
 \end{figure}
-
-% \begin{figure}[!h]
-% \centering
-% \begin{subfigure}{.235\textwidth}
-%   \centering
-%   \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_mesh.png}
-%   \caption{\inline{optimesh_steps=400}.}
-%   \label{fig:circular_ring_mesh}
-% \end{subfigure}%
-% \begin{subfigure}{.235\textwidth}
-%   \centering
-%   \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_mesh_no_optimesh.png}
-%   \caption{\inline{optimesh_steps=None}.}
-%   \label{fig:circular_ring_mesh_no_opt}
-% \end{subfigure}%
-% \begin{subfigure}{.235\textwidth}
-%   \centering
-%   \includegraphics[width=\linewidth]{examples/images/ring/square_ring_mesh.png}
-%   \caption{\inline{optimesh_steps=400}.}
-%   \label{fig:square_ring_mesh}
-% \end{subfigure}
-% \begin{subfigure}{.235\textwidth}
-%   \centering
-%   \includegraphics[width=\linewidth]{examples/images/ring/square_ring_mesh_no_optimesh.png}
-%   \caption{\inline{optimesh_steps=None}.}
-%   \label{fig:square_ring_mesh_no_opt}
-% \end{subfigure}
-% \caption{Device geometry and mesh for a circular (a, b) and square ring (c, d) generated using Code Blocks~\ref{code:device} and \ref{code:mesh_generation}, with (a, c) and without (b, d) \inline{optimesh} optimization.}
-% \label{fig:ring_mesh}
-% \end{figure}
 
@@
 \begin{minted}[fontsize=\small]{python}
-# Simulate the response to a uniform applied field of 0.25 mT
-applied_field = sc.sources.ConstantField(0.25)
+import numpy as np
+
+# Simulate the response of the square ring to a uniform applied field of 0.5 mT
+applied_field = sc.sources.ConstantField(0.5)
 field_units = "mT"
-
 solutions = sc.solve(
-    device=ring,
-    applied_field=applied_field,
-    field_units=field_units,
+    device=square_ring, applied_field=applied_field, field_units=field_units
 )
-assert len(solutions) == 1 # Since there is only one layer
-uniform_field = solutions[-1]
-
-# Simulate a current circulating around the hole in the ring.
-circulating_currents = {"hole": "1 mA"}
-
-solutions = sc.solve(
-    device=ring,
-    applied_field=None,
-    circulating_currents=circulating_currents
-)
-assert len(solutions) == 1 # Since there is only one layer
-trapped_flux = solutions[-1]
-
-for solution in (uniform_field, trapped_flux):
-    solution.plot_currents(
-        figsize=(6, 7), cross_section_ys=[0], units="mA/um",
-    )
-    solution.plot_fields(figsize=(6, 7), cross_section_ys=[0])
+assert len(solutions) == 1 # Since there is only one layer in this Device
+uniform_field_solution = solutions[-1]
+
+# Simulate a current circulating around the hole in the ring
+# (with no applied field).
+trapped_flux_solution = sc.solve(
+    device=square_ring, circulating_currents=dict(hole="1 mA"),
+)[-1]
+
+# Specify a sequence of (x, y) coordinates to plot cross-sections
+# of the simulated currents and fields.
+xs = np.linspace(-5.5, 5.5, 201) # [microns]
+cross_sections = [ # Two sets of [x, y] coordinates
+    np.stack([xs, xs], axis=1), # diagonal cross-section
+    np.stack([xs, np.zeros_like(xs)], axis=1), # horizontal cross-section
+]
+for solution in (uniform_field_solution, trapped_flux_solution):
+    solution.plot_currents(cross_section_coords=cross_sections, units="mA/um")
+    solution.plot_fields(cross_section_coords=cross_sections)
 \end{minted}
-\captionof{listing}{Solves for the current and magnetic field distributions for the \inline{ring} device given a uniform applied field, and circulating current with no applied field.}
+\captionof{listing}{Solves for the current and magnetic field distributions for the \inline{square_ring} device given a uniform applied field, and circulating current with no applied field, and plots the resulting sheet current and field.}
 \label{code:ring_circulating_current}
@@
 
-Code Block~\ref{code:ring_circulating_current} solves two models involving the \inline{ring} device.
+Code Block~\ref{code:ring_circulating_current} solves two models involving the \inline{square_ring} device, which was generated using Code Blocks~\ref{code:device} and \ref{code:mesh_generation}.
 First, Meissner screening of a spatially uniform applied out-of-plane magnetic field and second, the response of the ring to trapped flux with an associated circulating current of 1 mA (with no applied magnetic field).
-The resulting sheet current and magnetic field distributions can be visualized using the \inline{plot_current()} and \inline{plot_fields()} methods, which produce the images shown in Figure~\ref{fig:ring_plot_fields_currents}.
+The resulting sheet current and magnetic field distributions (calculated using the optimized mesh shown in Figure~\ref{fig:mesh}d) can be visualized using the \inline{plot_currents()} and \inline{plot_fields()} methods, which produce the images shown in Figure~\ref{fig:square-ring-results}.
 
@@
     \includegraphics[width=\textwidth]{examples/images/square_ring_results.png}
-    \caption{Caption}
+    \caption{Sheet current $\vec{J}(x, y)$ and out-of-plane magnetic field $\mu_0H_z(x, y)$ evaluated in the plane of a square ring with effective penetration depth $\Lambda=1\,\mu\mathrm{m}$ subject to a uniform applied field of 0.5 mT (a, b) or trapped flux inducing a circulating current of 1 mA (c, d).
+The sub-figures show the output of \inline{Solution.plot_currents()} (a, c) and \inline{Solution.plot_fields()} (b, d), as shown in Code Block~\ref{code:ring_circulating_current}.
+For the current plots (a, c), the color-scale indicates the magnitude of the sheet current (or current density), $|\vec{J}|$, and the direction is indicated by the white streamlines.}
     \label{fig:square-ring-results}
 \end{figure}
-
-% \begin{figure}[!h]
-% \centering
-% \begin{subfigure}{.235\textwidth}
-%   \centering
-%   \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_uniform_plot_currents.png}
-%   \caption{Uniform applied field.}
-%   \label{fig:circular_ring_plot_currents}
-% \end{subfigure}
-% \begin{subfigure}{.235\textwidth}
-%   \centering
-%   \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_uniform_plot_fields.png}
-%   \caption{Uniform applied field.}
-%   \label{fig:circular_ring_plot_fields}
-% \end{subfigure}
-% \begin{subfigure}{.235\textwidth}
-%   \centering
-%   \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_circ_plot_currents.png}
-%   \caption{Trapped flux.}
-%   \label{fig:square_ring_plot_currents}
-% \end{subfigure}
-% \begin{subfigure}{.235\textwidth}
-%   \centering
-%   \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_circ_plot_fields.png}
-%   \caption{Trapped flux.}
-%   \label{fig:square_ring_plot_fields}
-% \end{subfigure}
-
-% \caption{Sheet current $\vec{J}$ (a, c) and magnetic field $\mu_0H_z$ (b, d) distributions for the circular ring with a uniform field of 0.25 mT applied out-of-plane (a, b) and a circulating current of 1 mA (c, d) calculated using Code Block~\ref{code:ring_circulating_current}.}
-% \label{fig:ring_plot_fields_currents}
-% \end{figure}
 
@@
 \end{itemize}
-\inline{Solutions} also have several visualization methods built in (see Section~\ref{section:overview:visualization}).
+\inline{Solutions} also have several visualization methods built in (see Figure~\ref{fig:square-ring-results} and Section~\ref{section:overview:visualization}).
 

### 2021-10-22 main.tex

@@
 % \documentclass[final,3p,times,twocolumn]{elsarticle}
-%% \documentclass[final,5p,times]{elsarticle}
+% \documentclass[final,5p,times]{elsarticle}
 % \documentclass[final,5p,times,twocolumn]{elsarticle}
@@
 
-In Section~\ref{section:model} we outline Brandt's model, and in Section~\ref{section:implementation} we describe its numerical implementation.
+In Section~\ref{section:model} we outline the model, and in Section~\ref{section:implementation} we describe its numerical implementation.
 In Section~\ref{section:overview}, we provide an overview of the structure of the \SuperScreen package, highlighting notable functions, classes, and features, and discuss some important development details.
@@
 
-\begin{figure}
+\begin{figure}[h]
     \centering
@@
 
-See Code Block~\ref{code:ring_circulating_current} and  Figure~\ref{fig:ring_plot_fields_currents} for an example of the usage and output of \inline{plot_fields()} and \inline{plot_currents()}.
+See Code Block~\ref{code:ring_circulating_current} and  Figure~\ref{fig:square-ring-results} for an example of the usage and output of \inline{plot_fields()} and \inline{plot_currents()}.
 
@@
 
+\section{Fluxoid path independence}
+\label{appendix:fluxoid}
+
+\SuperScreen allows one to calculate the fluxoid $\Phi^f_S$ for any polygonal region $S$ whose boundary $\partial S$ lies completely within a superconducting film.
+As described in Section~\ref{section:model:fluxoid}, for a valid solution to Equation~\ref{eq:london} the fluxoid $\Phi^f_S$ should have the following properties:
+\begin{enumerate}
+    \item{$\Phi^f_S = \sum_{\mathrm{vortices}\,v}\Phi_v$ for any region $S$ lying completely within a superconducting film that contains a set of vortices $v$, each containing flux $\Phi_v$ (and $\Phi^f_S = 0$ if $S$ contains no vortices).}
+    \item{$\Phi^f_S = \Phi_h$ for any region $S$ that contains a hole $h$, where $\Phi_h$ is a constant (i.e.
+does not depend on the specific region $S$ or path $\partial S$) but need not be quantized in units of $\Phi_0$.}
+\end{enumerate}
+
+\section{Convergence of multi-layer solutions}
+\label{appendix:convergence}
+
 % \section{Scaling with number of layers}

### 2021-10-22 main.tex

@@
 
+\begin{figure}
+\centering
+\begin{subfigure}{0.75\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{examples/images/simply_connected_region.png}
+    \caption{The fluxoid $\Phi^f_S$ vanishes for simply-connected regions containing no vortices.}
+    \label{fig:fluxoid-simply}
+\end{subfigure}
+
+\begin{subfigure}{0.75\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{examples/images/simply_connected_region_with_vortices.png}
+    \caption{The fluxoid $\Phi^f_S$}
+    \label{fig:fluxoid-simply-vortices}
+\end{subfigure}
+
+\begin{subfigure}{0.75\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{examples/images/multiply_connected_region.png}
+    \caption{Multiply-connected region}
+    \label{fig:fluxoid-multiply}
+\end{subfigure}
+
+\end{figure}
+
 \section{Convergence of multi-layer solutions}

### 2021-10-22 main.tex
Updates from Overleaf

@@
 \centering
-\begin{subfigure}{0.75\textwidth}
+\begin{subfigure}{\textwidth}
     \centering
     \includegraphics[width=\textwidth]{examples/images/simply_connected_region.png}
-    \caption{The fluxoid $\Phi^f_S$ vanishes for simply-connected regions containing no vortices.}
+    \caption{The fluxoid $\Phi^f_S$ vanishes for simply-connected regions containing no vortices.
+Current density $|\vec{J}|$ (a) and out-of-plane field $\mu_0H_z$ (b) for the square ring with $\Lambda=1\,\mu\mathrm{m}$ subject to a uniform applied field of 0.1 mT.
+The ``flux part'' and ``supercurrent part`` of the fluxoid are shown as filled and unfilled bars respectively in (c), with the colors corresponding to the colors of the paths in (a, b).}
     \label{fig:fluxoid-simply}
@@
 
-\begin{subfigure}{0.75\textwidth}
+\begin{subfigure}{\textwidth}
     \centering

### 2021-10-26 main.tex

--- 2021-10-22 main.tex
@@
 \SuperScreen is an open-source Python package developed to simulate the static magnetic response of structures composed of one or more layers containing superconducting thin films.
-\SuperScreen solves the coupled Maxwell's and London's equations in and around superconducting films with spatially-varying penetration depth in the presence of applied magnetic fields, pinned vortices, and trapped flux using a matrix inversion method introduced by Brandt and Clem~\cite{Brandt_Clem_2004,brandt_thin_2005} and initially implemented by Kirtley, \emph{et al.} to model the magnetic response of scanning superconducting quantum interference device (SQUID) sensors.~\cite{kirtley_scanning_2016, kirtley_response_2016}
+\SuperScreen solves the coupled Maxwell's and London's equations in and around superconducting films with spatially-varying penetration depth in the presence of applied magnetic fields, pinned vortices, and trapped flux using a matrix inversion method introduced by Brandt and Clem~\cite{Brandt_Clem_2004,brandt_thin_2005} and subsequently used by Kirtley, \emph{et al.} to model the magnetic response of scanning superconducting quantum interference device (SQUID) sensors.~\cite{kirtley_scanning_2016, kirtley_response_2016}
 
@@
 Because the sheet current has zero divergence inside the superconducting film ($\nabla\cdot\vec{J}=0$)
-except at small contacts where current can be injected, one can express the sheet current in terms
+except at small terminals where current can be injected, one can express the sheet current in terms
 of a scalar potential $g(x, y)$, called the stream function:
@@
 The fluxoid should vanish for a region $S$ completely contained within a superconducting film that contains no holes or vortices.
-Similarly, the fluxoid $\Phi^f_S$ should have the same value for any region containing a given hole or collection of vortices in a superconducting film.
+Similarly, the fluxoid should have the same value for any region containing a given hole or collection of vortices in a superconducting film.
 This path-independence of the fluxoid follows from the static London equation (Eq.~\ref{eq:london}) on which the present model is based.
-However, because Eq.~\ref{eq:london} does not relate the supercurrent density $\vec{J}$ to the phase of a complex order parameter as in Ginzburg-Landau (GL) theory, or invoke the semi-classical Bohr-Sommerfeld quantization rule as London did~\cite{tinkham2004introduction}, within this model the fluxoid is in no way constrained to be an integer multiple of the flux quantum $\Phi_0=h/2e$.
+However, because Eq.~\ref{eq:london} does not relate the supercurrent density $\vec{J}$ to the phase of a complex order parameter as in Ginzburg-Landau (GL) theory, or invoke the semi-classical Bohr-Sommerfeld quantization rule as London did~\cite{tinkham2004introduction}, within this model the fluxoid is not constrained to be an integer multiple of the flux quantum $\Phi_0=h/2e$.
 
@@
 and $(\mathbf{A}\cdot\mathbf{v})_{ij}=(\mathbf{v}\cdot\mathbf{A})_{ij}=A_{ij}v_{i}$ for a matrix $\mathbf{A}$ and a column vector $\mathbf{v}$.
+$\mathbf{A}^T$ denotes the transpose of matrix $\mathbf{A}$.
 
@@
 
-\begin{equation}
+\begin{align}
     \label{eq:field_from_kernel_num}
     \underbrace{\mathbf{h}_z}_\text{total field}
-    = \underbrace{\mathbf{h}_{z,\,\mathrm{applied}}}_\text{applied field}
-    + \underbrace{(\mathbf{Q}\cdot\mathbf{w})\mathbf{g}}_\text{screening field}.
-\end{equation}
-
-The kernel matrix $\mathbf{Q}$ and weight matrix $\mathbf{w}$ together play the role of the
-kernel function $Q_z(\vec{r},\vec{r}')$ for all points lying in the plane of the film. They are both $n\times n$ matrices determined solely by the geometry of the mesh.
+    &= \underbrace{\mathbf{h}_{z,\,\mathrm{applied}}}_\text{applied field}
+    + \underbrace{\mathbf{Q}(\mathbf{g}\cdot\mathbf{w})}_\text{screening field}\\
+    &=\mathbf{h}_{z,\,\mathrm{applied}}
+    + (\mathbf{Q}\cdot\mathbf{w}^T)\mathbf{g}\\
+    h_{z, i} &= h_{z,\,\mathrm{applied}, i} + \sum_j Q_{ij}g_jw_j
+\end{align}
+
+The $n\times n$ kernel matrix $\mathbf{Q}$ and $n\times 1$ weight vector $\mathbf{w}$, both of which are solely determined by the geometry of the mesh, together play the role of the
+kernel function $Q_z(\vec{r},\vec{r}')$ for all points lying in the plane of the film.
 $\mathbf{h}_z$, $\mathbf{h}_{z,\,\mathrm{applied}}$, and $\mathbf{g}$ are all $n\times 1$ vectors, with each row representing the value of the quantity at the
@@
 and $\delta_{ij}$ is the Kronecker delta function.
-The diagonal terms involving the vector $\mathbf{C}$ are meant to work around the fact that $q_{ii}$ diverge (see \cite{brandt_thin_2005} for more details), and $\mathbf{C}$ is given by
+The diagonal terms involving the $n\times 1$ vector $\mathbf{C}$ are meant to work around the fact that $q_{ii}$ diverge (see Ref.~\cite{brandt_thin_2005} for more details), and $\mathbf{C}$ is given by
 
@@
     \label{eq:Heff_sub_num}
-     \mathbf{h}_{z,\,\mathrm{applied}} - \sum_{\mathrm{holes}\, k}\mathbf{h}_{z,\,\mathrm{eff},\,k} = -(\mathbf{Q}\cdot\mathbf{w}-\mathbf{\Lambda}\cdot\mathbf{\nabla}^2)\mathbf{g},
+     \mathbf{h}_{z,\,\mathrm{applied}} - \sum_{\mathrm{holes}\, k}\mathbf{h}_{z,\,\mathrm{eff},\,k} = -(\mathbf{Q}\cdot\mathbf{w}^T-\mathbf{\Lambda}\cdot\mathbf{\nabla}^2)\mathbf{g},
 \end{equation}
@@
 Since the stream function outside the film and inside holes in the film is already known, solving Eq.~\ref{eq:Heff_sub_num} gives us the stream function for the full mesh.
-Defining $\mathbf{K} = \left(\mathbf{Q}\cdot\mathbf{w}-\mathbf{\Lambda}\cdot\mathbf{\nabla}^2\right)^{-1}$, we have
+Defining $\mathbf{K} = \left(\mathbf{Q}\cdot\mathbf{w}^T-\mathbf{\Lambda}\cdot\mathbf{\nabla}^2\right)^{-1}$, we have
 
@@
 
-If there is a vortex containing flux $\Phi_j$ located in a film at position $\vec{r}_j$ indexed as mesh vertex $j$, then for each position $\vec{r}_i$ within that film, we add to the stream function $g_i$ the quantity $\mu_0^{-1}\Phi_jK_{ij} / M_{jj}$, where $K_{ij}$ is an element of the inverse matrix defined above, and $M_{jj}$ is an element of the ``mass matrix'' which assigns an effective area to the mesh vertex at which the vortex is located (see \ref{appendix:laplace} for the definition of the mass matrix).
+If there is a vortex containing flux $\Phi_j$ located in a film at position $\vec{r}_j$ indexed as mesh vertex $j$, then for each position $\vec{r}_i$ within that film, we add to the stream function $g_i$ the quantity $\mu_0^{-1}\Phi_jK_{ij} / w_{j}$, where $K_{ij}$ is an element of the inverse matrix defined above, and $w_{j}$ is an element of the weight matrix which assigns an effective area to the mesh vertex at which the vortex is located (see \ref{appendix:laplace} for the definition of the mass matrix).
 This process amounts to numerically inverting Eq.~\ref{eq:applied_to_stream_vortices} as described in Ref.~\cite{brandt_thin_2005}.
@@
 solutions = sc.solve(
-    device=square_ring, applied_field=applied_field, field_units=field_units
+    device=square_ring, applied_field=applied_field, field_units=field_units,
 )
@@
 trapped_flux_solution = sc.solve(
-    device=square_ring, circulating_currents=dict(hole="1 mA"),
+    device=square_ring, applied_field=None, circulating_currents=dict(hole="1 mA"),
 )[-1]
@@
 Functions and \inline{Parameters}, such as those that compute the applied field or penetration depth, are serialized in binary form using \inline{dill}~\cite{McKerns}.
-\inline{Numpy} arrays, such as the mesh itself and the computed stream functions and fields, are saved in the well-established \inline{numpy} \inline{npz} file format.
+\inline{Numpy} arrays, such as the mesh itself and the computed stream functions and fields, are saved in the \inline{numpy} \inline{npz} file format.
 A \inline{list} of \inline{Solutions}, such as that returned by \inline{superscreen.solve()} can be saved/loaded all at once using \inline{save_solutions()} and \inline{load_solutions()}.
 
-\section{Example application: Scanning SQUID magnetometry}
-\label{section:application}
-In scanning superconducting quantum interference device (SQUID) susceptometry, the diamagnetic susceptibility of a superconducting sample is measured by bringing the sample close to a pair of superconducting loops.
+% \section{Example application: Scanning SQUID magnetometry}
+% \label{section:application}
+% In scanning superconducting quantum interference device (SQUID) susceptometry, the diamagnetic susceptibility of a superconducting sample is measured by bringing the sample close to a pair of superconducting loops.
 The first loop, called the ``pickup loop" is attached to a SQUID circuit that sensitively measures the magnetic flux threading the loop.
@@
 
-Analysis developed to interpret the results of scanning SQUID susceptometry measurements makes several simplifying assumptions that are not always satisfied: 1) the sample's effective penetration depth $\Lambda$ (or Pearl length $2\Lambda$) is spatially homogeneous, 2) the sample is much larger than the field coil, and 3) the field coil and pickup loop can be approximated as one-dimensional coaxial, coplanar circular loops~\cite{Kirtley_Kalisky_2012}.
+% Analysis developed to interpret the results of scanning SQUID susceptometry measurements makes several simplifying assumptions that are not always satisfied: 1) the sample's effective penetration depth $\Lambda$ (or Pearl length $2\Lambda$) is spatially homogeneous, 2) the sample is much larger than the field coil, and 3) the field coil and pickup loop can be approximated as one-dimensional coaxial, coplanar circular loops~\cite{Kirtley_Kalisky_2012}.
 
@@
 
-Figure~\ref{fig:susceptometry}(a) shows a \inline{Device} representing field coil and pickup loop of an actual scanning SQUID sensor.
+% Figure~\ref{fig:susceptometry}(a) shows a \inline{Device} representing field coil and pickup loop of an actual scanning SQUID sensor.
 In addition to the field coil and pickup loop, there are superconducting shields that limit the amount of magnetic flux that can penetrate the leads connecting the loops to the rest of the circuit (the rest of the circuit is not modeled).
@@
 
+\section{Examples}
+\label{section:examples}
+
+\subsection{Calculating the fluxoid}
+\label{section:examples:fluxoid}
+
+\SuperScreen allows one to calculate the fluxoid $\Phi^f_S$ for any polygonal region $S$ whose boundary $\partial S$ lies completely within a superconducting film (see Section~\ref{section:model:fluxoid}).
+This calculation is implemented as follows: The ``flux part''  is calculated using \inline{Solution.polygon_flux()}, which computes the flux through a polygon representing a region $S$ by averaging the field at the three vertices of each triangle $t$ that lies in $S$ to estimate the field $\mu_0H_{z, t}$ at the center of the triangle, then returns the flux $\sum_t \mu_0H_{z,t}A_t$, where $A_t$ is the area of triangle $t$.
+The ``supercurrent part'' is calculated by evaluating the vector current density $\vec{J}$ at each point in the path $\partial S$ using \inline{Solution.interp_current_density()}, then computing the integral $\oint_S\mu_o\Lambda(\vec{r})\vec{J}(\vec{r})\cdot\mathrm{d}\vec{r}$ using the trapezoid rule.
+The sum of these two terms gives the fluxoid $\Phi^f_S$.
+
+As described in Section~\ref{section:model:fluxoid}, for a valid solution to the static 2D London equation as formulated in Equation~\ref{eq:london}, the fluxoid $\Phi^f_S$ should have the following properties:
+\begin{enumerate}
+    \item{$\Phi^f_S = \sum_{\mathrm{vortices}\,v}\Phi_v$ for any region $S$ lying completely within a superconducting film that contains a set of vortices $v$, each containing flux $\Phi_v$ (and $\Phi^f_S = 0$ if $S$ contains no vortices).}
+    \item{$\Phi^f_S = \Phi_h$ for any region $S$ that contains a hole $h$, where $\Phi_h$ is a constant (i.e.
+does not depend on the specific region $S$ or path $\partial S$) but need not be quantized in units of $\Phi_0$.}
+\end{enumerate}
+
+A demonstration of these properties for the case of the square ring with effective penetration depth $\Lambda=1\,\mu\mathrm{m}$, inner side length $5\,\mu\mathrm{m}$, and outer side length $10\,\mu\mathrm{m}$ subject to a uniform applied field of 0.1 mT is shown in Figure~\ref{fig:fluxoid}.
+See the figure caption for a detailed explanation of the results.
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=\textwidth]{examples/images/fluxoid_combined.png}
+    \caption{Demonstration of the fluxoid properties listed in \ref{section:examples:fluxoid} for a square ring with $\Lambda=1\,\mu\mathrm{m}$, inner side length $5\,\mu\mathrm{m}$, and outer side length $10\,\mu\mathrm{m}$ (whose outline is shown with white lines in the left and middle columns) subject to a uniform applied field of 0.1 mT.
+The left and middle columns show the computed current density and out-of-plane-field, overlaid with several regions $S$ for which the fluxoid $\Phi^f_S$ (calculating using \inline{Solution.polygon_fluxoid()}) is shown in the right column.
+The colors of the paths in the left and middle columns correspond to the colors of the bars in the right column.
+Top row (a - c): The fluxoid $\Phi^f_S$ vanishes for all simply-connected regions containing no vortices.
+The errors in (c) are given by $|\Phi^f_S / \Phi^f_{S,\,\text{(flux part)}}|$.
+Middle row (d - f): For simply-connected regions containing a set of vortices $v$, each carrying flux $\Phi_v$, the fluxoid is given by $\sum_v\Phi_v$.
+In this case, the body of the square ring contains both ``positive'' ($\Phi_v=\Phi_0$, counter-clockwise circulating current) and ``negative'' ($\Phi_v=-\Phi_0$, clockwise circulating current) vortices, which appear in (e) as yellow and blue dots respectively.
+The expected value for the fluxoid for each region $S$ given in units of $\Phi_0$ by (number of yellow vortices lying inside $S$) - (number of blue vortices lying inside $S$), and the errors in (f) are reported relative to this expected value.
+Bottom row (g - i): The fluxoid is approximately equal for all regions $S$ containing a given hole, shown here for both circular ($S = 0, 1, 2$) and square ($S=3, 4, 5, 6$) regions.}
+    \label{fig:fluxoid}
+\end{figure}
+
+\subsection{Calculating mutual inductance}
+\label{section:examples:mutual-inductance}
+
 \section{Conclusion}
@@
 There are cases where the model reproduces experimental results despite violation of this condition (e.g.
-the calculations in Section~\ref{section:application} and in~\cite{kirtley_scanning_2016,kirtley_response_2016}), but care must be taking in interpreting results in these cases.
-Second, as a London model, Brandt and Clem's method assumes that all superconducting films behave linearly and without dissipation, and that the applied magnetic field and current density are below the film's critical field and critical current density.
+the calculations and in Refs.~\cite{kirtley_scanning_2016,kirtley_response_2016}), but care must be taking in interpreting results in these cases.
+Second, as a London model, Brandt and Clem's method assumes that all superconducting films behave linearly and without dissipation, and that the applied magnetic field and current density are well below the critical field and critical current density of all films in a device.
 Third, while currents associated with vortices and flux trapped in holes can be modeled, \SuperScreen does not enforce fluxoid quantization or treat the energetics of vortex nucleation in films or fluxoid transitions in multiply-connected films.
@@
 Potential improvements to \SuperScreen include: more complete treatment of multiply-connected superconductors~\cite{Clem_Brandt_2005}, more sophisticated mesh generation (e.g.
-automated local mesh refinement based on device geometry), automated determination of solution convergence for models with multiple layers, an improved interface for generating complex device geometries (for example using 2D constructive solid geometry, CSG), and further optimization for memory and CPU efficiency (especially in the context of parallel processing).
+automated local mesh refinement based on device geometry), automated determination of solution convergence for models with multiple layers, an improved interface for generating complex device geometries (for example using 2D constructive solid geometry), and further optimization for memory and CPU efficiency (especially in the context of parallel processing).
 
@@
 
-\section{Fluxoid path independence}
-\label{appendix:fluxoid}
-
-\SuperScreen allows one to calculate the fluxoid $\Phi^f_S$ for any polygonal region $S$ whose boundary $\partial S$ lies completely within a superconducting film.
-As described in Section~\ref{section:model:fluxoid}, for a valid solution to Equation~\ref{eq:london} the fluxoid $\Phi^f_S$ should have the following properties:
-\begin{enumerate}
-    \item{$\Phi^f_S = \sum_{\mathrm{vortices}\,v}\Phi_v$ for any region $S$ lying completely within a superconducting film that contains a set of vortices $v$, each containing flux $\Phi_v$ (and $\Phi^f_S = 0$ if $S$ contains no vortices).}
-    \item{$\Phi^f_S = \Phi_h$ for any region $S$ that contains a hole $h$, where $\Phi_h$ is a constant (i.e.
+% \section{Fluxoid calculation}
+% \label{appendix:fluxoid}
+
+% \SuperScreen allows one to calculate the fluxoid $\Phi^f_S$ for any polygonal region $S$ whose boundary $\partial S$ lies completely within a superconducting film (see Section~\ref{section:model:fluxoid}).
+This calculation is implemented as follows: The ``flux part''  is calculated using \inline{Solution.polygon_flux()}, which computes the flux through a polygon representing a region $S$ by averaging the field at the three vertices of each triangle $t$ that lies in $S$ to estimate the field $\mu_0H_{z, t}$ at the center of the triangle, then returns the flux $\sum_t \mu_0H_{z,t}A_t$, where $A_t$ is the area of triangle $t$.
+The ``supercurrent part'' is calculated by evaluating the vector current density $\vec{J}$ at each point in the path $\partial S$ using \inline{Solution.interp_current_density()}, then computing the integral $\oint_S\mu_o\Lambda(\vec{r})\vec{J}(\vec{r})\cdot\mathrm{d}\vec{r}$ using the trapezoid rule.
+The sum of these two terms gives the fluxoid $\Phi^f_S$.
+
+% As described in Section~\ref{section:model:fluxoid}, for a valid solution to the static 2D London equation as formulated in Equation~\ref{eq:london}, the fluxoid $\Phi^f_S$ should have the following properties:
+% \begin{enumerate}
+%     \item{$\Phi^f_S = \sum_{\mathrm{vortices}\,v}\Phi_v$ for any region $S$ lying completely within a superconducting film that contains a set of vortices $v$, each containing flux $\Phi_v$ (and $\Phi^f_S = 0$ if $S$ contains no vortices).}
+%     \item{$\Phi^f_S = \Phi_h$ for any region $S$ that contains a hole $h$, where $\Phi_h$ is a constant (i.e.
 does not depend on the specific region $S$ or path $\partial S$) but need not be quantized in units of $\Phi_0$.}
-\end{enumerate}
+% \end{enumerate}
+
+% A demonstration of these properties for the case of the square ring with effective penetration depth $\Lambda=1\,\mu\mathrm{m}$, inner side length $5\,\mu\mathrm{m}$, and outer side length $10\,\mu\mathrm{m}$ subject to a uniform applied field of 0.1 mT is shown in Figure~\ref{fig:fluxoid}.
+See the figure caption for a detailed explanation of the results.
+
+% \begin{figure}[h]
+%     \centering
+%     \includegraphics[width=\textwidth]{examples/images/fluxoid_combined.png}
+%     \caption{Demonstration of the fluxoid properties listed in \ref{appendix:fluxoid} for a square ring with $\Lambda=1\,\mu\mathrm{m}$, inner side length $5\,\mu\mathrm{m}$, and outer side length $10\,\mu\mathrm{m}$ (whose outline is shown with white lines in the left and middle columns) subject to a uniform applied field of 0.1 mT.
+The left and middle columns show the computed current density and out-of-plane-field, overlaid with several regions $S$ for which the fluxoid $\Phi^f_S$ (calculating using \inline{Solution.polygon_fluxoid()}) is shown in the right column.
+The colors of the paths in the left and middle columns correspond to the colors of the bars in the right column.
+Top row (a - c): The fluxoid $\Phi^f_S$ vanishes for all simply-connected regions containing no vortices.
+The errors in (c) are given by $|\Phi^f_S / \Phi^f_{S,\,\text{(flux part)}}|$.
+Middle row (d - f): For simply-connected regions containing a set of vortices $v$, each carrying flux $\Phi_v$, the fluxoid is given by $\sum_v\Phi_v$.
+In this case, the body of the square ring contains both ``positive'' ($\Phi_v=\Phi_0$, counter-clockwise circulating current) and ``negative'' ($\Phi_v=-\Phi_0$, clockwise circulating current) vortices, which appear in (e) as yellow and blue dots respectively.
+The expected value for the fluxoid for each region $S$ given in units of $\Phi_0$ by (number of yellow vortices lying inside $S$) - (number of blue vortices lying inside $S$), and the errors in (f) are reported relative to this expected value.
+Bottom row (g - i): The fluxoid is approximately equal for all regions $S$ containing a given hole, shown here for both circular ($S = 0, 1, 2$) and square ($S=3, 4, 5, 6$) regions.}
+%     \label{fig:fluxoid}
+% \end{figure}
 

### 2021-11-02 main.tex

@@
 Quantitative understanding of the spatial distribution of magnetic fields and screening currents in two-dimensional (2D) superconductors and mesoscopic thin film superconducting devices is critical to interpreting the results of magnetic measurements of such systems.
-Here we introduce \SuperScreen, an open-source Python package for simulating the magnetic response of two-dimensional superconductors to applied time-independent magnetic fields.
-Given an applied magnetic field, \SuperScreen solves for Meissner screening currents and the resulting magnetic fields in structures composed of one or more superconducting thin films of arbitrary geometry with spatially inhomogeneous magnetic penetration depth using a matrix inversion method introduced by Brandt and Clem~\cite{Brandt_Clem_2004, brandt_thin_2005}.
+Here, we introduce \SuperScreen, an open-source Python package for simulating the magnetic response of 2D superconductors to applied time-independent magnetic fields.
+Given an applied magnetic field, \SuperScreen solves for the Meissner currents and magnetic fields in and around structures composed of one or more superconducting thin films of arbitrary geometry with spatially inhomogeneous magnetic penetration depth using an efficient matrix inversion method~\cite{Brandt2004-ew, Brandt2005-wj}.
 \SuperScreen can be used to model screening effects and calculate self- and mutual-inductance in superconducting circuits, and simulate the magnetic response of inhomogeneous 2D superconductors.
-
 \end{abstract}
@@
 %% keywords here, in the form: keyword \sep keyword
-superconductivity\sep Meissner screening\sep thin film\sep London equations
+superconductivity\sep Meissner screening\sep thin film\sep London equations \sep inductance
 
@@
   %Only required for a New Version summary, otherwise leave out.
-{\em Nature of problem:} \SuperScreen solves for Meissner screening currents in structures composed of 2D or thin film superconductors in the presence of an applied magnetic field.\\
+{\em Nature of problem:} \SuperScreen solves for Meissner screening currents in structures composed of 2D or thin film superconductors in the presence of an applied magnetic field, pinned vortices, and trapped flux.\\
   %Describe the nature of the problem here. \\
-{\em Solution method:} The package solves the 2D London equations inside superconducting regions and Maxwell's equations outside the superconductor using a matrix inversion method introduced by Brandt and Clem~\cite{Brandt_Clem_2004,brandt_thin_2005}.\\
+{\em Solution method:} This package solves the 2D London equation for superconducting thin films using a matrix inversion method~\cite{Brandt2004-ew,Brandt2005-wj}.\\
   %Describe the method solution here.
@@
 
-\SuperScreen is an open-source Python package developed to simulate the static magnetic response of structures composed of one or more layers containing superconducting thin films.
-\SuperScreen solves the coupled Maxwell's and London's equations in and around superconducting films with spatially-varying penetration depth in the presence of applied magnetic fields, pinned vortices, and trapped flux using a matrix inversion method introduced by Brandt and Clem~\cite{Brandt_Clem_2004,brandt_thin_2005} and subsequently used by Kirtley, \emph{et al.} to model the magnetic response of scanning superconducting quantum interference device (SQUID) sensors.~\cite{kirtley_scanning_2016, kirtley_response_2016}
-
-In Section~\ref{section:model} we outline the model, and in Section~\ref{section:implementation} we describe its numerical implementation.
+\SuperScreen is a Python package developed to simulate the static magnetic response of structures composed of one or more layers containing superconducting thin films.
+\SuperScreen solves the coupled Maxwell's and London's equations in and around superconducting films with spatially-varying penetration depth in the presence of inhomogeneous applied magnetic fields, pinned vortices, and trapped flux using a matrix inversion method introduced by Brandt and Clem~\cite{Brandt2004-ew,Brandt2005-wj} and subsequently used by Kirtley, \emph{et al.} to model the magnetic response of scanning superconducting quantum interference device (SQUID) sensors.~\cite{Kirtley2016-zz, Kirtley2016-gt}
+
+There have been many previous numerical studies of magnetic screening and inductance extraction in thin film and two-dimensional (2D) superconducting devices~\cite{Jaycox1981-zl, Ketchen1982-at, Ketchen2012-mb, Hildebrandt1995-uw, Khapaev1997-kw, Khapaev2001-xq, Khapaev2001-pw, Babaei_Brojeny2003-la, Brandt2004-ew, Brandt2005-wj, Clem2005-ye, Muller2021-ci}.
+However, few software tools for this task exist and those that are available are closed-source, are written in low-level compiled languages like C, and/or require the use of specialized file formats or separate computer aided design (CAD) software for defining device geometries and model configurations.\footnote{A brief summary of existing tools can be found in \ref{appendix:other-tools}, and a more thorough overview in Ref.~\cite{Gaj1999-ls}.} Most of these tools are intended for use in the design of superconducting integrated circuits for rapid single flux quantum (RSFQ) logic and are primarily used for inductance extraction~\cite{Gaj1999-ls}.
+In contrast, \SuperScreen is an open-source, user-friendly, portable research tool designed to lower the barrier to entry to quantitative modeling of 2D superconductors, and to help interpret and inform measurements of superconducting thin films and devices.
+
+This introduction to \SuperScreen is organized as follows: In Section~\ref{section:model}, we outline the model and its assumptions and in Section~\ref{section:implementation}, we describe its numerical implementation.
 In Section~\ref{section:overview}, we provide an overview of the structure of the \SuperScreen package, highlighting notable functions, classes, and features, and discuss some important development details.
-Finally, in Section~\ref{section:conlusion} we conclude with potential applications, extensions, and improvements to the package.
+In Section~\ref{section:examples}, we demonstrate how to perform a few simple types of simulations using \SuperScreen and compare the results to previous numerical and analytical solutions.
+Finally, in Section~\ref{section:conlusion}, we by discussing applications, limitations, and possible extensions of the package.
 
@@
 
-A convenient method for solving this problem was introduced by Brandt and Clem in Ref.~\cite{Brandt_Clem_2004}, expanded by Brandt in Ref.~\cite{brandt_thin_2005}, and subsequently used to model the magnetic response of scanning Superconducting Quantum Interference Device (SQUID) susceptometers~\cite{kirtley_scanning_2016, kirtley_response_2016}.
+A convenient method for solving this problem was introduced by Brandt and Clem in Ref.~\cite{Brandt2004-ew}, expanded by Brandt in Ref.~\cite{Brandt2005-wj}, and subsequently used to model the magnetic response of scanning Superconducting Quantum Interference Device (SQUID) susceptometers~\cite{Kirtley2016-zz, Kirtley2016-gt}.
 In the London model of superconductivity, the magnetic field $\vec{H}(\vec{r})$ and 3D current density $\vec{j}(\vec{r})$ in a superconductor with London penetration depth $\lambda(\vec{r})$ obey the second London equation:
@@
 where $\Lambda(x, y)=\lambda^2(x, y)/d$ is the effective penetration depth
-of the superconducting film (equal to half the Pearl length~\cite{pearl_current_1964}).
+of the superconducting film (equal to half the Pearl length~\cite{Pearl1964-cl}).
 
 It is important to note that the assumption $\vec{j}(x, y, z)\approx\vec{j}_{z_0}(x, y)$ is valid for only films that are thinner than their London penetration depth ($d<\lambda$, such that $\Lambda=\lambda^2/d>\lambda$).
-However the model has been applied with some success in structures with $\lambda\lesssim d$~\cite{kirtley_scanning_2016,kirtley_response_2016}.
-Aside from this limitation, the method described below can in principle to used to model films with any effective penetration depth $0\leq\Lambda<\infty$.
+However the model has been applied with some success in structures with $\lambda\lesssim d$~\cite{Kirtley2016-zz,Kirtley2016-gt}.
+Aside from this limitation, the method described below can be used to model films with any effective penetration depth $0\leq\Lambda<\infty$.
 
@@
 
-The stream function $g$ can be thought of as the local magnetization of the film, or the area density of magnetic dipole sources (see Ref.~\cite{brandt_thin_2005} for more interesting properties of the stream function).
+The stream function $g$ can be thought of as the local magnetization of the film, or the area density of magnetic dipole sources (see Ref.~\cite{Brandt2005-wj} for more interesting properties of the stream function).
 We can rewrite Eq.~\ref{eq:london}, which gives the magnetic field inside of a 2D film, in terms of $g$:
@@
     H_{z,\,\mathrm{eff},\,k}(\vec{r}) = -\int_{\mathrm{hole}\,k}[
-        Q_z(\vec{r},\vec{r}')-\Lambda(\vec{r}')\nabla^2
+        Q_z(\vec{r},\vec{r}')-\delta(\vec{r}-\vec{r}')\Lambda(\vec{r}')\nabla^2
     ] I_{\mathrm{circ},\,k} \,\mathrm{d}^2r'.   
@@
 
-The fluxoid $\Phi^f_S$ for a 2D region $S$ with 1D boundary $\partial S$ is given by the sum of flux through $S$ and the line integral of sheet current around $\partial S$~\cite{brandt_thin_2005,Clem_Brandt_2005,tinkham2004introduction}:
+The fluxoid $\Phi^f_S$ for a 2D region $S$ with 1D boundary $\partial S$ is given by the sum of flux through $S$ and the line integral of sheet current around $\partial S$~\cite{Brandt2005-wj,Clem2005-ye,Tinkham2004-zn}:
 
@@
 
-The fluxoid should vanish for a region $S$ completely contained within a superconducting film that contains no holes or vortices.
-Similarly, the fluxoid should have the same value for any region containing a given hole or collection of vortices in a superconducting film.
+The fluxoid vanishes for a region $S$ completely contained within a superconducting film that contains no holes or vortices, and has the same value for any region containing a given hole or collection of vortices in a superconducting film.
 This path-independence of the fluxoid follows from the static London equation (Eq.~\ref{eq:london}) on which the present model is based.
-However, because Eq.~\ref{eq:london} does not relate the supercurrent density $\vec{J}$ to the phase of a complex order parameter as in Ginzburg-Landau (GL) theory, or invoke the semi-classical Bohr-Sommerfeld quantization rule as London did~\cite{tinkham2004introduction}, within this model the fluxoid is not constrained to be an integer multiple of the flux quantum $\Phi_0=h/2e$.
+Fluxoid quantization---the requirement that the fluxoid $\Phi^f_S=n\Phi_0$ where $n$ is an integer and $\Phi_0=h/2e$ is the magnetic flux quantum---is not automatically enforced by Eq.~\ref{eq:london}, however it can be included as an external constraint.
+% However, because Eq.~\ref{eq:london} does not relate the supercurrent density $\vec{J}$ to the phase of a complex order parameter as in Ginzburg-Landau theory, or invoke the semi-classical Bohr-Sommerfeld quantization rule as London did~\cite{Tinkham2004-zn}, within this model the fluxoid is not constrained to be an integer multiple of the flux quantum $\Phi_0=h/2e$.
 
@@
 By solving Eq.~\ref{eq:applied_to_stream_vortices} to obtain $g(\vec{r})$, one can compute the supercurrent density in the film due to both an applied field and trapped vortices.
-For a simply-connected region $S$ containing a set of vortices $v$ each associated with a flux $\Phi_v$, the fluxoid should be equal to $\Phi^f_S=\sum_{\mathrm{vortices}\,v}\Phi_v$.
-It is important to note that this 2D London model does not contain the physics associated with how and where vortices nucleate in superconductors, nor is it included in the model that the flux carried by vortices must be quantized in units of $\Phi_0$, both which are captured phenomenologically by GL theory.
+For a simply-connected region $S$ containing a set of vortices $v$ each associated with a flux $\Phi_v$, the fluxoid is equal to $\Phi^f_S=\sum_{\mathrm{vortices}\,v}\Phi_v$.
 The numerical solution to Eq.~\ref{eq:applied_to_stream_vortices} is described at the end of Section~\ref{section:implementation}.
@@
 Convergence can be quantified by, for example, calculating the total magnetic flux though all films and holes in the model at the end of each iteration.
+In general, the more layers there are in a structure the more iterations are  required to reach a given level of convergence.
 
@@
 
-The matrix version of Eq.~\ref{eq:field_from_kernel} is
+The discrete version of Eq.~\ref{eq:field_from_kernel} is
 
 \begin{align}
+\begin{split}
     \label{eq:field_from_kernel_num}
@@
     + (\mathbf{Q}\cdot\mathbf{w}^T)\mathbf{g}\\
-    h_{z, i} &= h_{z,\,\mathrm{applied}, i} + \sum_j Q_{ij}g_jw_j
+    % h_{z, i} &= h_{z,\,\mathrm{applied}, i} + \sum_j Q_{ij}g_jw_j,
+\end{split}
 \end{align}
-
-The $n\times n$ kernel matrix $\mathbf{Q}$ and $n\times 1$ weight vector $\mathbf{w}$, both of which are solely determined by the geometry of the mesh, together play the role of the
-kernel function $Q_z(\vec{r},\vec{r}')$ for all points lying in the plane of the film.
+where for clarity we show both the matrix version of Eq.~\ref{eq:field_from_kernel} (top two lines) and the equivalent discrete sum version (bottom line).
+
+The $n\times n$ kernel matrix $\mathbf{Q}$ represents the kernel function $Q_z(\vec{r},\vec{r}')$ for all points lying in the plane of the film, and the $n\times 1$ weight vector $\mathbf{w}$, which assigns an effective area to each vertex in the mesh, represents the differential element $\mathrm{d}^2r'$.
+Both $\mathbf{Q}$ and $\mathbf{w}$ are solely determined by the geometry of the mesh, so they only need to be computed once for a given device.
 $\mathbf{h}_z$, $\mathbf{h}_{z,\,\mathrm{applied}}$, and $\mathbf{g}$ are all $n\times 1$ vectors, with each row representing the value of the quantity at the
-corresponding vertex in the mesh.
-There are several different methods for constructing the weight matrix $\mathbf{w}$, which are discussed in~\ref{appendix:laplace}.
-The kernel matrix $\mathbf{Q}$ is given by
+corresponding vertex in the mesh. The vector $\mathbf{w}$ is equal to the diagonal of the ``lumped mass matrix'' $\mathbf{M}$: $w_i=M_{ii} = \frac{1}{3}\sum_{t\in\mathcal{N}(i)}\mathrm{area}(t)$,
+where $\mathcal{N}(i)$ is the set of triangles $t$ adjacent to vertex $i$. The kernel matrix $\mathbf{Q}$ is given by
 
@@
 and $\delta_{ij}$ is the Kronecker delta function.
-The diagonal terms involving the $n\times 1$ vector $\mathbf{C}$ are meant to work around the fact that $q_{ii}$ diverge (see Ref.~\cite{brandt_thin_2005} for more details), and $\mathbf{C}$ is given by
+The diagonal terms involving the $n\times 1$ vector $\mathbf{C}$ are meant to work around the fact that $q_{ii}$ diverge (see Ref.~\cite{Brandt2005-wj} for more details), and $\mathbf{C}$ is given by
 
@@
     \label{eq:Heff_sub_num}
-     \mathbf{h}_{z,\,\mathrm{applied}} - \sum_{\mathrm{holes}\, k}\mathbf{h}_{z,\,\mathrm{eff},\,k} = -(\mathbf{Q}\cdot\mathbf{w}^T-\mathbf{\Lambda}\cdot\mathbf{\nabla}^2)\mathbf{g},
+     \mathbf{h}_{z,\,\mathrm{applied}} - \sum_{\mathrm{holes}\, k}\mathbf{h}_{z,\,\mathrm{eff},\,k} = -(\mathbf{Q}\cdot\mathbf{w}^T-\mathbf{\nabla}^2\cdot \mathbf{\Lambda}^T)\mathbf{g},
 \end{equation}
@@
 inside a superconducting film, which can efficiently be solved (e.g.
-by matrix inversion or LU decomposition) for the unknown vector $\mathbf{g}$, the stream function inside the film.
+by Cholesky or LU decomposition) for the unknown vector $\mathbf{g}$, the stream function inside the film.
 Since the stream function outside the film and inside holes in the film is already known, solving Eq.~\ref{eq:Heff_sub_num} gives us the stream function for the full mesh.
-Defining $\mathbf{K} = \left(\mathbf{Q}\cdot\mathbf{w}^T-\mathbf{\Lambda}\cdot\mathbf{\nabla}^2\right)^{-1}$, we have
+Defining $\mathbf{K} = \left(\mathbf{Q}\cdot\mathbf{w}^T-\mathbf{\nabla}^2\cdot\mathbf{\Lambda}^T\right)^{-1}$, we have
 
@@
 
-If there is a vortex containing flux $\Phi_j$ located in a film at position $\vec{r}_j$ indexed as mesh vertex $j$, then for each position $\vec{r}_i$ within that film, we add to the stream function $g_i$ the quantity $\mu_0^{-1}\Phi_jK_{ij} / w_{j}$, where $K_{ij}$ is an element of the inverse matrix defined above, and $w_{j}$ is an element of the weight matrix which assigns an effective area to the mesh vertex at which the vortex is located (see \ref{appendix:laplace} for the definition of the mass matrix).
-This process amounts to numerically inverting Eq.~\ref{eq:applied_to_stream_vortices} as described in Ref.~\cite{brandt_thin_2005}.
+If there is a vortex containing flux $\Phi_j$ located in a film at position $\vec{r}_j$ indexed as mesh vertex $j$, then for each position $\vec{r}_i$ within that film, we add to the stream function $g_i$ the quantity $\mu_0^{-1}\Phi_jK_{ij} / w_{j}$, where $K_{ij}$ is an element of the inverse matrix defined above, and $w_{j}$ is an element of the weight matrix which assigns an effective area to the mesh vertex at which the vortex is located.
+This process amounts to numerically inverting Eq.~\ref{eq:applied_to_stream_vortices} as described in Ref.~\cite{Brandt2005-wj}.
 
@@
 
-\SuperScreen has several important dependencies beyond the Python standard library: \inline{numpy}~\cite{2020NumPy-Array} and \inline{scipy}~\cite{2020SciPy-NMeth} for numerics, \inline{pint}~\cite{Grecco} for handling physical units, \inline{matplotlib}~\cite{Hunter_2007} for visualization, \inline{meshpy}~\cite{Klockner,Shewchuk,shewchuk96b} and \inline{optimesh}~\cite{nico_schlomer_adam_dobrawy_2021} for mesh generation, \inline{dill}~\cite{McKerns} for serializing objects to disk and between processes, and \inline{ray}~\cite{ray_2018,ray-docs} for parallel processing with shared memory (see~\ref{section:parallel}).
+\SuperScreen has several important dependencies beyond the Python standard library: \inline{numpy}~\cite{Harris2020-xv} and \inline{scipy}~\cite{Virtanen2020-zz} for numerics, \inline{pint}~\cite{Grecco} for handling physical units, \inline{matplotlib}~\cite{Hunter2007-il} for visualization, \inline{meshpy}~\cite{Klockner,Shewchuk,Shewchuk1996-va} and \inline{optimesh}~\cite{Schlomer2021-ua} for mesh generation, \inline{dill}~\cite{McKerns} for serializing objects to disk and between processes, and \inline{ray}~\cite{Moritz2018-mt,ray-docs} for parallel processing with shared memory (see~\ref{section:parallel}).
 
@@
 
-def make_ring(inner_radius=2.5, outer_radius=5, Lambda=1, square=False):
+def make_ring(
+    inner_radius: float = 2.5,
+    outer_radius: float = 5.0,
+    inner_points: int = 300,
+    outer_points: int = 500,
+    Lambda: float = 1.0,
+    square: bool = False,
+) -> sc.Device:
+    """Creates a Device representing a circular or square ring."""
     if square:
-        outer_points = geo.square(2 * outer_radius, points_per_side=150)
-        inner_points = geo.square(2 * inner_radius, points_per_side=75)
+        outer = geo.square(2 * outer_radius, points_per_side=outer_points // 4)
+        inner = geo.square(2 * inner_radius, points_per_side=inner_points // 4)
         bbox = geo.square(1.25 * 2 * outer_radius, points_per_side=10)
     else:
-        outer_points = geo.circle(outer_radius, points=500)
-        inner_points = geo.circle(inner_radius, points=300)
+        outer = geo.circle(outer_radius, points=outer_points)
+        inner = geo.circle(inner_radius, points=inner_points)
         bbox = geo.circle(1.4 * outer_radius, points=50)
     layers = [sc.Layer("base", Lambda=Lambda, z0=0)]
-    films = [sc.Polygon("ring", layer="base", points=outer_points)]
-    holes = [sc.Polygon("hole", layer="base", points=inner_points)]
+    films = [sc.Polygon("ring", layer="base", points=outer)]
+    holes = [sc.Polygon("hole", layer="base", points=inner)]
     abstract_regions = [sc.Polygon("bbox", layer="base", points=bbox)]
@@
 Mesh generation is a two step process.
-First, an initial Delaunay mesh is created using \inline{meshpy}~\cite{Klockner}, which is a Python interface to Triangle~\cite{shewchuk96b, Shewchuk}, a fast compiled 2D mesh generation tool.
-Second (and optionally), the mesh is further optimized using \inline{optimesh}~\cite{nico_schlomer_adam_dobrawy_2021}.
+First, an initial Delaunay mesh is created using \inline{meshpy}~\cite{Klockner}, which is a Python interface to Triangle~\cite{Shewchuk1996-va, Shewchuk}, a fast compiled 2D mesh generation tool.
+Second (and optionally), the mesh is further optimized using \inline{optimesh}~\cite{Schlomer2021-ua}.
 The goal of the mesh optimization step is to improve the quality of each triangular element in the mesh, where quality is defined as twice the ratio of the incircle radius to the circumcircle radius (quality $\leq1$, with equality for equilateral triangles).
@@
     \includegraphics[width=\textwidth]{examples/images/mesh.pdf}
-    \caption{Computational meshes for circular (a, b) and square (c, d) rings, without (a, c) and with (b, d) \inline{optimesh} optimization, generated using Code Block~\ref{code:mesh_generation}.
+    \caption{Computational meshes for (a, b) circular and (c, d) square rings, (a, c) without and (b, d) with \inline{optimesh} optimization, generated using Code Block~\ref{code:mesh_generation}.
 The bounding box (\inline{bbox}) is shown in purple, the ring's outer edge (\inline{ring}) is shown in red, and the ring's inner edge (\inline{hole}) is shown in blue.
@@
     \includegraphics[width=\textwidth]{examples/images/square_ring_results.png}
-    \caption{Sheet current $\vec{J}(x, y)$ and out-of-plane magnetic field $\mu_0H_z(x, y)$ evaluated in the plane of a square ring with effective penetration depth $\Lambda=1\,\mu\mathrm{m}$ subject to a uniform applied field of 0.5 mT (a, b) or trapped flux inducing a circulating current of 1 mA (c, d).
-The sub-figures show the output of \inline{Solution.plot_currents()} (a, c) and \inline{Solution.plot_fields()} (b, d), as shown in Code Block~\ref{code:ring_circulating_current}.
+    \caption{Sheet current $\vec{J}(x, y)$ and out-of-plane magnetic field $\mu_0H_z(x, y)$ evaluated in the plane of a square ring with effective penetration depth $\Lambda=1\,\mu\mathrm{m}$ subject to (a, b) a uniform applied field of 0.5 mT or (c, d) trapped flux inducing a circulating current of 1 mA.
+The sub-figures show the output of (a, c) \inline{Solution.plot_currents()} and (b, d) \inline{Solution.plot_fields()}, as shown in Code Block~\ref{code:ring_circulating_current}.
 For the current plots (a, c), the color-scale indicates the magnitude of the sheet current (or current density), $|\vec{J}|$, and the direction is indicated by the white streamlines.}
@@
     \item{
-    \inline{Solution.polygon_fluxoid()}: Calculates the fluxoid for a specified polygonal region in the device. See \ref{secction:fluxoid} for more details.
+    \inline{Solution.polygon_fluxoid()}: Calculates the fluxoid for a specified polygonal region in the device. See Section~\ref{section:examples:fluxoid} for more details.
     }
@@
 Instances of \inline{superscreen.Device} and \inline{superscreen.Solution} can be saved to and loaded from disk using their respective \inline{to_file()} and \inline{from_file()} methods, making it straightforward to share models and simulation results.
-\inline{Layers}, \inline{Polygons}, and all metadata are serialized to JSON, a widely-used, human-readable plain text format~\cite{JSON}.
+\inline{Layers}, \inline{Polygons}, and all metadata are serialized to JSON, a widely-used, human-readable plain text format.
 Functions and \inline{Parameters}, such as those that compute the applied field or penetration depth, are serialized in binary form using \inline{dill}~\cite{McKerns}.
@@
 
-\SuperScreen allows one to calculate the fluxoid $\Phi^f_S$ for any polygonal region $S$ whose boundary $\partial S$ lies completely within a superconducting film (see Section~\ref{section:model:fluxoid}).
-This calculation is implemented as follows: The ``flux part''  is calculated using \inline{Solution.polygon_flux()}, which computes the flux through a polygon representing a region $S$ by averaging the field at the three vertices of each triangle $t$ that lies in $S$ to estimate the field $\mu_0H_{z, t}$ at the center of the triangle, then returns the flux $\sum_t \mu_0H_{z,t}A_t$, where $A_t$ is the area of triangle $t$.
-The ``supercurrent part'' is calculated by evaluating the vector current density $\vec{J}$ at each point in the path $\partial S$ using \inline{Solution.interp_current_density()}, then computing the integral $\oint_S\mu_o\Lambda(\vec{r})\vec{J}(\vec{r})\cdot\mathrm{d}\vec{r}$ using the trapezoid rule.
+\SuperScreen allows one to calculate the fluxoid $\Phi^f_S$ for any polygonal region $S$ whose boundary $\partial S$ lies completely within a superconducting film using the method \inline{Solution.polygon_fluxoid()} (see Section~\ref{section:model:fluxoid}, Eq.~\ref{eq:fluxoid}).
+We calculate the ``flux part''  $\int_S\mu_0H_z(\vec{r})\,\mathrm{d}^2r$ using \inline{Solution.polygon_flux()}, which computes the flux through a polygon representing a region $S$ by averaging the field at the three vertices of each triangle $t$ that lies in $S$ to estimate the field $\mu_0H_{z, t}$ at the center of the triangle, then returns the flux $\sum_t \mu_0H_{z,t}A_t$, where $A_t$ is the area of triangle $t$.
+We calculate the ``supercurrent part'' $\oint_S\mu_o\Lambda(\vec{r})\vec{J}(\vec{r})\cdot\mathrm{d}\vec{r}$ by evaluating the vector current density $\vec{J}$ at each point in the path $\partial S$ using \inline{Solution.interp_current_density()}, then computing the line integral along the path using the trapezoid rule.
 The sum of these two terms gives the fluxoid $\Phi^f_S$.
@@
 A demonstration of these properties for the case of the square ring with effective penetration depth $\Lambda=1\,\mu\mathrm{m}$, inner side length $5\,\mu\mathrm{m}$, and outer side length $10\,\mu\mathrm{m}$ subject to a uniform applied field of 0.1 mT is shown in Figure~\ref{fig:fluxoid}.
+Property 1 is shown in the first two rows, and property 2 is shown in the last row.
 See the figure caption for a detailed explanation of the results.
 
-\begin{figure}[h]
+\begin{figure}
     \centering
     \includegraphics[width=\textwidth]{examples/images/fluxoid_combined.png}
-    \caption{Demonstration of the fluxoid properties listed in \ref{section:examples:fluxoid} for a square ring with $\Lambda=1\,\mu\mathrm{m}$, inner side length $5\,\mu\mathrm{m}$, and outer side length $10\,\mu\mathrm{m}$ (whose outline is shown with white lines in the left and middle columns) subject to a uniform applied field of 0.1 mT.
-The left and middle columns show the computed current density and out-of-plane-field, overlaid with several regions $S$ for which the fluxoid $\Phi^f_S$ (calculating using \inline{Solution.polygon_fluxoid()}) is shown in the right column.
+    \caption{Demonstration of the fluxoid properties listed in Section~\ref{section:examples:fluxoid} for a square ring with $\Lambda=1\,\mu\mathrm{m}$, inner side length $5\,\mu\mathrm{m}$, and outer side length $10\,\mu\mathrm{m}$, whose outline is shown with white (black) lines in the left (middle) column, subject to a uniform applied field of 0.1 mT.
+The left and middle columns show the computed current density and out-of-plane-field, overlaid with several regions $S$ for which the fluxoids $\Phi^f_S$, calculated using \inline{Solution.polygon_fluxoid()}, are shown in the right column.
 The colors of the paths in the left and middle columns correspond to the colors of the bars in the right column.
@@
 
+While the model doesn't ``know'' about fluxoid quantization, so to speak, we can nevertheless calculate current and field distributions for different fluxoid states $\Phi^f_S=n\Phi_0$.
+Consider again the circular or square ring.
+For a given applied field $H_{z,\,\mathrm{applied}}$ we can choose $I_h$, the current circulating around the hole in the ring, such that the fluxoid $\Phi^f_S=n\Phi_0$ for a region $S$ containing the hole.
+If there is a single hole, this is simply a root finding problem (see Code Block~\ref{code:fluxoid-root}).
+For a structure with $N_h$ holes, we can specify $N_h$ fluxoids $\Phi^f_h$ and find the circulating currents $I_h$ by minimizing, in the least-squares sense, the deviation between each fluxoid and its desired value.
+
+\begin{code}
+\begin{minted}[fontsize=\small]{python}
+from scipy import optimize
+
+def find_fluxoid_solution(
+    device: sc.Device,
+    applied_field: sc.Parameter,
+    hole_name: str,
+    polygon: np.ndarray,
+    fluxoid_n: int = 0,
+    **solve_kwargs,
+) -> sc.Solution:
+
+    solution = None
+
+    def residual_fluxoid(current: float) -> float:
+        """Returns (actual_fluxoid - desired_fluxoid) in units of Phi_0."""
+        nonlocal solution
+        solution = sc.solve(
+            device=device,
+            applied_field=applied_field,
+            circulating_currents={hole_name: current},
+            **solve_kwargs,
+        )[-1]
+        layer_name = device.holes[hole_name].layer
+        total_fluxoid = sum(solution.polygon_fluxoid(polygon)[layer_name])
+        return total_fluxoid.to("Phi_0").magnitude - fluxoid_n
+
+    # Replace optimize.root_scalar with optimize.minimize for multiple holes.
+    result = optimize.root_scalar(residual_fluxoid, x0=-1, x1=1)
+    # Return the optimal Solution
+    return solution
+\end{minted}
+\captionof{listing}{Given an applied field, this function solves for the current and field distribution in a \inline{Device} with a single hole for a specified fluxoid state $\Phi^f_S=n\Phi_0$ using root finding.}
+\label{code:fluxoid-root}
+\end{code}
+
 \subsection{Calculating mutual inductance}
@@
 
+As shown in Ref.~\cite{Brandt2005-wj}, the mutual inductance $M_{ij}$ between holes $i$ and $j$ in a superconducting structure is given by
+\begin{equation}
+    M_{ij}=\frac{\Phi^f_{S_i}}{I_j},
+\end{equation}
+where $\Phi^f_{S_i}$ is the fluxoid for a region $S_i$ containing the hole $i$, and $I_j$ is the current circulating around hole $j$.
+The mutual inductance values for a set of holes form a mutual inductance matrix.
+The diagonals of the mutual inductance matrix are the hole self-inductances ($M_{ii}=L_i$, the self-inductance of hole $i$), and the matrix must be symmetric ($M_{ij}=M_{ji}$) due to the reciprocity theorem.
+If the penetration depth of the film containing hole $i$ is $\Lambda = 0$, then no field penetrates the film and the fluxoid $\Phi^f_{S_i}$ is equal to $\Phi_i$, the flux through hole $i$.
+
+We'll focus first on the self-inductance of circular and square rings.
+For a circular ring with inner radius $a$, outer radius $b>a$, and penetration depth $\Lambda=0$, Clem~\cite{Babaei_Brojeny2003-la} found that the self-inductance approaches $L=2\mu_0 a$ in the ``small hole'' limit $\tilde{a}=a/b\ll 1$.
+In the opposite ``thin ring'' limit $\tilde{a}=a/b\approx 1$, the inductance was found to approach $L=\mu_0b(1+\tilde{a})(\tanh^{-1}\tilde{a}+\log 4 - 1)$.
+Clem and Brandt~\cite{Brandt2004-ew} and Khapaev~\cite{Khapaev1997-kw} calculated the self-inductance of circular and square rings as a function of the ratio of inner and outer diameters.
+
 \section{Conclusion}
@@
 \SuperScreen is an open-source, user-friendly, portable, and efficient tool that solves this problem.
-Applications of the package include calculating self- and mutual-inductance in mesoscopic superconducting circuits, and modeling the magnetic interaction between inhomogeneous superconducting samples and superconducting sensors such as scanning SQUID susceptometers~\cite{kirtley_scanning_2016}.
-
-There are three important limitations to the applicability of \SuperScreen and the matrix inversion method on which it is based~\cite{Brandt_Clem_2004,brandt_thin_2005}.
+Applications of the package include calculating self- and mutual-inductance in planar and multi-planar superconducting circuits, and modeling the magnetic interaction between inhomogeneous superconducting samples and superconducting sensors such as scanning SQUID susceptometers~\cite{Kirtley2016-zz}.
+
+There are several important limitations to the applicability of \SuperScreen and the matrix inversion method on which it is based~\cite{Brandt2004-ew,Brandt2005-wj}.
 First, strictly speaking all superconducting films should be in the 2D limit, with London penetration depth $\lambda$ less than film thickness $d$, such that the out-of-plane current density is approximately constant.
 There are cases where the model reproduces experimental results despite violation of this condition (e.g.
-the calculations and in Refs.~\cite{kirtley_scanning_2016,kirtley_response_2016}), but care must be taking in interpreting results in these cases.
+the calculations and in Refs.~\cite{Kirtley2016-zz,Kirtley2016-gt}), but care must be taking in interpreting results in these cases.
 Second, as a London model, Brandt and Clem's method assumes that all superconducting films behave linearly and without dissipation, and that the applied magnetic field and current density are well below the critical field and critical current density of all films in a device.
-Third, while currents associated with vortices and flux trapped in holes can be modeled, \SuperScreen does not enforce fluxoid quantization or treat the energetics of vortex nucleation in films or fluxoid transitions in multiply-connected films.
-For further discussion of these topics in the context of the present model, see Refs.~\cite{Brandt_Clem_2004, Clem_Brandt_2005}.
+% Third, while currents associated with vortices and flux trapped in holes can be modeled, \SuperScreen does not treat the energetics of vortex nucleation in films or fluxoid transitions in multiply-connected films.
+For further discussion of these topics in the context of the present model, see Refs.~\cite{Brandt2004-ew, Clem2005-ye}.
+Third, as currently implemented, \SuperScreen does not support ``terminal currents,'' i.e.
+currents flowing in one terminal of a device and out another terminal.
+This means that inductance calculations are limited to structures with holes, in which all applied currents are circulating currents associated with trapped flux (see Sections~\ref{section:model:holes} and~\ref{section:examples:mutual-inductance}).
+Terminal currents can be included in the stream function-base model by setting appropriate boundary conditions~\cite{Khapaev1997-kw,Khapaev2001-xq,Khapaev2001-pw,Muller2021-ci}.
 Finally, care should be taken to ensure that for a given model the mesh is of sufficient density and quality that, to within the desired precision, the results of simulations do not depend on mesh size.
 
-Potential improvements to \SuperScreen include: more complete treatment of multiply-connected superconductors~\cite{Clem_Brandt_2005}, more sophisticated mesh generation (e.g.
-automated local mesh refinement based on device geometry), automated determination of solution convergence for models with multiple layers, an improved interface for generating complex device geometries (for example using 2D constructive solid geometry), and further optimization for memory and CPU efficiency (especially in the context of parallel processing).
+Potential improvements to \SuperScreen include: support for terminal currents as discussed above, more sophisticated mesh generation (e.g.
+automated local mesh refinement based on device geometry), automated determination of solution convergence for models with multiple layers, an improved interface for generating complex device geometries (for example using 2D constructive solid geometry), and further optimization for memory and CPU efficiency.
 
@@
 
+\section{Existing tools}
+\label{appendix:other-tools}
+
+FastHenry, a widely-used 3D (normal metal) inductance extraction tool from MIT~\cite{Kamon1994-ck}, has been extended to support superconducting elements~\cite{wrcad, XicTools}.
+This modified version of FastHenry is used for inductance extraction in the commercial software InductEx~\cite{Fourie2011-wl}.
+While FastHenry is open-source, it is written in C and must be compiled for a specific computer architecture and operating system.
+FastHenry executables compiled for several common operating systems are available as part of the open-source XicTools superconducting integrated circuit design suite from Whiteley Research, Inc~\cite{wrcad, XicTools}.
+A 2D London model based on a scalar stream function, much like the model used by \SuperScreen~\cite{Brandt2004-ew, Brandt2005-wj} (described in detail in Section~\ref{section:model}), forms the basis of the 3D-MLSI software package, which is also written in C and is not open-source~\cite{Khapaev1997-kw, Khapaev2001-xq, Khapaev2001-pw}.
+\SuperScreen is an open-source, portable, user-friendly tool for modeling the magnetic response of 2D superconductors, designed to lower the barrier to entry to quantitative modeling of superconducting devices.
+
 \section{Laplace operator}
@@
 The definition of the discrete Laplace operator $\mathbf{\nabla}^2$ (also called the Laplace-Beltrami operator) deserves special attention, as it reduces the problem of solving a partial differential equation $\nabla^2g(x,y)=f(x,y)$ to the problem of solving a matrix equation
-$\mathbf{\nabla}^2\mathbf{g}=\mathbf{f}$~\cite{Reuter_Biasotti_Giorgi_Patane_Spagnuolo_2009}.
+$\mathbf{\nabla}^2\mathbf{g}=\mathbf{f}$~\cite{Reuter2009-hr}.
 As described in Ref.~\cite{Crane_Vouga_2014}, the Laplace operator $\mathbf{\nabla}^2$ for a mesh is defined in terms of two matrices, the mass matrix $\mathbf{M}$ and the
@@
 Finally, the Laplace operator is given by $\mathbf{\nabla}^2 = \mathbf{M}^{-1}\mathbf{L}$.
-
-The matrix $\mathbf{w}$ in Eqs.~\ref{eq:field_from_kernel_num} and \ref{eq:Heff_sub_num} that is used, together with the kernel matrix $\mathbf{Q}$, to approximate the dipole kernel $Q_z(\vec{r},\vec{r}')$ (Eq.~\ref{eq:kernels}) is simply a normalized version of the weight matrix $\mathbf{W}$ used in defining the Laplace operator.
-The relationship between $\mathbf{w}$ and $\mathbf{W}$ is given by:
-$$
-    w_{ij} = \begin{cases}
-        1&\text{if }i = j\\
-        W_{ij} / \sum_{i\neq j} W_{ij}&\text{otherwise.}
-    \end{cases}
-$$
 
@@
 
-\section{Convergence of multi-layer solutions}
-\label{appendix:convergence}
-
 % \section{Scaling with number of layers}
@@
 As discussed above, one can solve many models involving the same \inline{Device} in parallel across multiple CPUs using the \inline{superscreen.solve_many()} function.
-The recommended method for parallel processing is using \inline{ray}, a library for distributed computing using shared memory~\cite{ray_2018}.
+The recommended method for parallel processing is using \inline{ray}, a library for distributed computing using shared memory~\cite{Moritz2018-mt}.
 Note that at the time of writing, \inline{ray} support for Windows is experimental and under active development.

### 2021-11-09 main.tex
Updates from Overleaf

@@
 
-There have been many previous numerical studies of magnetic screening and inductance extraction in thin film and two-dimensional (2D) superconducting devices~\cite{Jaycox1981-zl, Ketchen1982-at, Ketchen2012-mb, Hildebrandt1995-uw, Khapaev1997-kw, Khapaev2001-xq, Khapaev2001-pw, Babaei_Brojeny2003-la, Brandt2004-ew, Brandt2005-wj, Clem2005-ye, Muller2021-ci}.
+There have been many previous numerical studies of magnetic screening and inductance extraction in thin film and two-dimensional (2D) superconducting devices~\cite{Jaycox1981-zl, Ketchen1982-at, Ketchen2012-mb, Hildebrandt1995-uw, Khapaev1997-kw, Khapaev2001-xq, Khapaev2001-pw, Babaei_Brojeny2003-la, Brandt2004-ew, Brandt2005-wj, Clem2005-ye, Muller2021-ci, Jackman2016-mf}.
 However, few software tools for this task exist and those that are available are closed-source, are written in low-level compiled languages like C, and/or require the use of specialized file formats or separate computer aided design (CAD) software for defining device geometries and model configurations.\footnote{A brief summary of existing tools can be found in \ref{appendix:other-tools}, and a more thorough overview in Ref.~\cite{Gaj1999-ls}.} Most of these tools are intended for use in the design of superconducting integrated circuits for rapid single flux quantum (RSFQ) logic and are primarily used for inductance extraction~\cite{Gaj1999-ls}.
@@
 In Section~\ref{section:examples}, we demonstrate how to perform a few simple types of simulations using \SuperScreen and compare the results to previous numerical and analytical solutions.
-Finally, in Section~\ref{section:conlusion}, we by discussing applications, limitations, and possible extensions of the package.
+Finally, in Section~\ref{section:conlusion}, we conclude by discussing applications, limitations, and possible extensions of the package.
 
@@
 At the time of writing, the test suite is executed using Python versions 3.6 through 3.9, and the test coverage is $>95\%$.
-Any changes to the \inline{main} branch of the repository also trigger an automatic re-build of the online documentation, which is located at \inline{superscreen.readthedocs.io}~\cite{superscreen-rtd}.
+Any changes to the \inline{main} branch of the repository also trigger an automatic re-build of the online documentation~\cite{superscreen-rtd}.
 Stable versions of the package are tagged on GitHub and uploaded to PyPI, the Python Package Index.
-The source code and documentation are covered by the MIT License.
-
-\SuperScreen has several important dependencies beyond the Python standard library: \inline{numpy}~\cite{Harris2020-xv} and \inline{scipy}~\cite{Virtanen2020-zz} for numerics, \inline{pint}~\cite{Grecco} for handling physical units, \inline{matplotlib}~\cite{Hunter2007-il} for visualization, \inline{meshpy}~\cite{Klockner,Shewchuk,Shewchuk1996-va} and \inline{optimesh}~\cite{Schlomer2021-ua} for mesh generation, \inline{dill}~\cite{McKerns} for serializing objects to disk and between processes, and \inline{ray}~\cite{Moritz2018-mt,ray-docs} for parallel processing with shared memory (see~\ref{section:parallel}).
+The source code and documentation are covered by the MIT License.\footnote{\href{https://opensource.org/licenses/MIT}{https://opensource.org/licenses/MIT}}
+
+\SuperScreen has several important dependencies beyond the Python standard library: \inline{numpy}~\cite{Harris2020-xv} and \inline{scipy}~\cite{Virtanen2020-zz} for numerics, \inline{pint}~\cite{Grecco} for handling physical units, \inline{matplotlib}~\cite{Hunter2007-il} for visualization, \inline{meshpy}~\cite{Klockner, Shewchuk, Shewchuk1996-va} and \inline{optimesh}~\cite{Schlomer2021-ua} for mesh generation, and \inline{ray}~\cite{Moritz2018-mt,ray-docs} for parallel processing with shared memory (see~\ref{section:parallel}).
 
@@
 
-\begin{code}
-\begin{minted}[fontsize=\small]{python}
-import numpy as np
-
-# Simulate the response of the square ring to a uniform applied field of 0.5 mT
-applied_field = sc.sources.ConstantField(0.5)
-field_units = "mT"
-solutions = sc.solve(
-    device=square_ring, applied_field=applied_field, field_units=field_units,
-)
-assert len(solutions) == 1 # Since there is only one layer in this Device
-uniform_field_solution = solutions[-1]
-
-# Simulate a current circulating around the hole in the ring
-# (with no applied field).
-trapped_flux_solution = sc.solve(
-    device=square_ring, applied_field=None, circulating_currents=dict(hole="1 mA"),
-)[-1]
-
-# Specify a sequence of (x, y) coordinates to plot cross-sections
-# of the simulated currents and fields.
-xs = np.linspace(-5.5, 5.5, 201) # [microns]
-cross_sections = [ # Two sets of [x, y] coordinates
-    np.stack([xs, xs], axis=1), # diagonal cross-section
-    np.stack([xs, np.zeros_like(xs)], axis=1), # horizontal cross-section
-]
-for solution in (uniform_field_solution, trapped_flux_solution):
-    solution.plot_currents(cross_section_coords=cross_sections, units="mA/um")
-    solution.plot_fields(cross_section_coords=cross_sections)
-\end{minted}
-\captionof{listing}{Solves for the current and magnetic field distributions for the \inline{square_ring} device given a uniform applied field, and circulating current with no applied field, and plots the resulting sheet current and field.}
-\label{code:ring_circulating_current}
-\end{code}
-
-Code Block~\ref{code:ring_circulating_current} solves two models involving the \inline{square_ring} device, which was generated using Code Blocks~\ref{code:device} and \ref{code:mesh_generation}.
+% \begin{code}
+% \begin{minted}[fontsize=\small]{python}
+% import numpy as np
+
+% # Simulate the response of the square ring to a uniform applied field of 0.5 mT
+% applied_field = sc.sources.ConstantField(0.5)
+% field_units = "mT"
+% solutions = sc.solve(
+%     device=square_ring, applied_field=applied_field, field_units=field_units,
+% )
+% assert len(solutions) == 1 # Since there is only one layer in this Device
+% uniform_field_solution = solutions[-1]
+
+% # Simulate a current circulating around the hole in the ring
+% # (with no applied field).
+% trapped_flux_solution = sc.solve(
+%     device=square_ring, applied_field=None, circulating_currents={"hole" : "1 mA"},
+% )[-1]
+
+% # Specify a sequence of (x, y) coordinates to plot cross-sections
+% # of the simulated currents and fields.
+% xs = np.linspace(-5.5, 5.5, 201) # [microns]
+% cross_sections = [ # Two sets of [x, y] coordinates
+%     np.stack([xs, xs], axis=1), # diagonal cross-section
+%     np.stack([xs, np.zeros_like(xs)], axis=1), # horizontal cross-section
+% ]
+% for solution in (uniform_field_solution, trapped_flux_solution):
+%     solution.plot_currents(cross_section_coords=cross_sections, units="mA/um")
+%     solution.plot_fields(cross_section_coords=cross_sections)
+% \end{minted}
+% \captionof{listing}{Solves for the current and magnetic field distributions for the \inline{square_ring} device given a uniform applied field, and circulating current with no applied field, and plots the resulting sheet current and field.}
+% \label{code:ring_circulating_current}
+% \end{code}
+
+% Code Block~\ref{code:ring_circulating_current} solves two models involving the \inline{square_ring} device, which was generated using Code Blocks~\ref{code:device} and \ref{code:mesh_generation}.
 First, Meissner screening of a spatially uniform applied out-of-plane magnetic field and second, the response of the ring to trapped flux with an associated circulating current of 1 mA (with no applied magnetic field).
@@
 
-\begin{figure}
-    \centering
-    \includegraphics[width=\textwidth]{examples/images/square_ring_results.png}
-    \caption{Sheet current $\vec{J}(x, y)$ and out-of-plane magnetic field $\mu_0H_z(x, y)$ evaluated in the plane of a square ring with effective penetration depth $\Lambda=1\,\mu\mathrm{m}$ subject to (a, b) a uniform applied field of 0.5 mT or (c, d) trapped flux inducing a circulating current of 1 mA.
+% \begin{figure}
+%     \centering
+%     \includegraphics[width=\textwidth]{examples/images/square_ring_results.png}
+%     \caption{Sheet current $\vec{J}(x, y)$ and out-of-plane magnetic field $\mu_0H_z(x, y)$ evaluated in the plane of a square ring with effective penetration depth $\Lambda=1\,\mu\mathrm{m}$ subject to (a, b) a uniform applied field of 0.5 mT or (c, d) trapped flux inducing a circulating current of 1 mA.
 The sub-figures show the output of (a, c) \inline{Solution.plot_currents()} and (b, d) \inline{Solution.plot_fields()}, as shown in Code Block~\ref{code:ring_circulating_current}.
 For the current plots (a, c), the color-scale indicates the magnitude of the sheet current (or current density), $|\vec{J}|$, and the direction is indicated by the white streamlines.}
-    \label{fig:square-ring-results}
-\end{figure}
+%     \label{fig:square-ring-results}
+% \end{figure}
 
@@
 The sum of these two terms gives the fluxoid $\Phi^f_S$.
-
-As described in Section~\ref{section:model:fluxoid}, for a valid solution to the static 2D London equation as formulated in Equation~\ref{eq:london}, the fluxoid $\Phi^f_S$ should have the following properties:
-\begin{enumerate}
-    \item{$\Phi^f_S = \sum_{\mathrm{vortices}\,v}\Phi_v$ for any region $S$ lying completely within a superconducting film that contains a set of vortices $v$, each containing flux $\Phi_v$ (and $\Phi^f_S = 0$ if $S$ contains no vortices).}
-    \item{$\Phi^f_S = \Phi_h$ for any region $S$ that contains a hole $h$, where $\Phi_h$ is a constant (i.e.
-does not depend on the specific region $S$ or path $\partial S$) but need not be quantized in units of $\Phi_0$.}
-\end{enumerate}
-
-A demonstration of these properties for the case of the square ring with effective penetration depth $\Lambda=1\,\mu\mathrm{m}$, inner side length $5\,\mu\mathrm{m}$, and outer side length $10\,\mu\mathrm{m}$ subject to a uniform applied field of 0.1 mT is shown in Figure~\ref{fig:fluxoid}.
-Property 1 is shown in the first two rows, and property 2 is shown in the last row.
-See the figure caption for a detailed explanation of the results.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=\textwidth]{examples/images/fluxoid_combined.png}
-    \caption{Demonstration of the fluxoid properties listed in Section~\ref{section:examples:fluxoid} for a square ring with $\Lambda=1\,\mu\mathrm{m}$, inner side length $5\,\mu\mathrm{m}$, and outer side length $10\,\mu\mathrm{m}$, whose outline is shown with white (black) lines in the left (middle) column, subject to a uniform applied field of 0.1 mT.
-The left and middle columns show the computed current density and out-of-plane-field, overlaid with several regions $S$ for which the fluxoids $\Phi^f_S$, calculated using \inline{Solution.polygon_fluxoid()}, are shown in the right column.
-The colors of the paths in the left and middle columns correspond to the colors of the bars in the right column.
-Top row (a - c): The fluxoid $\Phi^f_S$ vanishes for all simply-connected regions containing no vortices.
-The errors in (c) are given by $|\Phi^f_S / \Phi^f_{S,\,\text{(flux part)}}|$.
-Middle row (d - f): For simply-connected regions containing a set of vortices $v$, each carrying flux $\Phi_v$, the fluxoid is given by $\sum_v\Phi_v$.
-In this case, the body of the square ring contains both ``positive'' ($\Phi_v=\Phi_0$, counter-clockwise circulating current) and ``negative'' ($\Phi_v=-\Phi_0$, clockwise circulating current) vortices, which appear in (e) as yellow and blue dots respectively.
-The expected value for the fluxoid for each region $S$ given in units of $\Phi_0$ by (number of yellow vortices lying inside $S$) - (number of blue vortices lying inside $S$), and the errors in (f) are reported relative to this expected value.
-Bottom row (g - i): The fluxoid is approximately equal for all regions $S$ containing a given hole, shown here for both circular ($S = 0, 1, 2$) and square ($S=3, 4, 5, 6$) regions.}
-    \label{fig:fluxoid}
-\end{figure}
+See \ref{appendix:fluxoid} for a demonstration of the fluxoid properties listed in Section~\ref{section:model:fluxoid}.
 
@@
 For a given applied field $H_{z,\,\mathrm{applied}}$ we can choose $I_h$, the current circulating around the hole in the ring, such that the fluxoid $\Phi^f_S=n\Phi_0$ for a region $S$ containing the hole.
-If there is a single hole, this is simply a root finding problem (see Code Block~\ref{code:fluxoid-root}).
-For a structure with $N_h$ holes, we can specify $N_h$ fluxoids $\Phi^f_h$ and find the circulating currents $I_h$ by minimizing, in the least-squares sense, the deviation between each fluxoid and its desired value.
+If there is a single hole, this is simply a root finding problem.
+For a structure with $N_h$ holes, we can specify $N_h$ fluxoids $\Phi^f_h$ and find the circulating currents $I_h$ by minimizing the deviation of each fluxoid from some assumed value.
+These two calculations are implemented in the \inline{superscreen.find_fluxoid_solution()} function.
+
+Here, we use \inline{superscreen.find_fluxoid_solution()} to compute the current and field distributions in and around a film with a single hole in the $n=1$ fluxoid state as a function of the film's effective penetration depth, $\Lambda$.
+
+\subsection{Pearl vortices in thin films}
+\label{section:examples:pearl-vortices}
+Vortices trapped in 2D superconductors ($d\ll\lambda$, where $d$ is the film thickness and $\lambda$ is the London penetration depth), i.e.
+``Pearl vortices'', are associated with different current and magnetic field distributions than Abrikosov vortices trapped in bulk type-II superconductors~\cite{Pearl1964-cl}.
+The 2D Fourier transform $\tilde{H}_z(\vec{k}, z)$ of the out-of-plane component of the magnetic field $H_z(\vec{r}, z)$ from a Pearl vortex located at the origin $x=y=z=0$ is given by
+
+\begin{equation}
+    \tilde{H}_z(\vec{k}, z)=\mathcal{F}\{H_z(\vec{r}, z)\}=\frac{1}{\mu_0}\frac{\Phi_0e^{-|\vec{k}||z|}}{1+2\Lambda|\vec{k}|},
+    \label{eq:pearl}
+\end{equation}
+where $\mathcal{F}\{\cdot\}$ is the 2D Fourier transform, $\vec{k}=(k_x, k_y)$ are in-plane spatial frequencies, $z$ is the out-of-plane position at which the field is evaluated, and $2\Lambda = 2\lambda^2 / d$ is the Pearl length~\cite{Pearl1964-cl, Tafuri2004-ap}.
+The real-space magnetic field distribution near a Pearl vortex can be calculated numerically by taking the inverse Fourier transform of Equation~\ref{eq:pearl}: $H_z(\vec{r}, z)=\mathcal{F}^{-1}\{\tilde{H}_z(\vec{k}, z)\}$.
+The field distributions generated by \SuperScreen in the presence of vortices as described in Sections~\ref{section:model:vortices} and~\ref{section:implementation} agree to within a few percent with the distributions obtained using this Fourier transform method, as demonstrated in Code Block~\ref{code:pearl-vortex} and Figures XXX.
 
@@
 \begin{minted}[fontsize=\small]{python}
-from scipy import optimize
-
-def find_fluxoid_solution(
-    device: sc.Device,
-    applied_field: sc.Parameter,
-    hole_name: str,
-    polygon: np.ndarray,
-    fluxoid_n: int = 0,
-    **solve_kwargs,
-) -> sc.Solution:
-
-    solution = None
-
-    def residual_fluxoid(current: float) -> float:
-        """Returns (actual_fluxoid - desired_fluxoid) in units of Phi_0."""
-        nonlocal solution
+# Create a device representing square thin film.
+device = sc.Device(
+    "film",
+    layers=[sc.Layer("base", Lambda=0, z0=0)],
+    films=[sc.Polygon("film", layer="base", points=sc.geometry.square(20))],
+    # Add an abstract_polygon near the vortex position so that
+    # that region will be meshed densely.
+    abstract_regions=[
+        sc.Polygon("circle", layer="base", points=sc.geometry.circle(0.1)),
+    ],
+    length_units="um",
+)
+device.make_mesh(min_triangles=8000)
+# Specify the vortex position.
+vortices = [sc.Vortex(x=0, y=0, layer="base")]
+# Sweep Lambda, solve the model, and evaluate the field at the given coordinates.
+Lambdas = np.linspace(0, 1, 6) # [device.length_units]
+solutions = []
+for Lambda in Lambdas:
+    device.layers["base"].Lambda = Lambda
     solution = sc.solve(
-            device=device,
-            applied_field=applied_field,
-            circulating_currents={hole_name: current},
-            **solve_kwargs,
+        device=device, vortices=vortices, field_units="Phi_0/um**2"
     )[-1]
-        layer_name = device.holes[hole_name].layer
-        total_fluxoid = sum(solution.polygon_fluxoid(polygon)[layer_name])
-        return total_fluxoid.to("Phi_0").magnitude - fluxoid_n
-
-    # Replace optimize.root_scalar with optimize.minimize for multiple holes.
-    result = optimize.root_scalar(residual_fluxoid, x0=-1, x1=1)
-    # Return the optimal Solution
-    return solution
+    solutions.append(solution)
 \end{minted}
-\captionof{listing}{Given an applied field, this function solves for the current and field distribution in a \inline{Device} with a single hole for a specified fluxoid state $\Phi^f_S=n\Phi_0$ using root finding.}
-\label{code:fluxoid-root}
+\captionof{listing}{}
+\label{code:pearl-vortex}
 \end{code}
 
-\subsection{Calculating mutual inductance}
+\subsection{Self-inductance and mutual inductance}
 \label{section:examples:mutual-inductance}
@@
 The mutual inductance values for a set of holes form a mutual inductance matrix.
-The diagonals of the mutual inductance matrix are the hole self-inductances ($M_{ii}=L_i$, the self-inductance of hole $i$), and the matrix must be symmetric ($M_{ij}=M_{ji}$) due to the reciprocity theorem.
+The diagonals of the mutual inductance matrix are the hole self-inductances ($M_{ii}=L_i$, the self-inductance of hole $i$), and the matrix is symmetric ($M_{ij}=M_{ji}$) due to the reciprocity theorem.
 If the penetration depth of the film containing hole $i$ is $\Lambda = 0$, then no field penetrates the film and the fluxoid $\Phi^f_{S_i}$ is equal to $\Phi_i$, the flux through hole $i$.
@@
 Clem and Brandt~\cite{Brandt2004-ew} and Khapaev~\cite{Khapaev1997-kw} calculated the self-inductance of circular and square rings as a function of the ratio of inner and outer diameters.
+
+\subsection{Application: scanning SQUID susceptometry}
+\label{section:examples:susceptometry}
+
+In scanning superconducting quantum interference device (SQUID) susceptometry, the diamagnetic susceptibility of a superconducting sample is measured by bringing the sample close to a pair of superconducting loops.
+The first loop, called the ``pickup loop" is attached to a SQUID circuit that sensitively measures the magnetic flux threading the loop.
+The second loop, called the ``field coil," carries a known current and applies a known magnetic field to both the pickup loop and the sample.
+The superconducting sample screens the magnetic field from the field coil, modifying the amount of flux threading the pickup loop.
+Thus the mutual inductance between the field coil and pickup loop provides a measure of the sample's diamagnetic susceptibility, which is in turn a measure of the sample's penetration depth.
+
+Analysis developed to interpret the results of scanning SQUID susceptometry measurements makes several simplifying assumptions that are not always satisfied: 1) the sample's effective penetration depth $\Lambda$ (or Pearl length $2\Lambda$) is spatially homogeneous, 2) the sample is much larger than the field coil, and 3) the field coil and pickup loop can be approximated as one-dimensional coaxial, coplanar circular loops~\cite{Kirtley_Kalisky_2012}.
+
+% \begin{figure}[!h]
+% \centering
+% \begin{subfigure}{.35\textwidth}
+%   \centering
+%   \includegraphics[width=\linewidth]{examples/images/squid_susceptometry/squid_with_sample_mesh.png}
+%   \label{fig:squid_mesh}
+%   \caption{}
+% \end{subfigure}%
+% \hspace{10pt}
+% \begin{subfigure}{.5\textwidth}
+%   \centering
+%   \includegraphics[width=\linewidth]{examples/images/squid_susceptometry/squid_with_sample_M0_convergence.png}
+%   \label{fig:squid_convergence}
+%   \caption{}
+%   \caption{Fractional change in flux though all polygons vs.
+solver iteration with a current of $1\,\mathrm{mA}$ flowing in the field coil (\inline{fc}).
+The mutual inductance $M_0$ is given by the flux through the pickup loop (\inline{pl_hull}) divided by the field coil current.}
+% \end{subfigure}%
+% \caption{(a): Device polygons and mesh for the SQUID susceptometer model.
+(b) Fractional change in flux though all polygons vs.
+solver iteration with a current of $1\,\mathrm{mA}$ flowing in the field coil (\inline{fc}).
+The mutual inductance $M_0$ is given by the flux through the pickup loop (\inline{pl_hull}) divided by the field coil current.}
+% \label{fig:susceptometry}
+% \end{figure}
+
+Figure~\ref{fig:susceptometry}(a) shows a \inline{Device} representing field coil and pickup loop of an actual scanning SQUID sensor.
+In addition to the field coil and pickup loop, there are superconducting shields that limit the amount of magnetic flux that can penetrate the leads connecting the loops to the rest of the circuit (the rest of the circuit is not modeled).
+There are three relevant layers of superconducting films: the base electrode (``BE"), which is furthest from the sample contains the field coil; the first wiring layer (``W1"), which contains the pickup loop and a shield covering the field coil leads; and the second wiring layer (``W2"), which is closest to the sample and contains a shield covering the pickup loop leads.
+The device also contains a layer and film representing the superconducting sample.
+
+To model a SQUID susceptometry measurement, we first calculate $M_0$, the mutual inductance between the field coil and pickup loop in the absence of the sample.
+This can be done by temporarily setting the sample layer effective penetration depth to a very large value such that it essentially does not screen the field from the field coil (in this case, we set $\Lambda = 10^5\,\mu\mathrm{m}$).
+We then model the field from a known current flowing in the field coil following Section~\ref{section:model:holes} and self-consistently calculate the response of both the sample and the other superconducting layers of the SQUID sensor following Section~\ref{section:model:multilayer}.
+To ensure that the 2D current distribution in the field coil is approximately uniform (as we would expect for a real applied current), we set the field coil layer effective penetration depth to be greater than the width of the field coil conductor.
+
+Once $M_0$ is known, we can ``turn on" the sample's diamagnetic response by setting its effective penetration depth $\Lambda$ to the desired value and compute $M(z, \Lambda)$ for a given vertical distance $z$ between the sample and the SQUID as described in the previous paragraph.
+The SQUID susceptibility signal is then $M(z, \Lambda) - M_0$, the change in mutual inductance between the field coil and pickup loop due to the presence of the sample (usually given in units of $\Phi_0/\mathrm{A}$, where $\Phi_0$ is the superconducting flux quantum).
+The susceptibility can also be normalized to the bare mutual inductance $M_0$, giving a dimensionless susceptibility $\chi(z, \Lambda)=[M(z, \Lambda) - M_0] / M_0$.
 
@@
 Potential improvements to \SuperScreen include: support for terminal currents as discussed above, more sophisticated mesh generation (e.g.
-automated local mesh refinement based on device geometry), automated determination of solution convergence for models with multiple layers, an improved interface for generating complex device geometries (for example using 2D constructive solid geometry), and further optimization for memory and CPU efficiency.
+automated local mesh refinement based on device geometry), automated determination of solution convergence for models with multiple layers, an improved interface for generating complex device geometries (for example via integration with standard integrated circuit layout software), and further optimization for memory and CPU efficiency.
 
@@
 
+Here, we briefly describe existing software tools for modeling the magnetic response of superconducting devices, most of which are specifically designed for inductance extraction for superconducting integrated circuits.
 FastHenry, a widely-used 3D (normal metal) inductance extraction tool from MIT~\cite{Kamon1994-ck}, has been extended to support superconducting elements~\cite{wrcad, XicTools}.
-This modified version of FastHenry is used for inductance extraction in the commercial software InductEx~\cite{Fourie2011-wl}.
+This modified version of FastHenry has been used for inductance extraction in the commercial software InductEx~\cite{Fourie2011-wl}.
 While FastHenry is open-source, it is written in C and must be compiled for a specific computer architecture and operating system.
 FastHenry executables compiled for several common operating systems are available as part of the open-source XicTools superconducting integrated circuit design suite from Whiteley Research, Inc~\cite{wrcad, XicTools}.
-A 2D London model based on a scalar stream function, much like the model used by \SuperScreen~\cite{Brandt2004-ew, Brandt2005-wj} (described in detail in Section~\ref{section:model}), forms the basis of the 3D-MLSI software package, which is also written in C and is not open-source~\cite{Khapaev1997-kw, Khapaev2001-xq, Khapaev2001-pw}.
-\SuperScreen is an open-source, portable, user-friendly tool for modeling the magnetic response of 2D superconductors, designed to lower the barrier to entry to quantitative modeling of superconducting devices.
+A 2D London model based on a scalar stream function, much like the model used by \SuperScreen~\cite{Brandt2004-ew, Brandt2005-wj} (described in detail in Section~\ref{section:model}), forms the basis of the 3D-MLSI software package~\cite{Khapaev1997-kw, Khapaev2001-xq, Khapaev2001-pw}, which is also written in C and is not open-source.
+For a more thorough overview and comparison of inductance extraction tools, see Ref.~\cite{Gaj1999-ls}.
 
@@
 
-% \section{Fluxoid calculation}
-% \label{appendix:fluxoid}
-
-% \SuperScreen allows one to calculate the fluxoid $\Phi^f_S$ for any polygonal region $S$ whose boundary $\partial S$ lies completely within a superconducting film (see Section~\ref{section:model:fluxoid}).
-This calculation is implemented as follows: The ``flux part''  is calculated using \inline{Solution.polygon_flux()}, which computes the flux through a polygon representing a region $S$ by averaging the field at the three vertices of each triangle $t$ that lies in $S$ to estimate the field $\mu_0H_{z, t}$ at the center of the triangle, then returns the flux $\sum_t \mu_0H_{z,t}A_t$, where $A_t$ is the area of triangle $t$.
-The ``supercurrent part'' is calculated by evaluating the vector current density $\vec{J}$ at each point in the path $\partial S$ using \inline{Solution.interp_current_density()}, then computing the integral $\oint_S\mu_o\Lambda(\vec{r})\vec{J}(\vec{r})\cdot\mathrm{d}\vec{r}$ using the trapezoid rule.
-The sum of these two terms gives the fluxoid $\Phi^f_S$.
-
-% As described in Section~\ref{section:model:fluxoid}, for a valid solution to the static 2D London equation as formulated in Equation~\ref{eq:london}, the fluxoid $\Phi^f_S$ should have the following properties:
-% \begin{enumerate}
-%     \item{$\Phi^f_S = \sum_{\mathrm{vortices}\,v}\Phi_v$ for any region $S$ lying completely within a superconducting film that contains a set of vortices $v$, each containing flux $\Phi_v$ (and $\Phi^f_S = 0$ if $S$ contains no vortices).}
-%     \item{$\Phi^f_S = \Phi_h$ for any region $S$ that contains a hole $h$, where $\Phi_h$ is a constant (i.e.
+\section{Fluxoid calculation}
+\label{appendix:fluxoid}
+As described in Section~\ref{section:model:fluxoid}, for a valid solution to the static 2D London equation as formulated in Equation~\ref{eq:london}, the fluxoid $\Phi^f_S$ should have the following properties:
+\begin{enumerate}
+    \item{$\Phi^f_S = \sum_{\mathrm{vortices}\,v}\Phi_v$ for any region $S$ lying completely within a superconducting film that contains a set of vortices $v$, each containing flux $\Phi_v$ (and $\Phi^f_S = 0$ if $S$ contains no vortices).}
+    \item{$\Phi^f_S = \Phi_h$ for any region $S$ that contains a hole $h$, where $\Phi_h$ is a constant (i.e.
 does not depend on the specific region $S$ or path $\partial S$) but need not be quantized in units of $\Phi_0$.}
-% \end{enumerate}
-
-% A demonstration of these properties for the case of the square ring with effective penetration depth $\Lambda=1\,\mu\mathrm{m}$, inner side length $5\,\mu\mathrm{m}$, and outer side length $10\,\mu\mathrm{m}$ subject to a uniform applied field of 0.1 mT is shown in Figure~\ref{fig:fluxoid}.
+\end{enumerate}
+
+A demonstration of these properties for the case of the square ring with effective penetration depth $\Lambda=1\,\mu\mathrm{m}$, inner side length $5\,\mu\mathrm{m}$, and outer side length $10\,\mu\mathrm{m}$ subject to a uniform applied field of 0.1 mT is shown in Figure~\ref{fig:fluxoid}.
+Property 1 is shown in the first two rows, and property 2 is shown in the last row.
 See the figure caption for a detailed explanation of the results.
 
-% \begin{figure}[h]
-%     \centering
-%     \includegraphics[width=\textwidth]{examples/images/fluxoid_combined.png}
-%     \caption{Demonstration of the fluxoid properties listed in \ref{appendix:fluxoid} for a square ring with $\Lambda=1\,\mu\mathrm{m}$, inner side length $5\,\mu\mathrm{m}$, and outer side length $10\,\mu\mathrm{m}$ (whose outline is shown with white lines in the left and middle columns) subject to a uniform applied field of 0.1 mT.
-The left and middle columns show the computed current density and out-of-plane-field, overlaid with several regions $S$ for which the fluxoid $\Phi^f_S$ (calculating using \inline{Solution.polygon_fluxoid()}) is shown in the right column.
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{examples/images/fluxoid_combined.png}
+    \caption{Demonstration of the fluxoid properties listed in Section~\ref{section:examples:fluxoid} for a square ring with $\Lambda=1\,\mu\mathrm{m}$, inner side length $5\,\mu\mathrm{m}$, and outer side length $10\,\mu\mathrm{m}$, whose outline is shown with white lines in the left and middle columns, subject to a uniform applied field of 0.1 mT.
+The left and middle columns show the computed current density and out-of-plane-field, overlaid with several regions $S$ for which the fluxoids $\Phi^f_S$ are calculated using \inline{Solution.polygon_fluxoid()}.
+The corresponding fluxoids are shown in the right column.
 The colors of the paths in the left and middle columns correspond to the colors of the bars in the right column.
@@
 The expected value for the fluxoid for each region $S$ given in units of $\Phi_0$ by (number of yellow vortices lying inside $S$) - (number of blue vortices lying inside $S$), and the errors in (f) are reported relative to this expected value.
-Bottom row (g - i): The fluxoid is approximately equal for all regions $S$ containing a given hole, shown here for both circular ($S = 0, 1, 2$) and square ($S=3, 4, 5, 6$) regions.}
-%     \label{fig:fluxoid}
-% \end{figure}
+Bottom row (g - i): Fluxoid path independence for the $n=0$ fluxoid state, shown here for both circular ($S = 0, 1, 2$) and square ($S=3, 4, 5$) paths.
+Here again, the errors are given by $|\Phi^f_S / \Phi^f_{S,\,\text{(flux part)}}|$.}
+    \label{fig:fluxoid}
+\end{figure}
 

### 2021-11-09 main.tex

@@
     solutions.append(solution)
+    # Use solution.field_at_position() to evaluate the magnetic field profile.
 \end{minted}
@@
 \end{code}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{examples/images/pearl.pdf}
+    \caption{Caption}
+    \label{fig:pearl}
+\end{figure}
 

### 2021-11-09 main.tex
Updates from Overleaf

@@
 This introduction to \SuperScreen is organized as follows: In Section~\ref{section:model}, we outline the model and its assumptions and in Section~\ref{section:implementation}, we describe its numerical implementation.
-In Section~\ref{section:overview}, we provide an overview of the structure of the \SuperScreen package, highlighting notable functions, classes, and features, and discuss some important development details.
+In Section~\ref{section:overview}, we provide an overview of the structure of the \SuperScreen package and discuss some important development details.
 In Section~\ref{section:examples}, we demonstrate how to perform a few simple types of simulations using \SuperScreen and compare the results to previous numerical and analytical solutions.
@@
 Vortices trapped in 2D superconductors ($d\ll\lambda$, where $d$ is the film thickness and $\lambda$ is the London penetration depth), i.e.
-``Pearl vortices'', are associated with different current and magnetic field distributions than Abrikosov vortices trapped in bulk type-II superconductors~\cite{Pearl1964-cl}.
+``Pearl vortices,'' are associated with different current and magnetic field distributions than Abrikosov vortices trapped in bulk type-II superconductors~\cite{Pearl1964-cl}.
 The 2D Fourier transform $\tilde{H}_z(\vec{k}, z)$ of the out-of-plane component of the magnetic field $H_z(\vec{r}, z)$ from a Pearl vortex located at the origin $x=y=z=0$ is given by
@@
 The real-space magnetic field distribution near a Pearl vortex can be calculated numerically by taking the inverse Fourier transform of Equation~\ref{eq:pearl}: $H_z(\vec{r}, z)=\mathcal{F}^{-1}\{\tilde{H}_z(\vec{k}, z)\}$.
-The field distributions generated by \SuperScreen in the presence of vortices as described in Sections~\ref{section:model:vortices} and~\ref{section:implementation} agree to within a few percent with the distributions obtained using this Fourier transform method, as demonstrated in Code Block~\ref{code:pearl-vortex} and Figures XXX.
+The field distributions generated by \SuperScreen in the presence of vortices as described in Sections~\ref{section:model:vortices} and~\ref{section:implementation} agree to within a few percent with the distributions obtained using this Fourier transform method, as demonstrated in Code Block~\ref{code:pearl-vortex} and Figure~\ref{fig:pearl}.
 
@@
 \end{minted}
-\captionof{listing}{}
+\captionof{listing}{Calculates the magnetic field distribution near a vortex trapped in a uniform superconducting film as a function of the film's effective penetration depth, $\Lambda$ (see Figure~\ref{fig:pearl}).}
 \label{code:pearl-vortex}
@@
     \includegraphics[width=\textwidth]{examples/images/pearl.pdf}
-    \caption{Caption}
+    \caption{Vortex field profiles calculated with \SuperScreen agree to within a few percent with the analytical solution (Eq.~\ref{eq:pearl}).
+(a) Cross section along the $x$-axis of the out-of-plane magnetic field $\mu_0H_z$ from a vortex located at the origin, $x=y=z=0\,\mu\mathrm{m}$ in a superconducting film, evaluated at a vertical distance $z=1\,\mu\mathrm{m}$ above the film for several different effective penetration depths $\Lambda$.
+(b) Cross-section along the $z$-axis of $\mu_0H_z$ from a vortex located at the origin, evaluated at $x=y=0\,\mu\mathrm{m}$, directly above the center of the vortex (logarithmic $y$ axis scale).
+In (a) and (b), the results from \SuperScreen are shown as open circles and the results from the Fourier transform method are shown as solid lines.
+(c) Percentage difference between the $\mu_0H_z$ calculated with \SuperScreen and the Fourier transform method for the $x$-axis cut shown in (a).
+(d) Percentage difference between the $\mu_0H_z$ calculated with \SuperScreen and the Fourier transform method for the $z$-axis cut shown in (b).}
     \label{fig:pearl}
@@
 Terminal currents can be included in the stream function-base model by setting appropriate boundary conditions~\cite{Khapaev1997-kw,Khapaev2001-xq,Khapaev2001-pw,Muller2021-ci}.
-Finally, care should be taken to ensure that for a given model the mesh is of sufficient density and quality that, to within the desired precision, the results of simulations do not depend on mesh size.
+Finally, care should be taken to ensure that for a given model the mesh is of sufficient density that, to within the desired precision, the results of simulations do not depend on mesh size.
 

### 2021-11-09 main.tex

@@
 
-\subsection{Calculating the fluxoid}
-\label{section:examples:fluxoid}
-
-\SuperScreen allows one to calculate the fluxoid $\Phi^f_S$ for any polygonal region $S$ whose boundary $\partial S$ lies completely within a superconducting film using the method \inline{Solution.polygon_fluxoid()} (see Section~\ref{section:model:fluxoid}, Eq.~\ref{eq:fluxoid}).
-We calculate the ``flux part''  $\int_S\mu_0H_z(\vec{r})\,\mathrm{d}^2r$ using \inline{Solution.polygon_flux()}, which computes the flux through a polygon representing a region $S$ by averaging the field at the three vertices of each triangle $t$ that lies in $S$ to estimate the field $\mu_0H_{z, t}$ at the center of the triangle, then returns the flux $\sum_t \mu_0H_{z,t}A_t$, where $A_t$ is the area of triangle $t$.
-We calculate the ``supercurrent part'' $\oint_S\mu_o\Lambda(\vec{r})\vec{J}(\vec{r})\cdot\mathrm{d}\vec{r}$ by evaluating the vector current density $\vec{J}$ at each point in the path $\partial S$ using \inline{Solution.interp_current_density()}, then computing the line integral along the path using the trapezoid rule.
-The sum of these two terms gives the fluxoid $\Phi^f_S$.
-See \ref{appendix:fluxoid} for a demonstration of the fluxoid properties listed in Section~\ref{section:model:fluxoid}.
-
-While the model doesn't ``know'' about fluxoid quantization, so to speak, we can nevertheless calculate current and field distributions for different fluxoid states $\Phi^f_S=n\Phi_0$.
-Consider again the circular or square ring.
-For a given applied field $H_{z,\,\mathrm{applied}}$ we can choose $I_h$, the current circulating around the hole in the ring, such that the fluxoid $\Phi^f_S=n\Phi_0$ for a region $S$ containing the hole.
-If there is a single hole, this is simply a root finding problem.
-For a structure with $N_h$ holes, we can specify $N_h$ fluxoids $\Phi^f_h$ and find the circulating currents $I_h$ by minimizing the deviation of each fluxoid from some assumed value.
-These two calculations are implemented in the \inline{superscreen.find_fluxoid_solution()} function.
-
-Here, we use \inline{superscreen.find_fluxoid_solution()} to compute the current and field distributions in and around a film with a single hole in the $n=1$ fluxoid state as a function of the film's effective penetration depth, $\Lambda$.
-
 \subsection{Pearl vortices in thin films}
@@
 The real-space magnetic field distribution near a Pearl vortex can be calculated numerically by taking the inverse Fourier transform of Equation~\ref{eq:pearl}: $H_z(\vec{r}, z)=\mathcal{F}^{-1}\{\tilde{H}_z(\vec{k}, z)\}$.
-The field distributions generated by \SuperScreen in the presence of vortices as described in Sections~\ref{section:model:vortices} and~\ref{section:implementation} agree to within a few percent with the distributions obtained using this Fourier transform method, as demonstrated in Code Block~\ref{code:pearl-vortex} and Figure~\ref{fig:pearl}.
+The field distributions generated by \SuperScreen in the presence of vortices as described in Sections~\ref{section:model:vortices} and~\ref{section:implementation} agree to within a few percent with the distributions obtained using this Fourier transform method, as demonstrated in Code Block~\ref{code:pearl-vortex} and Figure~\ref{fig:pearl}(c-e).
 
@@
     abstract_regions=[
-        sc.Polygon("circle", layer="base", points=sc.geometry.circle(0.1)),
+        sc.Polygon("circle", layer="base", points=sc.geometry.circle(0.25)),
     ],
@@
 # Sweep Lambda, solve the model, and evaluate the field at the given coordinates.
-Lambdas = np.linspace(0, 1, 6) # [device.length_units]
+Lambdas = np.linspace(0, 2, 5) # [device.length_units]
 solutions = []
@@
     solutions.append(solution)
-    # Use solution.field_at_position() to evaluate the magnetic field profile.
+    # Use solution.field_at_position() to evaluate the magnetic field profile,
+    # and Solution.polygon_fluxoid() to calculate fluxoids.
 \end{minted}
@@
 \end{figure}
+
+\subsection{Calculating the fluxoid}
+\label{section:examples:fluxoid}
+
+\SuperScreen allows one to calculate the fluxoid $\Phi^f_S$ for any polygonal region $S$ whose boundary $\partial S$ lies completely within a superconducting film using the method \inline{Solution.polygon_fluxoid()} (see Section~\ref{section:model:fluxoid}, Eq.~\ref{eq:fluxoid}).
+We calculate the ``flux part''  $\int_S\mu_0H_z(\vec{r})\,\mathrm{d}^2r$ using \inline{Solution.polygon_flux()}, which computes the flux through a polygon representing a region $S$ by averaging the field at the three vertices of each triangle $t$ that lies in $S$ to estimate the field $\mu_0H_{z, t}$ at the center of the triangle, then returns the flux $\sum_t \mu_0H_{z,t}A_t$, where $A_t$ is the area of triangle $t$.
+We calculate the ``supercurrent part'' $\oint_S\mu_o\Lambda(\vec{r})\vec{J}(\vec{r})\cdot\mathrm{d}\vec{r}$ by evaluating the vector current density $\vec{J}$ at each point in the path $\partial S$ using \inline{Solution.interp_current_density()}, then computing the line integral along the path using the trapezoid rule.
+The sum of these two terms gives the fluxoid $\Phi^f_S$.
+See \ref{appendix:fluxoid} for a demonstration of the fluxoid properties listed in Section~\ref{section:model:fluxoid}.
+
+While the model doesn't ``know'' about fluxoid quantization, so to speak, we can nevertheless calculate current and field distributions for different fluxoid states $\Phi^f_S=n\Phi_0$.
+Consider again the circular or square ring.
+For a given applied field $H_{z,\,\mathrm{applied}}$ we can choose $I_h$, the current circulating around the hole in the ring, such that the fluxoid $\Phi^f_S=n\Phi_0$ for a region $S$ containing the hole.
+If there is a single hole, this is simply a root finding problem.
+For a structure with $N_h$ holes, we can specify $N_h$ fluxoids $\Phi^f_h$ and find the circulating currents $I_h$ by minimizing the deviation of each fluxoid from some assumed value.
+These two calculations are implemented in the \inline{superscreen.find_fluxoid_solution()} function.
+
+Here, we use \inline{superscreen.find_fluxoid_solution()} to compute the current and field distributions in and around a film with a single hole in the $n=1$ fluxoid state as a function of the film's effective penetration depth, $\Lambda$.
 

### 2021-11-09 main.tex

@@
     \caption{Vortex field profiles calculated with \SuperScreen agree to within a few percent with the analytical solution (Eq.~\ref{eq:pearl}).
-(a) Cross section along the $x$-axis of the out-of-plane magnetic field $\mu_0H_z$ from a vortex located at the origin, $x=y=z=0\,\mu\mathrm{m}$ in a superconducting film, evaluated at a vertical distance $z=1\,\mu\mathrm{m}$ above the film for several different effective penetration depths $\Lambda$.
-(b) Cross-section along the $z$-axis of $\mu_0H_z$ from a vortex located at the origin, evaluated at $x=y=0\,\mu\mathrm{m}$, directly above the center of the vortex (logarithmic $y$ axis scale).
+(a) The fluxoid $\Phi_S^f$ for a circular region in the film with radius $r=1\,\mu\mathrm{m}$ centered at the position of the vortex core, as a function of the film's effective penetration depth $\Lambda$.
+As $\Lambda$ increases, so to does the supercurrent contribution to the fluxoid.
+(b) Error in the total simulated fluxoid relative to $\Phi_0$: $(\Phi_S^f(\Lambda) - \Phi_0) / \Phi_0$.
+(c) Cross section along the $x$-axis of the out-of-plane magnetic field $\mu_0H_z$ from a vortex located at the origin, $x=y=z=0\,\mu\mathrm{m}$ in a superconducting film, evaluated at a vertical distance $z=1\,\mu\mathrm{m}$ above the film for several different effective penetration depths $\Lambda$.
+(d) Percentage difference between the $\mu_0H_z$ calculated with \SuperScreen and the Fourier transform method for the $x$-axis cut shown in (c).
+(e) Cross-section along the $z$-axis of $\mu_0H_z$ from a vortex located at the origin, evaluated at $x=y=0\,\mu\mathrm{m}$, directly above the center of the vortex (logarithmic $y$ axis scale).
+(f) Percentage difference between the $\mu_0H_z$ calculated with \SuperScreen and the Fourier transform method for the $z$-axis cut shown in (e).
 In (a) and (b), the results from \SuperScreen are shown as open circles and the results from the Fourier transform method are shown as solid lines.
-(c) Percentage difference between the $\mu_0H_z$ calculated with \SuperScreen and the Fourier transform method for the $x$-axis cut shown in (a).
-(d) Percentage difference between the $\mu_0H_z$ calculated with \SuperScreen and the Fourier transform method for the $z$-axis cut shown in (b).}
+}
     \label{fig:pearl}

### 2021-11-09 main.tex

@@
     films=[sc.Polygon("film", layer="base", points=sc.geometry.square(20))],
-    # Add an abstract_polygon near the vortex position so that
-    # that region will be meshed densely.
-    abstract_regions=[
-        sc.Polygon("circle", layer="base", points=sc.geometry.circle(0.25)),
-    ],
     length_units="um",
 )
-device.make_mesh(min_triangles=8000)
+device.make_mesh(min_triangles=8_000)
 # Specify the vortex position.
@@
 Lambdas = np.linspace(0, 2, 5) # [device.length_units]
-solutions = []
 for Lambda in Lambdas:
     device.layers["base"].Lambda = Lambda
-    solution = sc.solve(
-        device=device, vortices=vortices, field_units="Phi_0/um**2"
-    )[-1]
-    solutions.append(solution)
+    solution = sc.solve(device=device, vortices=vortices)[-1]
     # Use solution.field_at_position() to evaluate the magnetic field profile,
@@
 \end{minted}
-\captionof{listing}{Calculates the magnetic field distribution near a vortex trapped in a uniform superconducting film as a function of the film's effective penetration depth, $\Lambda$ (see Figure~\ref{fig:pearl}).}
+\captionof{listing}{Creates a square superconducting film with side length $20\,\mu\mathrm{m}$ and calculates the magnetic field distribution near a vortex at the center of the film as a function of the the effective penetration depth, $\Lambda$ (see Figure~\ref{fig:pearl}).}
 \label{code:pearl-vortex}
@@
     \includegraphics[width=\textwidth]{examples/images/pearl.pdf}
-    \caption{Vortex field profiles calculated with \SuperScreen agree to within a few percent with the analytical solution (Eq.~\ref{eq:pearl}).
-(a) The fluxoid $\Phi_S^f$ for a circular region in the film with radius $r=1\,\mu\mathrm{m}$ centered at the position of the vortex core, as a function of the film's effective penetration depth $\Lambda$.
+    \caption{Vortex field profiles calculated with \SuperScreen agree with the analytical solution (Eq.~\ref{eq:pearl}) to within a few percent.
+Here, we model a vortex trapped at the center of a square superconducting film lying in the $x-y$ plane with side length $20\,\mu\mathrm{m}$ as a function of the film's effective penetration depth, $\Lambda$.
+(a) The fluxoid $\Phi_S^f$ for a circular region in the film with radius $r=1\,\mu\mathrm{m}$ centered on the vortex core.
 As $\Lambda$ increases, so to does the supercurrent contribution to the fluxoid.
 (b) Error in the total simulated fluxoid relative to $\Phi_0$: $(\Phi_S^f(\Lambda) - \Phi_0) / \Phi_0$.
-(c) Cross section along the $x$-axis of the out-of-plane magnetic field $\mu_0H_z$ from a vortex located at the origin, $x=y=z=0\,\mu\mathrm{m}$ in a superconducting film, evaluated at a vertical distance $z=1\,\mu\mathrm{m}$ above the film for several different effective penetration depths $\Lambda$.
+(c) Cross section along the $x$-axis of the out-of-plane magnetic field $\mu_0H_z$ from the vortex, evaluated at a vertical distance $z=1\,\mu\mathrm{m}$ above the film.
 (d) Percentage difference between the $\mu_0H_z$ calculated with \SuperScreen and the Fourier transform method for the $x$-axis cut shown in (c).
-(e) Cross-section along the $z$-axis of $\mu_0H_z$ from a vortex located at the origin, evaluated at $x=y=0\,\mu\mathrm{m}$, directly above the center of the vortex (logarithmic $y$ axis scale).
+(e) Cross-section along the $z$-axis of $\mu_0H_z$ directly above the center of the vortex (logarithmic $y$ axis scale).
 (f) Percentage difference between the $\mu_0H_z$ calculated with \SuperScreen and the Fourier transform method for the $z$-axis cut shown in (e).
-In (a) and (b), the results from \SuperScreen are shown as open circles and the results from the Fourier transform method are shown as solid lines.
+In (c) and (e), the results from \SuperScreen are shown as open circles and the results from the Fourier transform method are shown as solid lines.
 }

### 2021-11-09 main.tex
Updates from Overleaf

@@
 \SetupFloatingEnvironment{listing}{name=Code Block}
+\BeforeBeginEnvironment{code}{\begin{minipage}{\textwidth}}
+\AfterEndEnvironment{code}{\end{minipage}}
+\captionsetup[listing]{skip=0pt}
 
@@
 \begin{code}
+\captionof{listing}{The basic usage of \inline{superscreen.Parameters}.}
+\label{code:parameters}
 \begin{minted}[fontsize=\small]{python}
@@
 \end{minted}
-\captionof{listing}{The basic usage of \inline{superscreen.Parameters}.}
-\label{code:parameters}
 \end{code}
@@
 \begin{code}
+\captionof{listing}{A function that creates a \inline{Device} representing a circular or square ring centered at the origin.}
+\label{code:device}
 \begin{minted}[fontsize=\small]{python}
@@
 \end{minted}
-\captionof{listing}{A function that creates a \inline{Device} representing a circular or square ring centered at the origin.}
-\label{code:device}
 \end{code}
@@
 \begin{code}
+\captionof{listing}{Generating and visualizing the computational mesh. See Figure~\ref{fig:mesh} to view the resulting meshes.}
+\label{code:mesh_generation}
 \begin{minted}[fontsize=\small]{python}
@@
 \end{minted}
-\captionof{listing}{Generating and visualizing the computational mesh. See Figure~\ref{fig:mesh} to view the resulting meshes.}
-\label{code:mesh_generation}
 \end{code}
@@
 % \begin{code}
+% \captionof{listing}{Solves for the current and magnetic field distributions for the \inline{square_ring} device given a uniform applied field, and circulating current with no applied field, and plots the resulting sheet current and field.}
+% \label{code:ring_circulating_current}
 % \begin{minted}[fontsize=\small]{python}
@@
 % \end{minted}
-% \captionof{listing}{Solves for the current and magnetic field distributions for the \inline{square_ring} device given a uniform applied field, and circulating current with no applied field, and plots the resulting sheet current and field.}
-% \label{code:ring_circulating_current}
 % \end{code}
@@
 \end{itemize}
-\inline{Solutions} also have several visualization methods built in (see Figure~\ref{fig:square-ring-results} and Section~\ref{section:overview:visualization}).
+\inline{Solutions} also have several visualization methods built in (see Section~\ref{section:overview:visualization}).
 
@@
 
-See Code Block~\ref{code:ring_circulating_current} and  Figure~\ref{fig:square-ring-results} for an example of the usage and output of \inline{plot_fields()} and \inline{plot_currents()}.
+% See Code Block~\ref{code:ring_circulating_current} and  Figure~\ref{fig:square-ring-results} for an example of the usage and output of \inline{plot_fields()} and \inline{plot_currents()}.
 
@@
 
+To include vortices in a \SuperScreen model, one can simply input a \inline{list} of \inline{superscreen.Vortex} objects when calling \inline{superscreen.solve()} (see Code Block~\ref{code:pearl-vortex}).
+A \inline{Vortex} object specifies the $x,y$ position for the vortex core, the name of the superconducting layer in which the vortex is pinned, and the number of flux quanta $\Phi_0$ contained in the vortex (which is 1 by default).
+See Ref.~\cite{Brandt2005-wj} for a method to compute the self-energy and interaction energies of vortices in thin films.
+
 \begin{code}
+\captionof{listing}{Creates a square superconducting film with side length $20\,\mu\mathrm{m}$ and calculates the magnetic field distribution near a vortex at the center of the film as a function of the the effective penetration depth, $\Lambda$ (see Figure~\ref{fig:pearl}).}
+\label{code:pearl-vortex}
 \begin{minted}[fontsize=\small]{python}
@@
 \end{minted}
-\captionof{listing}{Creates a square superconducting film with side length $20\,\mu\mathrm{m}$ and calculates the magnetic field distribution near a vortex at the center of the film as a function of the the effective penetration depth, $\Lambda$ (see Figure~\ref{fig:pearl}).}
-\label{code:pearl-vortex}
 \end{code}
 
-\begin{figure}
+\begin{figure}[h]
     \centering
@@
 Here, we model a vortex trapped at the center of a square superconducting film lying in the $x-y$ plane with side length $20\,\mu\mathrm{m}$ as a function of the film's effective penetration depth, $\Lambda$.
-(a) The fluxoid $\Phi_S^f$ for a circular region in the film with radius $r=1\,\mu\mathrm{m}$ centered on the vortex core.
+(a) Cross section along the $x$-axis of the out-of-plane magnetic field $\mu_0H_z$ from the vortex, evaluated at a vertical distance $z=1\,\mu\mathrm{m}$ above the film.
+(b) Percentage difference between the $\mu_0H_z$ calculated with \SuperScreen and the Fourier transform method for the $x$-axis cut shown in (a).
+(c) Cross-section along the $z$-axis of $\mu_0H_z$ directly above the center of the vortex (logarithmic $y$ axis scale).
+(d) Percentage difference between the $\mu_0H_z$ calculated with \SuperScreen and the Fourier transform method for the $z$-axis cut shown in (c).
+In (a) and (c), the results from \SuperScreen are shown as open circles and the results from the Fourier transform method are shown as solid lines.
+(e) The fluxoid $\Phi_S^f$ for a circular region in the film with radius $r=1\,\mu\mathrm{m}$ centered on the vortex core.
 As $\Lambda$ increases, so to does the supercurrent contribution to the fluxoid.
-(b) Error in the total simulated fluxoid relative to $\Phi_0$: $(\Phi_S^f(\Lambda) - \Phi_0) / \Phi_0$.
-(c) Cross section along the $x$-axis of the out-of-plane magnetic field $\mu_0H_z$ from the vortex, evaluated at a vertical distance $z=1\,\mu\mathrm{m}$ above the film.
-(d) Percentage difference between the $\mu_0H_z$ calculated with \SuperScreen and the Fourier transform method for the $x$-axis cut shown in (c).
-(e) Cross-section along the $z$-axis of $\mu_0H_z$ directly above the center of the vortex (logarithmic $y$ axis scale).
-(f) Percentage difference between the $\mu_0H_z$ calculated with \SuperScreen and the Fourier transform method for the $z$-axis cut shown in (e).
-In (c) and (e), the results from \SuperScreen are shown as open circles and the results from the Fourier transform method are shown as solid lines.
-}
+(f) Error in the total simulated fluxoid relative to $\Phi_0$: $(\Phi_S^f(\Lambda) - \Phi_0) / \Phi_0$.}
     \label{fig:pearl}
@@
 \SuperScreen allows one to calculate the fluxoid $\Phi^f_S$ for any polygonal region $S$ whose boundary $\partial S$ lies completely within a superconducting film using the method \inline{Solution.polygon_fluxoid()} (see Section~\ref{section:model:fluxoid}, Eq.~\ref{eq:fluxoid}).
-We calculate the ``flux part''  $\int_S\mu_0H_z(\vec{r})\,\mathrm{d}^2r$ using \inline{Solution.polygon_flux()}, which computes the flux through a polygon representing a region $S$ by averaging the field at the three vertices of each triangle $t$ that lies in $S$ to estimate the field $\mu_0H_{z, t}$ at the center of the triangle, then returns the flux $\sum_t \mu_0H_{z,t}A_t$, where $A_t$ is the area of triangle $t$.
-We calculate the ``supercurrent part'' $\oint_S\mu_o\Lambda(\vec{r})\vec{J}(\vec{r})\cdot\mathrm{d}\vec{r}$ by evaluating the vector current density $\vec{J}$ at each point in the path $\partial S$ using \inline{Solution.interp_current_density()}, then computing the line integral along the path using the trapezoid rule.
+The ``flux part''  $\int_S\mu_0H_z(\vec{r})\,\mathrm{d}^2r$ is calculated using \inline{Solution.polygon_flux()}, which computes the flux through a polygon representing a region $S$ by averaging the field at the three vertices of each triangle $t$ that lies in $S$ to estimate the field $\mu_0H_{z, t}$ at the center of the triangle, then returns the flux $\sum_t \mu_0H_{z,t}A_t$, where $A_t$ is the area of triangle $t$.
+The ``supercurrent part'' $\oint_S\mu_o\Lambda(\vec{r})\vec{J}(\vec{r})\cdot\mathrm{d}\vec{r}$ is calculated by evaluating the vector current density $\vec{J}$ at each point in the path $\partial S$ using \inline{Solution.interp_current_density()}, then computing the line integral along the path using the trapezoid rule.
 The sum of these two terms gives the fluxoid $\Phi^f_S$.
-See \ref{appendix:fluxoid} for a demonstration of the fluxoid properties listed in Section~\ref{section:model:fluxoid}.
+
+Figure~\ref{fig:pearl}(e) shows the fluxoid for a circular region $S$ with radius $r=1\,\mu\mathrm{m}$ enclosing a Pearl vortex trapped in a film as a function of the film's effective penetration depth, $\Lambda$.
+When $\Lambda=0$, the screening currents decay very quickly away from the center of the vortex, so the ``supercurrent part'' of the $\Phi^f_S$ vanishes.
+With increasing $\Lambda$, the ``supercurrent part'' accounts for an increasing fraction of the total fluxoid.
+% See \ref{appendix:fluxoid} for a demonstration of the fluxoid properties listed in Section~\ref{section:model:fluxoid}.
 
@@
 \begin{code}
+\captionof{listing}{Starting and stopping \inline{ray} outside of \inline{superscreen.solve_many()} using the Python API.
+See the ``API and Package Reference" section of the \inline{ray} documentation for additional options in \inline{ray.init()}~\cite{ray-docs}.}
+\label{code:ray-python}
 \begin{minted}[fontsize=\small]{python}
@@
 \end{minted}
-\captionof{listing}{Starting and stopping \inline{ray} outside of \inline{superscreen.solve_many()} using the Python API.
-See the ``API and Package Reference" section of the \inline{ray} documentation for additional options in \inline{ray.init()}~\cite{ray-docs}.}
-\label{code:ray-python}
 \end{code}
@@
 \begin{code}
+\captionof{listing}{Starting and stopping \inline{ray} outside of \inline{superscreen.solve_many()} using the command line interface.
+See the \inline{ray} documentation for additional options in \inline{ray start}~\cite{ray-docs}.}
+\label{code:ray-cli}
 \begin{minted}[fontsize=\small]{bash}
@@
 \end{minted}
-\captionof{listing}{Starting and stopping \inline{ray} outside of \inline{superscreen.solve_many()} using the command line interface.
-See the \inline{ray} documentation for additional options in \inline{ray start}~\cite{ray-docs}.}
-\label{code:ray-cli}
 \end{code}

### 2021-11-17 main.tex

@@
 \AfterEndEnvironment{minted}{\end{tcolorbox}\end{center}}
+% \usemintedstyle[python]{vs}
 \usepackage{caption}
@@
 In Section~\ref{section:overview}, we provide an overview of the structure of the \SuperScreen package and discuss some important development details.
-In Section~\ref{section:examples}, we demonstrate how to perform a few simple types of simulations using \SuperScreen and compare the results to previous numerical and analytical solutions.
+In Section~\ref{section:examples}, we demonstrate how to perform several types of simulations using \SuperScreen and compare the results to previous numerical/analytical solutions and experimental results.
 Finally, in Section~\ref{section:conlusion}, we conclude by discussing applications, limitations, and possible extensions of the package.
@@
 Stable versions of the package are tagged on GitHub and uploaded to PyPI, the Python Package Index.
-The source code and documentation are covered by the MIT License.\footnote{\href{https://opensource.org/licenses/MIT}{https://opensource.org/licenses/MIT}}
-
-\SuperScreen has several important dependencies beyond the Python standard library: \inline{numpy}~\cite{Harris2020-xv} and \inline{scipy}~\cite{Virtanen2020-zz} for numerics, \inline{pint}~\cite{Grecco} for handling physical units, \inline{matplotlib}~\cite{Hunter2007-il} for visualization, \inline{meshpy}~\cite{Klockner, Shewchuk, Shewchuk1996-va} and \inline{optimesh}~\cite{Schlomer2021-ua} for mesh generation, and \inline{ray}~\cite{Moritz2018-mt,ray-docs} for parallel processing with shared memory (see~\ref{section:parallel}).
+The source code and documentation are provided under the MIT License.\footnote{\href{https://opensource.org/licenses/MIT}{https://opensource.org/licenses/MIT}}
+
+\SuperScreen has several important dependencies beyond the Python standard library: \inline{numpy}~\cite{Harris2020-xv} and \inline{scipy}~\cite{Virtanen2020-zz} for numerics, \inline{matplotlib}~\cite{Hunter2007-il} for visualization, \inline{pint}~\cite{Grecco} for handling physical units, \inline{shapely}~\cite{shapely} for creating and manipulating device geometries, \inline{meshpy}~\cite{Klockner, Shewchuk, Shewchuk1996-va} and \inline{optimesh}~\cite{Schlomer2021-ua} for mesh generation, and \inline{ray}~\cite{Moritz2018-mt,ray-docs} for parallel processing with shared memory (see~\ref{section:parallel}).
 
@@
 \begin{code}
-\captionof{listing}{The basic usage of \inline{superscreen.Parameters}.}
-\label{code:parameters}
 \begin{minted}[fontsize=\small]{python}
@@
 \end{minted}
+\captionof{listing}{The basic usage of \inline{superscreen.Parameters}, which compute a scalar value as a function of $x, y$ (and optionally $z$) coordinates.
+Note that the positional arguments \inline{x} and \inline{y} can be either floating point scalars or 1-dimensional \inline{numpy} arrays.}
+\label{code:parameters}
 \end{code}
@@
 
-Each layer can contain one or more superconducting films which may have one or more holes in them.
+Each layer can contain one or more superconducting \inline{films} which may have one or more \inline{holes} in them.
 Films and holes are represented by instances of the \inline{superscreen.Polygon} class.
-A \inline{Polygon} contains the name of the layer to which is belongs, an array specifying the coordinates of its vertices, and a method, \inline{Polygon.contains_points()}, which determines whether specified coordinates lie within the polygon or not.
+All polygons in a device must be simply-connected; a hole in a film is modeled as one \inline{Polygon} instance whose coordinates all lie within the \inline{Polygon} representing the film.
+% A \inline{Polygon} contains the name of the layer to which is belongs, an array specifying the coordinates of its vertices, and a method, \inline{Polygon.contains_points()}, which determines whether specified coordinates lie within the polygon or not.
+\inline{Polygons} can constructed and combined using set-theoretic operations.
+Table~\ref{table:polygon} shows the four methods available for combining a \inline{supercreen.Polygon} instance \inline{polygonA}, whose vertices lie in set $A$, with a polygon \inline{polygonB}, whose vertices lie in set $B$.
+Note that \inline{polygonB} can be another \inline{superscreen.Polygon}, an $n\times 2$ \inline{numpy} array of vertex coordinates, or one of several compatible types of objects from the \inline{shapely} package.
+
+\begin{table}[h]
+\centering
+\begin{tabular}{|l|l|l|}
+\hline
+\SuperScreen                             & Set-theoretic  & Boolean   \\ \hline \hline
+\inline{polygonA.union(polygonB)}        & $A\cup B$      & \inline{OR}      \\
+\inline{polygonA.intersection(polygonB)} & $A\cap B$      & \inline{AND}     \\
+\inline{polygonA.difference(polygonB)}   & $A\setminus B$ & \inline{AND NOT} \\
+\inline{polygonA.difference(polygonB, symmetric=True)} & $(A\setminus B)\cup(B\setminus A)$ & \inline{XOR} \\ \hline
+\end{tabular}
+\caption{Methods for combining \inline{superscreen.Polygon} objects, along with their corresponding set-theoretic and boolean logic operations.
+The vertices of \inline{polygonA} lie in set $A$ and the vertices of \inline{polygonB} lie in the set $B$.
+The object \inline{polygonB} can be a \inline{superscreen.Polygon}, an $n\times 2$ \inline{numpy} array of vertex coordinates, or a \inline{LineString}, \inline{LinearRing}, or \inline{Polygon} from the \inline{shapely} package.}
+\label{table:polygon}
+\end{table}
+
 In addition to superconducting films and holes, one may define ``abstract regions,'' which are polygons that need not correspond to a physical feature in the structure, but will still be meshed.
-Abstract regions can be used to define a ``bounding box" around a structure.
-The \inline{superscreen.geometry} module provides functions for generating the underlying polygon vertices for simple geometries (ellipses and rectangles).
-See Code Block~\ref{code:device} for an example of a function that creates a square or circular superconducting ring centered at the origin, with an effective penetration depth $\Lambda = 1\,\mu\mathrm{m}$.
+Abstract regions can be used to define a ``bounding box" around a structure to be modeled, or to locally increase the density of the computational mesh in a given region.
+The \inline{superscreen.geometry} module provides functions for generating the underlying polygon vertices for simple shapes (ellipses and rectangles), which can be combined as described above to create more complicated geometries.
+% See Code Block~\ref{code:device} for an example of a function that creates a square or circular superconducting ring centered at the origin, with an effective penetration depth $\Lambda = 1\,\mu\mathrm{m}$.
 
 \begin{code}
+\begin{minted}[fontsize=\small]{python}
+import superscreen as sc
+from superscreen.geometry import circle, box
+
+# Define the device geometry.
+length_units = "um"
+ro = 3  # outer radius
+ri = 1  # inner radius
+slit_width = 0.5
+Lambda = 1  # effective penetration depth
+# circle() and box() generate arrays of polygon (x, y) coordinates.
+ring = circle(ro)
+hole = circle(ri)
+slit = box(slit_width, 1.5 * (ro - ri), center=(0, -(ro + ri) / 2))
+# Define the Polygon representing the superconductor.
+layer = sc.Layer("base", Lambda=Lambda)
+film = sc.Polygon.from_difference(
+    [ring, slit, hole], name="ring_with_slit", layer="base"
+)
+bounding_box = sc.Polygon("bounding_box", layer="base", points=circle(1.2 * ro))
+# Define the Device and generate the computational mesh.
+device = sc.Device(
+    film.name,
+    layers=[layer],
+    films=[film],
+    abstract_regions=[bounding_box],
+    length_units=length_units,
+)
+device.make_mesh(min_triangles=8_000, optimesh_steps=None)
+# Solve for the device's response to a uniform applied field.
+solution = sc.solve(
+    device,
+    applied_field=sc.sources.ConstantField(10),
+    field_units="uT",
+)[-1]
+# Visualize the solution.
+solution.plot_fields()
+solution.plot_currents()
+\end{minted}
 \captionof{listing}{A function that creates a \inline{Device} representing a circular or square ring centered at the origin.}
 \label{code:device}
-\begin{minted}[fontsize=\small]{python}
-import superscreen as sc
-import superscreen.geometry as geo
-
-def make_ring(
-    inner_radius: float = 2.5,
-    outer_radius: float = 5.0,
-    inner_points: int = 300,
-    outer_points: int = 500,
-    Lambda: float = 1.0,
-    square: bool = False,
-) -> sc.Device:
-    """Creates a Device representing a circular or square ring."""
-    if square:
-        outer = geo.square(2 * outer_radius, points_per_side=outer_points // 4)
-        inner = geo.square(2 * inner_radius, points_per_side=inner_points // 4)
-        bbox = geo.square(1.25 * 2 * outer_radius, points_per_side=10)
-    else:
-        outer = geo.circle(outer_radius, points=outer_points)
-        inner = geo.circle(inner_radius, points=inner_points)
-        bbox = geo.circle(1.4 * outer_radius, points=50)
-    layers = [sc.Layer("base", Lambda=Lambda, z0=0)]
-    films = [sc.Polygon("ring", layer="base", points=outer)]
-    holes = [sc.Polygon("hole", layer="base", points=inner)]
-    abstract_regions = [sc.Polygon("bbox", layer="base", points=bbox)]
-    return sc.Device(
-        "ring",
-        layers=layers,
-        films=films,
-        holes=holes,
-        abstract_regions=abstract_regions,
-        length_units="um",
-    )
-\end{minted}
 \end{code}
@@
 If no \inline{optimesh} optimization is done, then every polygon vertex is guaranteed to be a mesh vertex.
-See Code Block~\ref{code:mesh_generation} for a demonstration of \inline{Device.make_mesh()} and Figure~\ref{fig:mesh} to view the resulting meshes both with and without \inline{optimesh} optimization.
+See Code Block~\ref{code:device} for a demonstration of \inline{Device.make_mesh()} and Figure~\ref{fig:mesh} to view the resulting meshes both with and without \inline{optimesh} optimization.
 After the mesh has been generated, the geometry-dependent matrices and vectors described in Section~\ref{section:implementation} are computed and one can begin solving models.
@@
 \begin{code}
-\captionof{listing}{Generating and visualizing the computational mesh. See Figure~\ref{fig:mesh} to view the resulting meshes.}
-\label{code:mesh_generation}
 \begin{minted}[fontsize=\small]{python}
@@
 \end{minted}
+\captionof{listing}{Generating and visualizing the computational mesh. See Figure~\ref{fig:mesh} to view the resulting meshes.}
+\label{code:mesh_generation}
 \end{code}
@@
 One can also skip the iterative portion of the calculation entirely and only solve for the response of each layer to the applied field, assuming no interaction between layers.
+The \inline{Device.solve_dtype} attribute determines the \inline{numpy} floating point data type used by \inline{solve()}.
+The default data type is \inline{float64} (64-bit double-precision float, equivalent to Python's \inline{float} type), but one can, for instance, set \inline{device.solve_dtype = "float32"} to use 32-bit single-precision floats in order to save memory.
 
 % \begin{code}
-% \captionof{listing}{Solves for the current and magnetic field distributions for the \inline{square_ring} device given a uniform applied field, and circulating current with no applied field, and plots the resulting sheet current and field.}
-% \label{code:ring_circulating_current}
 % \begin{minted}[fontsize=\small]{python}
@@
 % \end{minted}
+% \captionof{listing}{Solves for the current and magnetic field distributions for the \inline{square_ring} device given a uniform applied field, and circulating current with no applied field, and plots the resulting sheet current and field.}
+% \label{code:ring_circulating_current}
 % \end{code}
@@
     \item{
-    \inline{Solution.grid_data()}: Interpolates the calculated stream functions and magnetic fields for each layer from the triangular mesh to a rectangular grid.
-    }
-    \item{
-    \inline{Solution.grid_current_density()}: Interpolates the stream functions to a rectangular grid and calculates the current density (sheet current) $\vec{J}(x, y)$ in each layer using Eq.~\ref{eq:stream}.
+    \inline{Solution.grid_data()}: Interpolates the calculated stream functions $g(x, y)$, magnetic fields $\mu_0H_z(x, y)$, or current densities $\vec{J}(x, y)$, for each layer from the triangular mesh to a rectangular grid.
+    }
+    % \item{
+    % \inline{Solution.grid_current_density()}: Interpolates the stream functions to a rectangular grid and calculates the current density (sheet current) $\vec{J}(x, y)$ in each layer using Eq.~\ref{eq:stream}.
+    % }
+    \item{
+    \inline{Solution.field_at_position()}: Calculates the vector magnetic field at any point(s) in space due the applied field and the currents flowing the in the device using Eqs.~\ref{eq:field_from_kernel} and \ref{eq:kernels}.
     }
@@
     \inline{Solution.polygon_fluxoid()}: Calculates the fluxoid for a specified polygonal region in the device. See Section~\ref{section:examples:fluxoid} for more details.
-    }
-    \item{
-    \inline{Solution.field_at_position()}: Calculates the vector magnetic field at any point(s) in space due the applied field and the currents flowing the in the device using Eqs.~\ref{eq:field_from_kernel} and \ref{eq:kernels}.
     }
@@
 \begin{equation}
-    \tilde{H}_z(\vec{k}, z)=\mathcal{F}\{H_z(\vec{r}, z)\}=\frac{1}{\mu_0}\frac{\Phi_0e^{-|\vec{k}||z|}}{1+2\Lambda|\vec{k}|},
+    \tilde{H}_z(\vec{k}, z)=\mathcal{F}\{H_z(\vec{r}, z)\}=\frac{1}{\mu_0}\frac{\Phi_0e^{-|\vec{k}|z}}{1+2\Lambda|\vec{k}|},
     \label{eq:pearl}
@@
 where $\mathcal{F}\{\cdot\}$ is the 2D Fourier transform, $\vec{k}=(k_x, k_y)$ are in-plane spatial frequencies, $z$ is the out-of-plane position at which the field is evaluated, and $2\Lambda = 2\lambda^2 / d$ is the Pearl length~\cite{Pearl1964-cl, Tafuri2004-ap}.
-The real-space magnetic field distribution near a Pearl vortex can be calculated numerically by taking the inverse Fourier transform of Equation~\ref{eq:pearl}: $H_z(\vec{r}, z)=\mathcal{F}^{-1}\{\tilde{H}_z(\vec{k}, z)\}$.
+The real-space magnetic field distribution near a Pearl vortex can be calculated numerically by taking the inverse Fourier transform of Eq.~\ref{eq:pearl}: $H_z(\vec{r}, z)=\mathcal{F}^{-1}\{\tilde{H}_z(\vec{k}, z)\}$.
 The field distributions generated by \SuperScreen in the presence of vortices as described in Sections~\ref{section:model:vortices} and~\ref{section:implementation} agree to within a few percent with the distributions obtained using this Fourier transform method, as demonstrated in Code Block~\ref{code:pearl-vortex} and Figure~\ref{fig:pearl}(c-e).
@@
 \begin{code}
-\captionof{listing}{Creates a square superconducting film with side length $20\,\mu\mathrm{m}$ and calculates the magnetic field distribution near a vortex at the center of the film as a function of the the effective penetration depth, $\Lambda$ (see Figure~\ref{fig:pearl}).}
-\label{code:pearl-vortex}
 \begin{minted}[fontsize=\small]{python}
@@
 )
-device.make_mesh(min_triangles=8_000)
+device.make_mesh(min_triangles=8000)
 # Specify the vortex position.
@@
     # Use solution.field_at_position() to evaluate the magnetic field profile,
-    # and Solution.polygon_fluxoid() to calculate fluxoids.
+    # and solution.polygon_fluxoid() to calculate fluxoids.
 \end{minted}
+\captionof{listing}{Creates a square superconducting film with side length $20\,\mu\mathrm{m}$ and calculates the magnetic field distribution near a vortex at the center of the film as a function of the the effective penetration depth, $\Lambda$ (see Figure~\ref{fig:pearl}).}
+\label{code:pearl-vortex}
 \end{code}
@@
 \SuperScreen allows one to calculate the fluxoid $\Phi^f_S$ for any polygonal region $S$ whose boundary $\partial S$ lies completely within a superconducting film using the method \inline{Solution.polygon_fluxoid()} (see Section~\ref{section:model:fluxoid}, Eq.~\ref{eq:fluxoid}).
-The ``flux part''  $\int_S\mu_0H_z(\vec{r})\,\mathrm{d}^2r$ is calculated using \inline{Solution.polygon_flux()}, which computes the flux through a polygon representing a region $S$ by averaging the field at the three vertices of each triangle $t$ that lies in $S$ to estimate the field $\mu_0H_{z, t}$ at the center of the triangle, then returns the flux $\sum_t \mu_0H_{z,t}A_t$, where $A_t$ is the area of triangle $t$.
+The ``flux part''  $\int_S\mu_0H_z(\vec{r})\,\mathrm{d}^2r$ is calculated using \inline{Solution.polygon_flux()}, which computes the flux through a polygon representing a region $S$ by averaging the field at the three vertices of each triangle $t$ whose centroid lies in $S$ to estimate the field $\mu_0H_{z, t}$ at the centroid of the triangle, then returns the flux $\sum_t \mu_0H_{z,t}A_t$, where $A_t$ is the area of triangle $t$.
 The ``supercurrent part'' $\oint_S\mu_o\Lambda(\vec{r})\vec{J}(\vec{r})\cdot\mathrm{d}\vec{r}$ is calculated by evaluating the vector current density $\vec{J}$ at each point in the path $\partial S$ using \inline{Solution.interp_current_density()}, then computing the line integral along the path using the trapezoid rule.
@@
 
-While the model doesn't ``know'' about fluxoid quantization, so to speak, we can nevertheless calculate current and field distributions for different fluxoid states $\Phi^f_S=n\Phi_0$.
-Consider again the circular or square ring.
-For a given applied field $H_{z,\,\mathrm{applied}}$ we can choose $I_h$, the current circulating around the hole in the ring, such that the fluxoid $\Phi^f_S=n\Phi_0$ for a region $S$ containing the hole.
-If there is a single hole, this is simply a root finding problem.
-For a structure with $N_h$ holes, we can specify $N_h$ fluxoids $\Phi^f_h$ and find the circulating currents $I_h$ by minimizing the deviation of each fluxoid from some assumed value.
-These two calculations are implemented in the \inline{superscreen.find_fluxoid_solution()} function.
+While the 2D London model doesn't ``know'' about fluxoid quantization, in the sense that it is not automatically satisfied by solutions to Eq.~\ref{eq:london} for multiply-connected films, we can nevertheless calculate current and field distributions for different fluxoid states $\Phi^f_S=n\Phi_0$ in multiply-connected superconductors by adjusting the currents circulating around each hole to realize a prescribed set of fluxoid values.
+For a structure with $N_h$ holes, we can specify $N_h$ fluxoids $\Phi^f_h$ and find the circulating currents $I_h$ by minimizing the deviation of each fluxoid from its desired value.
+(If $N_h=1$, this is a simple 1D root-finding problem.) This calculation is implemented in the \inline{superscreen.find_fluxoid_solution()} function.
 
@@
 
-\subsection{Application: scanning SQUID susceptometry}
-\label{section:examples:susceptometry}
+\subsection{Application: scanning SQUID microscopy}
+\label{section:examples:scanning-squid}
 
@@
 
-\section{Fluxoid calculation}
-\label{appendix:fluxoid}
-As described in Section~\ref{section:model:fluxoid}, for a valid solution to the static 2D London equation as formulated in Equation~\ref{eq:london}, the fluxoid $\Phi^f_S$ should have the following properties:
-\begin{enumerate}
-    \item{$\Phi^f_S = \sum_{\mathrm{vortices}\,v}\Phi_v$ for any region $S$ lying completely within a superconducting film that contains a set of vortices $v$, each containing flux $\Phi_v$ (and $\Phi^f_S = 0$ if $S$ contains no vortices).}
-    \item{$\Phi^f_S = \Phi_h$ for any region $S$ that contains a hole $h$, where $\Phi_h$ is a constant (i.e.
+% \section{Fluxoid calculation}
+% \label{appendix:fluxoid}
+% As described in Section~\ref{section:model:fluxoid}, for a valid solution to the static 2D London equation as formulated in Eq.~\ref{eq:london}, the fluxoid $\Phi^f_S$ should have the following properties:
+% \begin{enumerate}
+%     \item{$\Phi^f_S = \sum_{\mathrm{vortices}\,v}\Phi_v$ for any region $S$ lying completely within a superconducting film that contains a set of vortices $v$, each containing flux $\Phi_v$ (and $\Phi^f_S = 0$ if $S$ contains no vortices).}
+%     \item{$\Phi^f_S = \Phi_h$ for any region $S$ that contains a hole $h$, where $\Phi_h$ is a constant (i.e.
 does not depend on the specific region $S$ or path $\partial S$) but need not be quantized in units of $\Phi_0$.}
-\end{enumerate}
-
-A demonstration of these properties for the case of the square ring with effective penetration depth $\Lambda=1\,\mu\mathrm{m}$, inner side length $5\,\mu\mathrm{m}$, and outer side length $10\,\mu\mathrm{m}$ subject to a uniform applied field of 0.1 mT is shown in Figure~\ref{fig:fluxoid}.
+% \end{enumerate}
+
+% A demonstration of these properties for the case of the square ring with effective penetration depth $\Lambda=1\,\mu\mathrm{m}$, inner side length $5\,\mu\mathrm{m}$, and outer side length $10\,\mu\mathrm{m}$ subject to a uniform applied field of 0.1 mT is shown in Figure~\ref{fig:fluxoid}.
 Property 1 is shown in the first two rows, and property 2 is shown in the last row.
@@
 
-\begin{figure}
-    \centering
-    \includegraphics[width=\textwidth]{examples/images/fluxoid_combined.png}
-    \caption{Demonstration of the fluxoid properties listed in Section~\ref{section:examples:fluxoid} for a square ring with $\Lambda=1\,\mu\mathrm{m}$, inner side length $5\,\mu\mathrm{m}$, and outer side length $10\,\mu\mathrm{m}$, whose outline is shown with white lines in the left and middle columns, subject to a uniform applied field of 0.1 mT.
+% \begin{figure}
+%     \centering
+%     \includegraphics[width=\textwidth]{examples/images/fluxoid_combined.png}
+%     \caption{Demonstration of the fluxoid properties listed in Section~\ref{section:examples:fluxoid} for a square ring with $\Lambda=1\,\mu\mathrm{m}$, inner side length $5\,\mu\mathrm{m}$, and outer side length $10\,\mu\mathrm{m}$, whose outline is shown with white lines in the left and middle columns, subject to a uniform applied field of 0.1 mT.
 The left and middle columns show the computed current density and out-of-plane-field, overlaid with several regions $S$ for which the fluxoids $\Phi^f_S$ are calculated using \inline{Solution.polygon_fluxoid()}.
@@
 Here again, the errors are given by $|\Phi^f_S / \Phi^f_{S,\,\text{(flux part)}}|$.}
-    \label{fig:fluxoid}
-\end{figure}
-
-% \section{Scaling with number of layers}
-% \label{section:scaling-layers}
-% The iterative method used to solve multi-layer structures (Section~\ref{section:model:multilayer}) is time-consuming and memory-intensive for models with a large mesh (many vertices $v$ and triangles $t$) and/or many layers $L$.
+%     \label{fig:fluxoid}
+% \end{figure}
+
+\section{Numerical considerations}
+\label{appendix:numerics}
+While the numerical method described in Section~\ref{section:implementation} is generally quite robust, it can break down for certain extreme geometries.
+The stream function $g(x, y)$ represents the local magnetization or density of infinitesimal current loops.
+The $z$-component of the magnetic field at position $\vec{r}=(x, y, z)$ from a film $F$ with stream function $g$ lying in a plane parallel to the $x-y$ plane at vertical position $z'$ is given by (see Equations~\ref{eq:field_from_kernel} and \ref{eq:kernels}):
+\begin{align}
+\label{eq:hz-from-kernel}
+\begin{split}
+    H_z(\vec{r}) &= \int_F Q_z(\vec{r},\vec{r}')g(x', y')\,\mathrm{d}^2r',\,\text{where}\\
+    Q_z(\vec{r}, \vec{r}') &=  \frac{2(z-z')^2-\rho^2}
+            {4\pi[(z-z')^2+\rho^2]^{5/2}}
+\end{split}
+\end{align}
+and $\rho=\sqrt{(x-x')^2+(y-y')^2}$.
+Eq.~\ref{eq:hz-from-kernel} is exact for a continuous stream function $g$.
+However, the discretized version of Eq.~\ref{eq:hz-from-kernel}, in which the double integral over the film area $F$ is replaced by a sum over triangular mesh elements, is only valid if $z-z'$, the vertical distance between the film and the point at which the field is being evaluated, is larger than the typical distance $\delta r$ between vertices in the mesh representing the film.
+For $z-z'\lesssim\delta r$, the field $H_z(\vec{r})$ resembles that of a set of isolated dipoles located at the mesh vertex positions, rather than that of a continuous sheet of current.
+This can lead to unphysical results when evaluating the field very close to the surface of a film (for example using \inline{Solution.field_at_position()}), or when solving models involving multi-layer structures where the vertical spacing between layers is much smaller than the lateral extent of the films, in which case the iterative calculation (Section~\ref{section:model:multilayer}) may not converge.
+
+The latter case---mutli-layer structures with closely-spaced layers---is the most challenging class of problem to solve because the iterative method used to solve multi-layer structures (Section~\ref{section:model:multilayer}) is memory-intensive for models with a large mesh (many vertices $v$ and triangles $t$) and/or many layers $L$.
 As mentioned in Section~\ref{section:model:multilayer}, at each iteration of this process, we update the applied field $H_{z,\,\mathrm{applied}}(\vec{r}, z_\ell)$ at each layer $\ell$ based on the currents flowing in all other layers $m\neq\ell$, according to
 
-% \begin{equation}
-%     H_{z,\,\mathrm{applied}}(\vec{r}, z_\ell) \to
-%     H_{z,\,\mathrm{applied}}(\vec{r}, z_\ell)
-%     + \sum_{m\neq\ell}
-%     \int_{S_m} Q_z(\vec{r},\vec{r}')g_m(\vec{r}')\,\mathrm{d}^2r',
-%     \label{eq:iterative}
-% \end{equation}
-% where $S_m$ is surface of all films in layer $m$ and $g_m$ is the stream function for layer $m$.
+\begin{equation}
+    H_{z,\,\mathrm{applied}}(\vec{r}, z_\ell) \to
+    H_{z,\,\mathrm{applied}}(\vec{r}, z_\ell)
+    + \sum_{m\neq\ell}
+    \int_{S_m} Q_z(\vec{r},\vec{r}')g_m(\vec{r}')\,\mathrm{d}^2r',
+    \label{eq:iterative}
+\end{equation}
+where $S_m$ is surface of all films in layer $m$ and $g_m$ is the stream function for layer $m$.
 For a model with $L$ layers, at each iteration Eq.~\ref{eq:iterative} requires the calculation of $\binom{L}{2} = L(L-1)/2$ kernel matrices $\mathbf{Q_z}$, each of which is a dense $v\times t$ floating point matrix.
-For a mesh with $t=10,000$ triangles, each of these $\mathbf{Q_z}$ matrices is 800 MB.
+Typically the number of mesh vertices is approximately half the number of triangles ($v\approx t / 2$), so for a mesh with $t=10,000$ triangles, each of these $\mathbf{Q_z}$ matrices is roughly 400 MB (200 MB) if using 64-bit double-precision floats (32-bit single-precision floats).
 Furthermore, each iteration requires performing $2\binom{L}{2} = L(L-1)$ sums involving $\mathbf{Q_z}\cdot\mathbf{g}_m$, where $\mathbf{g}_m$ is the $n\times1$ vector defining the stream function in layer $m$ evaluated at the center of each triangle in the mesh.
@@
 \begin{code}
-\captionof{listing}{Starting and stopping \inline{ray} outside of \inline{superscreen.solve_many()} using the Python API.
-See the ``API and Package Reference" section of the \inline{ray} documentation for additional options in \inline{ray.init()}~\cite{ray-docs}.}
-\label{code:ray-python}
 \begin{minted}[fontsize=\small]{python}
@@
 \end{minted}
+\captionof{listing}{Starting and stopping \inline{ray} outside of \inline{superscreen.solve_many()} using the Python API.
+See the ``API and Package Reference" section of the \inline{ray} documentation for additional options in \inline{ray.init()}~\cite{ray-docs}.}
+\label{code:ray-python}
 \end{code}

### 2021-11-17 main.tex

@@
 If no \inline{optimesh} optimization is done, then every polygon vertex is guaranteed to be a mesh vertex.
-See Code Block~\ref{code:device} for a demonstration of \inline{Device.make_mesh()} and Figure~\ref{fig:mesh} to view the resulting meshes both with and without \inline{optimesh} optimization.
+See Code Block~\ref{code:device} for a demonstration of \inline{Device.make_mesh()} and Figure~\ref{fig:ring-with-slit} to view the resulting meshes both (a) with and (b) without \inline{optimesh} optimization.
 After the mesh has been generated, the geometry-dependent matrices and vectors described in Section~\ref{section:implementation} are computed and one can begin solving models.
 
-\begin{code}
-\begin{minted}[fontsize=\small]{python}
-import matplotlib.pyplot as plt
-
-fig, axes = plt.subplots(1, 4, figsize=(14, 5), constrained_layout=True)
-# Create the Devices
-ring = make_ring(square=False)
-square_ring = make_ring(square=True)
-# min_triangles specifies the minimum number of mesh elements.
-min_triangles = 12000
-# optimesh_steps specifies the the number of iterations of
-# optimesh optimization to perform.
-# Set optimesh_steps=None to disable optimesh optimization.
-optimesh_steps = (None, 40)
-# For more meshing options, see the docstring for Device.make_mesh().
-for row, device in zip(axes.reshape(2, 2), (ring, square_ring)):
-    for ax, opt_steps in zip(row, optimesh_steps):
-        # Generate and visualize the mesh
-        device.make_mesh(min_triangles=min_triangles, optimesh_steps=opt_steps)
-        device.plot_mesh(ax=ax, color="gray", linewidth=0.75)
-        device.plot_polygons(ax=ax, linewidth=3, legend=False)
-\end{minted}
-\captionof{listing}{Generating and visualizing the computational mesh. See Figure~\ref{fig:mesh} to view the resulting meshes.}
-\label{code:mesh_generation}
-\end{code}
+% \begin{code}
+% \begin{minted}[fontsize=\small]{python}
+% import matplotlib.pyplot as plt
+
+% fig, axes = plt.subplots(1, 4, figsize=(14, 5), constrained_layout=True)
+% # Create the Devices
+% ring = make_ring(square=False)
+% square_ring = make_ring(square=True)
+% # min_triangles specifies the minimum number of mesh elements.
+% min_triangles = 12000
+% # optimesh_steps specifies the the number of iterations of
+% # optimesh optimization to perform.
+% # Set optimesh_steps=None to disable optimesh optimization.
+% optimesh_steps = (None, 40)
+% # For more meshing options, see the docstring for Device.make_mesh().
+% for row, device in zip(axes.reshape(2, 2), (ring, square_ring)):
+%     for ax, opt_steps in zip(row, optimesh_steps):
+%         # Generate and visualize the mesh
+%         device.make_mesh(min_triangles=min_triangles, optimesh_steps=opt_steps)
+%         device.plot_mesh(ax=ax, color="gray", linewidth=0.75)
+%         device.plot_polygons(ax=ax, linewidth=3, legend=False)
+% \end{minted}
+% \captionof{listing}{Generating and visualizing the computational mesh. See Figure~\ref{fig:mesh} to view the resulting meshes.}
+% \label{code:mesh_generation}
+% \end{code}
 
@@
     \centering
-    \includegraphics[width=\textwidth]{examples/images/mesh.pdf}
-    \caption{Computational meshes for (a, b) circular and (c, d) square rings, (a, c) without and (b, d) with \inline{optimesh} optimization, generated using Code Block~\ref{code:mesh_generation}.
-The bounding box (\inline{bbox}) is shown in purple, the ring's outer edge (\inline{ring}) is shown in red, and the ring's inner edge (\inline{hole}) is shown in blue.
-Note that optimizing the mesh does not change the total number of vertices or triangles, but does tend to make the triangle size and density more uniform across the mesh.
-In this case, all four meshes (a-d) contain around 6,000 points and 12,000 triangles.}
-    \label{fig:mesh}
+    \includegraphics[width=\textwidth]{examples/images/ring_with_slit.pdf}
+    \caption{}
+    \label{fig:ring-with-slit}
 \end{figure}

### 2021-11-17 main.tex

@@
 \SetupFloatingEnvironment{listing}{name=Code Block}
-\BeforeBeginEnvironment{code}{\begin{minipage}{\textwidth}}
+\BeforeBeginEnvironment{code}{\vspace{10pt}\begin{minipage}{\textwidth}}
 \AfterEndEnvironment{code}{\end{minipage}}
@@
 
+Once the layers, films, holes, and abstract regions have been defined, one can generate the computational mesh by calling \inline{Device.make_mesh()}.
+The region that is meshed is defined by the convex hull of the union of all polygons in the device.
+Mesh generation is a two step process.
+First, an initial Delaunay mesh is created using \inline{meshpy}~\cite{Klockner}, which is a Python interface to Triangle~\cite{Shewchuk1996-va, Shewchuk}, a fast compiled 2D mesh generation tool.
+Second (and optionally), the mesh is further optimized using \inline{optimesh}~\cite{Schlomer2021-ua}.
+The goal of the mesh optimization step is to improve the quality of each triangular element in the mesh, where quality measures how close a triangle is to equilateral (quality $\leq1$, with equality for equilateral triangles).
+% , where quality is defined as twice the ratio of the incircle radius to the circumcircle radius (quality $\leq1$, with equality for equilateral triangles).
+The local density of triangles in the mesh is determined by the density of vertices in the device's polygons and the total number of triangles.
+Regions where there are many polygon vertices will be meshed more densely than regions with few polygon vertices.
+If no \inline{optimesh} optimization is done, then every polygon vertex is guaranteed to be a mesh vertex.
+See Code Block~\ref{code:device} for a demonstration of \inline{Device.make_mesh()} and Figure~\ref{fig:ring-with-slit}(a) to view the resulting mesh.
+After the mesh has been generated, the geometry-dependent matrices and vectors described in Section~\ref{section:implementation} are computed and one can begin solving models.
+
 \begin{code}
@@
 bounding_box = sc.Polygon("bounding_box", layer="base", points=circle(1.2 * ro))
-# Define the Device and generate the computational mesh.
+# Create a Device and generate and plot the computational mesh.
 device = sc.Device(
@@
 device.make_mesh(min_triangles=8_000, optimesh_steps=None)
-# Solve for the device's response to a uniform applied field.
-solution = sc.solve(
-    device,
-    applied_field=sc.sources.ConstantField(10),
-    field_units="uT",
-)[-1]
+device.plot(mesh=True)
+# Calculate the device's response to a uniform applied field.
+applied_field = sc.sources.ConstantField(10)
+solution = sc.solve(device, applied_field=applied_field, field_units="uT")[-1]
 # Visualize the solution.
@@
 \end{minted}
-\captionof{listing}{A function that creates a \inline{Device} representing a circular or square ring centered at the origin.}
+\captionof{listing}{The typical workflow for a \SuperScreen simulation: 1) Define device geometry and materials properties, 2) generate the computational mesh, 3) solve the model for a given applied field, and 4) visualize the results.}
 \label{code:device}
 \end{code}
-
-Once the layers, films, holes, and abstract regions have been defined, one can generate the computational mesh by calling \inline{Device.make_mesh()}.
-The region that is meshed is defined by the convex hull of the union of all polygons in the device.
-Mesh generation is a two step process.
-First, an initial Delaunay mesh is created using \inline{meshpy}~\cite{Klockner}, which is a Python interface to Triangle~\cite{Shewchuk1996-va, Shewchuk}, a fast compiled 2D mesh generation tool.
-Second (and optionally), the mesh is further optimized using \inline{optimesh}~\cite{Schlomer2021-ua}.
-The goal of the mesh optimization step is to improve the quality of each triangular element in the mesh, where quality is defined as twice the ratio of the incircle radius to the circumcircle radius (quality $\leq1$, with equality for equilateral triangles).
-The local density of triangles in the mesh is determined by the density of vertices in the device's polygons and the total number of triangles.
-Regions where there are many polygon vertices will be meshed more densely than regions with few polygon vertices.
-If no \inline{optimesh} optimization is done, then every polygon vertex is guaranteed to be a mesh vertex.
-See Code Block~\ref{code:device} for a demonstration of \inline{Device.make_mesh()} and Figure~\ref{fig:ring-with-slit} to view the resulting meshes both (a) with and (b) without \inline{optimesh} optimization.
-After the mesh has been generated, the geometry-dependent matrices and vectors described in Section~\ref{section:implementation} are computed and one can begin solving models.
-
-% \begin{code}
-% \begin{minted}[fontsize=\small]{python}
-% import matplotlib.pyplot as plt
-
-% fig, axes = plt.subplots(1, 4, figsize=(14, 5), constrained_layout=True)
-% # Create the Devices
-% ring = make_ring(square=False)
-% square_ring = make_ring(square=True)
-% # min_triangles specifies the minimum number of mesh elements.
-% min_triangles = 12000
-% # optimesh_steps specifies the the number of iterations of
-% # optimesh optimization to perform.
-% # Set optimesh_steps=None to disable optimesh optimization.
-% optimesh_steps = (None, 40)
-% # For more meshing options, see the docstring for Device.make_mesh().
-% for row, device in zip(axes.reshape(2, 2), (ring, square_ring)):
-%     for ax, opt_steps in zip(row, optimesh_steps):
-%         # Generate and visualize the mesh
-%         device.make_mesh(min_triangles=min_triangles, optimesh_steps=opt_steps)
-%         device.plot_mesh(ax=ax, color="gray", linewidth=0.75)
-%         device.plot_polygons(ax=ax, linewidth=3, legend=False)
-% \end{minted}
-% \captionof{listing}{Generating and visualizing the computational mesh. See Figure~\ref{fig:mesh} to view the resulting meshes.}
-% \label{code:mesh_generation}
-% \end{code}
 
@@
     \includegraphics[width=\textwidth]{examples/images/ring_with_slit.pdf}
-    \caption{}
+    \caption{The output of Code Block~\ref{code:device}: Meissner screening of a uniform $10\,\mu\mathrm{T}$ out-of-plane field by a ring with inner diameter $1\,\mu\mathrm{m}$, outer diameter $3\,\mu\mathrm{m}$, and effective penetration depth $\Lambda=1\,\mu\mathrm{m}$, interrupted by a slit of width $0.5\,\mu\mathrm{m}$.
+a) Plot of the boundary of the ring (blue), circular bounding box (orange), and the computational mesh (gray), generated by \inline{Device.plot()}.
+b) The $z$-component of the magnetic field $\mu_0H_z$ evaluated at the plane of the ring, generated by \inline{Solution.plot_fields()}.
+c) Current density $\vec{J}$ in the ring, generated by \inline{Solution.plot_currents()}.}
     \label{fig:ring-with-slit}

### 2021-11-17 main.tex
Updates from Overleaf

@@
 Second (and optionally), the mesh is further optimized using \inline{optimesh}~\cite{Schlomer2021-ua}.
-The goal of the mesh optimization step is to improve the quality of each triangular element in the mesh, where quality measures how close a triangle is to equilateral (quality $\leq1$, with equality for equilateral triangles).
+The goal of the mesh optimization step is to improve the ``quality'' of each triangular element in the mesh, where quality measures how close a triangle is to equilateral (quality $\leq1$, with equality for equilateral triangles).
 % , where quality is defined as twice the ratio of the incircle radius to the circumcircle radius (quality $\leq1$, with equality for equilateral triangles).
@@
 If no \inline{optimesh} optimization is done, then every polygon vertex is guaranteed to be a mesh vertex.
-See Code Block~\ref{code:device} for a demonstration of \inline{Device.make_mesh()} and Figure~\ref{fig:ring-with-slit}(a) to view the resulting mesh.
+See Code Block~\ref{code:device} for a demonstration of the process of creating a \inline{Device}, Figure~\ref{fig:ring-with-slit}(a) to view the resulting geometry and mesh.
 After the mesh has been generated, the geometry-dependent matrices and vectors described in Section~\ref{section:implementation} are computed and one can begin solving models.
@@
     \caption{The output of Code Block~\ref{code:device}: Meissner screening of a uniform $10\,\mu\mathrm{T}$ out-of-plane field by a ring with inner diameter $1\,\mu\mathrm{m}$, outer diameter $3\,\mu\mathrm{m}$, and effective penetration depth $\Lambda=1\,\mu\mathrm{m}$, interrupted by a slit of width $0.5\,\mu\mathrm{m}$.
-a) Plot of the boundary of the ring (blue), circular bounding box (orange), and the computational mesh (gray), generated by \inline{Device.plot()}.
-b) The $z$-component of the magnetic field $\mu_0H_z$ evaluated at the plane of the ring, generated by \inline{Solution.plot_fields()}.
-c) Current density $\vec{J}$ in the ring, generated by \inline{Solution.plot_currents()}.}
+a) Plot of the boundary of the ring (blue), circular bounding box (orange), and the computational mesh (gray), generated with \inline{Device.plot()}.
+b) The $z$-component of the magnetic field $\mu_0H_z$ evaluated at the plane of the ring, generated with \inline{Solution.plot_fields()}.
+c) Current density $\vec{J}$ in the ring, generated with \inline{Solution.plot_currents()}.}
     \label{fig:ring-with-slit}
@@
 One can also skip the iterative portion of the calculation entirely and only solve for the response of each layer to the applied field, assuming no interaction between layers.
-The \inline{Device.solve_dtype} attribute determines the \inline{numpy} floating point data type used by \inline{solve()}.
+The \inline{device.solve_dtype} attribute determines the \inline{numpy} floating point data type used by \inline{solve()}.
 The default data type is \inline{float64} (64-bit double-precision float, equivalent to Python's \inline{float} type), but one can, for instance, set \inline{device.solve_dtype = "float32"} to use 32-bit single-precision floats in order to save memory.
@@
 \end{itemize}
-\inline{Solutions} also have several visualization methods built in (see Section~\ref{section:overview:visualization}).
+\inline{Solutions} also have several visualization methods built in (see Code Block~\ref{code:device}, Figure~\ref{fig:ring-with-slit}, and Section~\ref{section:overview:visualization}).
 
 One may wish to solve many models involving the same device while varying other aspects of the model, for example sweeping the applied field, circulating currents, vortex properties, or some parameter of one or more layers in the device.
-Fortunately, the mesh and large matrices described in Section~\ref{section:implementation} depend only on the geometry of the device parallel to the $x-y$ plane.
-This means that the same mesh and matrices can be re-used for models with different applied fields, circulating currents, vortex properties, layer heights (vertical positions), and penetration depths.
+Fortunately, the mesh, Laplace operator, kernel matrix, etc.
+(described in Section~\ref{section:implementation}) depend only on the geometry of the device parallel to the $x-y$ plane.
+This means that the same mesh and matrices can be re-used for models with different applied fields, circulating currents, vortex properties, layer $z$-positions, and penetration depths.
 
@@
 
-% See Code Block~\ref{code:ring_circulating_current} and  Figure~\ref{fig:square-ring-results} for an example of the usage and output of \inline{plot_fields()} and \inline{plot_currents()}.
+See Code Block~\ref{code:device} and  Figure~\ref{fig:ring-with-slit} for an example of the usage and output of \inline{plot_fields()} and \inline{plot_currents()}.
 
@@
 
-Instances of \inline{superscreen.Device} and \inline{superscreen.Solution} can be saved to and loaded from disk using their respective \inline{to_file()} and \inline{from_file()} methods, making it straightforward to share models and simulation results.
+Instances of \inline{superscreen.Device} and \inline{superscreen.Solution} can be saved to and loaded from disk using their respective \inline{to_file()} and \inline{from_file()} methods, making it straightforward to store and share models and simulation results.
 \inline{Layers}, \inline{Polygons}, and all metadata are serialized to JSON, a widely-used, human-readable plain text format.
-Functions and \inline{Parameters}, such as those that compute the applied field or penetration depth, are serialized in binary form using \inline{dill}~\cite{McKerns}.
+Functions and \inline{Parameters}, such as those that compute the applied field or penetration depth, are serialized in binary form using the \inline{dill} package~\cite{McKerns}.
 \inline{Numpy} arrays, such as the mesh itself and the computed stream functions and fields, are saved in the \inline{numpy} \inline{npz} file format.

### 2021-11-18 main.tex
Updates from Overleaf

@@
 % \documentclass[preprint,12pt]{elsarticle}
+% \documentclass[preprint,3p,times,twocolumn]{elsarticle}
 
@@
 % \documentclass[final,1p,times,twocolumn]{elsarticle}
-\documentclass[final,3p,times]{elsarticle}
-% \documentclass[final,3p,times,twocolumn]{elsarticle}
+% \documentclass[final,3p,times]{elsarticle}
+\documentclass[final,3p,times,twocolumn]{elsarticle}
 % \documentclass[final,5p,times]{elsarticle}
@@
 \newcommand{\SuperScreen}{\inline{SuperScreen}}
+\newcommand{\um}{\mu\mathrm{m}}
 
@@
 \SetupFloatingEnvironment{listing}{name=Code Block}
-\BeforeBeginEnvironment{code}{\vspace{10pt}\begin{minipage}{\textwidth}}
-\AfterEndEnvironment{code}{\end{minipage}}
+\BeforeBeginEnvironment{code}{\vspace{10pt}\begin{figure*}[t!]}
+\AfterEndEnvironment{code}{\end{figure*}}
 \captionsetup[listing]{skip=0pt}
@@
     \begin{split}
-        \underbrace{\vec{H}(\vec{r})\cdot\hat{z} = H_z(\vec{r})
+        &\underbrace{\vec{H}(\vec{r})\cdot\hat{z} = H_z(\vec{r})
         = \Lambda\nabla^2g(x, y)}_{z-\text{component of the total field}}
-        = \underbrace{H_{z,\,\mathrm{applied}}(\vec{r})}_{\text{applied field}}
+        = \\ & \underbrace{H_{z,\,\mathrm{applied}}(\vec{r})}_{\text{applied field}}
         + \underbrace{\int_F Q_z(\vec{r},\vec{r}')g(\vec{r}')\,\mathrm{d}^2r'}_{\text{screening field}},
@@
 
-\begin{equation}
+\begin{align}
+\begin{split}
     \label{eq:applied_to_stream}
-    H_{z,\,\mathrm{applied}}(\vec{r})
-    = -\int_F\left[
+    &H_{z,\,\mathrm{applied}}(\vec{r})
+    = \\ &-\int_F\left[
         Q_z(\vec{r},\vec{r}')-\delta(\vec{r}-\vec{r}')\Lambda(\vec{r}')\nabla^2\right
     ]g(\vec{r}')\,\mathrm{d}^2r',
-\end{equation}
+\end{split}
+\end{align}
 where $\delta$ is the 2D Dirac delta function.
@@
 
-\begin{equation}
+\begin{align}
+\begin{split}
     \label{eq:Heff}
-    H_{z,\,\mathrm{eff},\,k}(\vec{r}) = -\int_{\mathrm{hole}\,k}[
+    &H_{z,\,\mathrm{eff},\,k}(\vec{r}) = \\
+    &-\int_{\mathrm{hole}\,k}[
         Q_z(\vec{r},\vec{r}')-\delta(\vec{r}-\vec{r}')\Lambda(\vec{r}')\nabla^2
     ] I_{\mathrm{circ},\,k} \,\mathrm{d}^2r'.   
-\end{equation}
+\end{split}
+\end{align}
 
@@
 
-\begin{equation}
+\begin{align}
+\begin{split}
     \label{eq:Heff_sub}
-    H_{z,\,\mathrm{applied}}(\vec{r}) - \sum_{\mathrm{holes}\,k} H_{z,\,\mathrm{eff},\,k}(\vec{r})
-    = -\int_F\left[
+    &H_{z,\,\mathrm{applied}}(\vec{r}) - \sum_{\mathrm{holes}\,k} H_{z,\,\mathrm{eff},\,k}(\vec{r})
+    = \\&-\int_F\left[
         Q_z(\vec{r},\vec{r}')-\delta(\vec{r}-\vec{r}')\Lambda(\vec{r}')\nabla^2\right
     ]g(\vec{r}')\,\mathrm{d}^2r'.
-\end{equation}
+\end{split}
+\end{align}
 
@@
 In addition to being trapped in holes (see Section~\ref{section:model:holes}), flux may be trapped in a superconducting film in the form of vortices.
-The presence of vortices trapped in a film at positions $\vec{r}_v$ modifies Eq.~\ref{eq:applied_to_stream} as follows:
-
-\begin{equation}
+The presence of vortices trapped in a film at positions $\vec{r}_v$ modifies Eq.~\ref{eq:Heff_sub} as follows:
+
+\begin{align}
+\begin{split}
     \label{eq:applied_to_stream_vortices}
-    H_{z,\,\mathrm{applied}}(\vec{r}) - \sum_{\mathrm{vortices}\,v}\frac{\Phi_v}{\mu_0}\delta(\vec{r}-\vec{r}_v)
-    = -\int_F\left[
+    & H_{z,\,\mathrm{applied}}(\vec{r}) - \sum_{\mathrm{holes}\,k} H_{z,\,\mathrm{eff},\,k}(\vec{r}) - \sum_{\mathrm{vortices}\,v}\frac{\Phi_v}{\mu_0}\delta(\vec{r}-\vec{r}_v)
+    = \\
+    &-\int_F\left[
         Q_z(\vec{r},\vec{r}')-\delta(\vec{r}-\vec{r}')\Lambda(\vec{r}')\nabla^2\right
     ]g(\vec{r}')\,\mathrm{d}^2r',
-\end{equation}
+\end{split}
+\end{align}
 where $\delta$ is the 2D Dirac delta function and each vortex $v$ is associated with a flux $\Phi_v$ (typically $\Phi_v=n\Phi_0=nh/2e$, where $n$ is an integer, $\Phi_0$ is the magnetic flux quantum, $h$ is the Planck constant, and $e$ is the elementary charge).
-By solving Eq.~\ref{eq:applied_to_stream_vortices} to obtain $g(\vec{r})$, one can compute the supercurrent density in the film due to both an applied field and trapped vortices.
+By solving Eq.~\ref{eq:applied_to_stream_vortices} to obtain $g(\vec{r})$, one can compute the supercurrent density in the film due to an applied field and flux trapped in both holes and vortices.
 For a simply-connected region $S$ containing a set of vortices $v$ each associated with a flux $\Phi_v$, the fluxoid is equal to $\Phi^f_S=\sum_{\mathrm{vortices}\,v}\Phi_v$.
@@
     \item{
-        Calculate the stream function $g_\ell(\vec{r})$ for each layer $\ell$ by solving Eq.~\ref{eq:Heff_sub} given an applied field $H_{z,\,\mathrm{applied}}(\vec{r}, z_\ell)$.
+        Calculate the stream function $g_\ell(\vec{r})$ for each layer $\ell$ by solving Eq.~\ref{eq:applied_to_stream_vortices} given an applied field $H_{z,\,\mathrm{applied}}(\vec{r}, z_\ell)$.
     }
@@
     \item{
-        Re-solve Eq.~\ref{eq:Heff_sub} taking the new applied field at each layer to be the original applied field plus the sum of screening fields from all other layers.
+        Re-solve Eq.~\ref{eq:applied_to_stream_vortices} taking the new applied field at each layer to be the original applied field plus the sum of screening fields from all other layers.
 This is accomplished via the substitution
-        $$
-            H_{z,\,\mathrm{applied}}(\vec{r}, z_\ell) \to
+        \begin{align}
+        \begin{split}
             H_{z,\,\mathrm{applied}}(\vec{r}, z_\ell)
-            + \sum_{m\neq\ell}
+            &\to H_{z,\,\mathrm{applied}}(\vec{r}, z_\ell)\\
+            &+ \sum_{m\neq\ell}
             \int_{F_m} Q_z(\vec{r},\vec{r}')g_m(\vec{r}')\,\mathrm{d}^2r',
-        $$
+            \label{eq:iterative}
+        \end{split}
+        \end{align}
         where $F_m$ is surface of all films in layer $m$ and $g_m$ is the stream function for layer $m$.
@@
 
-In order to numerically solve Eq.~\ref{eq:field_from_kernel} and Eq.~\ref{eq:applied_to_stream}, we have to discretize the films, holes, and the vacuum regions surrounding them. We use a triangular
+In order to numerically solve Eq.~\ref{eq:field_from_kernel} and Eq.~\ref{eq:Heff_sub}, we have to discretize the films, holes, and the vacuum regions surrounding them. We use a triangular
 (Delaunay) mesh, consisting of $n$ points (or vertices)
@@
     + (\mathbf{Q}\cdot\mathbf{w}^T)\mathbf{g}\\
-    % h_{z, i} &= h_{z,\,\mathrm{applied}, i} + \sum_j Q_{ij}g_jw_j,
+    h_{z, i} &= h_{z,\,\mathrm{applied}, i} + \sum_j Q_{ij}g_jw_j,
 \end{split}
@@
 from Eq.~\ref{eq:field_from_kernel_num}, and the full vector magnetic field $\vec{H}(x, y, z)$
-at any point in space can be computed from Eqs.~\ref{eq:field_from_kernel} and ~\ref{eq:kernels}.
-Multiply-connected films and multi-layer structures are solved as described in Sections~\ref{section:model:holes} and \ref{section:model:multilayer} respectively.
+at any point in space can be computed from Eqs.~\ref{eq:field_from_kernel} and ~\ref{eq:kernels}. Multi-layer structures are  iteratively as described in Section \ref{section:model:multilayer}.
 
@@
 A \inline{superscreen.Parameter} is a wrapper around a Python function that computes a scalar value as a function of position coordinates ($x$, $y$, and optionally $z$) based on some set of keyword arguments.
-Addition, subtraction, multiplication, division, and exponentiation between \inline{Parameters}, other \inline{Parameters}, and Python scalars (\inline{int} and \inline{float}) are supported (see Code Block~\ref{code:parameters}).
+Addition, subtraction, multiplication, division, and exponentiation between \inline{Parameters}, other \inline{Parameters}, and Python scalars (\inline{int} and \inline{float}) are supported.
 \inline{Parameters} can be used to conveniently define applied magnetic fields and penetration depths that depend on position, and make it possible to serialize wrapped Python functions for storage to disk or inter-process communication.
 
-\begin{code}
-\begin{minted}[fontsize=\small]{python}
-from superscreen import Parameter
-
-def f(x, y, a=1, b=0):
-    return a * x**2 + b * y
-
-param = Parameter(f, a=0, b=1)
-print(param) # Parameter<f(a=0, b=1)>
-other_param = Parameter(f, a=2, b=3)
-print(other_param) # Parameter<f(a=2, b=3)>
-print(param(0, 0) == f(0, 0, a=0, b=1)) # True
-print(other_param(1, 2) == f(1, 2, a=2, b=3)) # True
-param_squared = param ** 2
-print(param_squared) # CompositeParameter<(f(a=0, b=1) ** 2)>
-print(
-    (5 * param_squared / other_param)(5, 6)
-    == 5 * f(5, 6, a=0, b=1) ** 2 / f(5, 6, a=2, b=3)
-) # True
-\end{minted}
-\captionof{listing}{The basic usage of \inline{superscreen.Parameters}, which compute a scalar value as a function of $x, y$ (and optionally $z$) coordinates.
+% \begin{code}
+% \begin{minted}[fontsize=\small]{python}
+% from superscreen import Parameter
+
+% def f(x, y, a=1, b=0):
+%     return a * x**2 + b * y
+
+% param = Parameter(f, a=0, b=1)
+% print(param) # Parameter<f(a=0, b=1)>
+% other_param = Parameter(f, a=2, b=3)
+% print(other_param) # Parameter<f(a=2, b=3)>
+% print(param(0, 0) == f(0, 0, a=0, b=1)) # True
+% print(other_param(1, 2) == f(1, 2, a=2, b=3)) # True
+% param_squared = param ** 2
+% print(param_squared) # CompositeParameter<(f(a=0, b=1) ** 2)>
+% print(
+%     (5 * param_squared / other_param)(5, 6)
+%     == 5 * f(5, 6, a=0, b=1) ** 2 / f(5, 6, a=2, b=3)
+% ) # True
+% \end{minted}
+% \captionof{listing}{The basic usage of \inline{superscreen.Parameters}, which compute a scalar value as a function of $x, y$ (and optionally $z$) coordinates.
 Note that the positional arguments \inline{x} and \inline{y} can be either floating point scalars or 1-dimensional \inline{numpy} arrays.}
-\label{code:parameters}
-\end{code}
+% \label{code:parameters}
+% \end{code}
 
@@
 
-Information about the geometry and penetration depth of a superconducting structure is described by an instance of the \inline{superscreen.Device} class.
-A \inline{Device} is made up of one or more superconducting layers, each represented by an instance of  \inline{superscreen.Layer}.
-Each layer sits in a specified plane parallel to the $x-y$ plane and has its own effective penetration depth $\Lambda$, which can either be a constant or a \inline{superscreen.Parameter} that defines $\Lambda(x, y)$, the effective penetration depth as a function of position.
-Alternatively, the effective penetration depth $\Lambda$ can be defined in terms of a layer's London penetration depth $\lambda$ and its thickness $d$: $\Lambda=\lambda^2/d$, in which case the London penetration depth can be either a constant or a \inline{superscreen.Parameter}.
-
-Each layer can contain one or more superconducting \inline{films} which may have one or more \inline{holes} in them.
-Films and holes are represented by instances of the \inline{superscreen.Polygon} class.
-All polygons in a device must be simply-connected; a hole in a film is modeled as one \inline{Polygon} instance whose coordinates all lie within the \inline{Polygon} representing the film.
-% A \inline{Polygon} contains the name of the layer to which is belongs, an array specifying the coordinates of its vertices, and a method, \inline{Polygon.contains_points()}, which determines whether specified coordinates lie within the polygon or not.
-\inline{Polygons} can constructed and combined using set-theoretic operations.
-Table~\ref{table:polygon} shows the four methods available for combining a \inline{supercreen.Polygon} instance \inline{polygonA}, whose vertices lie in set $A$, with a polygon \inline{polygonB}, whose vertices lie in set $B$.
-Note that \inline{polygonB} can be another \inline{superscreen.Polygon}, an $n\times 2$ \inline{numpy} array of vertex coordinates, or one of several compatible types of objects from the \inline{shapely} package.
-
-\begin{table}[h]
+\begin{table*}
 \centering
@@
 \label{table:polygon}
-\end{table}
+\end{table*}
+
+Information about the geometry and penetration depth of a superconducting structure is described by an instance of the \inline{superscreen.Device} class.
+A \inline{Device} is made up of one or more superconducting layers, each represented by an instance of  \inline{superscreen.Layer}.
+Each layer sits in a specified plane parallel to the $x-y$ plane and has its own effective penetration depth $\Lambda$, which can either be a constant or a \inline{superscreen.Parameter} that defines $\Lambda(x, y)$, the effective penetration depth as a function of position.
+Alternatively, the effective penetration depth $\Lambda$ can be defined in terms of a layer's London penetration depth $\lambda$ and its thickness $d$: $\Lambda=\lambda^2/d$, in which case the London penetration depth can be either a constant or a \inline{superscreen.Parameter}.
+
+Each layer can contain one or more superconducting \inline{films} which may have one or more \inline{holes} in them.
+Films and holes are represented by instances of the \inline{superscreen.Polygon} class.
+All polygons in a device must be simply-connected; a hole in a film is modeled as one \inline{Polygon} instance whose coordinates all lie within the \inline{Polygon} representing the film.
+% A \inline{Polygon} contains the name of the layer to which is belongs, an array specifying the coordinates of its vertices, and a method, \inline{Polygon.contains_points()}, which determines whether specified coordinates lie within the polygon or not.
+\inline{Polygons} can constructed and combined using set-theoretic operations.
+Table~\ref{table:polygon} shows the four methods available for combining a \inline{supercreen.Polygon} instance \inline{polygonA}, whose vertices lie in set $A$, with a polygon \inline{polygonB}, whose vertices lie in set $B$.
+Note that \inline{polygonB} can be another \inline{superscreen.Polygon}, an $n\times 2$ \inline{numpy} array of vertex coordinates, or one of several compatible types of objects from the \inline{shapely} package.
 
@@
 The \inline{superscreen.geometry} module provides functions for generating the underlying polygon vertices for simple shapes (ellipses and rectangles), which can be combined as described above to create more complicated geometries.
-% See Code Block~\ref{code:device} for an example of a function that creates a square or circular superconducting ring centered at the origin, with an effective penetration depth $\Lambda = 1\,\mu\mathrm{m}$.
-
-Once the layers, films, holes, and abstract regions have been defined, one can generate the computational mesh by calling \inline{Device.make_mesh()}.
-The region that is meshed is defined by the convex hull of the union of all polygons in the device.
-Mesh generation is a two step process.
-First, an initial Delaunay mesh is created using \inline{meshpy}~\cite{Klockner}, which is a Python interface to Triangle~\cite{Shewchuk1996-va, Shewchuk}, a fast compiled 2D mesh generation tool.
-Second (and optionally), the mesh is further optimized using \inline{optimesh}~\cite{Schlomer2021-ua}.
-The goal of the mesh optimization step is to improve the ``quality'' of each triangular element in the mesh, where quality measures how close a triangle is to equilateral (quality $\leq1$, with equality for equilateral triangles).
-% , where quality is defined as twice the ratio of the incircle radius to the circumcircle radius (quality $\leq1$, with equality for equilateral triangles).
-The local density of triangles in the mesh is determined by the density of vertices in the device's polygons and the total number of triangles.
-Regions where there are many polygon vertices will be meshed more densely than regions with few polygon vertices.
-If no \inline{optimesh} optimization is done, then every polygon vertex is guaranteed to be a mesh vertex.
-See Code Block~\ref{code:device} for a demonstration of the process of creating a \inline{Device}, Figure~\ref{fig:ring-with-slit}(a) to view the resulting geometry and mesh.
-After the mesh has been generated, the geometry-dependent matrices and vectors described in Section~\ref{section:implementation} are computed and one can begin solving models.
-
 \begin{code}
@@
 \end{code}
-
-\begin{figure}[h]
+Once the layers, films, holes, and abstract regions have been defined, one can generate the computational mesh by calling \inline{Device.make_mesh()}.
+The region that is meshed is defined by the convex hull of the union of all polygons in the device.
+Mesh generation is a two step process.
+First, an initial Delaunay mesh is created using \inline{meshpy}~\cite{Klockner}, which is a Python interface to Triangle~\cite{Shewchuk1996-va, Shewchuk}, a fast compiled 2D mesh generation tool.
+Second (and optionally), the mesh is further optimized using \inline{optimesh}~\cite{Schlomer2021-ua}.
+The goal of the mesh optimization step is to improve the ``quality'' of each triangular element in the mesh, where quality measures how close a triangle is to equilateral (quality $\leq1$, with equality for equilateral triangles).
+In practice, the more \inline{optimesh} steps are performed, the more uniform in size and spatial density the triangles in the mesh become.
+% , where quality is defined as twice the ratio of the incircle radius to the circumcircle radius (quality $\leq1$, with equality for equilateral triangles).
+The local density of triangles in the mesh is determined by the density of vertices in the device's polygons and the total number of triangles.
+Regions where there are many polygon vertices will be meshed more densely than regions with few polygon vertices.
+If no \inline{optimesh} optimization is done, then every polygon vertex is guaranteed to be a mesh vertex.
+See Code Block~\ref{code:device} for a demonstration of the process of creating a \inline{Device}, and Figure~\ref{fig:ring-with-slit}(a) to view the resulting geometry and mesh.
+After the mesh has been generated, the geometry-dependent matrices and vectors described in Section~\ref{section:implementation} are computed and one can begin solving models.
+
+\subsection{Solvers}
+\label{section:overview:solvers}
+\begin{figure*}
     \centering
     \includegraphics[width=\textwidth]{examples/images/ring_with_slit.pdf}
-    \caption{The output of Code Block~\ref{code:device}: Meissner screening of a uniform $10\,\mu\mathrm{T}$ out-of-plane field by a ring with inner diameter $1\,\mu\mathrm{m}$, outer diameter $3\,\mu\mathrm{m}$, and effective penetration depth $\Lambda=1\,\mu\mathrm{m}$, interrupted by a slit of width $0.5\,\mu\mathrm{m}$.
+    \caption{The output of Code Block~\ref{code:device}: Meissner screening of a uniform $10\,\mu\mathrm{T}$ out-of-plane field by a ring with inner diameter $1\,\um$, outer diameter $3\,\um$, and effective penetration depth $\Lambda=1\,\um$, interrupted by a slit of width $0.5\,\um$.
 a) Plot of the boundary of the ring (blue), circular bounding box (orange), and the computational mesh (gray), generated with \inline{Device.plot()}.
@@
     \label{fig:ring-with-slit}
-\end{figure}
-
-\subsection{Solvers}
-\label{section:overview:solvers}
+\end{figure*}
 
@@
 %     \includegraphics[width=\textwidth]{examples/images/square_ring_results.png}
-%     \caption{Sheet current $\vec{J}(x, y)$ and out-of-plane magnetic field $\mu_0H_z(x, y)$ evaluated in the plane of a square ring with effective penetration depth $\Lambda=1\,\mu\mathrm{m}$ subject to (a, b) a uniform applied field of 0.5 mT or (c, d) trapped flux inducing a circulating current of 1 mA.
+%     \caption{Sheet current $\vec{J}(x, y)$ and out-of-plane magnetic field $\mu_0H_z(x, y)$ evaluated in the plane of a square ring with effective penetration depth $\Lambda=1\,\um$ subject to (a, b) a uniform applied field of 0.5 mT or (c, d) trapped flux inducing a circulating current of 1 mA.
 The sub-figures show the output of (a, c) \inline{Solution.plot_currents()} and (b, d) \inline{Solution.plot_fields()}, as shown in Code Block~\ref{code:ring_circulating_current}.
@@
     \inline{superscreen.plot_streams()}: Given a \inline{Solution}, plots the stream function $g(x, y)$ for one or more layers in the device.
-
-    See also: \inline{Solution.plot_streams()}.
     }
@@
     \inline{superscreen.plot_currents()}: Given a \inline{Solution}, plots the sheet current $\vec{J}(x, y)$ for one or more layers in the device.
-
-    See also: \inline{Solution.plot_currents()}.
     }
@@
     \inline{superscreen.plot_fields()}: Given a \inline{Solution}, plots the total field $H_z(x, y)$ or the screening field $H_z(x, y) - H_{z,\,\mathrm{applied}}(x, y)$ for one or more layers in the device.
-
-    See also: \inline{Solution.plot_fields()}.
     }
@@
     \inline{superscreen.plot_field_at_positions()}: Given a \inline{Solution}, plots the total field $\vec{H}(x, y, z)$ or $H_z(x, y, z)$ at an arbitrary set of positions $(x, y, z)$.
-
-    See also: \inline{Solution.plot_field_at_positions()}.
     }
@@
 % To model a SQUID susceptometry measurement, we first calculate $M_0$, the mutual inductance between the field coil and pickup loop in the absence of the sample.
-This can be done by temporarily setting the sample layer effective penetration depth to a very large value such that it essentially does not screen the field from the field coil (in this case, we set $\Lambda = 10^5\,\mu\mathrm{m}$).
+This can be done by temporarily setting the sample layer effective penetration depth to a very large value such that it essentially does not screen the field from the field coil (in this case, we set $\Lambda = 10^5\,\um$).
 We then model the field from a known current flowing in the field coil following Section~\ref{section:model:holes} and self-consistently calculate the response of both the sample and the other superconducting layers of the SQUID sensor following Section~\ref{section:model:multilayer}.
@@
     layers=[sc.Layer("base", Lambda=0, z0=0)],
-    films=[sc.Polygon("film", layer="base", points=sc.geometry.square(20))],
+    films=[sc.Polygon("film", layer="base", points=sc.geometry.box(20))],
     length_units="um",
@@
 \end{minted}
-\captionof{listing}{Creates a square superconducting film with side length $20\,\mu\mathrm{m}$ and calculates the magnetic field distribution near a vortex at the center of the film as a function of the the effective penetration depth, $\Lambda$ (see Figure~\ref{fig:pearl}).}
+\captionof{listing}{Creates a square superconducting film with side length $20\,\um$ and calculates the magnetic field distribution near a vortex at the center of the film as a function of the the effective penetration depth, $\Lambda$ (see Figure~\ref{fig:pearl}).}
 \label{code:pearl-vortex}
@@
 
-\begin{figure}[h]
+\begin{figure*}[h]
     \centering
@@
     \caption{Vortex field profiles calculated with \SuperScreen agree with the analytical solution (Eq.~\ref{eq:pearl}) to within a few percent.
-Here, we model a vortex trapped at the center of a square superconducting film lying in the $x-y$ plane with side length $20\,\mu\mathrm{m}$ as a function of the film's effective penetration depth, $\Lambda$.
-(a) Cross section along the $x$-axis of the out-of-plane magnetic field $\mu_0H_z$ from the vortex, evaluated at a vertical distance $z=1\,\mu\mathrm{m}$ above the film.
+Here, we model a vortex trapped at the center of a square superconducting film lying in the $x-y$ plane with side length $20\,\um$ as a function of the film's effective penetration depth, $\Lambda$.
+(a) Cross section along the $x$-axis of the out-of-plane magnetic field $\mu_0H_z$ from the vortex, evaluated at a vertical distance $z=1\,\um$ above the film.
 (b) Percentage difference between the $\mu_0H_z$ calculated with \SuperScreen and the Fourier transform method for the $x$-axis cut shown in (a).
@@
 In (a) and (c), the results from \SuperScreen are shown as open circles and the results from the Fourier transform method are shown as solid lines.
-(e) The fluxoid $\Phi_S^f$ for a circular region in the film with radius $r=1\,\mu\mathrm{m}$ centered on the vortex core.
+(e) The fluxoid $\Phi_S^f$ for a circular region in the film with radius $r=1\,\um$ centered on the vortex core.
 As $\Lambda$ increases, so to does the supercurrent contribution to the fluxoid.
@@
     \label{fig:pearl}
-\end{figure}
+\end{figure*}
 
@@
 
-Figure~\ref{fig:pearl}(e) shows the fluxoid for a circular region $S$ with radius $r=1\,\mu\mathrm{m}$ enclosing a Pearl vortex trapped in a film as a function of the film's effective penetration depth, $\Lambda$.
+Figure~\ref{fig:pearl}(e) shows the fluxoid for a circular region $S$ with radius $r=1\,\um$ enclosing a Pearl vortex trapped in a film as a function of the film's effective penetration depth, $\Lambda$.
 When $\Lambda=0$, the screening currents decay very quickly away from the center of the vortex, so the ``supercurrent part'' of the $\Phi^f_S$ vanishes.
@@
 
-While the 2D London model doesn't ``know'' about fluxoid quantization, in the sense that it is not automatically satisfied by solutions to Eq.~\ref{eq:london} for multiply-connected films, we can nevertheless calculate current and field distributions for different fluxoid states $\Phi^f_S=n\Phi_0$ in multiply-connected superconductors by adjusting the currents circulating around each hole to realize a prescribed set of fluxoid values.
+While the 2D London model doesn't ``know'' about fluxoid quantization, in the sense that the quantization condition $\Phi^f_S=n\Phi_0$ is not automatically satisfied by solutions to Eq.~\ref{eq:london} for multiply-connected films, we can nevertheless calculate current and field distributions for different fluxoid states in multiply-connected superconductors by adjusting the currents circulating around each hole to realize a prescribed set of fluxoid values.
 For a structure with $N_h$ holes, we can specify $N_h$ fluxoids $\Phi^f_h$ and find the circulating currents $I_h$ by minimizing the deviation of each fluxoid from its desired value.
-(If $N_h=1$, this is a simple 1D root-finding problem.) This calculation is implemented in the \inline{superscreen.find_fluxoid_solution()} function.
-
-Here, we use \inline{superscreen.find_fluxoid_solution()} to compute the current and field distributions in and around a film with a single hole in the $n=1$ fluxoid state as a function of the film's effective penetration depth, $\Lambda$.
+This calculation is implemented in the \inline{superscreen.find_fluxoid_solution()} function.
 
@@
 
-We'll focus first on the self-inductance of circular and square rings.
 For a circular ring with inner radius $a$, outer radius $b>a$, and penetration depth $\Lambda=0$, Clem~\cite{Babaei_Brojeny2003-la} found that the self-inductance approaches $L=2\mu_0 a$ in the ``small hole'' limit $\tilde{a}=a/b\ll 1$.
-In the opposite ``thin ring'' limit $\tilde{a}=a/b\approx 1$, the inductance was found to approach $L=\mu_0b(1+\tilde{a})(\tanh^{-1}\tilde{a}+\log 4 - 1)$.
 Clem and Brandt~\cite{Brandt2004-ew} and Khapaev~\cite{Khapaev1997-kw} calculated the self-inductance of circular and square rings as a function of the ratio of inner and outer diameters.
@@
 The superconducting sample screens the magnetic field from the field coil, modifying the amount of flux threading the pickup loop.
-Thus the mutual inductance between the field coil and pickup loop provides a measure of the sample's diamagnetic susceptibility, which is in turn a measure of the sample's penetration depth.
+Thus the mutual inductance between the field coil and pickup loop provides a measure of the sample's magnetic susceptibility.
+For superconducting samples, this diamagnetic response is a measure of the sample's penetration depth and therefore its superfluid density.
 
@@
 
-Figure~\ref{fig:susceptometry}(a) shows a \inline{Device} representing field coil and pickup loop of an actual scanning SQUID sensor.
+Figure~\ref{fig:squid-layouts}(a) shows \SuperScreen \inline{Device} models of the field coil and pickup loop region of four types of real SQUID susceptometers, with geometry taken from the layout artwork (GDS) files.
 In addition to the field coil and pickup loop, there are superconducting shields that limit the amount of magnetic flux that can penetrate the leads connecting the loops to the rest of the circuit (the rest of the circuit is not modeled).
 There are three relevant layers of superconducting films: the base electrode (``BE"), which is furthest from the sample contains the field coil; the first wiring layer (``W1"), which contains the pickup loop and a shield covering the field coil leads; and the second wiring layer (``W2"), which is closest to the sample and contains a shield covering the pickup loop leads.
-The device also contains a layer and film representing the superconducting sample.
+There are two insulating layers: $I1$, which separates BE and W1, and $I2$, which separates W1 and W2.
+Table~\ref{table:squid-layers}.
+
+\begin{table*}[]
+\centering
+\begin{tabular}{|l|l|l|}
+\hline
+Layer name        & Thickness [nm] & Films located in layer \\ \hline
+\hline
+BE (bottom) & 160            & Field coil, pickup loop shield      \\ \hline
+I1          & 150            & ---                                 \\ \hline
+W1          & 100            & Pickup loop, field coil shield      \\ \hline
+I2          & 130            & ---                                 \\ \hline
+W2 (top)    & 200            & Pickup loop shield, modulation coil \\ \hline
+\end{tabular}
+\caption{Layer stackup for the SQUID susceptometers Section~\ref{section:examples:scanning-squid}. See Ref.~\cite{kirtley_scanning_2016} for more details on the designed of the suscpetometers.}
+\label{table:squid-layers}
+\end{table*}
 
 To model a SQUID susceptometry measurement, we first calculate $M_0$, the mutual inductance between the field coil and pickup loop in the absence of the sample.
-This can be done by temporarily setting the sample layer effective penetration depth to a very large value such that it essentially does not screen the field from the field coil (in this case, we set $\Lambda = 10^5\,\mu\mathrm{m}$).
+This can be done by temporarily setting the sample layer effective penetration depth to a very large value such that it essentially does not screen the field from the field coil (in this case, we set $\Lambda = 10^5\,\um$).
 We then model the field from a known current flowing in the field coil following Section~\ref{section:model:holes} and self-consistently calculate the response of both the sample and the other superconducting layers of the SQUID sensor following Section~\ref{section:model:multilayer}.
@@
 the calculations and in Refs.~\cite{Kirtley2016-zz,Kirtley2016-gt}), but care must be taking in interpreting results in these cases.
-Second, as a London model, Brandt and Clem's method assumes that all superconducting films behave linearly and without dissipation, and that the applied magnetic field and current density are well below the critical field and critical current density of all films in a device.
-% Third, while currents associated with vortices and flux trapped in holes can be modeled, \SuperScreen does not treat the energetics of vortex nucleation in films or fluxoid transitions in multiply-connected films.
-For further discussion of these topics in the context of the present model, see Refs.~\cite{Brandt2004-ew, Clem2005-ye}.
-Third, as currently implemented, \SuperScreen does not support ``terminal currents,'' i.e.
+Second, the model assumes that all superconducting films behave linearly and without dissipation, and that the applied magnetic field and current density are well below the critical field and critical current density of all films in a device.
+
+Third, \SuperScreen does not support ``terminal currents,'' i.e.
 currents flowing in one terminal of a device and out another terminal.
 This means that inductance calculations are limited to structures with holes, in which all applied currents are circulating currents associated with trapped flux (see Sections~\ref{section:model:holes} and~\ref{section:examples:mutual-inductance}).
-Terminal currents can be included in the stream function-base model by setting appropriate boundary conditions~\cite{Khapaev1997-kw,Khapaev2001-xq,Khapaev2001-pw,Muller2021-ci}.
-Finally, care should be taken to ensure that for a given model the mesh is of sufficient density that, to within the desired precision, the results of simulations do not depend on mesh size.
-
-Potential improvements to \SuperScreen include: support for terminal currents as discussed above, more sophisticated mesh generation (e.g.
-automated local mesh refinement based on device geometry), automated determination of solution convergence for models with multiple layers, an improved interface for generating complex device geometries (for example via integration with standard integrated circuit layout software), and further optimization for memory and CPU efficiency.
+Terminal currents can, however, be included in stream function-base models by setting appropriate boundary conditions~\cite{Khapaev1997-kw,Khapaev2001-xq,Khapaev2001-pw,Muller2021-ci}.
+Finally, care should be taken to ensure that for a given model the mesh is of sufficient density that, to within the desired precision, the results of simulations do not depend on mesh size (see \ref{appendix:numerics}).
+
+Potential improvements to \SuperScreen include: support for terminal currents as discussed above, automated determination of solution convergence for models with multiple layers, more sophisticated mesh generation (e.g.
+automated local mesh refinement based on device geometry or adaptive mesh refinement based on solution convergence), integration with standard integrated circuit layout software and file formats, and further optimization for memory and CPU efficiency.
 
@@
 
-% A demonstration of these properties for the case of the square ring with effective penetration depth $\Lambda=1\,\mu\mathrm{m}$, inner side length $5\,\mu\mathrm{m}$, and outer side length $10\,\mu\mathrm{m}$ subject to a uniform applied field of 0.1 mT is shown in Figure~\ref{fig:fluxoid}.
+% A demonstration of these properties for the case of the square ring with effective penetration depth $\Lambda=1\,\um$, inner side length $5\,\um$, and outer side length $10\,\um$ subject to a uniform applied field of 0.1 mT is shown in Figure~\ref{fig:fluxoid}.
 Property 1 is shown in the first two rows, and property 2 is shown in the last row.
@@
 %     \includegraphics[width=\textwidth]{examples/images/fluxoid_combined.png}
-%     \caption{Demonstration of the fluxoid properties listed in Section~\ref{section:examples:fluxoid} for a square ring with $\Lambda=1\,\mu\mathrm{m}$, inner side length $5\,\mu\mathrm{m}$, and outer side length $10\,\mu\mathrm{m}$, whose outline is shown with white lines in the left and middle columns, subject to a uniform applied field of 0.1 mT.
+%     \caption{Demonstration of the fluxoid properties listed in Section~\ref{section:examples:fluxoid} for a square ring with $\Lambda=1\,\um$, inner side length $5\,\um$, and outer side length $10\,\um$, whose outline is shown with white lines in the left and middle columns, subject to a uniform applied field of 0.1 mT.
 The left and middle columns show the computed current density and out-of-plane-field, overlaid with several regions $S$ for which the fluxoids $\Phi^f_S$ are calculated using \inline{Solution.polygon_fluxoid()}.
@@
 
-The latter case---mutli-layer structures with closely-spaced layers---is the most challenging class of problem to solve because the iterative method used to solve multi-layer structures (Section~\ref{section:model:multilayer}) is memory-intensive for models with a large mesh (many vertices $v$ and triangles $t$) and/or many layers $L$.
-As mentioned in Section~\ref{section:model:multilayer}, at each iteration of this process, we update the applied field $H_{z,\,\mathrm{applied}}(\vec{r}, z_\ell)$ at each layer $\ell$ based on the currents flowing in all other layers $m\neq\ell$, according to
-
-\begin{equation}
-    H_{z,\,\mathrm{applied}}(\vec{r}, z_\ell) \to
-    H_{z,\,\mathrm{applied}}(\vec{r}, z_\ell)
-    + \sum_{m\neq\ell}
-    \int_{S_m} Q_z(\vec{r},\vec{r}')g_m(\vec{r}')\,\mathrm{d}^2r',
-    \label{eq:iterative}
-\end{equation}
-where $S_m$ is surface of all films in layer $m$ and $g_m$ is the stream function for layer $m$.
-For a model with $L$ layers, at each iteration Eq.~\ref{eq:iterative} requires the calculation of $\binom{L}{2} = L(L-1)/2$ kernel matrices $\mathbf{Q_z}$, each of which is a dense $v\times t$ floating point matrix.
-Typically the number of mesh vertices is approximately half the number of triangles ($v\approx t / 2$), so for a mesh with $t=10,000$ triangles, each of these $\mathbf{Q_z}$ matrices is roughly 400 MB (200 MB) if using 64-bit double-precision floats (32-bit single-precision floats).
+The latter case---mutli-layer structures with closely-spaced layers---is the most challenging class of problem to solve because the iterative method used to solve multi-layer structures (Section~\ref{section:model:multilayer}) is memory-intensive for models with a large mesh (many vertices $p$ and triangles $t$, with typically $p\approx t / 2$) and/or many layers $L$.
+The average distance between vertices decreases slowly with increasing number of triangles, $\delta r\sim t^{-1/2}$, whereas the size of the (dense floating-point) $p\times t$ matrix that represents the dipole kernel $Q_z(\vec{r},\vec{r}')$ in Eq.~\ref{eq:hz-from-kernel} increases roughly as $t^2$.
+The end result is that the memory footprint of kernel matrix scales roughly as $\delta r^{-4}$, so decreasing the mean distance between vertices by a factor of 2 increases the memory required by a factor of 16.
+Furthermore, for a model with $L$ layers there are $\binom{L}{2} = L(L-1)/2$ such kernel matrices needed for each iteration of the calculation outlined in Section~\ref{section:model:multilayer}.
+In \inline{superscreen.solve()}, these $\binom{L}{2}$ matrices are computed during the first iteration and then cached in memory for use in subsequent iterations.
+One can force the kernel matrices to be cached to disk if they would otherwise occupy too large a fraction of the available system memory using the \inline{cache_kernel_memory_cutoff} argument, but this comes at a significant performance cost.
+
+The limitation described above can be seen in the model of the largest SQUID susceptometer described in Section~\ref{section:examples:scanning-squid}, which has a field coil outer radius of $8\,\um$ and a total modeled area of roughly $600\,\um^2$.
+
+% As mentioned in Section~\ref{section:model:multilayer}, at each iteration of this process, we update the applied field $H_{z,\,\mathrm{applied}}(\vec{r}, z_\ell)$ at each layer $\ell$ based on the currents flowing in all other layers $m\neq\ell$, according to
+
+% \begin{align}
+% \begin{split}
+%     &H_{z,\,\mathrm{applied}}(\vec{r}, z_\ell) \to\\
+%     &H_{z,\,\mathrm{applied}}(\vec{r}, z_\ell)
+%     + \sum_{m\neq\ell}
+%     \int_{S_m} Q_z(\vec{r},\vec{r}')g_m(\vec{r}')\,\mathrm{d}^2r',
+%     \label{eq:iterative}
+% \end{split}
+% \end{align}
+% where $S_m$ is surface of all films in layer $m$ and $g_m$ is the stream function for layer $m$.
+% Furthermore, for a model with $L$ layers, at each iteration, Eq.~\ref{eq:iterative} requires the calculation of $\binom{L}{2} = L(L-1)/2$ such kernel matrices.
+representing $Q_z(\vec{r},\vec{r}')$ in Eq.~\ref{eq:hz-from-kernel}, each of which is a dense $p\times t$ floating point matrix.
+Typically the number of mesh vertices is approximately half the number of triangles ($p\approx t / 2$), so for a mesh with $t=10,000$ triangles, each of these $\mathbf{Q_z}$ matrices is roughly 400 MB (200 MB) if using 64-bit double-precision floats (32-bit single-precision floats).
 Furthermore, each iteration requires performing $2\binom{L}{2} = L(L-1)$ sums involving $\mathbf{Q_z}\cdot\mathbf{g}_m$, where $\mathbf{g}_m$ is the $n\times1$ vector defining the stream function in layer $m$ evaluated at the center of each triangle in the mesh.
@@
 \SuperScreen also supports parallel processing using the \inline{multiprocessing} module from the Python standard library, however this is generally less efficient than \inline{ray} in this application.
-
-There are three ways to invoke \inline{ray} from \SuperScreen when running on a single machine, e.g.
-a multi-core CPU.
-The first is to simply pass the keyword argument \inline{parallel_method="ray"} when calling \inline{solve_many()}.
-This will automatically create a \inline{ray} cluster using all available physical CPU cores, solve the models in parallel, and then shut down the cluster before returning.
-The second method is to manually create a \inline{ray} cluster using the \inline{ray} Python application programming interface (API) prior to calling \inline{solve_many(..., parallel_method="ray")}, as demonstrated in Code Block~\ref{code:ray-python}.
-The third method is to start a \inline{ray} cluster using the command line interface (CLI), then connect to the existing cluster using the Python API prior to calling \inline{solve_many(..., parallel_method="ray")}, as demonstrated in Code Block~\ref{code:ray-cli}.
-One of the latter two methods should be used for finer control over the \inline{ray} cluster (number of CPUs to utilize, etc.).
 
@@
 \end{minted}
+\captionof{listing}{Starting and stopping \inline{ray} outside of \inline{superscreen.solve_many()} using the Python API.
+See the ``API and Package Reference" section of the \inline{ray} documentation for additional options in \inline{ray.init()}~\cite{ray-docs}.}
+\label{code:ray-python}
 \end{code}
 
-\begin{minipage}{\textwidth}
 \begin{code}
-\captionof{listing}{Starting and stopping \inline{ray} outside of \inline{superscreen.solve_many()} using the command line interface.
-See the \inline{ray} documentation for additional options in \inline{ray start}~\cite{ray-docs}.}
-\label{code:ray-cli}
 \begin{minted}[fontsize=\small]{bash}
@@
 \end{minted}
-
 \begin{minted}[fontsize=\small]{python}
@@
 \end{minted}
-
 \begin{minted}[fontsize=\small]{bash}
@@
 \end{minted}
-\captionof{listing}{Starting and stopping \inline{ray} outside of \inline{superscreen.solve_many()} using the Python API.
-See the ``API and Package Reference" section of the \inline{ray} documentation for additional options in \inline{ray.init()}~\cite{ray-docs}.}
-\label{code:ray-python}
+\captionof{listing}{Starting and stopping \inline{ray} outside of \inline{superscreen.solve_many()} using the command line interface.
+See the \inline{ray} documentation for additional options in \inline{ray start}~\cite{ray-docs}.}
+\label{code:ray-cli}
 \end{code}
-\end{minipage}
+
+There are three ways to invoke \inline{ray} from \SuperScreen when running on a single machine, e.g.
+a multi-core CPU.
+The first is to simply pass the keyword argument \inline{parallel_method="ray"} when calling \inline{solve_many()}.
+This will automatically create a \inline{ray} cluster using all available physical CPU cores, solve the models in parallel, and then shut down the cluster before returning.
+The second method is to manually create a \inline{ray} cluster using the \inline{ray} Python application programming interface (API) prior to calling \inline{solve_many(..., parallel_method="ray")}, as demonstrated in Code Block~\ref{code:ray-python}.
+The third method is to start a \inline{ray} cluster using the command line interface (CLI), then connect to the existing cluster using the Python API prior to calling \inline{solve_many(..., parallel_method="ray")}, as demonstrated in Code Block~\ref{code:ray-cli}.
+One of the latter two methods should be used for finer control over the \inline{ray} cluster (number of CPUs to utilize, etc.).
 

### 2021-11-19 main.tex

@@
     \centering
-    \includegraphics[width=\textwidth]{examples/images/pearl.pdf}
+    \includegraphics[width=\textwidth]{examples/images/pearl.png}
     \caption{Vortex field profiles calculated with \SuperScreen agree with the analytical solution (Eq.~\ref{eq:pearl}) to within a few percent.
@@
 (a) Cross section along the $x$-axis of the out-of-plane magnetic field $\mu_0H_z$ from the vortex, evaluated at a vertical distance $z=1\,\um$ above the film.
+The inset shows the vortex field profile for $\Lambda=0\,\um$ evaluated at $z=1\,\um$, with a dashed white line indicating the cross-section axis.
 (b) Percentage difference between the $\mu_0H_z$ calculated with \SuperScreen and the Fourier transform method for the $x$-axis cut shown in (a).
@@
 
-Figure~\ref{fig:squid-layouts}(a) shows \SuperScreen \inline{Device} models of the field coil and pickup loop region of four types of real SQUID susceptometers, with geometry taken from the layout artwork (GDS) files.
+Figure~\ref{fig:squid-mutuals}(a) shows \SuperScreen \inline{Device} models of the field coil and pickup loop region of four types of real SQUID susceptometers, with geometry taken from the layout artwork (GDS) files.
 In addition to the field coil and pickup loop, there are superconducting shields that limit the amount of magnetic flux that can penetrate the leads connecting the loops to the rest of the circuit (the rest of the circuit is not modeled).
@@
 \end{tabular}
-\caption{Layer stackup for the SQUID susceptometers Section~\ref{section:examples:scanning-squid}. See Ref.~\cite{kirtley_scanning_2016} for more details on the designed of the suscpetometers.}
+\caption{Layer stackup for the SQUID susceptometers Section~\ref{section:examples:scanning-squid}. See Ref.~\cite{Kirtley2016-zz} for more details on the designed of the suscpetometers.}
 \label{table:squid-layers}
 \end{table*}
+
+\begin{figure*}
+    \centering
+    \includegraphics[width=\textwidth]{examples/images/squid-mutuals.png}
+    \caption{Calculating SQUID susceptometer mutual inductance, defined as the fluxoid induced in the SQUID pickup loop per unit current flowing in the field coil: $M=\Phi_\mathrm{PL} / I_\mathrm{FC}$.
+Top row (a): Schematics of \SuperScreen models for the field coil and pickup loop region of four sizes of scanning SQUID susceptometer (generated using \inline{Device.draw()}) with pickup loop inner radii ranging from $0.1\,\um$ (``Small'') to $3\,\um$ (``X-Large'').
+The wiring layers BE, W1, and W2 are shown in blue, orange, and green respectively.
+Middle row (b): Simulated magnetic field $\mu_0H_z$ evaluated at the plane of layer W1, which contains the pickup loop, normalized by the current $I_\mathrm{FC}$ flowing in the field coil (which is located in layer BE).
+Bottom row (c): Convergence of the four models, defined as the fractional change in mutual inductance between subsequent iterations $i$.
+For all four models, the simulated mutual inductance, $M_\mathrm{sim}$, falls within the range of mutual inductance values measured in real devices, $M_\mathrm{exp}$, which were reported in Table 1 of Ref.~\cite{Kirtley2016-zz}.
+The meshes for the ``Small,'' ``Medium,'' and ``Large'' models consisted of approximately 5,000 vertices and 10,000 triangles, whereas the mesh for the ``X-Large'' model consisted of about 7,700 vertices and 15,000 triangles.
+The two smaller models converge more quickly than the two larger models for reasons discussed in \ref{appendix:numerics}.}
+    \label{fig:squid-mutuals}
+\end{figure*}
 

### 2021-11-19 main.tex
Updates from Overleaf

@@
 # Visualize the solution.
+# Plot the magnetic field evaluated at each layer in the Device.
 solution.plot_fields()
+# Plot the current density evaluated at each layer in the Device.
 solution.plot_currents()
+# Plot the field evaluated at any points in space.
+solution.plot_field_at_positions(device.points, zs=0.5)
 \end{minted}
@@
 a) Plot of the boundary of the ring (blue), circular bounding box (orange), and the computational mesh (gray), generated with \inline{Device.plot()}.
-b) The $z$-component of the magnetic field $\mu_0H_z$ evaluated at the plane of the ring, generated with \inline{Solution.plot_fields()}.
-c) Current density $\vec{J}$ in the ring, generated with \inline{Solution.plot_currents()}.}
+b) The current density $\vec{J}$ in the ring, generated with \inline{Solution.plot_currents()}.
+c) The $z$-component of the magnetic field $\mu_0H_z$ evaluated at the plane of the ring, generated with \inline{Solution.plot_fields()}.
+d) The $z$-component of the magnetic field evaluated $z=0.5\,\um$ above the ring (generated using \inline{Solution.plot_field_at_positions()}.}
     \label{fig:ring-with-slit}

### 2021-11-19 main.tex
Updates from Overleaf

@@
 There have been many previous numerical studies of magnetic screening and inductance extraction in thin film and two-dimensional (2D) superconducting devices~\cite{Jaycox1981-zl, Ketchen1982-at, Ketchen2012-mb, Hildebrandt1995-uw, Khapaev1997-kw, Khapaev2001-xq, Khapaev2001-pw, Babaei_Brojeny2003-la, Brandt2004-ew, Brandt2005-wj, Clem2005-ye, Muller2021-ci, Jackman2016-mf}.
-However, few software tools for this task exist and those that are available are closed-source, are written in low-level compiled languages like C, and/or require the use of specialized file formats or separate computer aided design (CAD) software for defining device geometries and model configurations.\footnote{A brief summary of existing tools can be found in \ref{appendix:other-tools}, and a more thorough overview in Ref.~\cite{Gaj1999-ls}.} Most of these tools are intended for use in the design of superconducting integrated circuits for rapid single flux quantum (RSFQ) logic and are primarily used for inductance extraction~\cite{Gaj1999-ls}.
+However, few software tools for this task exist and those that are available are closed-source, are written in low-level compiled languages like C, and/or require the use of specialized file formats or separate computer aided design (CAD) software for defining device geometries and model configurations.\footnote{A brief summary of existing tools can be found in \ref{appendix:other-tools}, and a more thorough overview in Ref.~\cite{Gaj1999-ls}.} Most of these tools are intended for use in the design of superconducting integrated circuits for single flux quantum (SFQ) logic and are primarily used for inductance extraction~\cite{Gaj1999-ls}.
 In contrast, \SuperScreen is an open-source, user-friendly, portable research tool designed to lower the barrier to entry to quantitative modeling of 2D superconductors, and to help interpret and inform measurements of superconducting thin films and devices.
@@
 
-\SuperScreen requires Python version 3.6--3.9.
+At the time of writing, \SuperScreen requires Python version 3.6--3.9.
 The package is located in a public repository on GitHub~\cite{superscreen}, and a suite of unit tests is run automatically via the GitHub Actions continuous integration (CI) tool whenever a change or proposed change (Pull Request) is made to the \inline{main} branch of the repository.
@@
 ri = 1  # inner radius
-slit_width = 0.5
+slit_width = 0.25
 Lambda = 1  # effective penetration depth
@@
 \end{minted}
-\captionof{listing}{The typical workflow for a \SuperScreen simulation: 1) Define device geometry and materials properties, 2) generate the computational mesh, 3) solve the model for a given applied field, and 4) visualize the results.}
+\captionof{listing}{The typical workflow for a \SuperScreen simulation: 1) Define the device geometry and materials properties, 2) generate the computational mesh, 3) solve the model for a given applied field and/or trapped flux, and 4) visualize the results.}
 \label{code:device}
@@
     \includegraphics[width=\textwidth]{examples/images/ring_with_slit.pdf}
-    \caption{The output of Code Block~\ref{code:device}: Meissner screening of a uniform $10\,\mu\mathrm{T}$ out-of-plane field by a ring with inner diameter $1\,\um$, outer diameter $3\,\um$, and effective penetration depth $\Lambda=1\,\um$, interrupted by a slit of width $0.5\,\um$.
+    \caption{The output of Code Block~\ref{code:device}: Meissner screening of a uniform $10\,\mu\mathrm{T}$ out-of-plane field by a ring with inner diameter $1\,\um$, outer diameter $3\,\um$, and effective penetration depth $\Lambda=1\,\um$, interrupted by a slit of width $0.25\,\um$.
 a) Plot of the boundary of the ring (blue), circular bounding box (orange), and the computational mesh (gray), generated with \inline{Device.plot()}.

### 2021-11-20 main.tex

@@
 The \inline{superscreen.geometry} module provides functions for generating the underlying polygon vertices for simple shapes (ellipses and rectangles), which can be combined as described above to create more complicated geometries.
+
 \begin{code}
@@
 \end{code}
+
 Once the layers, films, holes, and abstract regions have been defined, one can generate the computational mesh by calling \inline{Device.make_mesh()}.

### 2021-11-20 main.tex
Updates from Overleaf

@@
 
+\begin{figure}
+    \centering
+    \includegraphics[width=\linewidth]{examples/images/xlarge-dz-dr.png}
+    \caption{(a) Field coil - pickup loop mutual inductance for the largest SQUID suscepometer modeled in Section~\ref{section:examples:scanning-squid} as a function of the minimum vertical spacing between layers, $\delta z$.
+The simulated mutual inductance is shown with blue circles, and a histogram of the mesh vertex-to-vertex distances $\delta r$ is shown }
+    \label{fig:xlarge-dz-dr}
+\end{figure}
+
 % As mentioned in Section~\ref{section:model:multilayer}, at each iteration of this process, we update the applied field $H_{z,\,\mathrm{applied}}(\vec{r}, z_\ell)$ at each layer $\ell$ based on the currents flowing in all other layers $m\neq\ell$, according to

### 2021-11-20 main.tex

--- 2021-11-20 main.tex
@@
 However, the discretized version of Eq.~\ref{eq:hz-from-kernel}, in which the double integral over the film area $F$ is replaced by a sum over triangular mesh elements, is only valid if $z-z'$, the vertical distance between the film and the point at which the field is being evaluated, is larger than the typical distance $\delta r$ between vertices in the mesh representing the film.
-For $z-z'\lesssim\delta r$, the field $H_z(\vec{r})$ resembles that of a set of isolated dipoles located at the mesh vertex positions, rather than that of a continuous sheet of current.
+For $z-z'\lesssim\delta r$, the field $H_z(\vec{r})$ resembles that of a discrete set of isolated dipoles located at the mesh vertex positions, rather than that of a continuous sheet of current.
 This can lead to unphysical results when evaluating the field very close to the surface of a film (for example using \inline{Solution.field_at_position()}), or when solving models involving multi-layer structures where the vertical spacing between layers is much smaller than the lateral extent of the films, in which case the iterative calculation (Section~\ref{section:model:multilayer}) may not converge.
+
+The limitation described above can be seen in the model of the largest SQUID susceptometer described in Section~\ref{section:examples:scanning-squid}, which has a field coil outer radius of $8\,\um$ and a total modeled area of roughly $600\,\um^2$.
+As shown in Figure~\ref{fig:xlarge-dz-dr}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\linewidth]{examples/images/xlarge-dz-dr.png}
+    \caption{\SuperScreen results may be unreliable for multi-layer models where the spacing between layers is smaller than the typical vertex-to-vertex distance, $\delta r$.
+(a) Field coil - pickup loop mutual inductance for the largest SQUID suscepometer modeled in Section~\ref{section:examples:scanning-squid} as a function of the minimum vertical spacing between layers, $\delta z$.
+The simulated mutual inductance is shown with blue circles, and a histogram of the mesh vertex-to-vertex distances $\delta r$ is shown in orange (arb.
+$y$ axis units).
+When $\delta z\lesssim\delta r$, the model significantly underestimates the mutual inductance.
+(b) and (c): Out-of-plane magnetic field $\mu_0H_z$ evaluated at the plane of the pickup loop (W1 layer) for (b) the nominal layer spacing with $\delta z<\delta 2$ (indicated with a black $\times$ in (a)) and (c) $\delta z > \delta r$ (indicated with a black $+$ in (a)).}
+    \label{fig:xlarge-dz-dr}
+\end{figure}
 
@@
 One can force the kernel matrices to be cached to disk if they would otherwise occupy too large a fraction of the available system memory using the \inline{cache_kernel_memory_cutoff} argument, but this comes at a significant performance cost.
-
-The limitation described above can be seen in the model of the largest SQUID susceptometer described in Section~\ref{section:examples:scanning-squid}, which has a field coil outer radius of $8\,\um$ and a total modeled area of roughly $600\,\um^2$.
 

### 2021-11-20 main.tex
Updates from Overleaf

@@
 The meshes for the ``Small,'' ``Medium,'' and ``Large'' models consisted of approximately 5,000 vertices and 10,000 triangles, whereas the mesh for the ``X-Large'' model consisted of about 7,700 vertices and 15,000 triangles.
-The two smaller models converge more quickly than the two larger models for reasons discussed in \ref{appendix:numerics}.}
+The two smaller models converge more quickly than the two larger models for reasons discussed in \ref{appendix:numerics}.
+Note that for the ``X-Large'' model, we set the thicknesses of layers I1 and I2 both to 300 nm to ensure convergence (see \ref{appendix:numerics} and Figure~\ref{fig:xlarge-dz-dr}).}
     \label{fig:squid-mutuals}
@@
 Eq.~\ref{eq:hz-from-kernel} is exact for a continuous stream function $g$.
-However, the discretized version of Eq.~\ref{eq:hz-from-kernel}, in which the double integral over the film area $F$ is replaced by a sum over triangular mesh elements, is only valid if $z-z'$, the vertical distance between the film and the point at which the field is being evaluated, is larger than the typical distance $\delta r$ between vertices in the mesh representing the film.
-For $z-z'\lesssim\delta r$, the field $H_z(\vec{r})$ resembles that of a discrete set of isolated dipoles located at the mesh vertex positions, rather than that of a continuous sheet of current.
+However, the discretized version of Eq.~\ref{eq:hz-from-kernel}, in which the double integral over the film area $F$ is replaced by a sum over triangular mesh elements, is only valid if $\delta z = z-z'$, the vertical distance between the film and the point at which the field is being evaluated, is larger than the typical distance $\delta r$ between vertices in the mesh representing the film.
+For $z-z'=\delta z\lesssim\delta r$, the field $H_z(\vec{r})$ resembles that of a discrete set of isolated dipoles located at the mesh vertex positions, rather than that of a continuous sheet of current (see Figure~\ref{fig:xlarge-dz-dr}(b)).
 This can lead to unphysical results when evaluating the field very close to the surface of a film (for example using \inline{Solution.field_at_position()}), or when solving models involving multi-layer structures where the vertical spacing between layers is much smaller than the lateral extent of the films, in which case the iterative calculation (Section~\ref{section:model:multilayer}) may not converge.
-
-The limitation described above can be seen in the model of the largest SQUID susceptometer described in Section~\ref{section:examples:scanning-squid}, which has a field coil outer radius of $8\,\um$ and a total modeled area of roughly $600\,\um^2$.
-As shown in Figure~\ref{fig:xlarge-dz-dr}
 
@@
 When $\delta z\lesssim\delta r$, the model significantly underestimates the mutual inductance.
-(b) and (c): Out-of-plane magnetic field $\mu_0H_z$ evaluated at the plane of the pickup loop (W1 layer) for (b) the nominal layer spacing with $\delta z<\delta 2$ (indicated with a black $\times$ in (a)) and (c) $\delta z > \delta r$ (indicated with a black $+$ in (a)).}
+(b) and (c): Out-of-plane magnetic field $\mu_0H_z$ evaluated at the plane of the pickup loop (W1 layer) for (b) the nominal layer spacing with $\delta z<\delta 2$ (indicated with a black $\times$ in (a)) and (c) $\delta z > \delta r$ (indicated with a black $+$ in (a)).
+For $\delta r\lesssim\delta z$, the magnet field calculated using Eq.~\ref{eq:hz-from-kernel} resembles that of a discrete set of isolated dipoles rather than a continuous sheet of current.}
     \label{fig:xlarge-dz-dr}
@@
 
-The latter case---mutli-layer structures with closely-spaced layers---is the most challenging class of problem to solve because the iterative method used to solve multi-layer structures (Section~\ref{section:model:multilayer}) is memory-intensive for models with a large mesh (many vertices $p$ and triangles $t$, with typically $p\approx t / 2$) and/or many layers $L$.
-The average distance between vertices decreases slowly with increasing number of triangles, $\delta r\sim t^{-1/2}$, whereas the size of the (dense floating-point) $p\times t$ matrix that represents the dipole kernel $Q_z(\vec{r},\vec{r}')$ in Eq.~\ref{eq:hz-from-kernel} increases roughly as $t^2$.
-The end result is that the memory footprint of kernel matrix scales roughly as $\delta r^{-4}$, so decreasing the mean distance between vertices by a factor of 2 increases the memory required by a factor of 16.
+The limitation described above can be seen in the model of the largest SQUID susceptometer described in Section~\ref{section:examples:scanning-squid}, which has a field coil inner radius of $6\,\um$ and a total modeled area of roughly $600\,\um^2$.
+As shown in Figure~\ref{fig:xlarge-dz-dr}, \SuperScreen significantly underestimates the mutual inductance between the field coil and pickup loop when $\delta z <\delta r$ because, in that case, the discretized version of Eq.~\ref{eq:hz-from-kernel} does not correctly compute the magnetic field due the stream function in the superconducting layers.
+For the sake of computing mutual inductance as in Section~\ref{section:examples:scanning-squid}, it is physically reasonable to artificially increase the vertical spacing between layers such that $\delta z\geq \delta r$ because we expect the magnetic field a vertical distance $\delta z$ away from the center of the field coil to fall off roughly as $\left(\delta z^2 + R^2_\mathrm{FC}\right)^{-3/2}$, where $R_\mathrm{FC}\approx 6\,\um\gg\delta z$.
+However, in situations where $\delta z$ is a critical dimension (in the sense that increasing it invalidates the physical model), one's only option is to decrease $\delta r$ by increasing the density of the mesh.
+
+For this reason, mutli-layer structures with closely-spaced layers are the most challenging class of problem to solve.
+The iterative method used described in Section~\ref{section:model:multilayer} is memory-intensive for models with a large mesh (many vertices $p$ and triangles $t$, with typically $p\approx t / 2$) and/or many layers $L$.
+The average distance between vertices decreases slowly with increasing number of triangles, $\langle\delta r\rangle\sim t^{-1/2}$, whereas the size of the (dense floating-point) $p\times t$ matrix that represents the dipole kernel $Q_z(\vec{r},\vec{r}')$ in Eq.~\ref{eq:hz-from-kernel} increases roughly as $t^2$.
+The end result is that the memory footprint of kernel matrix scales roughly as $\langle\delta r\rangle^{-4}$, so decreasing the mean distance between vertices by a factor of 2 increases the memory required by a factor of 16.
 Furthermore, for a model with $L$ layers there are $\binom{L}{2} = L(L-1)/2$ such kernel matrices needed for each iteration of the calculation outlined in Section~\ref{section:model:multilayer}.

### 2021-11-20 main.tex
Updates from Overleaf

@@
 \newcommand{\um}{\mu\mathrm{m}}
+\newcommand{\nm}{\mathrm{nm}}
 
@@
 )
-device.make_mesh(min_triangles=8000)
+device.make_mesh(min_triangles=8_000)
 # Specify the vortex position.
@@
 \hline
-Layer name        & Thickness [nm] & Films located in layer \\ \hline
+Layer name        & Thickness & Films located in layer \\ \hline
 \hline
-BE (bottom) & 160            & Field coil, pickup loop shield      \\ \hline
-I1          & 150            & ---                                 \\ \hline
-W1          & 100            & Pickup loop, field coil shield      \\ \hline
-I2          & 130            & ---                                 \\ \hline
-W2 (top)    & 200            & Pickup loop shield, modulation coil \\ \hline
+BE (bottom) & $d_\mathrm{BE} = 160\,\nm$            & Field coil, pickup loop shield      \\ \hline
+I1          & $d_\mathrm{I1} = 150\,\nm$            & ---                                 \\ \hline
+W1          & $d_\mathrm{W1}=100\,\nm$            & Pickup loop, field coil shield      \\ \hline
+I2          & $d_\mathrm{I2} = 130\,\nm$            & ---                                 \\ \hline
+W2 (top)    & $d_\mathrm{W2} = 200\,\nm$            & Pickup loop shield, modulation coil \\ \hline
 \end{tabular}
@@
 The limitation described above can be seen in the model of the largest SQUID susceptometer described in Section~\ref{section:examples:scanning-squid}, which has a field coil inner radius of $6\,\um$ and a total modeled area of roughly $600\,\um^2$.
-As shown in Figure~\ref{fig:xlarge-dz-dr}, \SuperScreen significantly underestimates the mutual inductance between the field coil and pickup loop when $\delta z <\delta r$ because, in that case, the discretized version of Eq.~\ref{eq:hz-from-kernel} does not correctly compute the magnetic field due the stream function in the superconducting layers.
-For the sake of computing mutual inductance as in Section~\ref{section:examples:scanning-squid}, it is physically reasonable to artificially increase the vertical spacing between layers such that $\delta z\geq \delta r$ because we expect the magnetic field a vertical distance $\delta z$ away from the center of the field coil to fall off roughly as $\left(\delta z^2 + R^2_\mathrm{FC}\right)^{-3/2}$, where $R_\mathrm{FC}\approx 6\,\um\gg\delta z$.
-However, in situations where $\delta z$ is a critical dimension (in the sense that increasing it invalidates the physical model), one's only option is to decrease $\delta r$ by increasing the density of the mesh.
+As shown in Figure~\ref{fig:xlarge-dz-dr}, \SuperScreen significantly underestimates the mutual inductance between the field coil and pickup loop when $\delta z <\delta r$ because, in that case, the discretized version of Eq.~\ref{eq:hz-from-kernel} does not correctly compute the magnetic field due the stream functions of the superconducting layers.
+For the sake of computing mutual inductance as in Section~\ref{section:examples:scanning-squid}, it is physically reasonable to artificially increase the vertical spacing between layers such that $\delta z\geq \delta r$ because we expect the magnetic field at the pickup loop, a vertical distance $\delta z$ away from the center of the field coil, to fall off roughly as $\left(\delta z^2 + R^2_\mathrm{FC}\right)^{-3/2}$, where $R_\mathrm{FC}\approx 6\,\um\gg\delta z$.
+However, in situations where $\delta z$ is a critical dimension (in the sense that increasing it would invalidate the physical model), one's only option is to decrease $\delta r$ by increasing the density of the mesh.
 
 For this reason, mutli-layer structures with closely-spaced layers are the most challenging class of problem to solve.
-The iterative method used described in Section~\ref{section:model:multilayer} is memory-intensive for models with a large mesh (many vertices $p$ and triangles $t$, with typically $p\approx t / 2$) and/or many layers $L$.
-The average distance between vertices decreases slowly with increasing number of triangles, $\langle\delta r\rangle\sim t^{-1/2}$, whereas the size of the (dense floating-point) $p\times t$ matrix that represents the dipole kernel $Q_z(\vec{r},\vec{r}')$ in Eq.~\ref{eq:hz-from-kernel} increases roughly as $t^2$.
+The iterative method used described in Section~\ref{section:model:multilayer} is memory-intensive for models with a large mesh (many vertices $p$ and triangles $t$, with typically $p\approx t / 2$) and/or many layers $L$, because the average distance between vertices decreases slowly with increasing number of triangles, $\langle\delta r\rangle\sim t^{-1/2}$, whereas the size of the (dense floating-point) $p\times t$ matrix that represents the dipole kernel $Q_z(\vec{r},\vec{r}')$ in Eq.~\ref{eq:hz-from-kernel} increases roughly as $t^2$.
 The end result is that the memory footprint of kernel matrix scales roughly as $\langle\delta r\rangle^{-4}$, so decreasing the mean distance between vertices by a factor of 2 increases the memory required by a factor of 16.

### 2021-11-22 main.tex

@@
     &= \underbrace{\mathbf{h}_{z,\,\mathrm{applied}}}_\text{applied field}
-    + \underbrace{\mathbf{Q}(\mathbf{g}\cdot\mathbf{w})}_\text{screening field}\\
-    &=\mathbf{h}_{z,\,\mathrm{applied}}
-    + (\mathbf{Q}\cdot\mathbf{w}^T)\mathbf{g}\\
-    h_{z, i} &= h_{z,\,\mathrm{applied}, i} + \sum_j Q_{ij}g_jw_j,
+    + \underbrace{(\mathbf{Q}\cdot\mathbf{w}^T)\mathbf{g}}_\text{screening field}\\
+    % &=\mathbf{h}_{z,\,\mathrm{applied}}
+    % + (\mathbf{Q}\cdot\mathbf{w}^T)\mathbf{g}\\
+    h_{z, i} &= h_{z,\,\mathrm{applied}, i} + \sum_j Q_{ij}w_jg_j,
 \end{split}
 \end{align}
-where for clarity we show both the matrix version of Eq.~\ref{eq:field_from_kernel} (top two lines) and the equivalent discrete sum version (bottom line).
+where for clarity we show both the matrix version of Eq.~\ref{eq:field_from_kernel} (top line) and the equivalent discrete sum version (bottom line).
 
@@
 Regions where there are many polygon vertices will be meshed more densely than regions with few polygon vertices.
-If no \inline{optimesh} optimization is done, then every polygon vertex is guaranteed to be a mesh vertex.
+If no \inline{optimesh} optimization is performed, then every polygon vertex is guaranteed to be a mesh vertex.
 See Code Block~\ref{code:device} for a demonstration of the process of creating a \inline{Device}, and Figure~\ref{fig:ring-with-slit}(a) to view the resulting geometry and mesh.
@@
 There are three relevant layers of superconducting films: the base electrode (``BE"), which is furthest from the sample contains the field coil; the first wiring layer (``W1"), which contains the pickup loop and a shield covering the field coil leads; and the second wiring layer (``W2"), which is closest to the sample and contains a shield covering the pickup loop leads.
-There are two insulating layers: $I1$, which separates BE and W1, and $I2$, which separates W1 and W2.
+There are two insulating layers: I1, which separates BE and W1, and I2, which separates W1 and W2.
 Table~\ref{table:squid-layers}.
@@
 \centering
-\begin{tabular}{|l|l|l|}
+\begin{tabular}{|l|l|l|l|l|}
 \hline
-Layer name        & Thickness & Films located in layer \\ \hline
+Layer name & Material & Thickness & Vertical position, $z_0$ & Films located in layer \\ \hline
 \hline
-BE (bottom) & $d_\mathrm{BE} = 160\,\nm$            & Field coil, pickup loop shield      \\ \hline
-I1          & $d_\mathrm{I1} = 150\,\nm$            & ---                                 \\ \hline
-W1          & $d_\mathrm{W1}=100\,\nm$            & Pickup loop, field coil shield      \\ \hline
-I2          & $d_\mathrm{I2} = 130\,\nm$            & ---                                 \\ \hline
-W2 (top)    & $d_\mathrm{W2} = 200\,\nm$            & Pickup loop shield, modulation coil \\ \hline
+W2 & Nb & $d_\mathrm{W2} = 200\,\nm$ & $d_\mathrm{W2} / 2$ & Pickup loop shield, modulation coil \\ \hline
+I2 & SiO${}_2$ & $d_\mathrm{I2} = 130\,\nm$ & --- & --- \\ \hline
+W1 & Nb & $d_\mathrm{W1} = 100\,\nm$ & $d_\mathrm{W2} + d_\mathrm{I2} + d_\mathrm{W1} / 2$ & Pickup loop, field coil shield \\ \hline
+I1 & SiO${}_2$ & $d_\mathrm{I1} = 150\,\nm$ & --- & --- \\ \hline
+BE & Nb & $d_\mathrm{BE} = 160\,\nm$ & $d_\mathrm{W2} + d_\mathrm{I2} + d_\mathrm{W1} + d_\mathrm{I1} + d_\mathrm{BE} / 2$ & Field coil, pickup loop shield \\ \hline
 \end{tabular}
-\caption{Layer stackup for the SQUID susceptometers Section~\ref{section:examples:scanning-squid}. See Ref.~\cite{Kirtley2016-zz} for more details on the designed of the suscpetometers.}
+\caption{Layer stackup for the SQUID susceptometers Section~\ref{section:examples:scanning-squid}.
+W2 is located at the surface of the chip (deposited last, closest to the sample) and BE deepest below the chip's surface (deposited first).
+See Ref.~\cite{Kirtley2016-zz} for more details on the designed of the suscpetometers.}
 \label{table:squid-layers}
@@
 % \end{figure}
+
+\section{Spatially inhomogeneous $\Lambda$}
+\label{appendix:inhomogeneous}
+
+As mentioned in Section~\ref{section:overview:device}, the effective penetration depth $\Lambda$ of each layer can be specified as a numeric constant or as a \inline{superscreen.Parameter} that computes $\Lambda(x, y)$, the effective penetration depth as a function of position.
+As a (somewhat contrived) example, here we update the model of a ring with a slit from Code Block~\ref{code:device} and Figure~\ref{fig:ring-with-slit} such that the ring's penetration depth $\Lambda(x, y)$ increases linearly as a function of the angle that the vector $\vec{r} = (x, y)$ makes with the $-y$ axis (along which the slit lies).
+
+\begin{code}
+\begin{minted}[fontsize=\small]{python}
+def linear_vs_angle(
+    x: np.ndarray, y: np.ndarray, *, min_val: float, max_val: float
+) -> np.ndarray:
+    # Rotate the input coordinates so that theta = 0
+    # corresponds to the slit position (along the -y axis).
+    x, y = sc.geometry.rotate(
+        np.stack(np.atleast_1d(x, y), axis=1), np.degrees(-np.pi / 2)
+    ).T
+    # Calculate the angular position of each mesh vertex.
+    angles = np.arctan2(y, x) + np.pi  # range: [0, 2 * pi]
+    # Set Lambda to increase linearly from min_val to max_val
+    # as a function of angular position.
+    Lambdas = angles / (2 * np.pi) * (max_val- min_val) + min_val
+    return Lambdas
+
+# Define the Parameter and assign it as the Lambda of the superconducting layer.
+Lambda = sc.Parameter(linear_vs_angle, min_val=0.1, max_val=1.0)
+device.layers["base"].Lambda = Lambda
+# Everything below is identical to Code Block 1:
+# Calculate the device's response to a uniform applied field.
+applied_field = sc.sources.ConstantField(10)
+solution = sc.solve(device, applied_field=applied_field, field_units="uT")[-1]
+# Visualize the solution.
+# Plot the magnetic field evaluated at each layer in the Device.
+solution.plot_fields()
+# Plot the current density evaluated at each layer in the Device.
+solution.plot_currents()
+# Plot the field evaluated at any points in space.
+solution.plot_field_at_positions(device.points, zs=0.5)
+\end{minted}
+\label{code:inhomogeneous}
+\captionof{listing}{Simulating an inhomogeneous superconducting device.
+Here we modify the superconducting ring with a slit (Code Block~\ref{code:device} to have an effective penetration depth $\Lambda(x, y)$, which increases linearly from $0.1\,\um$ to $1\,\um$ as a function of the angle between the point $(x, y)$ and the $-y$ axis.}
+\end{code}
 
@@
 One can force the kernel matrices to be cached to disk if they would otherwise occupy too large a fraction of the available system memory using the \inline{cache_kernel_memory_cutoff} argument, but this comes at a significant performance cost.
+In many cases, one can use lower-precision floating point numbers (e.g.
+using 32-bit single-precision floats instead of the default 64-bit double-precision floats by setting \inline{device.solve_dtype = "float32"}) to reduce memory requirements without significantly impacting solution accuracy.
 

### 2021-11-22 main.tex

@@
 
+\begin{figure*}[h]
+    \centering
+    \includegraphics[width=\textwidth]{examples/images/ring_with_slit_inhomogeneous.pdf}
+    \caption{The output of Code Block~\ref{code:inhomogeneous}: Screening of a uniform applied field of $10\,\mu\mathrm{T}$ by a ring with a slit in a superconducting film with inhomogeneous effective penetration depth $\Lambda(x, y)$}
+    \label{fig:inhomogeneous}
+\end{figure*}
+
 \section{Numerical considerations}

### 2021-11-22 main.tex
Updates from Overleaf

--- 2021-11-22 main.tex
@@
 is the thickness of the film, the second London equation reduces to
-
 \begin{equation}
@@
 of a scalar potential $g(x, y)$, called the stream function:
-
 \begin{equation}
@@
 We can rewrite Eq.~\ref{eq:london}, which gives the magnetic field inside of a 2D film, in terms of $g$:
-
 \begin{align}
@@
         &= -\Lambda\left[\nabla(\nabla\cdot(g\hat{z}))-\nabla^2(g\hat{z})\right]\\
-        &=\Lambda\nabla^2g(x,y)\hat{z}
+        &=\Lambda\nabla^2g(x,y)\hat{z},
     \end{split}
@@
 From Ampere's Law, the three components of the magnetic field $\vec{H}(\vec{r})$ at position $\vec{r}=(x, y, z)$ due to a sheet of current lying in the $x-y$ plane (at vertical position $z'$) with stream function $g(x', y')$ are given by:
-
 \begin{align}
@@
         H_z(\vec{r}) &= H_{z,\,\mathrm{applied}}(\vec{r})
-        + \int_F Q_z(\vec{r},\vec{r}')g(x', y')\,\mathrm{d}^2r'  
+        + \int_F Q_z(\vec{r},\vec{r}')g(x', y')\,\mathrm{d}^2r'.  
     \end{split}
@@
 $F$ is the film area (with $g = 0$ outside of the film), and $Q_x(\vec{r},\vec{r}')$, $Q_y(\vec{r},\vec{r}')$, and $Q_z(\vec{r},\vec{r}')$ are dipole kernel functions which give the respective component of the magnetic field at position $\vec{r}=(x, y, z)$ due to a dipole of unit strength at position $\vec{r}'=(x', y', z')$:
-
 \begin{align}
@@
 Comparing Eq.~\ref{eq:london_stream} and Eq.~\ref{eq:field_from_kernel}, we have in the plane of the film:
-
 \begin{align}
@@
 From Eq.~\ref{eq:integral_equation}, we arrive at an integral equation relating the stream function $g$ for points inside the superconductor to the applied field $H_{z,\,\mathrm{applied}}$:
-
 \begin{align}
@@
 The (hypothetical) applied field that would cause such a circulating current is given by Eq.~\ref{eq:applied_to_stream} if we set $g=I_{\mathrm{circ},\,k}$ for all points lying inside hole $k$:
-
 \begin{align}
@@
 In this case, we modify the left-hand side of Eq.~\ref{eq:applied_to_stream} as follows:
-
 \begin{align}
@@
 The fluxoid $\Phi^f_S$ for a 2D region $S$ with 1D boundary $\partial S$ is given by the sum of flux through $S$ and the line integral of sheet current around $\partial S$~\cite{Brandt2005-wj,Clem2005-ye,Tinkham2004-zn}:
-
 \begin{equation}
@@
 This path-independence of the fluxoid follows from the static London equation (Eq.~\ref{eq:london}) on which the present model is based.
-Fluxoid quantization---the requirement that the fluxoid $\Phi^f_S=n\Phi_0$ where $n$ is an integer and $\Phi_0=h/2e$ is the magnetic flux quantum---is not automatically enforced by Eq.~\ref{eq:london}, however it can be included as an external constraint.
-% However, because Eq.~\ref{eq:london} does not relate the supercurrent density $\vec{J}$ to the phase of a complex order parameter as in Ginzburg-Landau theory, or invoke the semi-classical Bohr-Sommerfeld quantization rule as London did~\cite{Tinkham2004-zn}, within this model the fluxoid is not constrained to be an integer multiple of the flux quantum $\Phi_0=h/2e$.
+Fluxoid quantization---the requirement that the fluxoid $\Phi^f_S=n\Phi_0$ where $n$ is an integer and $\Phi_0=h/2e$ is the magnetic flux quantum---is not automatically enforced by Eq.~\ref{eq:london} for multiply-connected films, however it can be included as an external constraint.
 
@@
 The presence of vortices trapped in a film at positions $\vec{r}_v$ modifies Eq.~\ref{eq:Heff_sub} as follows:
-
 \begin{align}
@@
 The discrete version of Eq.~\ref{eq:field_from_kernel} is
-
 \begin{align}
@@
 where $\mathcal{N}(i)$ is the set of triangles $t$ adjacent to vertex $i$. The kernel matrix $\mathbf{Q}$ is given by
-
 \begin{equation}
@@
 The diagonal terms involving the $n\times 1$ vector $\mathbf{C}$ are meant to work around the fact that $q_{ii}$ diverge (see Ref.~\cite{Brandt2005-wj} for more details), and $\mathbf{C}$ is given by
-
 \begin{equation}
@@
 The matrix version of Eq.~\ref{eq:Heff_sub} is
-
 \begin{equation}
@@
 Defining $\mathbf{K} = \left(\mathbf{Q}\cdot\mathbf{w}^T-\mathbf{\nabla}^2\cdot\mathbf{\Lambda}^T\right)^{-1}$, we have
-
 \begin{equation}
@@
 c) The $z$-component of the magnetic field $\mu_0H_z$ evaluated at the plane of the ring, generated with \inline{Solution.plot_fields()}.
-d) The $z$-component of the magnetic field evaluated $z=0.5\,\um$ above the ring (generated using \inline{Solution.plot_field_at_positions()}.}
+d) The $z$-component of the magnetic field evaluated $z=0.5\,\um$ above the ring (generated using \inline{Solution.plot_field_at_positions()}).}
     \label{fig:ring-with-slit}
@@
 As mentioned in Section~\ref{section:overview:device}, the effective penetration depth $\Lambda$ of each layer can be specified as a numeric constant or as a \inline{superscreen.Parameter} that computes $\Lambda(x, y)$, the effective penetration depth as a function of position.
-As a (somewhat contrived) example, here we update the model of a ring with a slit from Code Block~\ref{code:device} and Figure~\ref{fig:ring-with-slit} such that the ring's penetration depth $\Lambda(x, y)$ increases linearly as a function of the angle that the vector $\vec{r} = (x, y)$ makes with the $-y$ axis (along which the slit lies).
+As a (somewhat contrived) example, Code Block~\ref{code:inhomogeneous} demonstrates how to modify the model of a ring with a slit from Code Block~\ref{code:device} and Figure~\ref{fig:ring-with-slit} such that the ring's penetration depth $\Lambda(x, y)$ increases linearly as a function of the angle between the vector $\vec{r} = (x, y)$ and the $-y$ axis (along which the slit lies).
+The resulting current and field distributions are shown in Figure~\ref{fig:inhomogeneous}.
+Note that $\Lambda(x, y)$ must vary slowly on the scale of the spacing between mesh vertices in order for results to be reliable.
 
@@
 \end{minted}
+\captionof{listing}{Simulating an inhomogeneous superconducting device.
+Here we modify the superconducting ring with a slit (Code Block~\ref{code:device} to have an effective penetration depth $\Lambda(x, y)$, which increases linearly from $0.1\,\um$ to $1\,\um$ as a function of the angle between the vector $\vec{r}=(x, y)$ and the $-y$ axis.
+See Figure~\ref{fig:inhomogeneous} for the resulting current and field distributions.}
 \label{code:inhomogeneous}
-\captionof{listing}{Simulating an inhomogeneous superconducting device.
-Here we modify the superconducting ring with a slit (Code Block~\ref{code:device} to have an effective penetration depth $\Lambda(x, y)$, which increases linearly from $0.1\,\um$ to $1\,\um$ as a function of the angle between the point $(x, y)$ and the $-y$ axis.}
 \end{code}
+
+\begin{figure*}[h]
+    \centering
+    \includegraphics[width=\textwidth]{examples/images/ring_with_slit_inhomogeneous.pdf}
+    \caption{The output of Code Block~\ref{code:inhomogeneous}: Meissner screening of a uniform applied field of $10\,\mu\mathrm{T}$ by a ring with a slit in a superconducting film with inhomogeneous effective penetration depth $\Lambda(x, y)$.
+a) The inhomogeneous effective penetration depth $\Lambda(x, y)$, with the ring's outline overlaid in orange.
+b) The current density $\vec{J}$ in the ring, generated with \inline{Solution.plot_currents()}.
+c) The $z$-component of the magnetic field $\mu_0H_z$ evaluated at the plane of the ring, generated with \inline{Solution.plot_fields()}.
+d) The $z$-component of the magnetic field evaluated $z=0.5\,\um$ above the ring (generated using \inline{Solution.plot_field_at_positions()}).}
+    \label{fig:inhomogeneous}
+\end{figure*}
 

### 2021-11-23 main.tex

@@
 The 2D Fourier transform $\tilde{H}_z(\vec{k}, z)$ of the out-of-plane component of the magnetic field $H_z(\vec{r}, z)$ from a Pearl vortex located at the origin $x=y=z=0$ is given by
-
 \begin{equation}
@@
 The real-space magnetic field distribution near a Pearl vortex can be calculated numerically by taking the inverse Fourier transform of Eq.~\ref{eq:pearl}: $H_z(\vec{r}, z)=\mathcal{F}^{-1}\{\tilde{H}_z(\vec{k}, z)\}$.
-The field distributions generated by \SuperScreen in the presence of vortices as described in Sections~\ref{section:model:vortices} and~\ref{section:implementation} agree to within a few percent with the distributions obtained using this Fourier transform method, as demonstrated in Code Block~\ref{code:pearl-vortex} and Figure~\ref{fig:pearl}(c-e).
 
@@
 A \inline{Vortex} object specifies the $x,y$ position for the vortex core, the name of the superconducting layer in which the vortex is pinned, and the number of flux quanta $\Phi_0$ contained in the vortex (which is 1 by default).
+The field distributions generated by \SuperScreen in the presence of vortices as described in Sections~\ref{section:model:vortices} and~\ref{section:implementation} agree to within a few percent with the distributions obtained using this Fourier transform method, as demonstrated in Code Block~\ref{code:pearl-vortex} and Figure~\ref{fig:pearl}(c-e).
 See Ref.~\cite{Brandt2005-wj} for a method to compute the self-energy and interaction energies of vortices in thin films.
@@
 
-\begin{figure*}[h]
+\begin{figure*}[h!]
     \centering
@@
 As $\Lambda$ increases, so to does the supercurrent contribution to the fluxoid.
-(f) Error in the total simulated fluxoid relative to $\Phi_0$: $(\Phi_S^f(\Lambda) - \Phi_0) / \Phi_0$.}
+(f) Error in the total simulated fluxoid relative to $\Phi_0$: error = $(\Phi_S^f(\Lambda) - \Phi_0) / \Phi_0$.}
     \label{fig:pearl}
@@
 With increasing $\Lambda$, the ``supercurrent part'' accounts for an increasing fraction of the total fluxoid.
-% See \ref{appendix:fluxoid} for a demonstration of the fluxoid properties listed in Section~\ref{section:model:fluxoid}.
 
@@
 
-\subsection{Self-inductance and mutual inductance}
-\label{section:examples:mutual-inductance}
+\subsection{Application: scanning SQUID susceptometry}
+\label{section:examples:scanning-squid}
+
+In scanning superconducting quantum interference device (SQUID) susceptometry\cite{Gardner2001-gr, Huber2008-il, Kirtley_Kalisky_2012}, the diamagnetic susceptibility of a superconducting sample is measured by bringing the sample close to a pair of superconducting loops.
+The first loop, called the ``pickup loop" (PL) is attached to a SQUID circuit that sensitively measures the magnetic flux threading the loop.
+The second loop, called the ``field coil" (FC), carries a known current and applies a known magnetic field to both the pickup loop and the sample.
+The superconducting sample screens the magnetic field from the field coil, modifying the amount of flux threading the pickup loop.
+Thus the change in mutual inductance $M_\mathrm{PL-FC}$ between the field coil and pickup loop in the presence of a sample provides a measure of the sample's magnetic susceptibility.
+For superconducting samples, this diamagnetic response is a measure of the sample's penetration depth and therefore its superfluid density.
 
@@
 If the penetration depth of the film containing hole $i$ is $\Lambda = 0$, then no field penetrates the film and the fluxoid $\Phi^f_{S_i}$ is equal to $\Phi_i$, the flux through hole $i$.
-
-For a circular ring with inner radius $a$, outer radius $b>a$, and penetration depth $\Lambda=0$, Clem~\cite{Babaei_Brojeny2003-la} found that the self-inductance approaches $L=2\mu_0 a$ in the ``small hole'' limit $\tilde{a}=a/b\ll 1$.
-Clem and Brandt~\cite{Brandt2004-ew} and Khapaev~\cite{Khapaev1997-kw} calculated the self-inductance of circular and square rings as a function of the ratio of inner and outer diameters.
-
-\subsection{Application: scanning SQUID microscopy}
-\label{section:examples:scanning-squid}
-
-In scanning superconducting quantum interference device (SQUID) susceptometry, the diamagnetic susceptibility of a superconducting sample is measured by bringing the sample close to a pair of superconducting loops.
-The first loop, called the ``pickup loop" is attached to a SQUID circuit that sensitively measures the magnetic flux threading the loop.
-The second loop, called the ``field coil," carries a known current and applies a known magnetic field to both the pickup loop and the sample.
-The superconducting sample screens the magnetic field from the field coil, modifying the amount of flux threading the pickup loop.
-Thus the mutual inductance between the field coil and pickup loop provides a measure of the sample's magnetic susceptibility.
-For superconducting samples, this diamagnetic response is a measure of the sample's penetration depth and therefore its superfluid density.
-
-Analysis developed to interpret the results of scanning SQUID susceptometry measurements makes several simplifying assumptions that are not always satisfied: 1) the sample's effective penetration depth $\Lambda$ (or Pearl length $2\Lambda$) is spatially homogeneous, 2) the sample is much larger than the field coil, and 3) the field coil and pickup loop can be approximated as one-dimensional coaxial, coplanar circular loops~\cite{Kirtley_Kalisky_2012}.
-
-% \begin{figure}[!h]
-% \centering
-% \begin{subfigure}{.35\textwidth}
-%   \centering
-%   \includegraphics[width=\linewidth]{examples/images/squid_susceptometry/squid_with_sample_mesh.png}
-%   \label{fig:squid_mesh}
-%   \caption{}
-% \end{subfigure}%
-% \hspace{10pt}
-% \begin{subfigure}{.5\textwidth}
-%   \centering
-%   \includegraphics[width=\linewidth]{examples/images/squid_susceptometry/squid_with_sample_M0_convergence.png}
-%   \label{fig:squid_convergence}
-%   \caption{}
-%   \caption{Fractional change in flux though all polygons vs.
-solver iteration with a current of $1\,\mathrm{mA}$ flowing in the field coil (\inline{fc}).
-The mutual inductance $M_0$ is given by the flux through the pickup loop (\inline{pl_hull}) divided by the field coil current.}
-% \end{subfigure}%
-% \caption{(a): Device polygons and mesh for the SQUID susceptometer model.
-(b) Fractional change in flux though all polygons vs.
-solver iteration with a current of $1\,\mathrm{mA}$ flowing in the field coil (\inline{fc}).
-The mutual inductance $M_0$ is given by the flux through the pickup loop (\inline{pl_hull}) divided by the field coil current.}
-% \label{fig:susceptometry}
-% \end{figure}
+For a device with $N_h$ holes, the $N_h\times N_h$ mutual inductance matrix $\mathbf{M}$ can be computed using the $\inline{Device.mutual_inductance_matrix()}$ method.
 
@@
 In addition to the field coil and pickup loop, there are superconducting shields that limit the amount of magnetic flux that can penetrate the leads connecting the loops to the rest of the circuit (the rest of the circuit is not modeled).
-There are three relevant layers of superconducting films: the base electrode (``BE"), which is furthest from the sample contains the field coil; the first wiring layer (``W1"), which contains the pickup loop and a shield covering the field coil leads; and the second wiring layer (``W2"), which is closest to the sample and contains a shield covering the pickup loop leads.
+There are three relevant layers of superconducting films: the base electrode (BE), which is furthest from the sample contains the field coil; the first wiring layer (W1), which contains the pickup loop and a shield covering the field coil leads; and the second wiring layer (W2), which is closest to the sample and contains a shield covering the pickup loop leads.
 There are two insulating layers: I1, which separates BE and W1, and I2, which separates W1 and W2.
-Table~\ref{table:squid-layers}.
-
-\begin{table*}[]
+Table~\ref{table:squid-layers} shows the thickness $d$ of each layer in the real devices, as well as the vertical position of the 2D films used to model each layer.
+For the superconducting layers, which are made of Nb, we take the London penetration depth to be $\lambda = 80\,\nm$.
+It is important to note that because $\lambda < d$ for all three layers, the susceptometers are not in the 2D limit in which the model described in Section~\ref{section:model} is technically valid.
+Nevertheless, as shown in Figure~\ref{fig:squid-mutuals}, the field coil - pickup loop mutual inductances, $M_\mathrm{sim}$, computed by \SuperScreen lie within the range of mutual inductances measured in real devices, $M_\mathrm{exp}$ (taken from Ref.~\cite{Kirtley2016-zz} Table 1), for all four sizes of susceptometer.\footnote{The mutual inductance values are shown in units of $\Phi_0 / \mathrm{A}$, where $1\,\Phi_0 / \mathrm{A}\approx2.068\times10^{-3}\,\mathrm{pH}$.} This suggests that variation in current density along the thickness of each film (along the $z$-axis) is not critical in determining the mutual inductance.
+The convergence of $M_\mathrm{PL-FC}$ as a function of solver iteration (see Section~\ref{section:model:multilayer}) is shown in Figure~\ref{fig:squid-mutuals}(c).
+
+\begin{table*}
 \centering
@@
 \end{tabular}
-\caption{Layer stackup for the SQUID susceptometers Section~\ref{section:examples:scanning-squid}.
+\caption{Layer stackup for the SQUID susceptometers discussed in Section~\ref{section:examples:scanning-squid}.
 W2 is located at the surface of the chip (deposited last, closest to the sample) and BE deepest below the chip's surface (deposited first).
-See Ref.~\cite{Kirtley2016-zz} for more details on the designed of the suscpetometers.}
+See Refs.~\cite{Kirtley2016-zz, Kirtley2016-gt} for more details on the designed of the suscpetometers.}
 \label{table:squid-layers}
@@
     \includegraphics[width=\textwidth]{examples/images/squid-mutuals.png}
-    \caption{Calculating SQUID susceptometer mutual inductance, defined as the fluxoid induced in the SQUID pickup loop per unit current flowing in the field coil: $M=\Phi_\mathrm{PL} / I_\mathrm{FC}$.
+    \caption{Calculating SQUID susceptometer mutual inductance, defined as the fluxoid induced in the SQUID pickup loop per unit current flowing in the field coil: $M_\mathrm{PL-FC}=\Phi^f_\mathrm{PL} / I_\mathrm{FC}$.
 Top row (a): Schematics of \SuperScreen models for the field coil and pickup loop region of four sizes of scanning SQUID susceptometer (generated using \inline{Device.draw()}) with pickup loop inner radii ranging from $0.1\,\um$ (``Small'') to $3\,\um$ (``X-Large'').
@@
 
-To model a SQUID susceptometry measurement, we first calculate $M_0$, the mutual inductance between the field coil and pickup loop in the absence of the sample.
-This can be done by temporarily setting the sample layer effective penetration depth to a very large value such that it essentially does not screen the field from the field coil (in this case, we set $\Lambda = 10^5\,\um$).
-We then model the field from a known current flowing in the field coil following Section~\ref{section:model:holes} and self-consistently calculate the response of both the sample and the other superconducting layers of the SQUID sensor following Section~\ref{section:model:multilayer}.
-To ensure that the 2D current distribution in the field coil is approximately uniform (as we would expect for a real applied current), we set the field coil layer effective penetration depth to be greater than the width of the field coil conductor.
-
-Once $M_0$ is known, we can ``turn on" the sample's diamagnetic response by setting its effective penetration depth $\Lambda$ to the desired value and compute $M(z, \Lambda)$ for a given vertical distance $z$ between the sample and the SQUID as described in the previous paragraph.
-The SQUID susceptibility signal is then $M(z, \Lambda) - M_0$, the change in mutual inductance between the field coil and pickup loop due to the presence of the sample (usually given in units of $\Phi_0/\mathrm{A}$, where $\Phi_0$ is the superconducting flux quantum).
-The susceptibility can also be normalized to the bare mutual inductance $M_0$, giving a dimensionless susceptibility $\chi(z, \Lambda)=[M(z, \Lambda) - M_0] / M_0$.
+Having established the value of the field coil - pickup loop mutual inductance $M_\mathrm{PL-FC}$ in the absence of a sample, we can simulate a scanning SQUID susceptometry measurement by calculating $M_\mathrm{PL-FC}$ in the presence of a superconducting sample as a function of the relative position of the pickup loop and the sample.
+For example, in Figure XX, we simulate a SQUID susceptometry image of of a ``Large'' susceptometer (the sample) measured with a ``Medium'' suceptometer (the sensor).
+Given a \inline{Device} representing the sensor and a \inline{Device} representing the sample, this calculation is performed in three steps:
+\begin{enumerate}
+    \item{Simulate the sensor with some known current $I_\mathrm{FC}$ circulating in the field coil to get \inline{field_coil_solution}.}
+    \item{For a given relative position $(x_s, y_s)$ between the sensor and sample, simulate the sample with an applied field given by \inline{field_coil_solution.field_at_position()} to get \inline{sample_solution}.}
+    \item{Simulate the sensor again, this time with the applied field given by \inline{sample_solution.field_at_position()}, and evaluate the fluxoid $\Phi^f_\mathrm{PL}$ for the hole representing the sensor's pickup loop, and calculate the mutual inductance: $M_\mathrm{PL-FC}(x_s, y_s)=\Phi^f_\mathrm{PL} / I_\mathrm{FC}$.}
+\end{enumerate}
+These three steps are repeated for every desired $(x_s, y_s)$ to build up a susceptometry image.
+Note that in principle it is possible to combine the sensor and sample into a single \inline{Device} with 6 superconducting layers, however this is impractical because it would require generating a new mesh for each $(x_s, y_s)$ and, as discussed in detail in \ref{appendix:numerics}, the problem scales unfavorably with the number of layers in a device and with the total lateral extent of a device.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\linewidth]{}
+    \caption{Caption}
+    \label{fig:my_label}
+\end{figure}
+
+\subsection{Application: scanning SQUID magnetometry}
+\label{section:examples:magnetometry}
 
@@
 currents flowing in one terminal of a device and out another terminal.
-This means that inductance calculations are limited to structures with holes, in which all applied currents are circulating currents associated with trapped flux (see Sections~\ref{section:model:holes} and~\ref{section:examples:mutual-inductance}).
+This means that inductance calculations are limited to structures with holes, in which all applied currents are circulating currents associated with trapped flux (see Sections~\ref{section:model:holes} and~\ref{section:examples:scanning-squid}).
 Terminal currents can, however, be included in stream function-base models by setting appropriate boundary conditions~\cite{Khapaev1997-kw,Khapaev2001-xq,Khapaev2001-pw,Muller2021-ci}.
@@
 \label{appendix:inhomogeneous}
-
-As mentioned in Section~\ref{section:overview:device}, the effective penetration depth $\Lambda$ of each layer can be specified as a numeric constant or as a \inline{superscreen.Parameter} that computes $\Lambda(x, y)$, the effective penetration depth as a function of position.
-As a (somewhat contrived) example, Code Block~\ref{code:inhomogeneous} demonstrates how to modify the model of a ring with a slit from Code Block~\ref{code:device} and Figure~\ref{fig:ring-with-slit} such that the ring's penetration depth $\Lambda(x, y)$ increases linearly as a function of the angle between the vector $\vec{r} = (x, y)$ and the $-y$ axis (along which the slit lies).
-The resulting current and field distributions are shown in Figure~\ref{fig:inhomogeneous}.
-Note that $\Lambda(x, y)$ must vary slowly on the scale of the spacing between mesh vertices in order for results to be reliable.
 
@@
 
-\begin{figure*}[h]
+As mentioned in Section~\ref{section:overview:device}, the effective penetration depth $\Lambda$ of each layer can be specified as a numeric constant or as a \inline{superscreen.Parameter} that computes $\Lambda(x, y)$, the effective penetration depth as a function of position.
+As a (somewhat contrived) example, Code Block~\ref{code:inhomogeneous} demonstrates how to modify the model of a ring with a slit from Code Block~\ref{code:device} and Figure~\ref{fig:ring-with-slit} such that the ring's penetration depth $\Lambda(x, y)$ increases linearly as a function of the angle between the vector $\vec{r} = (x, y)$ and the $-y$ axis (along which the slit lies).
+The resulting current and field distributions are shown in Figure~\ref{fig:inhomogeneous}.
+Note that $\Lambda(x, y)$ must vary slowly on the scale of the spacing between mesh vertices in order for results to be reliable.
+
+\begin{figure*}
     \centering

### 2021-11-23 main.tex

@@
     \centering
-    \includegraphics[width=\linewidth]{}
-    \caption{Caption}
-    \label{fig:my_label}
+    \includegraphics[width=\linewidth]{examples/images/squid-susc-simulation.pdf}
+    \caption{Simulation of a scanning SQUID susceptometry measurement.
+a) Geometry of the \inline{Device} representing the ``sensor'' SQUID.
+b) Geometry of the \inline{Device} representing the ``sample'' SQUID.
+c) Susceptibility of the sample SQUID measured at a temperature of 4.0 K.
+d) Simulated susceptibility assuming a vertical distance of 50 nm between the surfaces of the two SQUID chips.
+The pickup loop of the sample, which in reality is connected to a SQUID circuit that has a non-linear magnteic response, is modeled as a continuous superconducting loop in the $n=0$ fluxoid state (i.e.
+Meissner state).
+The scale bar in (a) applies to all four panels.}
+    \label{fig:squid-susc}
 \end{figure}

### 2021-11-23 main.tex

--- 2021-11-23 main.tex
@@
 \begin{abstract}
-Quantitative understanding of the spatial distribution of magnetic fields and screening currents in two-dimensional (2D) superconductors and mesoscopic thin film superconducting devices is critical to interpreting the results of magnetic measurements of such systems.
+Quantitative understanding of the spatial distribution of magnetic fields and Meissner screening currents in two-dimensional (2D) superconductors and mesoscopic thin film superconducting devices is critical to interpreting the results of magnetic measurements of such systems.
 Here, we introduce \SuperScreen, an open-source Python package for simulating the magnetic response of 2D superconductors to applied time-independent magnetic fields.
@@
 However, few software tools for this task exist and those that are available are closed-source, are written in low-level compiled languages like C, and/or require the use of specialized file formats or separate computer aided design (CAD) software for defining device geometries and model configurations.\footnote{A brief summary of existing tools can be found in \ref{appendix:other-tools}, and a more thorough overview in Ref.~\cite{Gaj1999-ls}.} Most of these tools are intended for use in the design of superconducting integrated circuits for single flux quantum (SFQ) logic and are primarily used for inductance extraction~\cite{Gaj1999-ls}.
-In contrast, \SuperScreen is an open-source, user-friendly, portable research tool designed to lower the barrier to entry to quantitative modeling of 2D superconductors, and to help interpret and inform measurements of superconducting thin films and devices.
+\SuperScreen is an open-source, user-friendly, portable research tool designed to lower the barrier to entry to quantitative modeling of 2D superconductors, and to help interpret and inform measurements of superconducting thin films and devices.
 
@@
 In Section~\ref{section:overview}, we provide an overview of the structure of the \SuperScreen package and discuss some important development details.
-In Section~\ref{section:examples}, we demonstrate how to perform several types of simulations using \SuperScreen and compare the results to previous numerical/analytical solutions and experimental results.
+In Section~\ref{section:examples}, we demonstrate how to perform several types of simulations using \SuperScreen and compare the results to analytical solutions and experimental results.
 Finally, in Section~\ref{section:conlusion}, we conclude by discussing applications, limitations, and possible extensions of the package.
@@
 
-\subsection{Parameters}
-\label{section:overview:parameter}
-
-A \inline{superscreen.Parameter} is a wrapper around a Python function that computes a scalar value as a function of position coordinates ($x$, $y$, and optionally $z$) based on some set of keyword arguments.
+% \subsection{Parameters}
+% \label{section:overview:parameter}
+
+% A \inline{superscreen.Parameter} is a wrapper around a Python function that computes a scalar value as a function of position coordinates ($x$, $y$, and optionally $z$) based on some set of keyword arguments.
 Addition, subtraction, multiplication, division, and exponentiation between \inline{Parameters}, other \inline{Parameters}, and Python scalars (\inline{int} and \inline{float}) are supported.
-\inline{Parameters} can be used to conveniently define applied magnetic fields and penetration depths that depend on position, and make it possible to serialize wrapped Python functions for storage to disk or inter-process communication.
+\inline{Parameters} can be used to conveniently define applied magnetic fields and penetration depths that depend on position (see \ref{appendix:inhomogeneous}).
 
@@
 A \inline{Device} is made up of one or more superconducting layers, each represented by an instance of  \inline{superscreen.Layer}.
-Each layer sits in a specified plane parallel to the $x-y$ plane and has its own effective penetration depth $\Lambda$, which can either be a constant or a \inline{superscreen.Parameter} that defines $\Lambda(x, y)$, the effective penetration depth as a function of position.
+Each layer sits in a specified plane parallel to the $x-y$ plane and has its own effective penetration depth $\Lambda$, which can either be a constant or a \inline{superscreen.Parameter} that defines $\Lambda(x, y)$, the effective penetration depth as a function of position (see \ref{appendix:inhomogeneous}).
 Alternatively, the effective penetration depth $\Lambda$ can be defined in terms of a layer's London penetration depth $\lambda$ and its thickness $d$: $\Lambda=\lambda^2/d$, in which case the London penetration depth can be either a constant or a \inline{superscreen.Parameter}.
@@
 The \inline{superscreen.geometry} module provides functions for generating the underlying polygon vertices for simple shapes (ellipses and rectangles), which can be combined as described above to create more complicated geometries.
-
 \begin{code}
@@
 )
-device.make_mesh(min_triangles=8_000, optimesh_steps=None)
+device.make_mesh(min_triangles=8000, optimesh_steps=None)
 device.plot(mesh=True)
@@
 In practice, the more \inline{optimesh} steps are performed, the more uniform in size and spatial density the triangles in the mesh become.
-% , where quality is defined as twice the ratio of the incircle radius to the circumcircle radius (quality $\leq1$, with equality for equilateral triangles).
 The local density of triangles in the mesh is determined by the density of vertices in the device's polygons and the total number of triangles.
@@
     \caption{The output of Code Block~\ref{code:device}: Meissner screening of a uniform $10\,\mu\mathrm{T}$ out-of-plane field by a ring with inner diameter $1\,\um$, outer diameter $3\,\um$, and effective penetration depth $\Lambda=1\,\um$, interrupted by a slit of width $0.25\,\um$.
-a) Plot of the boundary of the ring (blue), circular bounding box (orange), and the computational mesh (gray), generated with \inline{Device.plot()}.
-b) The current density $\vec{J}$ in the ring, generated with \inline{Solution.plot_currents()}.
-c) The $z$-component of the magnetic field $\mu_0H_z$ evaluated at the plane of the ring, generated with \inline{Solution.plot_fields()}.
-d) The $z$-component of the magnetic field evaluated $z=0.5\,\um$ above the ring (generated using \inline{Solution.plot_field_at_positions()}).}
+(a) Plot of the boundary of the ring (blue), circular bounding box (orange), and the computational mesh (gray), generated with \inline{Device.plot()}.
+(b) The current density $\vec{J}$ in the ring, generated with \inline{Solution.plot_currents()}.
+(c) The $z$-component of the magnetic field $\mu_0H_z$ evaluated at the plane of the ring, generated with \inline{Solution.plot_fields()}.
+(d) The $z$-component of the magnetic field evaluated $z=0.5\,\um$ above the ring (generated using \inline{Solution.plot_field_at_positions()}).}
     \label{fig:ring-with-slit}
@@
     \item{
-    \inline{Solution.interp_current_density()}: Evaluates the current density (sheet current) $\vec{J}(x, y)$ in each layer at arbitrary $(x, y)$ coordinates via interpolation.
-    }
-    \item{
-    \inline{Solution.polygon_flux()}: Calculates the total flux through each polygon in the device (films, holes, and abstract regions).
+    \inline{Solution.interp_current_density()}: Evaluates the 2D current density $\vec{J}(x, y)$ in each layer at arbitrary $(x, y)$ coordinates via interpolation.
+    }
+    \item{
+    \inline{Solution.polygon_flux()}: Calculates the total flux through each polygon in the device.
     }
@@
 A \inline{list} of \inline{Solutions}, such as that returned by \inline{superscreen.solve()} can be saved/loaded all at once using \inline{save_solutions()} and \inline{load_solutions()}.
-
-% \section{Example application: Scanning SQUID magnetometry}
-% \label{section:application}
-% In scanning superconducting quantum interference device (SQUID) susceptometry, the diamagnetic susceptibility of a superconducting sample is measured by bringing the sample close to a pair of superconducting loops.
-The first loop, called the ``pickup loop" is attached to a SQUID circuit that sensitively measures the magnetic flux threading the loop.
-The second loop, called the ``field coil," carries a known current and applies a known magnetic field to both the pickup loop and the sample.
-The superconducting sample screens the magnetic field from the field coil, modifying the amount of flux threading the pickup loop.
-Thus the mutual inductance between the field coil and pickup loop provides a measure of the sample's diamagnetic susceptibility, which is in turn a measure of the sample's penetration depth.
-
-% Analysis developed to interpret the results of scanning SQUID susceptometry measurements makes several simplifying assumptions that are not always satisfied: 1) the sample's effective penetration depth $\Lambda$ (or Pearl length $2\Lambda$) is spatially homogeneous, 2) the sample is much larger than the field coil, and 3) the field coil and pickup loop can be approximated as one-dimensional coaxial, coplanar circular loops~\cite{Kirtley_Kalisky_2012}.
-
-% \begin{figure}[!h]
-% \centering
-% \begin{subfigure}{.35\textwidth}
-%   \centering
-%   \includegraphics[width=\linewidth]{examples/images/squid_susceptometry/squid_with_sample_mesh.png}
-%   \label{fig:squid_mesh}
-%   \caption{}
-% \end{subfigure}%
-% \hspace{10pt}
-% \begin{subfigure}{.5\textwidth}
-%   \centering
-%   \includegraphics[width=\linewidth]{examples/images/squid_susceptometry/squid_with_sample_M0_convergence.png}
-%   \label{fig:squid_convergence}
-%   \caption{}
-% %   \caption{Fractional change in flux though all polygons vs.
-solver iteration with a current of $1\,\mathrm{mA}$ flowing in the field coil (\inline{fc}).
-The mutual inductance $M_0$ is given by the flux through the pickup loop (\inline{pl_hull}) divided by the field coil current.}
-% \end{subfigure}%
-% \caption{(a): Device polygons and mesh for the SQUID susceptometer model.
-(b) Fractional change in flux though all polygons vs.
-solver iteration with a current of $1\,\mathrm{mA}$ flowing in the field coil (\inline{fc}).
-The mutual inductance $M_0$ is given by the flux through the pickup loop (\inline{pl_hull}) divided by the field coil current.}
-% \label{fig:susceptometry}
-% \end{figure}
-
-% Figure~\ref{fig:susceptometry}(a) shows a \inline{Device} representing field coil and pickup loop of an actual scanning SQUID sensor.
-In addition to the field coil and pickup loop, there are superconducting shields that limit the amount of magnetic flux that can penetrate the leads connecting the loops to the rest of the circuit (the rest of the circuit is not modeled).
-There are three relevant layers of superconducting films: the base electrode (``BE"), which is furthest from the sample contains the field coil; the first wiring layer (``W1"), which contains the pickup loop and a shield covering the field coil leads; and the second wiring layer (``W2"), which is closest to the sample and contains a shield covering the pickup loop leads.
-The device also contains a layer and film representing the superconducting sample.
-
-% To model a SQUID susceptometry measurement, we first calculate $M_0$, the mutual inductance between the field coil and pickup loop in the absence of the sample.
-This can be done by temporarily setting the sample layer effective penetration depth to a very large value such that it essentially does not screen the field from the field coil (in this case, we set $\Lambda = 10^5\,\um$).
-We then model the field from a known current flowing in the field coil following Section~\ref{section:model:holes} and self-consistently calculate the response of both the sample and the other superconducting layers of the SQUID sensor following Section~\ref{section:model:multilayer}.
-To ensure that the 2D current distribution in the field coil is approximately uniform (as we would expect for a real applied current), we set the field coil layer effective penetration depth to be greater than the width of the field coil conductor.
-
-% Once $M_0$ is known, we can ``turn on" the sample's diamagnetic response by setting its effective penetration depth $\Lambda$ to the desired value and compute $M(z, \Lambda)$ for a given vertical distance $z$ between the sample and the SQUID as described in the previous paragraph.
-The SQUID susceptibility signal is then $M(z, \Lambda) - M_0$, the change in mutual inductance between the field coil and pickup loop due to the presence of the sample (usually given in units of $\Phi_0/\mathrm{A}$, where $\Phi_0$ is the superconducting flux quantum).
-The susceptibility can also be normalized to the bare mutual inductance $M_0$, giving a dimensionless susceptibility $\chi(z, \Lambda)=[M(z, \Lambda) - M_0] / M_0$.
-
-% % \begin{figure}[!h]
-% % \centering
-% % \begin{subfigure}{\textwidth}
-% %   \centering
-% %   \includegraphics[width=\linewidth]{examples/images/squid_susceptometry/squid_with_sample_currents_Lambda=1_00__um__z=-1_00__um.png}
-% % %   \caption{Device polygons and mesh for the SQUID susceptometer model.}
-% % %   \label{fig:squid_mesh}
-% % \end{subfigure}%
-% % \vspace{-15pt}
-% % \begin{subfigure}{\textwidth}
-% %   \centering
-% %   \includegraphics[width=\linewidth]{examples/images/squid_susceptometry/squid_with_sample_currents_Lambda=10_00__um__z=-1_00__um.png}
-% % %   \caption{Fractional change in flux though all polygons vs.
-solver iteration with a current of $1\,\mathrm{mA}$ flowing in the field coil (\inline{fc}).
-The mutual inductance $M_0$ is given by the flux through the pickup loop (\inline{pl_hull}) divided by the field coil current.}
-% % %   \label{fig:squid_convergence}
-% % \end{subfigure}%
-% % \vspace{-15pt}
-% % \begin{subfigure}{\textwidth}
-% %   \centering
-% %   \includegraphics[width=\linewidth]{examples/images/squid_susceptometry/squid_with_sample_currents_Lambda=1_00__um__z=-10_00__um.png}
-% % %   \caption{Fractional change in flux though all polygons vs.
-solver iteration with a current of $1\,\mathrm{mA}$ flowing in the field coil (\inline{fc}).
-The mutual inductance $M_0$ is given by the flux through the pickup loop (\inline{pl_hull}) divided by the field coil current.}
-% % %   \label{fig:squid_convergence}
-% % \end{subfigure}%
-% % \caption{Left: Device polygons and mesh for the SQUID susceptometer model.
-Right: Fractional change in flux though all polygons vs.
-solver iteration with a current of $1\,\mathrm{mA}$ flowing in the field coil (\inline{fc}).
-The mutual inductance $M_0$ is given by the flux through the pickup loop (\inline{pl_hull}) divided by the field coil current.}
-% % % \label{fig:susceptometry}
-% % \end{figure}
 
@@
 
-To include vortices in a \SuperScreen model, one can simply input a \inline{list} of \inline{superscreen.Vortex} objects when calling \inline{superscreen.solve()} (see Code Block~\ref{code:pearl-vortex}).
+To include vortices in a \SuperScreen model, one can simply input a \inline{list} of \inline{superscreen.Vortex} objects when calling \inline{superscreen.solve()}.
 A \inline{Vortex} object specifies the $x,y$ position for the vortex core, the name of the superconducting layer in which the vortex is pinned, and the number of flux quanta $\Phi_0$ contained in the vortex (which is 1 by default).
-The field distributions generated by \SuperScreen in the presence of vortices as described in Sections~\ref{section:model:vortices} and~\ref{section:implementation} agree to within a few percent with the distributions obtained using this Fourier transform method, as demonstrated in Code Block~\ref{code:pearl-vortex} and Figure~\ref{fig:pearl}(c-e).
+The field distributions generated by \SuperScreen in the presence of vortices as described in Sections~\ref{section:model:vortices} and~\ref{section:implementation} agree to within a few percent with the distributions obtained using this Fourier transform method, as demonstrated in Figure~\ref{fig:pearl}(c-e).
 See Ref.~\cite{Brandt2005-wj} for a method to compute the self-energy and interaction energies of vortices in thin films.
 
-\begin{code}
-\begin{minted}[fontsize=\small]{python}
-# Create a device representing square thin film.
-device = sc.Device(
-    "film",
-    layers=[sc.Layer("base", Lambda=0, z0=0)],
-    films=[sc.Polygon("film", layer="base", points=sc.geometry.box(20))],
-    length_units="um",
-)
-device.make_mesh(min_triangles=8_000)
-# Specify the vortex position.
-vortices = [sc.Vortex(x=0, y=0, layer="base")]
-# Sweep Lambda, solve the model, and evaluate the field at the given coordinates.
-Lambdas = np.linspace(0, 2, 5) # [device.length_units]
-for Lambda in Lambdas:
-    device.layers["base"].Lambda = Lambda
-    solution = sc.solve(device=device, vortices=vortices)[-1]
-    # Use solution.field_at_position() to evaluate the magnetic field profile,
-    # and solution.polygon_fluxoid() to calculate fluxoids.
-\end{minted}
-\captionof{listing}{Creates a square superconducting film with side length $20\,\um$ and calculates the magnetic field distribution near a vortex at the center of the film as a function of the the effective penetration depth, $\Lambda$ (see Figure~\ref{fig:pearl}).}
-\label{code:pearl-vortex}
-\end{code}
+% \begin{code}
+% \begin{minted}[fontsize=\small]{python}
+% # Create a device representing square thin film.
+% device = sc.Device(
+%     "film",
+%     layers=[sc.Layer("base", Lambda=0, z0=0)],
+%     films=[sc.Polygon("film", layer="base", points=sc.geometry.box(20))],
+%     length_units="um",
+% )
+% device.make_mesh(min_triangles=8_000)
+% # Specify the vortex position.
+% vortices = [sc.Vortex(x=0, y=0, layer="base")]
+% # Sweep Lambda, solve the model, and evaluate the field at the given coordinates.
+% Lambdas = np.linspace(0, 2, 5) # [device.length_units]
+% for Lambda in Lambdas:
+%     device.layers["base"].Lambda = Lambda
+%     solution = sc.solve(device=device, vortices=vortices)[-1]
+%     # Use solution.field_at_position() to evaluate the magnetic field profile,
+%     # and solution.polygon_fluxoid() to calculate fluxoids.
+% \end{minted}
+% \captionof{listing}{Creates a square superconducting film with side length $20\,\um$ and calculates the magnetic field distribution near a vortex at the center of the film as a function of the the effective penetration depth, $\Lambda$ (see Figure~\ref{fig:pearl}).}
+% \label{code:pearl-vortex}
+% \end{code}
 
@@
 
-In scanning superconducting quantum interference device (SQUID) susceptometry\cite{Gardner2001-gr, Huber2008-il, Kirtley_Kalisky_2012}, the diamagnetic susceptibility of a superconducting sample is measured by bringing the sample close to a pair of superconducting loops.
+In scanning superconducting quantum interference device (SQUID) susceptometry, the diamagnetic susceptibility of a superconducting sample is measured by bringing the sample close to a pair of superconducting loops~\cite{Gardner2001-gr, Huber2008-il, Kirtley_Kalisky_2012}.
 The first loop, called the ``pickup loop" (PL) is attached to a SQUID circuit that sensitively measures the magnetic flux threading the loop.
-The second loop, called the ``field coil" (FC), carries a known current and applies a known magnetic field to both the pickup loop and the sample.
+The second loop, called the ``field coil" (FC), carries a known current $I_\mathrm{FC}$ and applies a known magnetic field to both the pickup loop and the sample.
 The superconducting sample screens the magnetic field from the field coil, modifying the amount of flux threading the pickup loop.
-Thus the change in mutual inductance $M_\mathrm{PL-FC}$ between the field coil and pickup loop in the presence of a sample provides a measure of the sample's magnetic susceptibility.
+Thus the mutual inductance $M_\mathrm{PL-FC}$ between the field coil and pickup loop in the presence of a sample provides a measure of the sample's magnetic susceptibility.
 For superconducting samples, this diamagnetic response is a measure of the sample's penetration depth and therefore its superfluid density.
@@
 
-Figure~\ref{fig:squid-mutuals}(a) shows \SuperScreen \inline{Device} models of the field coil and pickup loop region of four types of real SQUID susceptometers, with geometry taken from the layout artwork (GDS) files.
-In addition to the field coil and pickup loop, there are superconducting shields that limit the amount of magnetic flux that can penetrate the leads connecting the loops to the rest of the circuit (the rest of the circuit is not modeled).
-There are three relevant layers of superconducting films: the base electrode (BE), which is furthest from the sample contains the field coil; the first wiring layer (W1), which contains the pickup loop and a shield covering the field coil leads; and the second wiring layer (W2), which is closest to the sample and contains a shield covering the pickup loop leads.
-There are two insulating layers: I1, which separates BE and W1, and I2, which separates W1 and W2.
-Table~\ref{table:squid-layers} shows the thickness $d$ of each layer in the real devices, as well as the vertical position of the 2D films used to model each layer.
-For the superconducting layers, which are made of Nb, we take the London penetration depth to be $\lambda = 80\,\nm$.
-It is important to note that because $\lambda < d$ for all three layers, the susceptometers are not in the 2D limit in which the model described in Section~\ref{section:model} is technically valid.
-Nevertheless, as shown in Figure~\ref{fig:squid-mutuals}, the field coil - pickup loop mutual inductances, $M_\mathrm{sim}$, computed by \SuperScreen lie within the range of mutual inductances measured in real devices, $M_\mathrm{exp}$ (taken from Ref.~\cite{Kirtley2016-zz} Table 1), for all four sizes of susceptometer.\footnote{The mutual inductance values are shown in units of $\Phi_0 / \mathrm{A}$, where $1\,\Phi_0 / \mathrm{A}\approx2.068\times10^{-3}\,\mathrm{pH}$.} This suggests that variation in current density along the thickness of each film (along the $z$-axis) is not critical in determining the mutual inductance.
-The convergence of $M_\mathrm{PL-FC}$ as a function of solver iteration (see Section~\ref{section:model:multilayer}) is shown in Figure~\ref{fig:squid-mutuals}(c).
-
-\begin{table*}
-\centering
-\begin{tabular}{|l|l|l|l|l|}
-\hline
-Layer name & Material & Thickness & Vertical position, $z_0$ & Films located in layer \\ \hline
-\hline
-W2 & Nb & $d_\mathrm{W2} = 200\,\nm$ & $d_\mathrm{W2} / 2$ & Pickup loop shield, modulation coil \\ \hline
-I2 & SiO${}_2$ & $d_\mathrm{I2} = 130\,\nm$ & --- & --- \\ \hline
-W1 & Nb & $d_\mathrm{W1} = 100\,\nm$ & $d_\mathrm{W2} + d_\mathrm{I2} + d_\mathrm{W1} / 2$ & Pickup loop, field coil shield \\ \hline
-I1 & SiO${}_2$ & $d_\mathrm{I1} = 150\,\nm$ & --- & --- \\ \hline
-BE & Nb & $d_\mathrm{BE} = 160\,\nm$ & $d_\mathrm{W2} + d_\mathrm{I2} + d_\mathrm{W1} + d_\mathrm{I1} + d_\mathrm{BE} / 2$ & Field coil, pickup loop shield \\ \hline
-\end{tabular}
-\caption{Layer stackup for the SQUID susceptometers discussed in Section~\ref{section:examples:scanning-squid}.
-W2 is located at the surface of the chip (deposited last, closest to the sample) and BE deepest below the chip's surface (deposited first).
-See Refs.~\cite{Kirtley2016-zz, Kirtley2016-gt} for more details on the designed of the suscpetometers.}
-\label{table:squid-layers}
-\end{table*}
-
-\begin{figure*}
+\begin{figure*}[t]
     \centering
@@
 The two smaller models converge more quickly than the two larger models for reasons discussed in \ref{appendix:numerics}.
-Note that for the ``X-Large'' model, we set the thicknesses of layers I1 and I2 both to 300 nm to ensure convergence (see \ref{appendix:numerics} and Figure~\ref{fig:xlarge-dz-dr}).}
+Note that for the ``X-Large'' model, we set the thicknesses of layers I1 and I2 both to 300 nm (instead of the nominal values of 150 nm and 130 nm respectively), to ensure convergence (see \ref{appendix:numerics} and Figure~\ref{fig:xlarge-dz-dr}).}
     \label{fig:squid-mutuals}
@@
 
-Having established the value of the field coil - pickup loop mutual inductance $M_\mathrm{PL-FC}$ in the absence of a sample, we can simulate a scanning SQUID susceptometry measurement by calculating $M_\mathrm{PL-FC}$ in the presence of a superconducting sample as a function of the relative position of the pickup loop and the sample.
-For example, in Figure XX, we simulate a SQUID susceptometry image of of a ``Large'' susceptometer (the sample) measured with a ``Medium'' suceptometer (the sensor).
+Figure~\ref{fig:squid-mutuals}(a) shows \SuperScreen \inline{Device} models of the field coil and pickup loop region of four types of real SQUID susceptometers, with geometry taken from the layout artwork (GDS) files.
+In addition to the field coil and pickup loop, there are superconducting shields that limit the amount of magnetic flux that can penetrate the leads connecting the loops to the rest of the circuit (the rest of the circuit is not modeled).
+There are three relevant layers of superconducting films: the base electrode (BE), which is furthest from the sample contains the field coil; the first wiring layer (W1), which contains the pickup loop and a shield covering the field coil leads; and the second wiring layer (W2), which is closest to the sample and contains a shield covering the pickup loop leads.
+There are two insulating layers: I1, which separates BE and W1, and I2, which separates W1 and W2.
+% Table~\ref{table:squid-layers} shows the thickness $d$ of each layer in the real devices, as well as the vertical position of the 2D films used to model each layer. 
+For the superconducting layers, which are made of Nb, we take the London penetration depth to be $\lambda = 80\,\nm$, and the layer thicknesses correspond to the real device design (see Table 1 of Ref.~\cite{Kirtley2016-gt} and Figure 8 of Ref.~\cite{Kirtley2016-zz}).
+It is important to note that because $\lambda < d$ for all three layers, the susceptometers are not in the 2D limit in which the model described in Section~\ref{section:model} is technically valid.
+Nevertheless, as shown in Figure~\ref{fig:squid-mutuals}, the field coil - pickup loop mutual inductances, $M_\mathrm{sim}$, computed by \SuperScreen lie within the range of mutual inductances measured in real devices, $M_\mathrm{exp}$ (taken from Ref.~\cite{Kirtley2016-zz} Table 1), for all four sizes of susceptometer, indicating that variation in current density along the thickness of each film is not critical in determining the mutual inductance in this case.\footnote{The mutual inductance values are shown in units of $\Phi_0 / \mathrm{A}$, where $1\,\Phi_0 / \mathrm{A}\approx2.068\times10^{-3}\,\mathrm{pH}$.} The convergence of $M_\mathrm{PL-FC}$ as a function of solver iteration (see Section~\ref{section:model:multilayer}) is shown in Figure~\ref{fig:squid-mutuals}(c).
+
+% \begin{table*}
+% \centering
+% \begin{tabular}{|l|l|l|l|l|}
+% \hline
+% Layer name & Material & Thickness & Vertical position, $z_0$ & Films located in layer \\ \hline
+% \hline
+% W2 & Nb & $d_\mathrm{W2} = 200\,\nm$ & $d_\mathrm{W2} / 2$ & Pickup loop shield, modulation coil \\ \hline
+% I2 & SiO${}_2$ & $d_\mathrm{I2} = 130\,\nm$ & --- & --- \\ \hline
+% W1 & Nb & $d_\mathrm{W1} = 100\,\nm$ & $d_\mathrm{W2} + d_\mathrm{I2} + d_\mathrm{W1} / 2$ & Pickup loop, field coil shield \\ \hline
+% I1 & SiO${}_2$ & $d_\mathrm{I1} = 150\,\nm$ & --- & --- \\ \hline
+% BE & Nb & $d_\mathrm{BE} = 160\,\nm$ & $d_\mathrm{W2} + d_\mathrm{I2} + d_\mathrm{W1} + d_\mathrm{I1} + d_\mathrm{BE} / 2$ & Field coil, pickup loop shield \\ \hline
+% \end{tabular}
+% \caption{Layer stackup for the SQUID susceptometers discussed in Section~\ref{section:examples:scanning-squid}.
+W2 is located at the surface of the chip (deposited last, closest to the sample) and BE deepest below the chip's surface (deposited first).
+See Refs.~\cite{Kirtley2016-zz, Kirtley2016-gt} for more details on the designed of the suscpetometers.}
+% \label{table:squid-layers}
+% \end{table*}
+
+Having established the value of the field coil - pickup loop mutual inductance $M_\text{PL-FC, no sample}$ in the absence of a sample, we can simulate a scanning SQUID susceptometry measurement by calculating $M_\mathrm{PL-FC}$ in the presence of a superconducting sample as a function of the relative position of the pickup loop and the sample.
+For example, in Figure~\ref{fig:squid-susc} we simulate a SQUID susceptometry measurement of a ``Large'' susceptometer (the sample) measured with a ``Medium'' suceptometer (the sensor).
 Given a \inline{Device} representing the sensor and a \inline{Device} representing the sample, this calculation is performed in three steps:
 \begin{enumerate}
-    \item{Simulate the sensor with some known current $I_\mathrm{FC}$ circulating in the field coil to get \inline{field_coil_solution}.}
-    \item{For a given relative position $(x_s, y_s)$ between the sensor and sample, simulate the sample with an applied field given by \inline{field_coil_solution.field_at_position()} to get \inline{sample_solution}.}
+    \item{Simulate the sensor with some known current $I_\mathrm{FC}$ circulating in the field coil to obtain \inline{field_coil_solution} and $M_\text{PL-FC, no sample}$.}
+    \item{For a given relative position $(x_s, y_s)$ between the sensor and sample, simulate the sample with an applied field given by \inline{field_coil_solution.field_at_position()} to obtain \inline{sample_solution}.}
     \item{Simulate the sensor again, this time with the applied field given by \inline{sample_solution.field_at_position()}, and evaluate the fluxoid $\Phi^f_\mathrm{PL}$ for the hole representing the sensor's pickup loop, and calculate the mutual inductance: $M_\mathrm{PL-FC}(x_s, y_s)=\Phi^f_\mathrm{PL} / I_\mathrm{FC}$.}
@@
 These three steps are repeated for every desired $(x_s, y_s)$ to build up a susceptometry image.
+The susceptibility signal is reported as $M_\text{PL-FC}(x_s, y_s) - M_\text{PL-FC, no sample}$, where values that are more negative indicate a stronger diamagnetic response from the sample.
 Note that in principle it is possible to combine the sensor and sample into a single \inline{Device} with 6 superconducting layers, however this is impractical because it would require generating a new mesh for each $(x_s, y_s)$ and, as discussed in detail in \ref{appendix:numerics}, the problem scales unfavorably with the number of layers in a device and with the total lateral extent of a device.
 
-\begin{figure}
+\begin{figure}[t]
     \centering
-    \includegraphics[width=\linewidth]{}
-    \caption{Caption}
-    \label{fig:my_label}
+    \includegraphics[width=\linewidth]{examples/images/squid-susc-simulation.pdf}
+    \caption{Simulation of a scanning SQUID susceptometry measurement.
+(a) Geometry of the \inline{Device} representing the ``sensor'' SQUID.
+(b) Geometry of the \inline{Device} representing the ``sample'' SQUID.
+(c) Susceptibility of the sample SQUID measured at a temperature of 4.0 K.
+(d) Simulated susceptibility assuming a vertical distance of 50 nm between the surfaces of the two SQUID chips.
+The pickup loop of the sample, which in reality is connected to a SQUID circuit that has a non-linear magnteic response, is modeled as a continuous superconducting loop in the zero-fluxoid (i.e.
+Meissner) state.
+The susceptibility signal is defined as $M_\text{PL-FC} - M_\text{PL-FC, no sample}$.
+The scale bar in (a) applies to all four panels.}
+    \label{fig:squid-susc}
 \end{figure}
 
-\subsection{Application: scanning SQUID magnetometry}
-\label{section:examples:magnetometry}
+% \subsection{Application: scanning SQUID magnetometry}
+% \label{section:examples:magnetometry}
 
@@
 There are cases where the model reproduces experimental results despite violation of this condition (e.g.
-the calculations and in Refs.~\cite{Kirtley2016-zz,Kirtley2016-gt}), but care must be taking in interpreting results in these cases.
+the calculations and in Refs.~\cite{Kirtley2016-zz,Kirtley2016-gt} and Section~\ref{section:examples:scanning-squid}), but care must be taking in interpreting results in these cases.
 Second, the model assumes that all superconducting films behave linearly and without dissipation, and that the applied magnetic field and current density are well below the critical field and critical current density of all films in a device.
-
 Third, \SuperScreen does not support ``terminal currents,'' i.e.
 currents flowing in one terminal of a device and out another terminal.
-This means that inductance calculations are limited to structures with holes, in which all applied currents are circulating currents associated with trapped flux (see Sections~\ref{section:model:holes} and~\ref{section:examples:scanning-squid}).
+This means that inductance calculations are limited to structures with holes, in which all applied currents are circulating currents associated with trapped flux.
 Terminal currents can, however, be included in stream function-base models by setting appropriate boundary conditions~\cite{Khapaev1997-kw,Khapaev2001-xq,Khapaev2001-pw,Muller2021-ci}.
@@
 \captionof{listing}{Simulating an inhomogeneous superconducting device.
-Here we modify the superconducting ring with a slit (Code Block~\ref{code:device} to have an effective penetration depth $\Lambda(x, y)$, which increases linearly from $0.1\,\um$ to $1\,\um$ as a function of the angle between the vector $\vec{r}=(x, y)$ and the $-y$ axis.
+Here we modify the superconducting ring with a slit from Code Block~\ref{code:device} and Figure~\ref{fig:ring-with-slit} to have an effective penetration depth $\Lambda(x, y)$, which increases linearly from $0.1\,\um$ to $1\,\um$ as a function of the angle between the vector $\vec{r}=(x, y)$ and the $-y$ axis.
 See Figure~\ref{fig:inhomogeneous} for the resulting current and field distributions.}
@@
 \end{code}
+\begin{figure*}
+    \centering
+    \includegraphics[width=\textwidth]{examples/images/ring_with_slit_inhomogeneous.pdf}
+    \caption{The output of Code Block~\ref{code:inhomogeneous}: Meissner screening of a uniform applied field of $10\,\mu\mathrm{T}$ by a ring with a slit in a superconducting film with inhomogeneous effective penetration depth $\Lambda(x, y)$.
+(a) The inhomogeneous effective penetration depth $\Lambda(x, y)$, with the ring's outline overlaid in orange.
+(b) The current density $\vec{J}$ in the ring, generated with \inline{Solution.plot_currents()}.
+(c) The $z$-component of the magnetic field $\mu_0H_z$ evaluated at the plane of the ring, generated with \inline{Solution.plot_fields()}.
+(d) The $z$-component of the magnetic field evaluated $z=0.5\,\um$ above the ring (generated using \inline{Solution.plot_field_at_positions()}).}
+    \label{fig:inhomogeneous}
+\end{figure*}
 
@@
 Note that $\Lambda(x, y)$ must vary slowly on the scale of the spacing between mesh vertices in order for results to be reliable.
-
-\begin{figure*}
-    \centering
-    \includegraphics[width=\textwidth]{examples/images/ring_with_slit_inhomogeneous.pdf}
-    \caption{The output of Code Block~\ref{code:inhomogeneous}: Meissner screening of a uniform applied field of $10\,\mu\mathrm{T}$ by a ring with a slit in a superconducting film with inhomogeneous effective penetration depth $\Lambda(x, y)$.
-a) The inhomogeneous effective penetration depth $\Lambda(x, y)$, with the ring's outline overlaid in orange.
-b) The current density $\vec{J}$ in the ring, generated with \inline{Solution.plot_currents()}.
-c) The $z$-component of the magnetic field $\mu_0H_z$ evaluated at the plane of the ring, generated with \inline{Solution.plot_fields()}.
-d) The $z$-component of the magnetic field evaluated $z=0.5\,\um$ above the ring (generated using \inline{Solution.plot_field_at_positions()}).}
-    \label{fig:inhomogeneous}
-\end{figure*}
 

### 2021-11-24 main.tex

@@
 \end{align}
-where $\rho=\sqrt{(x-x')^2 + (y-y')^2}$.
+where $\rho=\sqrt{(x-x')^2 + (y-y')^2}$. Eq.~\ref{eq:field_from_kernel} can also be seen as the Biot-Savart Law formulated in terms of the stream function $g$.
 
@@
 
-\subsection{Application: scanning SQUID susceptometry}
-\label{section:examples:scanning-squid}
-
-In scanning superconducting quantum interference device (SQUID) susceptometry, the diamagnetic susceptibility of a superconducting sample is measured by bringing the sample close to a pair of superconducting loops~\cite{Gardner2001-gr, Huber2008-il, Kirtley_Kalisky_2012}.
-The first loop, called the ``pickup loop" (PL) is attached to a SQUID circuit that sensitively measures the magnetic flux threading the loop.
-The second loop, called the ``field coil" (FC), carries a known current $I_\mathrm{FC}$ and applies a known magnetic field to both the pickup loop and the sample.
-The superconducting sample screens the magnetic field from the field coil, modifying the amount of flux threading the pickup loop.
-Thus the mutual inductance $M_\mathrm{PL-FC}$ between the field coil and pickup loop in the presence of a sample provides a measure of the sample's magnetic susceptibility.
-For superconducting samples, this diamagnetic response is a measure of the sample's penetration depth and therefore its superfluid density.
+\subsection{Calculating inductance}
+\label{section:examples:inductance}
 
@@
 For a device with $N_h$ holes, the $N_h\times N_h$ mutual inductance matrix $\mathbf{M}$ can be computed using the $\inline{Device.mutual_inductance_matrix()}$ method.
+
+\subsection{Application: scanning SQUID susceptometry}
+\label{section:examples:scanning-squid}
+
+In scanning superconducting quantum interference device (SQUID) susceptometry, the magnetic susceptibility of a sample is measured by bringing the sample close to a pair of superconducting loops~\cite{Gardner2001-gr, Huber2008-il, Kirtley_Kalisky_2012}.
+The first loop, called the ``pickup loop" (PL) is attached to a SQUID circuit that sensitively measures the magnetic flux threading the loop.
+The second loop, called the ``field coil" (FC), carries a known current $I_\mathrm{FC}$ and applies a known magnetic field to both the pickup loop and the sample.
+A superconducting sample will screen the magnetic field from the field coil, modifying the amount of flux threading the pickup loop and reducing the mutual inductance $M_\mathrm{PL-FC}$.
+The magnitude of this reduction in $M_\mathrm{PL-FC}$ is a measure of the sample's penetration depth and therefore its superfluid density.
 
@@
 
-Having established the value of the field coil - pickup loop mutual inductance $M_\text{PL-FC, no sample}$ in the absence of a sample, we can simulate a scanning SQUID susceptometry measurement by calculating $M_\mathrm{PL-FC}$ in the presence of a superconducting sample as a function of the relative position of the pickup loop and the sample.
+Having established the value of the field coil - pickup loop mutual inductance in the absence of a sample, $M_\text{PL-FC, no sample}$, we can simulate a scanning SQUID susceptometry measurement by calculating $M_\mathrm{PL-FC}$ in the presence of a superconducting sample as a function of the relative position of the pickup loop and the sample, $(x_s, y_s)$.
 For example, in Figure~\ref{fig:squid-susc} we simulate a SQUID susceptometry measurement of a ``Large'' susceptometer (the sample) measured with a ``Medium'' suceptometer (the sensor).
@@
 automated local mesh refinement based on device geometry or adaptive mesh refinement based on solution convergence), integration with standard integrated circuit layout software and file formats, and further optimization for memory and CPU efficiency.
+
+\section{Acknowledgements}
+\label{section:acknowledgements}
+Some of the computing for this project was performed on the Sherlock cluster.
+We would like to thank Stanford University and the Stanford Research Computing Center for providing computational resources and support that contributed to these research results.
+We acknowledge useful discussions with John R.
+Kirtley.
 
@@
 
-% As mentioned in Section~\ref{section:model:multilayer}, at each iteration of this process, we update the applied field $H_{z,\,\mathrm{applied}}(\vec{r}, z_\ell)$ at each layer $\ell$ based on the currents flowing in all other layers $m\neq\ell$, according to
-
-% \begin{align}
-% \begin{split}
-%     &H_{z,\,\mathrm{applied}}(\vec{r}, z_\ell) \to\\
-%     &H_{z,\,\mathrm{applied}}(\vec{r}, z_\ell)
-%     + \sum_{m\neq\ell}
-%     \int_{S_m} Q_z(\vec{r},\vec{r}')g_m(\vec{r}')\,\mathrm{d}^2r',
-%     \label{eq:iterative}
-% \end{split}
-% \end{align}
-% where $S_m$ is surface of all films in layer $m$ and $g_m$ is the stream function for layer $m$.
-% Furthermore, for a model with $L$ layers, at each iteration, Eq.~\ref{eq:iterative} requires the calculation of $\binom{L}{2} = L(L-1)/2$ such kernel matrices.
-representing $Q_z(\vec{r},\vec{r}')$ in Eq.~\ref{eq:hz-from-kernel}, each of which is a dense $p\times t$ floating point matrix.
-Typically the number of mesh vertices is approximately half the number of triangles ($p\approx t / 2$), so for a mesh with $t=10,000$ triangles, each of these $\mathbf{Q_z}$ matrices is roughly 400 MB (200 MB) if using 64-bit double-precision floats (32-bit single-precision floats).
-Furthermore, each iteration requires performing $2\binom{L}{2} = L(L-1)$ sums involving $\mathbf{Q_z}\cdot\mathbf{g}_m$, where $\mathbf{g}_m$ is the $n\times1$ vector defining the stream function in layer $m$ evaluated at the center of each triangle in the mesh.
-
-% To avoid redundant computation at each iteration and running out of memory during the iterative process, the $\mathbf{Q_z}$ matrices are computed once during the first iteration, cached to a temporary directory on disk, and loaded from disk during subsequent iterations, such that only a single $\mathbf{Q_z}$ is in memory at any given time.
-If running \SuperScreen on a machine with both hard disk (HDD) and solid state disk (SSD) storage, one should ensure that Python uses a temporary directory located on a solid state disk to avoid a significant performance penalty due to hard disk read/write speeds.
-See the documentation for the \inline{tempfile} module of the Python standard library for more details.
-Both the amount of computation needed per iteration and the number of iterations required to reach a certain level of convergence (quantified, for example, by the fractional change in flux through each polygon in the model from one iteration to the next)
-
 \section{Parallel processing}

### 2021-11-24 main.tex
Updates from Overleaf

@@
 
+\begin{figure}
+    \centering
+    \includegraphics[width=\linewidth]{examples/images/inductance.pdf}
+    \caption{Self-inductance $L$ of a circular ring with inner radius $a$ and outer radius $b$, as a function of the ratio $a / b$ and the ring's effective penetration depth $\Lambda$.
+Filled circles indicate results from \SuperScreen, solid lines show numerical results from Ref.~\cite{Brandt2004-ew} (Figure 2), blue squares and diamonds show numerical results from Ref.~\cite{Khapaev_1997} (Figure 1), and the dashed line indicates the analytical solution, $L = 2\mu_0 a$, for $\Lambda=0$ in the limit $a/b\to 0$\cite{Ketchen2012-mb, Babaei_Brojeny2003-la}.}
+    \label{fig:inductance}
+\end{figure}
+
 \subsection{Calculating inductance}

### 2021-11-24 main.tex
Updates from Overleaf

--- 2021-11-24 main.tex
@@
 
+\begin{figure}
+    \centering
+    \includegraphics[width=\linewidth]{examples/images/inductance.pdf}
+    \caption{Self-inductance $L$ of a circular ring with inner radius $a$ and outer radius $b$ (see inset), as a function of the ratio $a / b$ and the ring's effective penetration depth $\Lambda$.
+Filled circles indicate results from \SuperScreen, solid lines show numerical results from Ref.~\cite{Brandt2004-ew} (Figure 2), blue squares and diamonds show numerical results from Ref.~\cite{Khapaev1997-kw} (Figure 1), and the dashed line indicates the analytical solution, $L = 2\mu_0 a$, for $\Lambda=0$ in the limit $a/b\to 0$\cite{Ketchen2012-mb, Babaei_Brojeny2003-la}.
+The \SuperScreen results were generated using a mesh with approximately 4,000 vertices and 8,000 triangles.}
+    \label{fig:inductance}
+\end{figure}
+
 As shown in Ref.~\cite{Brandt2005-wj}, the mutual inductance $M_{ij}$ between holes $i$ and $j$ in a superconducting structure is given by
@@
 For a device with $N_h$ holes, the $N_h\times N_h$ mutual inductance matrix $\mathbf{M}$ can be computed using the $\inline{Device.mutual_inductance_matrix()}$ method.
+
+The self-inductance $L$ of a 2D circular ring with inner radius $a$ and outer radius $b$ (see inset of Figure~\ref{fig:inductance}) has been used as an informal benchmark for superconducting inductance calculations.
+For a ring with effective penetration depth $\Lambda = 0$, it has been shown analytically that $L\to 2\mu_0 a$ in the limit $a/b\to 0$~\cite{Ketchen2012-mb, Babaei_Brojeny2003-la}.
+Khapaev calculated the inductance for $\Lambda = 0$ as a function of $a/b$~\cite{Khapaev1997-kw}, and Brandt and Clem calculated the inductance as a function of both $\Lambda$ and $a / b$~\cite{Brandt2004-ew}.
+Figure~\ref{fig:inductance} shows a comparison between these previous numerical results and the results from \SuperScreen.
+Note that the models used by Brandt and Clem (solid lines) and by the LCR2D software (blue diamonds) require a circularly symmetric film, whereas \SuperScreen (filled circles) and 3D-MLSI~\cite{Khapaev1997-kw, Khapaev2001-xq, Khapaev2001-pw} (blue squares) support arbitrary 2D geometry.
 
@@
 
-% \subsection{Application: scanning SQUID magnetometry}
-% \label{section:examples:magnetometry}
+\subsection{Application: scanning SQUID magnetometry}
+\label{section:examples:magnetometry}
+
+Scanning SQUID susceptometers can also be used for magnetometry, i.e. measuring the magnetic flux above a sample's surface without applying a field to the sample with the field coil.
 

### 2021-11-24 examples/squids/layers.py
Clean up repo

@@ -1,0 +1,54 @@
+from typing import List
+
+from superscreen import Layer
+
+
+def ibm_squid_layers(
+    align: str = "middle",
+    london_lambda: float = 0.08,
+    z0: float = 0.0,
+    d_BE: float = 0.16,
+    d_I1: float = 0.15,
+    d_W1: float = 0.10,
+    d_I2: float = 0.13,
+    d_W2: float = 0.20,
+) -> List[Layer]:
+    """Return a list of superscreen.Layers representing the superconducting layers
+    in IBM SQUID susceptometers.
+
+    See https://arxiv.org/pdf/1605.09483.pdf, Figure 8.
+
+    Args:
+        align: Whether to position the 2D model layer at the top, middle, or bottom
+            of the phyical 3D metal layer.
+        london_lambda: The London penetration depth for the superconducting films,
+            in microns.
+        z0: The vertical position of the bottom of W2, i.e. the surface of the
+            SQUID chip.
+        d_BE, d_I1, d_W1, d_I2, d_W2: Layer thicknesses in microns.
+
+    Returns:
+        A list a Layer objects representing the SQUID wiring layers.
+
+    """
+    assert align in ("top", "middle", "bottom")
+
+    # Metal layer vertical positions in microns.
+    if align == "bottom":
+        z0_W2 = z0
+        z0_W1 = z0 + d_W2 + d_I2
+        z0_BE = z0 + d_W2 + d_I2 + d_W1 + d_I1
+    elif align == "middle":
+        z0_W2 = z0 + d_W2 / 2
+        z0_W1 = z0 + d_W2 / 2 + d_I2 + d_W1 / 2
+        z0_BE = z0 + d_W2 / 2 + d_I2 + d_W1 / 2 + d_I1 + d_BE / 2
+    else:
+        z0_W2 = z0 + d_W2
+        z0_W1 = z0 + d_W2 + d_I2 + d_W1
+        z0_BE = z0 + d_W2 + d_I2 + d_W1 + d_I1 + d_BE
+
+    return [
+        Layer("W2", london_lambda=london_lambda, thickness=d_W2, z0=z0_W2),
+        Layer("W1", london_lambda=london_lambda, thickness=d_W1, z0=z0_W1),
+        Layer("BE", london_lambda=london_lambda, thickness=d_BE, z0=z0_BE),
+    ]

### 2021-11-24 examples/squids/xlarge.py

@@ -1,0 +1,136 @@
+"""IBM SQUID susceptometer, 3 um inner radius pickup loop."""
+
+import numpy as np
+
+import superscreen as sc
+
+from .layers import ibm_squid_layers
+
+
+def make_squid(
+    interp_points: int = 301,
+    align_layers: str = "middle",
+    d_I1: float = 0.3,
+    d_I2: float = 0.3,
+) -> sc.Device:
+    pl_length = 11.5
+    ri_pl = 3.0
+    ro_pl = 3.5
+    ri_fc = 6.0
+    ro_fc = 8.8
+
+    pl_center = sc.Polygon(
+        "pl_center",
+        layer="W1",
+        points=sc.geometry.circle(ri_pl),
+    ).union(sc.geometry.box(0.314, pl_length, center=(0, -pl_length / 2 - 0.9 * ri_pl)))
+
+    pl = sc.Polygon("pl", layer="W1", points=sc.geometry.circle(ro_pl)).union(
+        np.array(
+            [
+                [+0.8, -2.7],
+                [-0.8, -2.7],
+                [-4.6, -15.0],
+                [+4.6, -15.0],
+            ]
+        )
+    )
+
+    pl_shield1 = sc.Polygon(
+        "pl_shield1",
+        layer="W2",
+        points=np.array(
+            [
+                [+2.6, -6.3],
+                [+1.3, -3.6],
+                [-1.3, -3.6],
+                [-2.6, -6.3],
+                [-6.0, -16.0],
+                [+6.0, -16.0],
+            ]
+        ),
+    )
+
+    pl_shield2 = sc.Polygon(
+        "pl_shield2",
+        layer="BE",
+        points=np.array(
+            [
+                [+4.5, -13.2],
+                [-4.5, -13.2],
+                [-5.3, -15.5],
+                [+5.3, -15.5],
+            ]
+        ),
+    )
+
+    fc_center = sc.Polygon(
+        "fc_center", layer="BE", points=sc.geometry.circle(ri_fc)
+    ).union(
+        np.array(
+            [
+                [8.5, -10.3],
+                [4.15, -4.15],
+                [3.55, -4.75],
+                [7.75, -10.75],
+            ]
+        )
+    )
+
+    fc = sc.Polygon("fc", layer="BE", points=sc.geometry.circle(ro_fc)).union(
+        np.array(
+            [
+                [12.0, -9.6],
+                [7.5, -4.8],
+                [4.2, -4.2],
+                [3.2, -7.8],
+                [6.0, -13.5],
[…]

### 2021-11-24 main.tex
Updates from Overleaf

@@
 Finally, in Section~\ref{section:conlusion}, we conclude by discussing applications, limitations, and possible extensions of the package.
+Python scripts and Jupyter notebooks used to generate all figures presented below can be found in the GitHub repository accompanying this manuscript [ref.].
 
@@
 %     \centering
-%     \includegraphics[width=\textwidth]{examples/images/square_ring_results.png}
+%     \includegraphics[width=\textwidth]{examples/images/square_ring_results.jpg}
 %     \caption{Sheet current $\vec{J}(x, y)$ and out-of-plane magnetic field $\mu_0H_z(x, y)$ evaluated in the plane of a square ring with effective penetration depth $\Lambda=1\,\um$ subject to (a, b) a uniform applied field of 0.5 mT or (c, d) trapped flux inducing a circulating current of 1 mA.
@@
     \centering
-    \includegraphics[width=\textwidth]{examples/images/pearl.png}
+    \includegraphics[width=\textwidth]{examples/images/pearl.jpg}
     \caption{Vortex field profiles calculated with \SuperScreen agree with the analytical solution (Eq.~\ref{eq:pearl}) to within a few percent.
@@
     \centering
-    \includegraphics[width=\textwidth]{examples/images/squid-mutuals.png}
+    \includegraphics[width=\textwidth]{examples/images/squid-mutuals.jpg}
     \caption{Calculating SQUID susceptometer mutual inductance, defined as the fluxoid induced in the SQUID pickup loop per unit current flowing in the field coil: $M_\mathrm{PL-FC}=\Phi^f_\mathrm{PL} / I_\mathrm{FC}$.
@@
 \label{section:acknowledgements}
+We acknowledge useful discussions with John R.
+Kirtley.
+This work is supported by the Department of Energy,  Office of Science, Basic Energy Sciences, Materials Sciences and Engineering Division, under Contract DE-AC02-76SF00515.
 Some of the computing for this project was performed on the Sherlock cluster.
 We would like to thank Stanford University and the Stanford Research Computing Center for providing computational resources and support that contributed to these research results.
-We acknowledge useful discussions with John R.
-Kirtley.
 
@@
 %     \centering
-%     \includegraphics[width=\textwidth]{examples/images/fluxoid_combined.png}
+%     \includegraphics[width=\textwidth]{examples/images/fluxoid_combined.jpg}
 %     \caption{Demonstration of the fluxoid properties listed in Section~\ref{section:examples:fluxoid} for a square ring with $\Lambda=1\,\um$, inner side length $5\,\um$, and outer side length $10\,\um$, whose outline is shown with white lines in the left and middle columns, subject to a uniform applied field of 0.1 mT.
@@
     \centering
-    \includegraphics[width=\linewidth]{examples/images/xlarge-dz-dr.png}
+    \includegraphics[width=\linewidth]{examples/images/xlarge-dz-dr.jpg}
     \caption{\SuperScreen results may be unreliable for multi-layer models where the spacing between layers is smaller than the typical vertex-to-vertex distance, $\delta r$.

### 2021-11-25 main.tex

@@
 
-% \begin{code}
-% \begin{minted}[fontsize=\small]{python}
-% import numpy as np
-
-% # Simulate the response of the square ring to a uniform applied field of 0.5 mT
-% applied_field = sc.sources.ConstantField(0.5)
-% field_units = "mT"
-% solutions = sc.solve(
-%     device=square_ring, applied_field=applied_field, field_units=field_units,
-% )
-% assert len(solutions) == 1 # Since there is only one layer in this Device
-% uniform_field_solution = solutions[-1]
-
-% # Simulate a current circulating around the hole in the ring
-% # (with no applied field).
-% trapped_flux_solution = sc.solve(
-%     device=square_ring, applied_field=None, circulating_currents={"hole" : "1 mA"},
-% )[-1]
-
-% # Specify a sequence of (x, y) coordinates to plot cross-sections
-% # of the simulated currents and fields.
-% xs = np.linspace(-5.5, 5.5, 201) # [microns]
-% cross_sections = [ # Two sets of [x, y] coordinates
-%     np.stack([xs, xs], axis=1), # diagonal cross-section
-%     np.stack([xs, np.zeros_like(xs)], axis=1), # horizontal cross-section
-% ]
-% for solution in (uniform_field_solution, trapped_flux_solution):
-%     solution.plot_currents(cross_section_coords=cross_sections, units="mA/um")
-%     solution.plot_fields(cross_section_coords=cross_sections)
-% \end{minted}
-% \captionof{listing}{Solves for the current and magnetic field distributions for the \inline{square_ring} device given a uniform applied field, and circulating current with no applied field, and plots the resulting sheet current and field.}
-% \label{code:ring_circulating_current}
-% \end{code}
-
-% Code Block~\ref{code:ring_circulating_current} solves two models involving the \inline{square_ring} device, which was generated using Code Blocks~\ref{code:device} and \ref{code:mesh_generation}.
-First, Meissner screening of a spatially uniform applied out-of-plane magnetic field and second, the response of the ring to trapped flux with an associated circulating current of 1 mA (with no applied magnetic field).
-The resulting sheet current and magnetic field distributions (calculated using the optimized mesh shown in Figure~\ref{fig:mesh}d) can be visualized using the \inline{plot_currents()} and \inline{plot_fields()} methods, which produce the images shown in Figure~\ref{fig:square-ring-results}.
-
-% \begin{figure}
-%     \centering
-%     \includegraphics[width=\textwidth]{examples/images/square_ring_results.jpg}
-%     \caption{Sheet current $\vec{J}(x, y)$ and out-of-plane magnetic field $\mu_0H_z(x, y)$ evaluated in the plane of a square ring with effective penetration depth $\Lambda=1\,\um$ subject to (a, b) a uniform applied field of 0.5 mT or (c, d) trapped flux inducing a circulating current of 1 mA.
-The sub-figures show the output of (a, c) \inline{Solution.plot_currents()} and (b, d) \inline{Solution.plot_fields()}, as shown in Code Block~\ref{code:ring_circulating_current}.
-For the current plots (a, c), the color-scale indicates the magnitude of the sheet current (or current density), $|\vec{J}|$, and the direction is indicated by the white streamlines.}
-%     \label{fig:square-ring-results}
-% \end{figure}
-
 The output of \inline{superscreen.solve()} is a \inline{list} of \inline{superscreen.Solution} objects, with a length of 1 plus the number of iterations used for the iterative portion of the calculation.
@@
     \centering
-    \includegraphics[width=\textwidth]{examples/images/pearl.jpg}
-    \caption{Vortex field profiles calculated with \SuperScreen agree with the analytical solution (Eq.~\ref{eq:pearl}) to within a few percent.
+    \includegraphics[width=\textwidth]{examples/images/pearl.pdf}
+    \caption{Vortex field profiles calculated using \SuperScreen agree with the analytical solution (Eq.~\ref{eq:pearl}) to within a few percent.
 Here, we model a vortex trapped at the center of a square superconducting film lying in the $x-y$ plane with side length $20\,\um$ as a function of the film's effective penetration depth, $\Lambda$.
@@
 Figure~\ref{fig:inductance} shows a comparison between these previous numerical results and the results from \SuperScreen.
-Note that the models used by Brandt and Clem (solid lines) and by the LCR2D software (blue diamonds) require a circularly symmetric film, whereas \SuperScreen (filled circles) and 3D-MLSI~\cite{Khapaev1997-kw, Khapaev2001-xq, Khapaev2001-pw} (blue squares) support arbitrary 2D geometry.
+Note that the models used by Brandt and Clem (solid lines) and by the LCR2D software (blue diamonds) require a circularly symmetric superconducting film, whereas \SuperScreen (filled circles) and 3D-MLSI~\cite{Khapaev1997-kw, Khapaev2001-xq, Khapaev2001-pw} (blue squares) support arbitrary 2D geometry.
 
@@
     \centering
-    \includegraphics[width=\textwidth]{examples/images/squid-mutuals.jpg}
+    \includegraphics[width=\textwidth]{examples/images/squid-mutuals.pdf}
     \caption{Calculating SQUID susceptometer mutual inductance, defined as the fluxoid induced in the SQUID pickup loop per unit current flowing in the field coil: $M_\mathrm{PL-FC}=\Phi^f_\mathrm{PL} / I_\mathrm{FC}$.
@@
 %     \centering
-%     \includegraphics[width=\textwidth]{examples/images/fluxoid_combined.jpg}
+%     \includegraphics[width=\textwidth]{examples/images/fluxoid_combined.pdf}
 %     \caption{Demonstration of the fluxoid properties listed in Section~\ref{section:examples:fluxoid} for a square ring with $\Lambda=1\,\um$, inner side length $5\,\um$, and outer side length $10\,\um$, whose outline is shown with white lines in the left and middle columns, subject to a uniform applied field of 0.1 mT.
@@
     \centering
-    \includegraphics[width=\linewidth]{examples/images/xlarge-dz-dr.jpg}
+    \includegraphics[width=\linewidth]{examples/images/xlarge-dz-dr.pdf}
     \caption{\SuperScreen results may be unreliable for multi-layer models where the spacing between layers is smaller than the typical vertex-to-vertex distance, $\delta r$.

### 2021-11-28 examples/squids/xlarge.py
Update images

@@ -10,8 +10,8 @@ from .layers import ibm_squid_layers
 def make_squid(
     interp_points: int = 301,
     align_layers: str = "middle",
-    d_I1: float = 0.3,
-    d_I2: float = 0.3,
+    d_I1: float = 0.4,
+    d_I2: float = 0.4,
 ) -> sc.Device:
     pl_length = 11.5
     ri_pl = 3.0
@@ -103,7 +103,7 @@ def make_squid(
     )
 
     bbox = sc.Polygon(
-        "bounding_box", layer="BE", points=sc.geometry.box(24, 26, center=(2, -3.5))
+        "bounding_box", layer="BE", points=sc.geometry.box(24, 28, center=(2, -3.5))
     )
 
     films = [fc_shield, fc, pl_shield1, pl_shield2, pl]

### 2021-11-28 main.tex
Updates from Overleaf

@@
 
+\newcommand{\pvec}[1]{\vec{#1}\mkern2mu\vphantom{#1}}
 \newcommand{\inline}[1]{\mintinline{python}{#1}\xspace}
@@
 %% keywords here, in the form: keyword \sep keyword
-superconductivity\sep Meissner screening\sep thin film\sep London equations \sep inductance
+superconductivity\sep Meissner screening\sep thin film\sep London equation \sep inductance
 
@@
 
-This introduction to \SuperScreen is organized as follows: In Section~\ref{section:model}, we outline the model and its assumptions and in Section~\ref{section:implementation}, we describe its numerical implementation.
-In Section~\ref{section:overview}, we provide an overview of the structure of the \SuperScreen package and discuss some important development details.
-In Section~\ref{section:examples}, we demonstrate how to perform several types of simulations using \SuperScreen and compare the results to analytical solutions and experimental results.
-Finally, in Section~\ref{section:conlusion}, we conclude by discussing applications, limitations, and possible extensions of the package.
-Python scripts and Jupyter notebooks used to generate all figures presented below can be found in the GitHub repository accompanying this manuscript [ref.].
+This introduction to \SuperScreen is organized as follows: In Section~\ref{section:model} we outline the model and its assumptions, and in Section~\ref{section:implementation} we describe its numerical implementation.
+In Section~\ref{section:overview} we provide an overview of the structure of the \SuperScreen package and discuss some important development details.
+In Section~\ref{section:examples} we demonstrate how to perform several types of simulations using \SuperScreen and compare the results to analytical solutions and experimental results.
+Finally, in Section~\ref{section:conlusion} we conclude by discussing applications, limitations, and possible extensions of the package.\footnote{Python scripts and Jupyter notebooks used to generate all figures presented below can be found in the GitHub repository accompanying this manuscript [ref.].}
 
@@
 $H_{z,\,\mathrm{applied}}(x, y, z)$.
-Given $H_{z,\,\mathrm{applied}}(x, y, z)$ and information about the geometry and magnetic penetration depth of all films in a superconducting structure, we aim to calculate the thickness-integrated current density (or sheet current) $\vec{J}(x, y)$ at all points inside the films, from which one can calculate the vector magnetic field $\vec{H}(x, y, z)$ at all points both inside and outside the films.
+Given $H_{z,\,\mathrm{applied}}(x, y, z)$ and information about the geometry and magnetic penetration depth of all films in a superconducting structure, we aim to calculate the thickness-integrated current density $\vec{J}(x, y)$ at all points inside the films, from which one can calculate the vector magnetic field $\vec{H}(x, y, z)$ at all points both inside and outside the films.
 
@@
 $\nabla=\left(\frac{\partial}{\partial x}, \frac{\partial}{\partial y}, \frac{\partial}{\partial z}\right)$.
-Brandt's model assumes that the current density $\vec{j}$ is approximately independent of $z$, such that  $\vec{j}(\vec{r}) = \vec{j}(x, y, z)\approx\vec{j}_{z_0}(x, y)$ for a film lying parallel to the $x-y$ plane at vertical position $z_0$.
-Working now with the thickness-integrated current density (sheet current) $\vec{J}(x, y)=\vec{j}_{z_0}(x, y)\cdot d$, where $d$
+The 2D London model assumes that the current density $\vec{j}$ is approximately independent of $z$, such that  $\vec{j}(\vec{r}) = \vec{j}(x, y, z)\approx\vec{j}_{z_0}(x, y)$ for a film lying parallel to the $x-y$ plane at vertical position $z_0$.
+Working now with the thickness-integrated current density $\vec{J}(x, y)=\vec{j}_{z_0}(x, y)\cdot d$, where $d$
 is the thickness of the film, the second London equation reduces to
@@
 
-Because the sheet current has zero divergence inside the superconducting film ($\nabla\cdot\vec{J}=0$)
-except at small terminals where current can be injected, one can express the sheet current in terms
+Because the current density has zero divergence inside the superconducting film ($\nabla\cdot\vec{J}=0$)
+except at small terminals where current can be injected, one can express $\vec{J}$ in terms
 of a scalar potential $g(x, y)$, called the stream function:
@@
     \begin{split}
-        H_x(\vec{r}) &= \int_F Q_x(\vec{r},\vec{r}')g(x', y')\,\mathrm{d}^2r'\\
-        H_y(\vec{r}) &= \int_F Q_y(\vec{r},\vec{r}')g(x', y')\,\mathrm{d}^2r'\\
+        H_x(\vec{r}) &= \int_F Q_x(\vec{r},\pvec{r}')g(x', y')\,\mathrm{d}^2r'\\
+        H_y(\vec{r}) &= \int_F Q_y(\vec{r},\pvec{r}')g(x', y')\,\mathrm{d}^2r'\\
         H_z(\vec{r}) &= H_{z,\,\mathrm{applied}}(\vec{r})
-        + \int_F Q_z(\vec{r},\vec{r}')g(x', y')\,\mathrm{d}^2r'.  
+        + \int_F Q_z(\vec{r},\pvec{r}')g(x', y')\,\mathrm{d}^2r'.  
     \end{split}
@@
 
-Here we assume an out-of-plane applied magnetic field $\vec{H}_\mathrm{applied}(\vec{r}')=H_\mathrm{z,\,\mathrm{applied}}(\vec{r}')\hat{z}$.
-$F$ is the film area (with $g = 0$ outside of the film), and $Q_x(\vec{r},\vec{r}')$, $Q_y(\vec{r},\vec{r}')$, and $Q_z(\vec{r},\vec{r}')$ are dipole kernel functions which give the respective component of the magnetic field at position $\vec{r}=(x, y, z)$ due to a dipole of unit strength at position $\vec{r}'=(x', y', z')$:
+Here we assume an out-of-plane applied magnetic field $\vec{H}_\mathrm{applied}(\pvec{r}')=H_\mathrm{z,\,\mathrm{applied}}(\pvec{r}')\hat{z}$.
+$F$ is the film area (with $g = 0$ outside of the film), and $Q_x(\vec{r},\pvec{r}')$, $Q_y(\vec{r},\pvec{r}')$, and $Q_z(\vec{r},\pvec{r}')$ are dipole kernel functions which give the respective component of the magnetic field at position $\vec{r}=(x, y, z)$ due to a dipole of unit strength at position $\pvec{r}'=(x', y', z')$:
 \begin{align}
@@
     \begin{split}
-        Q_x(\vec{r}, \vec{r}') &=  3\frac{(x-x')(z-z')}
+        Q_x(\vec{r}, \pvec{r}') &=  3\frac{(x-x')(z-z')}
         {4\pi[(z-z')^2+\rho^2]^{5/2}}\\
-        Q_y(\vec{r}, \vec{r}') &=  3\frac{(y-y')(z-z')}
+        Q_y(\vec{r}, \pvec{r}') &=  3\frac{(y-y')(z-z')}
         {4\pi[(z-z')^2+\rho^2]^{5/2}}\\
-        Q_z(\vec{r}, \vec{r}') &=  \frac{2(z-z')^2-\rho^2}
+        Q_z(\vec{r}, \pvec{r}') &=  \frac{2(z-z')^2-\rho^2}
         {4\pi[(z-z')^2+\rho^2]^{5/2}},
@@
         = \\ & \underbrace{H_{z,\,\mathrm{applied}}(\vec{r})}_{\text{applied field}}
-        + \underbrace{\int_F Q_z(\vec{r},\vec{r}')g(\vec{r}')\,\mathrm{d}^2r'}_{\text{screening field}},
+        + \underbrace{\int_F Q_z(\vec{r},\pvec{r}')g(\pvec{r}')\,\mathrm{d}^2r'}_{\text{screening field}},
     \end{split}
 \end{align}
-where now $\vec{r}$ and $\vec{r}'$ are 2D vectors, i.e.
+where now $\vec{r}$ and $\pvec{r}'$ are 2D vectors, i.e.
 $z-z'=0$ since the film is in the same plane as itself.
@@
     = \\ &-\int_F\left[
-        Q_z(\vec{r},\vec{r}')-\delta(\vec{r}-\vec{r}')\Lambda(\vec{r}')\nabla^2\right
-    ]g(\vec{r}')\,\mathrm{d}^2r',
+        Q_z(\vec{r},\pvec{r}')-\delta(\vec{r}-\pvec{r}')\Lambda(\pvec{r}')\nabla^2\right
+    ]g(\pvec{r}')\,\mathrm{d}^2r',
 \end{split}
@@
 
-In films that have holes (regions of vacuum completely surrounded by superconductor), each hole $k$ can contain a trapped flux $\Phi_k$, with an associated circulating current $I_{\mathrm{circ},\,k}$.
-The (hypothetical) applied field that would cause such a circulating current is given by Eq.~\ref{eq:applied_to_stream} if we set $g=I_{\mathrm{circ},\,k}$ for all points lying inside hole $k$:
+In films that have holes (regions of vacuum completely surrounded by superconductor), each hole $k$ can contain a trapped flux associated a current $I_{\mathrm{circ},\,k}$ circulating around the hole.
+The applied field that would cause such a circulating current is given by Eq.~\ref{eq:applied_to_stream} if we set $g=I_{\mathrm{circ},\,k}$ for all points lying inside hole $k$:
 \begin{align}
@@
     &-\int_{\mathrm{hole}\,k}[
-        Q_z(\vec{r},\vec{r}')-\delta(\vec{r}-\vec{r}')\Lambda(\vec{r}')\nabla^2
+        Q_z(\vec{r},\pvec{r}')-\delta(\vec{r}-\pvec{r}')\Lambda(\pvec{r}')\nabla^2
     ] I_{\mathrm{circ},\,k} \,\mathrm{d}^2r'.   
@@
     = \\&-\int_F\left[
-        Q_z(\vec{r},\vec{r}')-\delta(\vec{r}-\vec{r}')\Lambda(\vec{r}')\nabla^2\right
-    ]g(\vec{r}')\,\mathrm{d}^2r'.
+        Q_z(\vec{r},\pvec{r}')-\delta(\vec{r}-\pvec{r}')\Lambda(\pvec{r}')\nabla^2\right
+    ]g(\pvec{r}')\,\mathrm{d}^2r'.
 \end{split}
@@
 
-The fluxoid $\Phi^f_S$ for a 2D region $S$ with 1D boundary $\partial S$ is given by the sum of flux through $S$ and the line integral of sheet current around $\partial S$~\cite{Brandt2005-wj,Clem2005-ye,Tinkham2004-zn}:
+The fluxoid $\Phi^f_S$ for a 2D region $S$ with 1D boundary $\partial S$ is given by the sum of magnetic flux through $S$ and the line integral of the supercurrent density $\vec{J}$ around $\partial S$~\cite{Brandt2005-wj,Clem2005-ye,Tinkham2004-zn}:
 \begin{equation}
@@
     &-\int_F\left[
-        Q_z(\vec{r},\vec{r}')-\delta(\vec{r}-\vec{r}')\Lambda(\vec{r}')\nabla^2\right
-    ]g(\vec{r}')\,\mathrm{d}^2r',
+        Q_z(\vec{r},\pvec{r}')-\delta(\vec{r}-\pvec{r}')\Lambda(\pvec{r}')\nabla^2\right
+    ]g(\pvec{r}')\,\mathrm{d}^2r',
 \end{split}
@@
             &+ \sum_{m\neq\ell}
-            \int_{F_m} Q_z(\vec{r},\vec{r}')g_m(\vec{r}')\,\mathrm{d}^2r',
+            \int_{F_m} Q_z(\vec{r},\pvec{r}')g_m(\pvec{r}')\,\mathrm{d}^2r',
             \label{eq:iterative}
@@
 
-The $n\times n$ kernel matrix $\mathbf{Q}$ represents the kernel function $Q_z(\vec{r},\vec{r}')$ for all points lying in the plane of the film, and the $n\times 1$ weight vector $\mathbf{w}$, which assigns an effective area to each vertex in the mesh, represents the differential element $\mathrm{d}^2r'$.
+The $n\times n$ kernel matrix $\mathbf{Q}$ represents the kernel function $Q_z(\vec{r},\pvec{r}')$ for all points lying in the plane of the film, and the $n\times 1$ weight vector $\mathbf{w}$, which assigns an effective area to each vertex in the mesh, represents the differential element $\mathrm{d}^2r'$.
 Both $\mathbf{Q}$ and $\mathbf{w}$ are solely determined by the geometry of the mesh, so they only need to be computed once for a given device.
@@
 where $q_{ij} = \left(4\pi|\vec{r}_i-\vec{r}_j|^3\right)^{-1}$
-(which is $\lim_{\Delta z\to 0}Q_z(\vec{r},\vec{r}')$ cf. Eq.~\ref{eq:kernels}),
+(which is $\lim_{\Delta z\to 0}Q_z(\vec{r},\pvec{r}')$ cf. Eq.~\ref{eq:kernels}),
 and $\delta_{ij}$ is the Kronecker delta function.
@@
 Once the stream function $\mathbf{g}$ is known for the full mesh,
-the sheet current flowing in the film can be computed from Eq.~\ref{eq:stream}, the $z$-component of the total field in the plane of the film can be computed
+the supercurrent flowing in the film can be computed from Eq.~\ref{eq:stream}, the $z$-component of the total field in the plane of the film can be computed
 from Eq.~\ref{eq:field_from_kernel_num}, and the full vector magnetic field $\vec{H}(x, y, z)$
@@
 )
-device.make_mesh(min_triangles=8000, optimesh_steps=None)
+device.make_mesh(min_points=5000, optimesh_steps=None)
 device.plot(mesh=True)
@@
 # Visualize the solution.
+# Plot the current density evaluated at each layer in the Device.
+solution.plot_currents()
 # Plot the magnetic field evaluated at each layer in the Device.
 solution.plot_fields()
-# Plot the current density evaluated at each layer in the Device.
-solution.plot_currents()
 # Plot the field evaluated at any points in space.
@@
     }
-    % \item{
-    % \inline{Solution.grid_current_density()}: Interpolates the stream functions to a rectangular grid and calculates the current density (sheet current) $\vec{J}(x, y)$ in each layer using Eq.~\ref{eq:stream}.
-    % }
     \item{
@@
     \item{
-    \inline{superscreen.plot_currents()}: Given a \inline{Solution}, plots the sheet current $\vec{J}(x, y)$ for one or more layers in the device.
+    \inline{superscreen.plot_currents()}: Given a \inline{Solution}, plots the current density $\vec{J}(x, y)$ for one or more layers in the device.
     }
@@
 % )
-% device.make_mesh(min_triangles=8_000)
+% device.make_mesh(min_points=5_000)
 % # Specify the vortex position.
@@
     \caption{Self-inductance $L$ of a circular ring with inner radius $a$ and outer radius $b$ (see inset), as a function of the ratio $a / b$ and the ring's effective penetration depth $\Lambda$.
-Filled circles indicate results from \SuperScreen, solid lines show numerical results from Ref.~\cite{Brandt2004-ew} (Figure 2), blue squares and diamonds show numerical results from Ref.~\cite{Khapaev1997-kw} (Figure 1), and the dashed line indicates the analytical solution, $L = 2\mu_0 a$, for $\Lambda=0$ in the limit $a/b\to 0$\cite{Ketchen2012-mb, Babaei_Brojeny2003-la}.
+Filled circles indicate results from \SuperScreen, solid lines show numerical results from Figure 2 of Ref.~\cite{Brandt2004-ew}, blue squares and diamonds show numerical results from Figure 1 of Ref.~\cite{Khapaev1997-kw}, and the dashed line indicates the analytical solution, $L = 2\mu_0 a$, for $\Lambda=0$ in the limit $a/b\to 0$\cite{Ketchen2012-mb, Babaei_Brojeny2003-la}.
 The \SuperScreen results were generated using a mesh with approximately 4,000 vertices and 8,000 triangles.}
@@
 \label{section:examples:scanning-squid}
-
-In scanning superconducting quantum interference device (SQUID) susceptometry, the magnetic susceptibility of a sample is measured by bringing the sample close to a pair of superconducting loops~\cite{Gardner2001-gr, Huber2008-il, Kirtley_Kalisky_2012}.
-The first loop, called the ``pickup loop" (PL) is attached to a SQUID circuit that sensitively measures the magnetic flux threading the loop.
-The second loop, called the ``field coil" (FC), carries a known current $I_\mathrm{FC}$ and applies a known magnetic field to both the pickup loop and the sample.
-A superconducting sample will screen the magnetic field from the field coil, modifying the amount of flux threading the pickup loop and reducing the mutual inductance $M_\mathrm{PL-FC}$.
-The magnitude of this reduction in $M_\mathrm{PL-FC}$ is a measure of the sample's penetration depth and therefore its superfluid density.
 
@@
     \label{fig:squid-mutuals}
+\end{figure*}
+
+In scanning superconducting quantum interference device (SQUID) susceptometry, the magnetic susceptibility of a sample is measured by bringing the sample close to a pair of superconducting loops~\cite{Gardner2001-gr, Huber2008-il, Kirtley_Kalisky_2012}.
+The first loop, called the ``pickup loop" (PL) is attached to a SQUID circuit that sensitively measures the magnetic flux threading the loop.
+The second loop, called the ``field coil" (FC), carries a known current $I_\mathrm{FC}$ and applies a known magnetic field to both the pickup loop and the sample.
+A superconducting sample will screen the magnetic field from the field coil, modifying the amount of flux threading the pickup loop and reducing the mutual inductance $M_\mathrm{PL-FC}$.
+The magnitude of this reduction in $M_\mathrm{PL-FC}$ is a measure of the sample's penetration depth and therefore its superfluid density.
+
+\begin{figure*}
+    \centering
+    \includegraphics[width=\textwidth]{examples/images/squid-susc-simulation.pdf}
+    \caption{Simulation of a scanning SQUID susceptometry measurement.
+(a) Geometry of the \inline{Device} representing the ``sensor'' SQUID.
+(b) Geometry of the \inline{Device} representing the ``sample'' SQUID.
+(c) Susceptibility of the sample SQUID measured at a temperature of 4.0 K.
+(d) Simulated susceptibility, calculcated using the method described in Section~\ref{section:examples:scanning-squid}.
+The pickup loop of the sample, which in reality is connected to a SQUID circuit that has a non-linear magnetic response, is modeled as a continuous superconducting loop in the zero-fluxoid (i.e.
+Meissner) state.
+The susceptibility signal is defined as $M_\text{PL-FC} - M_\text{PL-FC, no sample}$, where $M_\text{PL-FC, no sample}\approx163\,\Phi_0/\mathrm{A}$ (see Figure~\ref{fig:squid-mutuals}(a), second column).
+The scale bar in (a) applies to all four panels.}
+    \label{fig:squid-susc}
 \end{figure*}
@@
 
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=\linewidth]{examples/images/squid-susc-simulation.pdf}
-    \caption{Simulation of a scanning SQUID susceptometry measurement.
-(a) Geometry of the \inline{Device} representing the ``sensor'' SQUID.
-(b) Geometry of the \inline{Device} representing the ``sample'' SQUID.
-(c) Susceptibility of the sample SQUID measured at a temperature of 4.0 K.
-(d) Simulated susceptibility assuming a vertical distance of 50 nm between the surfaces of the two SQUID chips.
-The pickup loop of the sample, which in reality is connected to a SQUID circuit that has a non-linear magnteic response, is modeled as a continuous superconducting loop in the zero-fluxoid (i.e.
-Meissner) state.
-The susceptibility signal is defined as $M_\text{PL-FC} - M_\text{PL-FC, no sample}$.
-The scale bar in (a) applies to all four panels.}
-    \label{fig:squid-susc}
-\end{figure}
-
-\subsection{Application: scanning SQUID magnetometry}
-\label{section:examples:magnetometry}
-
-Scanning SQUID susceptometers can also be used for magnetometry, i.e. measuring the magnetic flux above a sample's surface without applying a field to the sample with the field coil.
+% \subsection{Application: scanning SQUID magnetometry}
+% \label{section:examples:magnetometry}
+
+% Scanning SQUID susceptometers can also be used for magnetometry, i.e. measuring the magnetic flux above a sample's surface without applying a field to the sample with the field coil.
 
@@
 \end{code}
-\begin{figure*}
+\begin{figure*}[h!]
     \centering
@@
 \begin{split}
-    H_z(\vec{r}) &= \int_F Q_z(\vec{r},\vec{r}')g(x', y')\,\mathrm{d}^2r',\,\text{where}\\
-    Q_z(\vec{r}, \vec{r}') &=  \frac{2(z-z')^2-\rho^2}
+    H_z(\vec{r}) &= \int_F Q_z(\vec{r},\pvec{r}')g(x', y')\,\mathrm{d}^2r',\,\text{where}\\
+    Q_z(\vec{r}, \pvec{r}') &=  \frac{2(z-z')^2-\rho^2}
             {4\pi[(z-z')^2+\rho^2]^{5/2}}
@@
 
-\begin{figure}
+\begin{figure}[t]
     \centering
@@
 For this reason, mutli-layer structures with closely-spaced layers are the most challenging class of problem to solve.
-The iterative method used described in Section~\ref{section:model:multilayer} is memory-intensive for models with a large mesh (many vertices $p$ and triangles $t$, with typically $p\approx t / 2$) and/or many layers $L$, because the average distance between vertices decreases slowly with increasing number of triangles, $\langle\delta r\rangle\sim t^{-1/2}$, whereas the size of the (dense floating-point) $p\times t$ matrix that represents the dipole kernel $Q_z(\vec{r},\vec{r}')$ in Eq.~\ref{eq:hz-from-kernel} increases roughly as $t^2$.
+The iterative method used described in Section~\ref{section:model:multilayer} is memory-intensive for models with a large mesh (many vertices $p$ and triangles $t$, with typically $p\approx t / 2$) and/or many layers $L$, because the average distance between vertices decreases slowly with increasing number of triangles, $\langle\delta r\rangle\sim t^{-1/2}$, whereas the size of the (dense floating-point) $p\times t$ matrix that represents the dipole kernel $Q_z(\vec{r},\pvec{r}')$ in Eq.~\ref{eq:hz-from-kernel} increases roughly as $t^2$.
 The end result is that the memory footprint of kernel matrix scales roughly as $\langle\delta r\rangle^{-4}$, so decreasing the mean distance between vertices by a factor of 2 increases the memory required by a factor of 16.

### 2021-11-29 main.tex

@@
 In order to numerically solve Eq.~\ref{eq:field_from_kernel} and Eq.~\ref{eq:Heff_sub}, we have to discretize the films, holes, and the vacuum regions surrounding them. We use a triangular
-(Delaunay) mesh, consisting of $n$ points (or vertices)
+(Delaunay) mesh, consisting of $p$ points (or vertices)
 which together form $t$ triangles. Below we denote column vectors and matrices using bold font. $\mathbf{A}\mathbf{B}$
@@
 
-The $n\times n$ kernel matrix $\mathbf{Q}$ represents the kernel function $Q_z(\vec{r},\pvec{r}')$ for all points lying in the plane of the film, and the $n\times 1$ weight vector $\mathbf{w}$, which assigns an effective area to each vertex in the mesh, represents the differential element $\mathrm{d}^2r'$.
+The $p\times p$ kernel matrix $\mathbf{Q}$ represents the kernel function $Q_z(\vec{r},\pvec{r}')$ for all points lying in the plane of the film, and the $p\times 1$ weight vector $\mathbf{w}$, which assigns an effective area to each vertex in the mesh, represents the differential element $\mathrm{d}^2r'$.
 Both $\mathbf{Q}$ and $\mathbf{w}$ are solely determined by the geometry of the mesh, so they only need to be computed once for a given device.
-$\mathbf{h}_z$, $\mathbf{h}_{z,\,\mathrm{applied}}$, and $\mathbf{g}$ are all $n\times 1$ vectors, with each row representing the value of the quantity at the
+$\mathbf{h}_z$, $\mathbf{h}_{z,\,\mathrm{applied}}$, and $\mathbf{g}$ are all $p\times 1$ vectors, with each row representing the value of the quantity at the
 corresponding vertex in the mesh. The vector $\mathbf{w}$ is equal to the diagonal of the ``lumped mass matrix'' $\mathbf{M}$: $w_i=M_{ii} = \frac{1}{3}\sum_{t\in\mathcal{N}(i)}\mathrm{area}(t)$,
@@
 and $\delta_{ij}$ is the Kronecker delta function.
-The diagonal terms involving the $n\times 1$ vector $\mathbf{C}$ are meant to work around the fact that $q_{ii}$ diverge (see Ref.~\cite{Brandt2005-wj} for more details), and $\mathbf{C}$ is given by
+The diagonal terms involving the $p\times 1$ vector $\mathbf{C}$ are meant to work around the fact that $q_{ii}$ diverge (see Ref.~\cite{Brandt2005-wj} for more details), and $\mathbf{C}$ is given by
 \begin{equation}
@@
 inside holes in the film. $\mathbf{\Lambda}$ is either a scalar or a vector defining the effective penetration depth at every included vertex in the mesh, and $\mathbf{\nabla}^2$
-is the Laplace operator, an $n\times n$ matrix defined such that $\mathbf{\nabla}^2\mathbf{f}$ computes the Laplacian $\nabla^2f(x,y)$ of a function $f(x,y)$ defined on the mesh  (see~\ref{appendix:laplace}).
+is the Laplace operator, a $p\times p$ matrix defined such that $\mathbf{\nabla}^2\mathbf{f}$ computes the Laplacian $\nabla^2f(x,y)$ of a function $f(x,y)$ defined on the mesh  (see~\ref{appendix:laplace}).
 
@@
 At the time of writing, \SuperScreen requires Python version 3.6--3.9.
-The package is located in a public repository on GitHub~\cite{superscreen}, and a suite of unit tests is run automatically via the GitHub Actions continuous integration (CI) tool whenever a change or proposed change (Pull Request) is made to the \inline{main} branch of the repository.
+The package is located in a public repository on GitHub~\cite{superscreen, BishopVanHorn2021-bd}, and a suite of unit tests is run automatically via the GitHub Actions continuous integration (CI) tool whenever a change or proposed change (Pull Request) is made to the \inline{main} branch of the repository.
 At the time of writing, the test suite is executed using Python versions 3.6 through 3.9, and the test coverage is $>95\%$.
@@
 \SuperScreen allows one to calculate the fluxoid $\Phi^f_S$ for any polygonal region $S$ whose boundary $\partial S$ lies completely within a superconducting film using the method \inline{Solution.polygon_fluxoid()} (see Section~\ref{section:model:fluxoid}, Eq.~\ref{eq:fluxoid}).
-The ``flux part''  $\int_S\mu_0H_z(\vec{r})\,\mathrm{d}^2r$ is calculated using \inline{Solution.polygon_flux()}, which computes the flux through a polygon representing a region $S$ by averaging the field at the three vertices of each triangle $t$ whose centroid lies in $S$ to estimate the field $\mu_0H_{z, t}$ at the centroid of the triangle, then returns the flux $\sum_t \mu_0H_{z,t}A_t$, where $A_t$ is the area of triangle $t$.
+The ``flux part''  $\int_S\mu_0H_z(\vec{r})\,\mathrm{d}^2r$ is calculated using \inline{Solution.polygon_flux()}, which computes the flux through a polygon representing a region $S$ as $\Phi_S=\sum_{i\in S} \mu_0H_{z,i}w_i$, where $H_{z,i}$ is the magnetic field at vertex $i$ (recall that $w_i$ assigns an effective area to mesh vertex $i$).
 The ``supercurrent part'' $\oint_S\mu_o\Lambda(\vec{r})\vec{J}(\vec{r})\cdot\mathrm{d}\vec{r}$ is calculated by evaluating the vector current density $\vec{J}$ at each point in the path $\partial S$ using \inline{Solution.interp_current_density()}, then computing the line integral along the path using the trapezoid rule.
@@
 For a structure with $N_h$ holes, we can specify $N_h$ fluxoids $\Phi^f_h$ and find the circulating currents $I_h$ by minimizing the deviation of each fluxoid from its desired value.
+For $N_h=1$, this is treated as a root-finding problem, which can be solved with typically only three calls to \inline{superscreen.solve()}.
+When $N_h>1$, it is a least-squares minimization problem with $N_h$ free parameters.
 This calculation is implemented in the \inline{superscreen.find_fluxoid_solution()} function.
@@
 For all four models, the simulated mutual inductance, $M_\mathrm{sim}$, falls within the range of mutual inductance values measured in real devices, $M_\mathrm{exp}$, which were reported in Table 1 of Ref.~\cite{Kirtley2016-zz}.
-The meshes for the ``Small,'' ``Medium,'' and ``Large'' models consisted of approximately 5,000 vertices and 10,000 triangles, whereas the mesh for the ``X-Large'' model consisted of about 7,700 vertices and 15,000 triangles.
+The meshes for the ``Small,'' ``Medium,'' and ``Large'' models consisted of approximately 7,000 vertices and 14,000 triangles, whereas the mesh for the ``X-Large'' model consisted of about 8,000 vertices and 15,000 triangles.
 The two smaller models converge more quickly than the two larger models for reasons discussed in \ref{appendix:numerics}.
-Note that for the ``X-Large'' model, we set the thicknesses of layers I1 and I2 both to 300 nm (instead of the nominal values of 150 nm and 130 nm respectively), to ensure convergence (see \ref{appendix:numerics} and Figure~\ref{fig:xlarge-dz-dr}).}
+Note that for the ``X-Large'' model, we set the thicknesses of layers I1 and I2 both to 400 nm (instead of the nominal values of 150 nm and 130 nm respectively), to ensure convergence (see \ref{appendix:numerics} and Figure~\ref{fig:xlarge-dz-dr}).}
     \label{fig:squid-mutuals}
@@
 $y$ axis units).
-When $\delta z\lesssim\delta r$, the model significantly underestimates the mutual inductance.
+When $\delta z\lesssim\delta r$, the model significantly overestimates the mutual inductance.
 (b) and (c): Out-of-plane magnetic field $\mu_0H_z$ evaluated at the plane of the pickup loop (W1 layer) for (b) the nominal layer spacing with $\delta z<\delta 2$ (indicated with a black $\times$ in (a)) and (c) $\delta z > \delta r$ (indicated with a black $+$ in (a)).
@@
 The limitation described above can be seen in the model of the largest SQUID susceptometer described in Section~\ref{section:examples:scanning-squid}, which has a field coil inner radius of $6\,\um$ and a total modeled area of roughly $600\,\um^2$.
-As shown in Figure~\ref{fig:xlarge-dz-dr}, \SuperScreen significantly underestimates the mutual inductance between the field coil and pickup loop when $\delta z <\delta r$ because, in that case, the discretized version of Eq.~\ref{eq:hz-from-kernel} does not correctly compute the magnetic field due the stream functions of the superconducting layers.
+As shown in Figure~\ref{fig:xlarge-dz-dr}, \SuperScreen significantly overestimates the mutual inductance between the field coil and pickup loop when $\delta z <\delta r$ because, in that case, the discretized version of Eq.~\ref{eq:hz-from-kernel} does not correctly compute the magnetic field due the stream functions of the superconducting layers.
 For the sake of computing mutual inductance as in Section~\ref{section:examples:scanning-squid}, it is physically reasonable to artificially increase the vertical spacing between layers such that $\delta z\geq \delta r$ because we expect the magnetic field at the pickup loop, a vertical distance $\delta z$ away from the center of the field coil, to fall off roughly as $\left(\delta z^2 + R^2_\mathrm{FC}\right)^{-3/2}$, where $R_\mathrm{FC}\approx 6\,\um\gg\delta z$.
@@
 For this reason, mutli-layer structures with closely-spaced layers are the most challenging class of problem to solve.
-The iterative method used described in Section~\ref{section:model:multilayer} is memory-intensive for models with a large mesh (many vertices $p$ and triangles $t$, with typically $p\approx t / 2$) and/or many layers $L$, because the average distance between vertices decreases slowly with increasing number of triangles, $\langle\delta r\rangle\sim t^{-1/2}$, whereas the size of the (dense floating-point) $p\times t$ matrix that represents the dipole kernel $Q_z(\vec{r},\pvec{r}')$ in Eq.~\ref{eq:hz-from-kernel} increases roughly as $t^2$.
+The iterative method used described in Section~\ref{section:model:multilayer} is memory-intensive for models with a large mesh (many vertices $p$ and triangles $t$, with typically $t\approx 2p$) and/or many layers $L$, because the average distance between vertices decreases slowly with increasing number of triangles, $\langle\delta r\rangle\sim p^{-1/2}$, whereas the size of the (dense floating-point) $p\times p$ matrix that represents the dipole kernel $Q_z(\vec{r},\pvec{r}')$ in Eq.~\ref{eq:hz-from-kernel} increases roughly as $p^2$.
 The end result is that the memory footprint of kernel matrix scales roughly as $\langle\delta r\rangle^{-4}$, so decreasing the mean distance between vertices by a factor of 2 increases the memory required by a factor of 16.

### 2021-11-29 main.tex
overleaf changes

@@
 \usepackage{etoolbox}
-\BeforeBeginEnvironment{minted}{\begin{center}\begin{tcolorbox}[width=0.9\textwidth]}
+\BeforeBeginEnvironment{minted}{\begin{center}\begin{tcolorbox}[width=\linewidth]}
 \AfterEndEnvironment{minted}{\end{tcolorbox}\end{center}}
@@
 \captionsetup[listing]{skip=0pt}
+
+\newenvironment{code-onecol}{\captionsetup{type=listing}}{\hfill}
+\SetupFloatingEnvironment{listing}{name=Code Block}
+\BeforeBeginEnvironment{code-onecol}{\vspace{10pt}\begin{figure}[t!]}
+\AfterEndEnvironment{code-onecol}{\end{figure}}
 
@@
 
+\subsection{Calculating the fluxoid}
+\label{section:examples:fluxoid}
+
+\SuperScreen allows one to calculate the fluxoid $\Phi^f_S$ for any polygonal region $S$ whose boundary $\partial S$ lies completely within a superconducting film using the method \inline{Solution.polygon_fluxoid()} (see Section~\ref{section:model:fluxoid}, Eq.~\ref{eq:fluxoid}).
+The ``flux part''  $\int_S\mu_0H_z(\vec{r})\,\mathrm{d}^2r$ is calculated using \inline{Solution.polygon_flux()}, which computes the flux through a polygon representing a region $S$ as $\Phi_S=\sum_{i\in S} \mu_0H_{z,i}w_i$, where $H_{z,i}$ is the magnetic field at vertex $i$ (recall that $w_i$ assigns an effective area to mesh vertex $i$).
+The ``supercurrent part'' $\oint_S\mu_o\Lambda(\vec{r})\vec{J}(\vec{r})\cdot\mathrm{d}\vec{r}$ is calculated by evaluating the vector current density $\vec{J}$ at each point in the path $\partial S$ using \inline{Solution.interp_current_density()}, then computing the line integral along the path using the trapezoid rule.
+The sum of these two terms gives the fluxoid $\Phi^f_S$.
+
+While the 2D London model doesn't ``know'' about fluxoid quantization, in the sense that the quantization condition $\Phi^f_S=n\Phi_0$ is not automatically satisfied by solutions to Eq.~\ref{eq:london} for multiply-connected films, we can nevertheless calculate current and field distributions for different fluxoid states in multiply-connected superconductors by adjusting the currents circulating around each hole to realize a prescribed set of fluxoid values.
+For a structure with $N_h$ holes, we can specify $N_h$ fluxoids $\Phi^f_h$ and find the circulating currents $I_h$ by minimizing the deviation of each fluxoid from its desired value.
+For $N_h=1$, this is treated as a root-finding problem, which can be solved with typically only three calls to \inline{superscreen.solve()}.
+When $N_h>1$, it is a least-squares minimization problem with $N_h$ free parameters.
+This calculation is implemented in the \inline{superscreen.find_fluxoid_solution()} function.
+Code Block~\ref{code:fluxoid} demonstrates how to model a device with one or more holes, each in the $n=0$ fluxoid state, subject to a uniform applied field, and Figure~\ref{fig:fluxoid} shows the field and current distributions for a rectangular superconducting film with $\Lambda=0.25\,\um$, which has one rectangular and one elliptical hole.
+The least-squares minimization for the model shown in Figure~\ref{fig:fluxoid}, with $N_h=2$, required 18 total calls to \inline{superscreen.solve()}.
+
+\begin{code-onecol}
+\begin{minted}[fontsize=\small]{python}
+import superscreen as sc
+# Assume that we have already created a
+# superscreen.Device with one or more
+# holes, and generated the mesh.
+# Specify the desired fluxoid for each
+# hole in the device:
+fluxoids = {
+    hole_name: 0
+    for hole_name in device.holes
+}
+applied_field = sc.sources.ConstantField(1)
+field_units = "mT"
+
+result = sc.find_fluxoid_solution(
+    device=device,
+    fluxoids=fluxoids,
+    applied_field=applied_field,
+    field_units=field_units,
+)
+solution, opt_result = result
+\end{minted}
+\captionof{listing}{Calculating the field and current distributions for fluxoid states in a multiply-connected superconducting film.
+Given a \inline{Device} with $N_h\geq 1$ holes and a desired fluxoid $\Phi^f_h$ for each hole, \inline{superscreen.find_fluxoid_solution()} optimizes the current $I_h$ circulating around each hole to realize the desired fluxoid state.
+The function returns a \inline{tuple} of length 2, the first element being the final optimized \inline{superscreen.Solution} and the second element being an instance of either \inline{scipy.optimize.RootResults} (if $N_h=1$) or \inline{scipy.optimize.OptimizeResult} (if $N_h>1$), which contains information about the optimization that was performed.
+See Figure~\ref{fig:fluxoid} for an example of the results for a film with two holes, both in the $n=0$ fluxoid state.}
+\label{code:fluxoid}
+\end{code-onecol}
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=\linewidth]{examples/images/fluxoid.pdf}
+    \caption{(a) Magnetic field and (b) current density distributions generated by Code Block~\ref{code:fluxoid} for a rectangular superconducting film with $\Lambda=0.25\,\um$, which has one rectangular and one elliptical hole.
+The film is subject to a uniform applied out-of-plane field of 1 mT, and both holes are set to be in the $n=0$ fluxoid (i.e.
+Meissner) state.
+The resulting ciruclating currents are $I_\text{rectangle} = -1.071$ mA and $I_\text{ellipse} = -1.589$ mA, and the residual fluxoid for each hole is smaller than $10^{-7}\,\Phi_0$.
+These results were computed using a mesh with approximately 5,000 vertices and 10,000 triangles.}
+    \label{fig:fluxoid}
+\end{figure}
+
 \subsection{Pearl vortices in thin films}
@@
 where $\mathcal{F}\{\cdot\}$ is the 2D Fourier transform, $\vec{k}=(k_x, k_y)$ are in-plane spatial frequencies, $z$ is the out-of-plane position at which the field is evaluated, and $2\Lambda = 2\lambda^2 / d$ is the Pearl length~\cite{Pearl1964-cl, Tafuri2004-ap}.
-The real-space magnetic field distribution near a Pearl vortex can be calculated numerically by taking the inverse Fourier transform of Eq.~\ref{eq:pearl}: $H_z(\vec{r}, z)=\mathcal{F}^{-1}\{\tilde{H}_z(\vec{k}, z)\}$.
+The real-space magnetic field distribution near a Pearl vortex can be calculated by taking the inverse Fourier transform of Eq.~\ref{eq:pearl}: $H_z(\vec{r}, z)=\mathcal{F}^{-1}\{\tilde{H}_z(\vec{k}, z)\}$.
 
@@
 The field distributions generated by \SuperScreen in the presence of vortices as described in Sections~\ref{section:model:vortices} and~\ref{section:implementation} agree to within a few percent with the distributions obtained using this Fourier transform method, as demonstrated in Figure~\ref{fig:pearl}(c-e).
+Figure~\ref{fig:pearl}(e) shows the fluxoid for a circular region $S$ with radius $r=1\,\um$ enclosing a Pearl vortex trapped in a film as a function of the film's effective penetration depth, $\Lambda$.
+When $\Lambda=0$, the screening currents decay very quickly away from the center of the vortex, so the ``supercurrent part'' of the $\Phi^f_S$ vanishes.
+With increasing $\Lambda$, the ``supercurrent part'' accounts for an increasing fraction of the total fluxoid.
 See Ref.~\cite{Brandt2005-wj} for a method to compute the self-energy and interaction energies of vortices in thin films.
@@
 
-\subsection{Calculating the fluxoid}
-\label{section:examples:fluxoid}
-
-\SuperScreen allows one to calculate the fluxoid $\Phi^f_S$ for any polygonal region $S$ whose boundary $\partial S$ lies completely within a superconducting film using the method \inline{Solution.polygon_fluxoid()} (see Section~\ref{section:model:fluxoid}, Eq.~\ref{eq:fluxoid}).
-The ``flux part''  $\int_S\mu_0H_z(\vec{r})\,\mathrm{d}^2r$ is calculated using \inline{Solution.polygon_flux()}, which computes the flux through a polygon representing a region $S$ as $\Phi_S=\sum_{i\in S} \mu_0H_{z,i}w_i$, where $H_{z,i}$ is the magnetic field at vertex $i$ (recall that $w_i$ assigns an effective area to mesh vertex $i$).
-The ``supercurrent part'' $\oint_S\mu_o\Lambda(\vec{r})\vec{J}(\vec{r})\cdot\mathrm{d}\vec{r}$ is calculated by evaluating the vector current density $\vec{J}$ at each point in the path $\partial S$ using \inline{Solution.interp_current_density()}, then computing the line integral along the path using the trapezoid rule.
-The sum of these two terms gives the fluxoid $\Phi^f_S$.
-
-Figure~\ref{fig:pearl}(e) shows the fluxoid for a circular region $S$ with radius $r=1\,\um$ enclosing a Pearl vortex trapped in a film as a function of the film's effective penetration depth, $\Lambda$.
-When $\Lambda=0$, the screening currents decay very quickly away from the center of the vortex, so the ``supercurrent part'' of the $\Phi^f_S$ vanishes.
-With increasing $\Lambda$, the ``supercurrent part'' accounts for an increasing fraction of the total fluxoid.
-
-While the 2D London model doesn't ``know'' about fluxoid quantization, in the sense that the quantization condition $\Phi^f_S=n\Phi_0$ is not automatically satisfied by solutions to Eq.~\ref{eq:london} for multiply-connected films, we can nevertheless calculate current and field distributions for different fluxoid states in multiply-connected superconductors by adjusting the currents circulating around each hole to realize a prescribed set of fluxoid values.
-For a structure with $N_h$ holes, we can specify $N_h$ fluxoids $\Phi^f_h$ and find the circulating currents $I_h$ by minimizing the deviation of each fluxoid from its desired value.
-For $N_h=1$, this is treated as a root-finding problem, which can be solved with typically only three calls to \inline{superscreen.solve()}.
-When $N_h>1$, it is a least-squares minimization problem with $N_h$ free parameters.
-This calculation is implemented in the \inline{superscreen.find_fluxoid_solution()} function.
-
 \subsection{Calculating inductance}
@@
 For a device with $N_h$ holes, the $N_h\times N_h$ mutual inductance matrix $\mathbf{M}$ can be computed using the $\inline{Device.mutual_inductance_matrix()}$ method.
+For example, the mutual inductance matrix for the device shown in Figure~\ref{fig:fluxoid} is:
+\begin{equation*}
+    \mathbf{M} = 
+    \begin{pmatrix}
+    	10.319 & -1.536 \\
+        -1.527 & 7.130
+    \end{pmatrix}
+    \,\mathrm{pH},
+\end{equation*}
+where the matrix is indexed as $$\begin{pmatrix}\text{ellipse}\\\text{rectangle}\end{pmatrix},$$
+and the ``fractional asymmetry'' of $\mathbf{M}$ is $|M_{01} - M_{10}| / \min(|M_{01}|, |M_{10}|)\approx 0.6\%$.
 
@@
 For all four models, the simulated mutual inductance, $M_\mathrm{sim}$, falls within the range of mutual inductance values measured in real devices, $M_\mathrm{exp}$, which were reported in Table 1 of Ref.~\cite{Kirtley2016-zz}.
+The mutual inductance values are shown in units of $\Phi_0 / \mathrm{A}$, where $1\,\Phi_0 / \mathrm{A}\approx2.068\times10^{-3}\,\mathrm{pH}$.
 The meshes for the ``Small,'' ``Medium,'' and ``Large'' models consisted of approximately 7,000 vertices and 14,000 triangles, whereas the mesh for the ``X-Large'' model consisted of about 8,000 vertices and 15,000 triangles.
@@
 It is important to note that because $\lambda < d$ for all three layers, the susceptometers are not in the 2D limit in which the model described in Section~\ref{section:model} is technically valid.
-Nevertheless, as shown in Figure~\ref{fig:squid-mutuals}, the field coil - pickup loop mutual inductances, $M_\mathrm{sim}$, computed by \SuperScreen lie within the range of mutual inductances measured in real devices, $M_\mathrm{exp}$ (taken from Ref.~\cite{Kirtley2016-zz} Table 1), for all four sizes of susceptometer, indicating that variation in current density along the thickness of each film is not critical in determining the mutual inductance in this case.\footnote{The mutual inductance values are shown in units of $\Phi_0 / \mathrm{A}$, where $1\,\Phi_0 / \mathrm{A}\approx2.068\times10^{-3}\,\mathrm{pH}$.} The convergence of $M_\mathrm{PL-FC}$ as a function of solver iteration (see Section~\ref{section:model:multilayer}) is shown in Figure~\ref{fig:squid-mutuals}(c).
+Nevertheless, as shown in Figure~\ref{fig:squid-mutuals}, the field coil - pickup loop mutual inductances, $M_\mathrm{sim}$, computed by \SuperScreen lie within the range of mutual inductances measured in real devices, $M_\mathrm{exp}$ (taken from Ref.~\cite{Kirtley2016-zz} Table 1), for all four sizes of susceptometer, indicating that variation in current density along the thickness of each film is not critical in determining the mutual inductance in this case.
+The convergence of $M_\mathrm{PL-FC}$ as a function of solver iteration (see Section~\ref{section:model:multilayer}) is shown in Figure~\ref{fig:squid-mutuals}(c).
 

### 2021-11-29 main.tex
Updates from Overleaf

@@
 There are several important limitations to the applicability of \SuperScreen and the matrix inversion method on which it is based~\cite{Brandt2004-ew,Brandt2005-wj}.
-First, strictly speaking all superconducting films should be in the 2D limit, with London penetration depth $\lambda$ less than film thickness $d$, such that the out-of-plane current density is approximately constant.
+First, strictly speaking all superconducting films should be in the 2D limit, with London penetration depth $\lambda$ less than film thickness $d$, such that the current density is approximately constant along the thickness of the film.
 There are cases where the model reproduces experimental results despite violation of this condition (e.g.
@@
 This means that inductance calculations are limited to structures with holes, in which all applied currents are circulating currents associated with trapped flux.
-Terminal currents can, however, be included in stream function-base models by setting appropriate boundary conditions~\cite{Khapaev1997-kw,Khapaev2001-xq,Khapaev2001-pw,Muller2021-ci}.
+Terminal currents can, however, be included in stream function-based models by setting appropriate boundary conditions~\cite{Khapaev1997-kw,Khapaev2001-xq,Khapaev2001-pw,Muller2021-ci}.
 Finally, care should be taken to ensure that for a given model the mesh is of sufficient density that, to within the desired precision, the results of simulations do not depend on mesh size (see \ref{appendix:numerics}).
@@
 Potential improvements to \SuperScreen include: support for terminal currents as discussed above, automated determination of solution convergence for models with multiple layers, more sophisticated mesh generation (e.g.
-automated local mesh refinement based on device geometry or adaptive mesh refinement based on solution convergence), integration with standard integrated circuit layout software and file formats, and further optimization for memory and CPU efficiency.
+automated local mesh refinement based on device geometry or adaptive mesh refinement based on solution convergence), integration with standard integrated circuit layout software/file formats, and further optimization for memory and CPU efficiency.
 
@@
 FastHenry executables compiled for several common operating systems are available as part of the open-source XicTools superconducting integrated circuit design suite from Whiteley Research, Inc~\cite{wrcad, XicTools}.
-A 2D London model based on a scalar stream function, much like the model used by \SuperScreen~\cite{Brandt2004-ew, Brandt2005-wj} (described in detail in Section~\ref{section:model}), forms the basis of the 3D-MLSI software package~\cite{Khapaev1997-kw, Khapaev2001-xq, Khapaev2001-pw}, which is also written in C and is not open-source.
+A 2D London model based on a scalar stream function, much like the model used by \SuperScreen~\cite{Brandt2004-ew, Brandt2005-wj}, forms the basis of the 3D-MLSI software package~\cite{Khapaev1997-kw, Khapaev2001-xq, Khapaev2001-pw}, which is also written in C and is not open-source.
 For a more thorough overview and comparison of inductance extraction tools, see Ref.~\cite{Gaj1999-ls}.
@@
 For this reason, mutli-layer structures with closely-spaced layers are the most challenging class of problem to solve.
-The iterative method used described in Section~\ref{section:model:multilayer} is memory-intensive for models with a large mesh (many vertices $p$ and triangles $t$, with typically $t\approx 2p$) and/or many layers $L$, because the average distance between vertices decreases slowly with increasing number of triangles, $\langle\delta r\rangle\sim p^{-1/2}$, whereas the size of the (dense floating-point) $p\times p$ matrix that represents the dipole kernel $Q_z(\vec{r},\pvec{r}')$ in Eq.~\ref{eq:hz-from-kernel} increases roughly as $p^2$.
+The iterative method used described in Section~\ref{section:model:multilayer} is memory-intensive for models with a large mesh (many vertices $p$ and triangles $t$, with typically $t\approx 2p$) and/or many layers $L$, because the average distance between vertices decreases slowly with increasing number of vertices, $\langle\delta r\rangle\sim p^{-1/2}$, whereas the size of the (dense floating-point) $p\times p$ matrix that represents the dipole kernel $Q_z(\vec{r},\pvec{r}')$ in Eq.~\ref{eq:hz-from-kernel} increases as $p^2$.
 The end result is that the memory footprint of kernel matrix scales roughly as $\langle\delta r\rangle^{-4}$, so decreasing the mean distance between vertices by a factor of 2 increases the memory required by a factor of 16.

### 2021-11-29 main.tex

@@
 The iterative method used described in Section~\ref{section:model:multilayer} is memory-intensive for models with a large mesh (many vertices $p$ and triangles $t$, with typically $t\approx 2p$) and/or many layers $L$, because the average distance between vertices decreases slowly with increasing number of vertices, $\langle\delta r\rangle\sim p^{-1/2}$, whereas the size of the (dense floating-point) $p\times p$ matrix that represents the dipole kernel $Q_z(\vec{r},\pvec{r}')$ in Eq.~\ref{eq:hz-from-kernel} increases as $p^2$.
-The end result is that the memory footprint of kernel matrix scales roughly as $\langle\delta r\rangle^{-4}$, so decreasing the mean distance between vertices by a factor of 2 increases the memory required by a factor of 16.
+The end result is that the memory footprint of kernel matrix scales roughly as $\langle\delta r\rangle^{-4}$, so decreasing the mean distance between vertices by a factor of 2 increases the memory required by a factor of 16 (see Figure~\ref{fig:scaling}).
 Furthermore, for a model with $L$ layers there are $\binom{L}{2} = L(L-1)/2$ such kernel matrices needed for each iteration of the calculation outlined in Section~\ref{section:model:multilayer}.
@@
 using 32-bit single-precision floats instead of the default 64-bit double-precision floats by setting \inline{device.solve_dtype = "float32"}) to reduce memory requirements without significantly impacting solution accuracy.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\linewidth]{examples/images/scaling.pdf}
+    \caption{Caption}
+    \label{fig:scaling}
+\end{figure}
 

### 2021-11-29 main.tex

@@
 The end result is that the memory footprint of kernel matrix scales roughly as $\langle\delta r\rangle^{-4}$, so decreasing the mean distance between vertices by a factor of 2 increases the memory required by a factor of 16 (see Figure~\ref{fig:scaling}).
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=\linewidth]{examples/images/scaling.pdf}
+    \caption{Scaling of kernel matrix size $p^2$ with mesh vertex spacing $\delta r$ for a mesh with $p$ vertices and $t$ triangles.
+(a) Typically the number of triangle $t$ in the mesh is close to twice the number of vertices $p$.
+(b) Normalized histograms of vertex distances $\delta r$ (colors correspond to the points in (a)).
+The histogram bins are given by \inline{numpy.linspace(0.15, 0.65, 201)}.
+(c) The mean vertex-to-vertex distance $\langle\delta r\rangle$ scales roughly as $p^{-1/2}$.
+(d).
+The size of each $p\times p$ kernel matrix (of which where are $\binom{L}{2}$ for a device with $L$ layers) scales roughly as $\langle\delta r\rangle^{-4}$.}
+    \label{fig:scaling}
+\end{figure}
+
 Furthermore, for a model with $L$ layers there are $\binom{L}{2} = L(L-1)/2$ such kernel matrices needed for each iteration of the calculation outlined in Section~\ref{section:model:multilayer}.
@@
 using 32-bit single-precision floats instead of the default 64-bit double-precision floats by setting \inline{device.solve_dtype = "float32"}) to reduce memory requirements without significantly impacting solution accuracy.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=\linewidth]{examples/images/scaling.pdf}
-    \caption{Caption}
-    \label{fig:scaling}
-\end{figure}
 

### 2021-11-29 main.tex
Updates from Overleaf

@@
 )
-device.make_mesh(min_points=5000, optimesh_steps=None)
+device.make_mesh(min_points=3500, optimesh_steps=None)
 device.plot(mesh=True)
@@
 The iterative method used described in Section~\ref{section:model:multilayer} is memory-intensive for models with a large mesh (many vertices $p$ and triangles $t$, with typically $t\approx 2p$) and/or many layers $L$, because the average distance between vertices decreases slowly with increasing number of vertices, $\langle\delta r\rangle\sim p^{-1/2}$, whereas the size of the (dense floating-point) $p\times p$ matrix that represents the dipole kernel $Q_z(\vec{r},\pvec{r}')$ in Eq.~\ref{eq:hz-from-kernel} increases as $p^2$.
-The end result is that the memory footprint of kernel matrix scales roughly as $\langle\delta r\rangle^{-4}$, so decreasing the mean distance between vertices by a factor of 2 increases the memory required by a factor of 16 (see Figure~\ref{fig:scaling}).
+The end result is that the memory footprint of kernel matrix scales roughly as $\langle\delta r\rangle^{-4}$, so decreasing the mean distance between vertices by a factor of 2 increases the memory required by a factor of roughly 16 (see Figure~\ref{fig:scaling}).
 \begin{figure}[t]
@@
     \includegraphics[width=\linewidth]{examples/images/scaling.pdf}
-    \caption{Scaling of kernel matrix size $p^2$ with mesh vertex spacing $\delta r$ for a mesh with $p$ vertices and $t$ triangles.
+    \caption{Scaling of kernel matrix size $p^2$ with mesh vertex spacing $\delta r$ for a mesh with $p$ vertices and $t$ triangles for the device shown in Figure~\ref{fig:xlarge-dz-dr}.
 (a) Typically the number of triangle $t$ in the mesh is close to twice the number of vertices $p$.

### 2021-11-30 main.tex

@@
 
-\author[PHYS,SIMES]{Logan Bishop-Van Horn}
-\author[AP,SIMES,GLAM]{Kathryn A. Moler\corref{author}}
-
-\cortext[author]{Corresponding author.\\\textit{E-mail address:} kmoler@stanford.edu}
+\author[PHYS,SIMES]{Logan Bishop-Van Horn}\ead{lbvh@stanford.edu}
+\author[AP,SIMES,GLAM]{Kathryn A. Moler\corref{kam}}\ead{kmoler@stanford.edu}
+
+\cortext[kam]{Corresponding author.}
 
@@
 Quantitative understanding of the spatial distribution of magnetic fields and Meissner screening currents in two-dimensional (2D) superconductors and mesoscopic thin film superconducting devices is critical to interpreting the results of magnetic measurements of such systems.
-Here, we introduce \SuperScreen, an open-source Python package for simulating the magnetic response of 2D superconductors to applied time-independent magnetic fields.
-Given an applied magnetic field, \SuperScreen solves for the Meissner currents and magnetic fields in and around structures composed of one or more superconducting thin films of arbitrary geometry with spatially inhomogeneous magnetic penetration depth using an efficient matrix inversion method~\cite{Brandt2004-ew, Brandt2005-wj}.
-\SuperScreen can be used to model screening effects and calculate self- and mutual-inductance in superconducting circuits, and simulate the magnetic response of inhomogeneous 2D superconductors.
+Here, we introduce \SuperScreen, an open-source Python package for simulating the response of 2D superconductors to applied time-independent magnetic fields and trapped flux.
+Given an applied magnetic field, \SuperScreen solves the 2D London equation using an efficient matrix inversion method~\cite{Brandt2004-ew, Brandt2005-wj} to obtain the Meissner currents and magnetic fields in and around structures composed of one or more superconducting thin films of arbitrary geometry with spatially inhomogeneous magnetic penetration depth.
+\SuperScreen can be used to model screening effects and calculate self- and mutual-inductance in superconducting devices, and simulate the magnetic response of inhomogeneous 2D superconductors.
 \end{abstract}
@@
 %% keywords here, in the form: keyword \sep keyword
-superconductivity\sep Meissner screening\sep thin film\sep London equation \sep inductance
+superconductivity\sep Meissner screening\sep London equation \sep inductance
 
@@
 In Section~\ref{section:examples} we demonstrate how to perform several types of simulations using \SuperScreen and compare the results to analytical solutions and experimental results.
-Finally, in Section~\ref{section:conlusion} we conclude by discussing applications, limitations, and possible extensions of the package.\footnote{Python scripts and Jupyter notebooks used to generate all figures presented below can be found in the GitHub repository accompanying this manuscript [ref.].}
+Finally, in Section~\ref{section:conlusion} we conclude by discussing applications, limitations, and possible extensions of the package.
+Python scripts and Jupyter notebooks used to generate all figures presented below can be found in the GitHub repository accompanying this manuscript [ref.].
 
@@
 
-Here we assume an out-of-plane applied magnetic field $\vec{H}_\mathrm{applied}(\pvec{r}')=H_\mathrm{z,\,\mathrm{applied}}(\pvec{r}')\hat{z}$.
+Here we assume a static out-of-plane applied magnetic field $\vec{H}_\mathrm{applied}(\pvec{r}')=H_\mathrm{z,\,\mathrm{applied}}(\pvec{r}')\hat{z}$.
 $F$ is the film area (with $g = 0$ outside of the film), and $Q_x(\vec{r},\pvec{r}')$, $Q_y(\vec{r},\pvec{r}')$, and $Q_z(\vec{r},\pvec{r}')$ are dipole kernel functions which give the respective component of the magnetic field at position $\vec{r}=(x, y, z)$ due to a dipole of unit strength at position $\pvec{r}'=(x', y', z')$:
@@
 
-In films that have holes (regions of vacuum completely surrounded by superconductor), each hole $k$ can contain a trapped flux associated a current $I_{\mathrm{circ},\,k}$ circulating around the hole.
-The applied field that would cause such a circulating current is given by Eq.~\ref{eq:applied_to_stream} if we set $g=I_{\mathrm{circ},\,k}$ for all points lying inside hole $k$:
+In films that have holes (regions of vacuum completely surrounded by superconductor), each hole $h$ can contain a trapped flux associated a current $I_{\mathrm{circ},\,h}$ circulating around the hole.
+The applied field that would cause such a circulating current is given by Eq.~\ref{eq:applied_to_stream} if we set $g=I_{\mathrm{circ},\,h}$ for all points lying inside hole $h$:
 \begin{align}
@@
     \label{eq:Heff}
-    &H_{z,\,\mathrm{eff},\,k}(\vec{r}) = \\
-    &-\int_{\mathrm{hole}\,k}[
+    &H_{z,\,\mathrm{eff},\,h}(\vec{r}) = \\
+    &-\int_{\mathrm{hole}\,h}[
         Q_z(\vec{r},\pvec{r}')-\delta(\vec{r}-\pvec{r}')\Lambda(\pvec{r}')\nabla^2
-    ] I_{\mathrm{circ},\,k} \,\mathrm{d}^2r'.   
+    ] I_{\mathrm{circ},\,h} \,\mathrm{d}^2r'.   
 \end{split}
@@
     \label{eq:Heff_sub}
-    &H_{z,\,\mathrm{applied}}(\vec{r}) - \sum_{\mathrm{holes}\,k} H_{z,\,\mathrm{eff},\,k}(\vec{r})
+    &H_{z,\,\mathrm{applied}}(\vec{r}) - \sum_{\mathrm{holes}\,h} H_{z,\,\mathrm{eff},\,h}(\vec{r})
     = \\&-\int_F\left[
@@
 \end{align}
+
+The circulating current $I_\mathrm{circ,\,h}$ is defined as the total current crossing any curve that connects the interior of the hole $h$ (where $g=I_\mathrm{circ,\,h}$ to the exterior of the film (where $g=0$)~\cite{Khapaev2001-pw,Brandt2005-wj}.
 
@@
 The \inline{superscreen.geometry} module provides functions for generating the underlying polygon vertices for simple shapes (ellipses and rectangles), which can be combined as described above to create more complicated geometries.
+
+Once the layers, films, holes, and abstract regions have been defined, one can generate the computational mesh by calling \inline{Device.make_mesh()}.
+The region that is meshed is defined by the convex hull of the union of all polygons in the device.
+Mesh generation is a two step process.
+First, an initial Delaunay mesh is created using \inline{meshpy}~\cite{Klockner}, which is a Python interface to Triangle~\cite{Shewchuk1996-va, Shewchuk}, a fast compiled 2D mesh generation tool.
+Second (and optionally), the mesh is further optimized using \inline{optimesh}~\cite{Schlomer2021-ua}.
+The goal of the mesh optimization step is to improve the ``quality'' of each triangular element in the mesh, where quality measures how close a triangle is to equilateral (quality $\leq1$, with equality for equilateral triangles).
+In practice, the more \inline{optimesh} steps are performed, the more uniform in size and spatial density the triangles in the mesh become.
+The local density of triangles in the mesh is determined by the density of vertices in the device's polygons and the total number of triangles.
+Regions where there are many polygon vertices will be meshed more densely than regions with few polygon vertices.
+If no \inline{optimesh} optimization is performed, then every polygon vertex is guaranteed to be a mesh vertex.
+See Code Block~\ref{code:device} for a demonstration of the process of creating a \inline{Device}, and Figure~\ref{fig:ring-with-slit}(a) to view the resulting geometry and mesh.
+After the mesh has been generated, the geometry-dependent matrices and vectors described in Section~\ref{section:implementation} are computed and one can begin solving models.
+
 \begin{code}
@@
 
-Once the layers, films, holes, and abstract regions have been defined, one can generate the computational mesh by calling \inline{Device.make_mesh()}.
-The region that is meshed is defined by the convex hull of the union of all polygons in the device.
-Mesh generation is a two step process.
-First, an initial Delaunay mesh is created using \inline{meshpy}~\cite{Klockner}, which is a Python interface to Triangle~\cite{Shewchuk1996-va, Shewchuk}, a fast compiled 2D mesh generation tool.
-Second (and optionally), the mesh is further optimized using \inline{optimesh}~\cite{Schlomer2021-ua}.
-The goal of the mesh optimization step is to improve the ``quality'' of each triangular element in the mesh, where quality measures how close a triangle is to equilateral (quality $\leq1$, with equality for equilateral triangles).
-In practice, the more \inline{optimesh} steps are performed, the more uniform in size and spatial density the triangles in the mesh become.
-The local density of triangles in the mesh is determined by the density of vertices in the device's polygons and the total number of triangles.
-Regions where there are many polygon vertices will be meshed more densely than regions with few polygon vertices.
-If no \inline{optimesh} optimization is performed, then every polygon vertex is guaranteed to be a mesh vertex.
-See Code Block~\ref{code:device} for a demonstration of the process of creating a \inline{Device}, and Figure~\ref{fig:ring-with-slit}(a) to view the resulting geometry and mesh.
-After the mesh has been generated, the geometry-dependent matrices and vectors described in Section~\ref{section:implementation} are computed and one can begin solving models.
-
 \subsection{Solvers}
@@
 For a structure with $N_h$ holes, we can specify $N_h$ fluxoids $\Phi^f_h$ and find the circulating currents $I_h$ by minimizing the deviation of each fluxoid from its desired value.
-For $N_h=1$, this is treated as a root-finding problem, which can be solved with typically only three calls to \inline{superscreen.solve()}.
-When $N_h>1$, it is a least-squares minimization problem with $N_h$ free parameters.
 This calculation is implemented in the \inline{superscreen.find_fluxoid_solution()} function.
+For $N_h=1$, it is treated as a root-finding problem, which can be solved with typically only three calls to \inline{superscreen.solve()}.
+For $N_h>1$, it is a least-squares minimization problem with $N_h$ free parameters.
 Code Block~\ref{code:fluxoid} demonstrates how to model a device with one or more holes, each in the $n=0$ fluxoid state, subject to a uniform applied field, and Figure~\ref{fig:fluxoid} shows the field and current distributions for a rectangular superconducting film with $\Lambda=0.25\,\um$, which has one rectangular and one elliptical hole.
@@
 The diagonals of the mutual inductance matrix are the hole self-inductances ($M_{ii}=L_i$, the self-inductance of hole $i$), and the matrix is symmetric ($M_{ij}=M_{ji}$) due to the reciprocity theorem.
-If the penetration depth of the film containing hole $i$ is $\Lambda = 0$, then no field penetrates the film and the fluxoid $\Phi^f_{S_i}$ is equal to $\Phi_i$, the flux through hole $i$.
+If the penetration depth of the film containing hole $i$ is $\Lambda = 0$, then no field penetrates the film and the fluxoid $\Phi^f_{S_i}$ is equal to $\Phi_{S_i}$, the flux through hole $i$.
 For a device with $N_h$ holes, the $N_h\times N_h$ mutual inductance matrix $\mathbf{M}$ can be computed using the $\inline{Device.mutual_inductance_matrix()}$ method.
@@
 
-In scanning superconducting quantum interference device (SQUID) susceptometry, the magnetic susceptibility of a sample is measured by bringing the sample close to a pair of superconducting loops~\cite{Gardner2001-gr, Huber2008-il, Kirtley_Kalisky_2012}.
+As an example application, we consider scanning superconducting quantum interference device (SQUID) microscopy, a technique in which a superconducting sensor is used to study superconducting or magnetic samples on micron length scales~\cite{Kirtley2016-zz}.
+In scanning SQUID susceptometry, the magnetic susceptibility of a sample is measured by bringing the sample close to a pair of superconducting loops~\cite{Gardner2001-gr, Huber2008-il, Kirtley_Kalisky_2012}.
 The first loop, called the ``pickup loop" (PL) is attached to a SQUID circuit that sensitively measures the magnetic flux threading the loop.
@@
 It is important to note that because $\lambda < d$ for all three layers, the susceptometers are not in the 2D limit in which the model described in Section~\ref{section:model} is technically valid.
-Nevertheless, as shown in Figure~\ref{fig:squid-mutuals}, the field coil - pickup loop mutual inductances, $M_\mathrm{sim}$, computed by \SuperScreen lie within the range of mutual inductances measured in real devices, $M_\mathrm{exp}$ (taken from Ref.~\cite{Kirtley2016-zz} Table 1), for all four sizes of susceptometer, indicating that variation in current density along the thickness of each film is not critical in determining the mutual inductance in this case.
-The convergence of $M_\mathrm{PL-FC}$ as a function of solver iteration (see Section~\ref{section:model:multilayer}) is shown in Figure~\ref{fig:squid-mutuals}(c).
+Nevertheless, as shown in Figure~\ref{fig:squid-mutuals}, the field coil - pickup loop mutual inductances, $M_\mathrm{sim}$, computed by \SuperScreen lie within the range of mutual inductances measured in real devices, $M_\mathrm{exp}$ (taken from Table 1 of Ref.~\cite{Kirtley2016-zz}), for all four sizes of susceptometer, indicating that variation in current density along the thickness of each film is not critical in determining the mutual inductance in this case.
+Figure~\ref{fig:squid-mutuals}(c) shows the convergence of $M_\mathrm{PL-FC}$ as a function of solver iteration (see Section~\ref{section:model:multilayer}).
 
@@
     \item{For a given relative position $(x_s, y_s)$ between the sensor and sample, simulate the sample with an applied field given by \inline{field_coil_solution.field_at_position()} to obtain \inline{sample_solution}.}
-    \item{Simulate the sensor again, this time with the applied field given by \inline{sample_solution.field_at_position()}, and evaluate the fluxoid $\Phi^f_\mathrm{PL}$ for the hole representing the sensor's pickup loop, and calculate the mutual inductance: $M_\mathrm{PL-FC}(x_s, y_s)=\Phi^f_\mathrm{PL} / I_\mathrm{FC}$.}
+    \item{Simulate the sensor again, this time with the applied field given by \inline{sample_solution.field_at_position()}, evaluate the fluxoid $\Phi^f_\mathrm{PL}$ for the hole representing the sensor's pickup loop, and calculate the mutual inductance: $M_\mathrm{PL-FC}(x_s, y_s)=\Phi^f_\mathrm{PL} / I_\mathrm{FC}$.}
 \end{enumerate}
@@
 Terminal currents can, however, be included in stream function-based models by setting appropriate boundary conditions~\cite{Khapaev1997-kw,Khapaev2001-xq,Khapaev2001-pw,Muller2021-ci}.
+An extension to the model described above that treats the magnetic response of a superconducting ring interrupted by two Josephson junctions (i.e.
+a SQUID) with trapped vortices and terminal currents is given in Ref.~\cite{Clem2005-ye}.
 Finally, care should be taken to ensure that for a given model the mesh is of sufficient density that, to within the desired precision, the results of simulations do not depend on mesh size (see \ref{appendix:numerics}).
@@
 Potential improvements to \SuperScreen include: support for terminal currents as discussed above, automated determination of solution convergence for models with multiple layers, more sophisticated mesh generation (e.g.
-automated local mesh refinement based on device geometry or adaptive mesh refinement based on solution convergence), integration with standard integrated circuit layout software/file formats, and further optimization for memory and CPU efficiency.
+automated local mesh refinement based on device geometry or adaptive mesh refinement based on solution convergence), integration with standard integrated circuit layout software or file formats, and further optimization for memory and CPU efficiency.
 
@@
 (a) Typically the number of triangle $t$ in the mesh is close to twice the number of vertices $p$.
-(b) Normalized histograms of vertex distances $\delta r$ (colors correspond to the points in (a)).
+(b) Normalized histograms of vertex distances $\delta r$.
 The histogram bins are given by \inline{numpy.linspace(0.15, 0.65, 201)}.
@@
 (d).
-The size of each $p\times p$ kernel matrix (of which where are $\binom{L}{2}$ for a device with $L$ layers) scales roughly as $\langle\delta r\rangle^{-4}$.}
+The size of each $p\times p$ kernel matrix (of which where are $\binom{L}{2}$ for a device with $L$ layers) scales roughly as $\langle\delta r\rangle^{-4}$.
+Note that in each row the colors correspond to the number of vertices $p$ in the mesh, as indicated in (a), with mesh size increasing from dark to light colors.}
     \label{fig:scaling}

### 2021-12-03 main.tex
Updates from Overleaf

@@
 \author[PHYS,SIMES]{Logan Bishop-Van Horn}\ead{lbvh@stanford.edu}
-\author[AP,SIMES,GLAM]{Kathryn A. Moler\corref{kam}}\ead{kmoler@stanford.edu}
+\author[PHYS,AP,SIMES,GLAM]{Kathryn A. Moler\corref{kam}}\ead{kmoler@stanford.edu}
 
@@
 
-A convenient method for solving this problem was introduced by Brandt and Clem in Ref.~\cite{Brandt2004-ew}, expanded by Brandt in Ref.~\cite{Brandt2005-wj}, and subsequently used to model the magnetic response of scanning Superconducting Quantum Interference Device (SQUID) susceptometers~\cite{Kirtley2016-zz, Kirtley2016-gt}.
+A convenient method for solving this problem was introduced by Brandt and Clem in Ref.~\cite{Brandt2004-ew}, expanded by Brandt in Ref.~\cite{Brandt2005-wj}, and subsequently used to model the magnetic response of scanning SQUID susceptometers~\cite{Kirtley2016-zz, Kirtley2016-gt}.
 In the London model of superconductivity, the magnetic field $\vec{H}(\vec{r})$ and 3D current density $\vec{j}(\vec{r})$ in a superconductor with London penetration depth $\lambda(\vec{r})$ obey the second London equation:
@@
     \label{eq:applied_to_stream_vortices}
-    & H_{z,\,\mathrm{applied}}(\vec{r}) - \sum_{\mathrm{holes}\,k} H_{z,\,\mathrm{eff},\,k}(\vec{r}) - \sum_{\mathrm{vortices}\,v}\frac{\Phi_v}{\mu_0}\delta(\vec{r}-\vec{r}_v)
+    & H_{z,\,\mathrm{applied}}(\vec{r}) - \sum_{\mathrm{holes}\,h} H_{z,\,\mathrm{eff},\,h}(\vec{r}) - \sum_{\mathrm{vortices}\,v}\frac{\Phi_v}{\mu_0}\delta(\vec{r}-\vec{r}_v)
     = \\
@@
     \label{eq:Heff_sub_num}
-     \mathbf{h}_{z,\,\mathrm{applied}} - \sum_{\mathrm{holes}\, k}\mathbf{h}_{z,\,\mathrm{eff},\,k} = -(\mathbf{Q}\cdot\mathbf{w}^T-\mathbf{\nabla}^2\cdot \mathbf{\Lambda}^T)\mathbf{g},
+     \mathbf{h}_{z,\,\mathrm{applied}} - \sum_{\mathrm{holes}\, h}\mathbf{h}_{z,\,\mathrm{eff},\,h} = -(\mathbf{Q}\cdot\mathbf{w}^T-\mathbf{\nabla}^2\cdot \mathbf{\Lambda}^T)\mathbf{g},
 \end{equation}
@@
         -\mathbf{K}
-        \left(\mathbf{h}_{z,\,\mathrm{applied}} - \sum_{\mathrm{holes}\,k}\mathbf{h}_{z,\,\mathrm{eff},\,k}\right)
+        \left(\mathbf{h}_{z,\,\mathrm{applied}} - \sum_{\mathrm{holes}\,h}\mathbf{h}_{z,\,\mathrm{eff},\,h}\right)
             & \text{inside the film}\\
-        I_{\mathrm{circ},\,k}
-            & \text{inside hole }k\\
+        I_{\mathrm{circ},\,h}
+            & \text{inside hole }h\\
         0
@@
 \end{tabular}
-\caption{Methods for combining \inline{superscreen.Polygon} objects, along with their corresponding set-theoretic and boolean logic operations.
-The vertices of \inline{polygonA} lie in set $A$ and the vertices of \inline{polygonB} lie in the set $B$.
-The object \inline{polygonB} can be a \inline{superscreen.Polygon}, an $n\times 2$ \inline{numpy} array of vertex coordinates, or a \inline{LineString}, \inline{LinearRing}, or \inline{Polygon} from the \inline{shapely} package.}
+\caption{Methods for combining \inline{superscreen.Polygon} objects, along with their corresponding set-theoretic and boolean logic operations.}
 \label{table:polygon}
@@
 Table~\ref{table:polygon} shows the four methods available for combining a \inline{supercreen.Polygon} instance \inline{polygonA}, whose vertices lie in set $A$, with a polygon \inline{polygonB}, whose vertices lie in set $B$.
-Note that \inline{polygonB} can be another \inline{superscreen.Polygon}, an $n\times 2$ \inline{numpy} array of vertex coordinates, or one of several compatible types of objects from the \inline{shapely} package.
-
-In addition to superconducting films and holes, one may define ``abstract regions,'' which are polygons that need not correspond to a physical feature in the structure, but will still be meshed.
+Note that \inline{polygonB} can be a \inline{superscreen.Polygon}, an $n\times 2$ \inline{numpy} array of vertex coordinates, or a \inline{LineString}, \inline{LinearRing}, or \inline{Polygon} from the \inline{shapely} package~\cite{shapely}.
+
+In addition to superconducting films and holes, one may define ``abstract regions,'' which are polygons that do not necessarily correspond to a physical feature in the structure, but will still be meshed.
 Abstract regions can be used to define a ``bounding box" around a structure to be modeled, or to locally increase the density of the computational mesh in a given region.
@@
 If no \inline{optimesh} optimization is performed, then every polygon vertex is guaranteed to be a mesh vertex.
-See Code Block~\ref{code:device} for a demonstration of the process of creating a \inline{Device}, and Figure~\ref{fig:ring-with-slit}(a) to view the resulting geometry and mesh.
+See Code Block~\ref{code:device} for a demonstration of the process of creating a \inline{Device}, and Figure~\ref{fig:ring-with-slit}({\bf a}) to view the resulting geometry and mesh.
 After the mesh has been generated, the geometry-dependent matrices and vectors described in Section~\ref{section:implementation} are computed and one can begin solving models.
@@
     \caption{The output of Code Block~\ref{code:device}: Meissner screening of a uniform $10\,\mu\mathrm{T}$ out-of-plane field by a ring with inner diameter $1\,\um$, outer diameter $3\,\um$, and effective penetration depth $\Lambda=1\,\um$, interrupted by a slit of width $0.25\,\um$.
-(a) Plot of the boundary of the ring (blue), circular bounding box (orange), and the computational mesh (gray), generated with \inline{Device.plot()}.
-(b) The current density $\vec{J}$ in the ring, generated with \inline{Solution.plot_currents()}.
-(c) The $z$-component of the magnetic field $\mu_0H_z$ evaluated at the plane of the ring, generated with \inline{Solution.plot_fields()}.
-(d) The $z$-component of the magnetic field evaluated $z=0.5\,\um$ above the ring (generated using \inline{Solution.plot_field_at_positions()}).}
+({\bf a}) Plot of the boundary of the ring (blue), circular bounding box (orange), and the computational mesh (gray), generated with \inline{Device.plot()}.
+({\bf b}) The current density $\vec{J}$ in the ring, generated with \inline{Solution.plot_currents()}.
+({\bf c}) The $z$-component of the magnetic field $\mu_0H_z$ evaluated at the plane of the ring, generated with \inline{Solution.plot_fields()}.
+({\bf d}) The $z$-component of the magnetic field evaluated $z=0.5\,\um$ above the ring (generated using \inline{Solution.plot_field_at_positions()}).}
     \label{fig:ring-with-slit}
@@
 The least-squares minimization for the model shown in Figure~\ref{fig:fluxoid}, with $N_h=2$, required 18 total calls to \inline{superscreen.solve()}.
+It is important to note that while \SuperScreen can calculate the field and current distributions or a given fluxoid state, the model does not capture transitions between fluxoid states.
 
@@
     \includegraphics[width=\linewidth]{examples/images/fluxoid.pdf}
-    \caption{(a) Magnetic field and (b) current density distributions generated by Code Block~\ref{code:fluxoid} for a rectangular superconducting film with $\Lambda=0.25\,\um$, which has one rectangular and one elliptical hole.
+    \caption{({\bf a}) Magnetic field and ({\bf b}) current density distributions generated by Code Block~\ref{code:fluxoid} for a rectangular superconducting film with $\Lambda=0.25\,\um$, which has one rectangular and one elliptical hole.
 The film is subject to a uniform applied out-of-plane field of 1 mT, and both holes are set to be in the $n=0$ fluxoid (i.e.
@@
 The field distributions generated by \SuperScreen in the presence of vortices as described in Sections~\ref{section:model:vortices} and~\ref{section:implementation} agree to within a few percent with the distributions obtained using this Fourier transform method, as demonstrated in Figure~\ref{fig:pearl}(c-e).
-Figure~\ref{fig:pearl}(e) shows the fluxoid for a circular region $S$ with radius $r=1\,\um$ enclosing a Pearl vortex trapped in a film as a function of the film's effective penetration depth, $\Lambda$.
+Figure~\ref{fig:pearl}({\bf e}) shows the fluxoid for a circular region $S$ with radius $r=1\,\um$ enclosing a Pearl vortex trapped in a film as a function of the film's effective penetration depth, $\Lambda$.
 When $\Lambda=0$, the screening currents decay very quickly away from the center of the vortex, so the ``supercurrent part'' of the $\Phi^f_S$ vanishes.
@@
 Here, we model a vortex trapped at the center of a square superconducting film lying in the $x-y$ plane with side length $20\,\um$ as a function of the film's effective penetration depth, $\Lambda$.
-(a) Cross section along the $x$-axis of the out-of-plane magnetic field $\mu_0H_z$ from the vortex, evaluated at a vertical distance $z=1\,\um$ above the film.
+({\bf a}) Cross section along the $x$-axis of the out-of-plane magnetic field $\mu_0H_z$ from the vortex, evaluated at a vertical distance $z=1\,\um$ above the film.
 The inset shows the vortex field profile for $\Lambda=0\,\um$ evaluated at $z=1\,\um$, with a dashed white line indicating the cross-section axis.
-(b) Percentage difference between the $\mu_0H_z$ calculated with \SuperScreen and the Fourier transform method for the $x$-axis cut shown in (a).
-(c) Cross-section along the $z$-axis of $\mu_0H_z$ directly above the center of the vortex (logarithmic $y$ axis scale).
-(d) Percentage difference between the $\mu_0H_z$ calculated with \SuperScreen and the Fourier transform method for the $z$-axis cut shown in (c).
-In (a) and (c), the results from \SuperScreen are shown as open circles and the results from the Fourier transform method are shown as solid lines.
-(e) The fluxoid $\Phi_S^f$ for a circular region in the film with radius $r=1\,\um$ centered on the vortex core.
+({\bf b}) Percentage difference between the $\mu_0H_z$ calculated with \SuperScreen and the Fourier transform method for the $x$-axis cut shown in ({\bf a}).
+({\bf c}) Cross-section along the $z$-axis of $\mu_0H_z$ directly above the center of the vortex (logarithmic $y$ axis scale).
+({\bf d}) Percentage difference between the $\mu_0H_z$ calculated with \SuperScreen and the Fourier transform method for the $z$-axis cut shown in ({\bf c}).
+In ({\bf a}) and ({\bf c}), the results from \SuperScreen are shown as open circles and the results from the Fourier transform method are shown as solid lines.
+({\bf e}) The fluxoid $\Phi_S^f$ for a circular region in the film with radius $r=1\,\um$ centered on the vortex core.
 As $\Lambda$ increases, so to does the supercurrent contribution to the fluxoid.
-(f) Error in the total simulated fluxoid relative to $\Phi_0$: error = $(\Phi_S^f(\Lambda) - \Phi_0) / \Phi_0$.}
+({\bf f}) Error in the total simulated fluxoid relative to $\Phi_0$: error = $(\Phi_S^f(\Lambda) - \Phi_0) / \Phi_0$.}
     \label{fig:pearl}
@@
 The diagonals of the mutual inductance matrix are the hole self-inductances ($M_{ii}=L_i$, the self-inductance of hole $i$), and the matrix is symmetric ($M_{ij}=M_{ji}$) due to the reciprocity theorem.
-If the penetration depth of the film containing hole $i$ is $\Lambda = 0$, then no field penetrates the film and the fluxoid $\Phi^f_{S_i}$ is equal to $\Phi_{S_i}$, the flux through hole $i$.
+In this context, the flux and supercurrent parts of the fluxoid correspond to the geometric and kinetic inductance respectively~\cite{Brandt2004-ew}.
+If the penetration depth of the film containing hole $i$ is $\Lambda = 0$, then no field penetrates the film, the fluxoid $\Phi^f_{S_i}$ is equal to the flux through hole $i$, and the total inductance is equal to the geometric inductance.
 For a device with $N_h$ holes, the $N_h\times N_h$ mutual inductance matrix $\mathbf{M}$ can be computed using the $\inline{Device.mutual_inductance_matrix()}$ method.
@@
     \caption{Calculating SQUID susceptometer mutual inductance, defined as the fluxoid induced in the SQUID pickup loop per unit current flowing in the field coil: $M_\mathrm{PL-FC}=\Phi^f_\mathrm{PL} / I_\mathrm{FC}$.
-Top row (a): Schematics of \SuperScreen models for the field coil and pickup loop region of four sizes of scanning SQUID susceptometer (generated using \inline{Device.draw()}) with pickup loop inner radii ranging from $0.1\,\um$ (``Small'') to $3\,\um$ (``X-Large'').
-The wiring layers BE, W1, and W2 are shown in blue, orange, and green respectively.
-Middle row (b): Simulated magnetic field $\mu_0H_z$ evaluated at the plane of layer W1, which contains the pickup loop, normalized by the current $I_\mathrm{FC}$ flowing in the field coil (which is located in layer BE).
-Bottom row (c): Convergence of the four models, defined as the fractional change in mutual inductance between subsequent iterations $i$.
+Top row ({\bf a}): Schematics of \SuperScreen models for the field coil and pickup loop region of four sizes of scanning SQUID susceptometer (generated using \inline{Device.draw()}) with pickup loop inner radii ranging from $0.1\,\um$ (``Small'') to $3\,\um$ (``X-Large'').
+Middle row ({\bf b}): Simulated magnetic field $\mu_0H_z$ evaluated at the plane of layer W1, which contains the pickup loop, normalized by the current $I_\mathrm{FC}$ flowing in the field coil (which is located in layer BE).
+Bottom row ({\bf c}): Convergence of the four models, defined as the fractional change in mutual inductance between subsequent iterations $i$.
 For all four models, the simulated mutual inductance, $M_\mathrm{sim}$, falls within the range of mutual inductance values measured in real devices, $M_\mathrm{exp}$, which were reported in Table 1 of Ref.~\cite{Kirtley2016-zz}.
@@
 
-As an example application, we consider scanning superconducting quantum interference device (SQUID) microscopy, a technique in which a superconducting sensor is used to study superconducting or magnetic samples on micron length scales~\cite{Kirtley2016-zz}.
+As an example application, we consider scanning SQUID microscopy, a technique in which a superconducting sensor is used to study superconducting or magnetic samples on micron length scales~\cite{Kirtley2016-zz}.
 In scanning SQUID susceptometry, the magnetic susceptibility of a sample is measured by bringing the sample close to a pair of superconducting loops~\cite{Gardner2001-gr, Huber2008-il, Kirtley_Kalisky_2012}.
@@
     \caption{Simulation of a scanning SQUID susceptometry measurement.
-(a) Geometry of the \inline{Device} representing the ``sensor'' SQUID.
-(b) Geometry of the \inline{Device} representing the ``sample'' SQUID.
-(c) Susceptibility of the sample SQUID measured at a temperature of 4.0 K.
-(d) Simulated susceptibility, calculcated using the method described in Section~\ref{section:examples:scanning-squid}.
+({\bf a}) Geometry of the \inline{Device} representing the ``sensor'' SQUID.
+({\bf b}) Geometry of the \inline{Device} representing the ``sample'' SQUID.
+({\bf c}) Susceptibility of the sample SQUID measured at a temperature of 4.0 K.
+({\bf d}) Simulated susceptibility, calculcated using the method described in Section~\ref{section:examples:scanning-squid}.
 The pickup loop of the sample, which in reality is connected to a SQUID circuit that has a non-linear magnetic response, is modeled as a continuous superconducting loop in the zero-fluxoid (i.e.
 Meissner) state.
-The susceptibility signal is defined as $M_\text{PL-FC} - M_\text{PL-FC, no sample}$, where $M_\text{PL-FC, no sample}\approx163\,\Phi_0/\mathrm{A}$ (see Figure~\ref{fig:squid-mutuals}(a), second column).
-The scale bar in (a) applies to all four panels.}
+The susceptibility signal is defined as $M_\text{PL-FC} - M_\text{PL-FC, no sample}$, where $M_\text{PL-FC, no sample}\approx163\,\Phi_0/\mathrm{A}$ (see Figure~\ref{fig:squid-mutuals}({\bf a}), second column).
+The scale bar in ({\bf a}) applies to all four panels.}
     \label{fig:squid-susc}
@@
 
-Figure~\ref{fig:squid-mutuals}(a) shows \SuperScreen \inline{Device} models of the field coil and pickup loop region of four types of real SQUID susceptometers, with geometry taken from the layout artwork (GDS) files.
+Figure~\ref{fig:squid-mutuals}({\bf a}) shows \SuperScreen \inline{Device} models of the field coil and pickup loop region of four types of real SQUID susceptometers, with geometry taken from the layout artwork (GDS) files.
 In addition to the field coil and pickup loop, there are superconducting shields that limit the amount of magnetic flux that can penetrate the leads connecting the loops to the rest of the circuit (the rest of the circuit is not modeled).
@@
 Nevertheless, as shown in Figure~\ref{fig:squid-mutuals}, the field coil - pickup loop mutual inductances, $M_\mathrm{sim}$, computed by \SuperScreen lie within the range of mutual inductances measured in real devices, $M_\mathrm{exp}$ (taken from Table 1 of Ref.~\cite{Kirtley2016-zz}), for all four sizes of susceptometer, indicating that variation in current density along the thickness of each film is not critical in determining the mutual inductance in this case.
-Figure~\ref{fig:squid-mutuals}(c) shows the convergence of $M_\mathrm{PL-FC}$ as a function of solver iteration (see Section~\ref{section:model:multilayer}).
+Figure~\ref{fig:squid-mutuals}({\bf c}) shows the convergence of $M_\mathrm{PL-FC}$ as a function of solver iteration (see Section~\ref{section:model:multilayer}).
 
@@
 Top row (a - c): The fluxoid $\Phi^f_S$ vanishes for all simply-connected regions containing no vortices.
-The errors in (c) are given by $|\Phi^f_S / \Phi^f_{S,\,\text{(flux part)}}|$.
+The errors in ({\bf c}) are given by $|\Phi^f_S / \Phi^f_{S,\,\text{(flux part)}}|$.
 Middle row (d - f): For simply-connected regions containing a set of vortices $v$, each carrying flux $\Phi_v$, the fluxoid is given by $\sum_v\Phi_v$.
-In this case, the body of the square ring contains both ``positive'' ($\Phi_v=\Phi_0$, counter-clockwise circulating current) and ``negative'' ($\Phi_v=-\Phi_0$, clockwise circulating current) vortices, which appear in (e) as yellow and blue dots respectively.
-The expected value for the fluxoid for each region $S$ given in units of $\Phi_0$ by (number of yellow vortices lying inside $S$) - (number of blue vortices lying inside $S$), and the errors in (f) are reported relative to this expected value.
+In this case, the body of the square ring contains both ``positive'' ($\Phi_v=\Phi_0$, counter-clockwise circulating current) and ``negative'' ($\Phi_v=-\Phi_0$, clockwise circulating current) vortices, which appear in ({\bf e}) as yellow and blue dots respectively.
+The expected value for the fluxoid for each region $S$ given in units of $\Phi_0$ by (number of yellow vortices lying inside $S$) - (number of blue vortices lying inside $S$), and the errors in ({\bf f}) are reported relative to this expected value.
 Bottom row (g - i): Fluxoid path independence for the $n=0$ fluxoid state, shown here for both circular ($S = 0, 1, 2$) and square ($S=3, 4, 5$) paths.
@@
     \caption{The output of Code Block~\ref{code:inhomogeneous}: Meissner screening of a uniform applied field of $10\,\mu\mathrm{T}$ by a ring with a slit in a superconducting film with inhomogeneous effective penetration depth $\Lambda(x, y)$.
-(a) The inhomogeneous effective penetration depth $\Lambda(x, y)$, with the ring's outline overlaid in orange.
-(b) The current density $\vec{J}$ in the ring, generated with \inline{Solution.plot_currents()}.
-(c) The $z$-component of the magnetic field $\mu_0H_z$ evaluated at the plane of the ring, generated with \inline{Solution.plot_fields()}.
-(d) The $z$-component of the magnetic field evaluated $z=0.5\,\um$ above the ring (generated using \inline{Solution.plot_field_at_positions()}).}
+({\bf a}) The inhomogeneous effective penetration depth $\Lambda(x, y)$, with the ring's outline overlaid in orange.
+({\bf b}) The current density $\vec{J}$ in the ring, generated with \inline{Solution.plot_currents()}.
+({\bf c}) The $z$-component of the magnetic field $\mu_0H_z$ evaluated at the plane of the ring, generated with \inline{Solution.plot_fields()}.
+({\bf d}) The $z$-component of the magnetic field evaluated $z=0.5\,\um$ above the ring (generated using \inline{Solution.plot_field_at_positions()}).}
     \label{fig:inhomogeneous}
@@
 However, the discretized version of Eq.~\ref{eq:hz-from-kernel}, in which the double integral over the film area $F$ is replaced by a sum over triangular mesh elements, is only valid if $\delta z = z-z'$, the vertical distance between the film and the point at which the field is being evaluated, is larger than the typical distance $\delta r$ between vertices in the mesh representing the film.
-For $z-z'=\delta z\lesssim\delta r$, the field $H_z(\vec{r})$ resembles that of a discrete set of isolated dipoles located at the mesh vertex positions, rather than that of a continuous sheet of current (see Figure~\ref{fig:xlarge-dz-dr}(b)).
+For $z-z'=\delta z\lesssim\delta r$, the field $H_z(\vec{r})$ resembles that of a discrete set of isolated dipoles located at the mesh vertex positions, rather than that of a continuous sheet of current (see Figure~\ref{fig:xlarge-dz-dr}({\bf b})).
 This can lead to unphysical results when evaluating the field very close to the surface of a film (for example using \inline{Solution.field_at_position()}), or when solving models involving multi-layer structures where the vertical spacing between layers is much smaller than the lateral extent of the films, in which case the iterative calculation (Section~\ref{section:model:multilayer}) may not converge.
@@
     \caption{\SuperScreen results may be unreliable for multi-layer models where the spacing between layers is smaller than the typical vertex-to-vertex distance, $\delta r$.
-(a) Field coil - pickup loop mutual inductance for the largest SQUID suscepometer modeled in Section~\ref{section:examples:scanning-squid} as a function of the minimum vertical spacing between layers, $\delta z$.
+({\bf a}) Field coil - pickup loop mutual inductance for the largest SQUID suscepometer modeled in Section~\ref{section:examples:scanning-squid} as a function of the minimum vertical spacing between layers, $\delta z$.
 The simulated mutual inductance is shown with blue circles, and a histogram of the mesh vertex-to-vertex distances $\delta r$ is shown in orange (arb.
@@
 When $\delta z\lesssim\delta r$, the model significantly overestimates the mutual inductance.
-(b) and (c): Out-of-plane magnetic field $\mu_0H_z$ evaluated at the plane of the pickup loop (W1 layer) for (b) the nominal layer spacing with $\delta z<\delta 2$ (indicated with a black $\times$ in (a)) and (c) $\delta z > \delta r$ (indicated with a black $+$ in (a)).
+({\bf b}) and ({\bf c}): Out-of-plane magnetic field $\mu_0H_z$ evaluated at the plane of the pickup loop (W1 layer) for ({\bf b}) the nominal layer spacing with $\delta z<\delta 2$ (indicated with a black $\times$ in ({\bf a})) and ({\bf c}) $\delta z > \delta r$ (indicated with a black $+$ in ({\bf a})).
 For $\delta r\lesssim\delta z$, the magnet field calculated using Eq.~\ref{eq:hz-from-kernel} resembles that of a discrete set of isolated dipoles rather than a continuous sheet of current.}
@@
     \caption{Scaling of kernel matrix size $p^2$ with mesh vertex spacing $\delta r$ for a mesh with $p$ vertices and $t$ triangles for the device shown in Figure~\ref{fig:xlarge-dz-dr}.
-(a) Typically the number of triangle $t$ in the mesh is close to twice the number of vertices $p$.
-(b) Normalized histograms of vertex distances $\delta r$.
+({\bf a}) Typically the number of triangle $t$ in the mesh is close to twice the number of vertices $p$.
+({\bf b}) Normalized histograms of vertex distances $\delta r$.
 The histogram bins are given by \inline{numpy.linspace(0.15, 0.65, 201)}.
-(c) The mean vertex-to-vertex distance $\langle\delta r\rangle$ scales roughly as $p^{-1/2}$.
-(d).
+({\bf c}) The mean vertex-to-vertex distance $\langle\delta r\rangle$ scales roughly as $p^{-1/2}$.
+({\bf d}).
 The size of each $p\times p$ kernel matrix (of which where are $\binom{L}{2}$ for a device with $L$ layers) scales roughly as $\langle\delta r\rangle^{-4}$.
-Note that in each row the colors correspond to the number of vertices $p$ in the mesh, as indicated in (a), with mesh size increasing from dark to light colors.}
+Note that in each row the colors correspond to the number of vertices $p$ in the mesh, as indicated in ({\bf a}), with mesh size increasing from dark to light colors.}
     \label{fig:scaling}

### 2021-12-03 main.tex

@@
 ({\bf a}) Cross section along the $x$-axis of the out-of-plane magnetic field $\mu_0H_z$ from the vortex, evaluated at a vertical distance $z=1\,\um$ above the film.
-The inset shows the vortex field profile for $\Lambda=0\,\um$ evaluated at $z=1\,\um$, with a dashed white line indicating the cross-section axis.
+The left inset shows the current density in the plane for film for the $\Lambda=2\,\um$ case, and the right inset shows the corresponding magnetic field profile for evaluated at $z=1\,\um$, with a dashed white line indicating the cross-section axis.
 ({\bf b}) Percentage difference between the $\mu_0H_z$ calculated with \SuperScreen and the Fourier transform method for the $x$-axis cut shown in ({\bf a}).

### 2021-12-03 main.tex
Updates from Overleaf

--- 2021-12-03 main.tex
@@
 ({\bf a}) Cross section along the $x$-axis of the out-of-plane magnetic field $\mu_0H_z$ from the vortex, evaluated at a vertical distance $z=1\,\um$ above the film.
-The inset shows the vortex field profile for $\Lambda=0\,\um$ evaluated at $z=1\,\um$, with a dashed white line indicating the cross-section axis.
+The left inset shows the current density in the plane for film for $\Lambda=2\,\um$, and the right inset shows the corresponding magnetic field evaluated at $z=1\,\um$, with a dashed white line indicating the cross-section axis.
 ({\bf b}) Percentage difference between the $\mu_0H_z$ calculated with \SuperScreen and the Fourier transform method for the $x$-axis cut shown in ({\bf a}).

### 2022-01-18 main.tex
Updates from Overleaf

@@
 
-\SuperScreen has several important dependencies beyond the Python standard library: \inline{numpy}~\cite{Harris2020-xv} and \inline{scipy}~\cite{Virtanen2020-zz} for numerics, \inline{matplotlib}~\cite{Hunter2007-il} for visualization, \inline{pint}~\cite{Grecco} for handling physical units, \inline{shapely}~\cite{shapely} for creating and manipulating device geometries, \inline{meshpy}~\cite{Klockner, Shewchuk, Shewchuk1996-va} and \inline{optimesh}~\cite{Schlomer2021-ua} for mesh generation, and \inline{ray}~\cite{Moritz2018-mt,ray-docs} for parallel processing with shared memory (see~\ref{section:parallel}).
+\SuperScreen has several important dependencies beyond the Python standard library: \inline{numpy}~\cite{Harris2020-xv} and \inline{scipy}~\cite{Virtanen2020-zz} for numerics, \inline{matplotlib}~\cite{Hunter2007-il} for visualization, \inline{pint}~\cite{Grecco} for handling physical units, \inline{shapely}~\cite{shapely} for creating and manipulating device geometries, \inline{meshpy}~\cite{Klockner, Shewchuk, Shewchuk1996-va} and \inline{optimesh}~\cite{Schlomer2021-ua} for mesh generation, and \inline{Ray}~\cite{Moritz2018-mt,ray-docs} for parallel processing with shared memory (see~\ref{section:parallel}).
 
@@
 A \inline{Vortex} object specifies the $x,y$ position for the vortex core, the name of the superconducting layer in which the vortex is pinned, and the number of flux quanta $\Phi_0$ contained in the vortex (which is 1 by default).
-The field distributions generated by \SuperScreen in the presence of vortices as described in Sections~\ref{section:model:vortices} and~\ref{section:implementation} agree to within a few percent with the distributions obtained using this Fourier transform method, as demonstrated in Figure~\ref{fig:pearl}(c-e).
+The field distributions generated by \SuperScreen in the presence of vortices as described in Sections~\ref{section:model:vortices} and~\ref{section:implementation} agree to within a few percent with the distributions obtained using this Fourier transform method, as demonstrated in Figure~\ref{fig:pearl}.
 Figure~\ref{fig:pearl}({\bf e}) shows the fluxoid for a circular region $S$ with radius $r=1\,\um$ enclosing a Pearl vortex trapped in a film as a function of the film's effective penetration depth, $\Lambda$.
@@
 As discussed above, one can solve many models involving the same \inline{Device} in parallel across multiple CPUs using the \inline{superscreen.solve_many()} function.
-The recommended method for parallel processing is using \inline{ray}, a library for distributed computing using shared memory~\cite{Moritz2018-mt}.
-Note that at the time of writing, \inline{ray} support for Windows is experimental and under active development.
-\SuperScreen also supports parallel processing using the \inline{multiprocessing} module from the Python standard library, however this is generally less efficient than \inline{ray} in this application.
+There are two methods available for process-based parallelism in \SuperScreen: \inline{parallel_method="multiprocessing"}, which uses the \inline{multiprocessing} package from the Python standard library, and \inline{parallel_method="ray"}, which uses the third-party distributed computing framework \inline{Ray}\footnote{Note that at the time of writing, \inline{Ray} support for Windows is experimental and under active development.}~\cite{Moritz2018-mt,ray-docs}.
+Both approaches utilize shared memory so that only a single copy is made of the large arrays required to solve a \inline{Device} (the mesh, kernel matrix $\mathbf{Q}$, Laplace operator $\mathbf{\nabla}^2$, etc.), rather than \inline{num_cpus} copies, where \inline{num_cpus} is the number of worker processes.
+
+\begin{code-onecol}
+\begin{minted}[fontsize=\small]{python}
+parallel_method = "multiprocessing"
+# parallel_method = "ray"
+
+# Specify number of worker processes:
+num_cpus = 4
+# Or automatically use all
+# available physical CPUs:
+# num_cpus = None
+
+_ = superscreen.solve_many(
+    device=device,
+    parallel_method=parallel_method,
+    num_cpus=num_cpus,
+    **solve_kwargs,
+)
+\end{minted}
+\captionof{listing}{Utilizing process-based parallelism in \SuperScreen given a \inline{superscreen.Device} and solver options stored in a dictionary \inline{solve_kwargs}.}
+\label{code:parallel}
+\end{code-onecol}
+
+There are three ways to invoke \inline{Ray} from \SuperScreen when running on a single machine, e.g.
+a multi-core CPU.
+The first is to simply pass the keyword argument \inline{parallel_method="ray"} when calling \inline{solve_many()} (see Code Block~\ref{code:parallel}).
+This will automatically create a \inline{Ray} cluster using (by default) all available physical CPU cores, solve the models in parallel, and then shut down the cluster before returning.
+The second method is to manually create a \inline{Ray} cluster using the \inline{Ray} Python application programming interface (API) prior to calling \inline{solve_many(..., parallel_method="ray")}, as demonstrated in Code Block~\ref{code:ray-python}.
+The third method is to start a \inline{Ray} cluster using the command line interface (CLI), then connect to the existing cluster using the Python API prior to calling \inline{solve_many(..., parallel_method="ray")}, as demonstrated in Code Block~\ref{code:ray-cli}.
+One of the latter two methods should be used for finer control over the \inline{Ray} cluster.
+For example, if calling \inline{solve_many()} many times in a single session, one can use these methods to avoid the overhead of starting and stopping a \inline{Ray} cluster multiple times.
+
+Running \inline{superscreen.solve_many()} in parallel across multiple nodes in a computing cluster is a simple extension to the method outlined in Code Block~\ref{code:ray-cli}, although the specifics depend upon the infrastructure of the cluster, e.g.
+job management software.
+See the ``Multi-Node Ray" section of the \inline{Ray} documentation for more details~\cite{ray-docs}.
 
@@
 \begin{minted}[fontsize=\small]{python}
-# Assume that we have already created a Device and put all
-# other inputs to superscreen.solve_many() into a dictionary
-# called other_kwargs.
-
+# Assume that we have already created a Device and put all other inputs
+# to superscreen.solve_many() into a dictionary called other_kwargs.
 import psutil
@@
 )
-# Shutdown the ray cluster
+# Potentially call solve_many() again using the same ray cluster...
+# Finally, shutdown the ray cluster
 ray.shutdown()
 \end{minted}
-\captionof{listing}{Starting and stopping \inline{ray} outside of \inline{superscreen.solve_many()} using the Python API.
-See the ``API and Package Reference" section of the \inline{ray} documentation for additional options in \inline{ray.init()}~\cite{ray-docs}.}
+\captionof{listing}{Starting and stopping \inline{Ray} outside of \inline{superscreen.solve_many()} using the Python API.
+See the ``API and Package Reference" section of the \inline{Ray} documentation for additional options in \inline{ray.init()}~\cite{ray-docs}.}
 \label{code:ray-python}
@@
 \begin{code}
+\begin{minipage}{1.0\textwidth}
 \begin{minted}[fontsize=\small]{bash}
@@
 \end{minted}
+
 \begin{minted}[fontsize=\small]{python}
-# Assume that we have already created a Device and put all
-# other inputs to superscreen.solve_many() into a dictionary
-# called other_kwargs.
+# Assume that we have already created a Device and put all other inputs
+# to superscreen.solve_many() into a dictionary called other_kwargs.
 import ray
@@
 )
+# Potentially call solve_many() again using the same ray cluster...
 \end{minted}
+
 \begin{minted}[fontsize=\small]{bash}
@@
 \end{minted}
-\captionof{listing}{Starting and stopping \inline{ray} outside of \inline{superscreen.solve_many()} using the command line interface.
-See the \inline{ray} documentation for additional options in \inline{ray start}~\cite{ray-docs}.}
+\captionof{listing}{Starting and stopping \inline{Ray} outside of \inline{superscreen.solve_many()} using the command line interface.
+See the \inline{Ray} documentation for additional options in \inline{ray start}~\cite{ray-docs}.}
 \label{code:ray-cli}
+\end{minipage}
 \end{code}
-
-There are three ways to invoke \inline{ray} from \SuperScreen when running on a single machine, e.g.
-a multi-core CPU.
-The first is to simply pass the keyword argument \inline{parallel_method="ray"} when calling \inline{solve_many()}.
-This will automatically create a \inline{ray} cluster using all available physical CPU cores, solve the models in parallel, and then shut down the cluster before returning.
-The second method is to manually create a \inline{ray} cluster using the \inline{ray} Python application programming interface (API) prior to calling \inline{solve_many(..., parallel_method="ray")}, as demonstrated in Code Block~\ref{code:ray-python}.
-The third method is to start a \inline{ray} cluster using the command line interface (CLI), then connect to the existing cluster using the Python API prior to calling \inline{solve_many(..., parallel_method="ray")}, as demonstrated in Code Block~\ref{code:ray-cli}.
-One of the latter two methods should be used for finer control over the \inline{ray} cluster (number of CPUs to utilize, etc.).
-
-Running \inline{superscreen.solve_many()} in parallel across multiple nodes in a computing cluster is a simple extension to the method outlined in Code Block~\ref{code:ray-cli}, although the specifics depend upon the infrastructure of the cluster, e.g.
-job management software.
-See the ``Multi-Node Ray" section of the \inline{ray} documentation for more details~\cite{ray-docs}.
-% Some applications of \SuperScreen may be ``embarrassingly parallel'' in the sense that all calls to \inline{superscreen.solve()} are completely independent.
-One such application is the scanning SQUID susceptometry simulation shown in Section~\ref{section:application}.
-In such cases, it may be simpler to avoid using \inline{ray} for shared memory and run many
 

### 2022-02-01 main.tex
Updates from Overleaf

@@
 ({\bf b}) and ({\bf c}): Out-of-plane magnetic field $\mu_0H_z$ evaluated at the plane of the pickup loop (W1 layer) for ({\bf b}) the nominal layer spacing with $\delta z<\delta 2$ (indicated with a black $\times$ in ({\bf a})) and ({\bf c}) $\delta z > \delta r$ (indicated with a black $+$ in ({\bf a})).
-For $\delta r\lesssim\delta z$, the magnet field calculated using Eq.~\ref{eq:hz-from-kernel} resembles that of a discrete set of isolated dipoles rather than a continuous sheet of current.}
+For $\delta r\lesssim\delta z$, the magnet field calculated using Eq.~\ref{eq:hz-from-kernel} resembles that of a discrete set of isolated dipoles rather than a continuous sheet of current.
+Note that ({\bf b}) and ({\bf c}) share the same color scale, which is saturated in ({\bf b}).}
     \label{fig:xlarge-dz-dr}

### 2022-03-11 main.tex
overleaf changes

@@
 
-\author[PHYS,SIMES]{Logan Bishop-Van Horn}\ead{lbvh@stanford.edu}
-\author[PHYS,AP,SIMES,GLAM]{Kathryn A. Moler\corref{kam}}\ead{kmoler@stanford.edu}
-
-\cortext[kam]{Corresponding author.}
+\author[PHYS,SIMES]{Logan Bishop-Van Horn\corref{lbvh}}\ead{lbvh@stanford.edu}
+\author[PHYS,AP,SIMES]{Kathryn A. Moler}\ead{kmoler@stanford.edu}
+
+\cortext[lbvh]{Corresponding author.}
 
@@
 \address[SIMES]{Stanford Institute for Materials and Energy Sciences, SLAC National Accelerator Laboratory, 2575 Sand Hill Road, Menlo Park, California 94025, USA}
-\address[GLAM]{Geballe Laboratory for Advanced Materials, Stanford University, Stanford, California 94305, USA}
 
@@
 Quantitative understanding of the spatial distribution of magnetic fields and Meissner screening currents in two-dimensional (2D) superconductors and mesoscopic thin film superconducting devices is critical to interpreting the results of magnetic measurements of such systems.
-Here, we introduce \SuperScreen, an open-source Python package for simulating the response of 2D superconductors to applied time-independent magnetic fields and trapped flux.
-Given an applied magnetic field, \SuperScreen solves the 2D London equation using an efficient matrix inversion method~\cite{Brandt2004-ew, Brandt2005-wj} to obtain the Meissner currents and magnetic fields in and around structures composed of one or more superconducting thin films of arbitrary geometry with spatially inhomogeneous magnetic penetration depth.
+Here, we introduce \SuperScreen, an open-source Python package for simulating the response of 2D superconductors to trapped flux and applied time-independent or quasi-DC magnetic fields for any value of the effective magnetic penetration depth, $\Lambda$.
+Given an applied magnetic field, \SuperScreen solves the 2D London equation using an efficient matrix inversion method~\cite{Brandt2004-ew, Brandt2005-wj} to obtain the Meissner currents and magnetic fields in and around structures composed of one or more superconducting thin films of arbitrary geometry with spatially nonuniform magnetic penetration depth.
 \SuperScreen can be used to model screening effects and calculate self- and mutual-inductance in superconducting devices, and simulate the magnetic response of inhomogeneous 2D superconductors.
@@
 {\em Code Ocean capsule:} (to be added by Technical Editor)\\
-{\em Licensing provisions:} MIT\\
-{\em Programming language: Python}\\
+{\em Licensing provisions:} \href{https://opensource.org/licenses/MIT}{MIT License}\\
+{\em Programming language:} Python\\
 % {\em Supplementary material:}\\
@@
 
-\SuperScreen is a Python package developed to simulate the static magnetic response of structures composed of one or more layers containing superconducting thin films.
-\SuperScreen solves the coupled Maxwell's and London's equations in and around superconducting films with spatially-varying penetration depth in the presence of inhomogeneous applied magnetic fields, pinned vortices, and trapped flux using a matrix inversion method introduced by Brandt and Clem~\cite{Brandt2004-ew,Brandt2005-wj} and subsequently used by Kirtley, \emph{et al.} to model the magnetic response of scanning superconducting quantum interference device (SQUID) sensors.~\cite{Kirtley2016-zz, Kirtley2016-gt}
+\SuperScreen is a Python package developed to simulate the static magnetic response of structures composed of one or more layers containing superconducting thin films characterized by a London penetration depth $\lambda$ that is large compared to the film thickness $d$.
+\SuperScreen solves the coupled Maxwell's and London's equations in and around superconducting films with spatially-varying penetration depth in the presence of inhomogeneous applied magnetic fields, pinned vortices, and trapped flux using a matrix inversion method introduced by Brandt and Clem~\cite{Brandt2004-ew,Brandt2005-wj} and subsequently used by Kirtley, \emph{et al.} to model the magnetic response of scanning superconducting quantum interference device (SQUID) sensors~\cite{Kirtley2016-zz, Kirtley2016-gt}.
 
@@
 
-It is important to note that the assumption $\vec{j}(x, y, z)\approx\vec{j}_{z_0}(x, y)$ is valid for only films that are thinner than their London penetration depth ($d<\lambda$, such that $\Lambda=\lambda^2/d>\lambda$).
-However the model has been applied with some success in structures with $\lambda\lesssim d$~\cite{Kirtley2016-zz,Kirtley2016-gt}.
+It is important to note that the assumption $\vec{j}(x, y, z)\approx\vec{j}_{z_0}(x, y)$ is valid for only films that are thinner than their London penetration depth ($d\ll\lambda$, such that $\Lambda=\lambda^2/d\gg\lambda$).
+However the model has been applied with some success in structures with $\lambda\lesssim d$, for example by Kirtley, \emph{et al.} in modeling the magnetic response of scanning SQUID susceptometers~\cite{Kirtley2016-zz,Kirtley2016-gt}.
 Aside from this limitation, the method described below can be used to model films with any effective penetration depth $0\leq\Lambda<\infty$.
@@
 There are several important limitations to the applicability of \SuperScreen and the matrix inversion method on which it is based~\cite{Brandt2004-ew,Brandt2005-wj}.
-First, strictly speaking all superconducting films should be in the 2D limit, with London penetration depth $\lambda$ less than film thickness $d$, such that the current density is approximately constant along the thickness of the film.
+First, strictly speaking all superconducting films should be in the 2D limit, with London penetration depth $\lambda$ large compared to the film thickness $d$, such that the current density is approximately constant along the thickness of the film.
 There are cases where the model reproduces experimental results despite violation of this condition (e.g.
@@
 Potential improvements to \SuperScreen include: support for terminal currents as discussed above, automated determination of solution convergence for models with multiple layers, more sophisticated mesh generation (e.g.
-automated local mesh refinement based on device geometry or adaptive mesh refinement based on solution convergence), integration with standard integrated circuit layout software or file formats, and further optimization for memory and CPU efficiency.
+automated local mesh refinement based on device geometry or adaptive mesh refinement based on solution convergence), integration with standard integrated circuit layout software or file formats, and further numerical optimization, including GPU acceleration.
 
@@
 Note that $\Lambda(x, y)$ must vary slowly on the scale of the spacing between mesh vertices in order for results to be reliable.
+For example, the simulated supercurrent density near a point-like defect (i.e small compared to the triangles in the mesh) associated with a penetration depth $\Lambda_\text{defect}$ in an otherwise uniform film with penetration depth $\Lambda_0\ll\Lambda_\text{defect}$ will depend strongly on the specifics of the mesh near the defect.
+One can avoid this problem by increasing the density of the mesh in regions of fast-varying $\Lambda$ by adding one or more ``abstract regions" to the \inline{Device} as described in Section~\ref{section:overview:device}.
 
@@
 Eq.~\ref{eq:hz-from-kernel} is exact for a continuous stream function $g$.
-However, the discretized version of Eq.~\ref{eq:hz-from-kernel}, in which the double integral over the film area $F$ is replaced by a sum over triangular mesh elements, is only valid if $\delta z = z-z'$, the vertical distance between the film and the point at which the field is being evaluated, is larger than the typical distance $\delta r$ between vertices in the mesh representing the film.
+However, the discretized version of Eq.~\ref{eq:hz-from-kernel}, in which the double integral over the film area $F$ is replaced by a sum over triangular mesh elements, is only valid if $\delta z = z-z'$, the vertical distance between the film and the point at which the field is being evaluated, is large compared to the typical distance $\delta r$ between vertices in the mesh representing the film.
 For $z-z'=\delta z\lesssim\delta r$, the field $H_z(\vec{r})$ resembles that of a discrete set of isolated dipoles located at the mesh vertex positions, rather than that of a continuous sheet of current (see Figure~\ref{fig:xlarge-dz-dr}({\bf b})).

### 2022-03-15 examples/scripts/squid_image_row.py
Update figures notebook

@@ -1,0 +1,274 @@
+"""
+This script uses SuperScreen to simulate a single row of a SQUID susceptometry
+image. The script can be called from squid_image.sbatch in order to simulate
+many rows in parallel using a slurm job array.
+"""
+
+import os
+import sys
+import time
+import logging
+
+import numpy as np
+
+import superscreen as sc
+
+sys.path.insert(0, os.path.join(os.path.dirname(__file__), os.pardir))
+import squids
+
+
+def mirror_layers(device, about=0, in_place=False):
+    new_layers = []
+    for layer in device.layers_list:
+        new_layer = layer.copy()
+        new_layer.z0 = about - layer.z0
+        new_layers.append(new_layer)
+    if not in_place:
+        device = device.copy()
+    device.layers_list = new_layers
+    return device
+
+
+def flip_device(device, about_axis="y"):
+    device = device.copy(with_arrays=False)
+    assert about_axis in "xy"
+    index = 0 if about_axis == "y" else 1
+    polygons = list(device.polygons.values())
+    for polygon in polygons:
+        polygon.points[:, index] *= -1
+    return device
+
+
+def update_origin(device, x0=0, y0=0):
+    device = device.copy(with_arrays=True, copy_arrays=True)
+    polygons = list(device.polygons.values())
+    p0 = np.array([[x0, y0]])
+    for polygon in polygons:
+        polygon.points += p0
+    if getattr(device, "points", None) is not None:
+        device.points += p0
+    return device
+
+
+def sample_applied_field(x, y, z, fc_solution=None, field_units="mT"):
+    x, y = np.atleast_1d(x, y)
+    f = fc_solution.field_at_position(
+        np.stack([x, y], axis=1),
+        zs=z,
+        units=field_units,
+        with_units=False,
+    )
+    return f
+
+
+def squid_applied_field(x, y, z, sample_solution=None, field_units="mT"):
+    x, y = np.atleast_1d(x, y)
+    f = sample_solution.field_at_position(
+        np.stack([x, y], axis=1),
+        zs=z,
+        units=field_units,
+        with_units=False,
+        return_sum=True,
+    )
+    return f
+
+
+def main():
+    import argparse
+
+    parser = argparse.ArgumentParser()
+    parser.add_argument(
+        "--outdir",
+        type=str,
+        help="output directory",
+    )
[…]

### 2022-03-16 main.tex
overleaf cleanup
Updates from Overleaf

@@
 from Eq.~\ref{eq:field_from_kernel_num}, and the full vector magnetic field $\vec{H}(x, y, z)$
-at any point in space can be computed from Eqs.~\ref{eq:field_from_kernel} and ~\ref{eq:kernels}. Multi-layer structures are  iteratively as described in Section \ref{section:model:multilayer}.
+at any point in space can be computed from Eqs.~\ref{eq:field_from_kernel} and ~\ref{eq:kernels}. Multi-layer structures are solved iteratively as described in Section \ref{section:model:multilayer}.
 
@@
 
-At the time of writing, \SuperScreen requires Python version 3.6--3.9.
+At the time of writing, \SuperScreen requires Python version 3.7--3.9.
 The package is located in a public repository on GitHub~\cite{superscreen, BishopVanHorn2021-bd}, and a suite of unit tests is run automatically via the GitHub Actions continuous integration (CI) tool whenever a change or proposed change (Pull Request) is made to the \inline{main} branch of the repository.
-At the time of writing, the test suite is executed using Python versions 3.6 through 3.9, and the test coverage is $>95\%$.
+At the time of writing, the test suite is executed using Python versions 3.7 through 3.9, and the test coverage is $>95\%$.
 Any changes to the \inline{main} branch of the repository also trigger an automatic re-build of the online documentation~\cite{superscreen-rtd}.
@@
 \SuperScreen has several important dependencies beyond the Python standard library: \inline{numpy}~\cite{Harris2020-xv} and \inline{scipy}~\cite{Virtanen2020-zz} for numerics, \inline{matplotlib}~\cite{Hunter2007-il} for visualization, \inline{pint}~\cite{Grecco} for handling physical units, \inline{shapely}~\cite{shapely} for creating and manipulating device geometries, \inline{meshpy}~\cite{Klockner, Shewchuk, Shewchuk1996-va} and \inline{optimesh}~\cite{Schlomer2021-ua} for mesh generation, and \inline{Ray}~\cite{Moritz2018-mt,ray-docs} for parallel processing with shared memory (see~\ref{section:parallel}).
-
-% \subsection{Parameters}
-% \label{section:overview:parameter}
-
-% A \inline{superscreen.Parameter} is a wrapper around a Python function that computes a scalar value as a function of position coordinates ($x$, $y$, and optionally $z$) based on some set of keyword arguments.
-Addition, subtraction, multiplication, division, and exponentiation between \inline{Parameters}, other \inline{Parameters}, and Python scalars (\inline{int} and \inline{float}) are supported.
-\inline{Parameters} can be used to conveniently define applied magnetic fields and penetration depths that depend on position (see \ref{appendix:inhomogeneous}).
-
-% \begin{code}
-% \begin{minted}[fontsize=\small]{python}
-% from superscreen import Parameter
-
-% def f(x, y, a=1, b=0):
-%     return a * x**2 + b * y
-
-% param = Parameter(f, a=0, b=1)
-% print(param) # Parameter<f(a=0, b=1)>
-% other_param = Parameter(f, a=2, b=3)
-% print(other_param) # Parameter<f(a=2, b=3)>
-% print(param(0, 0) == f(0, 0, a=0, b=1)) # True
-% print(other_param(1, 2) == f(1, 2, a=2, b=3)) # True
-% param_squared = param ** 2
-% print(param_squared) # CompositeParameter<(f(a=0, b=1) ** 2)>
-% print(
-%     (5 * param_squared / other_param)(5, 6)
-%     == 5 * f(5, 6, a=0, b=1) ** 2 / f(5, 6, a=2, b=3)
-% ) # True
-% \end{minted}
-% \captionof{listing}{The basic usage of \inline{superscreen.Parameters}, which compute a scalar value as a function of $x, y$ (and optionally $z$) coordinates.
-Note that the positional arguments \inline{x} and \inline{y} can be either floating point scalars or 1-dimensional \inline{numpy} arrays.}
-% \label{code:parameters}
-% \end{code}
 
@@
 All polygons in a device must be simply-connected; a hole in a film is modeled as one \inline{Polygon} instance whose coordinates all lie within the \inline{Polygon} representing the film.
-% A \inline{Polygon} contains the name of the layer to which is belongs, an array specifying the coordinates of its vertices, and a method, \inline{Polygon.contains_points()}, which determines whether specified coordinates lie within the polygon or not.
 \inline{Polygons} can constructed and combined using set-theoretic operations.
@@
 
-% \begin{code}
-% \begin{minted}[fontsize=\small]{python}
-% # Create a device representing square thin film.
-% device = sc.Device(
-%     "film",
-%     layers=[sc.Layer("base", Lambda=0, z0=0)],
-%     films=[sc.Polygon("film", layer="base", points=sc.geometry.box(20))],
-%     length_units="um",
-% )
-% device.make_mesh(min_points=5_000)
-% # Specify the vortex position.
-% vortices = [sc.Vortex(x=0, y=0, layer="base")]
-% # Sweep Lambda, solve the model, and evaluate the field at the given coordinates.
-% Lambdas = np.linspace(0, 2, 5) # [device.length_units]
-% for Lambda in Lambdas:
-%     device.layers["base"].Lambda = Lambda
-%     solution = sc.solve(device=device, vortices=vortices)[-1]
-%     # Use solution.field_at_position() to evaluate the magnetic field profile,
-%     # and solution.polygon_fluxoid() to calculate fluxoids.
-% \end{minted}
-% \captionof{listing}{Creates a square superconducting film with side length $20\,\um$ and calculates the magnetic field distribution near a vortex at the center of the film as a function of the the effective penetration depth, $\Lambda$ (see Figure~\ref{fig:pearl}).}
-% \label{code:pearl-vortex}
-% \end{code}
-
 \begin{figure*}[h!]
@@
 There are two insulating layers: I1, which separates BE and W1, and I2, which separates W1 and W2.
-% Table~\ref{table:squid-layers} shows the thickness $d$ of each layer in the real devices, as well as the vertical position of the 2D films used to model each layer. 
 For the superconducting layers, which are made of Nb, we take the London penetration depth to be $\lambda = 80\,\nm$, and the layer thicknesses correspond to the real device design (see Table 1 of Ref.~\cite{Kirtley2016-gt} and Figure 8 of Ref.~\cite{Kirtley2016-zz}).
@@
 Figure~\ref{fig:squid-mutuals}({\bf c}) shows the convergence of $M_\mathrm{PL-FC}$ as a function of solver iteration (see Section~\ref{section:model:multilayer}).
-
-% \begin{table*}
-% \centering
-% \begin{tabular}{|l|l|l|l|l|}
-% \hline
-% Layer name & Material & Thickness & Vertical position, $z_0$ & Films located in layer \\ \hline
-% \hline
-% W2 & Nb & $d_\mathrm{W2} = 200\,\nm$ & $d_\mathrm{W2} / 2$ & Pickup loop shield, modulation coil \\ \hline
-% I2 & SiO${}_2$ & $d_\mathrm{I2} = 130\,\nm$ & --- & --- \\ \hline
-% W1 & Nb & $d_\mathrm{W1} = 100\,\nm$ & $d_\mathrm{W2} + d_\mathrm{I2} + d_\mathrm{W1} / 2$ & Pickup loop, field coil shield \\ \hline
-% I1 & SiO${}_2$ & $d_\mathrm{I1} = 150\,\nm$ & --- & --- \\ \hline
-% BE & Nb & $d_\mathrm{BE} = 160\,\nm$ & $d_\mathrm{W2} + d_\mathrm{I2} + d_\mathrm{W1} + d_\mathrm{I1} + d_\mathrm{BE} / 2$ & Field coil, pickup loop shield \\ \hline
-% \end{tabular}
-% \caption{Layer stackup for the SQUID susceptometers discussed in Section~\ref{section:examples:scanning-squid}.
-W2 is located at the surface of the chip (deposited last, closest to the sample) and BE deepest below the chip's surface (deposited first).
-See Refs.~\cite{Kirtley2016-zz, Kirtley2016-gt} for more details on the designed of the suscpetometers.}
-% \label{table:squid-layers}
-% \end{table*}
 
@@
 Note that in principle it is possible to combine the sensor and sample into a single \inline{Device} with 6 superconducting layers, however this is impractical because it would require generating a new mesh for each $(x_s, y_s)$ and, as discussed in detail in \ref{appendix:numerics}, the problem scales unfavorably with the number of layers in a device and with the total lateral extent of a device.
-
-% \subsection{Application: scanning SQUID magnetometry}
-% \label{section:examples:magnetometry}
-
-% Scanning SQUID susceptometers can also be used for magnetometry, i.e. measuring the magnetic flux above a sample's surface without applying a field to the sample with the field coil.
 
@@
 Finally, the Laplace operator is given by $\mathbf{\nabla}^2 = \mathbf{M}^{-1}\mathbf{L}$.
-
-% \section{Fluxoid calculation}
-% \label{appendix:fluxoid}
-% As described in Section~\ref{section:model:fluxoid}, for a valid solution to the static 2D London equation as formulated in Eq.~\ref{eq:london}, the fluxoid $\Phi^f_S$ should have the following properties:
-% \begin{enumerate}
-%     \item{$\Phi^f_S = \sum_{\mathrm{vortices}\,v}\Phi_v$ for any region $S$ lying completely within a superconducting film that contains a set of vortices $v$, each containing flux $\Phi_v$ (and $\Phi^f_S = 0$ if $S$ contains no vortices).}
-%     \item{$\Phi^f_S = \Phi_h$ for any region $S$ that contains a hole $h$, where $\Phi_h$ is a constant (i.e.
-does not depend on the specific region $S$ or path $\partial S$) but need not be quantized in units of $\Phi_0$.}
-% \end{enumerate}
-
-% A demonstration of these properties for the case of the square ring with effective penetration depth $\Lambda=1\,\um$, inner side length $5\,\um$, and outer side length $10\,\um$ subject to a uniform applied field of 0.1 mT is shown in Figure~\ref{fig:fluxoid}.
-Property 1 is shown in the first two rows, and property 2 is shown in the last row.
-See the figure caption for a detailed explanation of the results.
-
-% \begin{figure}
-%     \centering
-%     \includegraphics[width=\textwidth]{examples/images/fluxoid_combined.pdf}
-%     \caption{Demonstration of the fluxoid properties listed in Section~\ref{section:examples:fluxoid} for a square ring with $\Lambda=1\,\um$, inner side length $5\,\um$, and outer side length $10\,\um$, whose outline is shown with white lines in the left and middle columns, subject to a uniform applied field of 0.1 mT.
-The left and middle columns show the computed current density and out-of-plane-field, overlaid with several regions $S$ for which the fluxoids $\Phi^f_S$ are calculated using \inline{Solution.polygon_fluxoid()}.
-The corresponding fluxoids are shown in the right column.
-The colors of the paths in the left and middle columns correspond to the colors of the bars in the right column.
-Top row (a - c): The fluxoid $\Phi^f_S$ vanishes for all simply-connected regions containing no vortices.
-The errors in ({\bf c}) are given by $|\Phi^f_S / \Phi^f_{S,\,\text{(flux part)}}|$.
-Middle row (d - f): For simply-connected regions containing a set of vortices $v$, each carrying flux $\Phi_v$, the fluxoid is given by $\sum_v\Phi_v$.
-In this case, the body of the square ring contains both ``positive'' ($\Phi_v=\Phi_0$, counter-clockwise circulating current) and ``negative'' ($\Phi_v=-\Phi_0$, clockwise circulating current) vortices, which appear in ({\bf e}) as yellow and blue dots respectively.
-The expected value for the fluxoid for each region $S$ given in units of $\Phi_0$ by (number of yellow vortices lying inside $S$) - (number of blue vortices lying inside $S$), and the errors in ({\bf f}) are reported relative to this expected value.
-Bottom row (g - i): Fluxoid path independence for the $n=0$ fluxoid state, shown here for both circular ($S = 0, 1, 2$) and square ($S=3, 4, 5$) paths.
-Here again, the errors are given by $|\Phi^f_S / \Phi^f_{S,\,\text{(flux part)}}|$.}
-%     \label{fig:fluxoid}
-% \end{figure}
 

### 2022-03-16 examples/scripts/squid_image_row.py
re-run notebooks

@@ -92,7 +92,7 @@ def main():
         "--optimesh-steps",
         type=int,
         default=None,
-        help="Number of optimesh steps to perform."
+        help="Number of optimesh steps to perform.",
     )
     parser.add_argument(
         "--iterations",
@@ -229,9 +229,9 @@ def main():
             iterations=iterations,
         )[-1]
         logging.info("\tComputing pickup loop flux...")
-        pl_flux = solution.polygon_flux(
-            polygons="pl", units="Phi_0", with_units=False
-        )["pl"]
+        pl_flux = solution.polygon_flux(polygons="pl", units="Phi_0", with_units=False)[
+            "pl"
+        ]
         pl_total_flux.append(pl_flux)
         fluxoid = solution.hole_fluxoid("pl_center", units="Phi_0")
         flux_part.append(fluxoid.flux_part.magnitude)

### 2022-03-16 main.tex
Add date accessed to online references

@@
 
-\title{\texttt{SuperScreen}: An open-source package for simulating the magnetic response of two-dimensional superconducting devices}
+\title{SuperScreen: An open-source package for simulating the magnetic response of two-dimensional superconducting devices}
 
@@
 Finally, in Section~\ref{section:conlusion} we conclude by discussing applications, limitations, and possible extensions of the package.
-Python scripts and Jupyter notebooks used to generate all figures presented below can be found in the GitHub repository accompanying this manuscript [ref.].
+Python scripts and Jupyter notebooks used to generate all figures presented below can be found in the GitHub repository accompanying this manuscript~\cite{logan_bishop_van_horn_2022_6363541}.
 
@@
 
-In this section we give a high-level overview of the \SuperScreen package. Further details can be found in the online documentation~\cite{superscreen-rtd}.
+In this section we give a high-level overview of the \SuperScreen package.
+Further details can be found in the online documentation~\cite{superscreen-rtd}.
+The specific version of the package corresponding to this manuscript is \texttt{v0.4.0}.
 
@@
 At the time of writing, \SuperScreen requires Python version 3.7--3.9.
-The package is located in a public repository on GitHub~\cite{superscreen, BishopVanHorn2021-bd}, and a suite of unit tests is run automatically via the GitHub Actions continuous integration (CI) tool whenever a change or proposed change (Pull Request) is made to the \inline{main} branch of the repository.
+The package is located in a public repository on GitHub~\cite{superscreen, BishopVanHorn2022-bd}, and a suite of unit tests is run automatically via the GitHub Actions continuous integration (CI) tool whenever a change or proposed change (Pull Request) is made to the \inline{main} branch of the repository.
 At the time of writing, the test suite is executed using Python versions 3.7 through 3.9, and the test coverage is $>95\%$.

### 2022-04-11 main.tex
Update notebooks

@@
 \AfterEndEnvironment{minted}{\end{tcolorbox}\end{center}}
-% \usemintedstyle[python]{vs}
 \usepackage{caption}
@@
 
-\title{SuperScreen: An open-source package for simulating the magnetic response of two-dimensional superconducting devices}
+\title{\SuperScreen: An open-source package for simulating the magnetic response of two-dimensional superconducting devices}
 
@@
 Given an applied magnetic field, \SuperScreen solves the 2D London equation using an efficient matrix inversion method~\cite{Brandt2004-ew, Brandt2005-wj} to obtain the Meissner currents and magnetic fields in and around structures composed of one or more superconducting thin films of arbitrary geometry with spatially nonuniform magnetic penetration depth.
-\SuperScreen can be used to model screening effects and calculate self- and mutual-inductance in superconducting devices, and simulate the magnetic response of inhomogeneous 2D superconductors.
+\SuperScreen can be used to model screening effects and calculate self- and mutual-inductance in thin film superconducting devices.
 \end{abstract}
@@
 \SuperScreen is a Python package developed to simulate the static magnetic response of structures composed of one or more layers containing superconducting thin films characterized by a London penetration depth $\lambda$ that is large compared to the film thickness $d$.
-\SuperScreen solves the coupled Maxwell's and London's equations in and around superconducting films with spatially-varying penetration depth in the presence of inhomogeneous applied magnetic fields, pinned vortices, and trapped flux using a matrix inversion method introduced by Brandt and Clem~\cite{Brandt2004-ew,Brandt2005-wj} and subsequently used by Kirtley, \emph{et al.} to model the magnetic response of scanning superconducting quantum interference device (SQUID) sensors~\cite{Kirtley2016-zz, Kirtley2016-gt}.
+\SuperScreen solves the coupled Maxwell's and London's equations in and around superconducting films in the presence of inhomogeneous applied magnetic fields, pinned vortices, and trapped flux using a matrix inversion method introduced by Brandt and Clem~\cite{Brandt2004-ew,Brandt2005-wj} and subsequently used by Kirtley, \emph{et al.} to model the magnetic response of scanning superconducting quantum interference device (SQUID) sensors~\cite{Kirtley2016-zz, Kirtley2016-gt}.
 
@@
 A convenient method for solving this problem was introduced by Brandt and Clem in Ref.~\cite{Brandt2004-ew}, expanded by Brandt in Ref.~\cite{Brandt2005-wj}, and subsequently used to model the magnetic response of scanning SQUID susceptometers~\cite{Kirtley2016-zz, Kirtley2016-gt}.
-In the London model of superconductivity, the magnetic field $\vec{H}(\vec{r})$ and 3D current density $\vec{j}(\vec{r})$ in a superconductor with London penetration depth $\lambda(\vec{r})$ obey the second London equation:
-$\nabla\times\vec{j}(\vec{r})=-\vec{H}(\vec{r})/\lambda^2(\vec{r})$, where
-$\nabla=\left(\frac{\partial}{\partial x}, \frac{\partial}{\partial y}, \frac{\partial}{\partial z}\right)$.
+In the London model of superconductivity, the magnetic field $\vec{H}(\vec{r})$ and 3D current density $\vec{j}(\vec{r})$ in a superconductor with London penetration depth $\lambda$ obey the second London equation:
+$\vec{H}(\vec{r})-\lambda^2\vec{\nabla}\times\vec{j}(\vec{r})=$, where
+$\vec{\nabla}=\left(\frac{\partial}{\partial x}, \frac{\partial}{\partial y}, \frac{\partial}{\partial z}\right)$ is the 3D gradient operator.
 The 2D London model assumes that the current density $\vec{j}$ is approximately independent of $z$, such that  $\vec{j}(\vec{r}) = \vec{j}(x, y, z)\approx\vec{j}_{z_0}(x, y)$ for a film lying parallel to the $x-y$ plane at vertical position $z_0$.
@@
     \label{eq:london}
-    \nabla\times\vec{J}(x, y)=-\vec{H}(x, y)/\Lambda(x, y),
+    \vec{H}(x, y)=-\Lambda\vec{\nabla}\times\vec{J}(x, y)\\
 \end{equation}
-where $\Lambda(x, y)=\lambda^2(x, y)/d$ is the effective penetration depth
-of the superconducting film (equal to half the Pearl length~\cite{Pearl1964-cl}).
+where $\Lambda=\lambda^2/d$ is the effective penetration depth
+of the superconducting film (equal to half the Pearl length~\cite{Pearl1964-cl}) and now $\vec{\nabla}=\left(\frac{\partial}{\partial x}, \frac{\partial}{\partial y}\right)$.
 
@@
     \label{eq:stream}
-    \vec{J}(x, y) = -\hat{z}\times\nabla g
-    = \nabla\times(g\hat{z})
+    \vec{J}(x, y) = -\hat{z}\times\vec{\nabla}g
+    = \vec{\nabla}\times(g\hat{z})
     = \left(\frac{\partial g}{\partial y}, -\frac{\partial g}{\partial x}\right).
@@
         \vec{H}(x, y) &= -\Lambda\left[\nabla\times\vec{J}(x, y)\right]\\
-        &= -\Lambda\left[\nabla\times\left(\nabla\times(g\hat{z})\right)\right]\\
-        &= -\Lambda\left[\nabla(\nabla\cdot(g\hat{z}))-\nabla^2(g\hat{z})\right]\\
+        &= -\Lambda\left[\vec{\nabla}\times\left(\vec{\nabla}\times(g\hat{z})\right)\right]\\
+        &= -\Lambda\left[\vec{\nabla}(\vec{\nabla}\cdot(g\hat{z}))-\nabla^2(g\hat{z})\right]\\
         &=\Lambda\nabla^2g(x,y)\hat{z},
@@
 \end{align}
-where $\nabla^2=\nabla\cdot\nabla$ is the Laplace operator.
-(The last line follows from the fact that $\nabla\cdot\left[g(x,y)\hat{z}\right] = 0$).
-From Ampere's Law, the three components of the magnetic field $\vec{H}(\vec{r})$ at position $\vec{r}=(x, y, z)$ due to a sheet of current lying in the $x-y$ plane (at vertical position $z'$) with stream function $g(x', y')$ are given by:
+where $\nabla^2=\vec{\nabla}\cdot\vec{\nabla}$ is the Laplace operator.
+(The last line follows from the fact that $\vec{\nabla}\cdot\left[g(x,y)\hat{z}\right] = 0$.) From Ampere's Law, the three components of the magnetic field $\vec{H}(\vec{r})$ at position $\vec{r}=(x, y, z)$ due to a sheet of current lying in the $x-y$ plane (at vertical position $z'$) with stream function $g(x', y')$ are given by:
 \begin{align}
@@
         &\underbrace{\vec{H}(\vec{r})\cdot\hat{z} = H_z(\vec{r})
-        = \Lambda\nabla^2g(x, y)}_{z-\text{component of the total field}}
+        = \Lambda\nabla^2g)}_{z-\text{component of the total field}}
         = \\ & \underbrace{H_{z,\,\mathrm{applied}}(\vec{r})}_{\text{applied field}}
@@
     = \\ &-\int_F\left[
-        Q_z(\vec{r},\pvec{r}')-\delta(\vec{r}-\pvec{r}')\Lambda(\pvec{r}')\nabla^2\right
+        Q_z(\vec{r},\pvec{r}')-\delta(\vec{r}-\pvec{r}')\Lambda\nabla^2\right
     ]g(\pvec{r}')\,\mathrm{d}^2r',
@@
     &-\int_{\mathrm{hole}\,h}[
-        Q_z(\vec{r},\pvec{r}')-\delta(\vec{r}-\pvec{r}')\Lambda(\pvec{r}')\nabla^2
+        Q_z(\vec{r},\pvec{r}')-\delta(\vec{r}-\pvec{r}')\Lambda\nabla^2
     ] I_{\mathrm{circ},\,h} \,\mathrm{d}^2r'.   
@@
     = \\&-\int_F\left[
-        Q_z(\vec{r},\pvec{r}')-\delta(\vec{r}-\pvec{r}')\Lambda(\pvec{r}')\nabla^2\right
+        Q_z(\vec{r},\pvec{r}')-\delta(\vec{r}-\pvec{r}')\Lambda\nabla^2\right
     ]g(\pvec{r}')\,\mathrm{d}^2r'.
@@
 \begin{equation}
-    \Phi^f_S = \underbrace{\int_S\mu_0H_z(\vec{r})\,\mathrm{d}^2r}_\text{``flux part''} + \underbrace{\oint_{\partial S}\mu_0\Lambda(\vec{r})\vec{J}(\vec{r})\cdot\mathrm{d}\vec{r}}_\text{``supercurrent part''}.
+    \Phi^f_S = \underbrace{\int_S\mu_0H_z(\vec{r})\,\mathrm{d}^2r}_\text{``flux part''} + \underbrace{\oint_{\partial S}\mu_0\Lambda\vec{J}(\vec{r})\cdot\mathrm{d}\vec{r}}_\text{``supercurrent part''}.
     \label{eq:fluxoid}
@@
 The presence of vortices trapped in a film at positions $\vec{r}_v$ modifies Eq.~\ref{eq:Heff_sub} as follows:
+
 \begin{align}
@@
     &-\int_F\left[
-        Q_z(\vec{r},\pvec{r}')-\delta(\vec{r}-\pvec{r}')\Lambda(\pvec{r}')\nabla^2\right
+        Q_z(\vec{r},\pvec{r}')-\delta(\vec{r}-\pvec{r}')\Lambda\nabla^2\right
     ]g(\pvec{r}')\,\mathrm{d}^2r',
@@
 Column vectors are treated as matrices with $\ell$ rows and 1 column.
-On the other hand, we denote element-wise multiplication with a dot: $(\mathbf{A}\cdot\mathbf{B})_{ij}=A_{ij}B_{ij}$ for two matrices
-and $(\mathbf{A}\cdot\mathbf{v})_{ij}=(\mathbf{v}\cdot\mathbf{A})_{ij}=A_{ij}v_{i}$ for a matrix $\mathbf{A}$ and a column vector $\mathbf{v}$.
-$\mathbf{A}^T$ denotes the transpose of matrix $\mathbf{A}$.
+We denote element-wise multiplication with a lower dot, $(\mathbf{A}.\mathbf{B})_{ij}=A_{ij}B_{ij}$, and $\mathbf{A}^T$ denotes the transpose of matrix $\mathbf{A}$.
 
@@
     &= \underbrace{\mathbf{h}_{z,\,\mathrm{applied}}}_\text{applied field}
-    + \underbrace{(\mathbf{Q}\cdot\mathbf{w}^T)\mathbf{g}}_\text{screening field}\\
-    % &=\mathbf{h}_{z,\,\mathrm{applied}}
-    % + (\mathbf{Q}\cdot\mathbf{w}^T)\mathbf{g}\\
+    + \underbrace{(\mathbf{Q}.\mathbf{w}^T)\mathbf{g}}_\text{screening field}\\
     h_{z, i} &= h_{z,\,\mathrm{applied}, i} + \sum_j Q_{ij}w_jg_j,
@@
     Q_{ij} = (\delta_{ij}-1)q_{ij}
-    + \delta_{ij}\frac{1}{w_{ij}}\left(C_i + \sum_{l\neq i}q_{il}w_{il}\right),
+    + \delta_{ij}\frac{1}{w_{j}}\left(C_i + \sum_{l\neq i}q_{il}w_{l}\right),
 \end{equation}
@@
     \label{eq:Heff_sub_num}
-     \mathbf{h}_{z,\,\mathrm{applied}} - \sum_{\mathrm{holes}\, h}\mathbf{h}_{z,\,\mathrm{eff},\,h} = -(\mathbf{Q}\cdot\mathbf{w}^T-\mathbf{\nabla}^2\cdot \mathbf{\Lambda}^T)\mathbf{g},
+     \mathbf{h}_{z,\,\mathrm{applied}} - \sum_{\mathrm{holes}\, h}\mathbf{h}_{z,\,\mathrm{eff},\,h} = -(\mathbf{Q}.\mathbf{w}^T-\Lambda\mathbf{\nabla}^2)\mathbf{g},
 \end{equation}
 where we exclude points in the mesh lying outside of the superconducting film but keep points
-inside holes in the film. $\mathbf{\Lambda}$ is either a scalar or a vector defining the effective penetration depth at every included vertex in the mesh, and $\mathbf{\nabla}^2$
-is the Laplace operator, a $p\times p$ matrix defined such that $\mathbf{\nabla}^2\mathbf{f}$ computes the Laplacian $\nabla^2f(x,y)$ of a function $f(x,y)$ defined on the mesh  (see~\ref{appendix:laplace}).
+inside holes in the film. $\mathbf{\nabla}^2$
+is the Laplace operator, a $p\times p$ matrix defined such that $\mathbf{\nabla}^2\mathbf{f}$ computes the Laplacian $\nabla^2f(x,y)$ of a scalar field $f(x,y)$ defined on the mesh vertices (see~\ref{appendix:laplace}).
 
@@
 Since the stream function outside the film and inside holes in the film is already known, solving Eq.~\ref{eq:Heff_sub_num} gives us the stream function for the full mesh.
-Defining $\mathbf{K} = \left(\mathbf{Q}\cdot\mathbf{w}^T-\mathbf{\nabla}^2\cdot\mathbf{\Lambda}^T\right)^{-1}$, we have
+Defining $\mathbf{K} = \left(\mathbf{Q}\cdot\mathbf{w}^T-\Lambda\mathbf{\nabla}^2\right)^{-1}$, we have
 \begin{equation}
@@
 A \inline{Device} is made up of one or more superconducting layers, each represented by an instance of  \inline{superscreen.Layer}.
-Each layer sits in a specified plane parallel to the $x-y$ plane and has its own effective penetration depth $\Lambda$, which can either be a constant or a \inline{superscreen.Parameter} that defines $\Lambda(x, y)$, the effective penetration depth as a function of position (see \ref{appendix:inhomogeneous}).
-Alternatively, the effective penetration depth $\Lambda$ can be defined in terms of a layer's London penetration depth $\lambda$ and its thickness $d$: $\Lambda=\lambda^2/d$, in which case the London penetration depth can be either a constant or a \inline{superscreen.Parameter}.
+Each layer sits in a specified plane parallel to the $x-y$ plane and has its own effective penetration depth $\Lambda$.
+Alternatively, the effective penetration depth $\Lambda$ can be defined in terms of a layer's London penetration depth $\lambda$ and its thickness $d$: $\Lambda=\lambda^2/d$.
 
@@
 applied_field = sc.sources.ConstantField(10)
-solution = sc.solve(device, applied_field=applied_field, field_units="uT")[-1]
+solution = sc.solve(device, applied_field=applied_field, field_units="mT")[-1]
 # Visualize the solution.
@@
     \includegraphics[width=\textwidth]{examples/images/ring_with_slit.pdf}
-    \caption{The output of Code Block~\ref{code:device}: Meissner screening of a uniform $10\,\mu\mathrm{T}$ out-of-plane field by a ring with inner diameter $1\,\um$, outer diameter $3\,\um$, and effective penetration depth $\Lambda=1\,\um$, interrupted by a slit of width $0.25\,\um$.
+    \caption{The output of Code Block~\ref{code:device}: Meissner screening of a uniform $1\,\mathrm{mT}$ out-of-plane field by a ring with inner diameter $1\,\um$, outer diameter $3\,\um$, and effective penetration depth $\Lambda=1\,\um$, interrupted by a slit of width $0.25\,\um$.
 ({\bf a}) Plot of the boundary of the ring (blue), circular bounding box (orange), and the computational mesh (gray), generated with \inline{Device.plot()}.
@@
 The ``flux part''  $\int_S\mu_0H_z(\vec{r})\,\mathrm{d}^2r$ is calculated using \inline{Solution.polygon_flux()}, which computes the flux through a polygon representing a region $S$ as $\Phi_S=\sum_{i\in S} \mu_0H_{z,i}w_i$, where $H_{z,i}$ is the magnetic field at vertex $i$ (recall that $w_i$ assigns an effective area to mesh vertex $i$).
-The ``supercurrent part'' $\oint_S\mu_o\Lambda(\vec{r})\vec{J}(\vec{r})\cdot\mathrm{d}\vec{r}$ is calculated by evaluating the vector current density $\vec{J}$ at each point in the path $\partial S$ using \inline{Solution.interp_current_density()}, then computing the line integral along the path using the trapezoid rule.
+The ``supercurrent part'' $\oint_S\mu_0\Lambda\vec{J}(\vec{r})\cdot\mathrm{d}\vec{r}$ is calculated by evaluating the vector current density $\vec{J}$ at each point in the path $\partial S$ using \inline{Solution.interp_current_density()}, then computing the line integral along the path using the trapezoid rule.
 The sum of these two terms gives the fluxoid $\Phi^f_S$.
@@
 
-The ability to model and visualize screening effects in inhomogeneous 2D superconductors and devices constructed from superconducting thin films can help to build intuition about these systems, aid in interpretation of measurement results, and enable optimization of measurement and device design.
+The ability to model and visualize screening effects in 2D superconductors and devices constructed from superconducting thin films can help to build intuition about these systems, aid in interpretation of measurement results, and enable optimization of measurement and device design.
 \SuperScreen is an open-source, user-friendly, portable, and efficient tool that solves this problem.
-Applications of the package include calculating self- and mutual-inductance in planar and multi-planar superconducting circuits, and modeling the magnetic interaction between inhomogeneous superconducting samples and superconducting sensors such as scanning SQUID susceptometers~\cite{Kirtley2016-zz}.
+Applications of the package include calculating self- and mutual-inductance in planar and multi-planar superconducting circuits, and modeling the magnetic interaction between superconducting samples and superconducting sensors such as scanning SQUID susceptometers~\cite{Kirtley2016-zz}.
 
@@
 \label{section:acknowledgements}
-We acknowledge useful discussions with John R.
-Kirtley.
-This work is supported by the Department of Energy,  Office of Science, Basic Energy Sciences, Materials Sciences and Engineering Division, under Contract DE-AC02-76SF00515.
+We acknowledge useful discussions with John R. Kirtley. This work is supported by the Department of Energy
+,  Office of Science, Basic Energy Sciences, Materials Sciences and Engineering Division, under Contract DE-AC02-76SF00515.
 Some of the computing for this project was performed on the Sherlock cluster.
@@
 
-\section{Laplace operator}
+\section{Mesh Laplace and gradient operators}
 \label{appendix:laplace}
 
-The definition of the discrete Laplace operator $\mathbf{\nabla}^2$ (also called the Laplace-Beltrami operator) deserves special attention, as it reduces the problem of solving a partial differential equation $\nabla^2g(x,y)=f(x,y)$ to the problem of solving a matrix equation
-$\mathbf{\nabla}^2\mathbf{g}=\mathbf{f}$~\cite{Reuter2009-hr}.
+The definitions of the Laplace operator $\mathbf{\nabla}^2$ (also called the Laplace-Beltrami operator) and the gradient operator $\vec{\nabla}=(\nabla_x, \nabla_y)^T$ deserve special attention, as these two operators reduce problem of solving a partial differential equation to the problem of solving a matrix equation~\cite{Reuter2009-hr}.
+Given a mesh consisting of $p$ vertices and $t$ triangles, and a scalar field $f(x, y)$ represented by a $p\times 1$ vector $\mathbf{f}$ containing the values of the field at the mesh vertices, the goal is to construct matrices $\nabla^2$ and $\vec{\nabla}=(\nabla_x, \nabla_y)^T$ such that the matrix products $\nabla^2\mathbf{f}$ and $\vec{\nabla}\mathbf{f}$ approximate the Laplacian $\left(\frac{\partial^2f}{\partial x^2}+\frac{\partial^2f}{\partial y^2}\right)$ and the gradient $\left(\frac{\partial f}{\partial x}, \frac{\partial f}{\partial y}\right)$ and  of $f(x, y)$ at the mesh vertices.
+
 As described in Ref.~\cite{Crane_Vouga_2014}, the Laplace operator $\mathbf{\nabla}^2$ for a mesh is defined in terms of two matrices, the mass matrix $\mathbf{M}$ and the
 weak Laplacian matrix $\mathbf{L}$: $\mathbf{\nabla}^2 = \mathbf{M}^{-1}\mathbf{L}$.
-
 In a 2D mesh, the mass matrix $\mathbf{M}$ gives an effective area to each vertex in the mesh.
@@
 
-\section{Spatially inhomogeneous $\Lambda$}
+We construct the two $p\times p$ gradient matrices $\nabla_x$ and $\nabla_y$, using the ``average gradient on a star" (or AGS) approach~\cite{Mancinelli2019-ci}.
+Briefly, we first construct two $t\times p$ matrices, $\vec{\nabla}_t=(\nabla_{t,x}, \nabla_{t,y})^T$ using ``per-cell linear estimation'' (or PCE)~\cite{Mancinelli2019-ci}, where $\nabla_{t,x}\mathbf{f}$ maps the field values at the vertices $\mathbf{f}$ to an estimate of the $x$-component of the gradient at the triangle centroids (centers-of-mass).
+The matrices $\nabla_x$ and $\nabla_y$ are then computed by, for each vertex $i$, taking the weighted average of $\nabla_{t,x}$ and $\nabla_{t,y}$ over adjacent triangles $t\in\mathcal{N}(i)$, with weights given by the angle between the two sides of the triangle adjacent to the vertex.
+The resulting $\vec{\nabla}=(\nabla_x, \nabla_y)^T$ is a $2\times p\times p$ stack of matrices defined such that $\vec{\nabla}\mathbf{f}$ produces a $2\times p$ matrix representing the gradient of $f(x, y)$ at the mesh vertices, with the first and second rows of $\vec{\nabla}\mathbf{f}$ containing the $x$ and $y$ components of the gradient, respectively
+
+\section{Spatially inhomogeneous $\lambda$}
 \label{appendix:inhomogeneous}
+
+One can write out the ``inhomogeneous second London equation'' for a superconductor with spatially-varying London penetration depth $\lambda(\vec{r})$~\cite{Kogan2011-zn}:
+\begin{align}
+\begin{split}
+    \label{eq:london_inhomogeneous_3d}
+    \vec{H}(\vec{r})&=-\vec{\nabla}\times\left(\lambda^2(\vec{r})\vec{j}(\vec{r})\right)\\
+    &=-\left(\lambda^2(\vec{r})\vec{\nabla}\times\vec{j}(\vec{r}) + \vec{\nabla}\lambda^2(\vec{r})\times\vec{j}(\vec{r})\right).
+\end{split}
+\end{align}
+
+In the 2D limit, i.e. a thin film with thickness $d\ll\lambda(x, y)$ lying parallel to the $x-y$ plane carrying sheet current density $\vec{J}(x, y)=\vec{j}(\vec{r})\cdot d$, we have:
+\begin{align}
+\begin{split}
+    \label{eq:london_inhomogeneous_2d}
+    \vec{H}(x, y)&=-\vec{\nabla}\times(\Lambda\vec{J})\\
+    &=-\left(\Lambda\vec{\nabla}\times\vec{J}+\vec{\nabla}\Lambda\times\vec{J}\,\right)\\
+    &=\left(\Lambda\nabla^2g+\vec{\nabla}\Lambda\cdot\vec{\nabla}g\right)\hat{z}
+\end{split}
+\end{align}
+where $\Lambda=\Lambda(x, y)$, $g=g(x, y)$, $\vec{\nabla}=\left(\frac{\partial}{\partial x},\frac{\partial}{\partial y}\right)$, and $\vec{J}=\vec{J}(x, y)=\vec{\nabla}\times(g\hat{z})$.
+
+If one defines an inhomogeneous effective penetration depth $\Lambda(x, y)$ in a \SuperScreen model, Equation~\ref{eq:london_inhomogeneous_2d} is solved numerically as follows.
+For a mesh with $p$ vertices, the penetration depth is represented by a $p\times 1$ vector $\mathbf{\Lambda}$.
+Equations~\ref{eq:Heff_sub_num} and \ref{eq:full_stream} are updated according to:
+\begin{align}
+\begin{split}
+    \label{eq:Heff_inhomogeneous}
+    &\mathbf{Q}.\mathbf{w}^T-\Lambda\mathbf{\nabla}^2\to\\
+    &\mathbf{Q}.\mathbf{w}^T-\mathbf{\Lambda}^T.\mathbf{\nabla}^2-\vec{\nabla}\mathbf{\Lambda}\cdot\vec{\nabla}
+\end{split}
+\end{align}
+The notation $\vec{\nabla}\mathbf{f}\cdot\vec{\nabla}$ indicates an inner (dot) product over the two spatial dimensions, resulting in a $p\times p$ matrix such that $(\vec{\nabla}\mathbf{f}\cdot\vec{\nabla})\mathbf{g}$ computes $(\vec{\nabla}f(x, y))\cdot(\vec{\nabla}g(x, y))$.
+
+Note that, unlike Equation~\ref{eq:london} in which $\Lambda$ is assumed to be constant as a function of position $\pvec{r}$, solutions to Equation~\ref{eq:london_inhomogeneous_2d} with $\vec{\nabla}\Lambda\neq0$ do not necessarily satisfy the fluxoid quantization condition $\Phi^f_S=0$ for a simply-connected superconducting region $S$, where
+\begin{equation}
+	\Phi^f_S=\underbrace{\int_S\mu_0H_z(\pvec{r})\,\mathrm{d}^2r}_{\text{``flux part''}} + \underbrace{\oint_S\mu_0\Lambda(\pvec{r})\vec{J}(\pvec{r})\cdot\mathrm{d}\pvec{r}}_{\text{``supercurrent part''}}.
+\end{equation}
+As a (somewhat contrived) example, Code Block~\ref{code:inhomogeneous} demonstrates how to modify the model of a ring with a slit from Code Block~\ref{code:device} and Figure~\ref{fig:ring-with-slit} such that the ring's penetration depth $\Lambda(x, y)$ increases linearly as a function of the angle between the vector $\vec{r} = (x, y)$ and the $-y$ axis (along which the slit lies).
+The resulting current and field distributions, and the deviation from perfect fluxoid quantization, are shown in Figure~\ref{fig:inhomogeneous}.
+%Note that $\Lambda(x, y)$ must vary slowly on the scale of the spacing between mesh vertices in order for results to be reliable.
+For example, the simulated supercurrent density near a point-like defect (i.e small compared to the triangles in the mesh) associated with a penetration depth $\Lambda_\text{defect}$ in an otherwise uniform film with penetration depth $\Lambda_0\ll\Lambda_\text{defect}$ will depend strongly on the specifics of the mesh near the defect.
+One can avoid this problem by increasing the density of the mesh in regions of fast-varying $\Lambda$ by adding one or more ``abstract regions" to the \inline{Device} as described in Section~\ref{section:overview:device}.
 
@@
  # Calculate the device's response to a uniform applied field.
-applied_field = sc.sources.ConstantField(10)
-solution = sc.solve(device, applied_field=applied_field, field_units="uT")[-1]
+ applied_field = sc.sources.ConstantField(1)
+ solution = sc.solve(device, applied_field=applied_field, field_units="mT")[-1]
  # Visualize the solution.
@@
      \includegraphics[width=\textwidth]{examples/images/ring_with_slit_inhomogeneous.pdf}
-    \caption{The output of Code Block~\ref{code:inhomogeneous}: Meissner screening of a uniform applied field of $10\,\mu\mathrm{T}$ by a ring with a slit in a superconducting film with inhomogeneous effective penetration depth $\Lambda(x, y)$.
-({\bf a}) The inhomogeneous effective penetration depth $\Lambda(x, y)$, with the ring's outline overlaid in orange.
+     \caption{The output of Code Block~\ref{code:inhomogeneous}: Meissner screening of a uniform applied field of $1\,\mathrm{mT}$ by a ring with a slit in a superconducting film with inhomogeneous effective penetration depth $\Lambda(x, y)$.
+({\bf a}) The inhomogeneous effective penetration depth $\Lambda(x, y)$, with the ring's outline overlaid in pink.
+Dashed squares indicate regions $S$ for which we calculate the fluxoid $\Phi^f_S$ in panel ({\bf e}).
 ({\bf b}) The current density $\vec{J}$ in the ring, generated with \inline{Solution.plot_currents()}.
 ({\bf c}) The $z$-component of the magnetic field $\mu_0H_z$ evaluated at the plane of the ring, generated with \inline{Solution.plot_fields()}.
-({\bf d}) The $z$-component of the magnetic field evaluated $z=0.5\,\um$ above the ring (generated using \inline{Solution.plot_field_at_positions()}).}
+({\bf d}) The $z$-component of the magnetic field evaluated $z=0.5\,\um$ above the ring (generated using \inline{Solution.plot_field_at_positions()}).
+({\bf e}) The fluxoid $\Phi^f_S$ for each of the six square fluxoid regions, $S$, shown with dotted lines in ({\bf a}).
+Unlike Equation~\ref{eq:london} (where $\Lambda$ is constant as a function of position), solutions to Equation~\ref{eq:london_inhomogeneous_2d} do not necessarily satisfy fluxoid quantization, $\Phi^f_S=0$ for simply-connected superconducting regions $S$.
+$\Delta=\Phi^f_S / \int_S\mu_0H_z(\vec{r})\,\mathrm{d}^2r$ is the deviation from perfect quantization, i.e.
+the total fluxoid expressed as a percentage of the flux part.
+In general we expect $\Delta$ to be largest in regions $S$ in which the gradient of the effective penetration depth $\vec{\nabla}\Lambda$ is large.}
      \label{fig:inhomogeneous}
@@
 
-As mentioned in Section~\ref{section:overview:device}, the effective penetration depth $\Lambda$ of each layer can be specified as a numeric constant or as a \inline{superscreen.Parameter} that computes $\Lambda(x, y)$, the effective penetration depth as a function of position.
+% As mentioned in Section~\ref{section:overview:device}, the effective penetration depth $\Lambda$ of each layer can be specified as a numeric constant or as a \inline{superscreen.Parameter} that computes $\Lambda(x, y)$, the effective penetration depth as a function of position.
 As a (somewhat contrived) example, Code Block~\ref{code:inhomogeneous} demonstrates how to modify the model of a ring with a slit from Code Block~\ref{code:device} and Figure~\ref{fig:ring-with-slit} such that the ring's penetration depth $\Lambda(x, y)$ increases linearly as a function of the angle between the vector $\vec{r} = (x, y)$ and the $-y$ axis (along which the slit lies).

### 2022-04-14 main.tex
Update text

@@
 All polygons in a device must be simply-connected; a hole in a film is modeled as one \inline{Polygon} instance whose coordinates all lie within the \inline{Polygon} representing the film.
-\inline{Polygons} can constructed and combined using set-theoretic operations.
+\inline{Polygons} can be constructed and combined using set-theoretic operations.
 Table~\ref{table:polygon} shows the four methods available for combining a \inline{supercreen.Polygon} instance \inline{polygonA}, whose vertices lie in set $A$, with a polygon \inline{polygonB}, whose vertices lie in set $B$.
@@
 The least-squares minimization for the model shown in Figure~\ref{fig:fluxoid}, with $N_h=2$, required 18 total calls to \inline{superscreen.solve()}.
-It is important to note that while \SuperScreen can calculate the field and current distributions or a given fluxoid state, the model does not capture transitions between fluxoid states.
+It is important to note that while \SuperScreen can calculate the field and current distributions for a given fluxoid state, the model does not capture transitions between fluxoid states.
 
@@
 
-The definitions of the Laplace operator $\mathbf{\nabla}^2$ (also called the Laplace-Beltrami operator) and the gradient operator $\vec{\nabla}=(\nabla_x, \nabla_y)^T$ deserve special attention, as these two operators reduce problem of solving a partial differential equation to the problem of solving a matrix equation~\cite{Reuter2009-hr}.
-Given a mesh consisting of $p$ vertices and $t$ triangles, and a scalar field $f(x, y)$ represented by a $p\times 1$ vector $\mathbf{f}$ containing the values of the field at the mesh vertices, the goal is to construct matrices $\nabla^2$ and $\vec{\nabla}=(\nabla_x, \nabla_y)^T$ such that the matrix products $\nabla^2\mathbf{f}$ and $\vec{\nabla}\mathbf{f}$ approximate the Laplacian $\left(\frac{\partial^2f}{\partial x^2}+\frac{\partial^2f}{\partial y^2}\right)$ and the gradient $\left(\frac{\partial f}{\partial x}, \frac{\partial f}{\partial y}\right)$ and  of $f(x, y)$ at the mesh vertices.
+The definitions of the Laplace operator $\mathbf{\nabla}^2$ (also called the Laplace-Beltrami operator) and the gradient operator $\vec{\nabla}=(\nabla_x, \nabla_y)^T$ deserve special attention, as these two operators reduce the problem of solving a partial differential equation to the problem of solving a matrix equation~\cite{Reuter2009-hr}.
+Given a mesh consisting of $p$ vertices and $t$ triangles, and a scalar field $f(x, y)$ represented by a $p\times 1$ vector $\mathbf{f}$ containing the values of the field at the mesh vertices, the goal is to construct matrices $\nabla^2$ and $\vec{\nabla}=(\nabla_x, \nabla_y)^T$ such that the matrix products $\nabla^2\mathbf{f}$ and $\vec{\nabla}\mathbf{f}$ approximate the Laplacian $\left(\frac{\partial^2f}{\partial x^2}+\frac{\partial^2f}{\partial y^2}\right)$ and the gradient $\left(\frac{\partial f}{\partial x}, \frac{\partial f}{\partial y}\right)$  of $f(x, y)$ at the mesh vertices.
 
@@
 The matrices $\nabla_x$ and $\nabla_y$ are then computed by, for each vertex $i$, taking the weighted average of $\nabla_{t,x}$ and $\nabla_{t,y}$ over adjacent triangles $t\in\mathcal{N}(i)$, with weights given by the angle between the two sides of the triangle adjacent to the vertex.
-The resulting $\vec{\nabla}=(\nabla_x, \nabla_y)^T$ is a $2\times p\times p$ stack of matrices defined such that $\vec{\nabla}\mathbf{f}$ produces a $2\times p$ matrix representing the gradient of $f(x, y)$ at the mesh vertices, with the first and second rows of $\vec{\nabla}\mathbf{f}$ containing the $x$ and $y$ components of the gradient, respectively
+The resulting $\vec{\nabla}=(\nabla_x, \nabla_y)^T$ is a $2\times p\times p$ stack of matrices defined such that $\vec{\nabla}\mathbf{f}$ produces a $2\times p$ matrix representing the gradient of $f(x, y)$ at the mesh vertices, with the first and second rows of $\vec{\nabla}\mathbf{f}$ containing the $x$ and $y$ components of the gradient, respectively.
 
@@
 
-One can write out the ``inhomogeneous second London equation'' for a superconductor with spatially-varying London penetration depth $\lambda(\vec{r})$~\cite{Kogan2011-zn}:
+The London equation (Equation~\ref{eq:london}) is valid only under the assumption that the London penetration depth $\lambda$, a proxy for the superfluid density, is constant as a function of position~\cite{Tinkham2004-zn}.
+In cases where the superfluid density varies as a function of position, Ginzburg-Landau theory provides a more accurate description of the magnetic response of the system.
+Nevertheless, in an effort to model inhomogeneous superconductors using London theory, one can write out the ``inhomogeneous second London equation'' for a superconductor with spatially-varying London penetration depth $\lambda(\vec{r})$~\cite{Cave1986-js, Kogan2011-zn}:
 \begin{align}
@@
     &=-\left(\Lambda\vec{\nabla}\times\vec{J}+\vec{\nabla}\Lambda\times\vec{J}\,\right)\\
-    &=\left(\Lambda\nabla^2g+\vec{\nabla}\Lambda\cdot\vec{\nabla}g\right)\hat{z}
+    &=\left(\Lambda\nabla^2g+\vec{\nabla}\Lambda\cdot\vec{\nabla}g\right)\hat{z},
 \end{split}
@@
 
-If one defines an inhomogeneous effective penetration depth $\Lambda(x, y)$ in a \SuperScreen model, Equation~\ref{eq:london_inhomogeneous_2d} is solved numerically as follows.
-For a mesh with $p$ vertices, the penetration depth is represented by a $p\times 1$ vector $\mathbf{\Lambda}$.
+If one defines an inhomogeneous effective penetration depth $\Lambda(x, y)$ in a \SuperScreen model, Equation~\ref{eq:london_inhomogeneous_2d}, rather than Equation~\ref{eq:london}, is solved numerically as follows.
+For a mesh with $p$ vertices, the effective penetration depth is represented by a $p\times 1$ vector $\mathbf{\Lambda}$.
 Equations~\ref{eq:Heff_sub_num} and \ref{eq:full_stream} are updated according to:
@@
 \end{align}
-The notation $\vec{\nabla}\mathbf{f}\cdot\vec{\nabla}$ indicates an inner (dot) product over the two spatial dimensions, resulting in a $p\times p$ matrix such that $(\vec{\nabla}\mathbf{f}\cdot\vec{\nabla})\mathbf{g}$ computes $(\vec{\nabla}f(x, y))\cdot(\vec{\nabla}g(x, y))$.
-
-Note that, unlike Equation~\ref{eq:london} in which $\Lambda$ is assumed to be constant as a function of position $\pvec{r}$, solutions to Equation~\ref{eq:london_inhomogeneous_2d} with $\vec{\nabla}\Lambda\neq0$ do not necessarily satisfy the fluxoid quantization condition $\Phi^f_S=0$ for a simply-connected superconducting region $S$, where
+The notation $\vec{\nabla}\mathbf{f}\cdot\vec{\nabla}$ indicates an inner (dot) product over the two spatial dimensions, resulting in a $p\times p$ matrix such that $(\vec{\nabla}\mathbf{f}\cdot\vec{\nabla})\mathbf{g}$ computes $(\vec{\nabla}f(x, y))\cdot(\vec{\nabla}g(x, y))$ (see~\ref{appendix:laplace}).
+
+Note that, unlike Equation~\ref{eq:london} in which $\Lambda$ is assumed to be constant as a function of position $\pvec{r}$, solutions to Equation~\ref{eq:london_inhomogeneous_2d} do not necessarily satisfy the fluxoid quantization condition $\Phi^f_S=0$ for simply-connected superconducting regions $S$ in which $\vec{\nabla}\Lambda(\pvec{r})\neq0$ , where
 \begin{equation}
@@
 \end{equation}
-As a (somewhat contrived) example, Code Block~\ref{code:inhomogeneous} demonstrates how to modify the model of a ring with a slit from Code Block~\ref{code:device} and Figure~\ref{fig:ring-with-slit} such that the ring's penetration depth $\Lambda(x, y)$ increases linearly as a function of the angle between the vector $\vec{r} = (x, y)$ and the $-y$ axis (along which the slit lies).
+%As a (somewhat contrived) example, Code Block~\ref{code:inhomogeneous} demonstrates how to modify the model of a ring with a slit from Code Block~\ref{code:device} and Figure~\ref{fig:ring-with-slit} such that the ring's penetration depth $\Lambda(x, y)$ increases linearly as a function of the angle between the vector $\vec{r} = (x, y)$ and the $-y$ axis (along which the slit lies).
 The resulting current and field distributions, and the deviation from perfect fluxoid quantization, are shown in Figure~\ref{fig:inhomogeneous}.
@@
 
- \begin{code}
- \begin{minted}[fontsize=\small]{python}
- def linear_vs_angle(
-     x: np.ndarray, y: np.ndarray, *, min_val: float, max_val: float
- ) -> np.ndarray:
-     # Rotate the input coordinates so that theta = 0
-     # corresponds to the slit position (along the -y axis).
-     x, y = sc.geometry.rotate(
-         np.stack(np.atleast_1d(x, y), axis=1), np.degrees(-np.pi / 2)
-     ).T
-     # Calculate the angular position of each mesh vertex.
-     angles = np.arctan2(y, x) + np.pi  # range: [0, 2 * pi]
-     # Set Lambda to increase linearly from min_val to max_val
-     # as a function of angular position.
-     Lambdas = angles / (2 * np.pi) * (max_val- min_val) + min_val
-     return Lambdas
-
- # Define the Parameter and assign it as the Lambda of the superconducting layer.
- Lambda = sc.Parameter(linear_vs_angle, min_val=0.1, max_val=1.0)
- device.layers["base"].Lambda = Lambda
- # Everything below is identical to Code Block 1:
- # Calculate the device's response to a uniform applied field.
- applied_field = sc.sources.ConstantField(1)
- solution = sc.solve(device, applied_field=applied_field, field_units="mT")[-1]
- # Visualize the solution.
- # Plot the current density evaluated at each layer in the Device.
- solution.plot_currents()
- # Plot the magnetic field evaluated at each layer in the Device.
- solution.plot_fields()
- # Plot the field evaluated at any points in space.
- solution.plot_field_at_positions(device.points, zs=0.5)
- \end{minted}
- \captionof{listing}{Simulating an inhomogeneous superconducting device.
+% \begin{code}
+% \begin{minted}[fontsize=\small]{python}
+% def linear_vs_angle(
+%     x: np.ndarray, y: np.ndarray, *, min_val: float, max_val: float
+% ) -> np.ndarray:
+%     # Rotate the input coordinates so that theta = 0
+%     # corresponds to the slit position (along the -y axis).
+%     x, y = sc.geometry.rotate(
+%         np.stack(np.atleast_1d(x, y), axis=1), np.degrees(-np.pi / 2)
+%     ).T
+%     # Calculate the angular position of each mesh vertex.
+%     angles = np.arctan2(y, x) + np.pi  # range: [0, 2 * pi]
+%     # Set Lambda to increase linearly from min_val to max_val
+%     # as a function of angular position.
+%     Lambdas = angles / (2 * np.pi) * (max_val- min_val) + min_val
+%     return Lambdas
+%
+% # Define the Parameter and assign it as the Lambda of the superconducting layer.
+% Lambda = sc.Parameter(linear_vs_angle, min_val=0.1, max_val=1.0)
+% device.layers["base"].Lambda = Lambda
+% # Everything below is identical to Code Block 1:
+% # Calculate the device's response to a uniform applied field.
+% applied_field = sc.sources.ConstantField(1)
+% solution = sc.solve(device, applied_field=applied_field, field_units="mT")[-1]
+% # Visualize the solution.
+% # Plot the current density evaluated at each layer in the Device.
+% solution.plot_currents()
+% # Plot the magnetic field evaluated at each layer in the Device.
+% solution.plot_fields()
+% # Plot the field evaluated at any points in space.
+% solution.plot_field_at_positions(device.points, zs=0.5)
+% \end{minted}
+% \captionof{listing}{Simulating an inhomogeneous superconducting device.
 Here we modify the superconducting ring with a slit from Code Block~\ref{code:device} and Figure~\ref{fig:ring-with-slit} to have an effective penetration depth $\Lambda(x, y)$, which increases linearly from $0.1\,\um$ to $1\,\um$ as a function of the angle between the vector $\vec{r}=(x, y)$ and the $-y$ axis.
 See Figure~\ref{fig:inhomogeneous} for the resulting current and field distributions.}
- \label{code:inhomogeneous}
- \end{code}
- \begin{figure*}[h!]
-     \centering
-     \includegraphics[width=\textwidth]{examples/images/ring_with_slit_inhomogeneous.pdf}
-     \caption{The output of Code Block~\ref{code:inhomogeneous}: Meissner screening of a uniform applied field of $1\,\mathrm{mT}$ by a ring with a slit in a superconducting film with inhomogeneous effective penetration depth $\Lambda(x, y)$.
+% \label{code:inhomogeneous}
+% \end{code}
+% \begin{figure*}[h!]
+%     \centering
+%     \includegraphics[width=\textwidth]{examples/images/ring_with_slit_inhomogeneous.pdf}
+%     \caption{The output of Code Block~\ref{code:inhomogeneous}: Meissner screening of a uniform applied field of $1\,\mathrm{mT}$ by a ring with a slit in a superconducting film with inhomogeneous effective penetration depth $\Lambda(x, y)$.
 ({\bf a}) The inhomogeneous effective penetration depth $\Lambda(x, y)$, with the ring's outline overlaid in pink.
@@
 In general we expect $\Delta$ to be largest in regions $S$ in which the gradient of the effective penetration depth $\vec{\nabla}\Lambda$ is large.}
-     \label{fig:inhomogeneous}
- \end{figure*}
+%     \label{fig:inhomogeneous}
+% \end{figure*}
 

### 2022-04-15 main.tex
bump superscreen version to 0.5.0
update tex

@@
 Further details can be found in the online documentation~\cite{superscreen-rtd}.
-The specific version of the package corresponding to this manuscript is \texttt{v0.4.0}.
+The specific version of the package corresponding to this manuscript is \texttt{v0.5.0}.
 
@@
 The mutual inductance values are shown in units of $\Phi_0 / \mathrm{A}$, where $1\,\Phi_0 / \mathrm{A}\approx2.068\times10^{-3}\,\mathrm{pH}$.
-The meshes for the ``Small,'' ``Medium,'' and ``Large'' models consisted of approximately 7,000 vertices and 14,000 triangles, whereas the mesh for the ``X-Large'' model consisted of about 8,000 vertices and 15,000 triangles.
+The meshes for all four models consisted of approximately 6,000 vertices and 12,000 triangles.
 The two smaller models converge more quickly than the two larger models for reasons discussed in \ref{appendix:numerics}.
@@
 \end{equation}
-%As a (somewhat contrived) example, Code Block~\ref{code:inhomogeneous} demonstrates how to modify the model of a ring with a slit from Code Block~\ref{code:device} and Figure~\ref{fig:ring-with-slit} such that the ring's penetration depth $\Lambda(x, y)$ increases linearly as a function of the angle between the vector $\vec{r} = (x, y)$ and the $-y$ axis (along which the slit lies).
-The resulting current and field distributions, and the deviation from perfect fluxoid quantization, are shown in Figure~\ref{fig:inhomogeneous}.
-%Note that $\Lambda(x, y)$ must vary slowly on the scale of the spacing between mesh vertices in order for results to be reliable.
-For example, the simulated supercurrent density near a point-like defect (i.e small compared to the triangles in the mesh) associated with a penetration depth $\Lambda_\text{defect}$ in an otherwise uniform film with penetration depth $\Lambda_0\ll\Lambda_\text{defect}$ will depend strongly on the specifics of the mesh near the defect.
-One can avoid this problem by increasing the density of the mesh in regions of fast-varying $\Lambda$ by adding one or more ``abstract regions" to the \inline{Device} as described in Section~\ref{section:overview:device}.
-
-% \begin{code}
-% \begin{minted}[fontsize=\small]{python}
-% def linear_vs_angle(
-%     x: np.ndarray, y: np.ndarray, *, min_val: float, max_val: float
-% ) -> np.ndarray:
-%     # Rotate the input coordinates so that theta = 0
-%     # corresponds to the slit position (along the -y axis).
-%     x, y = sc.geometry.rotate(
-%         np.stack(np.atleast_1d(x, y), axis=1), np.degrees(-np.pi / 2)
-%     ).T
-%     # Calculate the angular position of each mesh vertex.
-%     angles = np.arctan2(y, x) + np.pi  # range: [0, 2 * pi]
-%     # Set Lambda to increase linearly from min_val to max_val
-%     # as a function of angular position.
-%     Lambdas = angles / (2 * np.pi) * (max_val- min_val) + min_val
-%     return Lambdas
-%
-% # Define the Parameter and assign it as the Lambda of the superconducting layer.
-% Lambda = sc.Parameter(linear_vs_angle, min_val=0.1, max_val=1.0)
-% device.layers["base"].Lambda = Lambda
-% # Everything below is identical to Code Block 1:
-% # Calculate the device's response to a uniform applied field.
-% applied_field = sc.sources.ConstantField(1)
-% solution = sc.solve(device, applied_field=applied_field, field_units="mT")[-1]
-% # Visualize the solution.
-% # Plot the current density evaluated at each layer in the Device.
-% solution.plot_currents()
-% # Plot the magnetic field evaluated at each layer in the Device.
-% solution.plot_fields()
-% # Plot the field evaluated at any points in space.
-% solution.plot_field_at_positions(device.points, zs=0.5)
-% \end{minted}
-% \captionof{listing}{Simulating an inhomogeneous superconducting device.
-Here we modify the superconducting ring with a slit from Code Block~\ref{code:device} and Figure~\ref{fig:ring-with-slit} to have an effective penetration depth $\Lambda(x, y)$, which increases linearly from $0.1\,\um$ to $1\,\um$ as a function of the angle between the vector $\vec{r}=(x, y)$ and the $-y$ axis.
-See Figure~\ref{fig:inhomogeneous} for the resulting current and field distributions.}
-% \label{code:inhomogeneous}
-% \end{code}
-% \begin{figure*}[h!]
-%     \centering
-%     \includegraphics[width=\textwidth]{examples/images/ring_with_slit_inhomogeneous.pdf}
-%     \caption{The output of Code Block~\ref{code:inhomogeneous}: Meissner screening of a uniform applied field of $1\,\mathrm{mT}$ by a ring with a slit in a superconducting film with inhomogeneous effective penetration depth $\Lambda(x, y)$.
-({\bf a}) The inhomogeneous effective penetration depth $\Lambda(x, y)$, with the ring's outline overlaid in pink.
-Dashed squares indicate regions $S$ for which we calculate the fluxoid $\Phi^f_S$ in panel ({\bf e}).
-({\bf b}) The current density $\vec{J}$ in the ring, generated with \inline{Solution.plot_currents()}.
-({\bf c}) The $z$-component of the magnetic field $\mu_0H_z$ evaluated at the plane of the ring, generated with \inline{Solution.plot_fields()}.
-({\bf d}) The $z$-component of the magnetic field evaluated $z=0.5\,\um$ above the ring (generated using \inline{Solution.plot_field_at_positions()}).
-({\bf e}) The fluxoid $\Phi^f_S$ for each of the six square fluxoid regions, $S$, shown with dotted lines in ({\bf a}).
-Unlike Equation~\ref{eq:london} (where $\Lambda$ is constant as a function of position), solutions to Equation~\ref{eq:london_inhomogeneous_2d} do not necessarily satisfy fluxoid quantization, $\Phi^f_S=0$ for simply-connected superconducting regions $S$.
-$\Delta=\Phi^f_S / \int_S\mu_0H_z(\vec{r})\,\mathrm{d}^2r$ is the deviation from perfect quantization, i.e.
-the total fluxoid expressed as a percentage of the flux part.
-In general we expect $\Delta$ to be largest in regions $S$ in which the gradient of the effective penetration depth $\vec{\nabla}\Lambda$ is large.}
-%     \label{fig:inhomogeneous}
-% \end{figure*}
-
-% As mentioned in Section~\ref{section:overview:device}, the effective penetration depth $\Lambda$ of each layer can be specified as a numeric constant or as a \inline{superscreen.Parameter} that computes $\Lambda(x, y)$, the effective penetration depth as a function of position.
-As a (somewhat contrived) example, Code Block~\ref{code:inhomogeneous} demonstrates how to modify the model of a ring with a slit from Code Block~\ref{code:device} and Figure~\ref{fig:ring-with-slit} such that the ring's penetration depth $\Lambda(x, y)$ increases linearly as a function of the angle between the vector $\vec{r} = (x, y)$ and the $-y$ axis (along which the slit lies).
-The resulting current and field distributions are shown in Figure~\ref{fig:inhomogeneous}.
-Note that $\Lambda(x, y)$ must vary slowly on the scale of the spacing between mesh vertices in order for results to be reliable.
-For example, the simulated supercurrent density near a point-like defect (i.e small compared to the triangles in the mesh) associated with a penetration depth $\Lambda_\text{defect}$ in an otherwise uniform film with penetration depth $\Lambda_0\ll\Lambda_\text{defect}$ will depend strongly on the specifics of the mesh near the defect.
-One can avoid this problem by increasing the density of the mesh in regions of fast-varying $\Lambda$ by adding one or more ``abstract regions" to the \inline{Device} as described in Section~\ref{section:overview:device}.
 

### 2022-04-15 main.tex
Abstract

@@
 Here, we introduce \SuperScreen, an open-source Python package for simulating the response of 2D superconductors to trapped flux and applied time-independent or quasi-DC magnetic fields for any value of the effective magnetic penetration depth, $\Lambda$.
-Given an applied magnetic field, \SuperScreen solves the 2D London equation using an efficient matrix inversion method~\cite{Brandt2004-ew, Brandt2005-wj} to obtain the Meissner currents and magnetic fields in and around structures composed of one or more superconducting thin films of arbitrary geometry with spatially nonuniform magnetic penetration depth.
+Given an applied magnetic field, \SuperScreen solves the 2D London equation using an efficient matrix inversion method~\cite{Brandt2004-ew, Brandt2005-wj} to obtain the Meissner currents and magnetic fields in and around structures composed of one or more superconducting thin films of arbitrary geometry.
 \SuperScreen can be used to model screening effects and calculate self- and mutual-inductance in thin film superconducting devices.

### 2022-06-06 response-to-reviewer-comments.tex
Updates from Overleaf

\documentclass{article} % This command is used to set the type of document you are working on such as an article, book, or presenation

\usepackage{geometry} % This package allows the editing of the page layout
\usepackage{amsmath}  % This package allows the use of a large range of mathematical formula, commands, and symbols
\usepackage{graphicx}  % This package allows the importing of images

\title{Response to reviewer comments}
\author{Logan Bishop-Van Horn}
\date{\today}

\begin{document}
\maketitle

\section{Reviewer 1}

\begin{itemize}
    \item{
    {\bf Reviewer comment:} ``The manuscript is well written and the work is of interest to the applied superconductivity community.''

    {\bf Author response:} We are glad that the reviewer found the paper to be well written, and we agree that the software and manuscript will be valuable to the applied superconductivity community.
    }
    \item{
    {\bf Reviewer comment:} ``The software works, although the implementation is a bit slower and more memory hungry than commercial or closed-source tools.''

    {\bf Author response:} It is true that the software favors portability and simplicity of implementation over raw performance, likely making it less efficient than some commercial or closed-source tools. We do not see SuperScreen as a competitor to or replacement for superconducting electronic design automation (EDA) and inductance extraction tools such as InductEx and FastHenry. Rather, we see SuperScreen as a complementary research tool for modeling experiments involving 2D superconductors and mesoscopic superconducting devices, as opposed to designing superconducting integrated circuits. 
    }
    \item{
    {\bf Reviewer comment:} ``The reference to [16] for a review of inductance extraction is a bit old -- newer tools and methods and publications exist.''

    {\bf Author response:} Reference 16 is indeed a bit old. We have added more recent references
    }
    \item{
    {\bf Reviewer comment:} ``P.4, Left Column, Line 53: `though' should be `through'.''

    {\bf Author response:} Thank you for the careful reading and for catching this typo. The typo has been fixed in the revised version of the manuscript.
    }
\end{itemize}

\section{Reviewer 2}
\begin{itemize}
    \item{
    {\bf Reviewer comment:} ``Highlights and graphical abstract could be provided.''

    {\bf Author response:}
    }
    \item{
    {\bf Reviewer comment:} ``As there are many other similar works available, please provide a strong literature survey.''

    {\bf Author response:}
    }
    \item{
    {\bf Reviewer comment:} ``A comparison of the work with state of the art is necessary.''

    {\bf Author response:}
    }
\end{itemize}

\end{document}

### 2022-06-06 main.tex
Updates from Overleaf

--- 2022-04-14 main.tex
@@
 
-There have been many previous numerical studies of magnetic screening and inductance extraction in thin film and two-dimensional (2D) superconducting devices~\cite{Jaycox1981-zl, Ketchen1982-at, Ketchen2012-mb, Hildebrandt1995-uw, Khapaev1997-kw, Khapaev2001-xq, Khapaev2001-pw, Babaei_Brojeny2003-la, Brandt2004-ew, Brandt2005-wj, Clem2005-ye, Muller2021-ci, Jackman2016-mf}.
-However, few software tools for this task exist and those that are available are closed-source, are written in low-level compiled languages like C, and/or require the use of specialized file formats or separate computer aided design (CAD) software for defining device geometries and model configurations.\footnote{A brief summary of existing tools can be found in \ref{appendix:other-tools}, and a more thorough overview in Ref.~\cite{Gaj1999-ls}.} Most of these tools are intended for use in the design of superconducting integrated circuits for single flux quantum (SFQ) logic and are primarily used for inductance extraction~\cite{Gaj1999-ls}.
+There have been many previous numerical studies of magnetic screening and inductance extraction in thin film and two-dimensional (2D) superconducting devices~\cite{Jaycox1981-zl, Ketchen1982-at, Ketchen2012-mb, Hildebrandt1995-uw, Khapaev1997-kw, Khapaev2001-xq, Khapaev2001-pw, Khapaev2002-ev,  Babaei_Brojeny2003-la, Brandt2004-ew, Brandt2005-wj, Clem2005-ye, Muller2021-ci, Fourie2011-wl, Fourie2012-gv, Jackman2016-mf}.
+However, few software tools for this task exist and those that are available are closed-source, are written in low-level compiled languages like C, and/or require the use of specialized file formats or separate computer aided design (CAD) software for defining device geometries and model configurations.\footnote{A brief summary of existing tools can be found in \ref{appendix:other-tools}, and a more thorough overview in Ref.~\cite{Gaj1999-ls}.} Most of these tools are intended for use in the design of superconducting integrated circuits for single flux quantum (SFQ) logic and are primarily used for inductance extraction~\cite{Gaj1999-ls, Tolpygo2021-jz}.
 \SuperScreen is an open-source, user-friendly, portable research tool designed to lower the barrier to entry to quantitative modeling of 2D superconductors, and to help interpret and inform measurements of superconducting thin films and devices.
@@
 where $\Lambda=\lambda^2/d$ is the effective penetration depth
-of the superconducting film (equal to half the Pearl length~\cite{Pearl1964-cl}) and now $\vec{\nabla}=\left(\frac{\partial}{\partial x}, \frac{\partial}{\partial y}\right)$.
+of the superconducting film (equal to half the Pearl length~\cite{Pearl1964-cl}) and $\vec{\nabla}=\left(\frac{\partial}{\partial x}, \frac{\partial}{\partial y}\right)$ is now the 2D gradient operator.
 
@@
 We can rewrite Eq.~\ref{eq:london}, which gives the magnetic field inside of a 2D film, in terms of $g$:
+% \begin{align}
+%     \label{eq:london_stream}
+%     \begin{split}
+%         \vec{H}(x, y) &= -\Lambda\left[\nabla\times\vec{J}(x, y)\right]\\
+%         &= -\Lambda\left[\nabla\times\left(\nabla\times(g\hat{z})\right)\right]\\
+%         &= -\Lambda\left[\nabla(\nabla\cdot(g\hat{z}))-\nabla^2(g\hat{z})\right]\\
+%         &=\Lambda\nabla^2g(x,y)\hat{z},
+%     \end{split}
+% \end{align}
 \begin{align}
@@
 
-Convergence can be quantified by, for example, calculating the total magnetic flux though all films and holes in the model at the end of each iteration.
+Convergence can be quantified by, for example, calculating the total magnetic flux through all films and holes in the model at the end of each iteration.
 In general, the more layers there are in a structure the more iterations are  required to reach a given level of convergence.
@@
 Column vectors are treated as matrices with $\ell$ rows and 1 column.
-We denote element-wise multiplication with a lower dot, $(\mathbf{A}.\mathbf{B})_{ij}=A_{ij}B_{ij}$, and $\mathbf{A}^T$ denotes the transpose of matrix $\mathbf{A}$.
+On the other hand, we denote element-wise multiplication with a lower dot: $(\mathbf{A}.\mathbf{B})_{ij}=A_{ij}B_{ij}$ for two matrices
+and $(\mathbf{A}.\mathbf{v})_{ij}=(\mathbf{v}.\mathbf{A})_{ij}=A_{ij}v_{i}$ for a matrix $\mathbf{A}$ and a column vector $\mathbf{v}$. $\mathbf{A}^T$ denotes the transpose of matrix $\mathbf{A}$.
 
@@
     Q_{ij} = (\delta_{ij}-1)q_{ij}
-    + \delta_{ij}\frac{1}{w_{j}}\left(C_i + \sum_{l\neq i}q_{il}w_{l}\right),
+    + \delta_{ij}\frac{1}{w_{ij}}\left(C_i + \sum_{l\neq i}q_{il}w_{il}\right),
 \end{equation}
@@
 All polygons in a device must be simply-connected; a hole in a film is modeled as one \inline{Polygon} instance whose coordinates all lie within the \inline{Polygon} representing the film.
-\inline{Polygons} can be constructed and combined using set-theoretic operations.
+\inline{Polygons} can constructed and combined using set-theoretic operations.
 Table~\ref{table:polygon} shows the four methods available for combining a \inline{supercreen.Polygon} instance \inline{polygonA}, whose vertices lie in set $A$, with a polygon \inline{polygonB}, whose vertices lie in set $B$.
@@
 applied_field = sc.sources.ConstantField(10)
-solution = sc.solve(device, applied_field=applied_field, field_units="mT")[-1]
+solution = sc.solve(device, applied_field=applied_field, field_units="uT")[-1]
 # Visualize the solution.
@@
     \includegraphics[width=\textwidth]{examples/images/ring_with_slit.pdf}
-    \caption{The output of Code Block~\ref{code:device}: Meissner screening of a uniform $1\,\mathrm{mT}$ out-of-plane field by a ring with inner diameter $1\,\um$, outer diameter $3\,\um$, and effective penetration depth $\Lambda=1\,\um$, interrupted by a slit of width $0.25\,\um$.
+    \caption{The output of Code Block~\ref{code:device}: Meissner screening of a uniform $10\,\mu\mathrm{T}$ out-of-plane field by a ring with inner diameter $1\,\um$, outer diameter $3\,\um$, and effective penetration depth $\Lambda=1\,\um$, interrupted by a slit of width $0.25\,\um$.
 ({\bf a}) Plot of the boundary of the ring (blue), circular bounding box (orange), and the computational mesh (gray), generated with \inline{Device.plot()}.
@@
 The least-squares minimization for the model shown in Figure~\ref{fig:fluxoid}, with $N_h=2$, required 18 total calls to \inline{superscreen.solve()}.
-It is important to note that while \SuperScreen can calculate the field and current distributions for a given fluxoid state, the model does not capture transitions between fluxoid states.
+It is important to note that while \SuperScreen can calculate the field and current distributions or a given fluxoid state, the model does not capture transitions between fluxoid states.
 
@@
 Figure~\ref{fig:inductance} shows a comparison between these previous numerical results and the results from \SuperScreen.
-Note that the models used by Brandt and Clem (solid lines) and by the LCR2D software (blue diamonds) require a circularly symmetric superconducting film, whereas \SuperScreen (filled circles) and 3D-MLSI~\cite{Khapaev1997-kw, Khapaev2001-xq, Khapaev2001-pw} (blue squares) support arbitrary 2D geometry.
+Note that the models used by Brandt and Clem (solid lines) and by the LCR2D software (blue diamonds) require a circularly symmetric superconducting film, whereas \SuperScreen (filled circles) and 3D-MLSI~\cite{Khapaev1997-kw} (blue squares) support arbitrary 2D geometry.
 
@@
 This means that inductance calculations are limited to structures with holes, in which all applied currents are circulating currents associated with trapped flux.
-Terminal currents can, however, be included in stream function-based models by setting appropriate boundary conditions~\cite{Khapaev1997-kw,Khapaev2001-xq,Khapaev2001-pw,Muller2021-ci}.
+Terminal currents can, however, be included in stream function-based models by setting appropriate boundary conditions~\cite{Khapaev1997-kw,Khapaev2001-xq,Khapaev2001-pw, Khapaev2002-ev, Muller2021-ci}.
 An extension to the model described above that treats the magnetic response of a superconducting ring interrupted by two Josephson junctions (i.e.
@@
 FastHenry, a widely-used 3D (normal metal) inductance extraction tool from MIT~\cite{Kamon1994-ck}, has been extended to support superconducting elements~\cite{wrcad, XicTools}.
-This modified version of FastHenry has been used for inductance extraction in the commercial software InductEx~\cite{Fourie2011-wl}.
+This modified version of FastHenry has been used for inductance extraction in the commercial software InductEx~\cite{Fourie2011-wl, Fourie2012-gv, Jackman2016-mf}.
 While FastHenry is open-source, it is written in C and must be compiled for a specific computer architecture and operating system.
 FastHenry executables compiled for several common operating systems are available as part of the open-source XicTools superconducting integrated circuit design suite from Whiteley Research, Inc~\cite{wrcad, XicTools}.
-A 2D London model based on a scalar stream function, much like the model used by \SuperScreen~\cite{Brandt2004-ew, Brandt2005-wj}, forms the basis of the 3D-MLSI software package~\cite{Khapaev1997-kw, Khapaev2001-xq, Khapaev2001-pw}, which is also written in C and is not open-source.
-For a more thorough overview and comparison of inductance extraction tools, see Ref.~\cite{Gaj1999-ls}.
+A 2D London model based on a scalar stream function, much like the model used by \SuperScreen~\cite{Brandt2004-ew, Brandt2005-wj}, forms the basis of the 3D-MLSI software package~\cite{Khapaev1997-kw, Khapaev2001-xq, Khapaev2001-pw, Khapaev2002-ev}, which is also written in C and is not open-source.
+For a thorough historical overview and comparison of inductance extraction tools, see Ref.~\cite{Gaj1999-ls}.
+For a more recent overview of superconducting inductance extraction tools see Ref.~\cite{Tolpygo2021-jz}, particularly references [8--25] therein.
+
+\SuperScreen is not intended primarily as an inductance extraction tool and cannot be used to extract the inductance of superconducting transmission lines (a common superconducting circuit design task~\cite{Gaj1999-ls,Khapaev1996-uu,Tolpygo2021-jz}) due to the lack of support for ``terminal currents.'' Nevertheless, it is instructive to compare \SuperScreen to a state of the art commercial inductance extraction tool, InductEx~\cite{Fourie2011-wl, Fourie2012-gv, Jackman2016-mf}, on a problem that can be solved using both tools.
+One such problem, provided as an example in the InductEx user manual, is the self-inductance $L$ of a square washer with outer dimension $30\,\um$, inner dimension $10\,\um$, London penetration depth $\lambda=0.24\,\um$, and film thickness $d=0.20\,\um$, for which the InductEx solution reports a ``design'' value of $L=20\,\mathrm{pH}$ and an ``extracted'' value of $L=20.0956\,\mathrm{pH}$~\cite{inductex_user_manual_2020}.
+Code Block~\ref{code:washer} demonstrates how to solve this problem using \SuperScreen.
+The inductance extracted using \SuperScreen is within 1\% of the inductance extracted using InductEx.
+
+\begin{code-onecol}
+\begin{minted}[fontsize=\small]{python}
+import superscreen as sc
+from superscreen.geometry import box
+
+layer = sc.Layer(
+    "base",
+    london_lambda=0.24,
+    thickness=0.2,
+)
+film = sc.Polygon(
+    "washer",
+    layer="base",
+    points=box(30, points_per_side=50),
+)
+hole = sc.Polygon(
+    "hole",
+    layer="base",
+    points=box(10, points_per_side=250),
+)
+device = sc.Device(
+    "washer",
+    layers=[layer],
+    films=[film],
+    holes=[hole],
+    length_units="um",
+)
+device.make_mesh(min_points=3000)
+# See Equation 19.
+M = device.mutual_inductance_matrix()
+L = M[0, 0].to("pH")
+print(f"Inductance = {L:~.4fP}")
+# Output: Inductance = 19.9100 pH
+\end{minted}
+\captionof{listing}{\SuperScreen script to calculate the self-inductance of a square washer.
+The extracted inductance $L=19.91\,\mathrm{pH}$ differs from the InductEx ``design'' and ``extracted'' values by -0.45\% and -0.92\% respectively~\cite{inductex_user_manual_2020}.
+}
+\label{code:washer}
+\end{code-onecol}
 
@@
 
-The definitions of the Laplace operator $\mathbf{\nabla}^2$ (also called the Laplace-Beltrami operator) and the gradient operator $\vec{\nabla}=(\nabla_x, \nabla_y)^T$ deserve special attention, as these two operators reduce the problem of solving a partial differential equation to the problem of solving a matrix equation~\cite{Reuter2009-hr}.
-Given a mesh consisting of $p$ vertices and $t$ triangles, and a scalar field $f(x, y)$ represented by a $p\times 1$ vector $\mathbf{f}$ containing the values of the field at the mesh vertices, the goal is to construct matrices $\nabla^2$ and $\vec{\nabla}=(\nabla_x, \nabla_y)^T$ such that the matrix products $\nabla^2\mathbf{f}$ and $\vec{\nabla}\mathbf{f}$ approximate the Laplacian $\left(\frac{\partial^2f}{\partial x^2}+\frac{\partial^2f}{\partial y^2}\right)$ and the gradient $\left(\frac{\partial f}{\partial x}, \frac{\partial f}{\partial y}\right)$  of $f(x, y)$ at the mesh vertices.
+The definitions of the Laplace operator $\mathbf{\nabla}^2$ (also called the Laplace-Beltrami operator) and the gradient operator $\vec{\nabla}=(\nabla_x, \nabla_y)^T$ deserve special attention, as these two operators reduce problem of solving a partial differential equation to the problem of solving a matrix equation~\cite{Reuter2009-hr}.
+Given a mesh consisting of $p$ vertices and $t$ triangles, and a scalar field $f(x, y)$ represented by a $p\times 1$ vector $\mathbf{f}$ containing the values of the field at the mesh vertices, the goal is to construct matrices $\nabla^2$ and $\vec{\nabla}=(\nabla_x, \nabla_y)^T$ such that the matrix products $\nabla^2\mathbf{f}$ and $\vec{\nabla}\mathbf{f}$ approximate the Laplacian $\left(\frac{\partial^2f}{\partial x^2}+\frac{\partial^2f}{\partial y^2}\right)$ and the gradient $\left(\frac{\partial f}{\partial x}, \frac{\partial f}{\partial y}\right)$ and  of $f(x, y)$ at the mesh vertices.
 
@@
 The matrices $\nabla_x$ and $\nabla_y$ are then computed by, for each vertex $i$, taking the weighted average of $\nabla_{t,x}$ and $\nabla_{t,y}$ over adjacent triangles $t\in\mathcal{N}(i)$, with weights given by the angle between the two sides of the triangle adjacent to the vertex.
-The resulting $\vec{\nabla}=(\nabla_x, \nabla_y)^T$ is a $2\times p\times p$ stack of matrices defined such that $\vec{\nabla}\mathbf{f}$ produces a $2\times p$ matrix representing the gradient of $f(x, y)$ at the mesh vertices, with the first and second rows of $\vec{\nabla}\mathbf{f}$ containing the $x$ and $y$ components of the gradient, respectively.
+The resulting $\vec{\nabla}=(\nabla_x, \nabla_y)^T$ is a $2\times p\times p$ stack of matrices defined such that $\vec{\nabla}\mathbf{f}$ produces a $2\times p$ matrix representing the gradient of $f(x, y)$ at the mesh vertices, with the first and second rows of $\vec{\nabla}\mathbf{f}$ containing the $x$ and $y$ components of the gradient, respectively
 
@@
 
-The London equation (Equation~\ref{eq:london}) is valid only under the assumption that the London penetration depth $\lambda$, a proxy for the superfluid density, is constant as a function of position~\cite{Tinkham2004-zn}.
-In cases where the superfluid density varies as a function of position, Ginzburg-Landau theory provides a more accurate description of the magnetic response of the system.
-Nevertheless, in an effort to model inhomogeneous superconductors using London theory, one can write out the ``inhomogeneous second London equation'' for a superconductor with spatially-varying London penetration depth $\lambda(\vec{r})$~\cite{Cave1986-js, Kogan2011-zn}:
+One can write out the ``inhomogeneous second London equation'' for a superconductor with spatially-varying London penetration depth $\lambda(\vec{r})$~\cite{Kogan2011-zn}:
 \begin{align}
@@
     \vec{H}(\vec{r})&=-\vec{\nabla}\times\left(\lambda^2(\vec{r})\vec{j}(\vec{r})\right)\\
-    &=-\left(\lambda^2(\vec{r})\vec{\nabla}\times\vec{j}(\vec{r}) + \vec{\nabla}\lambda^2(\vec{r})\times\vec{j}(\vec{r})\right).
+    &=-\left(\lambda^2(\vec{r})\vec{\nabla}\times\vec{j}(\vec{r}) + 2\lambda(\vec{r})\vec{\nabla}\lambda(\vec{r})\times\vec{j}(\vec{r})\right).
 \end{split}
@@
     \vec{H}(x, y)&=-\vec{\nabla}\times(\Lambda\vec{J})\\
-    &=-\left(\Lambda\vec{\nabla}\times\vec{J}+\vec{\nabla}\Lambda\times\vec{J}\,\right)\\
-    &=\left(\Lambda\nabla^2g+\vec{\nabla}\Lambda\cdot\vec{\nabla}g\right)\hat{z},
+    &=-\left(\Lambda\vec{\nabla}\times\vec{J}+\lambda\vec{\nabla}\Lambda\times\vec{J}\,\right)\\
+    &=\left(\Lambda\nabla^2g+\vec{\nabla}\Lambda\cdot\vec{\nabla}g\right)\hat{z}
 \end{split}
@@
 
-If one defines an inhomogeneous effective penetration depth $\Lambda(x, y)$ in a \SuperScreen model, Equation~\ref{eq:london_inhomogeneous_2d}, rather than Equation~\ref{eq:london}, is solved numerically as follows.
-For a mesh with $p$ vertices, the effective penetration depth is represented by a $p\times 1$ vector $\mathbf{\Lambda}$.
+If one defines an inhomogeneous effective penetration depth $\Lambda(x, y)$ in a \SuperScreen model, Equation~\ref{eq:london_inhomogeneous_2d} is solved numerically as follows.
+For a mesh with $p$ vertices, the penetration depth is represented by a $p\times 1$ vector $\mathbf{\Lambda}$.
 Equations~\ref{eq:Heff_sub_num} and \ref{eq:full_stream} are updated according to:
@@
 \begin{split}
-    \label{eq:Heff_inhomogeneous}
     &\mathbf{Q}.\mathbf{w}^T-\Lambda\mathbf{\nabla}^2\to\\
@@
 \end{align}
-The notation $\vec{\nabla}\mathbf{f}\cdot\vec{\nabla}$ indicates an inner (dot) product over the two spatial dimensions, resulting in a $p\times p$ matrix such that $(\vec{\nabla}\mathbf{f}\cdot\vec{\nabla})\mathbf{g}$ computes $(\vec{\nabla}f(x, y))\cdot(\vec{\nabla}g(x, y))$ (see~\ref{appendix:laplace}).
-
-Note that, unlike Equation~\ref{eq:london} in which $\Lambda$ is assumed to be constant as a function of position $\pvec{r}$, solutions to Equation~\ref{eq:london_inhomogeneous_2d} do not necessarily satisfy the fluxoid quantization condition $\Phi^f_S=0$ for simply-connected superconducting regions $S$ in which $\vec{\nabla}\Lambda(\pvec{r})\neq0$ , where
-\begin{equation}
-	\Phi^f_S=\underbrace{\int_S\mu_0H_z(\pvec{r})\,\mathrm{d}^2r}_{\text{``flux part''}} + \underbrace{\oint_S\mu_0\Lambda(\pvec{r})\vec{J}(\pvec{r})\cdot\mathrm{d}\pvec{r}}_{\text{``supercurrent part''}}.
-\end{equation}
-%As a (somewhat contrived) example, Code Block~\ref{code:inhomogeneous} demonstrates how to modify the model of a ring with a slit from Code Block~\ref{code:device} and Figure~\ref{fig:ring-with-slit} such that the ring's penetration depth $\Lambda(x, y)$ increases linearly as a function of the angle between the vector $\vec{r} = (x, y)$ and the $-y$ axis (along which the slit lies).
-The resulting current and field distributions, and the deviation from perfect fluxoid quantization, are shown in Figure~\ref{fig:inhomogeneous}.
-%Note that $\Lambda(x, y)$ must vary slowly on the scale of the spacing between mesh vertices in order for results to be reliable.
-For example, the simulated supercurrent density near a point-like defect (i.e small compared to the triangles in the mesh) associated with a penetration depth $\Lambda_\text{defect}$ in an otherwise uniform film with penetration depth $\Lambda_0\ll\Lambda_\text{defect}$ will depend strongly on the specifics of the mesh near the defect.
-One can avoid this problem by increasing the density of the mesh in regions of fast-varying $\Lambda$ by adding one or more ``abstract regions" to the \inline{Device} as described in Section~\ref{section:overview:device}.
+The notation $\vec{\nabla}\mathbf{f}\cdot\vec{\nabla}$ indicates an inner (dot) product over the two spatial dimensions, resulting in a $p\times p$ matrix such that $(\vec{\nabla}\mathbf{f}\cdot\vec{\nabla})\mathbf{g}$ computes $(\vec{\nabla}f(x, y))\cdot(\vec{\nabla}g(x, y))$.
 
@@
 %     return Lambdas
-%
+
 % # Define the Parameter and assign it as the Lambda of the superconducting layer.
@@
 % # Calculate the device's response to a uniform applied field.
-% applied_field = sc.sources.ConstantField(1)
-% solution = sc.solve(device, applied_field=applied_field, field_units="mT")[-1]
+% applied_field = sc.sources.ConstantField(10)
+% solution = sc.solve(device, applied_field=applied_field, field_units="uT")[-1]
 % # Visualize the solution.
@@
 %     \includegraphics[width=\textwidth]{examples/images/ring_with_slit_inhomogeneous.pdf}
-%     \caption{The output of Code Block~\ref{code:inhomogeneous}: Meissner screening of a uniform applied field of $1\,\mathrm{mT}$ by a ring with a slit in a superconducting film with inhomogeneous effective penetration depth $\Lambda(x, y)$.
-({\bf a}) The inhomogeneous effective penetration depth $\Lambda(x, y)$, with the ring's outline overlaid in pink.
-Dashed squares indicate regions $S$ for which we calculate the fluxoid $\Phi^f_S$ in panel ({\bf e}).
+%     \caption{The output of Code Block~\ref{code:inhomogeneous}: Meissner screening of a uniform applied field of $10\,\mu\mathrm{T}$ by a ring with a slit in a superconducting film with inhomogeneous effective penetration depth $\Lambda(x, y)$.
+({\bf a}) The inhomogeneous effective penetration depth $\Lambda(x, y)$, with the ring's outline overlaid in orange.
 ({\bf b}) The current density $\vec{J}$ in the ring, generated with \inline{Solution.plot_currents()}.
 ({\bf c}) The $z$-component of the magnetic field $\mu_0H_z$ evaluated at the plane of the ring, generated with \inline{Solution.plot_fields()}.
-({\bf d}) The $z$-component of the magnetic field evaluated $z=0.5\,\um$ above the ring (generated using \inline{Solution.plot_field_at_positions()}).
-({\bf e}) The fluxoid $\Phi^f_S$ for each of the six square fluxoid regions, $S$, shown with dotted lines in ({\bf a}).
-Unlike Equation~\ref{eq:london} (where $\Lambda$ is constant as a function of position), solutions to Equation~\ref{eq:london_inhomogeneous_2d} do not necessarily satisfy fluxoid quantization, $\Phi^f_S=0$ for simply-connected superconducting regions $S$.
-$\Delta=\Phi^f_S / \int_S\mu_0H_z(\vec{r})\,\mathrm{d}^2r$ is the deviation from perfect quantization, i.e.
-the total fluxoid expressed as a percentage of the flux part.
-In general we expect $\Delta$ to be largest in regions $S$ in which the gradient of the effective penetration depth $\vec{\nabla}\Lambda$ is large.}
+({\bf d}) The $z$-component of the magnetic field evaluated $z=0.5\,\um$ above the ring (generated using \inline{Solution.plot_field_at_positions()}).}
 %     \label{fig:inhomogeneous}

### 2022-06-06 main.tex

--- 2022-04-15 main.tex
@@
 \end{align}
+
 The notation $\vec{\nabla}\mathbf{f}\cdot\vec{\nabla}$ indicates an inner (dot) product over the two spatial dimensions, resulting in a $p\times p$ matrix such that $(\vec{\nabla}\mathbf{f}\cdot\vec{\nabla})\mathbf{g}$ computes $(\vec{\nabla}f(x, y))\cdot(\vec{\nabla}g(x, y))$ (see~\ref{appendix:laplace}).

### 2022-06-06 response-to-reviewer-comments.tex
Updates from Overleaf

@@
 
-    {\bf Author response:} Reference 16 is indeed a bit old. We have added more recent references
+    {\bf Author response:} Reference [16] (Gaj, \emph{et al.}) is indeed a bit old.
+We have added more recent references about inductance extraction tools to Appendix A.
+In particular, Tolpygo, \emph{et al.} 2021 Supercond.
+Sci.
+Technol.
+{\bf 34} 085005 (which is now cited as reference [20]) and references [8--25] therein provide a thorough and up-to-date survey of inductance extraction software.
     }
@@
 
-    {\bf Author response:} Thank you for the careful reading and for catching this typo. The typo has been fixed in the revised version of the manuscript.
+    {\bf Author response:} Thank you for reading the manuscript carefully and catching this typo. The typo has been fixed in the revised version of the manuscript.
     }
@@
 
-    {\bf Author response:}
+    {\bf Author response:} Thank you for the suggestion. We have included highlights and a graphical abstract in the revised submission.
     }
@@
 
-    {\bf Author response:}
+    {\bf Author response:} The introductory section provides a survey of the literature of numerical modeling of 2D superconductors (references 1--20).
+In terms of surveying available software tools, we have added more recent references about inductance extraction tools to Appendix A.
+In particular, Tolpygo, \emph{et al.} 2021 Supercond.
+Sci.
+Technol.
+{\bf 34} 085005 (which is now cited as reference [20]) and references [8--25] therein provide a thorough and up-to-date survey of inductance extraction software.
     }
@@
 
-    {\bf Author response:}
+    {\bf Author response:} Figure 4 provides a comparison between SuperScreen, 3D-MLSI, LCR2D, and the axisymmetric model by  Brandt and Clem.
+The problem shown in Figure 4 (the self-inductance of an annulus as a function of the effective penetration depth $\Lambda$, inner radius $a$, and outer radius $b$) is the only problem for which we were able to find solutions from multiple methods in the literature.
+This problem also has an analytical solution in the limit $\Lambda=0$ and $a/b\to 0$.
+All of the numerical methods, including SuperScreen, agree well with the analytical solution in this limit.
+
+    To the best of our knowledge, the ``state of the art'' commercial tool for modeling the magnetic response of superconductors is InductEx.
+We have added to Appendix A an example problem from the InductEx user manual, namely the self-inductance of a thin film square washer.
+Code Block 3 in Appendix A, which we have added in the revised version of the manuscript, demonstrates that SuperScreen and InductEx agree to within 1\% on this problem.
     }
@@
 
+\section{Inhomogeneous films}
+
+After submitting the manuscript and posting the submitted version to arXiv.org, Dr.
+Vladimir G.
+Kogan brought to our attention his work on London modeling of superconductors with inhomogeneous penetration depth (V.
+G.
+Kogan \& J.
+R.
+Kirtley, Phys.
+Rev.
+B {\bf 83}, 214521 (2011)) and pointed out the existence of an additional term in the 2nd London equation for inhomogeneous superconductors, which is proportional to the gradient of the effective penetration depth, $\vec{\nabla}\Lambda$.
+
+We have modified the software so that this term is included if the user specifies an inhomogeneous penetration depth and have moved all discussion of inhomogeneous films from the main text into Appendix C, where we have clarified the applicability of the London model to films with inhomogeneous penetration depth based on V.
+G.
+Kogan \& J.
+R.
+Kirtley, Phys.
+Rev.
+B {\bf 83}, 214521 (2011) and J.
+R.
+Cave \& J.
+E.
+Evetts, Journal of Low Temperature Physics {\bf 63}, 35–55 (1986) (references [52] and [51] respectively in the revised manuscript).
+We also removed from Appendix C the example code (Code Block 3: Simulating an inhomogeneous superconducting device) and the accompanying Figure C.7.
+The main results of the manuscript are completely unchanged.
 \end{document}

### 2022-06-06 highlights.tex
Updates from Overleaf

\documentclass{article} % This command is used to set the type of document you are working on such as an article, book, or presenation

\usepackage{geometry} % This package allows the editing of the page layout
\usepackage{amsmath}  % This package allows the use of a large range of mathematical formula, commands, and symbols

\title{Highlights}
\date{\today}

\begin{document}
\maketitle
\begin{itemize}
    \item{SuperScreen is an open-source Python package that solves the London equation to simulate the Meissner response of two-dimensional superconductors for any value of the effective magnetic penetration depth.}
    \item{The package provides an intuitive object-oriented interface for the creation of models with complex geometries, and for post-processing and visualization of simulation results.}
    \item{The package can be used to calculate self- and mutual inductance in thin film superconducting devices.}
    \item{SuperScreen can be used to model flux trapping and fluxoid quantization effects and calculate the supercurrent distribution due to Pearl vortices in two-dimensional superconductors.}
    \item{SuperScreen enables quantitative modeling of the supercurrent distribution in mesoscopic superconducting devices to help inform and interpret measurements.}
\end{itemize}
\end{document}

### 2022-06-06 main.tex

@@
 )
-device.make_mesh(min_points=3500, optimesh_steps=None)
+device.make_mesh(min_points=3500)
 device.plot(mesh=True)
@@
 FastHenry executables compiled for several common operating systems are available as part of the open-source XicTools superconducting integrated circuit design suite from Whiteley Research, Inc~\cite{wrcad, XicTools}.
-A 2D London model based on a scalar stream function, much like the model used by \SuperScreen~\cite{Brandt2004-ew, Brandt2005-wj}, forms the basis of the 3D-MLSI software package~\cite{Khapaev1997-kw, Khapaev2001-xq, Khapaev2001-pw, Khapaev2002-ev}, which is also written in C and is not open-source.
+A 2D London-Maxwell approach based on a scalar stream function, much like the approach used by \SuperScreen~\cite{Brandt2004-ew, Brandt2005-wj}, forms the basis of the 3D-MLSI software package~\cite{Khapaev1997-kw, Khapaev2001-xq, Khapaev2001-pw, Khapaev2002-ev}, which is also written in C and is not open-source.
 For a thorough historical overview and comparison of inductance extraction tools, see Ref.~\cite{Gaj1999-ls}.
@@
 Code Block~\ref{code:washer} demonstrates how to solve this problem using \SuperScreen.
-The inductance extracted using \SuperScreen is within 1\% of the inductance extracted using InductEx.
+The inductance extracted using \SuperScreen, $L=19.91\,\mathrm{pH}$, is within 1\% of the inductance extracted using InductEx.
 
@@
 \end{minted}
-\captionof{listing}{\SuperScreen script to calculate the self-inductance of a square washer.
+\captionof{listing}{\SuperScreen script to calculate the self-inductance of a square washer with outer dimension $30\,\um$, inner dimension $10\,\um$, London penetration depth $\lambda=0.24\,\um$, and film thickness $d=0.20\,\um$.
 The extracted inductance $L=19.91\,\mathrm{pH}$ differs from the InductEx ``design'' and ``extracted'' values by -0.45\% and -0.92\% respectively~\cite{inductex_user_manual_2020}.

### 2022-06-06 response-to-reviewer-comments.tex
Updates from Overleaf

@@
 \usepackage{amsmath}  % This package allows the use of a large range of mathematical formula, commands, and symbols
-\usepackage{graphicx}  % This package allows the importing of images
+\usepackage{ulem,xcolor}
 
@@
 \maketitle
+
+In the revised manuscript, text that should be removed is shown in \textcolor{red}{red} with a strikethough, \textcolor{red}{\sout{like this}}, and text that has been modified or added is shown in \textcolor{blue}{blue, like this}.
 
@@
 
-    {\bf Author response:} Reference [16] (Gaj, \emph{et al.}) is indeed a bit old.
+    {\bf Author response:} Reference [16] (Gaj, \textit{et al.}) is indeed a bit old.
 We have added more recent references about inductance extraction tools to Appendix A.
-In particular, Tolpygo, \emph{et al.} 2021 Supercond.
+In particular, Tolpygo, \textit{et al.} 2021 Supercond.
 Sci.
@@
 In terms of surveying available software tools, we have added more recent references about inductance extraction tools to Appendix A.
-In particular, Tolpygo, \emph{et al.} 2021 Supercond.
+In particular, Tolpygo, \textit{et al.} 2021 Supercond.
 Sci.
@@
 
-\section{Inhomogeneous films}
+\section{Inhomogeneous films (Appendix C)}
 
@@
 We also removed from Appendix C the example code (Code Block 3: Simulating an inhomogeneous superconducting device) and the accompanying Figure C.7.
-The main results of the manuscript are completely unchanged.
+The main results of the manuscript are unchanged.
 \end{document}

### 2022-06-06 highlights.tex
Updates from Overleaf

@@
     \item{The package can be used to calculate self- and mutual inductance in thin film superconducting devices.}
-    \item{SuperScreen can be used to model flux trapping and fluxoid quantization effects and calculate the supercurrent distribution due to Pearl vortices in two-dimensional superconductors.}
+    \item{SuperScreen can be used to model flux trapping and fluxoid quantization effects, and calculate the supercurrent distribution due to Pearl vortices in two-dimensional superconductors.}
     \item{SuperScreen enables quantitative modeling of the supercurrent distribution in mesoscopic superconducting devices to help inform and interpret measurements.}

### 2022-06-06 main.tex
Updates from Overleaf

@@
 % \documentclass[final,5p,times,twocolumn]{elsarticle}
+
+\usepackage{ulem,xcolor}
 
@@
 Here, we introduce \SuperScreen, an open-source Python package for simulating the response of 2D superconductors to trapped flux and applied time-independent or quasi-DC magnetic fields for any value of the effective magnetic penetration depth, $\Lambda$.
-Given an applied magnetic field, \SuperScreen solves the 2D London equation using an efficient matrix inversion method~\cite{Brandt2004-ew, Brandt2005-wj} to obtain the Meissner currents and magnetic fields in and around structures composed of one or more superconducting thin films of arbitrary geometry.
-\SuperScreen can be used to model screening effects and calculate self- and mutual-inductance in thin film superconducting devices.
+Given an applied magnetic field, \SuperScreen solves the 2D London equation using an efficient matrix inversion method~\cite{Brandt2004-ew, Brandt2005-wj} to obtain the Meissner currents and magnetic fields in and around structures composed of one or more superconducting thin films of arbitrary geometry \textcolor{red}{\sout{with spatially nonuniform magnetic penetration depth}}.
+\SuperScreen can be used to model screening effects and calculate self- and mutual-inductance in thin film superconducting devices\textcolor{red}{\sout{, and simulate the magnetic response of inhomogeneous 2D superconductors}}.
 \end{abstract}
@@
 \SuperScreen is a Python package developed to simulate the static magnetic response of structures composed of one or more layers containing superconducting thin films characterized by a London penetration depth $\lambda$ that is large compared to the film thickness $d$.
-\SuperScreen solves the coupled Maxwell's and London's equations in and around superconducting films in the presence of inhomogeneous applied magnetic fields, pinned vortices, and trapped flux using a matrix inversion method introduced by Brandt and Clem~\cite{Brandt2004-ew,Brandt2005-wj} and subsequently used by Kirtley, \emph{et al.} to model the magnetic response of scanning superconducting quantum interference device (SQUID) sensors~\cite{Kirtley2016-zz, Kirtley2016-gt}.
+\SuperScreen solves the coupled Maxwell's and London's equations in and around superconducting films in the presence of inhomogeneous applied magnetic fields, pinned vortices, and trapped flux using a matrix inversion method introduced by Brandt and Clem~\cite{Brandt2004-ew,Brandt2005-wj} and subsequently used by Kirtley, \textit{et al.} to model the magnetic response of scanning superconducting quantum interference device (SQUID) sensors~\cite{Kirtley2016-zz, Kirtley2016-gt}.
 
 There have been many previous numerical studies of magnetic screening and inductance extraction in thin film and two-dimensional (2D) superconducting devices~\cite{Jaycox1981-zl, Ketchen1982-at, Ketchen2012-mb, Hildebrandt1995-uw, Khapaev1997-kw, Khapaev2001-xq, Khapaev2001-pw, Khapaev2002-ev,  Babaei_Brojeny2003-la, Brandt2004-ew, Brandt2005-wj, Clem2005-ye, Muller2021-ci, Fourie2011-wl, Fourie2012-gv, Jackman2016-mf}.
-However, few software tools for this task exist and those that are available are closed-source, are written in low-level compiled languages like C, and/or require the use of specialized file formats or separate computer aided design (CAD) software for defining device geometries and model configurations.\footnote{A brief summary of existing tools can be found in \ref{appendix:other-tools}, and a more thorough overview in Ref.~\cite{Gaj1999-ls}.} Most of these tools are intended for use in the design of superconducting integrated circuits for single flux quantum (SFQ) logic and are primarily used for inductance extraction~\cite{Gaj1999-ls, Tolpygo2021-jz}.
+However, few software tools for this task exist and those that are available are closed-source, are written in low-level compiled languages like C, and/or require the use of specialized file formats or separate computer aided design (CAD) software for defining device geometries and model configurations.\footnote{A brief summary of existing tools can be found in \ref{appendix:other-tools}\textcolor{red}{\sout{, and a more thorough overview in Ref.~\cite{Gaj1999-ls}}}.} Most of these tools are intended for use in the design of superconducting integrated circuits for single flux quantum (SFQ) logic and are primarily used for inductance extraction~\cite{Gaj1999-ls, Tolpygo2021-jz}.
 \SuperScreen is an open-source, user-friendly, portable research tool designed to lower the barrier to entry to quantitative modeling of 2D superconductors, and to help interpret and inform measurements of superconducting thin films and devices.
@@
 A convenient method for solving this problem was introduced by Brandt and Clem in Ref.~\cite{Brandt2004-ew}, expanded by Brandt in Ref.~\cite{Brandt2005-wj}, and subsequently used to model the magnetic response of scanning SQUID susceptometers~\cite{Kirtley2016-zz, Kirtley2016-gt}.
-In the London model of superconductivity, the magnetic field $\vec{H}(\vec{r})$ and 3D current density $\vec{j}(\vec{r})$ in a superconductor with London penetration depth $\lambda$ obey the second London equation:
-$\vec{H}(\vec{r})-\lambda^2\vec{\nabla}\times\vec{j}(\vec{r})=$, where
+In the London model of superconductivity, the magnetic field $\vec{H}(\vec{r})$ and 3D current density $\vec{j}(\vec{r})$ in a superconductor with London penetration depth \textcolor{blue}{$\lambda$ obey the second London equation:
+$\vec{H}(\vec{r})/\lambda^2=-\vec{\nabla}\times\vec{j}(\vec{r})$}, where
 $\vec{\nabla}=\left(\frac{\partial}{\partial x}, \frac{\partial}{\partial y}, \frac{\partial}{\partial z}\right)$ is the 3D gradient operator.
@@
 is the thickness of the film, the second London equation reduces to
+\begin{color}{blue}
 \begin{equation}
@@
 \end{equation}
-where $\Lambda=\lambda^2/d$ is the effective penetration depth
+\end{color}
+where \textcolor{blue}{$\Lambda=\lambda^2/d$} is the effective penetration depth
 of the superconducting film (equal to half the Pearl length~\cite{Pearl1964-cl}) and $\vec{\nabla}=\left(\frac{\partial}{\partial x}, \frac{\partial}{\partial y}\right)$ is now the 2D gradient operator.
@@
 It is important to note that the assumption $\vec{j}(x, y, z)\approx\vec{j}_{z_0}(x, y)$ is valid for only films that are thinner than their London penetration depth ($d\ll\lambda$, such that $\Lambda=\lambda^2/d\gg\lambda$).
-However the model has been applied with some success in structures with $\lambda\lesssim d$, for example by Kirtley, \emph{et al.} in modeling the magnetic response of scanning SQUID susceptometers~\cite{Kirtley2016-zz,Kirtley2016-gt}.
+However the model has been applied with some success in structures with $\lambda\lesssim d$, for example by Kirtley, \textit{et al.} in modeling the magnetic response of scanning SQUID susceptometers~\cite{Kirtley2016-zz,Kirtley2016-gt}.
 Aside from this limitation, the method described below can be used to model films with any effective penetration depth $0\leq\Lambda<\infty$.
@@
 where we exclude points in the mesh lying outside of the superconducting film but keep points
-inside holes in the film. $\mathbf{\nabla}^2$
+inside holes in the film. \textcolor{red}{\sout{$\mathbf{\Lambda}$ is either a scalar or a vector defining the
+effective penetration depth at every included vertex in the mesh, and }}$\mathbf{\nabla}^2$
 is the Laplace operator, a $p\times p$ matrix defined such that $\mathbf{\nabla}^2\mathbf{f}$ computes the Laplacian $\nabla^2f(x,y)$ of a scalar field $f(x,y)$ defined on the mesh vertices (see~\ref{appendix:laplace}).
@@
 The ``flux part''  $\int_S\mu_0H_z(\vec{r})\,\mathrm{d}^2r$ is calculated using \inline{Solution.polygon_flux()}, which computes the flux through a polygon representing a region $S$ as $\Phi_S=\sum_{i\in S} \mu_0H_{z,i}w_i$, where $H_{z,i}$ is the magnetic field at vertex $i$ (recall that $w_i$ assigns an effective area to mesh vertex $i$).
-The ``supercurrent part'' $\oint_S\mu_0\Lambda\vec{J}(\vec{r})\cdot\mathrm{d}\vec{r}$ is calculated by evaluating the vector current density $\vec{J}$ at each point in the path $\partial S$ using \inline{Solution.interp_current_density()}, then computing the line integral along the path using the trapezoid rule.
+The ``supercurrent part'' \textcolor{blue}{$\oint_S\mu_0\Lambda\vec{J}(\vec{r})\cdot\mathrm{d}\vec{r}$} is calculated by evaluating the vector current density $\vec{J}$ at each point in the path $\partial S$ using \inline{Solution.interp_current_density()}, then computing the line integral along the path using the trapezoid rule.
 The sum of these two terms gives the fluxoid $\Phi^f_S$.
@@
 
-The ability to model and visualize screening effects in 2D superconductors and devices constructed from superconducting thin films can help to build intuition about these systems, aid in interpretation of measurement results, and enable optimization of measurement and device design.
+The ability to model and visualize screening effects in \textcolor{red}{\sout{inhomogeneous} }2D superconductors and devices constructed from superconducting thin films can help to build intuition about these systems, aid in interpretation of measurement results, and enable optimization of measurement and device design.
 \SuperScreen is an open-source, user-friendly, portable, and efficient tool that solves this problem.
-Applications of the package include calculating self- and mutual-inductance in planar and multi-planar superconducting circuits, and modeling the magnetic interaction between superconducting samples and superconducting sensors such as scanning SQUID susceptometers~\cite{Kirtley2016-zz}.
+Applications of the package include calculating self- and mutual-inductance in planar and multi-planar superconducting circuits, and modeling the magnetic interaction between \textcolor{red}{\sout{inhomogeneous} }superconducting samples and superconducting sensors such as scanning SQUID susceptometers~\cite{Kirtley2016-zz}.
 
@@
 FastHenry executables compiled for several common operating systems are available as part of the open-source XicTools superconducting integrated circuit design suite from Whiteley Research, Inc~\cite{wrcad, XicTools}.
-A 2D London-Maxwell approach based on a scalar stream function, much like the approach used by \SuperScreen~\cite{Brandt2004-ew, Brandt2005-wj}, forms the basis of the 3D-MLSI software package~\cite{Khapaev1997-kw, Khapaev2001-xq, Khapaev2001-pw, Khapaev2002-ev}, which is also written in C and is not open-source.
+A 2D \textcolor{blue}{London-Maxwell approach based on a scalar stream function, much like the approach} used by \SuperScreen~\cite{Brandt2004-ew, Brandt2005-wj}, forms the basis of the 3D-MLSI software package~\cite{Khapaev1997-kw, Khapaev2001-xq, Khapaev2001-pw, Khapaev2002-ev}, which is also written in C and is not open-source.
 For a thorough historical overview and comparison of inductance extraction tools, see Ref.~\cite{Gaj1999-ls}.
-For a more recent overview of superconducting inductance extraction tools see Ref.~\cite{Tolpygo2021-jz}, particularly references [8--25] therein.
-
-\SuperScreen is not intended primarily as an inductance extraction tool and cannot be used to extract the inductance of superconducting transmission lines (a common superconducting circuit design task~\cite{Gaj1999-ls,Khapaev1996-uu,Tolpygo2021-jz}) due to the lack of support for ``terminal currents.'' Nevertheless, it is instructive to compare \SuperScreen to a state of the art commercial inductance extraction tool, InductEx~\cite{Fourie2011-wl, Fourie2012-gv, Jackman2016-mf}, on a problem that can be solved using both tools.
+\textcolor{blue}{For a more recent overview of superconducting inductance extraction tools see Ref.~\cite{Tolpygo2021-jz}, particularly references [8--25] therein.}
+
+\textcolor{blue}{\SuperScreen is not intended primarily as an inductance extraction tool and cannot be used to extract the inductance of superconducting transmission lines (a common superconducting circuit design task~\cite{Gaj1999-ls,Khapaev1996-uu,Tolpygo2021-jz}) due to the lack of support for ``terminal currents.'' Nevertheless, it is instructive to compare \SuperScreen to a state of the art commercial inductance extraction tool, InductEx~\cite{Fourie2011-wl, Fourie2012-gv, Jackman2016-mf}, on a problem that can be solved using both tools.
 One such problem, provided as an example in the InductEx user manual, is the self-inductance $L$ of a square washer with outer dimension $30\,\um$, inner dimension $10\,\um$, London penetration depth $\lambda=0.24\,\um$, and film thickness $d=0.20\,\um$, for which the InductEx solution reports a ``design'' value of $L=20\,\mathrm{pH}$ and an ``extracted'' value of $L=20.0956\,\mathrm{pH}$~\cite{inductex_user_manual_2020}.
 Code Block~\ref{code:washer} demonstrates how to solve this problem using \SuperScreen.
-The inductance extracted using \SuperScreen, $L=19.91\,\mathrm{pH}$, is within 1\% of the inductance extracted using InductEx.
+The inductance extracted using \SuperScreen, $L=19.91\,\mathrm{pH}$, is within 1\% of the inductance extracted using InductEx.}
 
@@
 \end{minted}
-\captionof{listing}{\SuperScreen script to calculate the self-inductance of a square washer with outer dimension $30\,\um$, inner dimension $10\,\um$, London penetration depth $\lambda=0.24\,\um$, and film thickness $d=0.20\,\um$.
-The extracted inductance $L=19.91\,\mathrm{pH}$ differs from the InductEx ``design'' and ``extracted'' values by -0.45\% and -0.92\% respectively~\cite{inductex_user_manual_2020}.
-}
+\captionof{listing}{\textcolor{blue}{\SuperScreen script to calculate the self-inductance of a square washer with outer dimension $30\,\um$, inner dimension $10\,\um$, London penetration depth $\lambda=0.24\,\um$, and film thickness $d=0.20\,\um$.
+The extracted inductance $L=19.91\,\mathrm{pH}$ differs from the InductEx ``design'' and ``extracted'' values by -0.45\% and -0.92\% respectively~\cite{inductex_user_manual_2020}.}}
 \label{code:washer}
@@
 
-The definitions of the Laplace operator $\mathbf{\nabla}^2$ (also called the Laplace-Beltrami operator) and the gradient operator $\vec{\nabla}=(\nabla_x, \nabla_y)^T$ deserve special attention, as these two operators reduce the problem of solving a partial differential equation to the problem of solving a matrix equation~\cite{Reuter2009-hr}.
-Given a mesh consisting of $p$ vertices and $t$ triangles, and a scalar field $f(x, y)$ represented by a $p\times 1$ vector $\mathbf{f}$ containing the values of the field at the mesh vertices, the goal is to construct matrices $\nabla^2$ and $\vec{\nabla}=(\nabla_x, \nabla_y)^T$ such that the matrix products $\nabla^2\mathbf{f}$ and $\vec{\nabla}\mathbf{f}$ approximate the Laplacian $\left(\frac{\partial^2f}{\partial x^2}+\frac{\partial^2f}{\partial y^2}\right)$ and the gradient $\left(\frac{\partial f}{\partial x}, \frac{\partial f}{\partial y}\right)$  of $f(x, y)$ at the mesh vertices.
+\textcolor{blue}{The definitions of the Laplace operator $\mathbf{\nabla}^2$ (also called the Laplace-Beltrami operator) and the gradient operator $\vec{\nabla}=(\nabla_x, \nabla_y)^T$ deserve special attention, as these two operators reduce the problem of solving a partial differential equation to the problem of solving a matrix equation~\cite{Reuter2009-hr}.
+Given a mesh consisting of $p$ vertices and $t$ triangles, and a scalar field $f(x, y)$ represented by a $p\times 1$ vector $\mathbf{f}$ containing the values of the field at the mesh vertices, the goal is to construct matrices $\nabla^2$ and $\vec{\nabla}=(\nabla_x, \nabla_y)^T$ such that the matrix products $\nabla^2\mathbf{f}$ and $\vec{\nabla}\mathbf{f}$ approximate the Laplacian $\left(\frac{\partial^2f}{\partial x^2}+\frac{\partial^2f}{\partial y^2}\right)$ and the gradient $\left(\frac{\partial f}{\partial x}, \frac{\partial f}{\partial y}\right)$  of $f(x, y)$ at the mesh vertices.}
 
@@
 
-We construct the two $p\times p$ gradient matrices $\nabla_x$ and $\nabla_y$, using the ``average gradient on a star" (or AGS) approach~\cite{Mancinelli2019-ci}.
+\textcolor{blue}{We construct the two $p\times p$ gradient matrices $\nabla_x$ and $\nabla_y$, using the ``average gradient on a star" (or AGS) approach~\cite{Mancinelli2019-ci}.
 Briefly, we first construct two $t\times p$ matrices, $\vec{\nabla}_t=(\nabla_{t,x}, \nabla_{t,y})^T$ using ``per-cell linear estimation'' (or PCE)~\cite{Mancinelli2019-ci}, where $\nabla_{t,x}\mathbf{f}$ maps the field values at the vertices $\mathbf{f}$ to an estimate of the $x$-component of the gradient at the triangle centroids (centers-of-mass).
 The matrices $\nabla_x$ and $\nabla_y$ are then computed by, for each vertex $i$, taking the weighted average of $\nabla_{t,x}$ and $\nabla_{t,y}$ over adjacent triangles $t\in\mathcal{N}(i)$, with weights given by the angle between the two sides of the triangle adjacent to the vertex.
-The resulting $\vec{\nabla}=(\nabla_x, \nabla_y)^T$ is a $2\times p\times p$ stack of matrices defined such that $\vec{\nabla}\mathbf{f}$ produces a $2\times p$ matrix representing the gradient of $f(x, y)$ at the mesh vertices, with the first and second rows of $\vec{\nabla}\mathbf{f}$ containing the $x$ and $y$ components of the gradient, respectively.
+The resulting $\vec{\nabla}=(\nabla_x, \nabla_y)^T$ is a $2\times p\times p$ stack of matrices defined such that $\vec{\nabla}\mathbf{f}$ produces a $2\times p$ matrix representing the gradient of $f(x, y)$ at the mesh vertices, with the first and second rows of $\vec{\nabla}\mathbf{f}$ containing the $x$ and $y$ components of the gradient, respectively.}
 
@@
 \label{appendix:inhomogeneous}
-
+\begin{color}{blue}
 The London equation (Equation~\ref{eq:london}) is valid only under the assumption that the London penetration depth $\lambda$, a proxy for the superfluid density, is constant as a function of position~\cite{Tinkham2004-zn}.
@@
 Nevertheless, in an effort to model inhomogeneous superconductors using London theory, one can write out the ``inhomogeneous second London equation'' for a superconductor with spatially-varying London penetration depth $\lambda(\vec{r})$~\cite{Cave1986-js, Kogan2011-zn}:
+
 \begin{align}
@@
 \end{equation}
+\end{color}
 

### 2022-07-18 main.tex
remove \textcolor and fix two typos

--- 2022-06-06 main.tex
@@
 % \documentclass[final,5p,times,twocolumn]{elsarticle}
+
+% \usepackage{ulem,xcolor}
 
@@
 \SuperScreen is a Python package developed to simulate the static magnetic response of structures composed of one or more layers containing superconducting thin films characterized by a London penetration depth $\lambda$ that is large compared to the film thickness $d$.
-\SuperScreen solves the coupled Maxwell's and London's equations in and around superconducting films in the presence of inhomogeneous applied magnetic fields, pinned vortices, and trapped flux using a matrix inversion method introduced by Brandt and Clem~\cite{Brandt2004-ew,Brandt2005-wj} and subsequently used by Kirtley, \emph{et al.} to model the magnetic response of scanning superconducting quantum interference device (SQUID) sensors~\cite{Kirtley2016-zz, Kirtley2016-gt}.
+\SuperScreen solves the coupled Maxwell's and London's equations in and around superconducting films in the presence of inhomogeneous applied magnetic fields, pinned vortices, and trapped flux using a matrix inversion method introduced by Brandt and Clem~\cite{Brandt2004-ew,Brandt2005-wj} and subsequently used by Kirtley, \textit{et al.} to model the magnetic response of scanning superconducting quantum interference device (SQUID) sensors~\cite{Kirtley2016-zz, Kirtley2016-gt}.
 
 There have been many previous numerical studies of magnetic screening and inductance extraction in thin film and two-dimensional (2D) superconducting devices~\cite{Jaycox1981-zl, Ketchen1982-at, Ketchen2012-mb, Hildebrandt1995-uw, Khapaev1997-kw, Khapaev2001-xq, Khapaev2001-pw, Khapaev2002-ev,  Babaei_Brojeny2003-la, Brandt2004-ew, Brandt2005-wj, Clem2005-ye, Muller2021-ci, Fourie2011-wl, Fourie2012-gv, Jackman2016-mf}.
-However, few software tools for this task exist and those that are available are closed-source, are written in low-level compiled languages like C, and/or require the use of specialized file formats or separate computer aided design (CAD) software for defining device geometries and model configurations.\footnote{A brief summary of existing tools can be found in \ref{appendix:other-tools}, and a more thorough overview in Ref.~\cite{Gaj1999-ls}.} Most of these tools are intended for use in the design of superconducting integrated circuits for single flux quantum (SFQ) logic and are primarily used for inductance extraction~\cite{Gaj1999-ls, Tolpygo2021-jz}.
+However, few software tools for this task exist and those that are available are closed-source, are written in low-level compiled languages like C, and/or require the use of specialized file formats or separate computer aided design (CAD) software for defining device geometries and model configurations.\footnote{A brief summary of existing tools can be found in \ref{appendix:other-tools}.} Most of these tools are intended for use in the design of superconducting integrated circuits for single flux quantum (SFQ) logic and are primarily used for inductance extraction~\cite{Gaj1999-ls, Tolpygo2021-jz}.
 \SuperScreen is an open-source, user-friendly, portable research tool designed to lower the barrier to entry to quantitative modeling of 2D superconductors, and to help interpret and inform measurements of superconducting thin films and devices.
@@
 Finally, in Section~\ref{section:conlusion} we conclude by discussing applications, limitations, and possible extensions of the package.
-Python scripts and Jupyter notebooks used to generate all figures presented below can be found in the GitHub repository accompanying this manuscript~\cite{logan_bishop_van_horn_2022_6363541}.
 
@@
 In the London model of superconductivity, the magnetic field $\vec{H}(\vec{r})$ and 3D current density $\vec{j}(\vec{r})$ in a superconductor with London penetration depth $\lambda$ obey the second London equation:
-$\vec{H}(\vec{r})-\lambda^2\vec{\nabla}\times\vec{j}(\vec{r})=$, where
+$\vec{H}(\vec{r})/\lambda^2=-\vec{\nabla}\times\vec{j}(\vec{r})$, where
 $\vec{\nabla}=\left(\frac{\partial}{\partial x}, \frac{\partial}{\partial y}, \frac{\partial}{\partial z}\right)$ is the 3D gradient operator.
@@
 is the thickness of the film, the second London equation reduces to
+
 \begin{equation}
     \label{eq:london}
-    \vec{H}(x, y)=-\Lambda\vec{\nabla}\times\vec{J}(x, y)\\
+    \vec{H}(x, y)=-\Lambda\vec{\nabla}\times\vec{J}(x, y)
 \end{equation}
@@
 \captionof{listing}{\SuperScreen script to calculate the self-inductance of a square washer with outer dimension $30\,\um$, inner dimension $10\,\um$, London penetration depth $\lambda=0.24\,\um$, and film thickness $d=0.20\,\um$.
-The extracted inductance $L=19.91\,\mathrm{pH}$ differs from the InductEx ``design'' and ``extracted'' values by -0.45\% and -0.92\% respectively~\cite{inductex_user_manual_2020}.
-}
+The extracted inductance $L=19.91\,\mathrm{pH}$ differs from the InductEx ``design'' and ``extracted'' values by -0.45\% and -0.92\% respectively~\cite{inductex_user_manual_2020}.}
 \label{code:washer}
@@
 When $\delta z\lesssim\delta r$, the model significantly overestimates the mutual inductance.
-({\bf b}) and ({\bf c}): Out-of-plane magnetic field $\mu_0H_z$ evaluated at the plane of the pickup loop (W1 layer) for ({\bf b}) the nominal layer spacing with $\delta z<\delta 2$ (indicated with a black $\times$ in ({\bf a})) and ({\bf c}) $\delta z > \delta r$ (indicated with a black $+$ in ({\bf a})).
-For $\delta r\lesssim\delta z$, the magnet field calculated using Eq.~\ref{eq:hz-from-kernel} resembles that of a discrete set of isolated dipoles rather than a continuous sheet of current.
+({\bf b}) and ({\bf c}): Out-of-plane magnetic field $\mu_0H_z$ evaluated at the plane of the pickup loop (W1 layer) for ({\bf b}) the nominal layer spacing with $\delta z<\delta r$ (indicated with a black $\times$ in ({\bf a})) and ({\bf c}) $\delta z > \delta r$ (indicated with a black $+$ in ({\bf a})).
+For $\delta r\lesssim\delta z$, the magnetic field calculated using Eq.~\ref{eq:hz-from-kernel} resembles that of a discrete set of isolated dipoles rather than a continuous sheet of current.
 Note that ({\bf b}) and ({\bf c}) share the same color scale, which is saturated in ({\bf b}).}

### 2022-07-27 main.tex
overleaf changes

@@
         &\underbrace{\vec{H}(\vec{r})\cdot\hat{z} = H_z(\vec{r})
-        = \Lambda\nabla^2g)}_{z-\text{component of the total field}}
+        = \Lambda\nabla^2g(\vec{r})}_{z-\text{component of the total field}}
         = \\ & \underbrace{H_{z,\,\mathrm{applied}}(\vec{r})}_{\text{applied field}}
@@
 \label{section:acknowledgements}
-We acknowledge useful discussions with John R. Kirtley. This work is supported by the Department of Energy
-,  Office of Science, Basic Energy Sciences, Materials Sciences and Engineering Division, under Contract DE-AC02-76SF00515.
+We acknowledge useful discussions with John R.
+Kirtley.
+This work is supported by the Department of Energy, Office of Science, Basic Energy Sciences, Materials Sciences and Engineering Division, under Contract DE-AC02-76SF00515.
 Some of the computing for this project was performed on the Sherlock cluster.
